### 2023-12-28 chapter4/ms.tex
Initial Overleaf Import

%UNLIKE IN A REGULAR TEX FILE, DON'T PUT ANY PREAMBLE MATERIAL HERE

%NOTE THE LACK OF A BIBLIOGRAPHY CALL IN THIS FILE. BIBLIOGRAPHY WORK HAPPENS OUTSIDE THE CHAPTER TEX FILES.

### 2023-12-28 chapter5/ms.tex
Initial Overleaf Import

%UNLIKE IN A REGULAR TEX FILE, DON'T PUT ANY PREAMBLE MATERIAL HERE

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Aditya-L1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Solar Ultraviolet Imaging Telescope}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SUIT \& Solar Flares}\label{sec:suit_and_flare}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Solar flares are the most powerful magnetic events in the solar system. They are described as a sudden increase in brightness in localized areas on Sun. Within tens of minutes, they can release over $10^{32}$ erg of energy, which is emitted across the entire electromagnetic spectrum from radio to gamma rays. They can also launch high energetic particles into the interplanetary medium. Most of the flares occur in magnetic active regions, and the amount of flare energy released is comparable to the free energy stored in the magnetic system. The term "flare" is generally used explicitly for the entire magnetically-driven event's electromagnetic radiation, as it is the most significant fraction of the total energy liberated. The total energy released varies from event to event. It is also known that larger events occur much less frequently than smaller events.

The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1} of the Indian Space Research Organization (ISRO). With its 11 science filters (3 broadband and eight narrowband), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another. SUIT will provide full disk as well as partial disk images of the Sun with a pixel size of 0.7". Through SUIT imaging, we would be able to resolve solar flares spatially on the surface of the Sun, for the first time in near ultra-violet (NUV), which will help us to address the questions regarding their build-up and triggering mechanism. In addition, to measure the spatially resolved solar spectral irradiance within the wavelength range that is central for studying the Chemistry of oxygen and ozone in the Stratosphere of Earth's atmosphere.

It has been shown that the majority of flare energy emerges at the visible and UV wavelength range \citep{woods06}. \cite{woods04} showed that about 77\% of the energy is released in the wavelength range > 200 nm, and only ~ 23\% is seen in extreme ultraviolet (EUV) and soft X-ray (SXR), i.e., below 200 nm \citep{Nei_1989,neidig93,kretzschmar11}. Although the energy content in hard X-ray (HXR) is a tiny fraction of the total energy budget, they are still crucial in understanding the energization process \citep{holeman11}. However, to develop a comprehensive understanding of solar flares, it is mandatory to perform multi-wavelength studies of all kinds of flares. This may have implications on the physics of the origin of solar flares and different physics processes and contribute to the solar spectral irradiance as a function of the solar activity cycle. Although we have been observing Sun and Solar flares in various wavelengths, the spectral energy distribution of the radiated energy from the flares is still very poorly understood. The first solar flares were observed from the ground in the visible domain \citep{carrington1859,neidig93}. It is also well known that the flare emission in the visible domain occurs mainly in $H\alpha$ and Ca \Romannum{2} lines \citep{canfield90,falchi92,heinzel94}. However, the lesser understood component of the visible and Near Ultra Violet (NUV) emission is the enhancement of the continuum. The study of the white-light (WL) flares has proven to be very difficult because they have a very short duration and low contrast against the background, making their observation from Earth rare and of poor quality. Also, the flares in NUV are not observable from any ground-based instrumentation as most of the NUV gets absorbed in the upper atmosphere, thus requires space-based observations.

The origin of the WLFs, i.e., the physical process responsible for generating the continuum and its contribution to the overall energy distribution, is still highly uncertain. The question remains whether WLFs are photospheric phenomena due to $H^{-}$ free-free emission or chromospheric phenomena due to H free-bound emission. The more recent studies further constrain the origin of the WLFs to be Chromospheric phenomena, as it has been shown that the WL and HXR footpoint centroids are cospatial. Similarly, \cite{krucker15} constrained the cospatial WL and HXR footpoints within the chromosphere for three flares. With the help of SUIT, we would be able to localize the WL flares and resolve them on various parts of the Solar disk, which along with observations from Interface Region Imaging Telescope (IRIS), Helioseismic and Magnetic Imager (HMI), would help us localize the source of the WL footpoints and also comment on the formation mechanism of the WL itself.

\begin{figure}
    \centering
    \includegraphics[width = \linewidth]{Figures/Krucker_2015_ApJ_802_19_page-0004.jpg}
    \caption{X-ray and optical imaging of the three flares at the peak time of the impulsive phase: the images are from HMI with the pre-flare image subtracted. The contours represent RHESSI Clean maps in the thermal (red, 12–15 keV) and non-thermal (blue, 30–80 keV) HXR range \citep{krucker15}.}
    \label{fig1}
\end{figure}

The spectral energy distribution of flares is one of the critical areas of interest in the physics of flares. A complete understanding of this will help us decode the physical processes involved in solar flares and help quantify their effects on solar spectral irradiance. Ideally, it would be essential to observe flares at all wavelengths simultaneously with sufficient spatiotemporal resolution to figure out the spectral energy distribution of flares. Unfortunately, this is generally not the case, and we have to rely on the sporadic observations made using ground-based instruments in the visible domain. As mentioned earlier, the majority of the flare energy is emitted in the NUV and visible domain. \cite{kretzschmar10,kretzschmar11}, performed statistical studies using a large number of flare observations across a wide energy range. They demonstrated, at the peak of the flare, about 70\% of the total energy was radiated in the continuum visible and NUV channel as illustrated in \ref{tab1}. SUIT would observe and resolve the solar flares within 200-400 nm using 8 NBs and 3 BBs. This, along with IRIS data, would help us comment on the energy distribution of flares of various classes.

%%--------------------------------------------%%
\begin{table}[]
    \centering
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{||m{.1\linewidth}|m{.15\linewidth}|m{.17\linewidth}|m{.17\linewidth}|m{.17\linewidth}|m{.15\linewidth}||}
    \hline
    \hline
        Mean X-ray class & TSI(ergs) & Ratio $\frac{26-34nm}{TSI}$ & Ratio $\frac{0-50nm}{TSI}$ & Ratio $\frac{0.1-0.8nm}{TSI}$ & Ratio $\frac{continuum}{TSI}$\\
        \hline
        X3.2 & 5.9$\times~10^{31}$ & 0.9-0.8\% & 12-9\% & 1.2-1\% & 67\% \\
        M9.1 & 1.6$\times~10^{31}$ & 1.7-0.4\% & 23-5\% & 1-0.4\% & 85\% \\
        M4.2 & 1.3$\times~10^{31}$ & 2.2-0.5\% & 18-6\% & 0.6-0.3\% & 74\% \\
        M2.0 & 5.1$\times~10^{30}$ & 1.7-0.6\% & 18-6\% & 0.7-0.4\% & 69\% \\
        C8.7 & 3.6$\times~10^{30}$ & 1.5-0.5\% & 16-5\% & 0.4-0.2\% & 72\% \\
        \hline
    \end{tabular}}
    \caption{Spectral Energy Distribution from a sample of 2100 flares across various wavelengths\citep{kretzschmar11}.}
    \label{tab1}
\end{table}
%%--------------------------------------------%%

Finally, one of the major question of interest is how the Solar flares affect the Spectral Solar Irradiance (SSI) and Total Solar Irradiance (TSI) variability from a short to much longer, Solar Cycle timescale. \cite{kretzschmar10,kretzschmar11} performed statistical studies using a large number of flare observations across a wide energy range. For this purpose, they used the full Sun observations of Solar flux from Solar and Heliospheric Observatory (SoHO), three visible Solar irradiances from VIRGO/Solar Photometer (SPM) passbands centred on 402 nm, 500 nm, and 862 nm, respectively, from 1996 to 2008. Additionally, they also use the EUV irradiance in the ranges 0.1-50 nm and 26-34 nm measured by SOHO/Solar EUV Monitor \citep{judge98} and SXR measurements from GOES satellites. They showed that stacked TSI variation profiles during solar flares show variation at more than 2 sigma level during the peak flare time, indicating the presence of flare signals in the TSI measurements.

\begin{figure}[h!]
    \centering
    \includegraphics[width = \linewidth]{Figures/nphys1741_page-0002.jpg}
    \caption{Averaged TSI variations during flares. The TSI time-series averages over four exclusive sets of solar flares of decreasing amplitude. The black and pink curves correspond respectively to the TSI measured by the PMOV6 and the DIARAD radiometers. The dashed lines correspond to the 95\% confidence levels, while the vertical line denotes the peak time of the flare \citep{kretzschmar10}.}
    \label{fig2}
\end{figure}

This allows us to quantify the solar variability induced be solar flares of various timescales. With the help of SUIT, we would be able to localize the flare locations and study the change in SSI from the local environment in the 11 science filters. This information combined with TSI measurements can allow us to quantify the effect of flares of various energy scales on the TSI variability of the Sun. As, both the TSI and SSI variability directly or indirectly couples with various atmospheric parameters, we can also study the effect the flares have on them. For example, the Earth's atmospheric chemistry and composition respond to any changes in solar UV output in a very nonlinear fashion \citep{haigh07}. Since the number of flares also shows a change with solar activity, it is prudent to ask how much flares contribute to the solar spectral irradiance in NUV. This is particularly important because the irradiance in NUV plays a key role in heating the upper and middle layers of the Earth's atmosphere directly and their coupling with Stratosphere. It also directly influences the middle and lower atmosphere chemistry and composition via the Ozone-Oxygen cycle.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Throughput model and imaging performance of SUIT}\label{sec:suit_imaging}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Filter Choice for SUIT}\label{sec:filter_choice}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Photometric, Radiometric \& Spectral Calibration of SUIT}\label{sec:suit_cal}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%NOTE THE LACK OF A BIBLIOGRAPHY CALL IN THIS FILE. BIBLIOGRAPHY WORK HAPPENS OUTSIDE THE CHAPTER TEX FILES.

### 2023-12-28 introduction/intro.tex
Initial Overleaf Import

The Sun is our nearest astrophysical object, which serves as a natural laboratory for various branches of Physics - atomic physics, spectroscopy, turbulence, magnetohydrodynamics, stellar evolution, dynamo and magnetism and plays a key role in space and terrestrial weather. The Sun is also the primary source of light and energy on earth. So it is only natural that we try to understand the different physical processes involved in the energectics of the Sun, which indirecrtly affects life on Earth. In this chapter I briefly introudce the Sun and various layers of its atmosphere. At the end we provide a motivation for the thesis.

The Sun is a G2V star, with surface luminosity $3.86~\times~10^{26}$ W and an effective temperature of $\sim 5780~K$. The Sun is mostky made out of Hydrogen(92.1\%) and Helium(7.8\%) along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe. The study of the Sun can be mainly divided into three components: the Solar interior, the Solar atmosphere and the Heliosphere.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The solar interiror}\label{solar_int}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the innermost zone of the star the Sun has a temperature of about 15 MK and a density of $1.6~\times~10^{5}~km.m^{-3}$ that fuses Hydrogen into Helium mainly by p-p cycle and to some extent by CNO cycle \sr{Ref here}.

%% ############# %%
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{Figures/solar_int.png}
    \caption{A schematic depiction of the different layers of the Sun. The figure also shows soe of the most prominent magnetic structures on the Sun e.g sunspot, prominence, coronal hole. Credit : NASA/Goddard. \sr{Better pic here.}}
    \label{fig_solar_int}
\end{figure}
%% ############# %%

Fig.~\ref{fig_solar_int} shows a schematic diagram of various layers of the Sun. Beyond the core we have the optically thick radiative zone, where the Hydrogen and Helium are completely ionized \sr{Ref. here}. The high energy $\gamma$-ray photons generated in the core, have very small mean free path in this region, as they collide neumerous times eventually thermalizing becoming visible photon. Beyond the radiative zone the degree of ionization of Hydrogen and Helium changes drastically giving rise to a sharp temperature gardient. This is the convective zone where the energy from the inner layers of the Sun is transported adiabetically to the surface of the Sun. Inbetween the radiative and the convective zone, there is a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine, which is believed to play a major role in generating Sun's magnetic field via the Dynamo process \sr{Ref. here}.

The core and the radiative zone of the Sun rotates as a solid body, whereas the convective zone rotates differentially. The rotation period varies from $\sim~25~days$ to $\sim~35~days$ from the equator to the pole.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The solar atmosphere}\label{solar_atmos}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The layers outside the convection zone together, form the solar atmpshere - the Photosphere, which is also known as the Sun's surface, the Chromosphere, the transition region and the Corona. While we can define geometrical height or depths to define these layers, it is much more useful to define them using the local optical depths of various spectral lines, which are directly used to observe the layers. This also gives us a idea about which spectral features originate mainly from which portions of the solar atmosphere. Fig.~\ref{fig_solar_atm} shows the variation of temperature and number density accross various layers of the Solar atmosphere \sr{Ref. here}.

%% ############# %%
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{Figures/solar_atm.png}
    \caption{The variation of electron temperature (solid line) and electron density (Ne, dashed line) and density of neutral hydrogen atoms (NH, dotted- dashed line) in the solar atmosphere as derived based on the 1-D model calcula- tions by \sr{Ref. here}.}
    \label{fig_solar_atm}
\end{figure}
%% ############# %%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{The Photosphere}\label{photosphere}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Photosphere is defined to be the layer where $\tau_{\lambda~\sim~5000}~=~1$. This is in the green part of the visible spectrum and the Sun is opaque in visible beyond this layer, hence it is called to be the surface of the Sun. This layer is 400-600 km deep and has an effective temperature of 5780 K. The magnetic filed lines arising from the tacholine penetrate the Photosphere and creates a `carpet' over the whole region \sr{(Priest 2014) ref here}. As mentioned earlier, this is the Solar surface known as the `Quite Sun'(QS from hereon). This region exhibits an average magnetic flux density of \textbf{10 -- 50~G}. The QS surface is covered with cells of roughly four size- granule, mesogranules, supergranules and giant cells. Some regions exhibit much sronger magnetic flux density often asociated with highly twisted magnetic field structures. These magnetic features are manifested as sunspots, spcules, bright points etc.

As the density changes drastically at the Photosphere compared to the convective zone, the thermalized photons from Sun's core start freestreaming again, as the mean free path also increases drastically and as a result perturbs the thermal equlibrium (TE from hereon). So, we have to define the thermodynamic quantites of the Photosphere in Local Thermal Equlibrium (LTE from hereon). As we move away from the Photosphere, because the density keeps on decreasing steadily, the LTE conditiobs also start deviating similarly \sr{Ref here}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{The Chromosphere}\label{chromosphere}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Chromosphere is a highly non-uniform dynamic layer with a thickness of 1500~--~3000~km, with increasing temperature (upto $10^{4}$ K) and decreasing numbr density. As seen in the fig. \ref{fig_solar_atm}, the temperature of the Chromosphere saturates before the dramatic rise in the transition region. This saturation is attributed to a steady deposition of accoustic energy by creation of shock waves \sr{Ref. here}. The Chromosphere also exhibits a sharp gradient in the plasma $\beta$ factor, non-LTE conditions, dominance of wave motions \sr{Ref. here}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{The Transition Region}\label{transition-region}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The transition region above the Chromosphere is a thin, dynamic layer where we witness a dramatic increase in temperature by two orders of magnitude along with a similar decrease in electron density by nearly 5-6 orders of magnitude which is demonstrated in fig. \ref{fig_solar_atm}. In general the this layer is roughly $\sim$ 100 km in thickness, but that can change depending on various dynamic conditions of Chromosphere($\sim~10^{4}~K$) below, or Corona($\sim~10^{6}~K$) on top. The transition region is generally characterized by the steep change in the temperature, pressure gradients, drastic change in local optical depth and competition between gas pressure and magnetic pressure. The transition region also manifests the ARs as various magnetic features such as small scale brightenings, jets, spicules, fibrils etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{The Corona}\label{corona}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The outermost layer of the Solar atmosphere is the Corona. The Corona is only visible in naked eyes during the total solar eclipse or via Coronagraphs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solar Flares}\label{sol_flr}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Solar flares are the most powerful magnetic events in the solar system. They are described as a sudden increase in brightness in localized areas on Sun. Within tens of minutes, they can release over $10^{32}$ erg of energy, which is emitted across the entire electromagnetic spectrum from radio to gamma rays. They can also launch high energetic particles into the interplanetary medium. Most of the flares occur in magnetic active regions, and the amount of flare energy released is comparable to the free energy stored in the magnetic system. The term "flare" is generally used explicitly for the entire magnetically-driven event's electromagnetic radiation, as it is the most significant fraction of the total energy liberated. The total energy released varies from event to event. It is also known that larger events occur much less frequently than smaller events.

%% ##################################################### %%
\subsection{Brief history of flare observation}\label{sol_flr_1}
%% ##################################################### %%

In September 1, 1859, R.C. Carrington and R. Hodgson observed the first flare in the continuum of white light\citep{carrington1859,hodgson1859}. The localized brightenings on the Sun have remained an enigma ever since. We have been observing the local flaring events acrsoss all wavelenths from both ground and space based observatories.  Shortly after the observation by Carrington and Hodgson, people started studying the Sun extensively in the H$\alpha$ line which is formed in the Chromosphere, and the reports of flaring events became more and more frequent and progressivly more and more complex. No two events were similar, as there were variations observed in source of size, ejections of plasma along with shockwaves driving into the interplanetary space. Advances of radio technology during the second world war ensured detections of prescence of non-thermal electrons in the solar corona, during military radar operations \citep{hey46}. Around the same time S.E. Forbrush noticed ground level cosmic ray enhancement during major solar flares. These discoveries illuded that the flaring events do not only involve the thermal plasma, but is somehow connects with high energy particles and involves the corona. in the 1950s we started observing the Sun in hard X-rays ($\ge~10~keV$) with rockets and baloons. \cite{peterson59} discovered the first hard X-ray emission during a flare in 1958. Later on, it was deduced from the observations of the enhancements observed in radio and hard X-rays that, the the ejected energetic particles may contain a substantial fraction of the intial energy released \citep{brown71}. The hard X-ray is created by the bremsstrahlung of the electrons colliding into dense material, resulting in a power-law energy distribution. The braodband radio emission from 1 to 100 GHz is created from gyrosynchrotron emission. Finally, observations in EUV and soft X-ray($\le$~10~keV) have shown that the energy released form the flare heats the plasma contained in the coronal loops to temperatures beyond 30 MK.

%% ################################################################# %%
\subsection{Neupert effect}\label{npt_eff}
%% ################################################################# %%

\cite{neupert68} observed a curious corelation that, the soft X-ray flux during the rise phase of the flare is proportional to the time integral of the centimeter radio flux since the start of the flare. The centimeter radio flux is emitted by relativistic electrons. So, later on the same corelation was found between the hard X-ray flux and soft X-ray flux and can be expressed as,

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}\label{npt_eff_eq}
    F_{SXR}(t)~\propto~\int_{t_{0}}^{t}~F_{HXR}(t')~dt'
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This emperical relation is known as the ``Neupert effect''. \cite{neupert68} had already suggested that thismay be due to a causal relationship between the thermal plasma and the energetic electrons. The logical explanation is: the soft X-ray mainly originates from a thermal plasma heated by the energy of the flaring event deposited by the flare acclerated electrons. It is important to mention that we know now, eqn.\ref{npt_eff_eq} is only valid if cooling by conduction of radiation is negligible.

%% ################################################################# %%
\subsection{Standard model of solar flare}\label{sol_flr_std_mod}
%% ################################################################# %%

There were several observations like Neupert effect, which would help us to constrain several phenomenon observed in the flares:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\linewidth]{Figures/phu_63_8_818_f2.jpg}
    \caption{A schematic diagram of the standard model of solar flare.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%
\begin{enumerate}
    \item The magnetic reconnetion happens in corona, releasing the magnetic free energy. Electrons and energetic particles from the reconnetion site are acclerated along the realigned magnetic field lines. The acclerated particles that escape along the open field lines towards the earth gives rise to the particle events seen from earth.
    \item The acclerated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave observations seen from falres via gyromagnetic radiation.
    \item The acclerated particles hit the Chromosphere which is considerably denser than the Corona, giving rise to Hard X-ray and gamma ray observed from the footpoints. This also explains why the coronal hard X-ray source is considerably softer than the footpoints. The energetic particles deposit their energy into the local Chromosphere, as they go through series of collision and eventually thermalize.
    \item  As the plasma thermalizes, it starts emitting in thermal bremsstrahlung giving rise to the soft X-ray observed. Also, as the energy is deposited into the Chromosphere from the acclerated particles, it heats the local Chromosphere environment it gradually increases the local pressure. 
    \item As the pressure grows, when the pressure gradient builds up enough the local plasma starts expanding upwards(essentially due to buoyancy) and slowly fills up the coronal loops with soft X-ray emitting plasma. This phenomenon is known as "Chromospheric evaporation". This was dorectly observed later on, in blue-shifted lines of hot material.
    \item This whole scenario explains the Neupert effect. As the energy form the acclerated particles is converted into the soft X-ray emitting plasma, and it builds up over time. That explains the soft X-ray being proportional to the time integral of the hard X-ray flux.
\end{enumerate}
%%%%%%%%%%%%%%%%%

This whole scenario is known as the ``Standard model of solar flare''. While the standard model is an attempt to explain and unify various kind of differences seen from the neumerous flares we observe, there are several cases where the stnadard model cannot explain the observations. For example, there have been observations of falres where the hard X-ray footpoint do not form. It is proposed that in these cases the plasma in the coronal loops is so dense that the acclerated particle collide enough to thermalize within the flare loops before reaching the Chromosphere, deffusing the energy more evenly within the loop, rather than dumping it at the base of the loops \citep{veronig02,veronig04}. Another flare which previously occured at the same region might explain the denser coronal loops \citep{strong84,bone07}.

%% ################################################################# %%
\subsection{The energectics of solar flares}\label{sol_flr_energ}
%% ################################################################# %%

With an experience of observing solar flares for more than 150 years, remarkably enough, we have barely started scratching the surface of the complexity involved with the solar flares. The reconfiguring of magnetic structure, which almost always involves complex geometry, making almost all events unique in some sense. After that the released magnetic free energy is transported accross various layers of the sun and converted into various other forms of energy. Consodering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses. In case of the eruptive events, there is the added complexity of the kinetic and potential energy of the CMEs, the enrgy of the shcoks and the kinetic energy of the solar energetic particles.

Inorder to constrain the models of solar eruptions and various nuanced aspects of it, like magnetic reconnection, particle accleration, heating etc. detailed quantitative characterization is absolutely necessary. There have been several studies that have tried to quantify the partition between various subsets of the energies. The questions that are perticularly important are:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item \textbf{If an active region can have enough free enrgy to account for the total energy relased in the solar flares and/or CMEs.}
    \item \textbf{What is the energy partition betwen flares and CMEs.}
    \item \textbf{If the non-thermal component have enough energy to power up the thermal component.}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It is generally well known by now that the active region have enough magnetic free energy to power the flare and CME \citep{emslie12,ash17}. The partition of energy between the flare and associated CME is much more fuzzy. \cite{emslie12} found that the flare and CME have energies of same order of magnitude, while \cite{ash17} concluded the flare dominates the CME in-terms of the energy. However the simple question, whether the non-thermal component of the flares have enough enrgy is still not resolved as even the most recent studies contradict each other in the most puzzling fashion. Here I will discuss the contradictions arising from some of the studies\citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17}. The details of the studies can be summarized as follows:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h!]
    \centering
    \hline 
    \hline
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{||c|c|c|c|c|c|c||}
       Study & No. of flares & GOES class range & Thermal model & Thermal spectrum & Thermal volume & Thermal losses \\
       \cite{stosire07} & 18 & A3-B7 & Isotherm. & RHESSI & TRACE & X \\
       \cite{emslie12} & 38 & C5-X28 & Isotherm. & RHESSI & RHESSI & Rad. \\
       \cite{inglis14} & 10 & B3-B9 & Multitherm. & RHESSI+AIA & RHESSI & Rad. \\
       \cite{warmuth16a,warmuth16b} & 24 & C3-X17 & Isotherm. & RHESSI+GOES & RHESSI & Rad.,Cond. \\
       \cite{ash17} & 188 & M1-X7 & Multitherm. & AIA & AIA & Rad. \\
       \hline
    \end{tabular}}
    \caption{The details of the studies.}
    \label{tab1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% ################################################################# %%
\section{Motivation}\label{sec:mot}
%% ################################################################# %%

%% ################################################################# %%
\section{Outline of Thesis}\label{sec:outline}
%% ################################################################# %%

### 2023-12-28 main_thesis_file.tex
Initial Overleaf Import

%THIS IS THE MAIN FILE THAT TELLS LATEX WHICH FILES TO INCLUDE IN YOUR THESIS.

%THIS TEMPLATE PASSED DOWN FROM COURTNEY DRESSING
%EDITED SLIGHTLY AND UPLOADED TO OVERLEAF BY BEN COOK (bacook17@gmail.com)

% use "plain" for committee to read, or for printing single-spaced in general
\documentclass[plain]{hvdthesis}

% use "bound" for submitting to Harvard 
%\documentclass[bound]{hvdthesis}

% no more microfilm?
%\documentclass[microfilm]{hvdthesis}

% Put all required packages and setup in one file
\input{setup}

% Put all your useful macros, shortcuts, and commands in one file
\input{mycommands}

\author{Soumya Roy}
\title{Thesis Title Goes Here}
\department{}
\subject{}
\month{Month}
\year{Year}
\advisor{Professor Durgesh Tripathi}

\begin{document}

% include the dissertation acceptance form
\includepdf[pages={1}]{placeholder_dac.pdf}

\clearpage
\thispagestyle{empty}
\begin{center}
\vspace*{\fill}
Page left intentionally blank.
\vspace*{\fill}
\end{center}

\frontmatter

	%% Title page
\makecover
	%% Copyright
%\copyright
	%% Abstract
\input{abstract.tex}
%\input{abstract_short.tex}
	%% Table of Contents
{\singlespace
\tableofcontents
}
\newpage
\clearpage

	%% List of Figures
%\addcontentsline{toc}{chapter}{List of Figures}
%\listoffigures
%\newpage
	%% List of Tables
%\addcontentsline{toc}{chapter}{List of Tables}
%\listoftables

\newpage
	%% Acknowledgments
%\input{acknowledge.tex}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Acknowledgments}
\chaptermark{Acknowledgments}

\vskip 0.5cm
{\centerline {\Large \bf Acknowledgments}}
\vskip 0.5cm
\normalsize
\input{acknowledge.tex}

%\hfill -- RCH
%\newpage

\clearpage
%	%% Dedication
%\input{dedication.tex}
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Dedication}

\vspace*{\fill}
{\centerline {\em Your thoughtful dedication goes here.}}
%\vskip 1.5cm
%{\centerline {\em }}
\vspace*{\fill}

%\clearpage

\mainmatter
\pagestyle{fancy}

%% Uncomment the next four lines, plus the \begin{bibunit} and \end{bibunit} 
%% to use bibunits.  Read bibunits.dvi for more documentation
%\bibliographyunit[\chapter]
%\bibliographystyle*{apj}
%\bibliography*{apj-jour,planets}
%\bibliographyunit

\chapter[Introduction]{Introduction}\label{c:intro}
\input{./introduction/intro}
\clearpage
%
\chapter{Existing Solar Observatories}\label{c:chap2}
\chaptermark{Solar Observatories}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter2/ms.tex}
\clearpage
%
\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap3}
\chaptermark{Solar Flare Energetics}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter3/ms.tex}
\clearpage
%
\chapter{Estimating thermal and non-thermal energy partition of Solar Flares}\label{c:chap4}
\chaptermark{Short Chapter 4 Title}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter4/ms.tex}
\clearpage
%
\chapter{The Solar Ultraviolet Imaging Telescope onboard Aditya-L1}\label{c:chap5}
\chaptermark{SUIT}
\begin{quote}
{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
{authors,
{\em journal reference info}}
\end{quote}
\input{./chapter5/ms.tex}

% I changed  thebibliography in hvdthesis.cls, so that it generates
% a ToC entry, and is headed References instead of Bibliography. -HJC
\singlespace
\bibliographystyle{apj}
\bibliography{your_bib_file}

\end{document}

### 2024-02-13 chapter2/ms.tex
Updates from Overleaf

--- 2023-12-28 chapter5/ms.tex
@@
 %UNLIKE IN A REGULAR TEX FILE, DON'T PUT ANY PREAMBLE MATERIAL HERE
+
+%UNLIKE IN A REGULAR TEX FILE, DON'T PUT ANY PREAMBLE MATERIAL HERE
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The remarkable technological progress attained in the last few decades has yielded significant benefits in the form of highly advanced imaging, spectroscopic, and polarimetric instruments designed for astronomical observations.
+These instruments have empowered us with the ability to scrutinize the Sun with exceptional detail.
+Specifically, the space based observatories have added new avenues of observing sun.
+Large portions of the electromagnetic spectra is heavily by Earth's atmosphere \sr{Reference here}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Throughput model and imaging performance of SUIT}\label{sec:suit_imaging}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Filter Choice for SUIT}\label{sec:filter_choice}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Photometric, Radiometric \& Spectral Calibration of SUIT}\label{sec:suit_cal}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%NOTE THE LACK OF A BIBLIOGRAPHY CALL IN THIS FILE. BIBLIOGRAPHY WORK HAPPENS OUTSIDE THE CHAPTER TEX FILES.
 

### 2024-02-13 chapter3/ms.tex
Updates from Overleaf

--- 2023-12-28 chapter5/ms.tex
@@
-%UNLIKE IN A REGULAR TEX FILE, DON'T PUT ANY PREAMBLE MATERIAL HERE
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Aditya-L1}
+\section{Introduction}\label{secc3_intro}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Solar Ultraviolet Imaging Telescope}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{SUIT \& Solar Flares}\label{sec:suit_and_flare}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Solar flares are the most powerful magnetic events in the solar system.
-They are described as a sudden increase in brightness in localized areas on Sun.
-Within tens of minutes, they can release over $10^{32}$ erg of energy, which is emitted across the entire electromagnetic spectrum from radio to gamma rays.
-They can also launch high energetic particles into the interplanetary medium.
-Most of the flares occur in magnetic active regions, and the amount of flare energy released is comparable to the free energy stored in the magnetic system.
-The term "flare" is generally used explicitly for the entire magnetically-driven event's electromagnetic radiation, as it is the most significant fraction of the total energy liberated.
-The total energy released varies from event to event.
-It is also known that larger events occur much less frequently than smaller events.
-
-The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1} of the Indian Space Research Organization (ISRO).
-With its 11 science filters (3 broadband and eight narrowband), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another.
-SUIT will provide full disk as well as partial disk images of the Sun with a pixel size of 0.7".
-Through SUIT imaging, we would be able to resolve solar flares spatially on the surface of the Sun, for the first time in near ultra-violet (NUV), which will help us to address the questions regarding their build-up and triggering mechanism.
-In addition, to measure the spatially resolved solar spectral irradiance within the wavelength range that is central for studying the Chemistry of oxygen and ozone in the Stratosphere of Earth's atmosphere.
-
-It has been shown that the majority of flare energy emerges at the visible and UV wavelength range \citep{woods06}.
-\cite{woods04} showed that about 77\% of the energy is released in the wavelength range > 200 nm, and only ~ 23\% is seen in extreme ultraviolet (EUV) and soft X-ray (SXR), i.e., below 200 nm \citep{Nei_1989,neidig93,kretzschmar11}.
-Although the energy content in hard X-ray (HXR) is a tiny fraction of the total energy budget, they are still crucial in understanding the energization process \citep{holeman11}.
-However, to develop a comprehensive understanding of solar flares, it is mandatory to perform multi-wavelength studies of all kinds of flares.
-This may have implications on the physics of the origin of solar flares and different physics processes and contribute to the solar spectral irradiance as a function of the solar activity cycle.
-Although we have been observing Sun and Solar flares in various wavelengths, the spectral energy distribution of the radiated energy from the flares is still very poorly understood.
-The first solar flares were observed from the ground in the visible domain \citep{carrington1859,neidig93}.
-It is also well known that the flare emission in the visible domain occurs mainly in $H\alpha$ and Ca \Romannum{2} lines \citep{canfield90,falchi92,heinzel94}.
-However, the lesser understood component of the visible and Near Ultra Violet (NUV) emission is the enhancement of the continuum.
-The study of the white-light (WL) flares has proven to be very difficult because they have a very short duration and low contrast against the background, making their observation from Earth rare and of poor quality.
-Also, the flares in NUV are not observable from any ground-based instrumentation as most of the NUV gets absorbed in the upper atmosphere, thus requires space-based observations.
-
-The origin of the WLFs, i.e., the physical process responsible for generating the continuum and its contribution to the overall energy distribution, is still highly uncertain.
-The question remains whether WLFs are photospheric phenomena due to $H^{-}$ free-free emission or chromospheric phenomena due to H free-bound emission.
-The more recent studies further constrain the origin of the WLFs to be Chromospheric phenomena, as it has been shown that the WL and HXR footpoint centroids are cospatial.
-Similarly, \cite{krucker15} constrained the cospatial WL and HXR footpoints within the chromosphere for three flares.
-With the help of SUIT, we would be able to localize the WL flares and resolve them on various parts of the Solar disk, which along with observations from Interface Region Imaging Telescope (IRIS), Helioseismic and Magnetic Imager (HMI), would help us localize the source of the WL footpoints and also comment on the formation mechanism of the WL itself.
-
-\begin{figure}
-    \centering
-    \includegraphics[width = \linewidth]{Figures/Krucker_2015_ApJ_802_19_page-0004.jpg}
-    \caption{X-ray and optical imaging of the three flares at the peak time of the impulsive phase: the images are from HMI with the pre-flare image subtracted.
-The contours represent RHESSI Clean maps in the thermal (red, 12–15 keV) and non-thermal (blue, 30–80 keV) HXR range \citep{krucker15}.}
-    \label{fig1}
-\end{figure}
-
-The spectral energy distribution of flares is one of the critical areas of interest in the physics of flares.
-A complete understanding of this will help us decode the physical processes involved in solar flares and help quantify their effects on solar spectral irradiance.
-Ideally, it would be essential to observe flares at all wavelengths simultaneously with sufficient spatiotemporal resolution to figure out the spectral energy distribution of flares.
-Unfortunately, this is generally not the case, and we have to rely on the sporadic observations made using ground-based instruments in the visible domain.
-As mentioned earlier, the majority of the flare energy is emitted in the NUV and visible domain.
-\cite{kretzschmar10,kretzschmar11}, performed statistical studies using a large number of flare observations across a wide energy range.
-They demonstrated, at the peak of the flare, about 70\% of the total energy was radiated in the continuum visible and NUV channel as illustrated in \ref{tab1}.
-SUIT would observe and resolve the solar flares within 200-400 nm using 8 NBs and 3 BBs.
-This, along with IRIS data, would help us comment on the energy distribution of flares of various classes.
-
-%%--------------------------------------------%%
-\begin{table}[]
-    \centering
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{||m{.1\linewidth}|m{.15\linewidth}|m{.17\linewidth}|m{.17\linewidth}|m{.17\linewidth}|m{.15\linewidth}||}
-    \hline
-    \hline
-        Mean X-ray class & TSI(ergs) & Ratio $\frac{26-34nm}{TSI}$ & Ratio $\frac{0-50nm}{TSI}$ & Ratio $\frac{0.1-0.8nm}{TSI}$ & Ratio $\frac{continuum}{TSI}$\\
-        \hline
-        X3.2 & 5.9$\times~10^{31}$ & 0.9-0.8\% & 12-9\% & 1.2-1\% & 67\% \\
-        M9.1 & 1.6$\times~10^{31}$ & 1.7-0.4\% & 23-5\% & 1-0.4\% & 85\% \\
-        M4.2 & 1.3$\times~10^{31}$ & 2.2-0.5\% & 18-6\% & 0.6-0.3\% & 74\% \\
-        M2.0 & 5.1$\times~10^{30}$ & 1.7-0.6\% & 18-6\% & 0.7-0.4\% & 69\% \\
-        C8.7 & 3.6$\times~10^{30}$ & 1.5-0.5\% & 16-5\% & 0.4-0.2\% & 72\% \\
-        \hline
-    \end{tabular}}
-    \caption{Spectral Energy Distribution from a sample of 2100 flares across various wavelengths\citep{kretzschmar11}.}
-    \label{tab1}
-\end{table}
-%%--------------------------------------------%%
-
-Finally, one of the major question of interest is how the Solar flares affect the Spectral Solar Irradiance (SSI) and Total Solar Irradiance (TSI) variability from a short to much longer, Solar Cycle timescale.
-\cite{kretzschmar10,kretzschmar11} performed statistical studies using a large number of flare observations across a wide energy range.
-For this purpose, they used the full Sun observations of Solar flux from Solar and Heliospheric Observatory (SoHO), three visible Solar irradiances from VIRGO/Solar Photometer (SPM) passbands centred on 402 nm, 500 nm, and 862 nm, respectively, from 1996 to 2008.
-Additionally, they also use the EUV irradiance in the ranges 0.1-50 nm and 26-34 nm measured by SOHO/Solar EUV Monitor \citep{judge98} and SXR measurements from GOES satellites.
-They showed that stacked TSI variation profiles during solar flares show variation at more than 2 sigma level during the peak flare time, indicating the presence of flare signals in the TSI measurements.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width = \linewidth]{Figures/nphys1741_page-0002.jpg}
-    \caption{Averaged TSI variations during flares.
-The TSI time-series averages over four exclusive sets of solar flares of decreasing amplitude.
-The black and pink curves correspond respectively to the TSI measured by the PMOV6 and the DIARAD radiometers.
-The dashed lines correspond to the 95\% confidence levels, while the vertical line denotes the peak time of the flare \citep{kretzschmar10}.}
-    \label{fig2}
-\end{figure}
-
-This allows us to quantify the solar variability induced be solar flares of various timescales.
-With the help of SUIT, we would be able to localize the flare locations and study the change in SSI from the local environment in the 11 science filters.
-This information combined with TSI measurements can allow us to quantify the effect of flares of various energy scales on the TSI variability of the Sun.
-As, both the TSI and SSI variability directly or indirectly couples with various atmospheric parameters, we can also study the effect the flares have on them.
-For example, the Earth's atmospheric chemistry and composition respond to any changes in solar UV output in a very nonlinear fashion \citep{haigh07}.
-Since the number of flares also shows a change with solar activity, it is prudent to ask how much flares contribute to the solar spectral irradiance in NUV.
-This is particularly important because the irradiance in NUV plays a key role in heating the upper and middle layers of the Earth's atmosphere directly and their coupling with Stratosphere.
-It also directly influences the middle and lower atmosphere chemistry and composition via the Ozone-Oxygen cycle.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Throughput model and imaging performance of SUIT}\label{sec:suit_imaging}
+\section{Throughput model of SUIT}\label{sec:suit_throughput}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%NOTE THE LACK OF A BIBLIOGRAPHY CALL IN THIS FILE. BIBLIOGRAPHY WORK HAPPENS OUTSIDE THE CHAPTER TEX FILES.

### 2024-02-13 introduction/intro.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The solar interiror}\label{solar_int}
+\section{The solar interior}\label{solar_int}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \caption{A schematic depiction of the different layers of the Sun.
-The figure also shows soe of the most prominent magnetic structures on the Sun e.g sunspot, prominence, coronal hole.
+The figure also shows some of the most prominent magnetic structures on the Sun e.g sunspot, prominence, coronal hole.
 Credit : NASA/Goddard.
@@
 here}.
-The high energy $\gamma$-ray photons generated in the core, have very small mean free path in this region, as they collide neumerous times eventually thermalizing becoming visible photon.
-Beyond the radiative zone the degree of ionization of Hydrogen and Helium changes drastically giving rise to a sharp temperature gardient.
+The high energy $\gamma$-ray photons generated in the core, have very small mean free path in this region, as they collide numerous times eventually thermalizing becoming visible photon.
+Beyond the radiative zone the degree of ionization of Hydrogen and Helium changes drastically giving rise to a sharp temperature gradient.
 This is the convective zone where the energy from the inner layers of the Sun is transported adiabetically to the surface of the Sun.
-Inbetween the radiative and the convective zone, there is a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine, which is believed to play a major role in generating Sun's magnetic field via the Dynamo process \sr{Ref.
+In between the radiative and the convective zone, there is a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine, which is believed to play a major role in generating Sun's magnetic field via the Dynamo process \sr{Ref.
 here}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The solar atmosphere}\label{solar_atmos}
+\section{The solar atmosphere}\label{solar_atmos}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The layers outside the convection zone together, form the solar atmpshere - the Photosphere, which is also known as the Sun's surface, the Chromosphere, the transition region and the Corona.
+The layers outside the convection zone together, form the solar atmosphere - the Photosphere, which is also known as the Sun's surface, the Chromosphere, the transition region and the Corona.
 While we can define geometrical height or depths to define these layers, it is much more useful to define them using the local optical depths of various spectral lines, which are directly used to observe the layers.
 This also gives us a idea about which spectral features originate mainly from which portions of the solar atmosphere.
-Fig.~\ref{fig_solar_atm} shows the variation of temperature and number density accross various layers of the Solar atmosphere \sr{Ref.
+Fig.~\ref{fig_solar_atm} shows the variation of temperature and number density across various layers of the Solar atmosphere \sr{Ref.
 here}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{The Photosphere}\label{photosphere}
+\subsection{The Photosphere}\label{photosphere}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This region exhibits an average magnetic flux density of \textbf{10 -- 50~G}.
-The QS surface is covered with cells of roughly four size- granule, mesogranules, supergranules and giant cells.
-Some regions exhibit much sronger magnetic flux density often asociated with highly twisted magnetic field structures.
-These magnetic features are manifested as sunspots, spcules, bright points etc.
+The QS surface is covered with cells of roughly four size- granule, meso granules, super granules and giant cells.
+Some regions exhibit much stronger magnetic flux density often associated with highly twisted magnetic field structures.
+These magnetic features are manifested as sunspots, spicules, bright points etc.
 
-As the density changes drastically at the Photosphere compared to the convective zone, the thermalized photons from Sun's core start freestreaming again, as the mean free path also increases drastically and as a result perturbs the thermal equlibrium (TE from hereon).
-So, we have to define the thermodynamic quantites of the Photosphere in Local Thermal Equlibrium (LTE from hereon).
-As we move away from the Photosphere, because the density keeps on decreasing steadily, the LTE conditiobs also start deviating similarly \sr{Ref here}.
+As the density changes drastically at the Photosphere compared to the convective zone, the thermalized photons from Sun's core start free streaming again, as the mean free path also increases drastically and as a result perturbs the thermal equilibrium (TE from hereon).
+So, we have to define the thermodynamic quantities of the Photosphere in Local Thermal Equilibrium (LTE from hereon).
+As we move away from the Photosphere, because the density keeps on decreasing steadily, the LTE conditions also start deviating similarly \sr{Ref here}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{The Chromosphere}\label{chromosphere}
+\subsection{The Chromosphere}\label{chromosphere}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The Chromosphere is a highly non-uniform dynamic layer with a thickness of 1500~--~3000~km, with increasing temperature (upto $10^{4}$ K) and decreasing numbr density.
+The Chromosphere is a highly non-uniform dynamic layer with a thickness of 1500~--~3000~km, with increasing temperature (upto $10^{4}$ K) and decreasing number density.
 As seen in the fig.
 \ref{fig_solar_atm}, the temperature of the Chromosphere saturates before the dramatic rise in the transition region.
-This saturation is attributed to a steady deposition of accoustic energy by creation of shock waves \sr{Ref.
+This saturation is attributed to a steady deposition of acoustic energy by creation of shock waves \sr{Ref.
 here}.
@@
 
+%%%%%%%%%%%%%%%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={1cm 3cm 2cm 5cm},clip,width=0.8\textwidth]{Figures/sji_images.pdf}
+    \caption{IRIS SJI Slit-jaw images of NOAA AR 13521 on Dec 21st, 2023 in \ion{Mg}{2} 2796~\AA~(left panel) showing the upper Chromosphere.
+The right panel shows the same active region in 2832~\AA~continuum corresponding to upper photosphere.}
+    \label{fig:sji_features}
+\end{figure}
+%%%%%%%%%%%%%%%%
+
+In fig.~\ref{fig:sji_features} we show the NOAA AR 13521 in IRIS SJI 2796~\AA (left panel) and 2832~\AA (right panel).
+The dark sunspots and plage regions surrounding it are clearly visible in the 2832~\AA wavelength window.
+In the 2796~\AA window we see the plage along with light bridges more clearly.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{The Transition Region}\label{transition-region}
+\subsection{The Transition Region}\label{transition-region}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{The Corona}\label{corona}
+\subsection{The Corona}\label{corona}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The outermost layer of the Solar atmosphere is the Corona. The Corona is only visible in naked eyes during the total solar eclipse or via Coronagraphs.
+The outermost layer of the Solar atmosphere is the Corona.
+The Corona is only visible in naked eyes during the total solar eclipse or via Coronagraphs.
+It maintains a steady temperature of 1-2 Mk during ambient conditions, but can rise upto tens of MK during solar flares.
+The coronal continuum spectrum is produced due to Thompson scattering of photons from photosphere off coronal electrons.
+Corona also emits in various emission lines, e.g.
+Mg, Fe, Si, S, Ca, O etc.
+across a wide band of elctro magnetic spectrum ranging from X-ray to visible wavelengths.
+
+Similar to the other layers, the corona exhibits a variety of structures such as ARs, coronal holes, bright points, filaments, flares.
+The flare arcades are most prominently visible in the Corona.
+So, most of our existing studies over the last decade has focused on the coronal features of the flares.
+In fig.~\ref{fig:sji_features} we show one of the most well known and well studied solar eruptions from Aug 31st, 2012.
+A giant prominence erupted from the south east limb.
+The erupted prominence material was visible in all AIA channels from 304 \AA~(Chromospheric He II, see fig.~\ref{fig:aia-feature} \textbf{panel (a)}) across all six Coronal channels (\textbf{panel (b){--}(g)}).
+The sun spots were also clearly visible in HMI magnetogram and continuum (see fig.~\ref{fig:aia-feature} \textbf{panel (h)}).
+In \textbf{panel (i)} we show the co-aligned AIA 304 \AA, 131 \AA and HMI magnetogram image.
+The sunspots lie at the base of the erupted prominence, accompanied by the hot thermal plasma associated with the accompanying flare.
+The novelty of such observation lies in the clear spatial connection across various layers of the sun, connected via energy and momentum transported from one layer to the other.
+
+%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/aia_features.pdf}
+    \caption{Image of the prominence eruption and associated flare from NOAA AR 11562 on Aug 31st, 2012$\sim$19:50 UT.
+The prominence is visible in all of the AIA channels.
+We see the coronal holes in AIA 335 \AA~\textbf{(panel c)}.
+The flare loops of the associated event is visible in AIA 94 \AA~\textbf{(panel e)} and AIA 131 \AA~\textbf{(panel f)}.
+The sunspots are visible in HMI continuum \textbf{panel (h)}.
+We show a co aligned map of AIA 304 \AA, HMI magnetogram and AIA 131 \AA~in \textbf{panel (i)}.
+The spatial association of the sunspots with the hot flareloop plasma and the prominence eruption is clearly demostrated here.
+}
+    \label{fig:aia-feature}
+\end{figure}
+%%%%%%%%%%%%%
 

### 2024-02-13 main_thesis_file.tex
Updates from Overleaf

@@
 %
-\chapter{Existing Solar Observatories}\label{c:chap2}
+\chapter{Existing Solar Observations and techniques}\label{c:chap2}
 \chaptermark{Solar Observatories}
-\begin{quote}
-{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
-{authors,
-{\em journal reference info}}
-\end{quote}
 \input{./chapter2/ms.tex}
@@
 %
-\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap3}
-\chaptermark{Solar Flare Energetics}
+\chapter{Intital preparatory analysis for SUIT}\label{c:chap3}
+\chaptermark{SUIT preparatory analysis}
 \begin{quote}
@@
 %
-\chapter{Estimating thermal and non-thermal energy partition of Solar Flares}\label{c:chap4}
-\chaptermark{Short Chapter 4 Title}
+\chapter{Forward modelling SUIT observations}\label{c:chap4}
+\chaptermark{SUIT forward model}
 \begin{quote}
@@
 \input{./chapter4/ms.tex}
-\clearpage
 %
-\chapter{The Solar Ultraviolet Imaging Telescope onboard Aditya-L1}\label{c:chap5}
-\chaptermark{SUIT}
+\chapter{Stellar calibration of SUIT}\label{c:chap5}
+\chaptermark{SUIT stellar calibration}
 \begin{quote}
@@
 \input{./chapter5/ms.tex}
+%
+\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap6}
+\chaptermark{Solar Flare Energetics}
+\begin{quote}
+{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
+{authors,
+{\em journal reference info}}
+\end{quote}
+\input{./chapter6/ms.tex}
+\clearpage
+%
+\chapter{Estimating thermal and non-thermal energy partition of Solar Flares}\label{c:chap7}
+\chaptermark{Solar flare energy}
+\begin{quote}
+{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
+{authors,
+{\em journal reference info}}
+\end{quote}
+\input{./chapter7/ms.tex}
+\clearpage
+%
+\chapter{First X-class flare observed from SUIT}\label{c:chap8}
+\chaptermark{Solar flare energy}
+\begin{quote}
+{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
+{authors,
+{\em journal reference info}}
+\end{quote}
+\input{./chapter7/ms.tex}
+\clearpage
+%
 

### 2024-02-14 chapter6/ms.tex
local change

%\begin{abstract}

 %   The \ion{Mg}{2}~k \& h line intensity ratios can be used to probe the characteristics of the plasma in the solar atmosphere. In this study, using the observations recorded by the Interface Region Imaging Spectrometer (IRIS), we study the variation of the \ion{Mg}{2}~k \& h intensity ratio for three flares belonging to X-class, M-class, and C-class, throughout their evolution. We also study the k-to-h intensity ratio as a function of magnetic flux density obtained from the line-of-sight magnetograms recorded by the Helioseismic and Magnetic Imager (HMI) on board the Solar Dynamics Observatory (SDO). Our results reveal that while the intensity ratios are independent of magnetic flux density, they show significant changes during the evolution of the C-class and M-class flares. The intensity ratios start to increase at the start of the flare and peak during the impulsive phase before the flare peak and decrease rapidly thereafter. The values of the ratios fall even below the pre-flare level during the peak and decline phases of the flare. These results are important in the light of heating and cooling of localized plasma and provide further constraint on the understanding of flare physics.

%\end{abstract}

%%----------------------------------------------------
\section{Introduction} \label{sec:intro}
%%----------------------------------------------------

Solar flares are the most energetic events on the Sun, where an enormous amount of magnetic free energy is released due to the reconfiguration of the coronal magnetic field. The released energy can cause particle acceleration, heating and flows in the solar atmosphere and a transient enhancement in solar radiative output. It is observed that most of the energy radiated in flares originates from the dense chromosphere \citep{fletcher10,milligan14}. Hence, studying the chromospheric lines during flares provides us with diagnostics, which may be important for understanding the physics of solar flares and their effect on the local plasma environment.

The chromosphere emits in various UltraViolet(UV) and optical lines. While many optical lines, e.g., H$\alpha$, \ion{Ca}{2}, are routinely observed from ground-based telescopes, observations in the \ion{Mg}{2} resonance lines have been rare in the past. Since the launch of the Interface Region Imaging Spectrograph \citep[IRIS;][]{IRIS} we have been in the position to monitor these lines regularly with excellent spatial and spectral resolution.

The \ion{Mg}{2}~k and h lines are transitions to the ground state from a finely split pair of upper levels ($3p~^{2}P_{\nicefrac{3}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$ and $3p ^{2}P_{\nicefrac{1}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$). These transitions create the optically thick lines in the wavelengths 2796.34~{\AA} (\ion{Mg}{2}~k) and 2803.52~{\AA} (\ion{Mg}{2}~h). It is suggested that the intensity ratios of these lines can be used to probe the optical depth of the local environment \citep{kerr15}.

The integrated intensity of a line transitioning from an upper-level j to a lower-level i, is dependent on the collision strength for that transition $\Omega_{ij}$, which is given by~\citep{henri62,mariska92},

%%---------------------------------------------------------------
\begin{equation*}
    \Omega_{ij}~=~\frac{8\pi}{\sqrt{3}}~\frac{I_{H}}{\Delta \epsilon_{ij}}~g~\omega_{i}~f_{ij}
\end{equation*}
%%---------------------------------------------------------------

\noindent Where $I_{H}$ is the ionization energy of Hydrogen, $\Delta \epsilon_{ij}$ is the threshold energy for the transition, g is the Gaunt factor, $\omega_{i}$ is the statistical weight of the level and $f_{ij}$ is the oscillator strength. In optically thin conditions, the intensity ratio of the k to h line is the ratio of the collision strengths, as the escape probability of photon is unity. The \ion{Mg}{2} k and h lines share the same ionization state and originate from a transition to a shared lowered level. As the statistical weight ($\omega_{i}$) is same in both cases, the line intensity ratio is simply the ratio of the oscillator strengths($f_{ij}$). This implies the ratio is 2:1 in optically thin conditions, and lower when the medium is optically thick \citep{kerr15,levens19}.

In addition, the \ion{Mg}{2} k and h lines can be used to estimate the velocity in the middle and upper chromosphere, the chromospheric velocity gradients, the temperature in the middle chromosphere \citep{leenarts13a,leenarts13b,pereira13}. The \ion{Mg}{2} triplets in emission can be used to identify heating in the lower chromosphere \citep{pereira15}. There have also been multiple studies that have shown a spatial variation of the \ion{Mg}{2} line profiles \citep{dalda23,panos18}. \cite{polito23} showed that the leading edge of the flare ribbon is associated with enhanced broadening and strong central reversal. They interpreted the difference in the profile as a difference in the heating mechanism at the leading edge and bright part of the flare ribbons. \cite{panos21,panos21_2} showed similar differences between the line profiles and energy input.

Using the observations recorded by the OSO-8 LPSP instrument, \citep{lemaire84} studied the evolution of the intensity ratio of \ion{Mg}{2}~h~\&~k, \ion{Ca}{2}~h~\&~k and Ly~$\alpha$~\&~$\beta$ lines. \cite{lemaire84} showed that the intensity ratio of the \ion{Ca}{2}~k/h lines increased from 1 to 1.2 during the ascending phase of a flare and returned to 1 during the later phases. The authors interpreted the correlated temporal behavior across various elements as an indication of downward energy propagation. We note that this may suggest a slight decrease in the opacity due to localized heating at the formation height of the \ion{Ca}{2} line during the rise phase of the flare.

%\sout{In spite of the excellent potential of these spectral lines in diagnosing the localized atmosphere, such} \sout{studies have not been taken up in detail due to the scarcity of spectral observations in these lines.}

Here, we study the evolution of the intensities ratios of the \ion{Mg}{2}~h~\&~k lines during the course of the evolution of three flares, \textit{viz.}, C-class, M-Class and X-class. We focus on the the dependence of line ratios on the underlying magnetic field strength, which to our knowledge has not been explored so far. The rest of the paper is structured as follows. \S\ref{sec:obs} discusses the observations used in this paper. We discuss how we reduce and analyze the data and the results in \S\ref{sec:dar}.

### 2024-05-06 chapter2/ms.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+%\section*{Introduction}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The remarkable technological progress attained in the last few decades has yielded significant benefits in the form of highly advanced imaging, spectroscopic, and polarimetric instruments designed for astronomical observations.
@@
 
+The studies within this thesis are using solar observations are multi wavelength analysis of solar flares with both imaging and spectroscopy.
+In this chapter we describe the details of the instruments and techniques used for our analysis.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Aditya-L1}
+\section{Solar Dynamic Observatory}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The Solar Dynamics Observatory \citep[SDO;][]{sdo} is a NASA mission designed to understand the causes of solar variability at various spatiotemporal and wavelength scales, as well as its impacts on Earth and the near-Earth environment.
+It is part of NASA’s Living With a Star program and houses multiple instruments onboard to address its numerous scientific goals.
+Among the numerous instruments on-board {\it SDO}, we have extensively used data from two instruments – the Atmospheric Imaging Assembly (AIA) and the Helioseismic and Magnetic Imager (HMI).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Atmospheric Imaging Assembly (AIA)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+AIA \citep{aia} obtains full-disk images of the solar transition region and corona at unprecedented spatio-temporal resolution.
+The field of view (FOV) covers up to 0.5 $\mathrm{R_{\odot}}$ above the limb.
+It incorporates several filters at 94 {\AA}, 131 {\AA}, 171 {\AA}, 193 {\AA}, 211 {\AA} and 335 {\AA}, mainly probing the Corona, along with filters at 304 {\AA}, 1600 {\AA}, 1700 {\AA}, and 4500 {\AA}, mainly observing the Chromosphere and Photosphere, providing a total temperature coverage range of 0.06 MK to 20 MK and across various heights.
+Figure 2.1 illustrates the temperature responses of these filters (Boerner et al., 2012), derived based on the CHIANTI model for solar emissivity (Dere et al., 1997, 2009).
+Under different conditions, these AIA filters observe different plasma phenomena \citep{o'dwyer10}.
+Typical exposure times range between 0.5 and 3 seconds.
+Each AIA telescope is accompanied by its own guide telescope to ensure highly accurate image stabilization.
+For ous analysis, we have extensively used the coronal EUV channel observations from AIA, e.g.
+94 {\AA}, 131 {\AA}, 171 {\AA}, 193 {\AA}, 211 {\AA} and 335 {\AA}.
+These coronal channels observations are usually available with a 12 s cadence.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Helioseismic and Magnetic Imager (HMI)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+HMI \citep{hmi} obtains images of the Sun across the \ion{Fe}{1} 6173 {\AA} line at six wavelength locations and infers all four components of the Stokes' parameter.
+Using these observations, various parameters are inferred e.g., Line of Sight (LOS) magnetic field, Doppler velocities, vector magnetic fields etc.
+We have mainly used the LOS magnetogram for our analysis.
+These magnetograms have a 0.5{\arcsec} per pixel resolution and 45 s cadence.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Interface Region Imaging Spectrograph (IRIS)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The Interface Region Imaging Spectrograph \citep[IRIS;][]{iris} is a NASA small satellite explorer mission designed to observe the dynamics of the lower solar atmosphere.
+IRIS contains a spectrograph and a slit-jaw imager (SJI), observing the chromosphere, the transition region, and the lower corona.
+It primarily observes the Sun in two passbands around 1400 {\AA} and 2800 {\AA}.
+IRIS provides data at high spatial resolution (0.33 {\arcsec} in FUV and 0.4 {\arcsec} in NUV), high time cadence (up to 1 second), and high spectral resolution (12 or 25 m{\AA} per pixel).
+
+IRIS observes three wavelength bands: two in the Far Ultraviolet (FUV) range, spanning 1331.7–1358.4 {\AA} and 1389.0–1407.0 {\AA}, and one in the Near Ultraviolet (NUV) range, covering 2782.7–2851.1 {\AA}.
+IRIS measures spectra through two primary modes: raster and sit-and-stare.
+In raster mode, the slit traverses a field of view, capturing spectra from each pixel along its path.
+When the displacement between consecutive slit positions is comparable to the slit width, it is called dense raster mode; otherwise, it is called sparse raster mode.
+Alternatively, the instrument may position the slit on a specific region for observation of the Sun.
+This mode can allow the Sun to naturally rotate across the region or adjust for solar rotation while maintaining continuous observation.
+This mode is referred to as sit-and-stare.
+In our analysis, we have used both spectra and SJI imaging from the \ion{Mg}{2} h \& k window and SJI imaging from the \ion{Si}{4} 1402 {\AA} window.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Spectrometer/Telescope for Imaging X-rays (STIX)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Solar Orbiter \citep[SO;][]{so} is a joint mission between the European Space Agency (ESA) and NASA, launched in February 2020 with the goal of studying the Sun and its dynamic behaviour.
+The spacecraft aims to provide unprecedented observations of the Sun's polar regions and the inner heliosphere, offering new insights into solar phenomena such as solar wind, coronal mass ejections, and the Sun's magnetic field.
+We have used observations from the Spectrometer/Telescope for Imaging X-rays (STIX) instrument for our analysis.
+
+ STIX \citep{stix,stix1} is designed to study the Sun's X-ray emissions, providing crucial insights into the processes driving solar flares and other high-energy phenomena.
+STIX incorporates a set of collimators and detectors to capture high-resolution images of the Sun in X-rays.
+These images allow scientists to pinpoint the locations and intensities of X-ray emissions associated with solar flares.
+The instrument covers a broad range of X-ray energies, from approximately 4 to 150 keV, enabling it to observe various aspects of solar activity.
+STIX can capture X-ray data with high temporal resolution, allowing scientists to study the rapid evolution of solar flares and other transient events in detail.
+STIX works synergistically with other instruments onboard Solar Orbiter, providing complementary measurements to enhance our understanding of the Sun's dynamic behaviour across different wavelengths and energy ranges.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Extreme Ultraviolet Imager (EUVI)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Solar Terrestrial Relations Observatory-Ahead \citep[{\it STEREO-A};][]{stereo}, is one of two spacecraft in NASA's STEREO mission, which was launched in October 2006 with the goal of studying the Sun and its dynamic behaviour.
+{\it STEREO-A} and its twin spacecraft {\it STEREO-B} (Behind) were designed to provide stereoscopic views of the Sun, enabling three-dimensional observations of solar phenomena such as coronal mass ejections (CMEs) and solar flares.
+Extreme Ultraviolet Imager \citep[{\it EUVI};][]{euvi} is one of the key instruments onboard the {\it STEREO-A} spacecraft.
+{\it EUVI} is designed to capture images of the Sun in the extreme ultraviolet (EUV) wavelength range.
+This range of wavelengths is particularly useful for studying the Sun's outer atmosphere, known as the corona, and observing features such as solar flares, coronal loops, and coronal holes.
+
+{\it EUVI} can capture high-resolution images of the Sun's corona, with spatial resolutions in order of a few arcseconds.
+It can observe the Sun in 171 {\AA}, 195 {\AA}, 284 {\AA} and 304 {\AA} simultaneously.
+{\it EUVI} provides continuous observations of the Sun from the STEREO-A spacecraft's vantage point, located slightly ahead of Earth in its orbit around the Sun.
+This allows {\it EUVI} to monitor solar activity over extended periods and to track the evolution of solar features such as sunspots, flares, and coronal mass ejections (CMEs).
+We have used 171 {\AA} and 195 {\AA} observations from EUVI for our analysis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{X-Ray Telescope (XRT)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+{\it Hinode} \citep{hinode}, meaning "Sunrise" in Japanese, is a space mission launched by the Japan Aerospace Exploration Agency (JAXA) in collaboration with NASA and the UK Space Agency in September 2006.
+Also known as Solar-B before its launch, {\it Hinode} is dedicated to studying the Sun's magnetic field and its dynamic behaviour, focusing on understanding the mechanisms driving solar activity and space weather phenomena.
+The X-Ray Telescope\citep[XRT;][]{xrt} is one of the key instruments aboard the {\it Hinode} spacecraft.
+
+{XRT captures high-resolution solar corona images in X-ray wavelengths, allowing us to study phenomena such as solar flares, coronal loops, etc.
+Its imaging capabilities enable us to investigate the solar corona's structure, dynamics, and heating mechanisms.
+XRT utilizes narrow-band filters to isolate specific X-ray emission lines emitted by highly ionized elements in the solar corona.
+XRT provides continuous observations of the solar corona from the vantage point of the {\it Hinode} spacecraft, which orbits the Earth in a Sun-synchronous polar orbit.
+This allows XRT to monitor solar activity over extended periods.
+In our analysis, we used XRT imaging observation from various filters.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Geostationary Operational Environmental Satellites (GOES)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Geostationary Operational Environmental Satellites (GOES) are a series of weather satellites operated by the National Oceanic and Atmospheric Administration (NOAA) in the United States.
+These satellites continuously monitor weather conditions across the Americas, including the United States, Canada, Mexico, and parts of South America.
+GOES data are used by meteorologists and weather forecasters to monitor and predict weather conditions, track severe weather events, and issue warnings and advisories to the public.
+The continuous monitoring provided by GOES satellites helps improve the accuracy and timeliness of weather forecasts.
+In addition to monitoring terrestrial weather, GOES satellites also monitor space weather conditions, including solar flares, coronal mass ejections (CMEs), and geomagnetic storms.
+This information is crucial for forecasting space weather events and assessing their potential impact on satellite communications, navigation systems, and power grids.
+Among the numerous instruments on-board {\GOES}, we have used data from two instruments extensively {--} X-Ray Sensor (XRS) and Solar Ultra Violet Imager (SUVI).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{X-Ray Sensor (XRS)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The X-Ray Sensor \citep[XRS;][]{xrs} is an instrument onboard {\it GOES}.
+The primary function of the XRS is to continuously monitor and measure full disk integrated solar soft X-ray emissions, particularly those associated with solar flares.
+XRS is designed to detect and measure solar X-ray emissions in two energy bands: short wavelength (0.5 to 4 {\AA}) and long wavelength (1 to 8 {\AA}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Solar Ultraviolet Imager (SUVI)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Solar Ultraviolet Imager \citep[SUVI;][]{suvi} is an instrument aboard {\it GOES}, designed to observe the Sun in the EUV spectrum, providing crucial data for monitoring solar activity and space weather.
+SUVI captures images of the Sun in 94 {\AA}, 131 {\AA}, 171 {\AA}, 195 {\AA}, 284 {\AA} and 304 {\AA}.
+These wavelengths are very similar to AIA and provide complementary observations.
+The FoV of SUVI is rotated by $\sim~45^{o}$, and hence, provides a larger radial distance coverage along the diagonals.
+In our analysis, we have used SUVI observations from 94 {\AA}, 131 {\AA}, 171 {\AA}, and 195 {\AA}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Various Plasma Diagnostic Methods}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We employ various techniques throughout this thesis to infer electron density, ion and electron temperature, velocity, thermal structure of the plasma observed in both Chromosphere and Corona.
+It is standard practice to use atomic databases like CHIANTI \citep{chianti,chianti1} to derive the plasma properties.
+Below we describe the working principle of the methods used within the scope of this thesis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Differential Emission Measure and Thermal Properties of the Plasma}\label{sec:c2_dem}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Differential emission measure analysis is a commonly employed method with instruments that observe multiple spectral bands to determine the temperature and emission measure of optically thin coronal plasma exhibiting multiple thermal components along a line of sight.
+However, the inversion process is often challenging due to its ill-posed nature and the frequent lack of sufficient constraints, making it an under determined problem.
+One of the very first DEM calculation algorithm was {\it xrt\_dem\_iterative}, which was designed and validated for use with XRT data \citep{golub04,weber04}.
+
+The intensity observed by any optically thin imager can be related to the temperature distribution in solar Corona with 
+%%%%%%%%%%%%
+\begin{equation}
+    \mathrm{g_{i}~=~\int_{T}R_{i}(T)~\zeta(T)~dT+\delta g_{i}}
+    \label{eqn:dem}
+\end{equation}
+%%%%%%%%%%%%
+
+In Eqn.~\ref{eqn:dem}, $\mathrm{g_{i}}$ is the counts observed in some specific filter (usually in units of $\mathrm{DN.s^{-1}.pix^{-1}}$), $\mathrm{\delta g_{i}}$ is the observed error, $\mathrm{R_{i}}$ is the temperature response function of the specific filter and DEM(T) describes the thermal distribution of the local plasma  (usually in units of $\mathrm{cm^{-5}.K^{-1}}$).
+For multiple filter observations, this problem can be posed as a matrix equation in the form of $\Vec{g}~=~\mathbb{R}~\Vec{\zeta}\implies \Vec{\zeta}~=~\mathbb{R}^{-1}\Vec{g}$.
+However, because of the ill-posed and under-determined nature of the inverse problem, any attempt to invert this set of equations and recovering the DEM results in a significant increase in the noise.
+
+There are several well-characterised methods for inverting the DEM.
+In this thesis, we have used the method based on regularized inversion developed by \cite{hannah&kontar12}, to infer the thermal distribution of the coronal plasma.Given the under-defined nature of the inverse problem, the problem reduces to a least-square minimizing problem
+
+%%%%%%%%%%%%
+\begin{equation}
+    \mathrm{||\Tilde{\mathbb{R}}\zeta(T)-\Tilde{g}||^{2}+\lambda||{\bf L}(\zeta(T)-\zeta_{0}(T))||^{2}~=~min}
+    \label{eqn:dem}
+\end{equation}
+%%%%%%%%%%%%
+
+where $\Tilde{\mathbb{R}}~=(\delta g)^{-1}\mathbb{R}$ and $\Tilde{g}~=(\delta g)^{-1} g$.
+The minimization is performed using the Lagrange multiplier method.
+{\bf L} is the constrain matrix, $\lambda$ is the regularization parameter and $\zeta_{0}(T)$ is the initial guess solution for the DEM.
+For further details please refer to \cite{hannah&kontar12}.
+
+With the inverted DEM we get information regarding the distribution of the plasma at a range of temperatures.
+We can calculate the Emission Measure (EM) given by, $EM=\int_{T}DEM(T)~dT$ (in units of $\mathrm{cm^{-5}}$).
+The EM is connected to the local plasma density by $EM=\int n_{e}^{2}~dl$.
+We can also infer the average temperature of the local plasma with the DEM by, $\bar{T}=\frac{1}{EM}\int_{T}DEM(T)~T~dT$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Plasma Velocity from Spectra}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The bulk motion of the plasma along our line of sight can be easily inferred by measuring the red/blue shift of various lines compared to their rest wavelengths.
+This shift in wavelength is related to the LOS velocity by, $\frac{V_{LOS}}{c}~=~\frac{\Delta \lambda}{\lambda}$.
+
+In addition to the plasma's bulk velocity, several parameters can be inferred from the spectra.
+The spectral lines are formed due to the transition of electrons between two atomic/ionic energy levels.
+Instead of a sharp Dirac-delta function, we get the spectra broadened over a wavelength range due to several factors, {\it e.g.}, thermal broadening, Doppler broadening, pressure, optical depth, etc.
+The FWHM of the spectral line is given by, $\mathrm{FWHM~\sim~\frac{\lambda_{0}}{c}\sqrt{\frac{2k_{B}T}{m}+v_{nth}^{2}+r^{2}}}$.
+Here, $\lambda_{0}$ is the central wavelength, T is the temperature of the plasma, m is the mass of the ion, $\mathrm{v_{nth}}$ is the non-thermal velocity and r is the given instrumental width.
+
+The non-thermal broadening of spectral lines is caused by various factors {\, e.g.}, turbulence, wave motion, nano flares, small-scale local flows, magnetic reconnection, etc.
+All of these broadening appear on top of the Doppler broadening.
+Accurate estimation of the non-thermal broadening depends significantly on the accurate estimation of the instrumental broadening.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Numerous modern and historical imaging, spectroscopic, and polarimetric instruments have significantly contributed to our comprehension of the Sun and its atmosphere.
+Several of these instruments, previously discussed, have been utilized in this thesis.
+While certain instruments are ground-based telescopes, others operate from space.
+Space-based instruments primarily observe the Sun in Ultraviolet (UV), extreme ultraviolet (EUV), and X-ray bands, capturing radiation emitted from upper atmospheric layers like the transition region and corona, which possess elevated temperatures.
+Over recent decades, various studies of the Sun have effectively unveiled the physical characteristics of the gas in its upper atmospheric layers using observations recorded by X-ray imaging (e.g., {\it Hinode} X-ray Telescope \citep[{\it Hindoe}/XRT,][]{xrt}) and spectroscopy (e.g., the Spectrometer/Telescope for Imaging X-rays on {\it Solar Orbiter} \citep[{\it SO}/STIX,][]{stix}) as well as extreme ultraviolet (EUV) imaging (e.g., Atmospheric Imaging Assembly on the {\it Solar Dynamic Observatory} \cite[{\it SDO}/AIA,][]{aia}; Extreme ultraviolet Imaging Telescope on {\it Solar and Heliospheric Observatory} \cite[{\it SoHO}/EIT,][]{eit}; Solar Ultraviolet Imager on the {\it Geostationary Operational Environmental Satellites} \citep[{\it GOES}/SUVI,][]{suvi}; the Extreme Ultraviolet Imager on {\it Solar Terrestrial Relations Observatory-A} \cite[{\it STEREO-A}/EUVI,][]{stereo,euvi}; the Extreme-Ultraviolet Imager on {\it SO} \citep[{\it SO}/EUI][]{eui}) and spectroscopy (e.g., \citep[Hinode/EIS,][]{eis}), among others.
+Instruments such as the {\it Transition Region and Coronal Explorer} \citep[{\it TRACE},][]{trace}, the Solar Ultraviolet Measurements of Emitted Radiation on {\it SoHO} \citep[{\it SoHO}/SUMER,][]{sumer}, and {\it Interface Region Imaging Spectrograph} \citep[{\it IRIS},][]{iris} have facilitated detailed examinations of the chromosphere and the transition region.
+These missions offer continuous full-disk and Region of Interest (RoI) coverage of the Sun across X-ray and EUV wavelengths.
+However, the scenario is notably different in the Near-Ultraviolet (NUV) regime, where there is evidently a lack of continuous full solar disk coverage within this wavelength range.
+
+A significant challenge in conducting solar observations in the UV range from the ground is the substantial attenuation caused by the Earth's atmosphere.
+To overcome this obstacle, one of the pioneering approaches involved the deployment of stratospheric balloon-borne instruments in 1970 and 1971, as documented by \cite{herse79}.
+This instrument featured a 20 cm telescope capable of imaging the Sun within the 200-460 nm range.
+Subsequently, the Rasolba balloon experiment utilized a 30 cm telescope equipped with an ultraviolet spectrograph, yielding high-resolution spectra of the Sun spanning 190 to 295 nm \citep{samain85,staath95}.
+Building upon these endeavors, the Sunrise project \citep{sunrise1,sunrise2} emerged as a balloon-borne observatory designed to observe the Sun in the Near Ultraviolet (NUV) range using a 1 m diameter telescope.
+Sunrise conducted two flights, in June 2009 and June 2013, respectively, and provided high-resolution imaging at wavelengths of 214, 300, 312, 388, and 397 nm with the Sunrise Filter Imager \citep[SuFI,][]{sufi} in 2009, and at 214, 279, and 397 nm in 2017 \citep{sunrise2}.
+Additionally, Dopplergrams and vector magnetograms were obtained in \ion{Fe}{1} 525.02 nm using the Imaging Magnetograph eXperiment \citep[IMaX,][]{imax} at various locations on the solar disk.
+Throughout these flights, Sunrise observed a variety of solar phenomena, including emerging flux events \citep{centeno17}, properties and dynamics of moving magnetic features around pores \citep{kaithakkal17}, proper motion of bright points in quiet sun and active regions \citep{jafarzadeh17}, and properties of fibrils \citep{gaferia17}.
+These observations underscored the wealth of information carried by this wavelength range and paved the way for full-disk coverage of the Sun in the NUV.
+
+The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article}, iss one of the seven payloads aboard the Aditya-L1 mission \citep{adityal1, aditya} led by the Indian Space Research Organization (ISRO).
+Launched on September 2, 2023, the satellite orbits around the Sun-Earth L1 point in a halo orbit.
+Equipped with eleven science filters, comprising eight narrow band and three broad band filters, SUIT possesses a distinctive capability to explore various heights within the solar photosphere and chromosphere.
+This capability aids in understanding the diverse physical processes involved in the transport of mass and energy across different layers of the Sun.
+Additionally, SUIT offers a unique opportunity to spatially measure the solar spectral irradiance in the Near Ultraviolet (NUV) range, a critical aspect in advancing our comprehension of Sun-climate relationships.
+
+{\suit} is designed to deliver continuous full-disk and Region of Interest (RoI) solar images, boasting a plate scale of 0.7 \arcsec.
+It possesses the ability to track RoIs while compensating for the effects of differential rotation, as outlined by \cite{suit_algo}.
+Additionally, SUIT is equipped with onboard intelligence to detect and localize flares, and it can autonomously adjust exposure times to prevent saturation.
+The primary scientific inquiries targeted by SUIT include \citep{suit_science, suit_main}:
+
+\begin{itemize}
+    \item dynamic coupling between the lower and the middle solar atmosphere
+    \item measurement of solar spectral radiance in the NUV.
+    \item spectral energy distribution of solar flares in NUV
+    \item dynamics of chromospheric eruptive phenomena at various spatiotemporal scales
+    \item Initiation of Coronal Mass Ejections(CMEs) and space weather: the kinematics of erupting prominences during the early phase.
+\end{itemize}
 
@@
 Since the number of flares also shows a change with solar activity, it is prudent to ask how much flares contribute to the solar spectral irradiance in NUV.
-This is particularly important because the irradiance in NUV plays a key role in heating the upper and middle layers of the Earth's atmosphere directly and their coupling with Stratosphere.
+This is particularly important because the irradiance in NUV plays a key role in heating the upper and middle layers of the Earth's atmosphere directly and their coupling with the Stratosphere.
 It also directly influences the middle and lower atmosphere chemistry and composition via the Ozone-Oxygen cycle.

### 2024-05-06 chapter6/ms.tex
Updates from Overleaf

@@
 
- %   The \ion{Mg}{2}~k \& h line intensity ratios can be used to probe the characteristics of the plasma in the solar atmosphere.
-In this study, using the observations recorded by the Interface Region Imaging Spectrometer (IRIS), we study the variation of the \ion{Mg}{2}~k \& h intensity ratio for three flares belonging to X-class, M-class, and C-class, throughout their evolution.
+ %   The Mg II~k \& h line intensity ratios can be used to probe the characteristics of the plasma in the solar atmosphere.
+In this study, using the observations recorded by the Interface Region Imaging Spectrometer (IRIS), we study the variation of the Mg II~k \& h intensity ratio for three flares belonging to X-class, M-class, and C-class, throughout their evolution.
 We also study the k-to-h intensity ratio as a function of magnetic flux density obtained from the line-of-sight magnetograms recorded by the Helioseismic and Magnetic Imager (HMI) on board the Solar Dynamics Observatory (SDO).
@@
 The released energy can cause particle acceleration, heating and flows in the solar atmosphere and a transient enhancement in solar radiative output.
-It is observed that most of the energy radiated in flares originates from the dense chromosphere \citep{fletcher10,milligan14}.
-Hence, studying the chromospheric lines during flares provides us with diagnostics, which may be important for understanding the physics of solar flares and their effect on the local plasma environment.
+Notably, a significant portion of the radiated energy during flares originates from the dense chromosphere \citep{fletcher10,milligan14}.
+Therefore, examining chromospheric lines during flares offers valuable diagnostic tools for understanding the physics of solar flares and their impact on the local plasma environment.
 
-The chromosphere emits in various UltraViolet(UV) and optical lines.
-While many optical lines, e.g., H$\alpha$, \ion{Ca}{2}, are routinely observed from ground-based telescopes, observations in the \ion{Mg}{2} resonance lines have been rare in the past.
-Since the launch of the Interface Region Imaging Spectrograph \citep[IRIS;][]{IRIS} we have been in the position to monitor these lines regularly with excellent spatial and spectral resolution.
+The chromosphere emits radiation across various ultraviolet (UV) and optical lines.
+While many optical lines, such as H$\alpha$ and \ion{Ca}{2}, are routinely observed from ground-based telescopes, observations of the Mg II resonance lines have been relatively infrequent in the past.
+However, since the launch of the Interface Region Imaging Spectrograph (IRIS) \citep{iris}, regular monitoring of these lines with excellent spatial and spectral resolution has become possible.
 
-The \ion{Mg}{2}~k and h lines are transitions to the ground state from a finely split pair of upper levels ($3p~^{2}P_{\nicefrac{3}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$ and $3p ^{2}P_{\nicefrac{1}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$).
-These transitions create the optically thick lines in the wavelengths 2796.34~{\AA} (\ion{Mg}{2}~k) and 2803.52~{\AA} (\ion{Mg}{2}~h).
-It is suggested that the intensity ratios of these lines can be used to probe the optical depth of the local environment \citep{kerr15}.
+The Mg II k and h lines represent transitions to the ground state from finely split upper levels ($3p~^{2}P_{\nicefrac{3}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$ and $3p ^{2}P_{\nicefrac{1}{2}}${--}$3s^{2}S_{\nicefrac{1}{2}}$), resulting in optically thick lines at wavelengths 2796.34~{\AA} (Mg II k) and 2803.52{\AA} (Mg II h).
+It has been suggested that the intensity ratios of these lines can offer insights into the optical depth of the local environment \citep{kerr15}.
 
-The integrated intensity of a line transitioning from an upper-level j to a lower-level i, is dependent on the collision strength for that transition $\Omega_{ij}$, which is given by~\citep{henri62,mariska92},
+The integrated intensity of a line transitioning from an upper level $j$ to a lower level $i$ depends on the collision strength $\Omega_{ij}$ for that transition, given by~\citep{henri62,mariska92},
 
@@
 \begin{equation*}
-    \Omega_{ij}~=~\frac{8\pi}{\sqrt{3}}~\frac{I_{H}}{\Delta \epsilon_{ij}}~g~\omega_{i}~f_{ij}
+\Omega_{ij}=\frac{8\pi}{\sqrt{3}}~\frac{I_{H}}{\Delta \epsilon_{ij}}g\omega_{i}~f_{ij}
 \end{equation*}
@@
 
-\noindent Where $I_{H}$ is the ionization energy of Hydrogen, $\Delta \epsilon_{ij}$ is the threshold energy for the transition, g is the Gaunt factor, $\omega_{i}$ is the statistical weight of the level and $f_{ij}$ is the oscillator strength.
-In optically thin conditions, the intensity ratio of the k to h line is the ratio of the collision strengths, as the escape probability of photon is unity.
-The \ion{Mg}{2} k and h lines share the same ionization state and originate from a transition to a shared lowered level.
-As the statistical weight ($\omega_{i}$) is same in both cases, the line intensity ratio is simply the ratio of the oscillator strengths($f_{ij}$).
-This implies the ratio is 2:1 in optically thin conditions, and lower when the medium is optically thick \citep{kerr15,levens19}.
+\noindent Here, $I_{H}$ denotes the ionization energy of hydrogen, $\Delta \epsilon_{ij}$ represents the threshold energy for the transition, $g$ is the Gaunt factor, $\omega_{i}$ is the statistical weight of the level, and $f_{ij}$ stands for the oscillator strength.
+In optically thin conditions, the intensity ratio of the k to h line equals the ratio of collision strengths, as the escape probability of photons is unity.
+As the Mg II k and h lines share the same ionization state and originate from a transition to a shared lower level, and given that the statistical weight ($\omega_{i}$) is the same in both cases, the line intensity ratio is simply the ratio of oscillator strengths ($f_{ij}$).
+Consequently, this ratio is expected to be 2:1 in optically thin conditions and lower when the medium is optically thick \citep{kerr15,levens19}.
 
-In addition, the \ion{Mg}{2} k and h lines can be used to estimate the velocity in the middle and upper chromosphere, the chromospheric velocity gradients, the temperature in the middle chromosphere \citep{leenarts13a,leenarts13b,pereira13}.
-The \ion{Mg}{2} triplets in emission can be used to identify heating in the lower chromosphere \citep{pereira15}.
-There have also been multiple studies that have shown a spatial variation of the \ion{Mg}{2} line profiles \citep{dalda23,panos18}.
-\cite{polito23} showed that the leading edge of the flare ribbon is associated with enhanced broadening and strong central reversal.
-They interpreted the difference in the profile as a difference in the heating mechanism at the leading edge and bright part of the flare ribbons.
-\cite{panos21,panos21_2} showed similar differences between the line profiles and energy input.
+Moreover, the Mg II k and h lines can serve to estimate velocity in the middle and upper chromosphere, chromospheric velocity gradients, and temperature in the middle chromosphere \citep{leenarts13a,leenarts13b,pereira13}.
+Emission from the Mg II triplets can help identify heating in the lower chromosphere \citep{pereira15}.
+Various studies have demonstrated spatial variations in Mg II line profiles \citep{dalda23,panos18}.
+For instance, \cite{polito23} associated the leading edge of flare ribbons with enhanced broadening and strong central reversal, interpreting this difference in profile as indicative of distinct heating mechanisms at different locations within flare ribbons.
+Similarly, \cite{panos21,panos21_2} revealed differences in line profiles and energy input.
 
-Using the observations recorded by the OSO-8 LPSP instrument, \citep{lemaire84} studied the evolution of the intensity ratio of \ion{Mg}{2}~h~\&~k, \ion{Ca}{2}~h~\&~k and Ly~$\alpha$~\&~$\beta$ lines.
-\cite{lemaire84} showed that the intensity ratio of the \ion{Ca}{2}~k/h lines increased from 1 to 1.2 during the ascending phase of a flare and returned to 1 during the later phases.
-The authors interpreted the correlated temporal behavior across various elements as an indication of downward energy propagation.
-We note that this may suggest a slight decrease in the opacity due to localized heating at the formation height of the \ion{Ca}{2} line during the rise phase of the flare.
+Using observations recorded by the OSO-8 LPSP instrument, \citep{lemaire84} investigated the evolution of intensity ratios of Mg II h \& k, \ion{Ca}{2} h \& k, and Ly$\alpha$ \&~$\beta$ lines.
+They observed that the intensity ratio of the \ion{Ca}{2}~k/h lines increased from 1 to 1.2 during the ascending phase of a flare and returned to 1 during later phases.
+This correlated temporal behavior across various elements was interpreted as an indication of downward energy propagation, suggesting a potential decrease in opacity due to localized heating at the formation height of the \ion{Ca}{2} line during the flare's rise phase.
 
-%\sout{In spite of the excellent potential of these spectral lines in diagnosing the localized atmosphere, such} \sout{studies have not been taken up in detail due to the scarcity of spectral observations in these lines.}
+Here, we investigate the evolution of intensity ratios of the Mg II h \& k lines during three flares: C-class, M-class, and X-class.
+Specifically, we focus on the dependence of line ratios on the underlying magnetic field strength, a relationship that, to our knowledge, has not been explored previously.
+The remainder of this chapter is organized as follows.
+Section \ref{sec:obs} presents the observations utilized in this study, followed by our data reduction and analysis methods, and the results in Section \ref{sec:dar}.
 
-Here, we study the evolution of the intensities ratios of the \ion{Mg}{2}~h~\&~k lines during the course of the evolution of three flares, \textit{viz.}, C-class, M-Class and X-class.
-We focus on the the dependence of line ratios on the underlying magnetic field strength, which to our knowledge has not been explored so far.
-The rest of the paper is structured as follows.
-\S\ref{sec:obs} discusses the observations used in this paper.
-We discuss how we reduce and analyze the data and the results in \S\ref{sec:dar}.
+%%----------------------------------------------------
+\section{Observations} \label{sec:obs}
+%%----------------------------------------------------
+%%-------------------------------------------------------
+\begin{table*}[ht!]
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+Event & Flare & Flare & Raster & Raster Step & Raster \\
+Date & Peak (UT) & Location (arcsec) & Details & (arcsec) & Cadence (s)\\
+\hline
+Nov 4, 2015  & 13:52 & [37",61"] & Coarse & 2" & 50\\
+(M-class) & & & 16-step  & & \\
+ & & & & & \\
+Oct 22, 2014 & 14:28 & [-292",-302"] & Coarse & 2" & 131\\
+(X-class) & & & 8-step  & & \\
+ & & & & & \\
+Feb 3, 2015 & 22:55 & [198",213"] & Dense & 0.35" & 33\\
+(C-class) & & & 16-step  & & \\
+\hline
+\end{tabular}%}
+%\end{center}
+\caption{List of flares studied in this chapter.}
+\label{tab:my_label}
+\end{table*}
+%%-------------------------------------------------------
+
+For this study, we selected three flares of M, X, and C classes, as listed in Table~\ref{tab:my_label} by IRIS.
+IRIS is a NASA small explorer-class solar observation satellite that obtains UV spectra with high spatial (0.33{--}0.4\arcsec per pixel), temporal (1s), and spectral resolution ($\sim$26 and $\sim$53~m{\AA}).
+The primary lines regularly observed by IRIS include \ion{C}{2}, Mg II, and \ion{Si}{4}.
+In the imaging channel, it typically observes in Mg II and \ion{Si}{4}.
+In our study, we utilized observations recorded in the Mg II h\& k lines.
+
+As mentioned earlier, this study aims to analyze the evolution of intensity ratios concerning magnetic flux density during the flares of various classes.
+To achieve this, we incorporated line-of-sight (LOS) magnetic field measurements from the Helioseismic and Magnetic Imager \citep[HMI;][]{hmi} on the Solar Dynamics Observatory \citep[SDO;][]{sdo}.
+We utilized observations taken at 1600~{\AA} by the Atmospheric Imaging Assembly \citep[AIA;][]{aia}, also onboard SDO, to co-align the IRIS observations with those from AIA and subsequently HMI.
+
+%%----------------------------------------------------
+\section{Data analysis and results} \label{sec:dar}
+%%----------------------------------------------------
+\subsection{M3.7 Flare Observed on Nov 4, 2015}
+%%%----------------------------------------------
+%%--------------------------------------------------
+
+NOAA AR 12443 generated a multi-ribbon GOES class M3.7 flare on November 4, 2015, which commenced around 13:31 UT and peaked at approximately 13:52 UT, as observed from the GOES Soft X-ray (SXR) 1{--}8~{\AA} flux (Fig.\ref{flare1}a).
+This event occurred at approximately [37\arcsec,61\arcsec] heliographic position and was extensively observed by IRIS, AIA, and HMI.
+Fig.\ref{flare1}a illustrates the GOES flux plot of the flare in the 0.5{--}4~{\AA} range (blue) and the 1.0{--}8.0~{\AA} range (red).
+Fig.\ref{flare1} b depicts AIA 1600{\AA} image of the flaring region, showing two ribbons indicated by arrows.
+In panel (c), we present the line-of-sight (LOS) magnetic flux density map obtained from HMI, recorded nearly simultaneously with the AIA image shown in panel (b).
+The white (black) box overlaid on Fig.\ref{flare1}(b) (c) represents the IRIS SJI (Slit-Jaw Imager) field of view (FOV).
+The white dot-dashed (magenta dashed) box in Fig.\ref{flare1}b (c) indicates the IRIS raster FOV.
+The FOV of the SJI (approximately [120\arcsec~$\times$119\arcsec]) covers the central part of the flaring region, with a spectral sampling of approximately 0.05~{\AA}/pixel.
+\cite{li17} investigated the dynamics of the ribbons for this flare, while \cite{karlick18} studied the associated radio bursts.
+
+%%--------------------------------------------------
+\begin{figure*}[ht!]
+    \centering
+\includegraphics[trim={7cm 5cm 7.7cm 6cm},clip,width=\textwidth]{Figures/Flare_M_Nov04_2015_2.eps}
+\caption{The M3.7 flare observed on November 4th, 2015.
+Panel a: GOES flux plot in 0.5{--}4~{\AA} (blue) and 1.0{--}8.0~{\AA} (red).
+Panel b: AIA 1600~{\AA} image of the flaring region.
+Arrows locate the primary ribbons.
+Panel c: LOS magnetic flux density map obtained from HMI near the peak of the flare.
+The over-plotted white (black) boxes in panel b (c) represent the IRIS SJI FOV.
+The over-plotted white dot-dashed (magenta dashed) box in panel b (c) shows the IRIS raster FOV.}\label{flare1}
+\end{figure*}
+%%--------------------------------------------------
+
+Figure~\ref{flare_m_ev} illustrates the evolution of the flare in AIA 304~{\AA}.
+The flare is connected with a pre-existing filament that undergoes an eruption, splitting into two structures denoted as F1 \& F2 in Fig.\ref{flare_m_ev}(b) \& (c).
+These two filament structures diverge from each other in opposite directions.
+The flare generates two primary flare ribbons, labeled as R1 \& R2 in Fig.\ref{flare_m_ev}(b), (c) \& (d).
+Starting around 13:32 UT, R1 travels southeastward, crossing the IRIS raster FOV, indicated by the white dotted box in Fig.\ref{flare_m_ev}(a), (b), (c) \& (d).
+The IRIS raster monitors the movement of the northern ribbon R1 and the eastern edge of R2.
+An animated version of Fig.\ref{flare_m_ev} is available in the online journal for further details.
+
+%%%--------------
+\begin{figure*}[ht!]
+    \begin{center}
+    \includegraphics[width=\textwidth]{Figures/nov_flare_304_aa_evolv.eps}
+    \end{center}
+    \caption{Sequence of AIA 304~{\AA}~images for the Nov 4th, 2015 flare.
+The white dotted box shows the portion of the IRIS raster FOV which scanned the ribbons.
+In panels b (c) F1 and F2 are the filament material, which move away from each other as the flare progresses.
+R1 and R2 in b (c,d) show the primary ribbons which move through the IRIS raster FOV.
+An animation of this image sequence is available in \cite{roy24}.}
+    \label{flare_m_ev}
+\end{figure*}
+%%%--------------
+
+Fig.\ref{flare_m_aia} presents the same region as depicted in Fig.\ref{flare_m_ev} across the six coronal channels (i.e., 94, 131, 171, 193, 211, 335~{\AA}) of SDO/AIA, recorded at the peak (top two rows) and during the decline phase (bottom two rows) of the flare.
+Post-eruption arcades \citep[][]{TriBC_2004} are clearly observable in all the channels, displaying slightly varied morphologies.
+These arcades contain evaporated thermal plasma and exhibit loop top brightening, likely due to colliding evaporation flows \citep[see, e.g.,][]{sharma16, patsourakos04}.
+
+%%%--------------
+\begin{figure*}[ht!]
+    \begin{center}
+        \includegraphics[trim={4.5cm 5.5cm 6cm 4cm},clip,width=0.9\textwidth]{Figures/nov_flare_aia_waves_2.pdf}
+    \end{center}
+    \caption{The Nov 4th, 2015 flare in the six Coronal channels of the SDO/AIA at the soft X-ray peak (panels (a)-(f)) and during the decline phase (panels (g)-(l)) of the flare.}
+    \label{flare_m_aia}
+\end{figure*}
+%%%--------------
+
+We begin by aligning the HMI observations with the IRIS observations using the 1600~{\AA} data recorded by AIA.
+Given that the observation involves an active region undergoing flaring, the magnetic field may also be rapidly changing \citep{wang02,dandan16,spirock02}.
+Therefore, we utilize a series of co-aligned full-disk maps from AIA and HMI to derive a rastered line-of-sight (LOS) map of magnetic flux density that precisely corresponds to the location and time of IRIS rasters.
+This procedure is outlined below.
+
+Initially, we align the AIA 1600~{\AA} observation with the HMI observation closest in time to the IRIS SJI (Slit-Jaw Imager) and raster observations.
+Using the `aia\_prep' tool available in the \textit{sswidl} distribution, we process the level 1 images to perform image registration and align AIA and HMI observations.
+Subsequently, we calculate the shift between AIA 1600~{\AA} and the SJI 1400~{\AA}.
+Using these calculated offsets, we co-align the magnetograms with the IRIS SJI 1400~{\AA} observations, given that the AIA 1600~{\AA} observation was already aligned with the HMI observations.
+We typically observe an offset of approximately $\sim$ 1.5\arcsec~between HMI and IRIS.
+These co-aligned HMI maps are then utilized to derive the rastered magnetograms, which can be directly compared with IRIS raster observations.
+
+For analyzing the properties of the Mg II lines, we fit a double Gaussian profile to both the k and h lines with a linear background symmetric about the line core.
+If excess emission is detected compared to the fitted background and line profile for wavelengths lower than 2792~{\AA} and in-between 2798~{\AA} to 2800~{\AA}, we infer the presence of Mg II triplets in emission.
+A single Gaussian profile is fitted to the excess emission.
+It's important to note that this approach may overlook the triplets unless the emission is sufficiently strong.
+However, this method serves our purpose since our primary objective is to characterize the Mg II k and h line profiles.
+
+Additionally, we exclude any pixels showing saturation in either of the lines.
+The uncertainty of the observed intensities is measured in DN (Data Numbers) using the method outlined in \S 2:1 of \cite{kerr15} and subsequently applied in the fitting procedure.
+The uncertainties of the fitted Gaussian profiles are incorporated while integrating the profile to obtain the uncertainty of the line intensities.
+
+%%%%-------------------------
+\begin{figure}[h!]
+\centering  
+\includegraphics[trim={7cm 5cm 6cm 10cm},width=0.8\textwidth]{Figures/m_flare_iris.pdf}
+\caption{Obtained images in Mg II h (panel a) and k (panel b) and corresponding co-aligned and artificially rastered HMI LOS magnetic field map (panel c) for the M3.7 flare observed on November 4th, 2015.
+The magenta and lime green contours on panel c show the contours of Mg II~h (panel a) and k (panel b) intensity.} \label{fig:aligned_raster}
+\end{figure}
+%%%%-------------------------
+
+%%%%%%%%%%%
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim={0cm 3cm 0.5cm 3cm},clip,width=\textwidth]{Figures/pix_fit.pdf}
+    \caption{Fit of the Mg II window for the pixel marked in northern ribbon (southern ribbon) in Fig.~\ref{fig:aligned_raster} in top panel (bottom panel) from various times during the evolution of the flare.
+}
+    \label{fig:pix_fit_ribbon}
+\end{figure*}
+%%%%%%%%%%%
+
+%%%%-------------------------
+\begin{figure}[ht!]
+\centering  
+\includegraphics[trim={1.5cm 4cm 0.5cm 4cm},clip,width=0.8\textwidth]{Figures/m_flare_iris_pt2.pdf}
+\caption{The 1{--}8~{\AA} GOES light curve of the flare over-plotted with the time variation of Mg II k/h line intensity ratio for the northern (black) and southern (green) asterisks marked in panels a, b \& c.}
+\label{fig:aligned_iris_ratio}
+\end{figure}
+%%%%-------------------------
+
+In Figure~\ref{fig:aligned_raster}, we present intensity maps obtained in Mg II h \& k (panels a \& b) alongside the rastered line-of-sight (LOS) magnetic field map in panel (c).
+The dashed magenta and solid green contours on the magnetic field maps represent the intensity from panels a and b, respectively.
+To investigate the Mg II k to h intensity line ratios over time, we selected two pixels—one in the northern ribbon and another in the southern ribbon, as indicated by crosses.
+Fig.\ref{fig:pix_fit_ribbon} displays the spectra overlaid with fits for the two pixels taken in the northern ribbon (top panel) and southern ribbon (bottom panel) obtained at different times.
+
+We illustrate the Mg II k to h line intensity ratio derived from the two locations in the northern (black) and southern ribbons (green) in Fig.\ref{fig:aligned_iris_ratio}.
+Additionally, we overlay the GOES light curve of the flare obtained in 1.0{--}8.0{\AA} (red solid line).
+Our observations indicate that the intensity ratios exhibit a slightly increasing trend, albeit within the margin of errors, during the early phase of the flare.
+The ratio demonstrates a distinct peak around the midpoint of the impulsive phase, lasting for a very brief duration of approximately 150 seconds, before beginning to decrease.
+It's worth emphasizing that the pixel-by-pixel fitting of the Mg II h \& k line profiles provided a sufficient signature of the time evolution of the k/h line intensity ratio during the flare.
+
+%%%%%%%--------%%%%%%%%%%%
+\subsection{Investigating the dependence on the local magnetic field in the Mg II lines}
+%%%%%%%---------%%%%%%%%%%
+
+To explore the time evolution of the intensity ratio and its potential relationship with the photospheric magnetic field, we binned the spectra into various magnetic field bins from different flaring pixels.
+We selected the flaring pixels based on an intensity threshold relative to the peak intensity observed in IRIS rasters.
+A double Gaussian fit with a constant background was performed in a smaller wavelength window for both the Mg II h and k lines separately.
+This step was essentially carried out to mitigate the effects of the background and potential contributions from other spectral features.
+
+Fig.~\ref{fig:fit_pix_fov} displays the Mg II k line profiles obtained at different times and averaged over different magnetic field bins.
+Each plot denotes the observation time and the magnetic field strength over which the spectra were averaged and fitted with a double Gaussian.
+Line intensities were computed by integrating the fitted Gaussians.
+
+In Fig.~\ref{fig:optical_depth_m}, we present the k to h intensity ratios obtained in various bins of magnetic flux density at different times corresponding to different flare phases.
+The curve corresponding to 13:07:05 UT (red) represents the pre-flare phase, where the ratio is approximately 1.2.
+The ratio shows an increase during the impulsive phase, i.e., the curves corresponding to 13:23:44 UT (blue dotted) and 13:32:04 UT (green dashed).
+The ratio measured at 13:41:11 UT (magenta dashed), which is closest to the UV peak of the flare, exhibits the largest value across all magnetic field bins.
+Subsequently, during the decline phase, the ratio measured at 13:57:23 UT (black solid) falls below the values observed during the pre-flare phase.
+Additionally, it's noteworthy that there are no significant differences among the k to h ratios obtained in different bins of magnetic flux density at all times (including pre-flare, impulsive, peak, and decline phases) of the flare.
+
+%%%%-----------------------
+\begin{figure*}[ht!]
+    \begin{center}
+    \includegraphics[trim={0cm 3cm 0cm 3cm},clip,width=\textwidth]{Figures/binned_fit_fov.pdf}
+    \end{center}
+    \caption{Fitted line profiles for the binned spectra for various magnetic field strengths from various times.}
+    \label{fig:fit_pix_fov}
+\end{figure*}
+%%%%-----------------------
+
+%%----------------------------------------------------------------------------
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={8cm 1cm 2cm 0.2cm},clip,width=0.9\textwidth]{Figures/Flare-m-optical-depth-2.jpeg}
+    \caption{Mg II k to h line intensity ratio for various magnetic flux density bins at various time steps during the evolution of the flare.}
+    \label{fig:optical_depth_m}
+\end{figure}
+%%----------------------------------------------------------------------------
+
+To explore further, we study the evolution of k to h intensity ratio as a function of time during the flare.
+In Fig.~\ref{fig:optical_dep_ev_m}, we plot the time evolution of the k to h line intensity ratio averaged within the bins of different magnetic flux densities as a function of time.
+For better visibility the 20.9{--}184.4 G and 348.9{--}513.3 G points are offset by 30s and -30s, respectively.
+We also plot the GOES 1{--}8~{\AA} light curve with the red solid line.
+These plots conspicuously reveal that the intensity ratios rise sharply during the impulsive phase, from $\sim$ 1.20 to $\sim$ 1.28 right before the soft X-ray flux peaks as seen from GOES, and decreases very rapidly thereafter, to lower than pre-flare values $\sim$ 1.12.
+The typical uncertainty value for the line intensity ratio is $\sim$ 0.02.
+We further note that the evolution of the Mg II k to h intensity ratio is remarkably similar across various strengths of magnetic flux densities.
+
+%%%----------------------------------------------
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim={3cm 3cm 2cm 4cm},clip,width=\textwidth]{Figures/Nov-11-2015-optical-dep-ev-5.pdf}
+    \caption{Time evolution of the Mg II k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin as labeled for the Nov 4, 2015 flare.
+For better visibility, the 20.9{--}184.4 G and 348.9{--}513.3 G points are offset by 30s and -30s respectively.
+Over-plotted red solid line displays the 1{--}8~{\AA} GOES X-ray light curve.}
+    \label{fig:optical_dep_ev_m}
+\end{figure*}
+%%%----------------------------------------------
+
+%%%----------------------------------------------
+\subsection{X1.6 Flare Observed on Oct 22, 2014}
+%%%----------------------------------------------
+
+An X~1.6 flare occurred on October 22, 2014, observed in AR 12192.
+The flare commenced at 14:02 UT and peaked at 14:28 UT as observed by GOES.
+Fig.\ref{flare2}(a) illustrates the GOES flux plot of the flare in the 0.5{--}4~{\AA} range (blue) and the 1.0{--}8.0~{\AA} range (red).
+Figs.\ref{flare2}(b) \& (c) display an AIA 1600{\AA} image and the line-of-sight (LOS) magnetic flux density map obtained from HMI, respectively.
+The overlaid boxes in panels (b) and (c) indicate the IRIS SJI (Slit-Jaw Imager) field of view (FOV).
+IRIS observed this flare with a large 8-step coarse raster covering a FOV of [14\arcsec,174\arcsec].
+It's worth noting that the IRIS SJI FOV and the slit direction were rotated by approximately 45$^\circ$ relative to the center of the HMI observation.
+
+%%--------------------------------------------------
+\begin{figure*}[ht!]
+    \centering
+\hspace*{-.5in}
+\includegraphics[width=\textwidth,trim={7cm 5cm 7.7cm 6cm},clip]{Figures/Flare_X_oct22_2014_2.eps}
+\caption{The X class flare observed on October 22, 2014.
+Panel a: GOES flux plot in 0.5{--}4~{\AA} (blue) and 1.0{--}8.0~{\AA} (red).
+Panel b: AIA 1600~{\AA} image taken at the peak of the flare.
+Arrows locate the primary and secondary ribbons.
+Panel c: LOS magnetic flux density map obtained from HMI at the peak of the flare.
+The over-plotted white (black) box in panel b (c) represents the IRIS SJI FOV, and white dot-dashed (dashed) box in panels b (c) represents the IRIS Raster FOV.}\label{flare2}
+\end{figure*}
+%%--------------------------------------------------
+
+The flare manifests two ribbons in AIA 1600{\AA}, as indicated by the arrows.
+The eastern ribbon extends around a negative field region and is entirely covered by the IRIS SJI FOV.
+Conversely, the western ribbon extends around a positive field region, with only a portion of it covered by the IRIS SJI FOV, as depicted in panel (b).
+In Fig.~\ref{fig:align_raster_flare2}, we present intensity maps obtained in Mg II h \& k (panels a \& b) alongside the rastered line-of-sight (LOS) magnetic field map (panel c).
+The black \& green dashed contours in the LOS magnetic field map (panel c) indicate the intensity contours of Mg II h \& k (panels a \& b).
+
+%%--------------------------------------------------
+\begin{figure}[ht!]
+    \centering
+%    \hspace{2in}
+    \includegraphics[trim={6cm 3cm 6cm 3cm},clip,width=0.45\textwidth]{Figures/contour_paper_plot_oct28.pdf}
+    \includegraphics[trim={3cm 2cm 2cm 3cm},clip,width=0.45\textwidth]{Figures/Oct-22-2014-optical-dep-ev-2.pdf}
+    \caption{Obtained intensity maps in Mg II~k (panel a) and h (panel b) lines at the peak of the flare.
+The rastrered HMI LOS magnetic field density map is shown in panel c.
+The black and lime green contours on panel c show the contours of Mg II~k (panel a) and h (panel b) intensity.}
+\label{fig:align_raster_flare2}
+\end{figure}
+%%--------------------------------------------------
+
+Similar to the M-class flare studied in the previous section, we derive the Mg II k to h line intensity ratio for various bins of the magnetic flux density within the flaring region and study their time evolution.
+In Fig.\ref{fig:align_raster_flare2} right panel, we plot the intensity ratio in black and magenta colors for two different magnetic field bins.
+In the same panel, we also overlay the 1{--}8~{\AA} GOES light curve (red solid line).
+We note that, unlike the M-class flare, we do not observe any noticeable change in the intensity ratio during the flare.
+There are approximately two to three data points showing an enhancement in the ratio, but these occur well before the onset of the flare.
+
+%%%----------------------------------------------
+\subsection{C3.5 Flare Observed on Feb 03, 2015}
+%%%----------------------------------------------
+
+On February 3, 2015, AR 12277 generated a C-class flare that peaked at 22:55 UT.
+Fig.\ref{flare3} depicts the GOES flux plot of the flare in the 0.5{--}4{\AA} range (blue) and the 1.0{--}8.0~{\AA} range (red) in panel (a).
+Fig.\ref{flare3}(b) \& (c) displays an AIA 1600{\AA} image and the line-of-sight (LOS) magnetic flux density map obtained from HMI, respectively, recorded near the peak of the flare.
+
+The overlaid white (black) box in panel (b) ((c)) indicates the IRIS SJI (Slit-Jaw Imager) field of view (FOV).
+The over-plotted white dot-dashed (magenta dashed) box in panel (b) ((c)) indicates the IRIS raster FOV.
+IRIS observed this flare with a large dense 16-step raster with a FOV of 5"$\times$119" and a step size of 0.35\arcsec.
+The flare exhibits a double ribbon structure, with the east ribbon elongating earlier and merging into the west ribbon.
+The IRIS raster scans through the west edge of the west ribbon through its eruption and merging with the east ribbon.
+Fig.~\ref{fig:align_raster_flare3} displays the intensity maps obtained in Mg II h \& k (panels a \& b).
+The rastered LOS magnetic field map is shown in panel (c).
+The black \& green dashed contours in the LOS magnetic field map (panel c) depict the intensity contours of Mg II h \& k (panels a \& b).
+
+%%--------------------------------------------------
+\begin{figure*}[ht!]
+    \centering
+\hspace*{-.6in}
+\includegraphics[width=1.12\textwidth,trim={7cm 5cm 7.7cm 6cm},clip]{Figures/Flare_C_feb03_2015_2.eps}
+%\includegraphics[width=.7\textwidth]{figures/Feb_03_2015/Feb-04-2015-optical-dep-ev-2.eps}
+\caption{The C class flare observed on February 3rd, 2015.
+Panel a: GOES flux plot in 0.5{--}4~{\AA} (blue) and 1.0{--}8.0~{\AA} (red).
+Panel b: AIA 1600~{\AA} image of the flaring region.
+Panel c: LOS magnetic flux density map obtained from HMI near the peak of the flare.
+The over-plotted white (black) boxes in panel b (c) represents the IRIS SJI FOV.
+The over-plotted white dot-dashed (magenta dashed) box in panel b (c) show the IRIS raster FOV.}\label{flare3}
+\end{figure*}
+%%--------------------------------------------------
+
+%%--------------------------------------------------
+\begin{figure}[ht!]
+    \centering
+%\hspace*{-1.in}
+\includegraphics[width=0.5\textwidth,trim={4cm 5cm 4cm 4cm},clip]{Figures/contour_paper_plot_feb-03-2015.pdf}
+\caption{Obtained intensity maps in Mg II~k (panel a) and h (panel b) lines at the peak of the flare.
+The rastrered HMI LOS magnetic field density map is shown in panel c.
+The black and lime green contours on panel c show the contours of Mg II~k (panel a) and h (panel b) intensity.}
+\label{fig:align_raster_flare3}
+\end{figure}
+%%--------------------------------------------------
+
+%%--------------------------------------------------
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={2cm 3cm 2cm 3cm},clip,width=0.8\textwidth]{Figures/Feb-04-2015-optical-dep-ev-2.pdf}
+    \caption{Time evolution of the Mg II k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin as labeled for the Feb 3, 2015 flare.
+Over-plotted red solid line displays the 1{--}8~{\AA} GOES X-ray light curve.}
+    \label{fig:optical_dep_ev_c}
+\end{figure}
+%%--------------------------------------------------
+
+We present the GOES 1{--}8~{\AA}light curve (red solid line) alongside the time evolution of the Mg II k to h line intensity ratio averaged within the bins of two different magnetic flux densities as a function of time in Fig.\ref{fig:optical_dep_ev_c}.
+The Mg II k to h line intensity ratio exhibits a similar variation as observed in the M-class flare.
+It peaks during the impulsive phase (k/h$\sim$ 1.12) and decreases to preflare values (k/h$\sim$ 1.09) during the decay phase of the flare, coinciding with the peak of the GOES light curve.
+It's worth noting that the change in the Mg II k to h line intensity ratio is less pronounced for this flare compared to the M-class event.
+However, we also observe that the ratio shows a persistent increase from the onset of the flare.
+
+%%--------------------------------------------------
+\section{Outlook}
+%%--------------------------------------------------
+
+The Mg II~k to h line intensity ratios serve as a valuable diagnostic for assessing the opacity of the local plasma and can provide insights into changes in the local plasma environment within the solar chromosphere during flares.
+In this study, we investigated the temporal variation of Mg IIk to h line intensity ratios during the evolution of three flares classified as X-class, M-class, and C-class.
+We also examined the variation of intensity ratios across different magnetic flux density bins, utilizing observations from IRIS and HMI.
+Co-alignment of IRIS and HMI observations was achieved using 1600{\AA} images recorded by AIA.
+
+It's well-documented that Mg II profiles exhibit significant spatial variations within flaring regions \citep{dalda23,panos18}.
+As we binned the IRIS observations based on magnetic field strength, it's important to note that any spatial variation is averaged out and not addressed in our analysis.
+
+Our findings reveal that Mg II k to h line intensity ratios undergo changes during flares.
+For M-class and C-class flares, the ratio starts increasing at the onset of the flare, peaks roughly halfway through the impulsive phase, and then steeply declines thereafter (see Figs.\ref{fig:optical_dep_ev_m} \& \ref{fig:optical_dep_ev_c}).
+Moreover, the ratios drop even below pre-flare levels during the later stages of the flare (peak and decline phase).
+However, this behavior is observed only in M and C-class flares, not in X-class flares.
+
+Our observations did not reveal any correlation between line intensity ratios and magnetic flux density.
+The line intensity ratios for different magnetic field strengths illustrated in Figs.\ref{fig:optical_depth_m},\ref{fig:optical_dep_ev_m},~\ref{fig:optical_dep_ev_c} indicate a consistent behavior from weak to strong magnetic field strengths.
+This suggests that the magnetic field similarly affects both Mg II~k and h lines, and such effects cancel out when taking the ratios.
+
+\cite{kerr15} studied Mg II~k to h line intensity ratios and their temporal variation for individual pixels in both quiet Sun regions and flare locations.
+While no change in ratios was observed for the quiet Sun region, variations were noted in flaring pixels, suggesting possible differences in heating conditions between non-flaring and flaring atmospheres.
+However, no correlated change in the ratio with respect to the flare light curve was observed.
+
+Our results align with those of \cite{kerr15}, wherein they also observe the highest change in the ratio during the impulsive phase of the flare, decreasing before the flare reaches its maximum in GOES 1{--}8~{\AA} observations.
+Such variations in the ratio may indicate changes in the optical depth of the local medium.
+During the impulsive phase, decreased optical depth might be attributed to localized heating and chromospheric evaporation, while during the decay phase, increased optical depth could be due to condensation and downflows.
+However, this interpretation remains speculative, particularly as we did not observe such effects in X-class flares.
+
+The results obtained for M-class and C-class flares can be explained by the aforementioned scenario, but the findings for X-class flares are more ambiguous.
+We couldn't establish a clear distinction in the general properties of these three flares.
+Notably, while the C-class flare is confined, both M and X flares are eruptive.
+Therefore, it's plausible that in X-class flares, energy deposition occurs more impulsively and on a shorter timescale than can be sampled.
+This high impulsiveness may lead to a greater degree of ionization of the medium compared to the other two flares, as supported by the large number of saturated pixels in the data that were discarded.
+A more definitive conclusion would necessitate analysis of additional such flares, including numerical and theoretical modeling.
+
+The SUIT has four separate narrow band filters for the Mg window, namely NB2 (Blue wing of Mg II k), NB3 (Mg II k), NB4 (Mg II h) and NB5 (Red wing of Mg II h).
+As mentioned in chapter \ref{c:chap2} SUIT observes the full-disk Sun continuously in NB4 with $\sim$ 1 minute cadence and full-disk observations in all eleven science filters every 90 minutes.
+With the full disk observations in all science filters, we can investigate the opacity variations continuously across various solar features with a cadence of 90 minutes with the NB3 and NB4 ratio.
+In flare mode, the observing filter sequence is customizable.
+With high cadence observations in NB3 and NB4, we can investigate the effect of flare heating on the local plasma environment via its manifestation in opacity.

### 2024-05-06 chapter7/ms.tex
Updates from Overleaf

%%----------------------------------------------------
\section{Introduction} \label{sec:intro}
%%----------------------------------------------------

Solar flares are the largest magnetic events within our solar system. They are characterized by the sudden release of magnetic energy, leading to localized, transient heating of coronal plasma to temperatures exceeding approximately 10 million Kelvin (MK), significantly hotter than the surrounding coronal plasma at around 1 MK. Flares are typically identified by the peak soft X-ray flux observed by the X-Ray Sensor onboard the Geostationary Operational Environmental Satellites (GOES/XRS), often referred to as the "GOES class" \citep{xrs}. Flares classified as GOES class C and above typically heat the coronal plasma to temperatures ranging from 5 to 20 MK. These observations, which integrate over the entire solar disk, are commonly used to characterize the average physical properties of flare plasma.

It is widely acknowledged that active regions possess sufficient magnetic free energy to trigger flares and associated Coronal Mass Ejections (CMEs) \citep{emslie12, ash17}. The high temperatures observed in flare-induced coronal plasma are often attributed to the evaporation of chromospheric material, heated by the collisions of flare-accelerated electrons during the impulsive phase \citep{fletcher11}. However, there is also evidence suggesting that plasma may be directly heated within the corona in certain cases \citep[e.g.,][]{longcope11, reeves17}.

Numerous studies \citep{stosire07, emslie12, inglis14, warmuth16a, warmuth16b, ash17} have examined the partition between thermal and non-thermal energies in flares, aiming to shed light on the underlying physical processes. However, the results have been inconclusive, and there is currently no consensus regarding whether non-thermal energetic electrons possess sufficient energy to account for the observed thermal energy component in smaller flares.

These studies typically utilize peak thermal energy as a representation of the overall thermal output of flares. Consequently, our comprehension of flare energetics has predominantly been shaped by statistical analyses of bolometric output and peak thermal energy. While these metrics provide reasonable representations of the overall thermal output of flares, discerning subtle differences in heating mechanisms occurring at various stages of flares necessitates quantifying thermal energy as a function of time.

For instance, \citet{longcope11} proposed the existence of a super hot plasma component in some large solar flares, directly heated within the corona. Sustained temperatures observed in supra-arcade fans during flares have been attributed to phenomena such as supra-arcade downflows \citep[e.g.,][]{reeves17}, suppression of conduction by turbulence \citep[e.g.,][]{xie23}, or global compression from reconnection inflows \citep[e.g.,][]{reeves19}. These processes represent distinct mechanisms from chromospheric evaporation, characterized by the development of hard X-ray footpoints and increasing intensity of soft X-ray and EUV-emitting plasma as the loops fill.

Several studies \citep{hilarie05, caspi10} have attempted to estimate thermal energy as a function of time. The thermal energy of flares is defined as:
\begin{equation}
\mathrm{U_{Th}~\simeq~3n_{e}k_{B}TV}f,
\end{equation} \label{eq:t_eneg_1}
where $\mathrm{n_{e}}$ is the electron number density of the flaring plasma, 'V' is the volume of the flaring plasma, 'f' is the volume filling factor, and 'T' is the instantaneous temperature. A key challenge in characterizing flare thermal energy lies in determining the volume.

\citet{li23} and \citet{zhang19} utilized soft X-ray emitting regions' $\frac{1}{e^{2}}$ contour or intensity threshold on AIA 131 {\AA} observations to estimate the flare area (A), subsequently inferring the volume as $V \sim A^{\frac{3}{2}}$. \citet{hilarie05} employed a similar method using RHESSI soft X-ray images to estimate the lower limit of volume, assuming a "perfect arc-shaped" loop. They also estimated the evolution of cumulative non-thermal energy injected by electrons, assuming a thick-target model \citep{brown71}, and fitting RHESSI spectra to determine non-thermal energies in time bins with significant emission above 25 keV. \citet{caspi10} utilized a 50\% intensity contour of cleaned RHESSI images to estimate the flare area, inferring volume assuming spherical symmetry.

In all these cases, the assumption of symmetrical expansion proves useful, as thermal energy is estimated from spectra obtained by integrating multiple pixels. However, addressing the spatially varying multi-thermal nature of flaring plasma remains a challenge in these analyses. Determining the volume of the flaring plasma is a significant challenge in characterizing the thermal energy of flares. The filling factor `f' quantifies the fraction of the apparent volume filled with plasma of a specific temperature and may also account for geometric projection effects, representing the real volume projected into the observed apparent volume. Given the highly multi-thermal nature of flaring plasma and the rapidly changing volume during the flare's rise phase, defining a filling factor that accurately describes plasma volume evolution throughout the flare is challenging.

Here, we investigate the thermal energy evolution of two flares, an M-class and an X-class flare, utilizing existing tools and observations from various vantage points to improve the accuracy of estimating flaring plasma volume. We demonstrate that a more precise estimate of plasma volume impacts thermal energy estimates and has implications for the flare's energy budget. Additionally, we estimate the cumulative non-thermal energy deposited by non-thermal electrons and compare it with our thermal energy estimates.

In Section \ref{sec:obs}, we detail the observations utilized in this study and describe our analysis approach. Section \ref{sec:therm} outlines our method for estimating thermal energy, while Sections \ref{sec:los} and \ref{sec:non-therm} discuss our techniques for volume estimation and cumulative non-thermal energy estimation, respectively. Finally, we present and discuss our results in Section \ref{res}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations and Data Analysis}\label{sec:obs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We investigate the two flares using EUV imaging from multiple instruments, including the Atmospheric Imaging Assembly onboard the Solar Dynamics Observatory \citep[SDO/AIA;][]{sdo,aia}, the Extreme Ultraviolet Imager onboard the Solar Terrestrial Relations Observatory-A \citep[STEREO-A/EUVI;][]{stereo,euvi}, and the Solar Ultraviolet Imager onboard GOES \citep[GOES/SUVI;][]{suvi}. Additionally, we utilize imaging data from the Spectrometer/Telescope for Imaging X-rays onboard Solar Orbiter \citep[SO/STIX;][]{so,stix,stix1}, the X-Ray Telescope onboard Hinode \citep[Hinode/XRT;][]{xrt}, and the X-Ray Sensor onboard GOES. The X and M class flares are observed at the disk center and limb of the Sun, respectively, from the perspective of AIA.

The positions of various spacecraft relative to the flares' locations on the solar disk are illustrated in Figure \ref{fig:sc_pos}. Panel (a) displays the AIA 193 Å observation of the Oct 28, 2021 flare projected onto Heliographic Stonyhurst (HGS) coordinates, with the positions of SDO (magenta cross), SO (cyan circle), and STEREO-A (green triangle) marked with respect to the flare location. The flare is delineated by a white dotted circle. The relative separations between the spacecraft indicate differences in polar and azimuthal angles due to varying vantage points. Panel (b) presents the spacecraft positions projected onto the Heliocentric Inertial (HCI) frame for the same event, demonstrating differences in azimuthal angle and distance from the Sun's center. Similar plots for the Nov 29, 2021 flare are depicted in Panels (c) and (d), with EUVI 171 Å emission projected onto HGS and HCI coordinates, respectively.

%%%%######%%%%%%
\begin{figure*}[ht!]
    \centering
    \includegraphics[trim={1cm 0.5cm 1.2cm 0.5cm},clip,width=\textwidth]{flare_pos.pdf}
    \caption{Position of various instruments during the flares. Panel a: AIA 193 {\AA} observation during the 2021 Oct 28 event projected to Heliographic Stonyhurst (HGS) coordinates. The position of the flare is marked with a white dotted circle. The positions of {\it Solar Orbiter}, {\it SDO} and {\it STEREO-A} are marked with an olive circle, magenta cross and green triangle, respectively. The positions of the spacecraft signify the difference in both the polar (vertical axis) and the azimuthal (horizontal axis) angle and do not mark the connectivity of the spacecraft to the solar surface. Panel b: The positions of the spacecrafts projected onto the Heliocentric Intertial (HCI) frame for the 2021 Oct 28 event. The difference between the spacecraft show the difference in the azimuthal angle. Panel c: {\it STEREO-A}/EUVI 171 {\AA} observation during the 2020 Nov 29 event projected to HGS coordinates. The position of the flare is marked with a white dotted circle. The positions of {\it SDO} and {\it STEREO-A} are marked with a magenta cross and green triangle, respectively. Panel d: The positions of the spacecraft projected onto the HCI frame for the 2020 Nov 29 event.}
    \label{fig:sc_pos}
\end{figure*}
%%%%######%%%%%%

The X1 flare occurred on Oct 28, 2021 (SOL2021-10-28T15:35) near approximately $\sim~[0\arcsec,-500\arcsec]$ solar coordinates as observed from AIA. It was captured by SDO/AIA, STEREO-A/EUVI, GOES/SUVI, XRT, GOES/XRS, and STIX. AIA provided observations with passbands at 94, 131, 193, 171, 211, and 335 Å, with a pixel size of approximately 0.6 arcseconds. SUVI provided similar wavelengths to AIA: 94, 131, 195, 171, 195, and 284 Å, with a pixel size of approximately 2.5 arcseconds. STEREO-A/EUVI offered imaging in 171, 195, and 284 Å coronal passbands.

The flare exhibited a standard two-ribbon structure, along with a ridge at the top of the rising flare arcade \citep{longcope22}. The ridge, most prominently visible in the AIA 193 Å channel, was primarily created by the hotter \ion{Fe}{24} line (T~$\simeq$17 MK) and had a height of approximately $26~Mm$. This ridge was utilized to identify the loop-top in the AIA observation and calculate the loop height.

STIX provided X-ray imaging and spectroscopy in the 4-150 keV range, with spectroscopic observations in 32 pre-defined energy channels. Fig.\ref{fig:flare}a depicts an AIA 193 Å image of the flare during the decay phase, while Fig.\ref{fig:flare}b overlays STIX intensity contours (15:27:40 {--} 15:28:00 UT) in the 4{--}16 keV (pink solid line) and 15{--}60 keV (blue solid lines) ranges on an AIA 1600 Å image during the rise phase. The MEM-GE algorithm was used to construct the STIX intensity maps.

The M flare occurred on November 29, 2020, near approximately $[-950\arcsec,-430\arcsec]$ solar coordinates from the AIA perspective. In AIA images, the footpoints were occulted behind the limb. It was recorded by STEREO-A/EUVI, GOES/SUVI, Hinode/XRT, GOES/XRS, and Fermi/GBM. There were no STIX observations for this event.

The flare exhibited a fan visible in the hot channels of AIA (131 and 193 Å) and the XRT channels. Fig. \ref{fig:flare2}a shows an AIA 131 Å image during the decay phase, while Fig.~\ref{fig:flare2}b displays an XRT Be-med filter observation taken near simultaneously with the AIA image. For the M-class event, Fermi observations were periodically eclipsed during the flare duration, rendering it challenging to estimate the cumulative non-thermal energy accurately. Hence, the estimation of cumulative non-thermal energy would not be a fair representation of the total non-thermal energy available.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Thermal Energy}\label{sec:therm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To estimate the thermal energy of the X-class event, we calculate the differential emission measure (DEM) of the flaring region using data from the six AIA passbands, including 94 Å (\ion{Fe}{10} $\sim$1.1 MK, \ion{Fe}{18} $\sim$7.1 MK), 131 Å (\ion{Fe}{8} $\sim$0.4 MK, \ion{Fe}{21} $\sim$11 MK), 171 Å (\ion{Fe}{9} $\sim$0.6 MK), 193 Å (\ion{Fe}{12} $\sim$1.6 MK, \ion{Fe}{24} $\sim$17 MK), 211 Å (\ion{Fe}{14} $\sim$2 MK), and 335 Å (\ion{Fe}{16} $\sim$2.5 MK) \citep{o'dwyer10,O'Dwyer12}. During the flare's peak, some AIA observations may be saturated, so we substitute SUVI observations, co-aligned and co-registered with AIA, for those specific frames. We bin AIA observations to the SUVI pixel size, ensuring consistency. Since the SUVI temperature response closely resembles that of AIA \citep{suvi}, we can utilize SUVI images for thermal energy estimates when necessary. In such cases, we also adjust the AIA temperature response functions to accommodate the binning of AIA data. Due to saturation, most of the XRT observations during the flare are not included in our analysis of this event.

For the M-class event, we estimate the thermal energy using AIA and XRT observations. Here, we bin the AIA observations to the XRT pixel size, co-align them, and calculate the DEMs. As previously described, we rescale the AIA temperature response functions to accommodate the binning of AIA data.

We employ the regularized inversion method \citep{hannah&kontar12} to calculate the DEMs, enabling us to derive the thermal energy estimates. We can calculate the EM and DEM weighted temperature using the methods discussed in chapter \ref{sec:c2_dem}. The temperature range of the integration are set to $5 < \log\,T < 7.4$. We calculate the emission measure and the DEM weighted temperature for all the pixels in the field of view (FOV). In Fig.~\ref{fig:flare}c \& d (\ref{fig:flare2}c \& d), we plot the DEM weighted temperature and emission measure in the temperature range 5.0$<$$\log\,T$$<$7.4, for the 2021 Oct 28 (2020 Nov 29) flare.

We use the emission measure and DEM weighted temperature estimated from the inverted DEM in the thermal energy expression of Equation \ref{eq:t_eneg_1} and sum over the pixels in the FOV to estimate the thermal energy arising from the FOV. This procedure gives us,
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
    U_{Th}~=~\sum_{j}~\frac{3k_{B}A\sqrt{LOS_{j}}}{\sqrt{EM^{c}_{j}}}\int_{T}~DEM_{c}(T)_{j}T~dT
    \label{eq:t_eneg}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
where $EM^{c}_{j}$ and $DEM_{c}(T)_{j}$ are the column emission measure and the column DEM in 5.0$<$$\log\,T$$<$7.4 for the j-th pixel in the FOV. We have used $n_{e}^{2}\times LOS~=EM_{c}$ and a filling factor $\textit{f}~=~1$. For the 2020 Nov 29 flare we mask the solar disk while calculating the DEMs and thermal energy. For our analysis, one of the major uncertainties in determining the emitting volume depends on determining the LOS for individual pixels in the FOV.

%%--------------------------
\begin{figure*}[ht!]
    %\hspace{-1cm}
    \includegraphics[width=0.9\textwidth,trim={2cm 5cm 3cm 3cm},clip]{oct28_align.pdf}
    \caption{Panel (a): the flare arcade in AIA 193 {\AA}. Panel (b): STIX soft X-ray contours (4 {--} 16 keV, solid pink lines) and hard X-ray contours (16 {--} 50 keV, solid blue lines) aligned to AIA 1600 {\AA} and over plotted. Panel (c): the emission measure map of the region for $5~<log(T)~<7.4$. Panel (d): the DEM weighted temperature map of the region.}
    \label{fig:flare}
\end{figure*}
%%--------------------------

%%--------------------------
\begin{figure*}[ht!]
\centering
    \includegraphics[trim={4.8cm 1.5cm 6cm 2.5cm},clip,width=0.9\textwidth]{nov_29_align.pdf}
    \caption{Panel (a): the flare arcade in AIA 131 {\AA}. Panel (b): {\it Hinode}/XRT Be-Med soft X-ray image recorded almost at the same time. Panel (c):  the DEM weighted temperature map of the region for $5~<log(T)~<7.4$. Panel (d): the emission measure map of the region for $5~<log(T)~<7.4$}
    \label{fig:flare2}
\end{figure*}
%%--------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Determining the LOS}\label{sec:los}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To determine the line of sight (LOS) along individual pixels in the field of view (FOV), we initially estimate the height of the flare loop using observations from different vantage points. STEREO-A/EUVI observed both events from a different angle compared to AIA, resulting in geometric effects on the observations.

Fig.\ref{fig:flare_orient}a & b illustrates the geometric effect of observing from different vantage points. The magenta cross in Fig.\ref{fig:flare_orient}a represents a point at the top of the flare arcade. The LOS extends into the page through that point from the STEREO-A vantage. The red line in Fig.\ref{fig:flare_orient}b shows the LOS through the point in Fig.\ref{fig:flare_orient}a projected to the SDO/AIA point of view. Similar projections are shown in Fig.~\ref{fig:flare_orient2} for the Nov 29, 2020 flare.

To calculate the height of the flare loop, we utilize co-temporal STEREO-A 171 {\AA}, 195 {\AA}, and AIA 171 {\AA}, 193 {\AA} images with \textit{scc\_measure.pro}, available in the \textit{sswidl}. This routine enables us to select a point on the observation from one vantage point, and the LOS through the same point is shown on the observation from the other vantage point. By identifying similar emission characteristics, we can determine the 3D coordinates of the point (heliographic latitude, longitude, and radial distance). This measurement is repeated at various positions along the loop top to calculate the change in loop height across the arcade. However, it is important to note that the height estimation using \textit{scc\_measure.pro} is limited by our ability to identify ``similar emission characteristics'' between the AIA and STEREO-A observations.

%%--------------
\begin{figure*}[ht!]
    \centering
    \includegraphics[width=\textwidth,trim={2cm 6cm 2cm 6cm},clip]{flare_orient.pdf}
    \caption{Panel (a): {\it STEREO-A}/EUVI 171 {\AA} observation of the flare arcade in the decay phase. The magenta cross marks a point on the top of the arcade. The LOS goes into the page through that point. Panel (b): SDO/AIA 171 {\AA} observation of the flare arcade. The red line marks the LOS through the arcade from the STEREO-A perspective projected to the AIA perspective.}
    \label{fig:flare_orient}
\end{figure*}
%%--------------

%%--------------
\begin{figure*}[ht!]
    \centering
    \includegraphics[width=0.9\textwidth,trim={4cm 5cm 3cm 5cm},clip]{nov29_triangulate.pdf}
    \caption{Panel (a): SDO/AIA 193 {\AA} observation of the Nov 29 flare in the decay phase. The blue cross marks a point on the top of the arcade. The LOS goes into the page from AIA perspective. Panel (b): {\it STEREO-A}/EUVI 195 {\AA} observation around same time. The blue solid line is the LOS from AIA perspective in panel (a) projected onto {\it STEREO-A} perspective. We can trace out the height of the flare arcade at various locations using \textit{scc\_measure.pro}. The height of the arcade at various points from the Sun's surface is marked in panel (a).}
    \label{fig:flare_orient2}
    \end{figure*}
%%--------------

%%--------------
\begin{figure*}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth,trim={3cm 2cm 3cm 0cm},clip]{flare_orient_pt2.pdf}
    \caption{Panel (a): Cartoon demonstrating the projection effects of a semicircular loop between STEREO-A and AIA vantages due to the difference between polar ($\theta$) and azimuthal ($\phi$) angles, respectively. Panel (b) : The calculated LOS map from the AIA perspective, with the estimated loop top height under the assumption of a semi-circular loop geometry.}
    \label{fig:flare_orient_2}
\end{figure*}
%%--------------

To determine the extent of the flare arcade, we select pixels within an emission measure contour of 5\% of the peak emission measure value. This contour is calculated based on the emission measure inferred from the DEM, which reflects the density of plasma across the temperature range of $5<\log,(T)<7.4$. This approach provides a more comprehensive estimate of the flare arcade compared to methods based solely on intensity observations, which may miss significant portions of the arcade due to the highly multi-thermal nature of the plasma. Outside of the flare arcade, we assume a line of sight (LOS) thickness of approximately 2 Mm, corresponding to the average thickness of the chromosphere.

Fig. \ref{fig:flare_orient_2}b illustrates an example of the calculated LOS in the field of view (FOV) for the October 28, 2021 flare. The highest point of the flare arcade follows the ridge from southeast to northwest. An estimate of the highest point of the loop is approximately 22 Mm, consistent with previous estimates of the ridge height around 20 Mm from magnetic loop modeling \citep{longcope22}. Using the LOS map shown in the bottom panel of Fig. \ref{fig:flare_orient_2}, we calculate the thermal energy in every pixel of the flare using Equation \ref{eq:t_eneg}. This process is repeated for the flare loops in the November 29, 2020 event.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Energy in the non-thermal electrons}\label{sec:non-therm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To estimate the energy deposited by the non-thermal electrons in the X-class event on October 28, 2021, we analyze the STIX spectra. Figure \ref{fig:stix_an}.a illustrates the STIX light curve for different energy bands: 4 to 6 keV (solid black line), 6 to 12 keV (solid magenta line), 12 to 25 keV (solid yellow line), and 25 to 50 keV (solid blue line). The attenuator was activated around 15:28 UT to prevent saturation, notably reducing the intensity. The hard X-ray peak appears around 25 to 50 keV at approximately 15:28 UT, while the soft X-ray peak is discernible within the attenuated flux in the 6 to 12 keV band at approximately 15:30 UT.

Following the methodology outlined in \cite{emslie12}, we fit the STIX spectra at various time intervals during the flare's evolution using the `2vth' and `thick2' functions available in the OSPEX X-ray spectra fitting package within `{\it sswidl}'. A representative fit is depicted in Figure \ref{fig:stix_an} panel (b) for the time bin around 15:26-15:27 UT using the `2vth' (solid yellow) and `thick2' (solid green) functions. The `2vth' function represents a two-component thermal model, with parameters for emission measure, temperature of the thermal components, and relative abundances of various elements with respect to CHIANTI coronal abundances \citep{chianti1,chianti}. On the other hand, the `thick2' function assumes a non-thermal component attributed to bremsstrahlung from energetic electrons, described by a broken power-law injected spectrum $F_{0}(E_{0})~(e^{-}s^{-1}cm^{-2}keV^{-1})$ :

%%--------
\begin{equation}
    F_{0}(E_{0})=A
    \begin{cases}
        0, & E_{0}<E_{min} \\
        E_{0}^{-\delta_{1}}, & E_{min} \le E_{0} < E_{b} \\
        E_{0}^{-\delta_{2}}E_{b}^{\delta_{2}-\delta_{1}}, & E_{b} \le E_{0} < E_{max} \\
        0, & E_{max} \le E_{0}
    \end{cases}
\end{equation}
%%--------

In the fitting process, the model spectrum parameters, such as the normalization parameter \( A \), the low- and high-energy cutoffs \( E_{\text{min}} \) and \( E_{\text{max}} \), the break energy \( E_{\text{b}} \), and the power law indices \( \delta_{1} \) and \( \delta_{2} \) below and above the break, are constrained. We set the high-energy cutoff at \( 3.2 \times 10^{4} \) keV for all fits, as it is significantly higher than the energy range of interest (around \( 10^{1} \) keV), making its effect on the X-ray spectra negligible \citep{emslie12}.

The fitting procedure in `\textit{OSPEX}' is a forward fitting process. The parameters of the `\textit{2vth}' and `\textit{thick2}' functions are adjusted to generate a photon spectrum, which is then convolved through the detector response matrix to produce a count rate spectrum. This count rate spectrum is compared with the measured count rate spectrum, and an iterative process minimizes the \( \chi^{2} \) between them to refine the parameter estimates.

Table \ref{tab1} presents the fitted temperature of the hotter thermal component at various phases of the flare. These temperatures align with the temperature range (\( \log(T_{\text{max}}) = 7.4 \) and \( \log(T_{\text{min}}) = 5 \)) used to calculate the emission measure (EM) and differential emission measure (DEM) weighted temperature, as discussed in Section \ref{sec:therm}.

%%%%%%%%%%%
\begin{table*}[ht!]
    \centering
    \begin{tabular}{|cl||c|c|}
    \hline
         &  & log(T) & EM \\ 
         & \hspace{-1cm}Time (UT) & of hotter component & ($cm^{-3}$) \\
    \hline
        Impulsive phase & \hspace{1cm}15:26 & 7.098 & $10^{48}$\\
        HXR peak & $\sim$ 15:27:20 - 15:28:20 & 7.19 & $3\times 10^{48}$\\
        Right after SXR peak & $\sim$ 15:35:39 - 15:36:34 & 6.88 & $4.1\times 10^{49}$\\
        Into the decay phase & \hspace{0.9cm}14:48:20 & 6.5 & $2\times 10^{49}$\\
        \hline
    \end{tabular}
    \caption{Fitted temperature of the hotter component of the thermal plasma during various stages of the flare.}
    \label{tab1}
\end{table*}
%%%%%%%%%%%

The non-thermal energy in the electrons (\( U_{e} \)) at any instant \( t = t' \) can be estimated by integrating the best-fit electron energy spectrum:
\[
U_{e}(t=t') = \Delta t \int_{E_{\text{min}}}^{E_{\text{max}}} F_{0}(E_{0})(t=t') dE_{0}
\]
where the electron energy distribution is constrained by fitting the count spectra for the time interval \( t' - \Delta t/2 \leq t \leq t' + \Delta t/2 \).

The cumulative energy deposited into the footpoint over time by the non-thermal electrons is a good indicator of the source of the thermal energy of the plasma. We can estimate the cumulative energy deposited by the non-thermal electrons up until a certain instant \( t \) by summing the energy deposited at the footpoints from every time bin:
\[
U^{cumulative}_{e}(t) = \sum_{t'=t_{0}}^{t} U_{e}(t')
\]

%%--------------
\begin{figure*}[ht!]
    \centering
    \includegraphics[trim={3cm 2cm 6cm 3.5cm},clip,width=0.54\textwidth]{oct28_lc_2.pdf} 
    \includegraphics[trim={3.5cm 8cm 3cm 2cm},clip,width=0.45\textwidth]{oct28_fit_2.pdf}
    \caption{Panel (a): STIX light curve of the 2021 Oct 28 X-class event in different energy bands as labelled. The black, magenta, yellow and blue solid lines show the light curve in 4{--}6~keV, 6{--}12~keV, 12{--}25~keV and 25{--}50 keV. Panel (b): STIX spectra fit at 15:27{--}15:28 UT, during impulsive phase. We fit the spectra with `\textit{thcik2}' (green solid line) and `\textit{2vth}' (yellow solid line). We show the complete fit function `\textit{2vth+thick2}' with the solid red line. The lower panel shows the normalized residuals of the fit.}
    \label{fig:stix_an}
    \end{figure*}
%%--------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}\label{res}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%###########%%
\begin{figure}[ht!]
    \centering
    \includegraphics[trim={4cm 1cm 4cm 1cm},clip,width=0.8\textwidth]{flare_eneg.pdf}
    \caption{Panel (a): The calculated thermal energy as a function of time for the 2021 Oct 28 flare. The magenta dot-dashed line shows the thermal energy calculated from the GOES light-curve using the effective volume and a filling factor \textit{f}~=~1. The red dot-dashed line and the black dashed line shows the energy calculated from the GOES light-curve and the effective volume with filling factor \textit{f}~=~0.4 and \textit{f}~=~0.2, respectively. The blue solid line shows the thermal energy estimated using the DEMs calculated from the AIA obeservations. The black solid line shows the thermal energy calculated from the GOES light curve, but the volume inferred from the area of the of the flaring arcade with STIX SXR images, under the assumption that $V\sim A^{\frac{3}{2}}$. Panel (b): The calculated thermal energy as a function of time for the 2020 Nov 29 flare. The red line shows the thermal energy calculated from the GOES light curves, using a constant effective volume. The blue curve shows the thermal energy calculated from the DEMs inferred from the imaging and a varying volume from the imaging.}
    \label{fig:eneg}
\end{figure}
%%###########%%

%%###########%%
\begin{figure}[ht!]
    \centering
    \includegraphics[trim={2cm 0cm 1cm 0cm},clip,width=0.8\textwidth]{fan_eneg.pdf}
    \caption{Calculated thermal energy for the 2020 Nov 29 flare. Total thermal energy of the flare (blue dot-dashed) in comparison to the thermal energy from the fan (red dashed). The magenta and the green solid line show the fit to the thermal energy output to the fan and the loop's thermal output. Fermi hard X-ray count (black) peaks around the same time as the total thermal output.}
    \label{fig:fan_eneg}
    \end{figure}
%%###########%%

Figure~\ref{fig:eneg}.a shows the thermal and non-thermal energy calculated for the 2021 October 28 event. The black solid curve with crosses shows the thermal energy calculated from the DEMs. The red solid curve shows the thermal energy calculated from the {\it GOES} light curve and the effective volume calculated assuming an RTV loop \citep{rtv78,serio91}. We use the {\it GOES} emission measure, temperature with a volume filling factor \textit{f}~=~1, to estimate an effective loop length for the flare and from that, calculate an effective volume. Note that the implicit assumption of mechanical equilibrium only holds during the decay phase of the flare. So, the effective volume estimated here would only be appropriate in the decay phase. The green solid curve with triangles and the blue solid curve with squares show the same {\it GOES} thermal energy, with volume filling factor \textit{f}~=~0.4 and \textit{f}~=~0.2, respectively. The blue dashed curve shows the thermal energy calculated from the {\it GOES} light curve, but the volume inferred from the area of the flaring region from the STIX soft X-ray contours, under the assumption that $V\sim A^{\frac{3}{2}}$.

The lime green solid line with circles in Fig.~\ref{fig:eneg}.a, shows the cumulative energy in the non-thermal electrons. This quantity is the amount of energy deposited at the flare foot points, and one of the sources of the thermal energy of the flare. The cumulative non-thermal energy of electrons $\simeq~1.2\times 10^{31}$ erg $>$ peak thermal energy calculated from the DEM estimates $\simeq~5\times 10^{30}$ erg. This is usual for an X-class flare. The differences in the estimates of thermal energy, due to different estimations of volume, also affects the partition between the thermal and non-thermal energies of flares. The efficiency of converting the energy deposited by non-thermal electrons into the thermal energy of the ambient plasma results in this partition and as a result, the volume estimation is a key parameter in understanding the conversion of non-thermal energy into thermal energy in flares.

The interesting trend in Fig.~\ref{fig:eneg}.a is that the thermal energy calculated from the constrained DEMs (solid black curve with crosses) is closer to a volume filling factor \textit{f}~=~0.2 in the impulsive phase, but is asymptotic with a filling factor \textit{f}~=~1 (solid red curve) during the decay phase. This indicates that the flare loops during the impulsive phase do not fill up apparent volumes similar to those in the decay phase. The change in the effective filling factor is indicative of the sharp change in the volume during the impulsive phase.

For the 2020 November 29 event, the {\it STEREO-A} perspective looks down into the supra-arcade plasma sheet. Thus the LOS of this feature can not be calculated as demonstrated in Section \ref{sec:los} for the supra-arcade pixels. For the supra-arcade fan pixels in the FOV, we assume a LOS $\simeq~8~\textrm{Mm}$, as suggested in several other studies \citep[see e.g.,][]{savage10,seaton17,li18}. We use these calculated LOS maps, along with equation~\ref{eq:t_eneg_1} to estimate the thermal energy as a function of time.

Figure \ref{fig:eneg}.b shows the energy calculated for the November 29th event. The blue solid curve shows the thermal energy calculated from the DEMs. The red solid curve shows the thermal energy calculated from the GOES light curves and the constant effective volume calculated assuming an RTV loop with a volume filling factor \textit{f}~=~1. The thermal energy shows similar characteristics as the October 28th, 2021 event. The RTV loop effective volume clearly is an overestimation in the rise phase of the the flare, and agrees very well in the decay phase.

There have been several studies that suggest that the plasma in the fan is directly heated \citep{hanneman14,chen17,reeves17,warren18,cai22,xie23}. Unlike the flare arcade, the thermal output of the fan is not directly related to the energy deposited by the non-thermal electrons and ions at the foot point. Hence, this different mechanism should also be reflected in the time evolution of the thermal output of the fan, compared to the thermal output of the loops. Under the assumption of the LOS~$\mathrm{\sim 8~Mm}$ in the fan region, we separately calculate the contribution from the fan to the total thermal energy for the 2020 Nov 29 event.

Figure~\ref{fig:fan_eneg} shows the thermal energy of the fan as a function of time (red dashed line) in comparison to the total thermal energy of the 2020 Nov 29 event (blue dot-dashed line). The thermal energy form the fan is $\sim$ two orders of magnitude lower than the total thermal energy of the event. The thermal energy of the fan also peaks much later ($\sim$ 20 minutes) compared to the total thermal energy. After the thermal energy of the fan peaks, the thermal energy of the fan (red + sign) and the total thermal energy of the event (blue crosses) are fitted with a power law of the form $at^{-\delta}$ as a function of time. The fits are shown with magenta and green solid line for the fan and the total thermal energy, respectively. The value of the power law index are -0.95 and -1.1, respectively, for the fan and the total thermal output. The plots shows that the thermal energy of the fan decay slower compared to the total thermal output. The normalized {\it Fermi} GBM 25 {--} 80 keV count rate (black solid line) peaks at a similar time as the total thermal energy of the event.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Outlook}\label{sec:out}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have used AIA, SUVI, and XRT observations to calculate DEM maps and estimate the thermal energy for two solar flares as a function of time. We have used observations from AIA and {\it STEREO-A} to calculate the geometry of the flare loops and estimate the LOS for the AIA observations. We have shown that the accurate estimation of volume can have significant implications for thermal energy estimates. For the 2020 November 20 flare, we have also estimated the thermal energy for the fan and compared the evolution of the thermal energy of the fan with respect to the total thermal energy of the event. We have shown that the thermal energy of the fan decays slower compared to the total thermal energy of the event. This result suggests that a fundamentally different heating mechanism is responsible for the thermal output of the fan.

The thermal energy of the flares is given as, $U_{Th}\simeq 3n_{e}k_{B}TVf$. The electron number density is given by, $n_{e}~=~\sqrt{\sfrac{EM^{v}}{Vf}}~\implies~U_{Th}~=~3k_{B}T\sqrt{EM^{v}\times~Vf}$, where $EM^{v}$ is the volume emission measure (in units of $cm^{-3}$). A filling factor, \textit{f} $<$ 1 decreases the thermal energy by $\sim f^{\sfrac{1}{2}}$. There are very diverse results reported on \textit{f}. X-ray observations have generally constrained within $0.1<\textit{f}<1$\citep{jak11,guo12}, while it is usually constrained to much lower values $0.001<\textit{f}<0.1$ in EUV\citep{ash&ash08}. The filling factor can also be constrained by imposing the requirement that the flare plasma has to be contained via magnetic pressure. From this constraint it can be inferred that the required coronal magnetic field strength $B_{cor}$ $\sim f^{-\sfrac{1}{4}}$\citep{caspi14,warmuth16a,warmuth16b}. These studies rule out values of $\textit{f}<0.1$. Similar results were obtained from spectroscopic observations of density sensitive \ion{Fe}{11} lines \citep{miligan12}.

It is easy to infer from our findings that a single value of volume filling factor is inadequate to describe the evolution of thermal energy throughout the duration of the flare. We need to estimate the volume as a function of time rather than depending on a filling factor. In Fig.~\ref{fig:eneg}.a, the thermal energy calculated from {\it GOES} with various filling factors demonstrates this concept perfectly. During the impulsive phase, the thermal energy calculated from the DEMs is consistent with \textit{f}=0.2, and later in the decay phase, it is consistent with \textit{f}=1. This result demonstrates how the volume of the flare arcade is changing over time with respect to the volume in the decay phase. The thermal energy calculated from $V\sim A^{\frac{3}{2}}$ assumption agrees well with the thermal energy calculated from constrained DEMs in the decay phase. But it still predicts higher energy in the impulsive phase. This discrepancy might signify that the assumption of self-similar expansion might not be valid at the initial sharp rise in the impulsive phase for some flares.

Our results are in line with the findings of \cite{hilarie05}. They demonstrated from {\it RHESSI} imaging for a sample of 9 M and C class flares that the volume estimation with the assumption of self-similar expansion resulted in thermal energy higher than the non-thermal energy during the impulsive phase (For more details, refer to \cite{hilarie05} Table 5 and the corresponding discussion). A statistically inferred representative filling factor might serve perfectly well for estimating the energies near the thermal peak for a sample of flares. Since we are trying to quantify the evolution of the energy over time for individual flares, we require more accurate estimates of the volume.

Our results also demonstrate the utility of estimating the volume from different vantages as a function of time. For events like the X-class event on 2021 October 28, the on-disk imaging allows the estimation of the volume from the flare ribbon area under the assumption of self-similar expansion. But for scenarios like the limb event 2020 November 29, where the flare ribbons are not visible from any imaging observation, or the visible foot point and/or visible portions of the loop are projected at a very high angle, estimating the volume of the loop by calculating the height of the loop at various points serves as an important tool in estimating the thermal energy at various phases of the flare.

In Figure~\ref{fig:fan_eneg}, the thermal energy from the fan (red dashed line ) is $\sim$ two orders of magnitude lower than the total thermal energy of the event (blue dot-dashed line). The thermal energy also peaks much later ($\sim$ 20 minutes) compared to the total thermal energy. This result shows that the fan plasma is being heated directly by a process different from the flare arcade (e.g. SADs \citep{reeves17}, plasma flow turbulence \citep{xie23}). The fan also cools slower than the arcade, which indicates that either continuous heating is present in the fan during the decay phase of the flare or there is suppression of cooling \citep[e.g.][]{xie23}. The event had both foot points occulted from the Earth's perspective, so it is a fair assumption that most of the hard X-ray is from the loop top coronal source. This circumstance explains the near-simultaneous peak in {\it Fermi} hard X-ray (black solid line) and the thermal energy peak from the flare.

Our results exhibit the importance of different solar missions that can observe the Sun with higher spatial resolution (to resolve the finer structures better) and from various vantages (to triangulate the geometry). The ability to spatially resolve the temperature structure of the flaring plasma not only gives us a better estimation of the thermal energy, but it also allows us to spatially separate various portions of the flaring plasma (e.g. for the 2020 November 29 event, we could separate the contribution of the fan from the total thermal energy). This separation enabled us to demonstrate that a different heating mechanism was at play in the fan. However, we do note that the reliability of any such estimations needs to be rigorously tested with observations of various flares from various geometric projections.

### 2024-05-06 introduction/intro.tex
Updates from Overleaf

@@
 
-In the innermost zone of the star the Sun has a temperature of about 15 MK and a density of $1.6~\times~10^{5}~km.m^{-3}$ that fuses Hydrogen into Helium mainly by p-p cycle and to some extent by CNO cycle \sr{Ref here}.
+In the innermost zone of the star the Sun has a temperature of about 15 MK and a density of $1.6~\times~10^{5}~km.m^{-3}$ that fuses Hydrogen into Helium mainly by p-p cycle \citep{bethe38} and to some extent by CNO cycle \citep{bethe39}.
 
@@
 Fig.~\ref{fig_solar_int} shows a schematic diagram of various layers of the Sun.
-Beyond the core we have the optically thick radiative zone, where the Hydrogen and Helium are completely ionized \sr{Ref.
-here}.
+Beyond the core we have the optically thick radiative zone, where the Hydrogen and Helium are completely ionized.
 The high energy $\gamma$-ray photons generated in the core, have very small mean free path in this region, as they collide numerous times eventually thermalizing becoming visible photon.
@@
 This is the convective zone where the energy from the inner layers of the Sun is transported adiabetically to the surface of the Sun.
-In between the radiative and the convective zone, there is a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine, which is believed to play a major role in generating Sun's magnetic field via the Dynamo process \sr{Ref.
-here}.
+In between the radiative and the convective zone, there is a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine, which is believed to play a major role in generating Sun's magnetic field via the Dynamo process \citep{corbard01}.
 
@@
 This layer is 400-600 km deep and has an effective temperature of 5780 K.
-The magnetic filed lines arising from the tacholine penetrate the Photosphere and creates a `carpet' over the whole region \sr{(Priest 2014) ref here}.
-As mentioned earlier, this is the Solar surface known as the `Quite Sun'(QS from hereon).
+The magnetic filed lines arising from the tacholine penetrate the Photosphere and creates a `carpet' over the whole region \citep{priest14}.
+As mentioned earlier, this is the Solar surface known as the `Quite Sun'(QS).
 This region exhibits an average magnetic flux density of \textbf{10 -- 50~G}.
@@
 So, we have to define the thermodynamic quantities of the Photosphere in Local Thermal Equilibrium (LTE from hereon).
-As we move away from the Photosphere, because the density keeps on decreasing steadily, the LTE conditions also start deviating similarly \sr{Ref here}.
+As we move away from the Photosphere, because the density keeps on decreasing steadily, the LTE conditions also start deviating similarly \citep{philips08}.
 
@@
 \ref{fig_solar_atm}, the temperature of the Chromosphere saturates before the dramatic rise in the transition region.
-This saturation is attributed to a steady deposition of acoustic energy by creation of shock waves \sr{Ref.
-here}.
+This saturation is attributed to a steady deposition of acoustic energy by creation of shock waves \citep{carlsson07}.
 The Chromosphere also exhibits a sharp gradient in the plasma $\beta$ factor, non-LTE conditions, dominance of wave motions \sr{Ref.
@@
     \includegraphics[width=0.5\linewidth]{Figures/phu_63_8_818_f2.jpg}
-    \caption{A schematic diagram of the standard model of solar flare.}
+    \caption{A schematic diagram of the standard model of solar flare (adapted from \cite{lysenko20}).}
 \end{figure}
@@
 However the simple question, whether the non-thermal component of the flares have enough enrgy is still not resolved as even the most recent studies contradict each other in the most puzzling fashion.
-Here I will discuss the contradictions arising from some of the studies\citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17}.
+\cite{warmuth20} discussed the contradictions arising from some of the studies\citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17}.
 The details of the studies can be summarized as follows:
@@
        Study & No. of flares & GOES class range & Thermal model & Thermal spectrum & Thermal volume & Thermal losses \\
-       \cite{stosire07} & 18 & A3-B7 & Isotherm. & RHESSI & TRACE & X \\
-       \cite{emslie12} & 38 & C5-X28 & Isotherm. & RHESSI & RHESSI & Rad. \\
-       \cite{inglis14} & 10 & B3-B9 & Multitherm. & RHESSI+AIA & RHESSI & Rad. \\
-       \cite{warmuth16a,warmuth16b} & 24 & C3-X17 & Isotherm. & RHESSI+GOES & RHESSI & Rad.,Cond. \\
-       \cite{ash17} & 188 & M1-X7 & Multitherm. & AIA & AIA & Rad. \\
+       \cite{stosire07} (S07 from hereon) & 18 & A3-B7 & Isotherm. & RHESSI & TRACE & X \\
+       \cite{emslie12} (E12 from hereon) & 38 & C5-X28 & Isotherm. & RHESSI & RHESSI & Rad. \\
+       \cite{inglis14} (IC14 from hereon) & 10 & B3-B9 & Multitherm. & RHESSI+AIA & RHESSI & Rad. \\
+       \cite{warmuth16a,warmuth16b} (WM16 from here on) & 24 & C3-X17 & Isotherm. & RHESSI+GOES & RHESSI & Rad.,Cond. \\
+       \cite{ash17} (A17 from here on) & 188 & M1-X7 & Multitherm. & AIA & AIA & Rad. \\
        \hline
@@
 
+The bolometric energy serves as a representation of the overall energy released during solar flares.
+Regardless of how energy is released in a solar flare, whether through direct plasma heating, rapid bulk flows, or nonthermal particle processes—the ultimate outcome is thermalization and subsequent radiation across the electromagnetic spectrum.
+Given that bolometric energy encompasses the entire spectrum, it is anticipated to reflect the total energy originally released.
+It's important to note that this specifically pertains to the energy liberated within the flare and does not encompass the energy associated with a concurrent coronal mass ejection (CME) or filament eruption.
+So, \cite{warmuth20} used the bolometric energy released in solar flares, to compare various studies on equal footing.
+Here we will discuss some of the main issues \cite{warmuth20} identifies comparing these studies.
+
+The calculated thermal energy of all studies show an excellent correlation with the {\it GOES} class.
+Fig.~\ref{fig:goes-therm} left panel shows the peak thermal energy as a function of peak {\it GOES} flux for all the flares from the five studies.
+EM12 and WM16 are consistently one order of magnitude lower than the bolometric energy.
+Interpolation of E12 and WM16 are about half an order of magnitude lower compared to IC14, while S07 is very consistent with the extrapolation.
+The energies of A17 is about an order of magnitude higher compared to other studies, and even higher than the extrapolated bolometric energy for flares of same class from \cite{kretzschmar11} and E12.
+There can be several reason of these differences between the studies arising.
+
+A possible reason can be attributed to different thermal models used to model the thermal component of the flares.
+{\it RHESSI} usually yields a higher temperature and lower emission measure compared to {\it GOES} due to the highly multi thermal nature of the flaring plasma \citep{bataglia05,ryan14,warmuth16a}.
+Although the {\it GOES} temperature is higher by a factor of 1.4, it is not dependant on the flare class.
+Along with that, \cite{warmuth20} also investigated whether assuming a isothermal or multithermal model introduces any differences in the thermal energy estimates.
+They reported no significant differences due to differences of models (refer to Fig.
+2 and the corresponding discussion in \cite{warmuth20}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.45\textwidth,trim={0cm 0cm 0cm 0.02cm},clip]{goes_flux_therm.jpg}
+    \includegraphics[width=0.45\textwidth,trim={0cm 0cm 0cm 0.02cm},clip]{goes_flux_vol.jpg}
+    \caption{{\it GOES} peak thermal energy (left panel) and volume of the thermal plasma (right panel) as a function of the peak {\it GOES} flux for all the flares from five studies (figure credit: \cite{warmuth20}).
+The C values show the linear correlation coefficient for various studies.}
+    \label{fig:goes-therm}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The thermal energy estimated usually depends on the source volume, $U_{Th}\sim V$.
+Apart from S07 and A17, all other studies used {\it RHESSI} imaging to estimate the flare volume with a filling factor $f=1$.
+S07 determined the volume by employing a semicircular loop model, utilizing the cross-sectional area and loop length derived from the observed areas and separations of foot point brightening of 1600 {\AA} by {\it TRACE}.
+In contrast, A17 estimated the volume based on the flare area exceeding a certain threshold in the emission measure obtained from the spatial synthesis DEM method.
+Fig.~\ref{fig:goes-therm} right panel shows the volumes used for various studies to estimate the thermal energy as a function of the peak {\it GOES} flux.
+It is worth noting that the volume estimates from E12 and WM16 align closely, as do those from A+17, despite employing entirely different methodologies.
+In contrast, the micro flare volumes reported by IC14 are notably larger, ranging from one to two orders of magnitude beyond what would be anticipated based on the findings of the other four studies.
+Intriguingly, this discrepancy aligns with the additional volume required to account for the higher thermal energies observed in IC14.
+The uncertainty in detecting volume can be due to the CLEAN algorithm systematically overestimates the source size \citep{warmuth13a}.
+There has also been studies demonstrating that {\it RHESSI} has difficulties in resolving small sources \citep{dennis09,warmuth13b}, that would be applicable for small thermal sources in the micro flares.
+This illustrates the requirement for better volume estimation for better estimates of the thermal energy of flares.
+
+We can conclude a few more puzzling questions from these studies as a whole:
+
+%%%%%%%%%
+\begin{itemize}
+    \item The primary challenge in estimating the thermal energy of the hot plasma stems from determining the distribution of the Differential Emission Measure (DEM), and the radiating plasma volume.
+    \item The dissipation of energy from the hot plasma is substantial.
+Although there is widespread agreement regarding radiative losses across studies, the extent of conductive losses disagree significantly between the studies.
+    \item The non-thermal energy in injected electrons is strongly dependent on the poorly constrained low-energy cutoff.
+    \item The thermal and non-thermal energy partition changes with flare class.
+In smaller flares, there appears to be a deficiency of energetic electrons, whereas in larger flares, the injected non-thermal energy seems to sufficient in powering the thermal component.
+Does this signify the existance of an additional third heating source?
+\end{itemize}
+%%%%%%%%%
+
 %% ################################################################# %%
@@
 
+The main motivation of this thesis is to add understanding of effects of flares on the surrounding environment in lower and upper solar atmosphere, to answer some of the questions posed above.
+We have used imaging and spectroscopic observations from multiple space based observatories ({\it e.g.} AIA, HMI, IRIS, XRT, etc.).
+This research contributes to creating a perspective of flare energetics and its effect on the surrounding plasma environment from Chromosphere to Corona.
+
+The solar flares are the strongest magnetic event in our solar system connecting various layers of the solar atmosphere ({\it e.g.} from Photosphere to Corona), coupled via mass and energy transport.
+While the Coronal manifestation of solar flares have been studied extensively with several instruments, there are only a few imaging and spectroscopic instruments observing the Photosphere to transition region.
+These include the {\it IRIS} \citep{iris}, AIA 1600, 1700, and 304 {\AA} \citep{aia} and some the filters of {\it Hinode}/SOT \citep{sot}.
+In addition to these, we also have had balloon experiment {\it SUNRISE} \citep{sunrise1,sunrise2}, which provided high resolution imaging of the transition regiopn, from the SuFI instrument \citep{sufi}.
+
+This illustrates the necessity of more observatories operating at the transition region wavelengths for more comprehensive understanding about how the solar flares manifest and affect the dynamics and heating of the lower solar atmosphere.
+In this regard, {\suit} onboard Aditya-L1 will play a crucial role in probing the lower solar atmosphere.
+The various imaging channels of {\suit} would observe the manifestation of flares in transition region at various heights (NB3 $\implies$ \ion{Mg}{2} k 279.6 nm, NB4 $\implies$ \ion{Mg}{2} h 280.3 nm, NB8 $\implies$ \ion{Ca}{2} h 396.8 nm), further lower in the transition region (NB2 $\implies$ blue wing of Mg window, NB5 $\implies$ red wing of Mg window) and Sunspots and possible signature of umbral brightening due to flares at the Photosphere (NB6 300 nm and NB7 388 nm) in full disk.
+This would also allow us to probe the interaction of the flaring region, with other active regions on disk, giving us a comprehensive overview of the effect of solar flares and their manifestation in the lower solat atmosphere.
+
 %% ################################################################# %%
@@
 %% ################################################################# %%
+
+The work within this thesis spans across various layers of the solar atmosphere to understand how solar flare couples these layers.
+It is carried out partly, as various preparatory analysis for {\suit}, forward modelling {\suit} observations, designing the stellar calibration scheme for {\suit}, analysis of existing transition region observations in anticipation of {\suit} observations, analysis of coronal observations of solar flares, and analysis of first solar flare observations by {\suit}.
+Here we will briefly discuss the structure of the rest of the thesis:
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{itemize}
+    \item In chapter \ref{c:chap2}, we review various space based missions available and used in this thesis.
+We also discuss various analysis techniques used in this thesis.
+We also motivate the importance of {\suit} and its main science goals.
+We also briefly discuss the specific questions regarding solar flares we can address with {\suit}.
+    \item In chapter \ref{c:chap3}, we discussed some of the initial preparatory analysis we did for {\suit}, including the throughput model for {\suit}, how the filters mounted on {\suit} were chosen, the analysis of spacecraft jitter simulation and what effect it would have on the imaging.
+    \item In chapter \ref{c:chap4}, we discuss the forward modelling pipeline developed for {\suit}.
+We use MPS-Atlas simulation and {\it IRIS} observations, with measured transmission profiles of various optical components and the PSF to forward model {\suit} observations.
+We also discuss a preliminary version of the deconvolution algorithm that will be deployed in the data reduction pipeline.
+    \item In chapter \ref{c:chap5}, we describe the stellar calibration scheme and the selection criteria for the standard star target.
+We also use a sun as a star spectra to evaluate the calibration scheme.
+    \item In chapter \ref{c:chap6}, we use existing {\it IRIS} observations of three solar flares to probe how the lower solar atmosphere is affected by the flares.
+The ratio of the \ion{Mg}{2} k and h lines, is a proxy for the optical depth of the surrounding plasma.
+Hence, we use the observations of \ion{Mg}{2} lines along HMI magentic field measurements to investigate the effects of magnetic field, if any.
+\cite{kerr15} conducted a similar study and found signatures of localised heating in the line intensity ratio.
+We found, that the line intensity ratio shows a correlated increase and decrease with the flare light curve.
+We argue this to be signature of plasma flow associated with flare, and a change in density of the local environment.
+This acts as a prelude of what is achievable with {\suit}.
+We can use a similar method to give full disk context of optical depth, with respect to eruptive events.
+\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-05-06 main_thesis_file.tex
local change
Updates from Overleaf

@@
 %
-\chapter{Existing Solar Observations and techniques}\label{c:chap2}
-\chaptermark{Solar Observatories}
+\chapter{Existing Solar Observations and Techniques: A bridge towards Solar Ultraviolet Imaging Telescope}\label{c:chap2}
+\chaptermark{Solar Observatories and Analysis Techniques}
 \input{./chapter2/ms.tex}
@@
 \chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap6}
-\chaptermark{Solar Flare Energetics}
+\chaptermark{Solar flares Mg II}
 \begin{quote}
-{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
-{authors,
-{\em journal reference info}}
+{ ~~~~~~~This thesis chapter originally appeared in the literature as} \\
+{{\em The Evolution of the Ratio of \ion{Mg}{2} Intensities During Solar Flares, Roy, S., \& Tripathi, D.
+2024, ApJ, 964, 106, doi:\href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}}.}
 \end{quote}
@@
 %
-\chapter{Estimating thermal and non-thermal energy partition of Solar Flares}\label{c:chap7}
+\chapter{Estimating thermal energy of two Solar Flares}\label{c:chap7}
 \chaptermark{Solar flare energy}
@@
 %
-\chapter{First X-class flare observed from SUIT}\label{c:chap8}
+\chapter{First flares observed from {\suit}}\label{c:chap8}
 \chaptermark{Solar flare energy}

### 2024-05-07 introduction/intro.tex
Updates from Overleaf

@@
 The figure also shows some of the most prominent magnetic structures on the Sun e.g sunspot, prominence, coronal hole.
-Credit : NASA/Goddard.
-\sr{Better pic here.}}
+Credit : NASA/Goddard.}
     \label{fig_solar_int}
@@
     \includegraphics[width = 0.8\linewidth]{Figures/solar_atm.png}
-    \caption{The variation of electron temperature (solid line) and electron density (Ne, dashed line) and density of neutral hydrogen atoms (NH, dotted- dashed line) in the solar atmosphere as derived based on the 1-D model calcula- tions by \sr{Ref.
+    \caption{The variation of electron temperature (solid line) and electron density ($\mamthrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dotted- dashed line) in the solar atmosphere as derived based on the 1-D model calcula- tions by \sr{Ref.
 here}.}

### 2024-07-22 abstract.tex
Updates from Overleaf

\justifying

\abstract{
Solar flares are the largest magnetic eruptions in the Solar system. The enigmatic magnetic eruptions have been studied for over a century. The effects of flare in the lower solar Atmosphere {\it e.g.} Chromosphere and Photosphere are also very ill-understood. There is also a lack of full-disk resolved observation in continuum channels in the NUV regime. In addition to this, instead of the availability of plethora of solar observations, we still hardly understand various aspects of the flares. Various statistical studies exhibit our lack of understanding between the partition of thermal and non-thermal energy, the conversion mechanism. The {\suit} on-board Aditya-L1 by the Indian Space Research Organisation (ISRO), aims to fill the gap of full disk observation in the NUV regime, specifically in 200 {--} 400 nm.

In this thesis we first describe the initial preparatory analysis carried out for {\suit}, including the throughput model, jitter estimation and its effect on imaging, the on ground spectral and photometric validation and the stellar calibration plan. We also use EUV, NUV, Soft and Hard X-ray spectroscopy and Full-disk integrated imaging to understand: (\romannum{1}) The effect of Solar flares on the surrounding plasma environment in Chromosphere, (\romannum{2}) The effect of volume estimation on the thermal energy budget of the Solar flare and the efficiency of the conversion from non-thermal to thermal energy. We propose a triangulation method using existing tools and observations from different vantages to estimate the volume of the arcade as a function of time. We also report the first flare observations from {\suit} and its implications on our understanding of flares moving forward.

}

### 2024-07-22 chapter2/ms.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\justifying
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Solar Dynamic Observatory}
+\section{Solar Dynamics Observatory}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The Solar Dynamics Observatory \citep[SDO;][]{sdo} is a NASA mission designed to understand the causes of solar variability at various spatiotemporal and wavelength scales, as well as its impacts on Earth and the near-Earth environment.
+The Solar Dynamics Observatory \citep[SDO;][]{sdo} is a NASA mission designed to understand the causes of solar variability at various spatio temporal and wavelength scales, as well as its impacts on Earth and the near-Earth environment.
 It is part of NASA’s Living With a Star program and houses multiple instruments onboard to address its numerous scientific goals.
@@
 It incorporates several filters at 94 {\AA}, 131 {\AA}, 171 {\AA}, 193 {\AA}, 211 {\AA} and 335 {\AA}, mainly probing the Corona, along with filters at 304 {\AA}, 1600 {\AA}, 1700 {\AA}, and 4500 {\AA}, mainly observing the Chromosphere and Photosphere, providing a total temperature coverage range of 0.06 MK to 20 MK and across various heights.
-Figure 2.1 illustrates the temperature responses of these filters (Boerner et al., 2012), derived based on the CHIANTI model for solar emissivity (Dere et al., 1997, 2009).
+Figure 2.1 illustrates the temperature responses of these filters \citep{borner12}, derived based on the CHIANTI model for solar emissivity \citep{chianti,chianti1}.
 Under different conditions, these AIA filters observe different plasma phenomena \citep{o'dwyer10}.
@@
 IRIS contains a spectrograph and a slit-jaw imager (SJI), observing the chromosphere, the transition region, and the lower corona.
-It primarily observes the Sun in two passbands around 1400 {\AA} and 2800 {\AA}.
+It primarily observes the Sun in two pass bands around 1400 {\AA} and 2800 {\AA}.
 IRIS provides data at high spatial resolution (0.33 {\arcsec} in FUV and 0.4 {\arcsec} in NUV), high time cadence (up to 1 second), and high spectral resolution (12 or 25 m{\AA} per pixel).
@@
 STIX can capture X-ray data with high temporal resolution, allowing scientists to study the rapid evolution of solar flares and other transient events in detail.
-STIX works synergistically with other instruments onboard Solar Orbiter, providing complementary measurements to enhance our understanding of the Sun's dynamic behaviour across different wavelengths and energy ranges.
+STIX works together with other instruments onboard Solar Orbiter, providing complementary measurements to enhance our understanding of the Sun's dynamic behaviour across different wavelengths and energy ranges.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Solar Ultraviolet Imaging Telescope}
+\section{The Solar Ultraviolet Imaging Telescope}\label{sec:suit}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \item spectral energy distribution of solar flares in NUV
-    \item dynamics of chromospheric eruptive phenomena at various spatiotemporal scales
-    \item Initiation of Coronal Mass Ejections(CMEs) and space weather: the kinematics of erupting prominences during the early phase.
+    \item dynamics of chromospheric eruptive phenomena at various spatio temporal scales
+    \item Initiation of Coronal Mass Ejections(CMEs) and space weather: the kinematics of erupting prominence during the early phase.
 \end{itemize}
@@
 The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1} of the Indian Space Research Organization (ISRO).
-With its 11 science filters (3 broadband and eight narrowband), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another.
+With its 11 science filters (3 broadband and eight narrow band), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another.
 SUIT will provide full disk as well as partial disk images of the Sun with a pixel size of 0.7".
@@
 The question remains whether WLFs are photospheric phenomena due to $H^{-}$ free-free emission or chromospheric phenomena due to H free-bound emission.
-The more recent studies further constrain the origin of the WLFs to be Chromospheric phenomena, as it has been shown that the WL and HXR footpoint centroids are cospatial.
-Similarly, \cite{krucker15} constrained the cospatial WL and HXR footpoints within the chromosphere for three flares.
-With the help of SUIT, we would be able to localize the WL flares and resolve them on various parts of the Solar disk, which along with observations from Interface Region Imaging Telescope (IRIS), Helioseismic and Magnetic Imager (HMI), would help us localize the source of the WL footpoints and also comment on the formation mechanism of the WL itself.
+The more recent studies further constrain the origin of the WLFs to be Chromospheric phenomena, as it has been shown that the WL and HXR foot point centroids are cospatial.
+Similarly, \cite{krucker15} constrained the cospatial WL and HXR foot points within the chromosphere for three flares.
+With the help of SUIT, we would be able to localize the WL flares and resolve them on various parts of the Solar disk, which along with observations from Interface Region Imaging Telescope (IRIS), Helioseismic and Magnetic Imager (HMI), would help us localize the source of the WL foot points and also comment on the formation mechanism of the WL itself.
 
@@
 A complete understanding of this will help us decode the physical processes involved in solar flares and help quantify their effects on solar spectral irradiance.
-Ideally, it would be essential to observe flares at all wavelengths simultaneously with sufficient spatiotemporal resolution to figure out the spectral energy distribution of flares.
+Ideally, it would be essential to observe flares at all wavelengths simultaneously with sufficient spatio temporal resolution to figure out the spectral energy distribution of flares.
 Unfortunately, this is generally not the case, and we have to rely on the sporadic observations made using ground-based instruments in the visible domain.
@@
 \cite{kretzschmar10,kretzschmar11} performed statistical studies using a large number of flare observations across a wide energy range.
-For this purpose, they used the full Sun observations of Solar flux from Solar and Heliospheric Observatory (SoHO), three visible Solar irradiances from VIRGO/Solar Photometer (SPM) passbands centred on 402 nm, 500 nm, and 862 nm, respectively, from 1996 to 2008.
+For this purpose, they used the full Sun observations of Solar flux from Solar and Heliospheric Observatory (SoHO), three visible Solar irradiances from VIRGO/Solar Photometer (SPM) pass bands centred on 402 nm, 500 nm, and 862 nm, respectively, from 1996 to 2008.
 Additionally, they also use the EUV irradiance in the ranges 0.1-50 nm and 26-34 nm measured by SOHO/Solar EUV Monitor \citep{judge98} and SXR measurements from GOES satellites.
@@
     \centering
-    \includegraphics[width = \linewidth]{Figures/nphys1741_page-0002.jpg}
+    \includegraphics[width = \linewidth]{Figures/nphys1741_page-0002.webp}
     \caption{Averaged TSI variations during flares.

### 2024-07-22 chapter3/ms.tex
Updates from Overleaf

@@
+\justifying
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\suit~consists of two main sub-units: The \suit~optics package - comprising an off-axis Ritchey-Chr\'{e}tien telescope, and \suit~Electronics package - responsible for communicating with the telescope to perform imaging.
+The main components of the \textit{SUIT} optics package include a multi-operation entrance door, a thermal filter to control the amount of incoming sunlight, primary and secondary mirrors, a shutter mechanism to control exposure times, baffles to reduce stray and scattered light, a motorized filter wheel assembly, a piezoelectric focusing mechanism, and a CCD detector.
+Figure \ref{fig:suit} shows a schematic diagram of the telescope.
+
+%%%%%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{SUITLayout.jpg}
+    \caption{Schematic diagram of the \textit{SUIT} telescope.}
+    \label{fig:suit}
+\end{figure}
+%%%%%%%%%%%%%%%%%%
+
+\suit~observes the Sun in eleven spectral bands, of which three are broadband (referred to as BB) and eight are narrow bands (referred to as NB), as listed in Table~\ref{tab:science_filters}.
+These are used to image different heights of the solar atmosphere, from the photosphere to the chromosphere.
+In the wavelength range of interest, i.e., 200--400 nm, the solar flux increases by two orders of magnitude (see Fig.~\ref{fig:sun_spec}).
+The spectrum is SOLSTICE and SOLSPEC solar flux combined.
+Therefore, we must employ certain combination filters to control solar flux levels and achieve the best signal-to-noise ratio (SNR) at each filter bandpass.
+These combination filters are listed in the second column of Table~\ref{tab:science_filters}.
+Note that \textit{SUIT} uses BB01 as a combination filter for NB01 and BB01.
+Similarly, NB08 is used as a combination filter for another NB08 filter.
+In total, \textit{SUIT} has 16 filters mounted on two filter wheels, each having eight slots.
+A given filter combination is achieved by rotating the two filter wheels independently and placing the desired filter combination in the beam path.
+
+%------------------------------------------------------------
+\begin{figure}
+    \begin{center}
+    \begin{tabular}{c}
+    \includegraphics[trim={0.8cm 0cm 2cm 1.2cm},clip,width=0.6\linewidth]{solar_spec_2.pdf}
+    \end{tabular}
+    \end{center}
+\caption{The solar spectrum from SOLSTICE and SOLSPEC combined. The inset plot shows a dramatic rise in solar irradiance within \suit's observation band.} 
+\label{fig:sun_spec} 
+\end{figure} 
+%-----------------------------------------------------------
+
+%-----------------------------------------------------------
+\begin{table*}[ht!]
+\begin{center}
+\begin{tabular}{||l|c|c|c|r||}
+\hline
+\textbf{Science}  &	\textbf{Combination} &	\textbf{Central} & \textbf{Bandpass} &\textbf{Science} \\
+\textbf{Filter}	&	\textbf{Filter}     &	\textbf{Wavelength  (nm)}	&		\textbf{(nm)	}	   	&\textbf{target}		\\
+\hline
+NB01     & BB01 		& 214.0 		    & 11.0 		& Continuum\\
+NB02 	& BP02		& 276.7				& 0.4 		& Mg~\rm{II}~k blue wing \\
+NB03 	& BP02		& 279.6 			& 0.4 		& Mg~\rm{II}~k\\
+NB04 	& BP02		& 280.3				& 0.4 		& Mg~\rm{II}~h\\
+NB05		& BP02		& 283.2				& 0.4 		& Mg~\rm{II}~h red wing\\
+NB06 	& BP03		& 300.0 			&1.0 		& Continuum\\
+NB07 	& BP03		& 388.0				&1.0 		& CN Band\\
+NB08		& NB08		& 396.85 			& 0.1 		& Ca~\rm{II}~h\\
+BB01 	& BB01		& 220.0				& 40.0		& Herzberg Continuum \\
+BB02 	& BP04		& 277.0 			& 58.0       & Hartley Band\\
+BB03 	& BP04		& 340.0				& 40.0        & Huggins Band\\
+\hline
+\end{tabular}
+\end{center}
+\caption{List of science filters on board \suit.
+Columns from left to right denote filter mnemonics (including science and combination filters; NB: Narrowband, BB: Broadband, BP: Bandpass), central wavelengths for science filters and corresponding bandpasses, and the observation interest for the filter.}
+\label{tab:science_filters}
+\end{table*}
+%-----------------------------------------------------------
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Throughput model of SUIT}\label{sec:suit_throughput}
+\section{Analysis of Spacecraft jitter simulation for {\suit}}\label{sec:suit_jitter}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+One of the key steps in estimating the imaging performance was to quantify, if the RMS level of spacecraft jitter would affect the imaging across various exposure time.
+For this purpose we analyzed the simulated spacecraft drift data provided by the ISRO URSC team to quantify the RMS jitter as a function of exposure time.
+There are two main moving components within the payload that can generate significant jitter on the payload, namely the shutter door and the filter wheel (FW) movement.
+The payload has a FW movement torque compensator in place, to minimize the jitter generated by the FW movement.
+So, there were four main scenarios that were simulated to be analyzed arranged from least to most amount of jitter:
+
+%%%
+\begin{enumerate}
+    \item No shutter torque + no filter movement
+    \item Only shutter torque
+    \item Shutter torque + FW movement + FW compensation torque
+    \item Shutter torque + FW movement + no FW compensation torque
+\end{enumerate}
+%%%
+
+%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[trim={1cm 0cm 1cm 1cm},clip,width=0.7\textwidth]{jitter_sim.pdf}
+    \caption{The figure shows the simulated drift for the yaw, roll and pitch axis of the payload as a function of time for the aforementioned four cases in \S\ref{sec:suit_jitter}.
+The panel (a) shows the simulated drift when there is no shutter or FW movement.
+Panel (b) shows the same when there is only shutter movement.
+Panel (c): when there is both shutter and FW movement and FW movement compensation is employed.
+Panel (d): when there is both shutter and FW movement but the FW movement compensation is not employed.}
+    \label{fig:jitter_sim}
+\end{figure}
+%%%%%%%%
+
+The Fig.~\ref{fig:jitter_sim} shows the simulated drift for the aforementioned four cases.
+We did a Fourier analysis of the simulated drift data to characterize the spacecraft jitter from the spacecraft drift.
+The Fig.~\ref{fig:jitter_sim_ps} shows the power spectrum for the simulated drift shown in Fig.~\ref{fig:jitter_sim}.
+The SUIT imaging channels have a maximum possible exposure$~\sim$~1.4 s, which corresponds to a frequency of~$\sim$~0.7 Hz and lower exposures would correspond to a higher frequency.
+So, signals in the Fourier transform corresponding to 0.7 Hz or higher are capable of affecting the imaging within the exposure window.
+We assumed any signal with a frequency 0.5 Hz or greater from the Fourier transform to be Jitter signal.
+We then took a frequency cut at 0.5 Hz, of the power spectrum to filter the drift from the jitter and then took an inverse FT to reconstruct the jitter signal for the three axis.
+To calculate the amount of RMS jitter on various time scales relevant in the context of SUIT exposure times, we took the extracted jitter signal and picked out bins of multiple time scales and calculated the RMS jitter for them.
+We had several bins for each time scale, each of which gave us RMS jitter and maximum jitter within that bin.
+We averaged all the bins to estimate the RMS jitter and maximum Jitter for that specific timescale.
+Figures \ref{fig:rms_jitter} ad \ref{fig:max_jitter} shows the RMS and maximum jitter as a function of timescale.
+SUIT has a 0.7\arcsec/pix resolution.
+Both the average and the maximum jitter even in the worst case scenario, i.e when shutter torque and FW movement is present but the FW movement compensation is not employed, is much lower than the pixel size of SUIT within timescales relevant to exposure times for SUIT.
+We did not need to account for the jitter while characterizing the imaging performance.
+
+%%-----------------------------%%
+\begin{figure}
+    \centering
+    \includegraphics[trim={0cm 0cm 1cm 1cm},clip,width=0.7\textwidth]{jitter_psd.pdf}
+    \caption{The figure shows the FT of the simulated drift for the yaw, roll and pitch axis of the payload as a function of time for the aforementioned four cases in \S\ref{sec:suit_jitter}.
+The \textbf{panel (a)} shows the FT of the simulated drift when there is no shutter or FW movement.
+\textbf{Panel (b)} shows the same when there is only shutter movement, \textbf{panel (c)}: when there is both shutter and FW movement and FW movement compensation is employed, \textbf{panel (d)}: when there is both shutter and FW movement but the FW movement compensation is not employed.}
+    \label{fig:jitter_sim_ps}
+\end{figure}
+%%-----------------------------%%
+
+%%-----------------------------%%
+\begin{figure}
+    \centering
+    \includegraphics[trim={0cm 0cm 1cm 1cm},clip,width=0.7\textwidth]{rms_jitter.pdf}
+    \caption{The RMS jitter at various timescales for the four scenarios of operation.}
+    \label{fig:rms_jitter}
+\end{figure}
+%%-----------------------------%%
+
+%%-----------------------------%%
+\begin{figure}
+    \centering
+    \includegraphics[trim={0cm 0cm 1cm 1cm},clip,width=0.7\textwidth]{max_jitter.pdf}
+    \caption{The Maximum jitter at various timescales for the four scenarios of operation.}
+    \label{fig:max_jitter}
+\end{figure}
+%%-----------------------------%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Throughput model of {\suit}}\label{sec:suit_throughput}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The design of the \suit~telescope prioritizes throughput and photometric accuracy requirements.
+Optical parameters of various optical elements, such as the reflectivity of primary and secondary mirrors, transmission of the thermal filter, field corrector lens, spectral transmission of the science filter, and combination filter, are optimized to maximize throughput within their corresponding wavelength ranges.
+
+The optical response of \suit~is evaluated based on the solar spectral irradiance and the throughput characteristics of each sub-assembly.
+Experimental throughput data is compared with a throughput model to validate the consistency between experimental and simulated results.
+This validation process is crucial for determining exposure times for the payload across the eleven science bandpasses in different operational modes.
+
+The throughput of \suit~is modeled using the Sun-as-a-Star spectrum to predict counts for specific science filter combinations.
+The measured wavelength responses of individual components are utilized to estimate these counts.
+If the photon flux incident at the entrance aperture is denoted by $P(\lambda)$, then the recorded data number in the images can be expressed as:
+
+%%%%%%%%%
+ \begin{equation}\label{eq1}
+     DN~=~\int~P(\lambda)~R(\lambda)~t~d\lambda
+ \end{equation}
+ %%%%%%%%%
+where $R(\lambda)$ is the effective area for the specific science filter combination, and $t$ is the exposure time for that filter.
+The effective area $R(\lambda)$ is derived by multiplying the measured response of all the optical sub-assemblies in the beam path-
+
+%%%%%%%%%
+\begin{equation}
+    R(\lambda)~=~TF(\lambda)\times PM(\lambda)\times SM(\lambda)\times SF_{i}(\lambda)\times SF_{j}(\lambda)\times L(\lambda)\times QE(\lambda)\times A
+    \label{eq:eff_area}
+\end{equation}
+%%%%%%%%%
+where $TF(\lambda), PM(\lambda), SM(\lambda), SF_{i}(\lambda), SF_{j}(\lambda), L(\lambda)~and~QE(\lambda)$ are the measured responses as a function of wavelength of thermal filter, primary mirror, secondary mirror, filters in filter wheel 1 and 2, field corrector lens and the quantum efficiency of the CCD.
+The effective area curves for each filter are shown in Fig.~\ref{fig:eff_area}.
+
+%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{eff_area.pdf}
+    \caption{The effective area curves for SUIT science filters.}
+    \label{fig:eff_area}
+\end{figure}
+%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Photometric Calibration and Spectral Validation {\suit}}\label{sec:suit_radiometric}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To achieve the scientific goals, photometric and spectral calibration of the payload is of utmost importance.
+The photometric throughput of the telescope is modeled during instrument design to ensure the required photometric throughput accuracy of 1\%.
+For this purpose, Light of a known wavelength and measured intensity is fed into the payload from a monochromator after collimation.
+The payload is operated in a vacuum chamber to simulate space-like conditions in this setup.
+For the details of the experimental setup refer to \cite{sarkar24}.
+We use these measurements and compare them with our throughput model to validate the measurements of the transmission profiles.
+We also use these measurements to validate the spectral transmission profile of the science filter channels.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Photometric Calibration}\label{sec:calibration}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this test, an optical fiber is used to feed light from the monochromator at the focal plane of the SUIT collimator.
+The monochromator uses a grating with a density of 1200 lines per mm (lpmm) and a nominal dispersion of 1.44 nm/mm, blazed at 500 nm.
+The spectral resolution of the monochromator depends on the entrance slit or the exit slit, whichever is geometrically wider.
+In our case, an entrance slit width of 3 mm is used to maximize the light output from the spectrograph.
+The emergent monochromatic light has a wavelength band of \(3 \times 1.44 = 4.32\) nm.
+This wavelength band accommodates the complete transmission spectrum of all the narrow band science filters being tested.
+The fiber carries light from the monochromator, which is collimated and fed into~\suit.
+
+A UV-enhanced photo diode, certified by the National Institute of Science and Technology (NIST) as traceable (specifically the Newport 918D-UV-OD3R model), is used to quantify the net output flux of the collimator.
+Both the monochromator and photo diode are set to align with the wavelength corresponding to the science filter under test.
+It's noteworthy that the Xenon lamp's spectral intensity remains stable within a 4.32 nm band, exhibiting a flat profile.
+By dividing the measured photo diode's output flux(\(nWm^{-2}\)), by the wavelength band of the spectrograph, we derive the spectral flux from the collimator(\(Wm^{-2}nm^{-1}\)).
+Following this, the photo diode is removed from the beam path, and an image of the fiber bundle is captured using \suit.
+The fiber face is obscured to record the background value, and another exposure is initiated.
+These findings are directly comparable with the modeled throughput derived from the Sun-as-a-Star spectrum for various filter wavelength bands.
+The following steps are followed to do that:
+
+\begin{itemize}
+     \item The background count is estimated by taking the median of the fiber occulted image.
+     \item From the background corrected optical fiber images, we calculate the 99\% ensquared energy radius and the total enclosed data counts ($DN_{0.99}$).
+     \item The photo diode gives the measurement of corresponding input flux ($E_{0.99}$) in units of $nW.m^{-2}$ for an input spectral bin of 4.32 nm.
+The flux is divided by the spectral bin size to get the spectral irradiance per unit area in units of $nW.m^{-2}.nm^{-1}$.
+The ratio of $DN_{0.99}$ and ${E_{0.99}}$ tells the expected counts for any given input flux, $F~=~\nicefrac{DN_{0.99}}{E_{0.99}}$ in units of $DN.s^{-1}/(nW.m^{-2}.nm^{-1})$ for that science filter bandpass.
+     \item We use a composite SOLar STellar Irradiance Comparison Experiment (SOLSTICE; 115{--}320 nm) onboard the SOlar Radiation and Climate Experiment (SORCE) \cite{rottman05,harder05,mcclintock05} satellite and SOLar SPECtrometer (SOLSPEC) \cite{thuillier09} solar spectrum as our standard for solar radiation.
+Using the spectra, we can calculate the total energy input from the Sun for the concerned filter within the wavelength extent, $E_{\odot}~=~\int_{\lambda_{1}}^{\lambda_{2}}~P(\lambda)~d\lambda$, where $P(\lambda)$ is the SOLSTICE, SOLSPEC composite solar spectrum.
+Here, $\lambda_{2}-\lambda_{1}$ is the extent of the concerned band.
+     \item Using eqn.\ref{eq1} along with the aforementioned spectrum, we can calculate the expected count observed (i.e., $DN_{throughput}~=~\int~P(\lambda)~R(\lambda)~t~d\lambda$) for a given filter combination.
+     \item $F~=~\nicefrac{DN_{0.99}}{E_{0.99}}$ is multiplied with the total energy input from the Sun ($E_{\odot}$) for the concerned filter to find the photo electrons collected per second ($DN_{measured}~=~E_{\odot}\times~F$).
+ \end{itemize}
+
+In Table~\ref{tab:throughput}, we present a comparison between the solar counts derived from our measurements and those calculated from the throughput model for specific filter combinations.
+It's noteworthy that NB01, BB01, and BB02 have transmission below 250~nm.
+The atmosphere significantly attenuates UV light below this wavelength as it passes through the monochromator and collimator, resulting in insufficient signal strength for measurement.
+Moreover, the radiance of the Xenon light source increases nearly linearly by 60 times between 200~nm and 300~nm, and then remains relatively constant up to 400~nm.
+Consequently, this phenomenon leads to an inadequate signal-to-noise ratio (SNR) in the output during photometric calibration and spectral validation for these filters.
+
+Our findings indicate that the measured data counts per second align within a 20\% margin of those derived from the throughput model (refer to Table \ref{tab:throughput}), except for NB07.
+One possible explanation for this discrepancy lies in the utilization of SOLSPEC data for modeling the throughput beyond 310~nm, while SOLSTICE data is employed for modeling throughput below this threshold.
+It's worth noting that SOLSPEC data provides a resolution of 0.05~nm, unlike SOLSTICE data, which offers a finer resolution of 0.025~nm.
+Consequently, this discrepancy leads to reduced accuracy in the modeled data counts for filters operating beyond 310 nm.
+
+%-----------------------------------------------------------
+\begin{table*}[ht]
+\begin{center}
+\begin{tabular}{||c|c|c|c||}
+\hline
+Science & Counts calculated & Counts calculated & Ratio of \\
+filter & from measurement & from throughput model &  \\
+ & $DN_{measured}~=~E_{\odot}\times~F$ & $DN_{throughput}~=~\int~P(\lambda)~R(\lambda)~t~d\lambda$ & $\frac{DN_{measured}}{DN_{throughput}}$\\
+ & ($Data~number~s^{-1}$) & ($Data~number~s^{-1}$) & \\
+\hline
+NB03 & 18531 & 15520 & 1.19 \\
+NB04 & 35040 & 36717 & 0.95 \\
+NB05 & 124116 & 131625 & 0.943 \\
+NB06 & 105138 & 107064 & 0.98 \\
+NB07 & 750744 & 391364 & 1.91 \\
+NB08 & 26523 & 24096 & 1.1 \\
+BB03 & 511722 & 434532 & 1.18 \\
+\hline
+
+\end{tabular}
+\end{center}
+\caption{Comparison of the data numbers derived from throughput model (using SOLSTICE and SOLSPEC data) with the data numbers inferred from the measurements.} 
+\label{tab:throughput}
+\end{table*}
+%-----------------------------------------------------------
+
+Surprisingly, the modeled counts for NB08, despite falling beyond 310 nm, do not exhibit significant deviation.
+This can be attributed to the extremely narrow bandpass of NB08, which is merely 0.01 nm wide and centered at the prominent Ca-II h spectral line.
+Conversely, BB03 features a broader effective bandpass of 40 nm, rendering the model less sensitive to minor fluctuations in the sparsely sampled SOLSPEC solar spectrum.
+Consequently, this results in comparable data counts per second to those observed in the laboratory.
+
+To validate this hypothesis, we compare the throughput modeled for the NB06 filter using lower-resolution SOLSPEC data with that calculated using higher-resolution SOLSTICE data.
+From Table \ref{tab:throughput}, it is evident that the ratio of measured to modeled throughput for NB06, when modeled using higher-resolution SOLSTICE data, is 0.98.
+However, when the NB06 throughput is modeled using lower-resolution SOLSPEC data, the obtained ratio is approximately 1.8, similar to what is observed for NB07 throughput modeled with SOLSPEC data.
+Hence, the high ratio for NB07 in Table \ref{tab:throughput} can be attributed to the sparsely populated SOLSPEC data used for modeling the throughput.
+
+%################################### 
+\subsection{Full Payload Spectral Validation}\label{valid}
+%###################################
+
+Spectral validation is aimed at confirming the transmission profile of the \textit{SUIT} payload with various science filters across different wavelengths within their respective bandpasses.
+Light from the monochromator is collimated and directed into the payload, as previously described.
+The wavelength band of the light source is selected to allow for multiple measurements to be taken at non-overlapping wavelength bins within the transmission band of a given filter.
+A holographic grating with a density of 2400 lines per mm (lpmm), blazed at 220 nm, is employed in the monochromator.
+The nominal dispersion of this grating is 0.74 nm/mm.
+The entrance slit width of the monochromator is configured to be 200 microns, resulting in a wavelength bin size of (0.74 nm/mm $\times$ 0.2 mm = 0.148 nm).
+This light is then introduced into the payload, and readings are acquired across the transmission spectrum of the science filter, ensuring that adjacent readings remain independent of each other.
+The total energy is quantified at each measured wavelength, allowing for the spectral response of the entire telescope across the concerned filters to be determined.
+
+Subsequently, the entrance slit width of the monochromator is enlarged to 3 mm, and the light output is gauged from the clear aperture of the collimator using the NIST traceable photo diode to validate the spectral flux being supplied to the \textit{SUIT} payload.
+This data serves as a basis for obtaining photometric calibration to match the measured spectral flux.
+For further details of the experimental setup refer to \cite{sarkar24}.
+The following steps were followed to perform the spectral validation:
+
+ %%%%%%%%%%
+ \begin{itemize}
+ \item Like image acquisition during photometric calibration - the fiber face is opened and closed consecutively to record light from the data and the contribution from the background.
+ \item The median value of the background image is subtracted from the fiber image, and we calculate the radius, which encircles 99\% of the total intensity contributed by the fiber bundle in the corrected image.
+ \item The total counts within the 99\% ensquared energy radius ($C_{i}$) is calculated in units of ADC counts/s.
+ \item The corresponding energy input is derived from photo-diode measurement ($E_{i}$) in units of $nW.m^{-2}.nm^{-1}$.
+ \item The same measurement can be carried out for various wavelength points within the bandpass of the concerned filter combination.
+The ratio of these two quantities, $F_{i}~=~\frac{C_{i}}{E_{i}}$ yield the spectral calibration for that filter combination in units of $\nicefrac{ADC~counts.s^{-1}}{nW.m^{-2}.nm^{-1}}$ as a function of wavelength.
+ \end{itemize}
+ %%%%%%%%%%
+
+In Fig.~\ref{fig:nb2_images}, we show the captured images for the NB02 filter combination at various wavelengths of incident light.
+The same was performed for all other filter combinations.
+The measurement wavelength and the calculated 99\% ensquared energy radius are quoted at the top of each panel.
+We plot the spectral validation results of all filter combinations with transmission bandpasses above 250 nm in Fig.~\ref{fig:sepc_calib}.
+The \textit{x} and \textit{y} error bars in Fig.~\ref{fig:sepc_calib} represent wavelength bins for the given input slit size and the Poisson uncertainty of the measured ADC counts, respectively.
+The plots demonstrate that the measured shape of the instrument spectral response agrees well with the modeled spectral response for all filter combinations with transmission bandpass above 250 nm.
+
+We could not carry out the spectral characterization for the NB08 filter due to the appearance of multiple strong ghost reflections close to the central patch.
+It is to be noted that the bandpass for NB08 is facilitated by a stack of two filters, which, unlike other filters, have no relative tilt between them, resulting in strong ghost reflections.
+These affect the estimation of ensquared energy across the transmission bandpass, affecting spectral validation results for this filter.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=0.9\linewidth]{nb2_images_edit.pdf}
+\end{center}
+\caption 
+{\label{fig:nb2_images} Images captured at various wavelengths for the NB02 filter of \suit.
+The measurement wavelength and the 99\% ensquared energy radius are quoted at the top of each panel.
+The axes of the images are in units of image pixels.}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+\includegraphics[trim={2.1cm 3.2cm 1.2cm 5.2cm},clip,width=0.95\textwidth] {spec_calib_new.pdf}
+\end{center}
+\caption 
+{\label{fig:sepc_calib} Spectral validation for various filter combinations inferred from the imaging measurements (blue markers).
+The wavelength bins give the $x$ errors for the given input slit size.
+The Poisson uncertainty of the measured ADC counts gives the $y$ errors.
+The red solid curve shows the effective area calculated from measured transmission profiles of each component using Eqn \ref{eq:eff_area}.}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Fig.
+\ref{fig:nb8_ghost} (a), we depict the fiber image captured at 396.85 nm.
+The position of the central image of the fiber, along with the sparsely spaced ghost reflections, is delineated by a white dashed box.
+Fig.
+\ref{fig:nb8_ghost} (b) offers a magnified perspective of this box, revealing the sparsely shaped ghost reflections indicated by white arrows.
+Some ghost reflections are observed very close to the central patch.
+Fig.
+\ref{fig:nb8_ghost} (c) provides a closer view around the central patch, with solid and dotted arrows indicating two closely spaced ghost reflections situated very close to the center.
+Given that these ghost reflections appear in proximity to the central patch and the relative brightness of the central patch to the ghost reflections fluctuates with wavelength, the estimation of the 99\% ensquared energy radius is also influenced.
+
+%%%%%%%%%%%%%%
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{nb8_ghost_im.pdf}
+    \caption{(a) The ghost reflections of the optical fiber as seen with the NB08 filter.
+The input beam is centered at 396.85 nm.
+The position of the ghost reflections is marked with a white dashed box.
+(b) The zoomed-in view of the white dashed box.
+The arrows indicate sparsely spaced ghost reflections.
+(c) The arrows indicate two closely spaced ghost reflections close to the center.
+(d) 99\% ensquared energy box around the fiber bundle at 396.85 nm.
+(e) 99\% ensquared energy box around the fiber bundle at 396.60 nm.}
+    \label{fig:nb8_ghost}
+\end{figure}
+%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Stellar Calibration of  {\suit}}\label{sec:stellar_calib}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The various science goals of \suit~were already mentioned in \S\ref{sec:suit}.
+To address these scientific objectives, the necessity of absolute stellar calibration is manifold.
+\suit, with its capabilities, will be imaging the Sun and dynamic processes such as solar flares and jets occurring in the solar atmosphere, including eruptions of various scales.
+Additionally, it will assist in measuring solar irradiance across 11 different passbands, probing various heights in the solar atmosphere from the photosphere to the chromosphere.
+With absolute calibration, we would be able to probe the underlying physical mechanisms driving these processes.
+
+Many properties of white-light flares are also observable in the near-ultraviolet (NUV) regime.
+Typically, there are significant correlations between different flare quantities in white light and X-ray emissions, such as white-light excess and soft X-ray flux \citep{benz16,hudson16}.
+These correlations enable us to infer underlying mechanisms that likely drive the correlation between these quantities, such as the mechanisms responsible for transferring energy and mass across different layers of the Sun.
+In our case, \suit~would observe the Sun alongside HEL1OS and SoLEXS \citep{solexs}.
+For comparative purposes across observations from three different instruments, absolute calibration becomes essential.
+
+Furthermore, in conjunction with \suit, the HEL1OS and SoLEXS data provide broad coverage of the electromagnetic spectrum from hard X-rays to the NUV.
+This comprehensive coverage allows us not only to study the initiation and triggering of eruptive events, but also to examine these quantities over a solar cycle and assess their contribution to changes in the solar spectral irradiance.
+Lastly, it's important to note that the Earth's atmosphere absorbs UV and X-ray emissions.
+UV radiation below 310 nm is largely absorbed by the atmosphere, while radiation beyond 310 nm can penetrate it.
+The absorption dynamics are primarily governed by oxygen ($O_{2}$) below 200 nm and ozone ($O_{3}$) beyond 240 nm, with both substances actively participating in the absorption process between 200 and 240 nm \citep{haigh07}.
+Therefore, understanding the solar spectral irradiance in the 200-400 nm range is pivotal for comprehending the dynamics and chemistry of Earth's atmosphere, particularly the ozone-oxygen cycle.
+This data serves as a crucial input for atmospheric modeling and provides insights into the Sun-Earth atmosphere connection.
+With absolute stellar calibration, \textit{SUIT} would furnish us with the solar irradiance in these bands and the radiance of various features on the solar disk before it encounters atmospheric attenuation.
+
+\suit~is equipped with 16 LEDs, with 8 each operating at two distinct peak wavelengths: 258 nm and 356 nm, primarily for calibration purposes.
+However, it's worth noting that LEDs may degrade over time and do not offer fluxes corresponding to each individual filter.
+We have obtained measurements of flux-to-count ratio at various wavelengths within the extent of the science filter bands.
+This data will undoubtedly assist us in providing absolute calibration to \suit~observations.
+Nevertheless, unlike LEDs, while we can quantify how the overall throughput of the science filter combinations changes over time, we cannot quantify how the effective area of the science filter combination degrades as a function of wavelength.
+This degradation would impact the radiometric calibration using these measurements over time.
+Therefore, calibration through alternative methods is necessary, such as utilizing standard astronomical sources.
+
+In an ideal scenario, the captured image would remain unaltered, devoid of any artifacts introduced by the instrumentation.
+However, in practice, the obtained image is influenced by the instrumental response, which can degrade over time.
+Radiometric calibration involves quantifying the instrumental response and using it to predict the actual signal received from the source.
+
+Furthermore, \suit~ lacks in-band spectral resolution and lacks an accurate on-calibration lamp corresponding to the wavelength coverage of each individual filter.
+Therefore, it becomes imperative to convert the total in-band photo-electron count to the corresponding energy in real units.
+This necessity arises from the fact that photons across a wide band possess varying energy levels, making it challenging, if not impossible, to ascertain the distribution of photo-electrons across a band observation.
+Failure to address this adequately may impede our ability to effectively achieve one or more science goals of \suit.
+
+In principle, for any astronomical source we encounter,
+
+%------------------------------------------------------------
+\begin{equation*}
+    S(\lambda) = R(\lambda) \times F(\lambda);
+\end{equation*}
+%------------------------------------------------------------
+
+where $F(\lambda)$, $S(\lambda)$ and $R(\lambda)$ are the emitted flux, measured signal and the response of the system at the wavelength $\lambda$, respectively.
+Here $R(\lambda)$ (instrumental response) will consists of the response from all the components of the telescope, namely thermal filter, the primary and secondary mirrors, science filter in conjunction with bandpass filer, focusing lens and the QE of the detector (a CCD in this case).
+In the case of an standard source we can write,
+
+%------------------------------------------------------------
+\begin{equation*}
+    S(\lambda)_{calib} = R(\lambda)_{calib} \times F(\lambda)_{calib},
+\end{equation*}
+%------------------------------------------------------------
+\noindent Therefore,
+%------------------------------------------------------------
+\begin{equation*}
+    R(\lambda)_{calib} = \frac{S(\lambda)_{calib}}{F(\lambda)_{calib}},
+\end{equation*}
+%------------------------------------------------------------
+
+\noindent where the subscript `calib' denotes all variables related to the standard absolute calibration source.
+The parameter $R(\lambda)_{calib}$ represents a calibration factor acquired by observing a standard source using an instrument.
+Photon flux can be straightforwardly computed from an absolutely calibrated spectrum $F(\lambda)$ using the formula $PF(\lambda) = SF(\lambda) \times \frac{\lambda}{hc}$.
+
+Similarly, for the target source under observation, we have,
+
+%------------------------------------------------------------
+\begin{equation*}
+    S(\lambda)_{target} = R(\lambda)_{target} \times F(\lambda)_{target}
+\end{equation*}
+
+\noindent and 
+\begin{equation}
+    F(\lambda)_{target} = \frac{S(\lambda)_{target}}{R(\lambda)_{calib}}
+\end{equation}
+%------------------------------------------------------------
+where, it is assumed that the instrumental response remains unchanged from the calibrated source to the target source being observed, and hence $R(\lambda)_{target}=R(\lambda)_{calib}$.
+
+%------------------------------------------------------------
+\subsection{Requirements of the calibration source} \label{req}
+%------------------------------------------------------------
+
+In general, for radiometric calibration, on-board standard sources such as diodes, LEDs, etc., or astronomical sources like standard stars are employed.
+However, in a space-based mission, the on-board artificial sources themselves undergo significant degradation, which needs to be meticulously modeled.
+Therefore, it is preferable to utilize standard stars as calibration sources, provided they satisfy the essential conditions listed below \citep{article2}.
+
+%%%%%%%%%%%%%%%
+\begin{itemize}
+    \item The calibration source must exhibit adequate brightness within the wavelength region of interest, which spans from 200 to 400 nm in the current context, to achieve the requisite photometric accuracy across all science filters.
+In our case, the thermal filter at the entrance aperture significantly attenuates in-band solar flux (along with nearly all out-band flux) reaching the detector to prevent pixel saturation.
+This mechanism applies equally to the calibration sources.
+Hence, the calibration source must possess sufficient brightness to attain an acceptable signal-to-noise ratio (SNR) within a reasonable observation time.
+    \item Ideally, the standard calibration source should exhibit minimal variability, with any changes occurring over timescales significantly longer than the time required to accumulate a sufficient number of photons from the source to achieve the desired level of photometric accuracy.
+    \item  Preferably, the calibration source should not be integrated into a complex system.
+However, if it is, any accompanying components should be sufficiently weak so that the photon flux from them does not significantly contribute to the total flux of the system.
+Otherwise, it would be necessary to model the contribution of the companion(s) separately.
+\end{itemize}
+%%%%%%%%%%%%%%%
+
+Any astronomical source that meets these criteria and has its spectral energy distribution (SED) studied and calibrated to absolute units would be suitable for radiometric calibration.
+Stars such as Sirius A (HD48915/HR2491) and Vega (HR7001) largely fulfill the aforementioned criteria, with the exception of Sirius A, which has a white dwarf companion known as Sirius B.
+However, the apparent magnitudes of Sirius A and Sirius B are $-1.46$ \citep{hoffleit91} and $8.44$ \citep{mccook99,holberg13} respectively, ensuring that the contribution from Sirius B is mostly negligible.
+The absolute calibrated spectra for both stars are depicted in Fig.~\ref{fig:spec_1} and are sourced from the CALSPEC archive, which contains composite stellar spectra used as flux standards in the Hubble Space Telescope (HST) system.
+
+%------------------------------------------------------------
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\linewidth]{spectrum_sir_veg.pdf}
+    \caption{Calibrated spectra of Vega and Sirius A taken from \href{https://www.stsci.edu/hst/instrumentation/reference-data-for-calibration-and-tools/astronomical-catalogs/calspec}{CALSPEC}, Vega in Blue and Sirius A in Orange.}
+    \label{fig:spec_1}
+\end{figure}
+%------------------------------------------------------------
+
+%------------------------------------------------------------
+\subsection{Exposure time for the calibration sources}\label{expo_time}
+%------------------------------------------------------------
+
+A high level of photometric accuracy is essential for imaging the Sun and monitoring spectral irradiance.
+It's noteworthy that the total energy output from the Sun at wavelengths below 400 nm comprises only about 8\% of the total solar irradiance (TSI).
+However, there is a recorded variability of over 60\% in radiation below 400 nm over a solar cycle \citep{krivova06}, whereas the variability in TSI over a solar cycle is approximately 0.1\%.
+Photometric accuracy is defined as the ratio of the Poisson noise of the signal to the signal itself.
+The number of photo-electrons produced in a given exposure time is give by Eqn.~\ref{eq1},\ref{eq:eff_area}.
+We aim for a photometric accuracy of 0.2\%, which corresponds to a photo-electron count of $\sim 2.5 \times 10^{5}$.
+Considering this requirement, we compute the exposure times required for both Vega and Sirius A, which are given in Table~\ref{tab_2}.
+
+%-------------------------------------------------
+\begin{table}
+\centering
+\begin{tabular}{ccccc}
+\hline
+        & Exposure time(minutes) & Exposure time(minutes) \\
+        Band & Vega & Sirius A\\
+        \hline
+        NB1 & 8 & 2\\
+        NB2 & 23 & 6\\
+        NB3 & 23 & 6\\
+        NB4 & 19 & 5\\
+        NB5 & 16.5 & 4\\
+        NB6 & 15 & 3.5\\
+        NB7 & 12 & 3\\
+        NB8 & 368 & 90\\
+        BB1 & 2 & 0.5\\
+        BB2 & 20 & 5\\
+        BB3 & 13 & 3\\
+        \hline
+    \end{tabular}
+    \caption{The exposure time required to obtain $2.5 \times 10^{5}$ photo-electrons to achieve 0.2\% photometric accuracy in each of the science filters for both Vega and Sirius A.}
+\label{tab_2}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Method for Calibration}\label{cal_meth}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+With the exposure times calculated for all filters, for calibration purposes, we will assume a photometric accuracy of 0.2\% across all bands for the calibration source.
+This implies that the Poisson noise arising from the total photo electron count is 0.2\%, corresponding to a total photo electron count of approximately $2.5 \times 10^{5}$.
+As described in Section \ref{sec:stellar_calib}, the flux from the target source is given by $F(\lambda)_{\text{target}}=\frac{S(\lambda)_{\text{target}}}{R(\lambda)_{\text{calib}}}$, where we assume that the instrumental response $R(\lambda)_{\text{calib}}$ remains unchanged from the calibration source to the target source.
+Therefore, given a calibration source using the absolute spectra ($F(\lambda)_{\text{calib}}$) and the signal ($S(\lambda)_{\text{calib}}$) received from it, we can quantify the filter profiles ($R(\lambda)_{\text{calib}}$).
+
+In the case of \suit, though there is no spectral resolution within the bands, and the only information we will obtain from an observation is the total number of photo electron counts from the bands for a given exposure time.
+The general method is as follows:
+
+\begin{itemize}
+    \item Given the spectra of a calibration source one can create the photo elctron count profiles using the instrument filter profiles.
+
+    \item One can calculate the total number of photo elctrons generated for some exposure time as:
+    \begin{equation*}
+        DN_{calib} = \int P(\lambda)_{calib\hspace{0.1cm}}R(\lambda)\hspace{0.1cm}A\hspace{0.1cm}t\hspace{0.1cm} d\lambda
+    \end{equation*}
+    \noindent where, $P(\lambda)$ is the photon flux from the Calibration source.
+
+    \item The inband energy from the spectra of the calibration source for the same exposure time can be calculated. The FWHM is taken to be the extent of each band while calculating the total energy.
+    \begin{equation*}
+        T_{calib} = \int_{inband} F(\lambda)_{calib}\hspace{0.1cm} A\hspace{0.1cm}t\hspace{0.1cm} d\lambda
+    \end{equation*}
+    \item The ratio of these two quantities give the calibration constant, `C' for each band, C = $\frac{T_{calib}}{DN_{calib}}$
+\end{itemize}
+
+To estimate how well this method performs, we use Vega (Sirius~A) as the calibration source and produce the phtoelctron count profiles from Sirius~A (Vega) and the Sun.
+The total count arising from each band multiplied by the calibration constant(C) should give the total energy from the spectra.
+
+%------------------------------------------------------------
+\subsection{Sirius A as calibration source}\label{sirius}
+%------------------------------------------------------------
+
+Table~\ref{tab:my_table_sun_sir} shows the performance of the method for a Sirius A as the calibrating source and sun as a target with 200s exposure in all bands.
+The uncertainties in the table~\ref{tab:my_table_sun_sir} are obtained by propagating the uncertainties of the \href{https://www.stsci.edu/hst/instrumentation/reference-data-for-calibration-and-tools/astronomical-catalogs/calspec}{CALSPEC} spectra.
+Key thing to note here, the comparisons for Solar spectra are made with a sun as a star spectra, while SUIT is going to observe the full solar disk on $(4k \times 4k)$ CCD.
+We have to add the contribution from all the pixels to have the full disk contribution.
+In practice, in the stellar pointing calibration run \suit~will be re-pointed towards Sirius A and the measurements would be used for absolute calibration.
+
+%------------------------------------------------------------
+\begin{table}[ht!]
+\small
+\centering
+    \begin{tabular}{|ccccc|}
+    \hline
+        Band & $(C=\frac{T_{sir}}{DN_{sir}})\times 10^{15}$ & DN/$10^{13}$ & Predicted Energy & Energy from \\
+         & (J/DN) & & ($C \times DN$) & spectra(J) \\
+        \hline
+        \hline
+        NB1 & $(72.62\pm0.88)$ & $(9.47 \pm 9.7 \times 10^{-7})$ & $(6.881 \pm 0.083)$ & 6.839\\
+        \hline
+        NB2 & $(5.164\pm0.062)$ & $(20.6\pm1.4\times10^{-6})$ & $(1.065\pm0.013)$ & $1.072$\\
+        \hline
+        NB3 & $(3.627\pm0.044)$ & $(10.5\pm1.0\times10^{-6})$ & $(3.854\pm0.043)\times10^{-1}$ & $3.884\times10^{-1}$ \\
+        \hline
+        NB4 & $(3.253\pm0.039)$ & $(12.3\pm1.1\times10^{-6})$ & $(4.003\pm0.048)\times10^{-1}$ & $(4.001\times10^{-1})$ \\
+        \hline
+        NB5 & $(3.160\pm0.038)$ & $(40.6\pm2.0\times10^{-6})$ & $(1.284\pm0.016)$ & $1.307$ \\
+        \hline
+        NB6 & $(7.295\pm0.088)$ & $(65.7 \pm 2.6 \times 10^{-6})$ & $(4.797\pm0.058)$ & $4.836$ \\
+        \hline
+        NB7 & $(8.715\pm0.010)$ & $(123 \pm 4 \times 10^{-6})$ & $(1.073\pm0.013)\times10^{1}$ & $1.055\times10^{1}$ \\
+        \hline
+        NB8 & $(17.71\pm0.21)$ & $(5.01 \pm 7.1 \times 10^{-7})$ & $(8.88\pm0.11)\times10^{-1}$ & $8.93\times10^{-1}$ \\
+        \hline
+        BB1 & $(28.50\pm0.41)$ & $(46.0 \pm 2.1 \times 10^{-6})$ & $(13.114\pm0.188)$ & 13.113 \\
+        \hline
+        BB2 & $(469.9\pm5.7)$ &$(28.3 \pm 1.7 \times 10^{-6})$ & $(132.997\pm1.607)$ & 132.994 \\
+        \hline
+        BB3 & $(221.1\pm2.7)$ & $(176 \pm 4 \times 10^{-6})$ & $(3.903\pm0.047)\times10^{2}$ & $3.896\times10^{2}$\\
+        \hline
+    \end{tabular}
+    \caption{The performance of the method with Sirius A as calibrating source and sun as a target with 200s exposure in all bands.}
+\label{tab:my_table_sun_sir}
+\end{table}
+%------------------------------------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Filter Choice for {\suit}}\label{sec:suit_filter_choice}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Filter Choice for SUIT}\label{sec:filter_choice}
+\section{Outlook}\label{sec:c3_outlook}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Photometric, Radiometric \& Spectral Calibration of SUIT}\label{sec:suit_cal}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\suit~is our first full-disk eye on the Sun in \ion{Mg}{2} window and \ion{Ca}{2} h line \sr{is this technically true?
+SOT did observe in the same wavelength.
+How much of it was full-disk?} and the various continuum channels onboard.
+The narrow band continuum and line channels provide us with targeted view into various layers of the sun, while the three broad band channels are designed to probe the radiance from the Sun, to investigate the effect on Earth's atmosphere over the duration of a solar cycle.
+This chapter focused on the various initial preparatory analysis we carried out in anticipation of \suit, and some of the calibration scheme planning initially carried on.
+
+The initial jitter estimation was done from simulations provided by the ISRO URSC team.
+That exhibited the jitter to be minimal compared to \suit~exposure timescales, hence would have no noticeable effects on the imaging.
+The proper estimation of the spacecraft jitter on orbit would be possible once the stellar calibration is done.
+During the stellar calibration the long exposure of Sirius-A, {\it i.e.} a point source would be carried out in a series of short exposures.
+This would give us the opportunity to quantify the amount of jitter of the spacecraft.
+
+The initial throughput model of \suit~was designed out of the necessity of a robust throughput model to estimate the expected SNR of various vendor provided science filters, in accordance to the scientific cases.
+It proved useful in finalizing the choice of the science filters to be mounted on the the payload.
+The throughput model also proved useful in designing our stellar calibration scheme, and provided a useful benchmark for validating the photometric performance of the payload on ground.
+The spectral validation of the science filters is important primarily for verifying the science filter combinations are observing the necessary wavelength windows.
+The necessity of a accurate throughput model, spectral and photometric validation of the payload, stellar calibration of the payload are intertwined with one another.
+A full characterization of all of these quantities is only possible after steallr callibration is carried out.

### 2024-07-22 chapter5/ms.tex
Updates from Overleaf

@@
-%UNLIKE IN A REGULAR TEX FILE, DON'T PUT ANY PREAMBLE MATERIAL HERE
+%\begin{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Aditya-L1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %   The  \ion{Mg}{2}~k \& h line intensity ratios can be used to probe the characteristics of the plasma in the solar atmosphere.
+In this study, using the observations recorded by the Interface Region Imaging Spectrometer (IRIS), we study the variation of the  \ion{Mg}{2}~k \& h intensity ratio for three flares belonging to X-class, M-class, and C-class, throughout their evolution.
+We also study the k-to-h intensity ratio as a function of magnetic flux density obtained from the line-of-sight magnetograms recorded by the Helioseismic and Magnetic Imager (HMI) on board the Solar Dynamics Observatory (SDO).
+Our results reveal that while the intensity ratios are independent of magnetic flux density, they show significant changes during the evolution of the C-class and M-class flares.
+The intensity ratios start to increase at the start of the flare and peak during the impulsive phase before the flare peak and decrease rapidly thereafter.
+The values of the ratios fall even below the pre-flare level during the peak and decline phases of the flare.
+These results are important in the light of heating and cooling of localized plasma and provide further constraint on the understanding of flare physics.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Solar Ultraviolet Imaging Telescope}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\end{abstract}
+\justifying
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{SUIT \& Solar Flares}\label{sec:suit_and_flare}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%----------------------------------------------------
+\section{Introduction} \label{sec:intro}
+%%----------------------------------------------------
 
-Solar flares are the most powerful magnetic events in the solar system.
-They are described as a sudden increase in brightness in localized areas on Sun.
-Within tens of minutes, they can release over $10^{32}$ erg of energy, which is emitted across the entire electromagnetic spectrum from radio to gamma rays.
-They can also launch high energetic particles into the interplanetary medium.
-Most of the flares occur in magnetic active regions, and the amount of flare energy released is comparable to the free energy stored in the magnetic system.
-The term "flare" is generally used explicitly for the entire magnetically-driven event's electromagnetic radiation, as it is the most significant fraction of the total energy liberated.
-The total energy released varies from event to event.
-It is also known that larger events occur much less frequently than smaller events.
+Solar flares are the most energetic events on the Sun, where an enormous amount of magnetic free energy is released due to the reconfiguration of the coronal magnetic field.
+The released energy can cause particle acceleration, heating and flows in the solar atmosphere and a transient enhancement in solar radiative output.
+Notably, a significant portion of the radiated energy during flares originates from the dense chromosphere \citep{fletcher10,milligan14}.
+Therefore, examining chromospheric lines during flares offers valuable diagnostic tools for understanding the physics of solar flares and their impact on the local plasma environment.
 
-The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1} of the Indian Space Research Organization (ISRO).
-With its 11 science filters (3 broadband and eight narrowband), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another.
-SUIT will provide full disk as well as partial disk images of the Sun with a pixel size of 0.7".
-Through SUIT imaging, we would be able to resolve solar flares spatially on the surface of the Sun, for the first time in near ultra-violet (NUV), which will help us to address the questions regarding their build-up and triggering mechanism.
-In addition, to measure the spatially resolved solar spectral irradiance within the wavelength range that is central for studying the Chemistry of oxygen and ozone in the Stratosphere of Earth's atmosphere.
+The chromosphere emits radiation across various ultraviolet (UV) and optical lines.
+While many optical lines, such as H$\alpha$ and \ion{Ca}{2}, are routinely observed from ground-based telescopes, observations of the  \ion{Mg}{2} resonance lines have been relatively infrequent in the past.
+However, since the launch of the Interface Region Imaging Spectrograph (IRIS) \citep{iris}, regular monitoring of these lines with excellent spatial and spectral resolution has become possible.
 
-It has been shown that the majority of flare energy emerges at the visible and UV wavelength range \citep{woods06}.
-\cite{woods04} showed that about 77\% of the energy is released in the wavelength range > 200 nm, and only ~ 23\% is seen in extreme ultraviolet (EUV) and soft X-ray (SXR), i.e., below 200 nm \citep{Nei_1989,neidig93,kretzschmar11}.
-Although the energy content in hard X-ray (HXR) is a tiny fraction of the total energy budget, they are still crucial in understanding the energization process \citep{holeman11}.
-However, to develop a comprehensive understanding of solar flares, it is mandatory to perform multi-wavelength studies of all kinds of flares.
-This may have implications on the physics of the origin of solar flares and different physics processes and contribute to the solar spectral irradiance as a function of the solar activity cycle.
-Although we have been observing Sun and Solar flares in various wavelengths, the spectral energy distribution of the radiated energy from the flares is still very poorly understood.
-The first solar flares were observed from the ground in the visible domain \citep{carrington1859,neidig93}.
-It is also well known that the flare emission in the visible domain occurs mainly in $H\alpha$ and Ca \Romannum{2} lines \citep{canfield90,falchi92,heinzel94}.
-However, the lesser understood component of the visible and Near Ultra Violet (NUV) emission is the enhancement of the continuum.
-The study of the white-light (WL) flares has proven to be very difficult because they have a very short duration and low contrast against the background, making their observation from Earth rare and of poor quality.
-Also, the flares in NUV are not observable from any ground-based instrumentation as most of the NUV gets absorbed in the upper atmosphere, thus requires space-based observations.
+The  \ion{Mg}{2} k and h lines represent transitions to the ground state from finely split upper levels ($3p~^{2}P_{\nicefrac{3}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$ and $3p ^{2}P_{\nicefrac{1}{2}}${--}$3s^{2}S_{\nicefrac{1}{2}}$), resulting in optically thick lines at wavelengths 2796.34~{\AA} ( \ion{Mg}{2} k) and 2803.52{\AA} ( \ion{Mg}{2} h).
+It has been suggested that the intensity ratios of these lines can offer insights into the optical depth of the local environment \citep{kerr15}.
 
-The origin of the WLFs, i.e., the physical process responsible for generating the continuum and its contribution to the overall energy distribution, is still highly uncertain.
-The question remains whether WLFs are photospheric phenomena due to $H^{-}$ free-free emission or chromospheric phenomena due to H free-bound emission.
-The more recent studies further constrain the origin of the WLFs to be Chromospheric phenomena, as it has been shown that the WL and HXR footpoint centroids are cospatial.
-Similarly, \cite{krucker15} constrained the cospatial WL and HXR footpoints within the chromosphere for three flares.
-With the help of SUIT, we would be able to localize the WL flares and resolve them on various parts of the Solar disk, which along with observations from Interface Region Imaging Telescope (IRIS), Helioseismic and Magnetic Imager (HMI), would help us localize the source of the WL footpoints and also comment on the formation mechanism of the WL itself.
+The integrated intensity of a line transitioning from an upper level $j$ to a lower level $i$ depends on the collision strength $\Omega_{ij}$ for that transition, given by~\citep{henri62,mariska92},
 
-\begin{figure}
+%%---------------------------------------------------------------
+\begin{equation*}
+\Omega_{ij}=\frac{8\pi}{\sqrt{3}}~\frac{I_{H}}{\Delta \epsilon_{ij}}g\omega_{i}~f_{ij}
+\end{equation*}
+%%---------------------------------------------------------------
+
+\noindent Here, $I_{H}$ denotes the ionization energy of hydrogen, $\Delta \epsilon_{ij}$ represents the threshold energy for the transition, $g$ is the Gaunt factor, $\omega_{i}$ is the statistical weight of the level, and $f_{ij}$ stands for the oscillator strength.
+In optically thin conditions, the intensity ratio of the k to h line equals the ratio of collision strengths, as the escape probability of photons is unity.
+As the  \ion{Mg}{2} k and h lines share the same ionization state and originate from a transition to a shared lower level, and given that the statistical weight ($\omega_{i}$) is the same in both cases, the line intensity ratio is simply the ratio of oscillator strengths ($f_{ij}$).
+Consequently, this ratio is expected to be 2:1 in optically thin conditions and lower when the medium is optically thick \citep{kerr15,levens19}.
+
+Moreover, the  \ion{Mg}{2} k and h lines can serve to estimate velocity in the middle and upper chromosphere, chromospheric velocity gradients, and temperature in the middle chromosphere \citep{leenarts13a,leenarts13b,pereira13}.
+Emission from the  \ion{Mg}{2} triplets can help identify heating in the lower chromosphere \citep{pereira15}.
+Various studies have demonstrated spatial variations in  \ion{Mg}{2} line profiles \citep{dalda23,panos18}.
+For instance, \cite{polito23} associated the leading edge of flare ribbons with enhanced broadening and strong central reversal, interpreting this difference in profile as indicative of distinct heating mechanisms at different locations within flare ribbons.
+Similarly, \cite{panos21,panos21_2} revealed differences in line profiles and energy input.
+
+Using observations recorded by the OSO-8 LPSP instrument, \citep{lemaire84} investigated the evolution of intensity ratios of  \ion{Mg}{2} h \& k, \ion{Ca}{2} h \& k, and Ly$\alpha$ \&~$\beta$ lines.
+They observed that the intensity ratio of the \ion{Ca}{2}~k/h lines increased from 1 to 1.2 during the ascending phase of a flare and returned to 1 during later phases.
+This correlated temporal behavior across various elements was interpreted as an indication of downward energy propagation, suggesting a potential decrease in opacity due to localized heating at the formation height of the \ion{Ca}{2} line during the flare's rise phase.
+
+Here, we investigate the evolution of intensity ratios of the  \ion{Mg}{2} h \& k lines during three flares: C-class, M-class, and X-class.
+Specifically, we focus on the dependence of line ratios on the underlying magnetic field strength, a relationship that, to our knowledge, has not been explored previously.
+The remainder of this chapter is organized as follows.
+Section \ref{sec:obs} presents the observations utilized in this study, followed by our data reduction and analysis methods, and the results in Section \ref{sec:dar}.
+
+%%----------------------------------------------------
+\section{Observations} \label{sec:obs}
+%%----------------------------------------------------
+%%-------------------------------------------------------
+\begin{table*}[ht!]
 \centering
-    \includegraphics[width = \linewidth]{Figures/Krucker_2015_ApJ_802_19_page-0004.jpg}
-    \caption{X-ray and optical imaging of the three flares at the peak time of the impulsive phase: the images are from HMI with the pre-flare image subtracted.
-The contours represent RHESSI Clean maps in the thermal (red, 12–15 keV) and non-thermal (blue, 30–80 keV) HXR range \citep{krucker15}.}
-    \label{fig1}
-\end{figure}
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+Event & Flare & Flare & Raster & Raster Step & Raster \\
+Date & Peak (UT) & Location (arcsec) & Details & (arcsec) & Cadence (s)\\
+\hline
+Nov 4, 2015  & 13:52 & [37",61"] & Coarse & 2" & 50\\
+(M-class) & & & 16-step  & & \\
+ & & & & & \\
+Oct 22, 2014 & 14:28 & [-292",-302"] & Coarse & 2" & 131\\
+(X-class) & & & 8-step  & & \\
+ & & & & & \\
+Feb 3, 2015 & 22:55 & [198",213"] & Dense & 0.35" & 33\\
+(C-class) & & & 16-step  & & \\
+\hline
+\end{tabular}%}
+%\end{center}
+\caption{List of flares studied in this chapter.}
+\label{tab:my_label}
+\end{table*}
+%%-------------------------------------------------------
 
-The spectral energy distribution of flares is one of the critical areas of interest in the physics of flares.
-A complete understanding of this will help us decode the physical processes involved in solar flares and help quantify their effects on solar spectral irradiance.
-Ideally, it would be essential to observe flares at all wavelengths simultaneously with sufficient spatiotemporal resolution to figure out the spectral energy distribution of flares.
-Unfortunately, this is generally not the case, and we have to rely on the sporadic observations made using ground-based instruments in the visible domain.
-As mentioned earlier, the majority of the flare energy is emitted in the NUV and visible domain.
-\cite{kretzschmar10,kretzschmar11}, performed statistical studies using a large number of flare observations across a wide energy range.
-They demonstrated, at the peak of the flare, about 70\% of the total energy was radiated in the continuum visible and NUV channel as illustrated in \ref{tab1}.
-SUIT would observe and resolve the solar flares within 200-400 nm using 8 NBs and 3 BBs.
-This, along with IRIS data, would help us comment on the energy distribution of flares of various classes.
+For this study, we selected three flares of M, X, and C classes, as listed in Table~\ref{tab:my_label} by IRIS.
+IRIS is a NASA small explorer-class solar observation satellite that obtains UV spectra with high spatial (0.33{--}0.4\arcsec per pixel), temporal (1s), and spectral resolution ($\sim$26 and $\sim$53~m{\AA}).
+The primary lines regularly observed by IRIS include \ion{C}{2},  \ion{Mg}{2}, and \ion{Si}{4}.
+In the imaging channel, it typically observes in  \ion{Mg}{2} and \ion{Si}{4}.
+In our study, we utilized observations recorded in the  \ion{Mg}{2} h\& k lines.
 
-%%--------------------------------------------%%
-\begin{table}[]
+As mentioned earlier, this study aims to analyze the evolution of intensity ratios concerning magnetic flux density during the flares of various classes.
+To achieve this, we incorporated line-of-sight (LOS) magnetic field measurements from the Helioseismic and Magnetic Imager \citep[HMI;][]{hmi} on the Solar Dynamics Observatory \citep[SDO;][]{sdo}.
+We utilized observations taken at 1600~{\AA} by the Atmospheric Imaging Assembly \citep[AIA;][]{aia}, also onboard SDO, to co-align the IRIS observations with those from AIA and subsequently HMI.
+
+%%----------------------------------------------------
+\section{Data analysis and results} \label{sec:dar}
+%%----------------------------------------------------
+\subsection{M3.7 Flare Observed on Nov 4, 2015}
+%%%----------------------------------------------
+%%--------------------------------------------------
+
+NOAA AR 12443 generated a multi-ribbon GOES class M3.7 flare on November 4, 2015, which commenced around 13:31 UT and peaked at approximately 13:52 UT, as observed from the GOES Soft X-ray (SXR) 1{--}8~{\AA} flux (Fig.\ref{flare1}a).
+This event occurred at approximately [37\arcsec,61\arcsec] heliographic position and was extensively observed by IRIS, AIA, and HMI.
+Fig.\ref{flare1}a illustrates the GOES flux plot of the flare in the 0.5{--}4~{\AA} range (blue) and the 1.0{--}8.0~{\AA} range (red).
+Fig.\ref{flare1} b depicts AIA 1600{\AA} image of the flaring region, showing two ribbons indicated by arrows.
+In panel (c), we present the line-of-sight (LOS) magnetic flux density map obtained from HMI, recorded nearly simultaneously with the AIA image shown in panel (b).
+The white (black) box overlaid on Fig.\ref{flare1}(b) (c) represents the IRIS SJI (Slit-Jaw Imager) field of view (FOV).
+The white dot-dashed (magenta dashed) box in Fig.\ref{flare1}b (c) indicates the IRIS raster FOV.
+The FOV of the SJI (approximately [120\arcsec~$\times$119\arcsec]) covers the central part of the flaring region, with a spectral sampling of approximately 0.05~{\AA}/pixel.
+\cite{li17} investigated the dynamics of the ribbons for this flare, while \cite{karlick18} studied the associated radio bursts.
+
+%%--------------------------------------------------
+\begin{figure*}[ht!]
     \centering
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{||m{.1\linewidth}|m{.15\linewidth}|m{.17\linewidth}|m{.17\linewidth}|m{.17\linewidth}|m{.15\linewidth}||}
-    \hline
-    \hline
-        Mean X-ray class & TSI(ergs) & Ratio $\frac{26-34nm}{TSI}$ & Ratio $\frac{0-50nm}{TSI}$ & Ratio $\frac{0.1-0.8nm}{TSI}$ & Ratio $\frac{continuum}{TSI}$\\
-        \hline
-        X3.2 & 5.9$\times~10^{31}$ & 0.9-0.8\% & 12-9\% & 1.2-1\% & 67\% \\
-        M9.1 & 1.6$\times~10^{31}$ & 1.7-0.4\% & 23-5\% & 1-0.4\% & 85\% \\
-        M4.2 & 1.3$\times~10^{31}$ & 2.2-0.5\% & 18-6\% & 0.6-0.3\% & 74\% \\
-        M2.0 & 5.1$\times~10^{30}$ & 1.7-0.6\% & 18-6\% & 0.7-0.4\% & 69\% \\
-        C8.7 & 3.6$\times~10^{30}$ & 1.5-0.5\% & 16-5\% & 0.4-0.2\% & 72\% \\
-        \hline
-    \end{tabular}}
-    \caption{Spectral Energy Distribution from a sample of 2100 flares across various wavelengths\citep{kretzschmar11}.}
-    \label{tab1}
-\end{table}
-%%--------------------------------------------%%
+\includegraphics[trim={7cm 5cm 7.7cm 6cm},clip,width=\textwidth]{Figures/Flare_M_Nov04_2015_2.eps}
+\caption{The M3.7 flare observed on November 4th, 2015.
+Panel a: GOES flux plot in 0.5{--}4~{\AA} (blue) and 1.0{--}8.0~{\AA} (red).
+Panel b: AIA 1600~{\AA} image of the flaring region.
+Arrows locate the primary ribbons.
+Panel c: LOS magnetic flux density map obtained from HMI near the peak of the flare.
+The over-plotted white (black) boxes in panel b (c) represent the IRIS SJI FOV.
+The over-plotted white dot-dashed (magenta dashed) box in panel b (c) shows the IRIS raster FOV.}\label{flare1}
+\end{figure*}
+%%--------------------------------------------------
 
-Finally, one of the major question of interest is how the Solar flares affect the Spectral Solar Irradiance (SSI) and Total Solar Irradiance (TSI) variability from a short to much longer, Solar Cycle timescale.
-\cite{kretzschmar10,kretzschmar11} performed statistical studies using a large number of flare observations across a wide energy range.
-For this purpose, they used the full Sun observations of Solar flux from Solar and Heliospheric Observatory (SoHO), three visible Solar irradiances from VIRGO/Solar Photometer (SPM) passbands centred on 402 nm, 500 nm, and 862 nm, respectively, from 1996 to 2008.
-Additionally, they also use the EUV irradiance in the ranges 0.1-50 nm and 26-34 nm measured by SOHO/Solar EUV Monitor \citep{judge98} and SXR measurements from GOES satellites.
-They showed that stacked TSI variation profiles during solar flares show variation at more than 2 sigma level during the peak flare time, indicating the presence of flare signals in the TSI measurements.
+Figure~\ref{flare_m_ev} illustrates the evolution of the flare in AIA 304~{\AA}.
+The flare is connected with a pre-existing filament that undergoes an eruption, splitting into two structures denoted as F1 \& F2 in Fig.\ref{flare_m_ev}(b) \& (c).
+These two filament structures diverge from each other in opposite directions.
+The flare generates two primary flare ribbons, labeled as R1 \& R2 in Fig.\ref{flare_m_ev}(b), (c) \& (d).
+Starting around 13:32 UT, R1 travels southeastward, crossing the IRIS raster FOV, indicated by the white dotted box in Fig.\ref{flare_m_ev}(a), (b), (c) \& (d).
+The IRIS raster monitors the movement of the northern ribbon R1 and the eastern edge of R2.
+An animated version of Fig.\ref{flare_m_ev} is available in the online journal for further details.
 
+%%%--------------
+\begin{figure*}[ht!]
+    \begin{center}
+    \includegraphics[width=\textwidth]{Figures/nov_flare_304_aa_evolv.eps}
+    \end{center}
+    \caption{Sequence of AIA 304~{\AA}~images for the Nov 4th, 2015 flare.
+The white dotted box shows the portion of the IRIS raster FOV which scanned the ribbons.
+In panels b (c) F1 and F2 are the filament material, which move away from each other as the flare progresses.
+R1 and R2 in b (c,d) show the primary ribbons which move through the IRIS raster FOV.
+An animation of this image sequence is available in \cite{roy24}.}
+    \label{flare_m_ev}
+\end{figure*}
+%%%--------------
+
+Fig.\ref{flare_m_aia} presents the same region as depicted in Fig.\ref{flare_m_ev} across the six coronal channels (i.e., 94, 131, 171, 193, 211, 335~{\AA}) of SDO/AIA, recorded at the peak (top two rows) and during the decline phase (bottom two rows) of the flare.
+Post-eruption arcades \citep[][]{TriBC_2004} are clearly observable in all the channels, displaying slightly varied morphologies.
+These arcades contain evaporated thermal plasma and exhibit loop top brightening, likely due to colliding evaporation flows \citep[see, e.g.,][]{sharma16, patsourakos04}.
+
+%%%--------------
+\begin{figure*}[ht!]
+    \begin{center}
+        \includegraphics[trim={4.5cm 5.5cm 6cm 4cm},clip,width=0.9\textwidth]{Figures/nov_flare_aia_waves_2.pdf}
+    \end{center}
+    \caption{The Nov 4th, 2015 flare in the six Coronal channels of the SDO/AIA at the soft X-ray peak (panels (a)-(f)) and during the decline phase (panels (g)-(l)) of the flare.}
+    \label{flare_m_aia}
+\end{figure*}
+%%%--------------
+
+We begin by aligning the HMI observations with the IRIS observations using the 1600~{\AA} data recorded by AIA.
+Given that the observation involves an active region undergoing flaring, the magnetic field may also be rapidly changing \citep{wang02,dandan16,spirock02}.
+Therefore, we utilize a series of co-aligned full-disk maps from AIA and HMI to derive a rastered line-of-sight (LOS) map of magnetic flux density that precisely corresponds to the location and time of IRIS rasters.
+This procedure is outlined below.
+
+Initially, we align the AIA 1600~{\AA} observation with the HMI observation closest in time to the IRIS SJI (Slit-Jaw Imager) and raster observations.
+Using the `aia\_prep' tool available in the \textit{sswidl} distribution, we process the level 1 images to perform image registration and align AIA and HMI observations.
+Subsequently, we calculate the shift between AIA 1600~{\AA} and the SJI 1400~{\AA}.
+Using these calculated offsets, we co-align the magnetograms with the IRIS SJI 1400~{\AA} observations, given that the AIA 1600~{\AA} observation was already aligned with the HMI observations.
+We typically observe an offset of approximately $\sim$ 1.5\arcsec~between HMI and IRIS.
+These co-aligned HMI maps are then utilized to derive the rastered magnetograms, which can be directly compared with IRIS raster observations.
+
+For analyzing the properties of the  \ion{Mg}{2} lines, we fit a double Gaussian profile to both the k and h lines with a linear background symmetric about the line core.
+If excess emission is detected compared to the fitted background and line profile for wavelengths lower than 2792~{\AA} and in-between 2798~{\AA} to 2800~{\AA}, we infer the presence of  \ion{Mg}{2} triplets in emission.
+A single Gaussian profile is fitted to the excess emission.
+It's important to note that this approach may overlook the triplets unless the emission is sufficiently strong.
+However, this method serves our purpose since our primary objective is to characterize the  \ion{Mg}{2} k and h line profiles.
+
+Additionally, we exclude any pixels showing saturation in either of the lines.
+The uncertainty of the observed intensities is measured in DN (Data Numbers) using the method outlined in \S 2:1 of \cite{kerr15} and subsequently applied in the fitting procedure.
+The uncertainties of the fitted Gaussian profiles are incorporated while integrating the profile to obtain the uncertainty of the line intensities.
+
+%%%%-------------------------
 \begin{figure}[h!]
 \centering  
-    \includegraphics[width = \linewidth]{Figures/nphys1741_page-0002.jpg}
-    \caption{Averaged TSI variations during flares.
-The TSI time-series averages over four exclusive sets of solar flares of decreasing amplitude.
-The black and pink curves correspond respectively to the TSI measured by the PMOV6 and the DIARAD radiometers.
-The dashed lines correspond to the 95\% confidence levels, while the vertical line denotes the peak time of the flare \citep{kretzschmar10}.}
-    \label{fig2}
+\includegraphics[trim={7cm 5cm 6cm 10cm},width=0.8\textwidth]{Figures/m_flare_iris.pdf}
+\caption{Obtained images in  \ion{Mg}{2} h (panel a) and k (panel b) and corresponding co-aligned and artificially rastered HMI LOS magnetic field map (panel c) for the M3.7 flare observed on November 4th, 2015.
+The magenta and lime green contours on panel c show the contours of  \ion{Mg}{2}~h (panel a) and k (panel b) intensity.} \label{fig:aligned_raster}
 \end{figure}
+%%%%-------------------------
 
-This allows us to quantify the solar variability induced be solar flares of various timescales.
-With the help of SUIT, we would be able to localize the flare locations and study the change in SSI from the local environment in the 11 science filters.
-This information combined with TSI measurements can allow us to quantify the effect of flares of various energy scales on the TSI variability of the Sun.
-As, both the TSI and SSI variability directly or indirectly couples with various atmospheric parameters, we can also study the effect the flares have on them.
-For example, the Earth's atmospheric chemistry and composition respond to any changes in solar UV output in a very nonlinear fashion \citep{haigh07}.
-Since the number of flares also shows a change with solar activity, it is prudent to ask how much flares contribute to the solar spectral irradiance in NUV.
-This is particularly important because the irradiance in NUV plays a key role in heating the upper and middle layers of the Earth's atmosphere directly and their coupling with Stratosphere.
-It also directly influences the middle and lower atmosphere chemistry and composition via the Ozone-Oxygen cycle.
+%%%%%%%%%%%
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim={0cm 3cm 0.5cm 3cm},clip,width=\textwidth]{Figures/pix_fit.pdf}
+    \caption{Fit of the  \ion{Mg}{2} window for the pixel marked in northern ribbon (southern ribbon) in Fig.~\ref{fig:aligned_raster} in top panel (bottom panel) from various times during the evolution of the flare.
+}
+    \label{fig:pix_fit_ribbon}
+\end{figure*}
+%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Throughput model and imaging performance of SUIT}\label{sec:suit_imaging}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%-------------------------
+\begin{figure}[ht!]
+\centering  
+\includegraphics[trim={1.5cm 4cm 0.5cm 4cm},clip,width=0.8\textwidth]{Figures/m_flare_iris_pt2.pdf}
+\caption{The 1{--}8~{\AA} GOES light curve of the flare over-plotted with the time variation of  \ion{Mg}{2} k/h line intensity ratio for the northern (black) and southern (green) asterisks marked in panels a, b \& c.}
+\label{fig:aligned_iris_ratio}
+\end{figure}
+%%%%-------------------------
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Filter Choice for SUIT}\label{sec:filter_choice}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In Figure~\ref{fig:aligned_raster}, we present intensity maps obtained in  \ion{Mg}{2} h \& k (panels a \& b) alongside the rastered line-of-sight (LOS) magnetic field map in panel (c).
+The dashed magenta and solid green contours on the magnetic field maps represent the intensity from panels a and b, respectively.
+To investigate the  \ion{Mg}{2} k to h intensity line ratios over time, we selected two pixels—one in the northern ribbon and another in the southern ribbon, as indicated by crosses.
+Fig.\ref{fig:pix_fit_ribbon} displays the spectra overlaid with fits for the two pixels taken in the northern ribbon (top panel) and southern ribbon (bottom panel) obtained at different times.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Photometric, Radiometric \& Spectral Calibration of SUIT}\label{sec:suit_cal}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We illustrate the  \ion{Mg}{2} k to h line intensity ratio derived from the two locations in the northern (black) and southern ribbons (green) in Fig.\ref{fig:aligned_iris_ratio}.
+Additionally, we overlay the GOES light curve of the flare obtained in 1.0{--}8.0{\AA} (red solid line).
+Our observations indicate that the intensity ratios exhibit a slightly increasing trend, albeit within the margin of errors, during the early phase of the flare.
+The ratio demonstrates a distinct peak around the midpoint of the impulsive phase, lasting for a very brief duration of approximately 150 seconds, before beginning to decrease.
+It's worth emphasizing that the pixel-by-pixel fitting of the  \ion{Mg}{2} h \& k line profiles provided a sufficient signature of the time evolution of the k/h line intensity ratio during the flare.
 
-%NOTE THE LACK OF A BIBLIOGRAPHY CALL IN THIS FILE. BIBLIOGRAPHY WORK HAPPENS OUTSIDE THE CHAPTER TEX FILES.
+%%%%%%%--------%%%%%%%%%%%
+\subsection{Investigating the dependence on the local magnetic field in the  \ion{Mg}{2} lines}
+%%%%%%%---------%%%%%%%%%%
+
+To explore the time evolution of the intensity ratio and its potential relationship with the photospheric magnetic field, we binned the spectra into various magnetic field bins from different flaring pixels.
+We selected the flaring pixels based on an intensity threshold relative to the peak intensity observed in IRIS rasters.
+A double Gaussian fit with a constant background was performed in a smaller wavelength window for both the  \ion{Mg}{2} h and k lines separately.
+This step was essentially carried out to mitigate the effects of the background and potential contributions from other spectral features.
+
+Fig.~\ref{fig:fit_pix_fov} displays the  \ion{Mg}{2} k line profiles obtained at different times and averaged over different magnetic field bins.
+Each plot denotes the observation time and the magnetic field strength over which the spectra were averaged and fitted with a double Gaussian.
+Line intensities were computed by integrating the fitted Gaussian.
+
+In Fig.~\ref{fig:optical_depth_m}, we present the k to h intensity ratios obtained in various bins of magnetic flux density at different times corresponding to different flare phases.
+The curve corresponding to 13:07:05 UT (red) represents the pre-flare phase, where the ratio is approximately 1.2.
+The ratio shows an increase during the impulsive phase, i.e., the curves corresponding to 13:23:44 UT (blue dotted) and 13:32:04 UT (green dashed).
+The ratio measured at 13:41:11 UT (magenta dashed), which is closest to the UV peak of the flare, exhibits the largest value across all magnetic field bins.
+Subsequently, during the decline phase, the ratio measured at 13:57:23 UT (black solid) falls below the values observed during the pre-flare phase.
+Additionally, it's noteworthy that there are no significant differences among the k to h ratios obtained in different bins of magnetic flux density at all times (including pre-flare, impulsive, peak, and decline phases) of the flare.
+
+%%%%-----------------------
+\begin{figure*}[ht!]
+    \begin{center}
+    \includegraphics[trim={0cm 3cm 0cm 3cm},clip,width=\textwidth]{Figures/binned_fit_fov.pdf}
+    \end{center}
+    \caption{Fitted line profiles for the binned spectra for various magnetic field strengths from various times.}
+    \label{fig:fit_pix_fov}
+\end{figure*}
+%%%%-----------------------
+
+%%----------------------------------------------------------------------------
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={8cm 1cm 2cm 0.2cm},clip,width=0.9\textwidth]{Figures/Flare-m-optical-depth-2.jpeg}
+    \caption{ \ion{Mg}{2} k to h line intensity ratio for various magnetic flux density bins at various time steps during the evolution of the flare.}
+    \label{fig:optical_depth_m}
+\end{figure}
+%%----------------------------------------------------------------------------
+
+To explore further, we study the evolution of k to h intensity ratio as a function of time during the flare.
+In Fig.~\ref{fig:optical_dep_ev_m}, we plot the time evolution of the k to h line intensity ratio averaged within the bins of different magnetic flux densities as a function of time.
+For better visibility the 20.9{--}184.4 G and 348.9{--}513.3 G points are offset by 30s and -30s, respectively.
+We also plot the GOES 1{--}8~{\AA} light curve with the red solid line.
+These plots conspicuously reveal that the intensity ratios rise sharply during the impulsive phase, from $\sim$ 1.20 to $\sim$ 1.28 right before the soft X-ray flux peaks as seen from GOES, and decreases very rapidly thereafter, to lower than pre-flare values $\sim$ 1.12.
+The typical uncertainty value for the line intensity ratio is $\sim$ 0.02.
+We further note that the evolution of the  \ion{Mg}{2} k to h intensity ratio is remarkably similar across various strengths of magnetic flux densities.
+
+%%%----------------------------------------------
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim={3cm 3cm 2cm 4cm},clip,width=\textwidth]{Figures/Nov-11-2015-optical-dep-ev-5.pdf}
+    \caption{Time evolution of the  \ion{Mg}{2} k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin as labeled for the Nov 4, 2015 flare.
+For better visibility, the 20.9{--}184.4 G and 348.9{--}513.3 G points are offset by 30s and -30s respectively.
+Over-plotted red solid line displays the 1{--}8~{\AA} GOES X-ray light curve.}
+    \label{fig:optical_dep_ev_m}
+\end{figure*}
+%%%----------------------------------------------
+
+%%%----------------------------------------------
+\subsection{X1.6 Flare Observed on Oct 22, 2014}
+%%%----------------------------------------------
+
+An X~1.6 flare occurred on October 22, 2014, observed in AR 12192.
+The flare commenced at 14:02 UT and peaked at 14:28 UT as observed by GOES.
+Fig.\ref{flare2}(a) illustrates the GOES flux plot of the flare in the 0.5{--}4~{\AA} range (blue) and the 1.0{--}8.0~{\AA} range (red).
+Figs.\ref{flare2}(b) \& (c) display an AIA 1600{\AA} image and the line-of-sight (LOS) magnetic flux density map obtained from HMI, respectively.
+The overlaid boxes in panels (b) and (c) indicate the IRIS SJI (Slit-Jaw Imager) field of view (FOV).
+IRIS observed this flare with a large 8-step coarse raster covering a FOV of [14\arcsec,174\arcsec].
+It's worth noting that the IRIS SJI FOV and the slit direction were rotated by approximately 45$^\circ$ relative to the center of the HMI observation.
+
+%%--------------------------------------------------
+\begin{figure*}[ht!]
+    \centering
+\hspace*{-.5in}
+\includegraphics[width=\textwidth,trim={7cm 5cm 7.7cm 6cm},clip]{Figures/Flare_X_oct22_2014_2.eps}
+\caption{The X class flare observed on October 22, 2014.
+Panel a: GOES flux plot in 0.5{--}4~{\AA} (blue) and 1.0{--}8.0~{\AA} (red).
+Panel b: AIA 1600~{\AA} image taken at the peak of the flare.
+Arrows locate the primary and secondary ribbons.
+Panel c: LOS magnetic flux density map obtained from HMI at the peak of the flare.
+The over-plotted white (black) box in panel b (c) represents the IRIS SJI FOV, and white dot-dashed (dashed) box in panels b (c) represents the IRIS Raster FOV.}\label{flare2}
+\end{figure*}
+%%--------------------------------------------------
+
+The flare manifests two ribbons in AIA 1600{\AA}, as indicated by the arrows.
+The eastern ribbon extends around a negative field region and is entirely covered by the IRIS SJI FOV.
+Conversely, the western ribbon extends around a positive field region, with only a portion of it covered by the IRIS SJI FOV, as depicted in panel (b).
+In Fig.~\ref{fig:align_raster_flare2}, we present intensity maps obtained in  \ion{Mg}{2} h \& k (panels a \& b) alongside the rastered line-of-sight (LOS) magnetic field map (panel c).
+The black \& green dashed contours in the LOS magnetic field map (panel c) indicate the intensity contours of  \ion{Mg}{2} h \& k (panels a \& b).
+
+%%--------------------------------------------------
+\begin{figure}[ht!]
+    \centering
+%    \hspace{2in}
+    \includegraphics[trim={6cm 3cm 6cm 3cm},clip,width=0.45\textwidth]{Figures/contour_paper_plot_oct28.pdf}
+    \includegraphics[trim={3cm 2cm 2cm 3cm},clip,width=0.45\textwidth]{Figures/Oct-22-2014-optical-dep-ev-2.pdf}
+    \caption{Obtained intensity maps in  \ion{Mg}{2}~k (panel a) and h (panel b) lines at the peak of the flare.
+The rastrered HMI LOS magnetic field density map is shown in panel c.
+The black and lime green contours on panel c show the contours of  \ion{Mg}{2}~k (panel a) and h (panel b) intensity.}
+\label{fig:align_raster_flare2}
+\end{figure}
+%%--------------------------------------------------
+
+Similar to the M-class flare studied in the previous section, we derive the  \ion{Mg}{2} k to h line intensity ratio for various bins of the magnetic flux density within the flaring region and study their time evolution.
+In Fig.\ref{fig:align_raster_flare2} right panel, we plot the intensity ratio in black and magenta colors for two different magnetic field bins.
+In the same panel, we also overlay the 1{--}8~{\AA} GOES light curve (red solid line).
+We note that, unlike the M-class flare, we do not observe any noticeable change in the intensity ratio during the flare.
+There are approximately two to three data points showing an enhancement in the ratio, but these occur well before the onset of the flare.
+
+%%%----------------------------------------------
+\subsection{C3.5 Flare Observed on Feb 03, 2015}
+%%%----------------------------------------------
+
+On February 3, 2015, AR 12277 generated a C-class flare that peaked at 22:55 UT.
+Fig.\ref{flare3} depicts the GOES flux plot of the flare in the 0.5{--}4{\AA} range (blue) and the 1.0{--}8.0~{\AA} range (red) in panel (a).
+Fig.\ref{flare3}(b) \& (c) displays an AIA 1600{\AA} image and the line-of-sight (LOS) magnetic flux density map obtained from HMI, respectively, recorded near the peak of the flare.
+
+The overlaid white (black) box in panel (b) ((c)) indicates the IRIS SJI (Slit-Jaw Imager) field of view (FOV).
+The over-plotted white dot-dashed (magenta dashed) box in panel (b) ((c)) indicates the IRIS raster FOV.
+IRIS observed this flare with a large dense 16-step raster with a FOV of 5"$\times$119" and a step size of 0.35\arcsec.
+The flare exhibits a double ribbon structure, with the east ribbon elongating earlier and merging into the west ribbon.
+The IRIS raster scans through the west edge of the west ribbon through its eruption and merging with the east ribbon.
+Fig.~\ref{fig:align_raster_flare3} displays the intensity maps obtained in  \ion{Mg}{2} h \& k (panels a \& b).
+The rastered LOS magnetic field map is shown in panel (c).
+The black \& green dashed contours in the LOS magnetic field map (panel c) depict the intensity contours of  \ion{Mg}{2} h \& k (panels a \& b).
+
+%%--------------------------------------------------
+\begin{figure*}[ht!]
+    \centering
+\hspace*{-.6in}
+\includegraphics[width=1.12\textwidth,trim={7cm 5cm 7.7cm 6cm},clip]{Figures/Flare_C_feb03_2015_2.eps}
+%\includegraphics[width=.7\textwidth]{figures/Feb_03_2015/Feb-04-2015-optical-dep-ev-2.eps}
+\caption{The C class flare observed on February 3rd, 2015.
+Panel a: GOES flux plot in 0.5{--}4~{\AA} (blue) and 1.0{--}8.0~{\AA} (red).
+Panel b: AIA 1600~{\AA} image of the flaring region.
+Panel c: LOS magnetic flux density map obtained from HMI near the peak of the flare.
+The over-plotted white (black) boxes in panel b (c) represents the IRIS SJI FOV.
+The over-plotted white dot-dashed (magenta dashed) box in panel b (c) show the IRIS raster FOV.}\label{flare3}
+\end{figure*}
+%%--------------------------------------------------
+
+%%--------------------------------------------------
+\begin{figure}[ht!]
+    \centering
+%\hspace*{-1.in}
+\includegraphics[width=0.5\textwidth,trim={4cm 5cm 4cm 4cm},clip]{Figures/contour_paper_plot_feb-03-2015.pdf}
+\caption{Obtained intensity maps in  \ion{Mg}{2}~k (panel a) and h (panel b) lines at the peak of the flare.
+The rastrered HMI LOS magnetic field density map is shown in panel c.
+The black and lime green contours on panel c show the contours of  \ion{Mg}{2}~k (panel a) and h (panel b) intensity.}
+\label{fig:align_raster_flare3}
+\end{figure}
+%%--------------------------------------------------
+
+%%--------------------------------------------------
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={2cm 3cm 2cm 3cm},clip,width=0.8\textwidth]{Figures/Feb-04-2015-optical-dep-ev-2.pdf}
+    \caption{Time evolution of the  \ion{Mg}{2} k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin as labeled for the Feb 3, 2015 flare.
+Over-plotted red solid line displays the 1{--}8~{\AA} GOES X-ray light curve.}
+    \label{fig:optical_dep_ev_c}
+\end{figure}
+%%--------------------------------------------------
+
+We present the GOES 1{--}8~{\AA}light curve (red solid line) alongside the time evolution of the  \ion{Mg}{2} k to h line intensity ratio averaged within the bins of two different magnetic flux densities as a function of time in Fig.\ref{fig:optical_dep_ev_c}.
+The  \ion{Mg}{2} k to h line intensity ratio exhibits a similar variation as observed in the M-class flare.
+It peaks during the impulsive phase (k/h$\sim$ 1.12) and decreases to preflare values (k/h$\sim$ 1.09) during the decay phase of the flare, coinciding with the peak of the GOES light curve.
+It's worth noting that the change in the  \ion{Mg}{2} k to h line intensity ratio is less pronounced for this flare compared to the M-class event.
+However, we also observe that the ratio shows a persistent increase from the onset of the flare.
+
+%%--------------------------------------------------
+\section{Outlook}
+%%--------------------------------------------------
+
+The  \ion{Mg}{2}~k to h line intensity ratios serve as a valuable diagnostic for assessing the opacity of the local plasma and can provide insights into changes in the local plasma environment within the solar chromosphere during flares.
+In this study, we investigated the temporal variation of  \ion{Mg}{2}k to h line intensity ratios during the evolution of three flares classified as X-class, M-class, and C-class.
+We also examined the variation of intensity ratios across different magnetic flux density bins, utilizing observations from IRIS and HMI.
+Co-alignment of IRIS and HMI observations was achieved using 1600{\AA} images recorded by AIA.
+
+It's well-documented that  \ion{Mg}{2} profiles exhibit significant spatial variations within flaring regions \citep{dalda23,panos18}.
+As we binned the IRIS observations based on magnetic field strength, it's important to note that any spatial variation is averaged out and not addressed in our analysis.
+
+Our findings reveal that  \ion{Mg}{2} k to h line intensity ratios undergo changes during flares.
+For M-class and C-class flares, the ratio starts increasing at the onset of the flare, peaks roughly halfway through the impulsive phase, and then steeply declines thereafter (see Figs.\ref{fig:optical_dep_ev_m} \& \ref{fig:optical_dep_ev_c}).
+Moreover, the ratios drop even below pre-flare levels during the later stages of the flare (peak and decline phase).
+However, this behavior is observed only in M and C-class flares, not in X-class flares.
+
+Our observations did not reveal any correlation between line intensity ratios and magnetic flux density.
+The line intensity ratios for different magnetic field strengths illustrated in Figs.\ref{fig:optical_depth_m},\ref{fig:optical_dep_ev_m},~\ref{fig:optical_dep_ev_c} indicate a consistent behavior from weak to strong magnetic field strengths.
+This suggests that the magnetic field similarly affects both  \ion{Mg}{2}~k and h lines, and such effects cancel out when taking the ratios.
+
+\cite{kerr15} studied  \ion{Mg}{2}~k to h line intensity ratios and their temporal variation for individual pixels in both quiet Sun regions and flare locations.
+While no change in ratios was observed for the quiet Sun region, variations were noted in flaring pixels, suggesting possible differences in heating conditions between non-flaring and flaring atmospheres.
+However, no correlated change in the ratio with respect to the flare light curve was observed.
+
+Our results align with those of \cite{kerr15}, wherein they also observe the highest change in the ratio during the impulsive phase of the flare, decreasing before the flare reaches its maximum in GOES 1{--}8~{\AA} observations.
+Such variations in the ratio may indicate changes in the optical depth of the local medium.
+During the impulsive phase, decreased optical depth might be attributed to localized heating and chromospheric evaporation, while during the decay phase, increased optical depth could be due to condensation and downflows.
+However, this interpretation remains speculative, particularly as we did not observe such effects in X-class flares.
+
+The results obtained for M-class and C-class flares can be explained by the aforementioned scenario, but the findings for X-class flares are more ambiguous.
+We couldn't establish a clear distinction in the general properties of these three flares.
+Notably, while the C-class flare is confined, both M and X flares are eruptive.
+Therefore, it's plausible that in X-class flares, energy deposition occurs more impulsively and on a shorter timescale than can be sampled.
+This high impulsiveness may lead to a greater degree of ionization of the medium compared to the other two flares, as supported by the large number of saturated pixels in the data that were discarded.
+A more definitive conclusion would necessitate analysis of additional such flares, including numerical and theoretical modeling.
+
+The SUIT has four separate narrow band filters for the Mg window, namely NB2 (Blue wing of  \ion{Mg}{2} k), NB3 ( \ion{Mg}{2} k), NB4 ( \ion{Mg}{2} h) and NB5 (Red wing of  \ion{Mg}{2} h).
+As mentioned in chapter \ref{c:chap2} SUIT observes the full-disk Sun continuously in NB4 with $\sim$ 1 minute cadence and full-disk observations in all eleven science filters every 90 minutes.
+With the full disk observations in all science filters, we can investigate the opacity variations continuously across various solar features with a cadence of 90 minutes with the NB3 and NB4 ratio.
+In flare mode, the observing filter sequence is customizable.
+With high cadence observations in NB3 and NB4, we can investigate the effect of flare heating on the local plasma environment via its manifestation in opacity.

### 2024-07-22 chapter6/ms.tex
Updates from Overleaf

--- 2024-02-14 chapter6/ms.tex
@@
-%\begin{abstract}
-
- %   The \ion{Mg}{2}~k \& h line intensity ratios can be used to probe the characteristics of the plasma in the solar atmosphere.
-In this study, using the observations recorded by the Interface Region Imaging Spectrometer (IRIS), we study the variation of the \ion{Mg}{2}~k \& h intensity ratio for three flares belonging to X-class, M-class, and C-class, throughout their evolution.
-We also study the k-to-h intensity ratio as a function of magnetic flux density obtained from the line-of-sight magnetograms recorded by the Helioseismic and Magnetic Imager (HMI) on board the Solar Dynamics Observatory (SDO).
-Our results reveal that while the intensity ratios are independent of magnetic flux density, they show significant changes during the evolution of the C-class and M-class flares.
-The intensity ratios start to increase at the start of the flare and peak during the impulsive phase before the flare peak and decrease rapidly thereafter.
-The values of the ratios fall even below the pre-flare level during the peak and decline phases of the flare.
-These results are important in the light of heating and cooling of localized plasma and provide further constraint on the understanding of flare physics.
-
-%\end{abstract}
+\justifying
 
@@
 
-Solar flares are the most energetic events on the Sun, where an enormous amount of magnetic free energy is released due to the reconfiguration of the coronal magnetic field.
-The released energy can cause particle acceleration, heating and flows in the solar atmosphere and a transient enhancement in solar radiative output.
-It is observed that most of the energy radiated in flares originates from the dense chromosphere \citep{fletcher10,milligan14}.
-Hence, studying the chromospheric lines during flares provides us with diagnostics, which may be important for understanding the physics of solar flares and their effect on the local plasma environment.
+Solar flares are the largest magnetic events within our solar system.
+They are characterized by the sudden release of magnetic energy, leading to localized, transient heating of coronal plasma to temperatures exceeding approximately 10 million Kelvin (MK), significantly hotter than the surrounding coronal plasma at around 1 MK.
+Flares are typically identified by the peak soft X-ray flux observed by the X-Ray Sensor onboard the Geostationary Operational Environmental Satellites (GOES/XRS), often referred to as the "GOES class" \citep{xrs}.
+Flares classified as GOES class C and above typically heat the coronal plasma to temperatures ranging from 5 to 20 MK.
+These observations, which integrate over the entire solar disk, are commonly used to characterize the average physical properties of flare plasma.
 
-The chromosphere emits in various UltraViolet(UV) and optical lines.
-While many optical lines, e.g., H$\alpha$, \ion{Ca}{2}, are routinely observed from ground-based telescopes, observations in the \ion{Mg}{2} resonance lines have been rare in the past.
-Since the launch of the Interface Region Imaging Spectrograph \citep[IRIS;][]{IRIS} we have been in the position to monitor these lines regularly with excellent spatial and spectral resolution.
+It is widely acknowledged that active regions possess sufficient magnetic free energy to trigger flares and associated Coronal Mass Ejections (CMEs) \citep{emslie12, ash17}.
+The high temperatures observed in flare-induced coronal plasma are often attributed to the evaporation of chromospheric material, heated by the collisions of flare-accelerated electrons during the impulsive phase \citep{fletcher11}.
+However, there is also evidence suggesting that plasma may be directly heated within the corona in certain cases \citep[e.g.,][]{longcope11, reeves17}.
 
-The \ion{Mg}{2}~k and h lines are transitions to the ground state from a finely split pair of upper levels ($3p~^{2}P_{\nicefrac{3}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$ and $3p ^{2}P_{\nicefrac{1}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$).
-These transitions create the optically thick lines in the wavelengths 2796.34~{\AA} (\ion{Mg}{2}~k) and 2803.52~{\AA} (\ion{Mg}{2}~h).
-It is suggested that the intensity ratios of these lines can be used to probe the optical depth of the local environment \citep{kerr15}.
+Numerous studies \citep{stosire07, emslie12, inglis14, warmuth16a, warmuth16b, ash17} have examined the partition between thermal and non-thermal energies in flares, aiming to shed light on the underlying physical processes.
+However, the results have been inconclusive, and there is currently no consensus regarding whether non-thermal energetic electrons possess sufficient energy to account for the observed thermal energy component in smaller flares.
 
-The integrated intensity of a line transitioning from an upper-level j to a lower-level i, is dependent on the collision strength for that transition $\Omega_{ij}$, which is given by~\citep{henri62,mariska92},
+These studies typically utilize peak thermal energy as a representation of the overall thermal output of flares.
+Consequently, our comprehension of flare energetics has predominantly been shaped by statistical analyses of bolometric output and peak thermal energy.
+While these metrics provide reasonable representations of the overall thermal output of flares, discerning subtle differences in heating mechanisms occurring at various stages of flares necessitates quantifying thermal energy as a function of time.
 
-%%---------------------------------------------------------------
-\begin{equation*}
-    \Omega_{ij}~=~\frac{8\pi}{\sqrt{3}}~\frac{I_{H}}{\Delta \epsilon_{ij}}~g~\omega_{i}~f_{ij}
-\end{equation*}
-%%---------------------------------------------------------------
+For instance, \citet{longcope11} proposed the existence of a super hot plasma component in some large solar flares, directly heated within the corona.
+Sustained temperatures observed in supra-arcade fans during flares have been attributed to phenomena such as supra-arcade downflows \citep[e.g.,][]{reeves17}, suppression of conduction by turbulence \citep[e.g.,][]{xie23}, or global compression from reconnection inflows \citep[e.g.,][]{reeves19}.
+These processes represent distinct mechanisms from chromospheric evaporation, characterized by the development of hard X-ray footpoints and increasing intensity of soft X-ray and EUV-emitting plasma as the loops fill.
 
-\noindent Where $I_{H}$ is the ionization energy of Hydrogen, $\Delta \epsilon_{ij}$ is the threshold energy for the transition, g is the Gaunt factor, $\omega_{i}$ is the statistical weight of the level and $f_{ij}$ is the oscillator strength.
-In optically thin conditions, the intensity ratio of the k to h line is the ratio of the collision strengths, as the escape probability of photon is unity.
-The \ion{Mg}{2} k and h lines share the same ionization state and originate from a transition to a shared lowered level.
-As the statistical weight ($\omega_{i}$) is same in both cases, the line intensity ratio is simply the ratio of the oscillator strengths($f_{ij}$).
-This implies the ratio is 2:1 in optically thin conditions, and lower when the medium is optically thick \citep{kerr15,levens19}.
+Several studies \citep{hilarie05, caspi10} have attempted to estimate thermal energy as a function of time. The thermal energy of flares is defined as:
+\begin{equation}
+\mathrm{U_{Th}~\simeq~3n_{e}k_{B}TV}f,
+\end{equation} \label{eq:t_eneg_1}
+where $\mathrm{n_{e}}$ is the electron number density of the flaring plasma, 'V' is the volume of the flaring plasma, 'f' is the volume filling factor, and 'T' is the instantaneous temperature.
+A key challenge in characterizing flare thermal energy lies in determining the volume.
 
-In addition, the \ion{Mg}{2} k and h lines can be used to estimate the velocity in the middle and upper chromosphere, the chromospheric velocity gradients, the temperature in the middle chromosphere \citep{leenarts13a,leenarts13b,pereira13}.
-The \ion{Mg}{2} triplets in emission can be used to identify heating in the lower chromosphere \citep{pereira15}.
-There have also been multiple studies that have shown a spatial variation of the \ion{Mg}{2} line profiles \citep{dalda23,panos18}.
-\cite{polito23} showed that the leading edge of the flare ribbon is associated with enhanced broadening and strong central reversal.
-They interpreted the difference in the profile as a difference in the heating mechanism at the leading edge and bright part of the flare ribbons.
-\cite{panos21,panos21_2} showed similar differences between the line profiles and energy input.
+\citet{li23} and \citet{zhang19} utilized soft X-ray emitting regions' $\frac{1}{e^{2}}$ contour or intensity threshold on AIA 131 {\AA} observations to estimate the flare area (A), subsequently inferring the volume as $V \sim A^{\frac{3}{2}}$.
+\citet{hilarie05} employed a similar method using RHESSI soft X-ray images to estimate the lower limit of volume, assuming a "perfect arc-shaped" loop.
+They also estimated the evolution of cumulative non-thermal energy injected by electrons, assuming a thick-target model \citep{brown71}, and fitting RHESSI spectra to determine non-thermal energies in time bins with significant emission above 25 keV.
+\citet{caspi10} utilized a 50\% intensity contour of cleaned RHESSI images to estimate the flare area, inferring volume assuming spherical symmetry.
 
-Using the observations recorded by the OSO-8 LPSP instrument, \citep{lemaire84} studied the evolution of the intensity ratio of \ion{Mg}{2}~h~\&~k, \ion{Ca}{2}~h~\&~k and Ly~$\alpha$~\&~$\beta$ lines.
-\cite{lemaire84} showed that the intensity ratio of the \ion{Ca}{2}~k/h lines increased from 1 to 1.2 during the ascending phase of a flare and returned to 1 during the later phases.
-The authors interpreted the correlated temporal behavior across various elements as an indication of downward energy propagation.
-We note that this may suggest a slight decrease in the opacity due to localized heating at the formation height of the \ion{Ca}{2} line during the rise phase of the flare.
+In all these cases, the assumption of symmetrical expansion proves useful, as thermal energy is estimated from spectra obtained by integrating multiple pixels.
+However, addressing the spatially varying multi-thermal nature of flaring plasma remains a challenge in these analyses.
+Determining the volume of the flaring plasma is a significant challenge in characterizing the thermal energy of flares.
+The filling factor `f' quantifies the fraction of the apparent volume filled with plasma of a specific temperature and may also account for geometric projection effects, representing the real volume projected into the observed apparent volume.
+Given the highly multi-thermal nature of flaring plasma and the rapidly changing volume during the flare's rise phase, defining a filling factor that accurately describes plasma volume evolution throughout the flare is challenging.
 
-%\sout{In spite of the excellent potential of these spectral lines in diagnosing the localized atmosphere, such} \sout{studies have not been taken up in detail due to the scarcity of spectral observations in these lines.}
+Here, we investigate the thermal energy evolution of two flares, an M-class and an X-class flare, utilizing existing tools and observations from various vantage points to improve the accuracy of estimating flaring plasma volume.
+We demonstrate that a more precise estimate of plasma volume impacts thermal energy estimates and has implications for the flare's energy budget.
+Additionally, we estimate the cumulative non-thermal energy deposited by non-thermal electrons and compare it with our thermal energy estimates.
 
-Here, we study the evolution of the intensities ratios of the \ion{Mg}{2}~h~\&~k lines during the course of the evolution of three flares, \textit{viz.}, C-class, M-Class and X-class.
-We focus on the the dependence of line ratios on the underlying magnetic field strength, which to our knowledge has not been explored so far.
-The rest of the paper is structured as follows.
-\S\ref{sec:obs} discusses the observations used in this paper.
-We discuss how we reduce and analyze the data and the results in \S\ref{sec:dar}.
+In Section \ref{sec:obs}, we detail the observations utilized in this study and describe our analysis approach.
+Section \ref{sec:therm} outlines our method for estimating thermal energy, while Sections \ref{sec:los} and \ref{sec:non-therm} discuss our techniques for volume estimation and cumulative non-thermal energy estimation, respectively.
+Finally, we present and discuss our results in Section \ref{res}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Observations and Data Analysis}\label{sec:obs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We investigate the two flares using EUV imaging from multiple instruments, including the Atmospheric Imaging Assembly onboard the Solar Dynamics Observatory \citep[SDO/AIA;][]{sdo,aia}, the Extreme Ultraviolet Imager onboard the Solar Terrestrial Relations Observatory-A \citep[STEREO-A/EUVI;][]{stereo,euvi}, and the Solar Ultraviolet Imager onboard GOES \citep[GOES/SUVI;][]{suvi}.
+Additionally, we utilize imaging data from the Spectrometer/Telescope for Imaging X-rays onboard Solar Orbiter \citep[SO/STIX;][]{so,stix,stix1}, the X-Ray Telescope onboard Hinode \citep[Hinode/XRT;][]{xrt}, and the X-Ray Sensor onboard GOES.
+The X and M class flares are observed at the disk center and limb of the Sun, respectively, from the perspective of AIA.
+
+The positions of various spacecraft relative to the flares' locations on the solar disk are illustrated in Figure \ref{fig:sc_pos}.
+Panel (a) displays the AIA 193 Å observation of the Oct 28, 2021 flare projected onto Heliographic Stonyhurst (HGS) coordinates, with the positions of SDO (magenta cross), SO (cyan circle), and STEREO-A (green triangle) marked with respect to the flare location.
+The flare is delineated by a white dotted circle.
+The relative separations between the spacecraft indicate differences in polar and azimuthal angles due to varying vantage points.
+Panel (b) presents the spacecraft positions projected onto the Heliocentric Inertial (HCI) frame for the same event, demonstrating differences in azimuthal angle and distance from the Sun's center.
+Similar plots for the Nov 29, 2021 flare are depicted in Panels (c) and (d), with EUVI 171 Å emission projected onto HGS and HCI coordinates, respectively.
+
+%%%%######%%%%%%
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim={1cm 0.5cm 1.2cm 0.5cm},clip,width=\textwidth]{flare_pos.pdf}
+    \caption{Position of various instruments during the flares.
+Panel a: AIA 193 {\AA} observation during the 2021 Oct 28 event projected to Heliographic Stonyhurst (HGS) coordinates.
+The position of the flare is marked with a white dotted circle.
+The positions of {\it Solar Orbiter}, {\it SDO} and {\it STEREO-A} are marked with an olive circle, magenta cross and green triangle, respectively.
+The positions of the spacecraft signify the difference in both the polar (vertical axis) and the azimuthal (horizontal axis) angle and do not mark the connectivity of the spacecraft to the solar surface.
+Panel b: The positions of the spacecrafts projected onto the Heliocentric Intertial (HCI) frame for the 2021 Oct 28 event.
+The difference between the spacecraft show the difference in the azimuthal angle.
+Panel c: {\it STEREO-A}/EUVI 171 {\AA} observation during the 2020 Nov 29 event projected to HGS coordinates.
+The position of the flare is marked with a white dotted circle.
+The positions of {\it SDO} and {\it STEREO-A} are marked with a magenta cross and green triangle, respectively.
+Panel d: The positions of the spacecraft projected onto the HCI frame for the 2020 Nov 29 event.}
+    \label{fig:sc_pos}
+\end{figure*}
+%%%%######%%%%%%
+
+The X1 flare occurred on Oct 28, 2021 (SOL2021-10-28T15:35) near approximately $\sim~[0\arcsec,-500\arcsec]$ solar coordinates as observed from AIA.
+It was captured by SDO/AIA, STEREO-A/EUVI, GOES/SUVI, XRT, GOES/XRS, and STIX.
+AIA provided observations with passbands at 94, 131, 193, 171, 211, and 335 Å, with a pixel size of approximately 0.6 arcseconds.
+SUVI provided similar wavelengths to AIA: 94, 131, 195, 171, 195, and 284 Å, with a pixel size of approximately 2.5 arcseconds.
+STEREO-A/EUVI offered imaging in 171, 195, and 284 Å coronal passbands.
+
+The flare exhibited a standard two-ribbon structure, along with a ridge at the top of the rising flare arcade \citep{longcope22}.
+The ridge, most prominently visible in the AIA 193 Å channel, was primarily created by the hotter \ion{Fe}{24} line (T~$\simeq$17 MK) and had a height of approximately $26~Mm$.
+This ridge was utilized to identify the loop-top in the AIA observation and calculate the loop height.
+
+STIX provided X-ray imaging and spectroscopy in the 4-150 keV range, with spectroscopic observations in 32 pre-defined energy channels.
+Fig.\ref{fig:flare}a depicts an AIA 193 Å image of the flare during the decay phase, while Fig.\ref{fig:flare}b overlays STIX intensity contours (15:27:40 {--} 15:28:00 UT) in the 4{--}16 keV (pink solid line) and 15{--}60 keV (blue solid lines) ranges on an AIA 1600 Å image during the rise phase.
+The MEM-GE algorithm was used to construct the STIX intensity maps.
+
+The M flare occurred on November 29, 2020, near approximately $[-950\arcsec,-430\arcsec]$ solar coordinates from the AIA perspective.
+In AIA images, the footpoints were occulted behind the limb.
+It was recorded by STEREO-A/EUVI, GOES/SUVI, Hinode/XRT, GOES/XRS, and Fermi/GBM.
+There were no STIX observations for this event.
+
+The flare exhibited a fan visible in the hot channels of AIA (131 and 193 Å) and the XRT channels.
+Fig.
+\ref{fig:flare2}a shows an AIA 131 Å image during the decay phase, while Fig.~\ref{fig:flare2}b displays an XRT Be-med filter observation taken near simultaneously with the AIA image.
+For the M-class event, Fermi observations were periodically eclipsed during the flare duration, rendering it challenging to estimate the cumulative non-thermal energy accurately.
+Hence, the estimation of cumulative non-thermal energy would not be a fair representation of the total non-thermal energy available.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Thermal Energy}\label{sec:therm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To estimate the thermal energy of the X-class event, we calculate the differential emission measure (DEM) of the flaring region using data from the six AIA passbands, including 94 Å (\ion{Fe}{10} $\sim$1.1 MK, \ion{Fe}{18} $\sim$7.1 MK), 131 Å (\ion{Fe}{8} $\sim$0.4 MK, \ion{Fe}{21} $\sim$11 MK), 171 Å (\ion{Fe}{9} $\sim$0.6 MK), 193 Å (\ion{Fe}{12} $\sim$1.6 MK, \ion{Fe}{24} $\sim$17 MK), 211 Å (\ion{Fe}{14} $\sim$2 MK), and 335 Å (\ion{Fe}{16} $\sim$2.5 MK) \citep{o'dwyer10,O'Dwyer12}.
+During the flare's peak, some AIA observations may be saturated, so we substitute SUVI observations, co-aligned and co-registered with AIA, for those specific frames.
+We bin AIA observations to the SUVI pixel size, ensuring consistency.
+Since the SUVI temperature response closely resembles that of AIA \citep{suvi}, we can utilize SUVI images for thermal energy estimates when necessary.
+In such cases, we also adjust the AIA temperature response functions to accommodate the binning of AIA data.
+Due to saturation, most of the XRT observations during the flare are not included in our analysis of this event.
+
+For the M-class event, we estimate the thermal energy using AIA and XRT observations.
+Here, we bin the AIA observations to the XRT pixel size, co-align them, and calculate the DEMs.
+As previously described, we rescale the AIA temperature response functions to accommodate the binning of AIA data.
+
+We employ the regularized inversion method \citep{hannah&kontar12} to calculate the DEMs, enabling us to derive the thermal energy estimates.
+We can calculate the EM and DEM weighted temperature using the methods discussed in chapter \ref{sec:c2_dem}.
+The temperature range of the integration are set to $5 < \log\,T < 7.4$.
+We calculate the emission measure and the DEM weighted temperature for all the pixels in the field of view (FOV).
+In Fig.~\ref{fig:flare}c \& d (\ref{fig:flare2}c \& d), we plot the DEM weighted temperature and emission measure in the temperature range 5.0$<$$\log\,T$$<$7.4, for the 2021 Oct 28 (2020 Nov 29) flare.
+
+We use the emission measure and DEM weighted temperature estimated from the inverted DEM in the thermal energy expression of Equation \ref{eq:t_eneg_1} and sum over the pixels in the FOV to estimate the thermal energy arising from the FOV.
+This procedure gives us,
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+    U_{Th}~=~\sum_{j}~\frac{3k_{B}A\sqrt{LOS_{j}}}{\sqrt{EM^{c}_{j}}}\int_{T}~DEM_{c}(T)_{j}T~dT
+    \label{eq:t_eneg}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+where $EM^{c}_{j}$ and $DEM_{c}(T)_{j}$ are the column emission measure and the column DEM in 5.0$<$$\log\,T$$<$7.4 for the j-th pixel in the FOV.
+We have used $n_{e}^{2}\times LOS~=EM_{c}$ and a filling factor $\textit{f}~=~1$.
+For the 2020 Nov 29 flare we mask the solar disk while calculating the DEMs and thermal energy.
+For our analysis, one of the major uncertainties in determining the emitting volume depends on determining the LOS for individual pixels in the FOV.
+
+%%--------------------------
+\begin{figure*}[ht!]
+    %\hspace{-1cm}
+    \includegraphics[width=0.9\textwidth,trim={2cm 5cm 3cm 3cm},clip]{oct28_align.pdf}
+    \caption{Panel (a): the flare arcade in AIA 193 {\AA}.
+Panel (b): STIX soft X-ray contours (4 {--} 16 keV, solid pink lines) and hard X-ray contours (16 {--} 50 keV, solid blue lines) aligned to AIA 1600 {\AA} and over plotted.
+Panel (c): the emission measure map of the region for $5~<log(T)~<7.4$.
+Panel (d): the DEM weighted temperature map of the region.}
+    \label{fig:flare}
+\end{figure*}
+%%--------------------------
+
+%%--------------------------
+\begin{figure*}[ht!]
+\centering
+    \includegraphics[trim={4.8cm 1.5cm 6cm 2.5cm},clip,width=0.9\textwidth]{nov_29_align.pdf}
+    \caption{Panel (a): the flare arcade in AIA 131 {\AA}.
+Panel (b): {\it Hinode}/XRT Be-Med soft X-ray image recorded almost at the same time.
+Panel (c):  the DEM weighted temperature map of the region for $5~<log(T)~<7.4$.
+Panel (d): the emission measure map of the region for $5~<log(T)~<7.4$}
+    \label{fig:flare2}
+\end{figure*}
+%%--------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Determining the LOS}\label{sec:los}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To determine the line of sight (LOS) along individual pixels in the field of view (FOV), we initially estimate the height of the flare loop using observations from different vantage points.
+STEREO-A/EUVI observed both events from a different angle compared to AIA, resulting in geometric effects on the observations.
+
+Fig.\ref{fig:flare_orient}a & b illustrates the geometric effect of observing from different vantage points.
+The magenta cross in Fig.\ref{fig:flare_orient}a represents a point at the top of the flare arcade.
+The LOS extends into the page through that point from the STEREO-A vantage.
+The red line in Fig.\ref{fig:flare_orient}b shows the LOS through the point in Fig.\ref{fig:flare_orient}a projected to the SDO/AIA point of view.
+Similar projections are shown in Fig.~\ref{fig:flare_orient2} for the Nov 29, 2020 flare.
+
+To calculate the height of the flare loop, we utilize co-temporal STEREO-A 171 {\AA}, 195 {\AA}, and AIA 171 {\AA}, 193 {\AA} images with \textit{scc\_measure.pro}, available in the \textit{sswidl}.
+This routine enables us to select a point on the observation from one vantage point, and the LOS through the same point is shown on the observation from the other vantage point.
+By identifying similar emission characteristics, we can determine the 3D coordinates of the point (heliographic latitude, longitude, and radial distance).
+This measurement is repeated at various positions along the loop top to calculate the change in loop height across the arcade.
+However, it is important to note that the height estimation using \textit{scc\_measure.pro} is limited by our ability to identify ``similar emission characteristics'' between the AIA and STEREO-A observations.
+
+%%--------------
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[width=\textwidth,trim={2cm 6cm 2cm 6cm},clip]{flare_orient.pdf}
+    \caption{Panel (a): {\it STEREO-A}/EUVI 171 {\AA} observation of the flare arcade in the decay phase.
+The magenta cross marks a point on the top of the arcade.
+The LOS goes into the page through that point.
+Panel (b): SDO/AIA 171 {\AA} observation of the flare arcade.
+The red line marks the LOS through the arcade from the STEREO-A perspective projected to the AIA perspective.}
+    \label{fig:flare_orient}
+\end{figure*}
+%%--------------
+
+%%--------------
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[width=0.9\textwidth,trim={4cm 5cm 3cm 5cm},clip]{nov29_triangulate.pdf}
+    \caption{Panel (a): SDO/AIA 193 {\AA} observation of the Nov 29 flare in the decay phase.
+The blue cross marks a point on the top of the arcade.
+The LOS goes into the page from AIA perspective.
+Panel (b): {\it STEREO-A}/EUVI 195 {\AA} observation around same time.
+The blue solid line is the LOS from AIA perspective in panel (a) projected onto {\it STEREO-A} perspective.
+We can trace out the height of the flare arcade at various locations using \textit{scc\_measure.pro}.
+The height of the arcade at various points from the Sun's surface is marked in panel (a).}
+    \label{fig:flare_orient2}
+    \end{figure*}
+%%--------------
+
+%%--------------
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[width=0.8\textwidth,trim={3cm 2cm 3cm 0cm},clip]{flare_orient_pt2.pdf}
+    \caption{Panel (a): Cartoon demonstrating the projection effects of a semicircular loop between STEREO-A and AIA vantages due to the difference between polar ($\theta$) and azimuthal ($\phi$) angles, respectively.
+Panel (b) : The calculated LOS map from the AIA perspective, with the estimated loop top height under the assumption of a semi-circular loop geometry.}
+    \label{fig:flare_orient_2}
+\end{figure*}
+%%--------------
+
+To determine the extent of the flare arcade, we select pixels within an emission measure contour of 5\% of the peak emission measure value.
+This contour is calculated based on the emission measure inferred from the DEM, which reflects the density of plasma across the temperature range of $5<\log,(T)<7.4$.
+This approach provides a more comprehensive estimate of the flare arcade compared to methods based solely on intensity observations, which may miss significant portions of the arcade due to the highly multi-thermal nature of the plasma.
+Outside of the flare arcade, we assume a line of sight (LOS) thickness of approximately 2 Mm, corresponding to the average thickness of the chromosphere.
+
+Fig.
+\ref{fig:flare_orient_2}b illustrates an example of the calculated LOS in the field of view (FOV) for the October 28, 2021 flare.
+The highest point of the flare arcade follows the ridge from southeast to northwest.
+An estimate of the highest point of the loop is approximately 22 Mm, consistent with previous estimates of the ridge height around 20 Mm from magnetic loop modeling \citep{longcope22}.
+Using the LOS map shown in the bottom panel of Fig.
+\ref{fig:flare_orient_2}, we calculate the thermal energy in every pixel of the flare using Equation \ref{eq:t_eneg}.
+This process is repeated for the flare loops in the November 29, 2020 event.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Energy in the non-thermal electrons}\label{sec:non-therm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To estimate the energy deposited by the non-thermal electrons in the X-class event on October 28, 2021, we analyze the STIX spectra.
+Figure \ref{fig:stix_an}.a illustrates the STIX light curve for different energy bands: 4 to 6 keV (solid black line), 6 to 12 keV (solid magenta line), 12 to 25 keV (solid yellow line), and 25 to 50 keV (solid blue line).
+The attenuator was activated around 15:28 UT to prevent saturation, notably reducing the intensity.
+The hard X-ray peak appears around 25 to 50 keV at approximately 15:28 UT, while the soft X-ray peak is discernible within the attenuated flux in the 6 to 12 keV band at approximately 15:30 UT.
+
+Following the methodology outlined in \cite{emslie12}, we fit the STIX spectra at various time intervals during the flare's evolution using the `2vth' and `thick2' functions available in the OSPEX X-ray spectra fitting package within `{\it sswidl}'.
+A representative fit is depicted in Figure \ref{fig:stix_an} panel (b) for the time bin around 15:26-15:27 UT using the `2vth' (solid yellow) and `thick2' (solid green) functions.
+The `2vth' function represents a two-component thermal model, with parameters for emission measure, temperature of the thermal components, and relative abundances of various elements with respect to CHIANTI coronal abundances \citep{chianti1,chianti}.
+On the other hand, the `thick2' function assumes a non-thermal component attributed to bremsstrahlung from energetic electrons, described by a broken power-law injected spectrum $F_{0}(E_{0})~(e^{-}s^{-1}cm^{-2}keV^{-1})$ :
+
+%%--------
+\begin{equation}
+    F_{0}(E_{0})=A
+    \begin{cases}
+        0, & E_{0}<E_{min} \\
+        E_{0}^{-\delta_{1}}, & E_{min} \le E_{0} < E_{b} \\
+        E_{0}^{-\delta_{2}}E_{b}^{\delta_{2}-\delta_{1}}, & E_{b} \le E_{0} < E_{max} \\
+        0, & E_{max} \le E_{0}
+    \end{cases}
+\end{equation}
+%%--------
+
+In the fitting process, the model spectrum parameters, such as the normalization parameter \( A \), the low- and high-energy cutoffs \( E_{\text{min}} \) and \( E_{\text{max}} \), the break energy \( E_{\text{b}} \), and the power law indices \( \delta_{1} \) and \( \delta_{2} \) below and above the break, are constrained.
+We set the high-energy cutoff at \( 3.2 \times 10^{4} \) keV for all fits, as it is significantly higher than the energy range of interest (around \( 10^{1} \) keV), making its effect on the X-ray spectra negligible \citep{emslie12}.
+
+The fitting procedure in `\textit{OSPEX}' is a forward fitting process.
+The parameters of the `\textit{2vth}' and `\textit{thick2}' functions are adjusted to generate a photon spectrum, which is then convolved through the detector response matrix to produce a count rate spectrum.
+This count rate spectrum is compared with the measured count rate spectrum, and an iterative process minimizes the \( \chi^{2} \) between them to refine the parameter estimates.
+
+Table \ref{tab1} presents the fitted temperature of the hotter thermal component at various phases of the flare.
+These temperatures align with the temperature range (\( \log(T_{\text{max}}) = 7.4 \) and \( \log(T_{\text{min}}) = 5 \)) used to calculate the emission measure (EM) and differential emission measure (DEM) weighted temperature, as discussed in Section \ref{sec:therm}.
+
+%%%%%%%%%%%
+\begin{table*}[ht!]
+    \centering
+    \begin{tabular}{|cl||c|c|}
+    \hline
+         &  & log(T) & EM \\ 
+         & \hspace{-1cm}Time (UT) & of hotter component & ($cm^{-3}$) \\
+    \hline
+        Impulsive phase & \hspace{1cm}15:26 & 7.098 & $10^{48}$\\
+        HXR peak & $\sim$ 15:27:20 - 15:28:20 & 7.19 & $3\times 10^{48}$\\
+        Right after SXR peak & $\sim$ 15:35:39 - 15:36:34 & 6.88 & $4.1\times 10^{49}$\\
+        Into the decay phase & \hspace{0.9cm}14:48:20 & 6.5 & $2\times 10^{49}$\\
+        \hline
+    \end{tabular}
+    \caption{Fitted temperature of the hotter component of the thermal plasma during various stages of the flare.}
+    \label{tab1}
+\end{table*}
+%%%%%%%%%%%
+
+The non-thermal energy in the electrons (\( U_{e} \)) at any instant \( t = t' \) can be estimated by integrating the best-fit electron energy spectrum:
+\[
+U_{e}(t=t') = \Delta t \int_{E_{\text{min}}}^{E_{\text{max}}} F_{0}(E_{0})(t=t') dE_{0}
+\]
+where the electron energy distribution is constrained by fitting the count spectra for the time interval \( t' - \Delta t/2 \leq t \leq t' + \Delta t/2 \).
+
+The cumulative energy deposited into the footpoint over time by the non-thermal electrons is a good indicator of the source of the thermal energy of the plasma.
+We can estimate the cumulative energy deposited by the non-thermal electrons up until a certain instant \( t \) by summing the energy deposited at the footpoints from every time bin:
+\[
+U^{cumulative}_{e}(t) = \sum_{t'=t_{0}}^{t} U_{e}(t')
+\]
+
+%%--------------
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim={3cm 2cm 6cm 3.5cm},clip,width=0.54\textwidth]{oct28_lc_2.pdf} 
+    \includegraphics[trim={3.5cm 8cm 3cm 2cm},clip,width=0.45\textwidth]{oct28_fit_2.pdf}
+    \caption{Panel (a): STIX light curve of the 2021 Oct 28 X-class event in different energy bands as labelled.
+The black, magenta, yellow and blue solid lines show the light curve in 4{--}6~keV, 6{--}12~keV, 12{--}25~keV and 25{--}50 keV.
+Panel (b): STIX spectra fit at 15:27{--}15:28 UT, during impulsive phase.
+We fit the spectra with `\textit{thcik2}' (green solid line) and `\textit{2vth}' (yellow solid line).
+We show the complete fit function `\textit{2vth+thick2}' with the solid red line.
+The lower panel shows the normalized residuals of the fit.}
+    \label{fig:stix_an}
+    \end{figure*}
+%%--------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{res}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%###########%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={4cm 1cm 4cm 1cm},clip,width=0.8\textwidth]{flare_eneg.pdf}
+    \caption{Panel (a): The calculated thermal energy as a function of time for the 2021 Oct 28 flare.
+The magenta dot-dashed line shows the thermal energy calculated from the GOES light-curve using the effective volume and a filling factor \textit{f}~=~1.
+The red dot-dashed line and the black dashed line shows the energy calculated from the GOES light-curve and the effective volume with filling factor \textit{f}~=~0.4 and \textit{f}~=~0.2, respectively.
+The blue solid line shows the thermal energy estimated using the DEMs calculated from the AIA obeservations.
+The black solid line shows the thermal energy calculated from the GOES light curve, but the volume inferred from the area of the of the flaring arcade with STIX SXR images, under the assumption that $V\sim A^{\frac{3}{2}}$.
+Panel (b): The calculated thermal energy as a function of time for the 2020 Nov 29 flare.
+The red line shows the thermal energy calculated from the GOES light curves, using a constant effective volume.
+The blue curve shows the thermal energy calculated from the DEMs inferred from the imaging and a varying volume from the imaging.}
+    \label{fig:eneg}
+\end{figure}
+%%###########%%
+
+%%###########%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={2cm 0cm 1cm 0cm},clip,width=0.8\textwidth]{fan_eneg.pdf}
+    \caption{Calculated thermal energy for the 2020 Nov 29 flare.
+Total thermal energy of the flare (blue dot-dashed) in comparison to the thermal energy from the fan (red dashed).
+The magenta and the green solid line show the fit to the thermal energy output to the fan and the loop's thermal output.
+Fermi hard X-ray count (black) peaks around the same time as the total thermal output.}
+    \label{fig:fan_eneg}
+    \end{figure}
+%%###########%%
+
+Figure~\ref{fig:eneg}.a shows the thermal and non-thermal energy calculated for the 2021 October 28 event.
+The black solid curve with crosses shows the thermal energy calculated from the DEMs.
+The red solid curve shows the thermal energy calculated from the {\it GOES} light curve and the effective volume calculated assuming an RTV loop \citep{rtv78,serio91}.
+We use the {\it GOES} emission measure, temperature with a volume filling factor \textit{f}~=~1, to estimate an effective loop length for the flare and from that, calculate an effective volume.
+Note that the implicit assumption of mechanical equilibrium only holds during the decay phase of the flare.
+So, the effective volume estimated here would only be appropriate in the decay phase.
+The green solid curve with triangles and the blue solid curve with squares show the same {\it GOES} thermal energy, with volume filling factor \textit{f}~=~0.4 and \textit{f}~=~0.2, respectively.
+The blue dashed curve shows the thermal energy calculated from the {\it GOES} light curve, but the volume inferred from the area of the flaring region from the STIX soft X-ray contours, under the assumption that $V\sim A^{\frac{3}{2}}$.
+
+The lime green solid line with circles in Fig.~\ref{fig:eneg}.a, shows the cumulative energy in the non-thermal electrons.
+This quantity is the amount of energy deposited at the flare foot points, and one of the sources of the thermal energy of the flare.
+The cumulative non-thermal energy of electrons $\simeq~1.2\times 10^{31}$ erg $>$ peak thermal energy calculated from the DEM estimates $\simeq~5\times 10^{30}$ erg.
+This is usual for an X-class flare.
+The differences in the estimates of thermal energy, due to different estimations of volume, also affects the partition between the thermal and non-thermal energies of flares.
+The efficiency of converting the energy deposited by non-thermal electrons into the thermal energy of the ambient plasma results in this partition and as a result, the volume estimation is a key parameter in understanding the conversion of non-thermal energy into thermal energy in flares.
+
+The interesting trend in Fig.~\ref{fig:eneg}.a is that the thermal energy calculated from the constrained DEMs (solid black curve with crosses) is closer to a volume filling factor \textit{f}~=~0.2 in the impulsive phase, but is asymptotic with a filling factor \textit{f}~=~1 (solid red curve) during the decay phase.
+This indicates that the flare loops during the impulsive phase do not fill up apparent volumes similar to those in the decay phase.
+The change in the effective filling factor is indicative of the sharp change in the volume during the impulsive phase.
+
+For the 2020 November 29 event, the {\it STEREO-A} perspective looks down into the supra-arcade plasma sheet.
+Thus the LOS of this feature can not be calculated as demonstrated in Section \ref{sec:los} for the supra-arcade pixels.
+For the supra-arcade fan pixels in the FOV, we assume a LOS $\simeq~8~\textrm{Mm}$, as suggested in several other studies \citep[see e.g.,][]{savage10,seaton17,li18}.
+We use these calculated LOS maps, along with equation~\ref{eq:t_eneg_1} to estimate the thermal energy as a function of time.
+
+Figure \ref{fig:eneg}.b shows the energy calculated for the November 29th event.
+The blue solid curve shows the thermal energy calculated from the DEMs.
+The red solid curve shows the thermal energy calculated from the GOES light curves and the constant effective volume calculated assuming an RTV loop with a volume filling factor \textit{f}~=~1.
+The thermal energy shows similar characteristics as the October 28th, 2021 event.
+The RTV loop effective volume clearly is an overestimation in the rise phase of the the flare, and agrees very well in the decay phase.
+
+There have been several studies that suggest that the plasma in the fan is directly heated \citep{hanneman14,chen17,reeves17,warren18,cai22,xie23}.
+Unlike the flare arcade, the thermal output of the fan is not directly related to the energy deposited by the non-thermal electrons and ions at the foot point.
+Hence, this different mechanism should also be reflected in the time evolution of the thermal output of the fan, compared to the thermal output of the loops.
+Under the assumption of the LOS~$\mathrm{\sim 8~Mm}$ in the fan region, we separately calculate the contribution from the fan to the total thermal energy for the 2020 Nov 29 event.
+
+Figure~\ref{fig:fan_eneg} shows the thermal energy of the fan as a function of time (red dashed line) in comparison to the total thermal energy of the 2020 Nov 29 event (blue dot-dashed line).
+The thermal energy form the fan is $\sim$ two orders of magnitude lower than the total thermal energy of the event.
+The thermal energy of the fan also peaks much later ($\sim$ 20 minutes) compared to the total thermal energy.
+After the thermal energy of the fan peaks, the thermal energy of the fan (red + sign) and the total thermal energy of the event (blue crosses) are fitted with a power law of the form $at^{-\delta}$ as a function of time.
+The fits are shown with magenta and green solid line for the fan and the total thermal energy, respectively.
+The value of the power law index are -0.95 and -1.1, respectively, for the fan and the total thermal output.
+The plots shows that the thermal energy of the fan decay slower compared to the total thermal output.
+The normalized {\it Fermi} GBM 25 {--} 80 keV count rate (black solid line) peaks at a similar time as the total thermal energy of the event.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Outlook}\label{sec:out}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We have used AIA, SUVI, and XRT observations to calculate DEM maps and estimate the thermal energy for two solar flares as a function of time.
+We have used observations from AIA and {\it STEREO-A} to calculate the geometry of the flare loops and estimate the LOS for the AIA observations.
+We have shown that the accurate estimation of volume can have significant implications for thermal energy estimates.
+For the 2020 November 20 flare, we have also estimated the thermal energy for the fan and compared the evolution of the thermal energy of the fan with respect to the total thermal energy of the event.
+We have shown that the thermal energy of the fan decays slower compared to the total thermal energy of the event.
+This result suggests that a fundamentally different heating mechanism is responsible for the thermal output of the fan.
+
+The thermal energy of the flares is given as, $U_{Th}\simeq 3n_{e}k_{B}TVf$.
+The electron number density is given by, $n_{e}~=~\sqrt{\sfrac{EM^{v}}{Vf}}~\implies~U_{Th}~=~3k_{B}T\sqrt{EM^{v}\times~Vf}$, where $EM^{v}$ is the volume emission measure (in units of $cm^{-3}$).
+A filling factor, \textit{f} $<$ 1 decreases the thermal energy by $\sim f^{\sfrac{1}{2}}$.
+There are very diverse results reported on \textit{f}.
+X-ray observations have generally constrained within $0.1<\textit{f}<1$\citep{jak11,guo12}, while it is usually constrained to much lower values $0.001<\textit{f}<0.1$ in EUV\citep{ash&ash08}.
+The filling factor can also be constrained by imposing the requirement that the flare plasma has to be contained via magnetic pressure.
+From this constraint it can be inferred that the required coronal magnetic field strength $B_{cor}$ $\sim f^{-\sfrac{1}{4}}$\citep{caspi14,warmuth16a,warmuth16b}.
+These studies rule out values of $\textit{f}<0.1$.
+Similar results were obtained from spectroscopic observations of density sensitive \ion{Fe}{11} lines \citep{miligan12}.
+
+It is easy to infer from our findings that a single value of volume filling factor is inadequate to describe the evolution of thermal energy throughout the duration of the flare.
+We need to estimate the volume as a function of time rather than depending on a filling factor.
+In Fig.~\ref{fig:eneg}.a, the thermal energy calculated from {\it GOES} with various filling factors demonstrates this concept perfectly.
+During the impulsive phase, the thermal energy calculated from the DEMs is consistent with \textit{f}=0.2, and later in the decay phase, it is consistent with \textit{f}=1.
+This result demonstrates how the volume of the flare arcade is changing over time with respect to the volume in the decay phase.
+The thermal energy calculated from $V\sim A^{\frac{3}{2}}$ assumption agrees well with the thermal energy calculated from constrained DEMs in the decay phase.
+But it still predicts higher energy in the impulsive phase.
+This discrepancy might signify that the assumption of self-similar expansion might not be valid at the initial sharp rise in the impulsive phase for some flares.
+
+Our results are in line with the findings of \cite{hilarie05}.
+They demonstrated from {\it RHESSI} imaging for a sample of 9 M and C class flares that the volume estimation with the assumption of self-similar expansion resulted in thermal energy higher than the non-thermal energy during the impulsive phase (For more details, refer to \cite{hilarie05} Table 5 and the corresponding discussion).
+A statistically inferred representative filling factor might serve perfectly well for estimating the energies near the thermal peak for a sample of flares.
+Since we are trying to quantify the evolution of the energy over time for individual flares, we require more accurate estimates of the volume.
+
+Our results also demonstrate the utility of estimating the volume from different vantages as a function of time.
+For events like the X-class event on 2021 October 28, the on-disk imaging allows the estimation of the volume from the flare ribbon area under the assumption of self-similar expansion.
+But for scenarios like the limb event 2020 November 29, where the flare ribbons are not visible from any imaging observation, or the visible foot point and/or visible portions of the loop are projected at a very high angle, estimating the volume of the loop by calculating the height of the loop at various points serves as an important tool in estimating the thermal energy at various phases of the flare.
+
+In Figure~\ref{fig:fan_eneg}, the thermal energy from the fan (red dashed line ) is $\sim$ two orders of magnitude lower than the total thermal energy of the event (blue dot-dashed line).
+The thermal energy also peaks much later ($\sim$ 20 minutes) compared to the total thermal energy.
+This result shows that the fan plasma is being heated directly by a process different from the flare arcade (e.g.
+SADs \citep{reeves17}, plasma flow turbulence \citep{xie23}).
+The fan also cools slower than the arcade, which indicates that either continuous heating is present in the fan during the decay phase of the flare or there is suppression of cooling \citep[e.g.][]{xie23}.
+The event had both foot points occulted from the Earth's perspective, so it is a fair assumption that most of the hard X-ray is from the loop top coronal source.
+This circumstance explains the near-simultaneous peak in {\it Fermi} hard X-ray (black solid line) and the thermal energy peak from the flare.
+
+Our results exhibit the importance of different solar missions that can observe the Sun with higher spatial resolution (to resolve the finer structures better) and from various vantages (to triangulate the geometry).
+The ability to spatially resolve the temperature structure of the flaring plasma not only gives us a better estimation of the thermal energy, but it also allows us to spatially separate various portions of the flaring plasma (e.g.
+for the 2020 November 29 event, we could separate the contribution of the fan from the total thermal energy).
+This separation enabled us to demonstrate that a different heating mechanism was at play in the fan.
+However, we do note that the reliability of any such estimations needs to be rigorously tested with observations of various flares from various geometric projections.

### 2024-07-22 introduction/intro.tex
Updates from Overleaf

@@
-The Sun is our nearest astrophysical object, which serves as a natural laboratory for various branches of Physics - atomic physics, spectroscopy, turbulence, magnetohydrodynamics, stellar evolution, dynamo and magnetism and plays a key role in space and terrestrial weather.
+\justifying
+
+The Sun is our nearest astrophysical object, which serves as a natural laboratory for various branches of Physics - atomic physics, spectroscopy, turbulence, magneto-hydrodynamics, stellar evolution, dynamo and magnetism and plays a key role in space and terrestrial weather.
 The Sun is also the primary source of light and energy on earth.
-So it is only natural that we try to understand the different physical processes involved in the energectics of the Sun, which indirecrtly affects life on Earth.
-In this chapter I briefly introudce the Sun and various layers of its atmosphere.
+So it is only natural that we try to understand the different physical processes involved in the energectics of the Sun, which indirectly affects life on Earth.
+In this chapter I briefly introduce the Sun and various layers of its atmosphere.
 At the end we provide a motivation for the thesis.
@@
 The Sun is a G2V star, with surface luminosity $3.86~\times~10^{26}$ W and an effective temperature of $\sim 5780~K$.
-The Sun is mostky made out of Hydrogen(92.1\%) and Helium(7.8\%) along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe.
+The Sun is mostly made out of Hydrogen(92.1\%) and Helium(7.8\%) along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe.
 The study of the Sun can be mainly divided into three components: the Solar interior, the Solar atmosphere and the Heliosphere.
@@
     \includegraphics[width = 0.8\linewidth]{Figures/solar_atm.png}
-    \caption{The variation of electron temperature (solid line) and electron density ($\mamthrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dotted- dashed line) in the solar atmosphere as derived based on the 1-D model calcula- tions by \sr{Ref.
+    \caption{The variation of electron temperature (solid line) and electron density ($\mamthrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dotted- dashed line) in the solar atmosphere as derived based on the 1-D model calculations by \sr{Ref.
 here}.}
@@
     \includegraphics[trim={1cm 3cm 2cm 5cm},clip,width=0.8\textwidth]{Figures/sji_images.pdf}
-    \caption{IRIS SJI Slit-jaw images of NOAA AR 13521 on Dec 21st, 2023 in \ion{Mg}{2} 2796~\AA~(left panel) showing the upper Chromosphere.
-The right panel shows the same active region in 2832~\AA~continuum corresponding to upper photosphere.}
+    \caption{IRIS SJI Slit-jaw images of NOAA AR 13521 on Dec 21st, 2023 in \ion{Mg}{2} 2796 {\AA}~(left panel) showing the upper Chromosphere.
+The right panel shows the same active region in 2832 {\AA}~continuum corresponding to upper photosphere.}
     \label{fig:sji_features}
@@
 
-In fig.~\ref{fig:sji_features} we show the NOAA AR 13521 in IRIS SJI 2796~\AA (left panel) and 2832~\AA (right panel).
-The dark sunspots and plage regions surrounding it are clearly visible in the 2832~\AA wavelength window.
-In the 2796~\AA window we see the plage along with light bridges more clearly.
+In fig.~\ref{fig:sji_features} we show the NOAA AR 13521 in IRIS SJI 2796 {\AA} (left panel) and 2832 {\AA} (right panel).
+The dark sunspots and plage regions surrounding it are clearly visible in the 2832 {\AA} wavelength window.
+In the 2796 {\AA} window we see the plage along with light bridges more clearly.
 
@@
 The transition region is generally characterized by the steep change in the temperature, pressure gradients, drastic change in local optical depth and competition between gas pressure and magnetic pressure.
-The transition region also manifests the ARs as various magnetic features such as small scale brightenings, jets, spicules, fibrils etc.
+The transition region also manifests the ARs as various magnetic features such as small scale brightening, jets, spicules, fibrils etc.
 
@@
 Mg, Fe, Si, S, Ca, O etc.
-across a wide band of elctro magnetic spectrum ranging from X-ray to visible wavelengths.
+across a wide band of electromagnetic spectrum ranging from X-ray to visible wavelengths.
 
@@
 Hodgson observed the first flare in the continuum of white light\citep{carrington1859,hodgson1859}.
-The localized brightenings on the Sun have remained an enigma ever since.
-We have been observing the local flaring events acrsoss all wavelenths from both ground and space based observatories.
-Shortly after the observation by Carrington and Hodgson, people started studying the Sun extensively in the H$\alpha$ line which is formed in the Chromosphere, and the reports of flaring events became more and more frequent and progressivly more and more complex.
-No two events were similar, as there were variations observed in source of size, ejections of plasma along with shockwaves driving into the interplanetary space.
-Advances of radio technology during the second world war ensured detections of prescence of non-thermal electrons in the solar corona, during military radar operations \citep{hey46}.
+The localized brightening on the Sun have remained an enigma ever since.
+We have been observing the local flaring events across all wavelengths from both ground and space based observatories.
+Shortly after the observation by Carrington and Hodgson, people started studying the Sun extensively in the H$\alpha$ line which is formed in the Chromosphere, and the reports of flaring events became more and more frequent and progressively more and more complex.
+No two events were similar, as there were variations observed in source of size, ejections of plasma along with shock waves driving into the interplanetary space.
+Advances of radio technology during the second world war ensured detection of presence of non-thermal electrons in the solar corona, during military radar operations \citep{hey46}.
 Around the same time S.E.
 Forbrush noticed ground level cosmic ray enhancement during major solar flares.
-These discoveries illuded that the flaring events do not only involve the thermal plasma, but is somehow connects with high energy particles and involves the corona.
-in the 1950s we started observing the Sun in hard X-rays ($\ge~10~keV$) with rockets and baloons.
+These discoveries eluded that the flaring events do not only involve the thermal plasma, but is somehow connects with high energy particles and involves the corona.
+in the 1950s we started observing the Sun in hard X-rays ($\ge~10~keV$) with rockets and balloons.
 \cite{peterson59} discovered the first hard X-ray emission during a flare in 1958.
-Later on, it was deduced from the observations of the enhancements observed in radio and hard X-rays that, the the ejected energetic particles may contain a substantial fraction of the intial energy released \citep{brown71}.
+Later on, it was deduced from the observations of the enhancements observed in radio and hard X-rays that, the the ejected energetic particles may contain a substantial fraction of the initial energy released \citep{brown71}.
 The hard X-ray is created by the bremsstrahlung of the electrons colliding into dense material, resulting in a power-law energy distribution.
-The braodband radio emission from 1 to 100 GHz is created from gyrosynchrotron emission.
+The broadband radio emission from 1 to 100 GHz is created from gyrosynchrotron emission.
 Finally, observations in EUV and soft X-ray($\le$~10~keV) have shown that the energy released form the flare heats the plasma contained in the coronal loops to temperatures beyond 30 MK.
@@
 
-\cite{neupert68} observed a curious corelation that, the soft X-ray flux during the rise phase of the flare is proportional to the time integral of the centimeter radio flux since the start of the flare.
+\cite{neupert68} observed a curious correlation that, the soft X-ray flux during the rise phase of the flare is proportional to the time integral of the centimeter radio flux since the start of the flare.
 The centimeter radio flux is emitted by relativistic electrons.
-So, later on the same corelation was found between the hard X-ray flux and soft X-ray flux and can be expressed as,
+So, later on the same correlation was found between the hard X-ray flux and soft X-ray flux and can be expressed as,
 
@@
 
-This emperical relation is known as the ``Neupert effect''.
-\cite{neupert68} had already suggested that thismay be due to a causal relationship between the thermal plasma and the energetic electrons.
-The logical explanation is: the soft X-ray mainly originates from a thermal plasma heated by the energy of the flaring event deposited by the flare acclerated electrons.
-It is important to mention that we know now, eqn.\ref{npt_eff_eq} is only valid if cooling by conduction of radiation is negligible.
+This empirical relation is known as the ``Neupert effect''.
+\cite{neupert68} had already suggested that this may be due to a causal relationship between the thermal plasma and the energetic electrons.
+The logical explanation is: the soft X-ray mainly originates from a thermal plasma heated by the energy of the flaring event deposited by the flare accelerated electrons.
+It is important to mention that we know now, Eqn.\ref{npt_eff_eq} is only valid if cooling by conduction of radiation is negligible.
 
 %% ################################################################# %%
-\subsection{Standard model of solar flare}\label{sol_flr_std_mod}
+\subsection{``Standard'' model of solar flare}\label{sol_flr_std_mod}
 %% ################################################################# %%
@@
     \item The magnetic reconnetion happens in corona, releasing the magnetic free energy.
-Electrons and energetic particles from the reconnetion site are acclerated along the realigned magnetic field lines.
-The acclerated particles that escape along the open field lines towards the earth gives rise to the particle events seen from earth.
-    \item The acclerated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave observations seen from falres via gyromagnetic radiation.
-    \item The acclerated particles hit the Chromosphere which is considerably denser than the Corona, giving rise to Hard X-ray and gamma ray observed from the footpoints.
-This also explains why the coronal hard X-ray source is considerably softer than the footpoints.
+Electrons and energetic particles from the reconnetion site are accelerated along the realigned magnetic field lines.
+The accelerated particles that escape along the open field lines towards the earth gives rise to the particle events seen from earth.
+    \item The accelerated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave observations seen from flares via gyro magnetic radiation.
+    \item The accelerated particles hit the Chromosphere which is considerably denser than the Corona, giving rise to Hard X-ray and gamma ray observed from the foot points.
+This also explains why the coronal hard X-ray source is considerably softer than the foot points.
 The energetic particles deposit their energy into the local Chromosphere, as they go through series of collision and eventually thermalize.
     \item  As the plasma thermalizes, it starts emitting in thermal bremsstrahlung giving rise to the soft X-ray observed.
-Also, as the energy is deposited into the Chromosphere from the acclerated particles, it heats the local Chromosphere environment it gradually increases the local pressure.
+Also, as the energy is deposited into the Chromosphere from the accelerated particles, it heats the local Chromosphere environment it gradually increases the local pressure.
     \item As the pressure grows, when the pressure gradient builds up enough the local plasma starts expanding upwards(essentially due to buoyancy) and slowly fills up the coronal loops with soft X-ray emitting plasma.
 This phenomenon is known as "Chromospheric evaporation".
-This was dorectly observed later on, in blue-shifted lines of hot material.
+This was directly observed later on, in blue-shifted lines of hot material.
     \item This whole scenario explains the Neupert effect.
-As the energy form the acclerated particles is converted into the soft X-ray emitting plasma, and it builds up over time.
+As the energy form the accelerated particles is converted into the soft X-ray emitting plasma, and it builds up over time.
 That explains the soft X-ray being proportional to the time integral of the hard X-ray flux.
@@
 
-This whole scenario is known as the ``Standard model of solar flare''.
-While the standard model is an attempt to explain and unify various kind of differences seen from the neumerous flares we observe, there are several cases where the stnadard model cannot explain the observations.
-For example, there have been observations of falres where the hard X-ray footpoint do not form.
-It is proposed that in these cases the plasma in the coronal loops is so dense that the acclerated particle collide enough to thermalize within the flare loops before reaching the Chromosphere, deffusing the energy more evenly within the loop, rather than dumping it at the base of the loops \citep{veronig02,veronig04}.
-Another flare which previously occured at the same region might explain the denser coronal loops \citep{strong84,bone07}.
+This whole scenario is known as the ``Standard'' model of solar flare.
+While the standard model is an attempt to explain and unify various kind of differences seen from the numerous flares we observe, there are several cases where the standard model cannot explain the observations.
+For example, there have been observations of flares where the hard X-ray foot point do not form.
+It is proposed that in these cases the plasma in the coronal loops is so dense that the accelerated particle collide enough to thermalize within the flare loops before reaching the Chromosphere, defusing the energy more evenly within the loop, rather than dumping it at the base of the loops \citep{veronig02,veronig04}.
+Another flare which previously occurred at the same region might explain the denser coronal loops \citep{strong84,bone07}.
 
@@
 With an experience of observing solar flares for more than 150 years, remarkably enough, we have barely started scratching the surface of the complexity involved with the solar flares.
-The reconfiguring of magnetic structure, which almost always involves complex geometry, making almost all events unique in some sense.
-After that the released magnetic free energy is transported accross various layers of the sun and converted into various other forms of energy.
-Consodering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses.
-In case of the eruptive events, there is the added complexity of the kinetic and potential energy of the CMEs, the enrgy of the shcoks and the kinetic energy of the solar energetic particles.
+The re-configuring of magnetic structure, which almost always involves complex geometry, making almost all events unique in some sense.
+After that the released magnetic free energy is transported across various layers of the sun and converted into various other forms of energy.
+Considering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses.
+In case of the eruptive events, there is the added complexity of the kinetic and potential energy of the CMEs, the energy of the shocks and the kinetic energy of the solar energetic particles.
 
-Inorder to constrain the models of solar eruptions and various nuanced aspects of it, like magnetic reconnection, particle accleration, heating etc.
+In order to constrain the models of solar eruptions and various nuanced aspects of it, like magnetic reconnection, particle acceleration, heating etc.
 detailed quantitative characterization is absolutely necessary.
 There have been several studies that have tried to quantify the partition between various subsets of the energies.
-The questions that are perticularly important are:
+The questions that are particularly important are:
 
@@
 \begin{itemize}
-    \item \textbf{If an active region can have enough free enrgy to account for the total energy relased in the solar flares and/or CMEs.}
-    \item \textbf{What is the energy partition betwen flares and CMEs.}
+    \item \textbf{If an active region can have enough free energy to account for the total energy released in the solar flares and/or CMEs.}
+    \item \textbf{What is the energy partition between flares and CMEs.}
     \item \textbf{If the non-thermal component have enough energy to power up the thermal component.}
@@
 \cite{emslie12} found that the flare and CME have energies of same order of magnitude, while \cite{ash17} concluded the flare dominates the CME in-terms of the energy.
-However the simple question, whether the non-thermal component of the flares have enough enrgy is still not resolved as even the most recent studies contradict each other in the most puzzling fashion.
+However the simple question, whether the non-thermal component of the flares have enough energy is still not resolved as even the most recent studies contradict each other in the most puzzling fashion.
 \cite{warmuth20} discussed the contradictions arising from some of the studies\citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17}.
@@
 The bolometric energy serves as a representation of the overall energy released during solar flares.
-Regardless of how energy is released in a solar flare, whether through direct plasma heating, rapid bulk flows, or nonthermal particle processes—the ultimate outcome is thermalization and subsequent radiation across the electromagnetic spectrum.
+Regardless of how energy is released in a solar flare, whether through direct plasma heating, rapid bulk flows, or non thermal particle processes—the ultimate outcome is thermalization and subsequent radiation across the electromagnetic spectrum.
 Given that bolometric energy encompasses the entire spectrum, it is anticipated to reflect the total energy originally released.
 It's important to note that this specifically pertains to the energy liberated within the flare and does not encompass the energy associated with a concurrent coronal mass ejection (CME) or filament eruption.
-So, \cite{warmuth20} used the bolometric energy released in solar flares, to compare various studies on equal footing.
+\cite{warmuth20} used the bolometric energy released in solar flares, to compare various studies on equal footing.
 Here we will discuss some of the main issues \cite{warmuth20} identifies comparing these studies.
@@
 Although the {\it GOES} temperature is higher by a factor of 1.4, it is not dependant on the flare class.
-Along with that, \cite{warmuth20} also investigated whether assuming a isothermal or multithermal model introduces any differences in the thermal energy estimates.
+Along with that, \cite{warmuth20} also investigated whether assuming a isothermal or multi thermal model introduces any differences in the thermal energy estimates.
 They reported no significant differences due to differences of models (refer to Fig.
@@
 \begin{itemize}
-    \item The primary challenge in estimating the thermal energy of the hot plasma stems from determining the distribution of the Differential Emission Measure (DEM), and the radiating plasma volume.
+    \item The primary challenge in estimating the thermal energy of the hot plasma stems from determining the temperature distribution of the plasma using Differential Emission Measure (DEM), and the radiating plasma volume.
     \item The dissipation of energy from the hot plasma is substantial.
@@
 In smaller flares, there appears to be a deficiency of energetic electrons, whereas in larger flares, the injected non-thermal energy seems to sufficient in powering the thermal component.
-Does this signify the existance of an additional third heating source?
+Does this signify the existence of an additional third heating source?
 \end{itemize}
@@
 The various imaging channels of {\suit} would observe the manifestation of flares in transition region at various heights (NB3 $\implies$ \ion{Mg}{2} k 279.6 nm, NB4 $\implies$ \ion{Mg}{2} h 280.3 nm, NB8 $\implies$ \ion{Ca}{2} h 396.8 nm), further lower in the transition region (NB2 $\implies$ blue wing of Mg window, NB5 $\implies$ red wing of Mg window) and Sunspots and possible signature of umbral brightening due to flares at the Photosphere (NB6 300 nm and NB7 388 nm) in full disk.
-This would also allow us to probe the interaction of the flaring region, with other active regions on disk, giving us a comprehensive overview of the effect of solar flares and their manifestation in the lower solat atmosphere.
+This would also allow us to probe the interaction of the flaring region, with other active regions on disk, giving us a comprehensive overview of the effect of solar flares and their manifestation in the lower solar atmosphere.
 
@@
     \item In chapter \ref{c:chap3}, we discussed some of the initial preparatory analysis we did for {\suit}, including the throughput model for {\suit}, how the filters mounted on {\suit} were chosen, the analysis of spacecraft jitter simulation and what effect it would have on the imaging.
+We also describe the stellar calibration scheme and the selection criteria for the standard star target.
+We use a sun as a star spectra to evaluate the calibration scheme with the aforementioned throughput model.
     \item In chapter \ref{c:chap4}, we discuss the forward modelling pipeline developed for {\suit}.
@@
 We also discuss a preliminary version of the deconvolution algorithm that will be deployed in the data reduction pipeline.
-    \item In chapter \ref{c:chap5}, we describe the stellar calibration scheme and the selection criteria for the standard star target.
-We also use a sun as a star spectra to evaluate the calibration scheme.
-    \item In chapter \ref{c:chap6}, we use existing {\it IRIS} observations of three solar flares to probe how the lower solar atmosphere is affected by the flares.
+    \item In chapter \ref{c:chap5}, we use existing {\it IRIS} observations of three solar flares to probe how the lower solar atmosphere is affected by the flares.
 The ratio of the \ion{Mg}{2} k and h lines, is a proxy for the optical depth of the surrounding plasma.
-Hence, we use the observations of \ion{Mg}{2} lines along HMI magentic field measurements to investigate the effects of magnetic field, if any.
+Hence, we use the observations of \ion{Mg}{2} lines along HMI magnetic field measurements to investigate the effects of magnetic field, if any.
 \cite{kerr15} conducted a similar study and found signatures of localised heating in the line intensity ratio.
@@
 We can use a similar method to give full disk context of optical depth, with respect to eruptive events.
+    \item We address the issues raised in \S\ref{sol_flr_std_mod} regarding the uncertainties of volume estimation for flaring plasma and its effects on the thermal energy estimation in chapter \ref{c:chap6}.
+We use observations from {\it SDO}/AIA, {\it STEREO-A}/EUVI, {\it SO}/STIX, {\it GOES}/SUVI to estimate the thermal energy of two solar flares.
+We propose a new  using existing tools, to use observations from different vantages ({\it e.g.} AIA and EUVI from different angles) to accurately calculate the volume of the flare arcade and estimate the thermal energy.
+We show that the accurate estimate as a function of time can have effects on the accurate estimation of thermal energy and the partition between the thermal and non-thermal component.
 \end{itemize}

### 2024-07-22 main_thesis_file.tex
Updates from Overleaf

@@
 \author{Soumya Roy}
-\title{Thesis Title Goes Here}
-\department{}
+\title{Dynamics of the Lower Solar Atmosphere}
+\department{Jawaharlal Nehru University, New Delhi, India}
 \subject{}
-\month{Month}
-\year{Year}
-\advisor{Professor Durgesh Tripathi}
+\month{July}
+\year{2024}
+\advisor{Prof. Durgesh Tripathi}
 
@@
 	%% List of Figures
-%\addcontentsline{toc}{chapter}{List of Figures}
-%\listoffigures
-%\newpage
+\addcontentsline{toc}{chapter}{List of Figures}
+\listoffigures
+\newpage
 	%% List of Tables
-%\addcontentsline{toc}{chapter}{List of Tables}
-%\listoftables
+\addcontentsline{toc}{chapter}{List of Tables}
+\listoftables
+
+\newpage
+
+\thispagestyle{plain}
+\addcontentsline{toc}{chapter}{List of Abbreviations}
+\chaptermark{List of Abbreviations}
+\vskip 0.5cm
+{\centerline {\Large \bf List of Abbreviations}}
+\vskip 0.5cm
+\normalsize
+
+\input{abbr.tex}
 
@@
 %
-\chapter{Stellar calibration of SUIT}\label{c:chap5}
-\chaptermark{SUIT stellar calibration}
-\begin{quote}
-{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
-{authors,
-{\em journal reference info}}
-\end{quote}
-\input{./chapter5/ms.tex}
+%\chapter{Stellar calibration of SUIT}\label{c:chap5}
+%\chaptermark{SUIT stellar calibration}
+%\begin{quote}
+%{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
+%{authors,
+%{\em journal reference info}}
+%\end{quote}
+%\input{./chapter5/ms.tex}
 %
-\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap6}
+\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap5}
 \chaptermark{Solar flares Mg II}
@@
 \end{quote}
-\input{./chapter6/ms.tex}
+\input{./chapter5/ms.tex}
 \clearpage
 %
-\chapter{Estimating thermal energy of two Solar Flares}\label{c:chap7}
+\chapter{Estimating thermal energy of two Solar Flares}\label{c:chap6}
 \chaptermark{Solar flare energy}
@@
 \end{quote}
-\input{./chapter7/ms.tex}
+\input{./chapter6/ms.tex}
 \clearpage
 %
-\chapter{First flares observed from {\suit}}\label{c:chap8}
+\chapter{First flares observed from {\suit}}\label{c:chap7}
 \chaptermark{Solar flare energy}

### 2024-07-23 chapter3/ms.tex
Updates from Overleaf

@@
 \hline
-NB01     & BB01 		& 214.0 		    & 11.0 		& Continuum\\
-NB02 	& BP02		& 276.7				& 0.4 		& Mg~\rm{II}~k blue wing \\
-NB03 	& BP02		& 279.6 			& 0.4 		& Mg~\rm{II}~k\\
-NB04 	& BP02		& 280.3				& 0.4 		& Mg~\rm{II}~h\\
-NB05		& BP02		& 283.2				& 0.4 		& Mg~\rm{II}~h red wing\\
-NB06 	& BP03		& 300.0 			&1.0 		& Continuum\\
-NB07 	& BP03		& 388.0				&1.0 		& CN Band\\
-NB08		& NB08		& 396.85 			& 0.1 		& Ca~\rm{II}~h\\
-BB01 	& BB01		& 220.0				& 40.0		& Herzberg Continuum \\
-BB02 	& BP04		& 277.0 			& 58.0       & Hartley Band\\
-BB03 	& BP04		& 340.0				& 40.0        & Huggins Band\\
+NB1     & BB1 		& 214.0 		    & 11.0 		& Continuum\\
+NB2 	& BP2		& 276.7				& 0.4 		& Mg~\rm{II}~k blue wing \\
+NB3 	& BP2		& 279.6 			& 0.4 		& Mg~\rm{II}~k\\
+NB4 	& BP2		& 280.3				& 0.4 		& Mg~\rm{II}~h\\
+NB5		& BP2		& 283.2				& 0.4 		& Mg~\rm{II}~h red wing\\
+NB6 	& BP3		& 300.0 			&1.0 		& Continuum\\
+NB7 	& BP3		& 388.0				&1.0 		& CN Band\\
+NB8		& NB8		& 396.85 			& 0.1 		& Ca~\rm{II}~h\\
+BB1 	& BB1		& 220.0				& 40.0		& Herzberg Continuum \\
+BB2 	& BP4		& 277.0 			& 58.0       & Hartley Band\\
+BB3 	& BP4		& 340.0				& 40.0        & Huggins Band\\
 \hline

### 2024-07-23 chapter7/ms.tex
Updates from Overleaf

@@
+\justifying
+
 %%----------------------------------------------------
@@
 
-Solar flares are the largest magnetic events within our solar system.
-They are characterized by the sudden release of magnetic energy, leading to localized, transient heating of coronal plasma to temperatures exceeding approximately 10 million Kelvin (MK), significantly hotter than the surrounding coronal plasma at around 1 MK.
-Flares are typically identified by the peak soft X-ray flux observed by the X-Ray Sensor onboard the Geostationary Operational Environmental Satellites (GOES/XRS), often referred to as the "GOES class" \citep{xrs}.
-Flares classified as GOES class C and above typically heat the coronal plasma to temperatures ranging from 5 to 20 MK.
-These observations, which integrate over the entire solar disk, are commonly used to characterize the average physical properties of flare plasma.
+The Solar Ultraviolet Imaging Telescope onboard {\it Aditya-L1} \citep[{\it Aditya-L1}/SUIT,][]{article,ghosh16,adityal1,suit_main} provides a targeted probe into the Chromosphere and Transition region.
+It provides continuous full-disk and Region of Interest (RoI) coverage of the Sun in eleven pass bands.
+The details of these bands are provided in chapter~\ref{c:chap3} Tab.~\ref{tab:science_filters}.
+The eight narrow bands provide coverage across the \ion{Mg}{2} k and h lines, \ion{Ca}{2} h line, the CN band, red and blue wing of the \ion{Mg}{2} window and parts of the NUV continuum.
+As alluded earlier, this provides unprecedented coverage of the Chromospheric and Transition region structure of solar flares.
 
-It is widely acknowledged that active regions possess sufficient magnetic free energy to trigger flares and associated Coronal Mass Ejections (CMEs) \citep{emslie12, ash17}.
-The high temperatures observed in flare-induced coronal plasma are often attributed to the evaporation of chromospheric material, heated by the collisions of flare-accelerated electrons during the impulsive phase \citep{fletcher11}.
-However, there is also evidence suggesting that plasma may be directly heated within the corona in certain cases \citep[e.g.,][]{longcope11, reeves17}.
-
-Numerous studies \citep{stosire07, emslie12, inglis14, warmuth16a, warmuth16b, ash17} have examined the partition between thermal and non-thermal energies in flares, aiming to shed light on the underlying physical processes.
-However, the results have been inconclusive, and there is currently no consensus regarding whether non-thermal energetic electrons possess sufficient energy to account for the observed thermal energy component in smaller flares.
-
-These studies typically utilize peak thermal energy as a representation of the overall thermal output of flares.
-Consequently, our comprehension of flare energetics has predominantly been shaped by statistical analyses of bolometric output and peak thermal energy.
-While these metrics provide reasonable representations of the overall thermal output of flares, discerning subtle differences in heating mechanisms occurring at various stages of flares necessitates quantifying thermal energy as a function of time.
-
-For instance, \citet{longcope11} proposed the existence of a super hot plasma component in some large solar flares, directly heated within the corona.
-Sustained temperatures observed in supra-arcade fans during flares have been attributed to phenomena such as supra-arcade downflows \citep[e.g.,][]{reeves17}, suppression of conduction by turbulence \citep[e.g.,][]{xie23}, or global compression from reconnection inflows \citep[e.g.,][]{reeves19}.
-These processes represent distinct mechanisms from chromospheric evaporation, characterized by the development of hard X-ray footpoints and increasing intensity of soft X-ray and EUV-emitting plasma as the loops fill.
-
-Several studies \citep{hilarie05, caspi10} have attempted to estimate thermal energy as a function of time. The thermal energy of flares is defined as:
-\begin{equation}
-\mathrm{U_{Th}~\simeq~3n_{e}k_{B}TV}f,
-\end{equation} \label{eq:t_eneg_1}
-where $\mathrm{n_{e}}$ is the electron number density of the flaring plasma, 'V' is the volume of the flaring plasma, 'f' is the volume filling factor, and 'T' is the instantaneous temperature.
-A key challenge in characterizing flare thermal energy lies in determining the volume.
-
-\citet{li23} and \citet{zhang19} utilized soft X-ray emitting regions' $\frac{1}{e^{2}}$ contour or intensity threshold on AIA 131 {\AA} observations to estimate the flare area (A), subsequently inferring the volume as $V \sim A^{\frac{3}{2}}$.
-\citet{hilarie05} employed a similar method using RHESSI soft X-ray images to estimate the lower limit of volume, assuming a "perfect arc-shaped" loop.
-They also estimated the evolution of cumulative non-thermal energy injected by electrons, assuming a thick-target model \citep{brown71}, and fitting RHESSI spectra to determine non-thermal energies in time bins with significant emission above 25 keV.
-\citet{caspi10} utilized a 50\% intensity contour of cleaned RHESSI images to estimate the flare area, inferring volume assuming spherical symmetry.
-
-In all these cases, the assumption of symmetrical expansion proves useful, as thermal energy is estimated from spectra obtained by integrating multiple pixels.
-However, addressing the spatially varying multi-thermal nature of flaring plasma remains a challenge in these analyses.
-Determining the volume of the flaring plasma is a significant challenge in characterizing the thermal energy of flares.
-The filling factor `f' quantifies the fraction of the apparent volume filled with plasma of a specific temperature and may also account for geometric projection effects, representing the real volume projected into the observed apparent volume.
-Given the highly multi-thermal nature of flaring plasma and the rapidly changing volume during the flare's rise phase, defining a filling factor that accurately describes plasma volume evolution throughout the flare is challenging.
-
-Here, we investigate the thermal energy evolution of two flares, an M-class and an X-class flare, utilizing existing tools and observations from various vantage points to improve the accuracy of estimating flaring plasma volume.
-We demonstrate that a more precise estimate of plasma volume impacts thermal energy estimates and has implications for the flare's energy budget.
-Additionally, we estimate the cumulative non-thermal energy deposited by non-thermal electrons and compare it with our thermal energy estimates.
-
-In Section \ref{sec:obs}, we detail the observations utilized in this study and describe our analysis approach.
-Section \ref{sec:therm} outlines our method for estimating thermal energy, while Sections \ref{sec:los} and \ref{sec:non-therm} discuss our techniques for volume estimation and cumulative non-thermal energy estimation, respectively.
-Finally, we present and discuss our results in Section \ref{res}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Observations and Data Analysis}\label{sec:obs}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We investigate the two flares using EUV imaging from multiple instruments, including the Atmospheric Imaging Assembly onboard the Solar Dynamics Observatory \citep[SDO/AIA;][]{sdo,aia}, the Extreme Ultraviolet Imager onboard the Solar Terrestrial Relations Observatory-A \citep[STEREO-A/EUVI;][]{stereo,euvi}, and the Solar Ultraviolet Imager onboard GOES \citep[GOES/SUVI;][]{suvi}.
-Additionally, we utilize imaging data from the Spectrometer/Telescope for Imaging X-rays onboard Solar Orbiter \citep[SO/STIX;][]{so,stix,stix1}, the X-Ray Telescope onboard Hinode \citep[Hinode/XRT;][]{xrt}, and the X-Ray Sensor onboard GOES.
-The X and M class flares are observed at the disk center and limb of the Sun, respectively, from the perspective of AIA.
-
-The positions of various spacecraft relative to the flares' locations on the solar disk are illustrated in Figure \ref{fig:sc_pos}.
-Panel (a) displays the AIA 193 Å observation of the Oct 28, 2021 flare projected onto Heliographic Stonyhurst (HGS) coordinates, with the positions of SDO (magenta cross), SO (cyan circle), and STEREO-A (green triangle) marked with respect to the flare location.
-The flare is delineated by a white dotted circle.
-The relative separations between the spacecraft indicate differences in polar and azimuthal angles due to varying vantage points.
-Panel (b) presents the spacecraft positions projected onto the Heliocentric Inertial (HCI) frame for the same event, demonstrating differences in azimuthal angle and distance from the Sun's center.
-Similar plots for the Nov 29, 2021 flare are depicted in Panels (c) and (d), with EUVI 171 Å emission projected onto HGS and HCI coordinates, respectively.
-
-%%%%######%%%%%%
-\begin{figure*}[ht!]
-    \centering
-    \includegraphics[trim={1cm 0.5cm 1.2cm 0.5cm},clip,width=\textwidth]{flare_pos.pdf}
-    \caption{Position of various instruments during the flares.
-Panel a: AIA 193 {\AA} observation during the 2021 Oct 28 event projected to Heliographic Stonyhurst (HGS) coordinates.
-The position of the flare is marked with a white dotted circle.
-The positions of {\it Solar Orbiter}, {\it SDO} and {\it STEREO-A} are marked with an olive circle, magenta cross and green triangle, respectively.
-The positions of the spacecraft signify the difference in both the polar (vertical axis) and the azimuthal (horizontal axis) angle and do not mark the connectivity of the spacecraft to the solar surface.
-Panel b: The positions of the spacecrafts projected onto the Heliocentric Intertial (HCI) frame for the 2021 Oct 28 event.
-The difference between the spacecraft show the difference in the azimuthal angle.
-Panel c: {\it STEREO-A}/EUVI 171 {\AA} observation during the 2020 Nov 29 event projected to HGS coordinates.
-The position of the flare is marked with a white dotted circle.
-The positions of {\it SDO} and {\it STEREO-A} are marked with a magenta cross and green triangle, respectively.
-Panel d: The positions of the spacecraft projected onto the HCI frame for the 2020 Nov 29 event.}
-    \label{fig:sc_pos}
-\end{figure*}
-%%%%######%%%%%%
-
-The X1 flare occurred on Oct 28, 2021 (SOL2021-10-28T15:35) near approximately $\sim~[0\arcsec,-500\arcsec]$ solar coordinates as observed from AIA.
-It was captured by SDO/AIA, STEREO-A/EUVI, GOES/SUVI, XRT, GOES/XRS, and STIX.
-AIA provided observations with passbands at 94, 131, 193, 171, 211, and 335 Å, with a pixel size of approximately 0.6 arcseconds.
-SUVI provided similar wavelengths to AIA: 94, 131, 195, 171, 195, and 284 Å, with a pixel size of approximately 2.5 arcseconds.
-STEREO-A/EUVI offered imaging in 171, 195, and 284 Å coronal passbands.
-
-The flare exhibited a standard two-ribbon structure, along with a ridge at the top of the rising flare arcade \citep{longcope22}.
-The ridge, most prominently visible in the AIA 193 Å channel, was primarily created by the hotter \ion{Fe}{24} line (T~$\simeq$17 MK) and had a height of approximately $26~Mm$.
-This ridge was utilized to identify the loop-top in the AIA observation and calculate the loop height.
-
-STIX provided X-ray imaging and spectroscopy in the 4-150 keV range, with spectroscopic observations in 32 pre-defined energy channels.
-Fig.\ref{fig:flare}a depicts an AIA 193 Å image of the flare during the decay phase, while Fig.\ref{fig:flare}b overlays STIX intensity contours (15:27:40 {--} 15:28:00 UT) in the 4{--}16 keV (pink solid line) and 15{--}60 keV (blue solid lines) ranges on an AIA 1600 Å image during the rise phase.
-The MEM-GE algorithm was used to construct the STIX intensity maps.
-
-The M flare occurred on November 29, 2020, near approximately $[-950\arcsec,-430\arcsec]$ solar coordinates from the AIA perspective.
-In AIA images, the footpoints were occulted behind the limb.
-It was recorded by STEREO-A/EUVI, GOES/SUVI, Hinode/XRT, GOES/XRS, and Fermi/GBM.
-There were no STIX observations for this event.
-
-The flare exhibited a fan visible in the hot channels of AIA (131 and 193 Å) and the XRT channels.
-Fig.
-\ref{fig:flare2}a shows an AIA 131 Å image during the decay phase, while Fig.~\ref{fig:flare2}b displays an XRT Be-med filter observation taken near simultaneously with the AIA image.
-For the M-class event, Fermi observations were periodically eclipsed during the flare duration, rendering it challenging to estimate the cumulative non-thermal energy accurately.
-Hence, the estimation of cumulative non-thermal energy would not be a fair representation of the total non-thermal energy available.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Thermal Energy}\label{sec:therm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To estimate the thermal energy of the X-class event, we calculate the differential emission measure (DEM) of the flaring region using data from the six AIA passbands, including 94 Å (\ion{Fe}{10} $\sim$1.1 MK, \ion{Fe}{18} $\sim$7.1 MK), 131 Å (\ion{Fe}{8} $\sim$0.4 MK, \ion{Fe}{21} $\sim$11 MK), 171 Å (\ion{Fe}{9} $\sim$0.6 MK), 193 Å (\ion{Fe}{12} $\sim$1.6 MK, \ion{Fe}{24} $\sim$17 MK), 211 Å (\ion{Fe}{14} $\sim$2 MK), and 335 Å (\ion{Fe}{16} $\sim$2.5 MK) \citep{o'dwyer10,O'Dwyer12}.
-During the flare's peak, some AIA observations may be saturated, so we substitute SUVI observations, co-aligned and co-registered with AIA, for those specific frames.
-We bin AIA observations to the SUVI pixel size, ensuring consistency.
-Since the SUVI temperature response closely resembles that of AIA \citep{suvi}, we can utilize SUVI images for thermal energy estimates when necessary.
-In such cases, we also adjust the AIA temperature response functions to accommodate the binning of AIA data.
-Due to saturation, most of the XRT observations during the flare are not included in our analysis of this event.
-
-For the M-class event, we estimate the thermal energy using AIA and XRT observations.
-Here, we bin the AIA observations to the XRT pixel size, co-align them, and calculate the DEMs.
-As previously described, we rescale the AIA temperature response functions to accommodate the binning of AIA data.
-
-We employ the regularized inversion method \citep{hannah&kontar12} to calculate the DEMs, enabling us to derive the thermal energy estimates.
-We can calculate the EM and DEM weighted temperature using the methods discussed in chapter \ref{sec:c2_dem}.
-The temperature range of the integration are set to $5 < \log\,T < 7.4$.
-We calculate the emission measure and the DEM weighted temperature for all the pixels in the field of view (FOV).
-In Fig.~\ref{fig:flare}c \& d (\ref{fig:flare2}c \& d), we plot the DEM weighted temperature and emission measure in the temperature range 5.0$<$$\log\,T$$<$7.4, for the 2021 Oct 28 (2020 Nov 29) flare.
-
-We use the emission measure and DEM weighted temperature estimated from the inverted DEM in the thermal energy expression of Equation \ref{eq:t_eneg_1} and sum over the pixels in the FOV to estimate the thermal energy arising from the FOV.
-This procedure gives us,
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{equation}
-    U_{Th}~=~\sum_{j}~\frac{3k_{B}A\sqrt{LOS_{j}}}{\sqrt{EM^{c}_{j}}}\int_{T}~DEM_{c}(T)_{j}T~dT
-    \label{eq:t_eneg}
-\end{equation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-where $EM^{c}_{j}$ and $DEM_{c}(T)_{j}$ are the column emission measure and the column DEM in 5.0$<$$\log\,T$$<$7.4 for the j-th pixel in the FOV.
-We have used $n_{e}^{2}\times LOS~=EM_{c}$ and a filling factor $\textit{f}~=~1$.
-For the 2020 Nov 29 flare we mask the solar disk while calculating the DEMs and thermal energy.
-For our analysis, one of the major uncertainties in determining the emitting volume depends on determining the LOS for individual pixels in the FOV.
-
-%%--------------------------
-\begin{figure*}[ht!]
-    %\hspace{-1cm}
-    \includegraphics[width=0.9\textwidth,trim={2cm 5cm 3cm 3cm},clip]{oct28_align.pdf}
-    \caption{Panel (a): the flare arcade in AIA 193 {\AA}.
-Panel (b): STIX soft X-ray contours (4 {--} 16 keV, solid pink lines) and hard X-ray contours (16 {--} 50 keV, solid blue lines) aligned to AIA 1600 {\AA} and over plotted.
-Panel (c): the emission measure map of the region for $5~<log(T)~<7.4$.
-Panel (d): the DEM weighted temperature map of the region.}
-    \label{fig:flare}
-\end{figure*}
-%%--------------------------
-
-%%--------------------------
-\begin{figure*}[ht!]
-\centering
-    \includegraphics[trim={4.8cm 1.5cm 6cm 2.5cm},clip,width=0.9\textwidth]{nov_29_align.pdf}
-    \caption{Panel (a): the flare arcade in AIA 131 {\AA}.
-Panel (b): {\it Hinode}/XRT Be-Med soft X-ray image recorded almost at the same time.
-Panel (c):  the DEM weighted temperature map of the region for $5~<log(T)~<7.4$.
-Panel (d): the emission measure map of the region for $5~<log(T)~<7.4$}
-    \label{fig:flare2}
-\end{figure*}
-%%--------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Determining the LOS}\label{sec:los}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To determine the line of sight (LOS) along individual pixels in the field of view (FOV), we initially estimate the height of the flare loop using observations from different vantage points.
-STEREO-A/EUVI observed both events from a different angle compared to AIA, resulting in geometric effects on the observations.
-
-Fig.\ref{fig:flare_orient}a & b illustrates the geometric effect of observing from different vantage points.
-The magenta cross in Fig.\ref{fig:flare_orient}a represents a point at the top of the flare arcade.
-The LOS extends into the page through that point from the STEREO-A vantage.
-The red line in Fig.\ref{fig:flare_orient}b shows the LOS through the point in Fig.\ref{fig:flare_orient}a projected to the SDO/AIA point of view.
-Similar projections are shown in Fig.~\ref{fig:flare_orient2} for the Nov 29, 2020 flare.
-
-To calculate the height of the flare loop, we utilize co-temporal STEREO-A 171 {\AA}, 195 {\AA}, and AIA 171 {\AA}, 193 {\AA} images with \textit{scc\_measure.pro}, available in the \textit{sswidl}.
-This routine enables us to select a point on the observation from one vantage point, and the LOS through the same point is shown on the observation from the other vantage point.
-By identifying similar emission characteristics, we can determine the 3D coordinates of the point (heliographic latitude, longitude, and radial distance).
-This measurement is repeated at various positions along the loop top to calculate the change in loop height across the arcade.
-However, it is important to note that the height estimation using \textit{scc\_measure.pro} is limited by our ability to identify ``similar emission characteristics'' between the AIA and STEREO-A observations.
-
-%%--------------
-\begin{figure*}[ht!]
-    \centering
-    \includegraphics[width=\textwidth,trim={2cm 6cm 2cm 6cm},clip]{flare_orient.pdf}
-    \caption{Panel (a): {\it STEREO-A}/EUVI 171 {\AA} observation of the flare arcade in the decay phase.
-The magenta cross marks a point on the top of the arcade.
-The LOS goes into the page through that point.
-Panel (b): SDO/AIA 171 {\AA} observation of the flare arcade.
-The red line marks the LOS through the arcade from the STEREO-A perspective projected to the AIA perspective.}
-    \label{fig:flare_orient}
-\end{figure*}
-%%--------------
-
-%%--------------
-\begin{figure*}[ht!]
-    \centering
-    \includegraphics[width=0.9\textwidth,trim={4cm 5cm 3cm 5cm},clip]{nov29_triangulate.pdf}
-    \caption{Panel (a): SDO/AIA 193 {\AA} observation of the Nov 29 flare in the decay phase.
-The blue cross marks a point on the top of the arcade.
-The LOS goes into the page from AIA perspective.
-Panel (b): {\it STEREO-A}/EUVI 195 {\AA} observation around same time.
-The blue solid line is the LOS from AIA perspective in panel (a) projected onto {\it STEREO-A} perspective.
-We can trace out the height of the flare arcade at various locations using \textit{scc\_measure.pro}.
-The height of the arcade at various points from the Sun's surface is marked in panel (a).}
-    \label{fig:flare_orient2}
-    \end{figure*}
-%%--------------
-
-%%--------------
-\begin{figure*}[ht!]
-    \centering
-    \includegraphics[width=0.8\textwidth,trim={3cm 2cm 3cm 0cm},clip]{flare_orient_pt2.pdf}
-    \caption{Panel (a): Cartoon demonstrating the projection effects of a semicircular loop between STEREO-A and AIA vantages due to the difference between polar ($\theta$) and azimuthal ($\phi$) angles, respectively.
-Panel (b) : The calculated LOS map from the AIA perspective, with the estimated loop top height under the assumption of a semi-circular loop geometry.}
-    \label{fig:flare_orient_2}
-\end{figure*}
-%%--------------
-
-To determine the extent of the flare arcade, we select pixels within an emission measure contour of 5\% of the peak emission measure value.
-This contour is calculated based on the emission measure inferred from the DEM, which reflects the density of plasma across the temperature range of $5<\log,(T)<7.4$.
-This approach provides a more comprehensive estimate of the flare arcade compared to methods based solely on intensity observations, which may miss significant portions of the arcade due to the highly multi-thermal nature of the plasma.
-Outside of the flare arcade, we assume a line of sight (LOS) thickness of approximately 2 Mm, corresponding to the average thickness of the chromosphere.
-
-Fig.
-\ref{fig:flare_orient_2}b illustrates an example of the calculated LOS in the field of view (FOV) for the October 28, 2021 flare.
-The highest point of the flare arcade follows the ridge from southeast to northwest.
-An estimate of the highest point of the loop is approximately 22 Mm, consistent with previous estimates of the ridge height around 20 Mm from magnetic loop modeling \citep{longcope22}.
-Using the LOS map shown in the bottom panel of Fig.
-\ref{fig:flare_orient_2}, we calculate the thermal energy in every pixel of the flare using Equation \ref{eq:t_eneg}.
-This process is repeated for the flare loops in the November 29, 2020 event.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Energy in the non-thermal electrons}\label{sec:non-therm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To estimate the energy deposited by the non-thermal electrons in the X-class event on October 28, 2021, we analyze the STIX spectra.
-Figure \ref{fig:stix_an}.a illustrates the STIX light curve for different energy bands: 4 to 6 keV (solid black line), 6 to 12 keV (solid magenta line), 12 to 25 keV (solid yellow line), and 25 to 50 keV (solid blue line).
-The attenuator was activated around 15:28 UT to prevent saturation, notably reducing the intensity.
-The hard X-ray peak appears around 25 to 50 keV at approximately 15:28 UT, while the soft X-ray peak is discernible within the attenuated flux in the 6 to 12 keV band at approximately 15:30 UT.
-
-Following the methodology outlined in \cite{emslie12}, we fit the STIX spectra at various time intervals during the flare's evolution using the `2vth' and `thick2' functions available in the OSPEX X-ray spectra fitting package within `{\it sswidl}'.
-A representative fit is depicted in Figure \ref{fig:stix_an} panel (b) for the time bin around 15:26-15:27 UT using the `2vth' (solid yellow) and `thick2' (solid green) functions.
-The `2vth' function represents a two-component thermal model, with parameters for emission measure, temperature of the thermal components, and relative abundances of various elements with respect to CHIANTI coronal abundances \citep{chianti1,chianti}.
-On the other hand, the `thick2' function assumes a non-thermal component attributed to bremsstrahlung from energetic electrons, described by a broken power-law injected spectrum $F_{0}(E_{0})~(e^{-}s^{-1}cm^{-2}keV^{-1})$ :
-
-%%--------
-\begin{equation}
-    F_{0}(E_{0})=A
-    \begin{cases}
-        0, & E_{0}<E_{min} \\
-        E_{0}^{-\delta_{1}}, & E_{min} \le E_{0} < E_{b} \\
-        E_{0}^{-\delta_{2}}E_{b}^{\delta_{2}-\delta_{1}}, & E_{b} \le E_{0} < E_{max} \\
-        0, & E_{max} \le E_{0}
-    \end{cases}
-\end{equation}
-%%--------
-
-In the fitting process, the model spectrum parameters, such as the normalization parameter \( A \), the low- and high-energy cutoffs \( E_{\text{min}} \) and \( E_{\text{max}} \), the break energy \( E_{\text{b}} \), and the power law indices \( \delta_{1} \) and \( \delta_{2} \) below and above the break, are constrained.
-We set the high-energy cutoff at \( 3.2 \times 10^{4} \) keV for all fits, as it is significantly higher than the energy range of interest (around \( 10^{1} \) keV), making its effect on the X-ray spectra negligible \citep{emslie12}.
-
-The fitting procedure in `\textit{OSPEX}' is a forward fitting process.
-The parameters of the `\textit{2vth}' and `\textit{thick2}' functions are adjusted to generate a photon spectrum, which is then convolved through the detector response matrix to produce a count rate spectrum.
-This count rate spectrum is compared with the measured count rate spectrum, and an iterative process minimizes the \( \chi^{2} \) between them to refine the parameter estimates.
-
-Table \ref{tab1} presents the fitted temperature of the hotter thermal component at various phases of the flare.
-These temperatures align with the temperature range (\( \log(T_{\text{max}}) = 7.4 \) and \( \log(T_{\text{min}}) = 5 \)) used to calculate the emission measure (EM) and differential emission measure (DEM) weighted temperature, as discussed in Section \ref{sec:therm}.
-
-%%%%%%%%%%%
-\begin{table*}[ht!]
-    \centering
-    \begin{tabular}{|cl||c|c|}
-    \hline
-         &  & log(T) & EM \\ 
-         & \hspace{-1cm}Time (UT) & of hotter component & ($cm^{-3}$) \\
-    \hline
-        Impulsive phase & \hspace{1cm}15:26 & 7.098 & $10^{48}$\\
-        HXR peak & $\sim$ 15:27:20 - 15:28:20 & 7.19 & $3\times 10^{48}$\\
-        Right after SXR peak & $\sim$ 15:35:39 - 15:36:34 & 6.88 & $4.1\times 10^{49}$\\
-        Into the decay phase & \hspace{0.9cm}14:48:20 & 6.5 & $2\times 10^{49}$\\
-        \hline
-    \end{tabular}
-    \caption{Fitted temperature of the hotter component of the thermal plasma during various stages of the flare.}
-    \label{tab1}
-\end{table*}
-%%%%%%%%%%%
-
-The non-thermal energy in the electrons (\( U_{e} \)) at any instant \( t = t' \) can be estimated by integrating the best-fit electron energy spectrum:
-\[
-U_{e}(t=t') = \Delta t \int_{E_{\text{min}}}^{E_{\text{max}}} F_{0}(E_{0})(t=t') dE_{0}
-\]
-where the electron energy distribution is constrained by fitting the count spectra for the time interval \( t' - \Delta t/2 \leq t \leq t' + \Delta t/2 \).
-
-The cumulative energy deposited into the footpoint over time by the non-thermal electrons is a good indicator of the source of the thermal energy of the plasma.
-We can estimate the cumulative energy deposited by the non-thermal electrons up until a certain instant \( t \) by summing the energy deposited at the footpoints from every time bin:
-\[
-U^{cumulative}_{e}(t) = \sum_{t'=t_{0}}^{t} U_{e}(t')
-\]
-
-%%--------------
-\begin{figure*}[ht!]
-    \centering
-    \includegraphics[trim={3cm 2cm 6cm 3.5cm},clip,width=0.54\textwidth]{oct28_lc_2.pdf} 
-    \includegraphics[trim={3.5cm 8cm 3cm 2cm},clip,width=0.45\textwidth]{oct28_fit_2.pdf}
-    \caption{Panel (a): STIX light curve of the 2021 Oct 28 X-class event in different energy bands as labelled.
-The black, magenta, yellow and blue solid lines show the light curve in 4{--}6~keV, 6{--}12~keV, 12{--}25~keV and 25{--}50 keV.
-Panel (b): STIX spectra fit at 15:27{--}15:28 UT, during impulsive phase.
-We fit the spectra with `\textit{thcik2}' (green solid line) and `\textit{2vth}' (yellow solid line).
-We show the complete fit function `\textit{2vth+thick2}' with the solid red line.
-The lower panel shows the normalized residuals of the fit.}
-    \label{fig:stix_an}
-    \end{figure*}
-%%--------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{res}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%###########%%
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[trim={4cm 1cm 4cm 1cm},clip,width=0.8\textwidth]{flare_eneg.pdf}
-    \caption{Panel (a): The calculated thermal energy as a function of time for the 2021 Oct 28 flare.
-The magenta dot-dashed line shows the thermal energy calculated from the GOES light-curve using the effective volume and a filling factor \textit{f}~=~1.
-The red dot-dashed line and the black dashed line shows the energy calculated from the GOES light-curve and the effective volume with filling factor \textit{f}~=~0.4 and \textit{f}~=~0.2, respectively.
-The blue solid line shows the thermal energy estimated using the DEMs calculated from the AIA obeservations.
-The black solid line shows the thermal energy calculated from the GOES light curve, but the volume inferred from the area of the of the flaring arcade with STIX SXR images, under the assumption that $V\sim A^{\frac{3}{2}}$.
-Panel (b): The calculated thermal energy as a function of time for the 2020 Nov 29 flare.
-The red line shows the thermal energy calculated from the GOES light curves, using a constant effective volume.
-The blue curve shows the thermal energy calculated from the DEMs inferred from the imaging and a varying volume from the imaging.}
-    \label{fig:eneg}
-\end{figure}
-%%###########%%
-
-%%###########%%
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[trim={2cm 0cm 1cm 0cm},clip,width=0.8\textwidth]{fan_eneg.pdf}
-    \caption{Calculated thermal energy for the 2020 Nov 29 flare.
-Total thermal energy of the flare (blue dot-dashed) in comparison to the thermal energy from the fan (red dashed).
-The magenta and the green solid line show the fit to the thermal energy output to the fan and the loop's thermal output.
-Fermi hard X-ray count (black) peaks around the same time as the total thermal output.}
-    \label{fig:fan_eneg}
-    \end{figure}
-%%###########%%
-
-Figure~\ref{fig:eneg}.a shows the thermal and non-thermal energy calculated for the 2021 October 28 event.
-The black solid curve with crosses shows the thermal energy calculated from the DEMs.
-The red solid curve shows the thermal energy calculated from the {\it GOES} light curve and the effective volume calculated assuming an RTV loop \citep{rtv78,serio91}.
-We use the {\it GOES} emission measure, temperature with a volume filling factor \textit{f}~=~1, to estimate an effective loop length for the flare and from that, calculate an effective volume.
-Note that the implicit assumption of mechanical equilibrium only holds during the decay phase of the flare.
-So, the effective volume estimated here would only be appropriate in the decay phase.
-The green solid curve with triangles and the blue solid curve with squares show the same {\it GOES} thermal energy, with volume filling factor \textit{f}~=~0.4 and \textit{f}~=~0.2, respectively.
-The blue dashed curve shows the thermal energy calculated from the {\it GOES} light curve, but the volume inferred from the area of the flaring region from the STIX soft X-ray contours, under the assumption that $V\sim A^{\frac{3}{2}}$.
-
-The lime green solid line with circles in Fig.~\ref{fig:eneg}.a, shows the cumulative energy in the non-thermal electrons.
-This quantity is the amount of energy deposited at the flare foot points, and one of the sources of the thermal energy of the flare.
-The cumulative non-thermal energy of electrons $\simeq~1.2\times 10^{31}$ erg $>$ peak thermal energy calculated from the DEM estimates $\simeq~5\times 10^{30}$ erg.
-This is usual for an X-class flare.
-The differences in the estimates of thermal energy, due to different estimations of volume, also affects the partition between the thermal and non-thermal energies of flares.
-The efficiency of converting the energy deposited by non-thermal electrons into the thermal energy of the ambient plasma results in this partition and as a result, the volume estimation is a key parameter in understanding the conversion of non-thermal energy into thermal energy in flares.
-
-The interesting trend in Fig.~\ref{fig:eneg}.a is that the thermal energy calculated from the constrained DEMs (solid black curve with crosses) is closer to a volume filling factor \textit{f}~=~0.2 in the impulsive phase, but is asymptotic with a filling factor \textit{f}~=~1 (solid red curve) during the decay phase.
-This indicates that the flare loops during the impulsive phase do not fill up apparent volumes similar to those in the decay phase.
-The change in the effective filling factor is indicative of the sharp change in the volume during the impulsive phase.
-
-For the 2020 November 29 event, the {\it STEREO-A} perspective looks down into the supra-arcade plasma sheet.
-Thus the LOS of this feature can not be calculated as demonstrated in Section \ref{sec:los} for the supra-arcade pixels.
-For the supra-arcade fan pixels in the FOV, we assume a LOS $\simeq~8~\textrm{Mm}$, as suggested in several other studies \citep[see e.g.,][]{savage10,seaton17,li18}.
-We use these calculated LOS maps, along with equation~\ref{eq:t_eneg_1} to estimate the thermal energy as a function of time.
-
-Figure \ref{fig:eneg}.b shows the energy calculated for the November 29th event.
-The blue solid curve shows the thermal energy calculated from the DEMs.
-The red solid curve shows the thermal energy calculated from the GOES light curves and the constant effective volume calculated assuming an RTV loop with a volume filling factor \textit{f}~=~1.
-The thermal energy shows similar characteristics as the October 28th, 2021 event.
-The RTV loop effective volume clearly is an overestimation in the rise phase of the the flare, and agrees very well in the decay phase.
-
-There have been several studies that suggest that the plasma in the fan is directly heated \citep{hanneman14,chen17,reeves17,warren18,cai22,xie23}.
-Unlike the flare arcade, the thermal output of the fan is not directly related to the energy deposited by the non-thermal electrons and ions at the foot point.
-Hence, this different mechanism should also be reflected in the time evolution of the thermal output of the fan, compared to the thermal output of the loops.
-Under the assumption of the LOS~$\mathrm{\sim 8~Mm}$ in the fan region, we separately calculate the contribution from the fan to the total thermal energy for the 2020 Nov 29 event.
-
-Figure~\ref{fig:fan_eneg} shows the thermal energy of the fan as a function of time (red dashed line) in comparison to the total thermal energy of the 2020 Nov 29 event (blue dot-dashed line).
-The thermal energy form the fan is $\sim$ two orders of magnitude lower than the total thermal energy of the event.
-The thermal energy of the fan also peaks much later ($\sim$ 20 minutes) compared to the total thermal energy.
-After the thermal energy of the fan peaks, the thermal energy of the fan (red + sign) and the total thermal energy of the event (blue crosses) are fitted with a power law of the form $at^{-\delta}$ as a function of time.
-The fits are shown with magenta and green solid line for the fan and the total thermal energy, respectively.
-The value of the power law index are -0.95 and -1.1, respectively, for the fan and the total thermal output.
-The plots shows that the thermal energy of the fan decay slower compared to the total thermal output.
-The normalized {\it Fermi} GBM 25 {--} 80 keV count rate (black solid line) peaks at a similar time as the total thermal energy of the event.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Outlook}\label{sec:out}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We have used AIA, SUVI, and XRT observations to calculate DEM maps and estimate the thermal energy for two solar flares as a function of time.
-We have used observations from AIA and {\it STEREO-A} to calculate the geometry of the flare loops and estimate the LOS for the AIA observations.
-We have shown that the accurate estimation of volume can have significant implications for thermal energy estimates.
-For the 2020 November 20 flare, we have also estimated the thermal energy for the fan and compared the evolution of the thermal energy of the fan with respect to the total thermal energy of the event.
-We have shown that the thermal energy of the fan decays slower compared to the total thermal energy of the event.
-This result suggests that a fundamentally different heating mechanism is responsible for the thermal output of the fan.
-
-The thermal energy of the flares is given as, $U_{Th}\simeq 3n_{e}k_{B}TVf$.
-The electron number density is given by, $n_{e}~=~\sqrt{\sfrac{EM^{v}}{Vf}}~\implies~U_{Th}~=~3k_{B}T\sqrt{EM^{v}\times~Vf}$, where $EM^{v}$ is the volume emission measure (in units of $cm^{-3}$).
-A filling factor, \textit{f} $<$ 1 decreases the thermal energy by $\sim f^{\sfrac{1}{2}}$.
-There are very diverse results reported on \textit{f}.
-X-ray observations have generally constrained within $0.1<\textit{f}<1$\citep{jak11,guo12}, while it is usually constrained to much lower values $0.001<\textit{f}<0.1$ in EUV\citep{ash&ash08}.
-The filling factor can also be constrained by imposing the requirement that the flare plasma has to be contained via magnetic pressure.
-From this constraint it can be inferred that the required coronal magnetic field strength $B_{cor}$ $\sim f^{-\sfrac{1}{4}}$\citep{caspi14,warmuth16a,warmuth16b}.
-These studies rule out values of $\textit{f}<0.1$.
-Similar results were obtained from spectroscopic observations of density sensitive \ion{Fe}{11} lines \citep{miligan12}.
-
-It is easy to infer from our findings that a single value of volume filling factor is inadequate to describe the evolution of thermal energy throughout the duration of the flare.
-We need to estimate the volume as a function of time rather than depending on a filling factor.
-In Fig.~\ref{fig:eneg}.a, the thermal energy calculated from {\it GOES} with various filling factors demonstrates this concept perfectly.
-During the impulsive phase, the thermal energy calculated from the DEMs is consistent with \textit{f}=0.2, and later in the decay phase, it is consistent with \textit{f}=1.
-This result demonstrates how the volume of the flare arcade is changing over time with respect to the volume in the decay phase.
-The thermal energy calculated from $V\sim A^{\frac{3}{2}}$ assumption agrees well with the thermal energy calculated from constrained DEMs in the decay phase.
-But it still predicts higher energy in the impulsive phase.
-This discrepancy might signify that the assumption of self-similar expansion might not be valid at the initial sharp rise in the impulsive phase for some flares.
-
-Our results are in line with the findings of \cite{hilarie05}.
-They demonstrated from {\it RHESSI} imaging for a sample of 9 M and C class flares that the volume estimation with the assumption of self-similar expansion resulted in thermal energy higher than the non-thermal energy during the impulsive phase (For more details, refer to \cite{hilarie05} Table 5 and the corresponding discussion).
-A statistically inferred representative filling factor might serve perfectly well for estimating the energies near the thermal peak for a sample of flares.
-Since we are trying to quantify the evolution of the energy over time for individual flares, we require more accurate estimates of the volume.
-
-Our results also demonstrate the utility of estimating the volume from different vantages as a function of time.
-For events like the X-class event on 2021 October 28, the on-disk imaging allows the estimation of the volume from the flare ribbon area under the assumption of self-similar expansion.
-But for scenarios like the limb event 2020 November 29, where the flare ribbons are not visible from any imaging observation, or the visible foot point and/or visible portions of the loop are projected at a very high angle, estimating the volume of the loop by calculating the height of the loop at various points serves as an important tool in estimating the thermal energy at various phases of the flare.
-
-In Figure~\ref{fig:fan_eneg}, the thermal energy from the fan (red dashed line ) is $\sim$ two orders of magnitude lower than the total thermal energy of the event (blue dot-dashed line).
-The thermal energy also peaks much later ($\sim$ 20 minutes) compared to the total thermal energy.
-This result shows that the fan plasma is being heated directly by a process different from the flare arcade (e.g.
-SADs \citep{reeves17}, plasma flow turbulence \citep{xie23}).
-The fan also cools slower than the arcade, which indicates that either continuous heating is present in the fan during the decay phase of the flare or there is suppression of cooling \citep[e.g.][]{xie23}.
-The event had both foot points occulted from the Earth's perspective, so it is a fair assumption that most of the hard X-ray is from the loop top coronal source.
-This circumstance explains the near-simultaneous peak in {\it Fermi} hard X-ray (black solid line) and the thermal energy peak from the flare.
-
-Our results exhibit the importance of different solar missions that can observe the Sun with higher spatial resolution (to resolve the finer structures better) and from various vantages (to triangulate the geometry).
-The ability to spatially resolve the temperature structure of the flaring plasma not only gives us a better estimation of the thermal energy, but it also allows us to spatially separate various portions of the flaring plasma (e.g.
-for the 2020 November 29 event, we could separate the contribution of the fan from the total thermal energy).
-This separation enabled us to demonstrate that a different heating mechanism was at play in the fan.
-However, we do note that the reliability of any such estimations needs to be rigorously tested with observations of various flares from various geometric projections.
+The {\it Aditya-L1} was launched on September 2nd, 2023.
+The first light observations were made on December 5th, 2023 while the payload was still in cruise phase.
+For the majority of the cruise phase the payload only operated in the 2k synoptic mode, i.e.
+it only captured continuous (2k $\times$ 2k) observations in NB4 (\ion{Mg}{2} h line) with one minute cadence.
+The L1 insertion was carried out on January 6th, 2024.
+Following that the payload also started taking (4k $\times$ 4k) observations in all eleven science filters.
+Various components of the flare detection algorithm were progressively turned on.
+In this chapter we discuss some of the initial flare observations made by SUIT.
+The first flare triggered by the flare detection algorithm was a X6.3 flare from north-west corner of the disk, which was also observed by several other instruments {\it e.g.} {\it SDO}/AIA, {\it IRIS}, {\it SO}/STIX.

### 2024-07-27 chapter5/ms.tex
Updates from Overleaf

@@
     \begin{center}
-        \includegraphics[trim={4.5cm 5.5cm 6cm 4cm},clip,width=0.9\textwidth]{Figures/nov_flare_aia_waves_2.pdf}
+        \includegraphics[trim={4.5cm 5.5cm 6cm 4cm},clip,width=\textwidth]{Figures/nov_flare_aia_waves_2.pdf}
     \end{center}
@@
 
+%%%%-------------------------
+\begin{figure}[ht!]
+\centering  
+\vspace{10cm}
+\includegraphics[trim={7cm 5cm 6cm 15cm},width=0.7\textwidth]{Figures/m_flare_iris.pdf}
+\caption{Obtained images in  \ion{Mg}{2} h (panel a) and k (panel b) and corresponding co-aligned and artificially rastered HMI LOS magnetic field map (panel c) for the M3.7 flare observed on November 4th, 2015.
+The magenta and lime green contours on panel c show the contours of  \ion{Mg}{2}~h (panel a) and k (panel b) intensity.} \label{fig:aligned_raster}
+\end{figure}
+%%%%-------------------------
+
 For analyzing the properties of the  \ion{Mg}{2} lines, we fit a double Gaussian profile to both the k and h lines with a linear background symmetric about the line core.
@@
 Additionally, we exclude any pixels showing saturation in either of the lines.
-The uncertainty of the observed intensities is measured in DN (Data Numbers) using the method outlined in \S 2:1 of \cite{kerr15} and subsequently applied in the fitting procedure.
+The uncertainty of the observed intensities is measured in DN (Data Numbers) using the method outlined in \S2.1 of \cite{kerr15} and subsequently applied in the fitting procedure.
 The uncertainties of the fitted Gaussian profiles are incorporated while integrating the profile to obtain the uncertainty of the line intensities.
-
-%%%%-------------------------
-\begin{figure}[h!]
-\centering  
-\includegraphics[trim={7cm 5cm 6cm 10cm},width=0.8\textwidth]{Figures/m_flare_iris.pdf}
-\caption{Obtained images in  \ion{Mg}{2} h (panel a) and k (panel b) and corresponding co-aligned and artificially rastered HMI LOS magnetic field map (panel c) for the M3.7 flare observed on November 4th, 2015.
-The magenta and lime green contours on panel c show the contours of  \ion{Mg}{2}~h (panel a) and k (panel b) intensity.} \label{fig:aligned_raster}
-\end{figure}
-%%%%-------------------------
 
@@
 To investigate the  \ion{Mg}{2} k to h intensity line ratios over time, we selected two pixels—one in the northern ribbon and another in the southern ribbon, as indicated by crosses.
-Fig.\ref{fig:pix_fit_ribbon} displays the spectra overlaid with fits for the two pixels taken in the northern ribbon (top panel) and southern ribbon (bottom panel) obtained at different times.
+Fig.~\ref{fig:pix_fit_ribbon} displays the spectra overlaid with fits for the two pixels taken in the northern ribbon (top panel) and southern ribbon (bottom panel) obtained at different times.
 
@@
 %%--------------------------------------------------
-\begin{figure*}[ht!]
+\begin{figure}[ht!]
     \centering
@@
 The over-plotted white (black) box in panel b (c) represents the IRIS SJI FOV, and white dot-dashed (dashed) box in panels b (c) represents the IRIS Raster FOV.}\label{flare2}
-\end{figure*}
+\end{figure}
 %%--------------------------------------------------

### 2024-07-27 chapter7/ms.tex
Updates from Overleaf

@@
 In this chapter we discuss some of the initial flare observations made by SUIT.
-The first flare triggered by the flare detection algorithm was a X6.3 flare from north-west corner of the disk, which was also observed by several other instruments {\it e.g.} {\it SDO}/AIA, {\it IRIS}, {\it SO}/STIX.
+The first flare triggered by the flare detection algorithm was a X6.3 flare from north-west corner of the disk on February 22nd, 2024, which was also observed by several other instruments {\it e.g.} {\it SDO}/AIA, {\it IRIS}, {\it SO}/STIX.
+During the cruise phase, SUIT also observed a X1 flare from the south-east limb of the Sun on December 31st, 2023.
+We only have observations in the NB4 (\ion{Mg}{2} h line) channel for this flare.
+But this provides us with an unprecedented view of post-flare loops and possibly reconnection slingshot in the \ion{Mg}{2} line.
+Subsequent portions of this chapter will be divided into two parts, where we discuss the observations of these two flares separately.
+
+%%----------------------------------------------------
+\section{X6.3 flare observed on Feb 22nd, 2024} \label{sec:feb_22nd}
+%%----------------------------------------------------
+
+NOAA AR 13590 was visible on the north-east of the Solar disk on February 22, 2024.
+The AR was around a large sunspot in a cluster of sunspots, accompanied by a complex magnetic field structure.
+The active region flared multiple times during the same day, including an X1.7 flare that peaked around $\sim$ 06:32 UT, an M4.8 flare that peaked around $\sim$ 20:46 UT and an X6.3 flare that peaked $\sim$ 22:34 UT .
+\suit~is equipped with an onboard flare detection algorithm.
+Once the flare detection algorithm flags a flare and localizes the position of the flare on the detector, the program sequence prioritizes reading a fixed smaller Region of Interest (RoI) around the location for fast, higher cadence observation (for further details, please refer to \cite{flare_det}).
+The X6.3 flare was one of the first flares to be localized by the on-board flare detection algorithm.
+\suit~did not observe the X1.7 flare because, during that time, the payload was off-pointed to verify the stellar calibration program sequences.
+The flares were also observed by {\it SDO}/AIA, {\it SO}/STIX.
+{\it IRIS} observed the eastern edge of the X6.3 flare ribbons in a small [66\arcsec,62\arcsec] field of view (FoV) with a 4 step raster and 15 s raster cadence.
+
+We show the light curve arising from the whole RoI observation in comparison to {\it GOES} flux in Fig.~\ref{fig:flare_full}.
+In Fig.~\ref{fig:flare_full}.b, we plot the AIA 1600 {\AA} (dashed blue line) and AIA 1700 {\AA} (black dot-dashed line), in comparison to the {\it GOES} 1 {--} 8 {\AA} light curve (Solid red line) for both the flares.
+In Fig.~\ref{fig:flare_full}.b, we show the GOES 1 {--} 8 {\AA} light curve in comparison to the NB3 (\ion{Mg}{2} k 279.6 nm, black dotted), NB4 (\ion{Mg}{2} h 280.3 nm, green dot-dashed) and NB8 (\ion{Ca}{2} h 396.85 nm, magenta dashed) light curves.
+NB4 light curve is offset from NB3 by -0.1 for better visibility.
+The NB8 light curve exhibits lower contrast and does not show a sharp peak compared to NB3 and NB4.
+The other interesting trend is exhibited by the continuum channels NB5, NB6 and NB7 in Fig.~\ref{fig:flare_full}.c, as a conspicuous rise in the continuum intensity is seen after both flares.
+In Fig.~\ref{fig:flare_full}.d we plot the {\it GOES} 1 {--} 8 {\AA} light curve in comparison to the STIX hard (25 {--} 50 keV, black dashed) and soft (5 {--} 10 keV, green dotted) X-ray light curve.
+The hard X-ray observation from STIX peaks at a time similar to that of NB3, NB4, and NB8.
+
+%%%%%%%%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.8\textwidth,trim={2.3cm 2.5cm 1cm 4.5cm},clip]{lc_full_suit_contour.pdf}
+    \caption{Light curves from the whole RoI FoV of \suit~observations compared with AIA, {\it GOES} and STIX observation for the two flares.}
+    \label{fig:flare_full}
+\end{figure}
+%%%%%%%%%
+
+The X6.3 flare provides a good example of the response of the local plasma environment to the flare in the Near Ultraviolet (NUV) regime in 200 {--} 400 nm.
+The flare peaked around $\sim$ 22:34 UT in the {\it GOES} observation.
+Images from six narrow band (NB) channels of \suit~ are shown in Fig.~\ref{fig:flare_nb3_peak} top panel at around $\sim$ 22:28-22:29 UT.
+This is at the peak of the NB3 (\ion{Mg}{2} k 279.6 nm) channel, as observed by \suit.
+The 60\% peak intensity contour of the NB3 intensity is marked with the black line in all figures of Fig.~\ref{fig:flare_nb3_peak} top panel.
+From the figure, we also see a similar structure in the NB4 (\ion{Mg}{2} h 280.3 nm) and NB8 (\ion{Ca}{2} h 396.9 nm).
+No similar structure is observed in the other continuum channels of Fig.~\ref{fig:flare_nb3_peak} top panel.
+
+In Fig.~\ref{fig:flare_nb3_peak} bottom panel, we show the flare observations by \suit~ at their respective peaks.
+Again, we see very similar structures in NB3, NB4, and NB8.
+NB3 and NB4 peak at almost the same time $\sim$ 22:29 UT.
+Although NB8 shows a similar structure, the peak intensity of NB8 is observed slightly later around $\sim$ 22:29:41 UT.
+The peak intensities of the other continuum NB channels are observed progressively later.
+The NB5 (Red wing of the Mg window) peaks around $\sim$ 22:32:41 UT.
+Faint signatures of flare brightening are observed in NB5, marked with red arrows in Fig.~\ref{fig:flare_nb3_peak} bottom panel.
+No such signatures are observed as clearly in NB6 and NB7.
+Both of these channels peak around $\sim$ 22:28 UT.
+
+%%%%%%%%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={0cm 0.65cm 0cm 0cm},clip,width=0.5\textwidth]{suit_roi_nb3_peak.pdf} \\
+    \includegraphics[width=0.5\textwidth]{suit_roi_all_peak.pdf}
+    \caption{\suit~observations of the flare from various NB filters. Top panel: during NB3 peak. Bottom panel: During the peak of individual bands.}
+    \label{fig:flare_nb3_peak}
+\end{figure}
+%%%%%%%%%
+
+In Fig.~\ref{fig:flare_lc_suit}, we plot the light curve of the event to compare the observations across various bands.
+The AIA and \suit~ light curves in Fig.~\ref{fig:flare_lc_suit} are calculated by adding the counts within the region of 60\% peak intensity contour of NB3 (shown in Fig.~\ref{fig:flare_nb3_peak} top panel), after co-aligning and registering the AIA and \suit~observations and normalizing them to the peak intensity.
+In Fig.~\ref{fig:flare_lc_suit}.a, we show the GOES 1 {--} 8 {\AA} light curve in comparison to AIA 1600 {\AA} and AIA 1700 {\AA}.
+The AIA 1600 and 1700 {\AA} light curve peaks around $\sim$ 5 minutes earlier than the {\it GOES} peak.
+
+In Fig.~\ref{fig:flare_lc_suit}.b, we show the GOES 1 {--} 8 {\AA} light curve in comparison to the NB3, NB4 and NB8 light curves.
+All the NB light curves behave remarkably similarly.
+The vertical dotted black line across all the panels in Fig.~\ref{fig:flare_lc_suit} denotes the peak intensity in NB3.
+NB3, NB4, and NB8 peaks around $\sim$ 22:29 UT, which is very similar to AIA 1600 {\AA} and 1700 {\AA}.
+We also plot the {\it GONG}-H$\alpha$ light curve from the \suit~contour region.
+The {\it GONG} light curve also peaks at around $\sim$ 22:29 UT.
+Both NB8 and {\it GONG}-H$\alpha$ shows less contrast variation in the light curve than NB3 and NB4.
+
+We show the GOES 1 {--} 8 {\AA} light curve in comparison to the NB5 (Red wing of the Mg lines, blue dashed), NB6 and NB7 continuum channels in Fig.~\ref{fig:flare_lc_suit}.c.
+NB5 shows signs of flare response, although much weaker than NB3, NB4 and NB8.
+NB5 peaks around $\sim$ 22:31 UT, about $\sim$ 3 minutes later than NB3.
+Similar traits were observed from the images also, as pointed out in Fig.~\ref{fig:flare_nb3_peak} bottom panel and the accompanying discussions.
+More interestingly, NB6 and NB7 do not show the hallmark sign of a flare light curve, i.e.
+gradual increase and decrease in the intensity.
+These bands exhibit a slow but steady rise in intensity after the flare.
+Finally, in Fig.~\ref{fig:flare_lc_suit}.d, we show the {\it GOES} 1 {--} 8 {\AA} light curve in comparison to the STIX hard and soft X-ray light curve.
+The hard X-ray peaks around a similar time around $\sim$ 22:29 UT, similar to NB3, NB4 and AIA 1600 and 1700 {\AA}.
+
+%%%%%%%%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.8\textwidth,trim={2.3cm 2.5cm 0cm 4.5cm},clip]{lc_suit_contour.pdf}
+    \caption{Light curves from the pixels within intensity contour picked from \suit~and co-aligned AIA observations.
+The NB4 light curve in the second panel is offset by -0.1 from NB3 for better visibility.
+The vertical dotted dark line marks the flare's peak in NB3 observation.}
+    \label{fig:flare_lc_suit}
+\end{figure}
+%%%%%%%%%
+
+%%%%%%% ############# %%%%%%%
+\subsection{XSM-spectra}\label{sec:xsm}
+%%%%%%% ############# %%%%%%%
+
+The Solar X-ray monitor on {\it Chandrayan-2}\citep[{\it Chandrayan-2}/XSM,][]{xsm} provides sun as a star soft X-ray spectra in 1{--}15 keV with 1s cadence and significantly better spectral resolution (180 eV at 5.9 keV) compared to STIX (1 keV ar 5.9 keV).
+The high spectral and temporal resolution allows us to measure the change in elemental abundances over the duration of the flares.
+XSM observed both flares with coverage in both impulsive and decay phase.
+The existing studies with XSM has successfully studies the thermal and elemental abundance evolution of various flares \citep{mondal21,kkepa23,nama23}.
+
+Both the M and X-class flares were observed by XSM.
+The XSM 1{--}8 {\AA} light curves are plotted in Fig.~\ref{fig:xsm-obs} top panel.
+The red shaded region marks the time window where the Be filter was inserted to prevent saturation.
+There are periodic gaps in the data due to periodic lunar occultation.
+We show the spectra obtained by XSM in Fig.~\ref{fig:xsm-obs} bottom panel, during various phases of the flare.
+The violet spectra at 22:33 UT is near the flare peak, and shows a sharp decrease below 3 keV due to the insertion of the Be filter to avoid saturation.
+Various Mg, Al, S and Si lines are visible in the pre-flare spectra.
+In stark contrast during impulsive and peak of the flare we see strong signatures of Ca, Ar and Fe.
+Due to the uncertainty of the spectra during the Be window observation in $<~3~\mathrm{keV}$ regime, we fit the spectra beyond 3 keV throughput this analysis.
+We fit the spectra with the XSPEC model {\it chisoth}, which uses a wide range of pre-calculated spectra to fit the observed spectra (For more details please refer to the appendix of \cite{mondal21}).
+
+%%%%%%%%
+\begin{figure}[ht!]
+\centering
+    \includegraphics[trim={0.5cm 3.3cm 0.8cm 4cm}, clip, width=0.76\textwidth]{xsm_lc.pdf} \\
+    \includegraphics[trim={1.8cm 2.5cm 3cm 3cm},clip,width=0.75\textwidth]{xsm_spec.pdf}
+    \caption{Top panel: XSM observation of the two flares.
+The red shaded region marks the window when the Be filter was inserted.
+Bottom panel: X-ray spectra during various phases of the flare.
+The violet spectra is during the soft X-ray peak of the flare and shows a sharp decrease in the intensity below 3 keV.
+This is due to the insertion of Be filter to avoid saturation.}
+    \label{fig:xsm-obs}
+\end{figure}
+%%%%%%%%
+
+%%%%%%% ############# %%%%%%%
+\subsubsection{Fitting XSM spectra}\label{sec:xsm-fit}
+%%%%%%% ############# %%%%%%%
+
+The observed soft X-ray spectra from the flaring plasma can be modelled by an isothermal plasma characterized by various parameters {\it e.g.} temperature, emission measure and abundance of various elements.
+As alluded earlier, we use the `{\it chisoth}' model \citep{mondal21} to fit the observed spectra from XSM.
+The `{\it chisoth}' model uses CHIANTI atomic database \cite{chianti} to calculate spectra for individual elements over a large temperature grid and stores as tables.
+The model includes elements from H (Z=1) to Zn (Z=30).
+The spectra of individual elements are calculated over a wide temperature range (0.3 {--} 50 MK).
+These modelled spectra of various elemental abundance over a wide temperature range are loaded in XSPEC and added with varying weights to fit the observed spectra.
+The Total model spectrum is given by  $$I_{mod}(T)~=~EM\sum_{X}I_{X}(T)N_{X}$$`EM' is the volume emission measure, $N_{X}$ is the abundance of element X relative to H and $I_{X}(T)$ is the modelled spectrum of element X at temperature T.
+The fit is done in a recursive process by minimizing the chi-squared between the observed and modelled spectra.
+
+We initially used an isothermal model to fit the spectra.
+One of the key observations we make is a presence of systematic residual around the Fe complex around $\sim$ 6.5 keV.
+This is illustrated in the top panel of Fig.~\ref{fig:xsm_fit} top panel, where there is an excess visible in the blue side of the Fe line complex at $\sim$ 6.7 keV.
+\cite{mithun22} could not explain this systematic excess with multithermal DEM distributions.
+One of the possible explanation of this excess flux is Fe fluorescence emission.
+There have been observations of Fe line fluorescence at 6.4 keV (Fe K$\alpha$) and 7.06 keV (Fe K$\beta$) \citep{neupert67,doscheck71,bai79,tanaka84,parmar84,phillips12} using high-resolution X-ray spectra from Bent Crystal Spectrometer on-board Solar Maximum Mission \citep[Bent/{\it SMM},][]{bent,smm} and Yokoh \citep{yokoh} mission.
+Previous studies have suggested that this emission arises from the excitation of low ionization state Fe in the Photosphere either via the X-ray from the flaring plasma \citep{bai79} or directly from the non-thermal electron beam \citep{phillips73}.
+The Fe K$\alpha$ fluorescence is usually dependent on the position on the solar disk \citep{parmar84}.
+The emergent Fe K$\alpha$ emission suffers significant absorption and scattering along the line of sight, which increases with increasing heliocentric angle, resulting in a decrease in the observed intensity.
+For our event, the flaring region is near the disk center making the Fe K$\alpha$ fluorescence a valid candidate for explaining the excess.
+We added a Gaussian component to the `{\it chisoth}' model to get better fit (see Fig.~\ref{fig:flare_obs} bottom panel).
+
+We add a Gaussian line component to our fit at 6.4 keV to explore the possibility of the excess flux arising from Fe K$\alpha$ fluorescence.
+We find that this fits the observed spectra better than previous instances, as demonstrated in Fig.~\ref{fig:xsm_fit} bottom panel.
+The K$\alpha$ emission would arise from the X-ray emission from the flaring regions having energies $>$ 7.12 keV, the K edge of Fe, exciting the Fe atoms in the Photosphere.
+We show the intensity of the fitted Fe 6.4 keV component excess (blue solid line), in comparison to the fitted flux in 7.12 {--} 8.5 keV (green dot-dashed line) in Fig.~\ref{fig:fe_excess} top panel.
+For reference, {\it GOES} 1{--}8 {\AA} soft X-ray flux (red dotted line) and STIX 25 {--} 50 keV Hard X-ray flux (black dashed line) are overplotted.
+STIX Hard X-ray is a fair representative of the non-thermal electron flux deposited into the foot points.
+In the bottom panel, the light curve fitted Fe 6.4 keV excess Gaussian component is plotted with the lightcurve from the bright kernels marked with the two boxes in Fig.~\ref{fig:flare_nb3_peak} bottom panel.
+In both panels, the peak time of the Fe excess (blue solid line), STIX hard X-ray (black dashed line) and NB5 brightness from box 1 (dotted magenta line) are marked with vertical lines.
+
+%%%%%%%%%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={0.5cm 1cm 0.5cm 0.7cm}, clip, width=0.77\textwidth]{xsm_fit.pdf}
+    \caption{XSM spectra in 3 {--} 8.5 keV binned between 22:27:20 {--} 22:27:25 UT.
+Top panel shows the fit with ``chisoth+chisoth" model.
+Bottom panel shows the same spectra fitted with ``chisoth+chisoth+gaussian" model.}
+    \label{fig:xsm_fit}
+\end{figure}
+%%%%%%%%%%
+
+%%%%%%%%%%
+\begin{figure}[ht!]
+\centering
+    \includegraphics[trim={1.3cm 0.1cm 0.3cm 1.2cm}, clip, width=0.95\textwidth]{fe_excess_4.pdf}
+    \caption{Fe excess emission from 6.4 keV(blue solid) in comparison to STIX 25-50 keV(black dashed), GOES 1 {--} 8 $\AA$ (dotted red) and XSM 7.12 {--} 8.5 keV (green dot-dashed) light curve.}
+    \label{fig:fe_excess}
+\end{figure}
+%%%%%%%%%%
+
+%%%%%%% ############# %%%%%%%
+\subsection{Discussion}\label{sec:dis1}
+%%%%%%% ############# %%%%%%%
+
+This section reports the \suit~narrow band imaging of the first localized flare by the onboard flare detection algorithm.
+We report the observation in NB3 (\ion{Mg}{2} k 279.6 nm), NB4 (\ion{Mg}{2} h 280.3 nm), NB8 (\ion{Ca}{2} h 396.9 nm) and the continuum channels NB5 (Red wing of \ion{Mg}{2}), NB6 and NB7.
+For both the flares, the NB3, NB4 and NB8 peak around the same time as AIA 1600 and 1700 {\AA}.
+For the X6.3 flare, NB3, NB4 behave very similarly to NB8 within the NB3 intensity contour (see Fig.~\ref{fig:flare_lc_suit}.b).
+But the NB8 peak over the whole active region is much broader compared to the NB3 and NB4 light curves (see Fig.~\ref{fig:flare_full}).
+This implies that NB8 behaves differently in other parts of the active region.
+
+The NB5 observes the continuum that is usually attributed as the Balmer continuum.
+There have been previous studies where Photospheric metal lines went into emission and affected the Balmer continuum \citep{heinzel14,kleint17}.
+The dominant contribution would still be the Balmer continuum.
+\cite{reetika21} attributed the brightening in the SJI 2832 {\AA} continuum for a mini flare to direct signature of electron beams.
+\cite{kowalski19} showed for one event, that the SJI 2832 {\AA} continuum enhancement and several Phototspheric absorption lines going into emission can be attributed to significant Photospheric heating.
+The entire 2832 {\AA} window of IRIS had several \ion{Fe}{2} and \ion{Cr}{2} lines which are usually observed as absorption lines, in emission.
+Curiously enough, this observation was also made in a bright umbral flare kernel, similar to the current event.
+As there was no {\it IRIS} scan of the umbral brightening visible in NB5, unfortunately, we can not comment on the spectral nature of the bright kernel.
+
+We see an excess around the 6.5 keV Fe complex from the XSM observations which can be fitted with a single Gaussian.
+From Fig.~\ref{fig:fe_excess}, the Fe excess light curve (blue solid line) behaves very similar to the soft X-ray flux beyond the Fe K edge at 7.12 keV (green dot-dashed line).
+The excess also shows no correlation with the STIX 25 {--} 50 keV hard X-ray flux (black dashed line), illustrating no significant contribution from the non-thermal electron flux.
+This suggests that the excess flux seen around 6.4 keV Fe complex arises from the Fe fluorescence from the flaring X-ray.
+If we assume the penumbral brightening observed in this flare to be similar as observed by \cite{kowalski19}, the bright kernels observed in NB5 mainly arises from a plethora of \ion{Fe}{2} lines.
+The flaring X-ray beyond Fe K edge (7.12 keV) photoionizes the Fe in the Photosphere, giving rise to both \ion{Fe}{2} lines in the red wing of \ion{Mg}{2}, along with the observed Fe fluorescence by XSM.
+
+We see a similar brightening in NB2, the blue wing of the Mg window.
+The light curve of the brightening of the blue wing of Mg is shown in Fig.~\ref{fig:fe_excess} third panel.
+The light curve shows peak at both hard X-ray peak and later on closer to Fe excess component peak.
+This possibly shows both Photospheric and Chromospheric components from the NB2.
+Further investigation and modelling is required to comment on the local plasma parameters that would produce the bright kernels observed in both NB5 and NB2, with the relative timing within themselves and also in comparison to the various energies in X-ray.
+
+The other interesting observation is the rise in the continuum intensity, specifically in NB6 and NB7 as the flares happen.
+We can see a steady rise in the continuum intensity after the M and X class flare (see Fig.~\ref{fig:flare_full}).
+For the X6.3 flare, we do see some signature of the flare in NB5, although it peaks about $\sim$ 5 minutes later compared to NB3 and NB4.
+The photospheric nature of the NB5 continuum explains the 5-minute delay of the peak from NB3.
+We see the flare peak in sequential order of formation height NB3 and NB4 (\ion{Mg}{2}, 22:29 UT) and NB8 (\ion{Ca}{2}) $\Longrightarrow$ NB5 (Photospheric continuum, 22:32:41 UT).
+We are observing the increase in continuum intensity from 283.2 nm to 388 nm.
+The consistent increase in continuum intensity is happening across the Balmer jump ($\lambda$~=~364.5 nm).
+
+%%----------------------------------------------------
+\section{X1 flare observed on Dec 31st, 2023} \label{sec:dec_31st}
+%%----------------------------------------------------

### 2024-08-14 chapter2/ms.tex
Updates from Overleaf

@@
 
-\begin{figure}
+\begin{figure}[ht!]
     \centering
@@
 \cite{kretzschmar10,kretzschmar11}, performed statistical studies using a large number of flare observations across a wide energy range.
-They demonstrated, at the peak of the flare, about 70\% of the total energy was radiated in the continuum visible and NUV channel as illustrated in \ref{tab1}.
+They demonstrated, at the peak of the flare, about 70\% of the total energy was radiated in the continuum visible and NUV channel as illustrated in \ref{tab:tab1_}.
 SUIT would observe and resolve the solar flares within 200-400 nm using 8 NBs and 3 BBs.
@@
 %%--------------------------------------------%%
-\begin{table}[]
+\begin{table}[ht!]
     \centering
@@
     \caption{Spectral Energy Distribution from a sample of 2100 flares across various wavelengths\citep{kretzschmar11}.}
-    \label{tab1}
+    \label{tab:tab1_}
 \end{table}
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
-    \includegraphics[width = \linewidth]{Figures/nphys1741_page-0002.webp}
+    \includegraphics[width = 0.7\linewidth]{Figures/nphys1741_page-0002.png}
     \caption{Averaged TSI variations during flares.

### 2024-08-14 chapter4/ms.tex
Updates from Overleaf

@@
-%UNLIKE IN A REGULAR TEX FILE, DON'T PUT ANY PREAMBLE MATERIAL HERE
+\justifying
 
-%NOTE THE LACK OF A BIBLIOGRAPHY CALL IN THIS FILE. BIBLIOGRAPHY WORK HAPPENS OUTSIDE THE CHAPTER TEX FILES.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction} \label{sec:intro}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The remarkable technological progress attained in the last few decades has yielded significant benefits in the form of highly advanced imaging, spectroscopic, and polarimetric instruments designed for astronomical observations.
+These instruments have empowered us with the ability to scrutinize the Sun with exceptional detail.
+While some of these are ground based telescopes, the others operate from space.
+Primarily, space-based instruments observe the Sun in Ultraviolet (UV), extreme ultraviolet (EUV), and X-ray bands, capturing radiation from upper atmospheric layers such as the transition region and corona
+, which emit due to their elevated temperatures.
+Various studies of the Sun over the last few decades have successfully uncovered the physical properties of the gas in the upper layers of the solar atmosphere using the observations recorded by X-ray imaging ({\it Hinode} X-ray Telescope \citep[{\it Hindoe}/XRT,][]{xrt}) and spectroscopy (the Spectrometer/Telescope for Imaging X-rays on {\it Solar Orbiter} \citep[{\it SO}/STIX,][]{stix}) and extreme ultraviolet (EUV) imaging (Atmospheric Imaging Assembly on the {\it Solar Dynamic Observatory} \cite[{\it SDO}/AIA,][]{aia}, Extreme ultraviolet Imaging Telescope on {\it Solar and Heliospheric Observatory} \cite[{\it SoHO}/EIT,][]{eit}, Solar Ultraviolet Imager on the {\it Geostationary Operational Environmental Satellites} \citep[{\it GOES}/SUVI,][]{suvi}, the Extreme Ultraviolet Imager on {\it Solar Terrestrial Relations Observatory-A} \cite[{\it STEREO-A}/EUVI,][]{stereo,euvi}, \textbf{the Extreme-Ultraviolet Imager on {\it SO} \citep[{\it SO}/EUI][]{eui}}) and spectroscopy \citep[Hinode/EIS,][]{eis}, among many others.
+The {\it Transition Region and Coronal Explorer} \citep[{\it TRACE},][]{trace}, \textbf{the Solar Ultraviolet Measurements of Emitted Radiation on {\it SoHO} \citep[{\it SoHO}/SUMER,][]{sumer}} and the {\it Interface Region Imaging Spectrograph} \citep[~{\it IRIS},][]{iris} allowed us to probe the chromosphere and the transition region in detail.
+These missions provide us with continuous full disk and Region of Interest (RoI) coverage of the Sun over the X-ray and EUV wavelengths.
+The situation is rather different in the Near-Ultraviolet (NUV) regime.
+There is clearly a lack of continuous coverage of the full solar disk in this wavelength range.
+
+One of the key challenges of carrying out Solar observations in the UV regime from ground is the strong attenuation by the Earth's atmosphere.
+To circumnavigate this, one of the first stratospheric balloon-borne instrument was flown in 1970 and 1971 by \cite{herse79}.
+The instrument carried a 20 cm telescope that imaged the sun in 200{--}460 nm.
+The Rasolba balloon experiment was composed of a 30 cm telescope with an ultraviolet spectrograph.
+They obtained high resolution spectra of the Sun in the spectral range 190 {--} 295 nm \citep{samain85,staath95}.
+Sunrise \citep{sunrise1,sunrise2} is a balloon-borne observatory that followed up these instruments to observe the Sun in the Near UltraViolet (NUV) regime with a telescope of 1 m diameter.
+It has flown twice, in June 2009 and June 2013, respectively and provided us with high resolution imaging in 214, 300, 312, 388 and 397~nm with the Sunrise Filter Imager \citep[SuFI,][]{sufi} in 2009 and at 214, 279 and 397~nm in 2017 \citep{sunrise2}, Dopplergrams and vector magnetorams in \ion{Fe}{1} 525.02 nm with the Imaging Magnetograph eXperiment \citep[IMaX,][]{imax} at various locations on the Solar disk.
+During these two flights, along with quiet sun and active regions, Sunrise observed various solar phenomenon e.g.
+emerging flux events \citep{centeno17}, properties and dynamics of moving magnetic features around pores \citep{kaithakkal17}, proper motion of bright points in quiet sun and active regions \citep{jafarzadeh17}, properites of fibrils \citep{gaferia17} etc.
+These observations demonstrated the wealth of information this wavelength range carries and opened the path for full disk coverage of the Sun in the NUV.
+
+The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1, aditya} of the Indian Space Research Organization (ISRO), launched on September 2, 2023.
+The satellite is placed in a halo orbit around the Sun-Earth L1 point.
+With its eleven science filters (eight narrow band and three broad band), {\suit} has the unique capability to probe different heights in the solar photosphere and chromosphere; helping us to understand various physical processes responsible for the transport of mass and energy from one layer to another.
+Moreover, SUIT provides the unique opportunity to measure the spatially resolved solar spectral irradiance in the NUV, which is central to our understanding of Sun climate relations.
+
+{\suit} is designed to provide full-disk and RoI images of the Sun continuously, with a plate scale of 0.7{\arcsec}.
+It has the capability of tracking the RoIs while compensating for the differential rotation \citep{suit_algo}.
+Moreover, it is also capable of detecting and localizing flares with on-board intelligence and can also automatically control the exposure time to avoid saturation.
+The main science questions that {\suit} aims to address are \citep[][]{suit_science,suit_main}:
+
+\begin{itemize}
+    \item Coupling and dynamics of the solar atmosphere: {\it How is energy channeled and transferred from the photosphere to the chromosphere in the solar atmosphere?}
+    \item Sun-Climate Relationship: {\it Understanding the Variability of Solar Spectral Irradiance (SSI) and NUV radiance of various features on the Sun.}
+    \item Solar Flare Dynamics and Energy Distribution: {\it At Which wavelength Do flares emit the majority of their energy, and what proportion of this energy is from the NUV Range?
+What is the spectral energy distribution of flares?}
+    \item Physics of eruptions at various spatio-temporal scales: {\it what physical processes drive eruptive phenomena observed at various spatio-temporal scales in the Photosphere and Chromosphere?}
+\end{itemize}
+
+In this work we aim to forward model the observations recorded by {\suit} using the Max Planck Institute/University of Chicago Radiative Magneto Hydrodynamics \citep[MURaM,][]{muram} and MPS-ATLAS codes as well as observations recorded by the Interface Region Imaging Spectrograph (IRIS).
+MURaM is a three-dimensional (3D) MHD code designed to facilitate realistic simulations of magneto-convection and other related magnetic features (such as pores, sunspots and emerging flux) in the upper convection zone and photosphere.
+The simulation includes the effects of non-gray radiative transfer, partial ionization, full compressibility and open boundary conditions.
+The simulation gives us various physical quantities such as density, temperature, magnetic flux density etc.
+The MPS-ATLAS \citep{witzke12} code, which solves the radiative transfer equation vary rapidly with the help of opacity distribution functions, can be applied to the model atmosphere obtained from MURaM  to synthesize the spectrum.
+Since the MURaM simulation cubes used here do not include the non-local thermodynamic equilibrium, these cannot be used to forward model the observations for chromospheric filter.
+Therefore, for this purpose, we utilize the observations recorded by~{\it IRIS} in \ion{Mg}{2} lines.
+
+Since the observations taken by an instrument such as {\suit} are convolved with their respective response functions, we need to have a de-convolution algorithm in place that can be employed in the data reduction pipeline.
+Here, we present the de-convolution algorithm employed in the data reduction pipeline for {\suit}.
+To ensure the reliability of the deconvolution algorithm, we must treat the radiation coming from the solar model (or from the~{\it IRIS} spacecraft) in exactly the same way as the solar photons are treated by the instrument.
+I.e.
+they must be spatially convolved by the point spread function (PSF) of the instrument at the relevant wavelength and spectrally filtered and attenuated.
+For this purpose we use measured filter profiles and PSFs.
+%\sks{Is this addition correct?
+Without it, readers may wonder at much of Sect.
+2.}
+
+The rest of the paper is structured as follows.
+In \S\ref{sec:inst} we briefly describe details of the payload and present the effective area of various filter combinations.
+We present our method for calculating intensity maps from model atmospheres computed from MURaM, using MPS-ATLAS in \S\ref{sec:mps}.
+We present the measured point spread function (PSF) for the eleven science filters of {\suit} and the effects of the instrument PSF on the imaging in \S\ref{sec:psf} with the calculated intensity maps presented in \S\ref{sec:mps} and~{\it IRIS} observations.
+Finally, we summarize and conclude in \S\ref{sec:con}.
+
+%%---------------------------------------------------
+\begin{figure}
+    \centering
+    \includegraphics[trim={0.4cm 3.8cm 1cm 0cm},clip,width=0.75\textwidth]{optical_comp.jpeg}
+    \caption{Transmission as a function of wavelength of thermal filter (panel a), science filters (panels c and d), band pass filters (panel e) and the field corrector lens (panel f).
+We also plot the reflectivity of the mirrors in panel b and the quantum efficiency curve of the detector (panel g).
+Labels on x-axes are wavelength in nanometers.}
+    \label{fig:tras_prof}
+\end{figure}
+%%---------------------------------------------------
+
+%%---------------------------------------------------
+%\begin{figure}
+ %   \centering
+  %  \includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=0.75\textwidth]{eff_area.pdf}
+   % \caption{The effective area curves for all science filters as labeled.}
+    %\label{fig:eff_area}
+%\end{figure}
+%%---------------------------------------------------
+
+%%---------------------------------------------------
+\section{The Instrument} \label{sec:inst}
+%%---------------------------------------------------
+The {\suit} is a two mirror off-axis telescope, which is designed to image the Sun with a plate scale of ~0.7{\arcsec}, and a field of view (FOV) of 0.75{\degree} on a 4096~$\times$~4096 charged coupled device (CCD), which has 12~$\mu$m pixel size.
+%Figure~\ref{fig:layout} shows a schematic diagram of the {\suit}.
+The entrance of the payload consists of an entrance door mechanism and a thermal filter(TF).
+The TF \cite[][]{thermal_filter_1, thermal_filter_2} is designed to cut down most of the incoming visible ($\approx$ 99.75\%) and infrared($\approx$ 99.5\%) radiation and transmits a very small fraction ($\approx$ 0.3\%) of the radiation within 200{--}400~nm.
+The transmitted light passes through the telescope, gets reflected from the primary and secondary mirrors, respectively, to arrive at the shutter mechanism, which is located between the secondary mirror and the filter wheels.
+For more details on the instrument, see \cite{article,suit_main}.
+
+%%---------------------------%%
+\begin{figure*}
+    \centering
+    \includegraphics[trim={1.7cm 3cm 2cm 1.5cm},clip,width=0.8\textwidth]{Figures/suit_psf_3d.pdf}
+    \caption{The measured PSF for the various filter combinations. The colormap is area normalized, i.e. the sum of the PSF over the total area is unity.}
+    \label{fig:psf_3d}
+\end{figure*}
+%%---------------------------%%
+
+{\suit} has 11 science filters (first column Table~\ref{tab:science_filters}), and five band pass filters (BPFs), which are used to keep the photon flux within the dynamic range of the CCD.
+Out of these five band pass filters, while two are the spare copies NB8 and BB1, we designed three additional band pass filters namely, BP2, BP3 and BP4.
+These 16 filters are mounted on two filter wheels (FWs), each holding eight filters.
+The combination of the appropriate science filter and band pass filter is achieved by rotating the two filter wheels independently.
+Note that secondary piece of BB1 is used as combination filters NB1 and BB1.
+Similarly, NB8 is combined with an identical NB8.
+Between the FWs and the detectors a focusing lens is mounted on a piezo motor, which can be used as a focusing mechanism.
+Fig.~\ref{fig:tras_prof} displays the the transmission profile of the individual components in the optical path.
+
+%%---------------------------%%
+\begin{figure*}
+    \centering
+    %\hspace{-1cm}
+    \includegraphics[trim={1.5cm 3cm 2.5cm 4cm},clip,width=0.6\textwidth]{psf_ese_2.eps}
+    \caption{The encircled energy curve for the measured PSF.
+The 95\% encircled energy radius are marked with the vertical dashed red line.
+The angular scale of the 95\% encircled energy radius is also quoted in each panel for the specific filter combination.}
+    \label{fig:psf_ese}
+\end{figure*}
+%%---------------------------%%
+
+%%---------------------------------------------------------------
+\begin{figure*}
+    \begin{center}
+    \resizebox{0.9\textwidth}{!}{%
+        \begin{tikzpicture}[node distance=2cm]
+            \node(muram)[io]{Model 3D atmospheres simulated by the radiative-MHD code MURaM};
+            \node(slice)[io,right of=muram,xshift=3.5cm]{Slice the MURaM cubes and interpolate them to various $\mu$ values};
+            \node(filter)[io,below of=muram,yshift=-1cm]{Use \suit~ science filter profiles accounting for all the optics on the ray path};
+            \node(odf)[io,right of=filter,xshift=3.5cm]{Generate ODF tables for various filters using the MPS-ATLAS code};
+            \node(rdt)[io,right of=odf,xshift=3.5cm,yshift=1.5cm]{Use ODF tables and 1D ray-atmospheres from the 3D MHD cube to carry out RT calculations using MPS-ATLAS};
+            \node(int)[io,below of=rdt,yshift=-3cm]{Integrate the generated spectra for each pixel of the cube over the wavelength range of the filter profile to generate the intensity map};
+            \node(conv)[io,left of=int,xshift=-4.5cm]{Convolve the total emergent intensity maps with relevant \suit~ PSF and bin to \suit~ plate scale to create mock observation};
+            \draw[arrow](muram)--(slice);
+            \draw[arrow](slice)--(rdt);
+            \draw[arrow](filter)--(odf);
+            \draw[arrow](odf)--(rdt);
+            \draw[arrow](rdt)--(int);
+            \draw[arrow](int)--(conv);
+        \end{tikzpicture}}
+        \caption{The flow chart shows the entire process of generating the simulated intensity maps, from the data cubes and characterizing the filters.}
+        \label{fig:flow}
+    \end{center}
+\end{figure*}
+%%---------------------------------------------------------------
+%%---------------------------------------------------------------
+\subsection{The Point Spread Function (PSF) of SUIT} \label{sec:psf}
+%%-----------------------------------------------------------------
+
+In Fig.~\ref{fig:psf_3d}, we plot the measured Point Spread Function (PSF) at the centre of the CCD for the different science filter combinations for {\suit}.
+The PSFs are highly peaked at the centre.
+The scattered light background becomes clearly visible due to the log scaling of the color bar and is more than two orders of magnitude lower than the peak.
+
+Fig.~\ref{fig:psf_ese} shows the encircled energy curve for the measured PSFs for various filter combinations normalized to the total integral of unity.
+The vertical dashed lines in each plot show the radius within which 95\% of the incident light falls.
+For example, for the NB2 filter, 95\% of the incident light from a point source arrives within a 2.31{\arcsec} radius ($\sim$ 4.6{\arcsec} diameter) and 5\% of the light falls outside that region.
+Note that while the 95\% diameter is 4.6{\arcsec}, the PSF is strongly peaked.
+The overall diameter is considerably larger than the highly peaked part of the PSF because of the presence of a pedestal in the PSF.
+The pedestal is visible in all of the cases at the base of the central peak, although it is about 2 order of magnitude lower in all the cases (see Fig.~\ref{fig:psf_3d}).
+In some cases (e.g.
+NB1, BB2 etc.) a few or multiple smaller peaks apart form the pedestal are also visible.
+Similar radii for other filters are quoted in the corresponding panels of Fig.~\ref{fig:psf_ese}.
+The encircled count curves help us characterize the stray light for various filter combinations.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Forward Modeling SUIT intensity maps using MPS-ATLAS and MURaM} \label{sec:mps}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+One of the essential steps of characterizing the science filters was to conduct a thorough throughput modeling for the concerned filter combinations.
+However, quantifying the effects of the wavelength response of the optical components and the PSF on the spatially resolved observations, as well as the contrast variation, requires detailed modeling with resolved simulations of the Sun's surface.
+For this purpose, we use the MPS-ATLAS code.
+It is an updated version of the well established ATLAS9 \citep{atlas9} code that can efficiently generate Opacity Distribution Functions (ODFs), model atmospheres, and calculate emergent spectra in local thermodynamic equilibrium (LTE) for a given wavelength range by solving radiative transfer (RT) equation in plane parallel geometry using the assumptions of local-thermodynamic-equilibrium (LTE).
+
+%%%%%%%%%%%%%%%%%%%%%%
+\begin{wrapfigure}{l}{0.45\textwidth}
+    \centering
+    \includegraphics[width=.4\textwidth]{mps.pdf}
+        \caption{Forward modeled intensity maps at various $\mu$ values for BB2 filter of SUIT.}
+    \label{fig:flux_maps}
+\end{wrapfigure}
+%%%%%%%%%%%%%%%%%%%%%%
+
+We use 3D MHD model atmospheres simulated by \cite{rempel20} and 1.5D RT with MPS-ATLAS \citep[see e.g.,][for details]{anusha21} with measured filter profiles of {\suit}, to calculate the emergent intensity.
+The 3D MHD simulation employs a symmetric lower boundary condition for the magnetic field and a variety of initial magnetic field configurations to create small-scale variations and various levels of magnetization.
+The RT equation is solved using the method of ODFs, accounting for both continuum and line opacities within the concerned wavelength range.
+This takes into account both continuum and line opacity within the concerned wavelength range.
+Accurately accounting for the line opacity is one of the major challenges in synthesizing spectra over a broad wavelength range.
+In the ODFs method, the opacity is sorted without the information of the corresponding wavelength within small intervals of wavelengths known as bins.
+The geometric mean of the sorted opacity values for multiple sub intervals within a given wavelength bin is pre-tabulated over atmospheric parameters such as temperature, pressure and micro-turbulent velocities.
+During RT calculations, opacity is then interpolated for the required grid parameters of the atmospheric model.
+The primary goal of the ODF method is to significantly minimize the computational time required for RT calculations.
+This becomes particularly crucial when computing emergent spectra across numerous atmospheres, such as those arising from 3D MHD simulations.

### 2024-08-14 chapter5/ms.tex
Updates from Overleaf

@@
 \centering
+\resizebox{0.9\textwidth}{!}{%
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 \hline
-\end{tabular}%}
+\end{tabular}}
 %\end{center}
@@
 
-The flare manifests two ribbons in AIA 1600{\AA}, as indicated by the arrows.
+The flare manifests two ribbons in AIA 1600 {\AA}, as indicated by the arrows.
 The eastern ribbon extends around a negative field region and is entirely covered by the IRIS SJI FOV.
@@
 On February 3, 2015, AR 12277 generated a C-class flare that peaked at 22:55 UT.
-Fig.\ref{flare3} depicts the GOES flux plot of the flare in the 0.5{--}4{\AA} range (blue) and the 1.0{--}8.0~{\AA} range (red) in panel (a).
-Fig.\ref{flare3}(b) \& (c) displays an AIA 1600{\AA} image and the line-of-sight (LOS) magnetic flux density map obtained from HMI, respectively, recorded near the peak of the flare.
+Fig.\ref{flare3} depicts the GOES flux plot of the flare in the 0.5{--}4 {\AA} range (blue) and the 1.0{--}8.0 {\AA} range (red) in panel (a).
+Fig.\ref{flare3}(b) \& (c) displays an AIA 1600 {\AA} image and the line-of-sight (LOS) magnetic flux density map obtained from HMI, respectively, recorded near the peak of the flare.
 
@@
 Our observations did not reveal any correlation between line intensity ratios and magnetic flux density.
-The line intensity ratios for different magnetic field strengths illustrated in Figs.\ref{fig:optical_depth_m},\ref{fig:optical_dep_ev_m},~\ref{fig:optical_dep_ev_c} indicate a consistent behavior from weak to strong magnetic field strengths.
+The line intensity ratios for different magnetic field strengths illustrated in Figs.\ref{fig:optical_dep_ev_m},\ref{fig:align_raster_flare2} right panel,\ref{fig:optical_dep_ev_c} indicate a consistent behavior from weak to strong magnetic field strengths.
 This suggests that the magnetic field similarly affects both  \ion{Mg}{2}~k and h lines, and such effects cancel out when taking the ratios.

### 2024-08-14 chapter6/ms.tex
Updates from Overleaf

--- 2024-02-14 chapter6/ms.tex
@@
-%\begin{abstract}
+\justifying
 
- %   The \ion{Mg}{2}~k \& h line intensity ratios can be used to probe the characteristics of the plasma in the solar atmosphere.
-In this study, using the observations recorded by the Interface Region Imaging Spectrometer (IRIS), we study the variation of the \ion{Mg}{2}~k \& h intensity ratio for three flares belonging to X-class, M-class, and C-class, throughout their evolution.
-We also study the k-to-h intensity ratio as a function of magnetic flux density obtained from the line-of-sight magnetograms recorded by the Helioseismic and Magnetic Imager (HMI) on board the Solar Dynamics Observatory (SDO).
-Our results reveal that while the intensity ratios are independent of magnetic flux density, they show significant changes during the evolution of the C-class and M-class flares.
-The intensity ratios start to increase at the start of the flare and peak during the impulsive phase before the flare peak and decrease rapidly thereafter.
-The values of the ratios fall even below the pre-flare level during the peak and decline phases of the flare.
-These results are important in the light of heating and cooling of localized plasma and provide further constraint on the understanding of flare physics.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction} \label{sec:intro}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%\end{abstract}
+Solar flares are the largest magnetic events in our solar system.
+They are characterized by the eruptive release of magnetic energy, and manifest as localized transient heating of coronal plasma to temperatures over $\sim$ 10~MK.
+Flares are characterized by the full-disk integrated peak soft X-ray flux observed by the X-Ray Sensor onboard the {\it Geostationary Operational Environmental Satellites} \citep[{\it GOES}/XRS,][]{xrs} (``\textit{GOES class}'').
+The various components of the flare manifest in different wavelengths of the electromagnetic spectrum.
+The flare arcade and the fan exhibit the thermal plasma, while the majority of the non-thermal energy is from the foot points \citep{benz17}.
+The hot coronal plasma exhibited by flares is generally attributed to chromospheric evaporation, heated by the collisions of the flare-accelerated electrons in the impulsive phase \citep{fletcher11}.
+There is also strong evidence that the plasma might be directly heated in the corona in some cases \citep[e.g.][]{longcope11, reeves17}.
 
-%%----------------------------------------------------
-\section{Introduction} \label{sec:intro}
-%%----------------------------------------------------
+There have been several works \citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17} that study the partition between the thermal and non-thermal energies in flares, which holds key insight into the relevant underlying physical processes in the flares.
+The results have been contradictory, and there is no consensus on whether non-thermal energetic electrons have enough energy to power the observed thermal energy component of smaller flares.
+These studies usually use peak thermal energy as a representative of the bulk thermal output of the flares.
+While these quantities are fair representation of the bulk thermal output of the flare, identifying subtle differences in the heating mechanisms at play at different stages of the flares requires a quantification of the thermal energy as a function of time.
 
-Solar flares are the most energetic events on the Sun, where an enormous amount of magnetic free energy is released due to the reconfiguration of the coronal magnetic field.
-The released energy can cause particle acceleration, heating and flows in the solar atmosphere and a transient enhancement in solar radiative output.
-It is observed that most of the energy radiated in flares originates from the dense chromosphere \citep{fletcher10,milligan14}.
-Hence, studying the chromospheric lines during flares provides us with diagnostics, which may be important for understanding the physics of solar flares and their effect on the local plasma environment.
+There are several studies \citep{hilarie05,caspi10} that estimate the thermal energy as a function of time. The thermal energy of the flares is defined as 
+\begin{equation}
+\mathrm{U_{Th}~\simeq~3n_{e}k_{B}TV}f,
+\end{equation} \label{eq:t_eneg_1}
+ where `$\mathrm{n_{e}}$' is the electron number density of the flaring plasma, `V' is the volume of the flaring plasma, `\textit{f}' is the volume filling factor, and `T' is the instantaneous temperature.
+One of the key challenges in characterizing the flares' thermal energy is determining the volume.
 
-The chromosphere emits in various UltraViolet(UV) and optical lines.
-While many optical lines, e.g., H$\alpha$, \ion{Ca}{2}, are routinely observed from ground-based telescopes, observations in the \ion{Mg}{2} resonance lines have been rare in the past.
-Since the launch of the Interface Region Imaging Spectrograph \citep[IRIS;][]{IRIS} we have been in the position to monitor these lines regularly with excellent spatial and spectral resolution.
+\cite{li23} used $\frac{1}{e^{2}}$ contour of soft X-ray emitting region to identify the flare area `A', which was subsequently used to estimate the volume, $V\sim A^{\frac{3}{2}}$.
+\cite{zhang19} used a similar method, using intensity threshold on AIA 131~{\AA} observation, to estimate the flare area (A).
+\cite{hilarie05} used a similar method with {\it Reuven Ramaty High Energy Solar Spectroscopic Imager} \citep[{\it RHESSI},][]{rhessi} soft X-ray images to estimate the lower limit of the volume.
+They used {\it RHESSI} hard X-ray imaging to estimate the distance between two footpoints.
+Assuming a perfect ``arc-shaped" loop they calculated the upper estimate of the volume and concluded that the largest source of uncertainty in determining the thermal energy arises from the uncertainty in the filling factors.
 
-The \ion{Mg}{2}~k and h lines are transitions to the ground state from a finely split pair of upper levels ($3p~^{2}P_{\nicefrac{3}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$ and $3p ^{2}P_{\nicefrac{1}{2}}${--}$3s~^{2}S_{\nicefrac{1}{2}}$).
-These transitions create the optically thick lines in the wavelengths 2796.34~{\AA} (\ion{Mg}{2}~k) and 2803.52~{\AA} (\ion{Mg}{2}~h).
-It is suggested that the intensity ratios of these lines can be used to probe the optical depth of the local environment \citep{kerr15}.
+\cite{hilarie05} also estimated the evolution of cumulative non-thermal energy injected by the electrons by assuming a thick-target model \citep{brown71} and fitting the {\it RHESSI} spectrum of the events.
+They fitted the {\it RHESSI} spectra in 25{--}35 keV bands to determine the non-thermal energies in time bins with significant emission above 25 keV.
+This process ensures a better accuracy for determining non-thermal energy by dividing the flare into short time intervals with large energy inputs, resulting in small thermal energy losses.
+They found that the non-thermal cumulative energy was larger than the thermal component of the flare for most of the duration of the flare.
+This is expected as radiative cooling significantly lower the temperature of the flare arcade as the flare evolves.
+They also deduced that during the early impulsive phase, the cumulative non-thermal energy could be lower than the thermal energy, depending on the estimates used for the flaring plasma volume.
 
-The integrated intensity of a line transitioning from an upper-level j to a lower-level i, is dependent on the collision strength for that transition $\Omega_{ij}$, which is given by~\citep{henri62,mariska92},
+The filling factor `\textit{f}' quantifies the fraction of the apparent volume that is filled with the plasma of a specific temperature.
+It might also hold information about the geometric projection effects of the real volume into the apparent projected volume that is observed.
+Due to the highly multi-thermal nature of the flaring plasma and rapidly changing volume during the rise phase of the flare, it is challenging to define a filling factor that describes the plasma volume across the evolution of the flare.
+%Furthermore, most of the statistical studies so far, deals with bolometric or time averaged quantities near the peak of the flare.}
+%This would indicate that direct heating possibly happens before or during the impulsive phase of flares.
 
-%%---------------------------------------------------------------
-\begin{equation*}
-    \Omega_{ij}~=~\frac{8\pi}{\sqrt{3}}~\frac{I_{H}}{\Delta \epsilon_{ij}}~g~\omega_{i}~f_{ij}
-\end{equation*}
-%%---------------------------------------------------------------
+\cite{caspi10} studied super hot flares from {\it RHESSI} observations, and used a 50\% intensity contour of cleaned {\it RHESSI} images to estimate the flare area, A.
+The volume $V=\frac{4}{3}\pi (A/\pi)^{3/2}$ was inferred from the area assuming spherical symmetry.
+The two temperature components from the {\it RHESSI} spectral fit were assigned a volume V/2 each to estimate the total thermal energy.
+In all of these cases, the assumption of symmetrical expansion is useful because the thermal energy was estimated from a spectra obtained by integrating multiple pixels.
+There is no reliable way to address the spatially varying multi-thermal nature of the flaring plasma in these cases.
 
-\noindent Where $I_{H}$ is the ionization energy of Hydrogen, $\Delta \epsilon_{ij}$ is the threshold energy for the transition, g is the Gaunt factor, $\omega_{i}$ is the statistical weight of the level and $f_{ij}$ is the oscillator strength.
-In optically thin conditions, the intensity ratio of the k to h line is the ratio of the collision strengths, as the escape probability of photon is unity.
-The \ion{Mg}{2} k and h lines share the same ionization state and originate from a transition to a shared lowered level.
-As the statistical weight ($\omega_{i}$) is same in both cases, the line intensity ratio is simply the ratio of the oscillator strengths($f_{ij}$).
-This implies the ratio is 2:1 in optically thin conditions, and lower when the medium is optically thick \citep{kerr15,levens19}.
+In addition to the bulk thermal plasma in the flare loop, there are studies that suggested completely different heating mechanisms at play in specific flares.
+For example, \citet{longcope11} suggested a super hot plasma component in flares is directly heated in the corona in some large solar flares.
+Sustained temperatures in supra-arcade fans in flares have been hypothesized to be caused by supra-arcade down flows \citep[e.g.][]{reeves17}, suppression of conduction by turbulence \citep[e.g.][]{xie23} or global compression from reconnection inflows \citep[e.g.][]{reeves19}.
+These processes are distinctly different from chromospheric evaporation, which is characterized by the development of the hard X-ray foot-points and increasing intensity of soft X-ray and EUV-emitting plasma as the loops fill up.
 
-In addition, the \ion{Mg}{2} k and h lines can be used to estimate the velocity in the middle and upper chromosphere, the chromospheric velocity gradients, the temperature in the middle chromosphere \citep{leenarts13a,leenarts13b,pereira13}.
-The \ion{Mg}{2} triplets in emission can be used to identify heating in the lower chromosphere \citep{pereira15}.
-There have also been multiple studies that have shown a spatial variation of the \ion{Mg}{2} line profiles \citep{dalda23,panos18}.
-\cite{polito23} showed that the leading edge of the flare ribbon is associated with enhanced broadening and strong central reversal.
-They interpreted the difference in the profile as a difference in the heating mechanism at the leading edge and bright part of the flare ribbons.
-\cite{panos21,panos21_2} showed similar differences between the line profiles and energy input.
+%%%%######%%%%%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={0cm 0.5cm 1.2cm 0.5cm},clip,width=\textwidth]{flare_pos.pdf}
+    \caption{Position of various instruments during the flares.
+AIA 193~{\AA} observations during 2021 Oct 28 (panel a) and EUVI 171~{\AA} observation during 2020 Nov 29 (panel c) in Heliographic Stonyhurst (HGS) coordinates.
+The two flares studied here are enclosed by white dotted circle.
+The projected positions of {\it Solar Orbiter}, {\it SDO} and {\it STEREO-A} are marked as labelled.
+Positions of various spacecrafts projected onto the Heliocentric Inertial (HCI) frame for the for 2021 Oct 28 (panel c) and 2020 Nov 29 (panel d), as labelled.}
+    \label{fig:sc_pos}
+\end{figure}
+%%%%######%%%%%%
 
-Using the observations recorded by the OSO-8 LPSP instrument, \citep{lemaire84} studied the evolution of the intensity ratio of \ion{Mg}{2}~h~\&~k, \ion{Ca}{2}~h~\&~k and Ly~$\alpha$~\&~$\beta$ lines.
-\cite{lemaire84} showed that the intensity ratio of the \ion{Ca}{2}~k/h lines increased from 1 to 1.2 during the ascending phase of a flare and returned to 1 during the later phases.
-The authors interpreted the correlated temporal behavior across various elements as an indication of downward energy propagation.
-We note that this may suggest a slight decrease in the opacity due to localized heating at the formation height of the \ion{Ca}{2} line during the rise phase of the flare.
+Here we study the evolution of the thermal energy of two flares, \textit{viz.} M-class and X-class.
+We use existing tools and observations of the same region on the Sun from different vantages to estimate the volume of the flaring plasma more accurately.
+We show that a better estimate of the plasma volume affects the estimate of the thermal energy and has implications towards the energy budget of the flare.
+We also estimate the cumulative non-thermal energy deposited by the non-thermal electrons and compare it with our thermal energy estimates for the flare observed on 28 October, 2021.
+In \S\ref{sec:obs} we discuss the observations used in this paper and details of our analysis.
+We discuss our method for estimating the thermal energy in \S\ref{sec:therm}.
+In \S\ref{sec:los} and \S\ref{sec:non-therm}, we describe our method of volume estimation and cumulative non-thermal energy estimation, respectively.
+We discuss the results in \S\ref{res}.
 
-%\sout{In spite of the excellent potential of these spectral lines in diagnosing the localized atmosphere, such} \sout{studies have not been taken up in detail due to the scarcity of spectral observations in these lines.}
+%%%%%%
+\begin{table}
+    \centering
+    \resizebox{\textwidth}{!}{%
+    \begin{tabular}{||c|c|c||}
+    \hline
+    Instruments & Details & Flares\\
+    \hline 
+    \hline
+      & 0.6 \arcsec/pix. Used&   \\
+     {\it SDO}/AIA &  for estimating the thermal & 28 October, 2021 \\
+     & properties. Temperature coverage & \& 29 November, 2020 \\
+     & 5 $< log\ (T) <$ 7.5 & \\
+         \hline
+        & 2.5 \arcsec/pix. Has & \\
+       & similar temp. response as AIA. & 28 October 2021 \\
+      {\it GOES}/SUVI & Used for replacing saturated & \& 29 November, 2020 \\
+       & AIA frames in DEM estimation & \\
+       \hline 
+        & 1 \arcsec/pix. Used simultaneously & \\
+       & with AIA data in estimation of the thermal  & \\
+     {\it Hindoe}/XRT  & properties. Temperature coverage  & 29 November, 2020 \\
+       & 6.1 $< log\ (T) <$ 7.5, provides better & \\
+       & constraints on the higher temp. end. & \\
+       \hline 
+       & 1.6 \arcsec/pix. Used & \\
+       & for estimating the geometry & 28 October 2021  \\
+     {\it STEREO-A}/EUVI   & of the arcade. 171 and 195 \AA & \& 29 November, 2020 \\
+       & Observations are used with & \\
+       & AIA 171 and 193 \AA. & \\
+       \hline
+        & X-ray imaging and spectroscopy in the  &   \\
+       & 4-150 keV range. Soft X-ray imaging used & \\
+      {\it SO}/STIX & for calculating the area of the flare. & 28 October 2021 \\
+       &  Spectra used for constraining the thermal & \\
+       & and non-thermal properties & \\
+       \hline
+       & Continuous full disk integrated soft X-ray light curve. & 28 October, 2021 \\
+     {\it GOES}/XRS  & Used for estimating the bulk thermal & \& 29 November, 2020 \\
+       & properties of the flare. & \\
+       \hline
+    \end{tabular}}
+    \caption{List of the various instruments with their relevant specifications that were used for the analysis of the specific flares.}
+    \label{tab:data}
+\end{table}
+%%%%%%
 
-Here, we study the evolution of the intensities ratios of the \ion{Mg}{2}~h~\&~k lines during the course of the evolution of three flares, \textit{viz.}, C-class, M-Class and X-class.
-We focus on the the dependence of line ratios on the underlying magnetic field strength, which to our knowledge has not been explored so far.
-The rest of the paper is structured as follows.
-\S\ref{sec:obs} discusses the observations used in this paper.
-We discuss how we reduce and analyze the data and the results in \S\ref{sec:dar}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Observations and Data Analysis}\label{sec:obs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We study the two flares observed on 28 October, 2021 (X-class) and 29 November, 2020 (M-class) observed on the disk center and limb of the Sun, respectively, from the perspective of Atmospheric Imaging Assembly onboard the {\it Solar Dynamic Observatory} \citep[{\it SDO}/AIA,][]{sdo,aia} vantage point.
+For this study, we primarily use the observations from AIA, the Extreme Ultraviolet Imager onboard {\it Solar Terrestrial Relations Observatory-A} \citep[{\it STEREO-A}/EUVI,][]{stereo,euvi} and the Solar Ultraviolet Imager onboard {\it GOES} \citep[{\it GOES}/SUVI,][]{suvi}, along with imaging from the Spectrometer/Telescope for Imaging X-rays onboard {\it Solar Orbiter} \citep[{\it SO}/STIX,][]{so,stix,stix1}, the X-Ray Telescope onboard {\it Hinode} \citep[{\it Hinode}/XRT,][]{xrt} and the X-Ray Sensor onboard {\it GOES} \citep[{\it GOES}/XRS,][]{xrs}.
+For the relevant specification of the instruments used, refer to Table~\ref{tab:data}.
+
+The positions of various spacecraft with respect to the flares' location on the solar disk is illustrated in Fig.~\ref{fig:sc_pos}.
+The AIA 193 {\AA} observation of the 2021 Oct 28 flare is projected to Heliographic Stonyhurst (HGS) coordinates in panel a, with {\it SDO} (magenta cross), {\it SO} (cyan circle) and {\it STEREO-A} (green triangle) positions marked with respect to the flare location in Fig.~\ref{fig:sc_pos}.a.
+The flare is marked with white dotted circle.
+The relative separation between the spacecrafts show the difference in the polar angle (vertical axis in Fig.~\ref{fig:sc_pos}.a) and azimuthal angle (horizontal axis in Fig.~\ref{fig:sc_pos}.a) introduced due to difference in vantages.
+The positions of the spacecrafts projected onto the Heliocentric Intertial (HCI) frame for the 2021 Oct 28 event is plotted in Fig.~\ref{fig:sc_pos}.b.
+The relative separation between the spacecrafts show the difference in azimuthal angle and the distance from the sun (distance from the center radially outwards in Fig.~\ref{fig:sc_pos}.b).
+We show the same for the 2021 Nov 29 flare in Fig.~\ref{fig:sc_pos}.c and d, with {\it STEREO-A}/EUVI 171 {\AA} emission projected to HGS and HCI coordinates.% {\bf We list out the various instruments used for the analysis of the two flares in Tab.~\ref{tab:data}.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{X flare on 28th October, 2021}\label{sec:x1-obs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%--------------------------
+\begin{figure}[ht!]
+    %\hspace{-1cm}
+    \centering
+    \includegraphics[width=0.95\textwidth,trim={0.3cm 4cm 0cm 2cm},clip]{oct28_align_new.pdf}
+    \caption{X-class flare observed on October 28, 2021.
+Panel (a): the post eruption arcade as observed in AIA 193~{\AA}.
+Panel (b): Two ribbon of the flare observed in AIA 1600 {\AA}, overplotted with STIX soft X-ray contours of 4{--}15 keV (solid blue lines) and hard X-ray contours of 15{--}25 keV (dashed red lines).
+Panel (c): the emission measure map of the region integrated over the temperature range of 5$<\log\,T<$7.4.
+Panel (d): the obtained DEM weighted temperature.}
+    \label{fig:flare}
+\end{figure}
+%%--------------------------
+The X1 flare occurred on Oct 28, 2021 (SOL2021-10-28T15:35) near $\sim~[0\arcsec,-500\arcsec]$ solar coordinates as seen from AIA.
+The flare was observed by {\it SDO}/AIA, {\it STEREO-A}/EUVI, {\it GOES}/SUVI, and XRT, along with {\it GOES}/XRS and STIX observations.
+AIA observations provide imaging with 94, 131, 193, 171, 211 and 335 {\AA} passbands.
+SUVI provides imaging with similar wavelengths as AIA: 94, 131, 195, 171, 195 and 284 {\AA}, while {\it STEREO-A}/EUVI provides imaging in 171, 195, 284 {\AA} coronal passbands.
+The flare exhibits a standard two-ribbon structure, along with a ridge at the top of the rising flare arcade \citep{longcope22}.
+The ridge most prominently shows up in the AIA 193 {\AA} channel with contributions from \ion{Fe}{12} and \ion{Fe}{24}.
+%\cite{longcope22} showed that the ridge was mainly created by the hotter \ion{Fe}{24} line (T~$\simeq$~17~MK) and a height of the flare arcade, $h~\simeq~20~Mm$.
+We use this ridge to identify the loop-top in the AIA observation and calculate the height of the loop (see \S\ref{sec:los} for further details).
+
+{\it SO}/STIX provides X-ray imaging and spectroscopy in the 4-150 keV range.
+Spectroscopic observations are provided with 32 pre-defined energy channels distributed in this energy range.
+STIX is an indirect imager measuring visibilities in the Fourier space, and images can be reconstructed from these visibilities with different algorithms.
+We use the MEM-GE algorithm \citep{massa20} to construct the STIX intensity maps.
+
+In Figure.~\ref{fig:flare} (top row) we display the flare as observed with AIA~193 {\AA} (panel a) and 1600~{\AA} (panel b, inverted colors).
+These images reveal the two ribbon nature of the flare with post eruption arcades \cite[see e.g.][]{TriBC_2004}.
+We also overplot the STIX intensity contours (15:27:40 {--} 15:28:00 UT) in 4{--}15 keV (blue solid lines) and 15{--}25 keV (red dashed lines), on an AIA 1600 {\AA} image during the rise phase of the flare (see Fig.~\ref{fig:flare}.b).
+The STIX hard X-ray contour aligns with AIA 1600 {\AA} ribbons.
+
+%%--------------------------
+\begin{figure}[ht!]
+\centering
+    \includegraphics[trim={4.8cm 2.5cm 6cm 2.5cm},clip,width=0.8\textwidth]{nov_29_align.pdf}
+    \caption{M-class flare on Nov 29, 2020 as observed nearly simultaneously by AIA~{131 \AA} (panel a) and XRT Be-med filer (panel b) and the derived EM map (panel c) and DEM weighted temperature (panel d).
+The EM map is obtained by integrating over the temperature range of 5$<\log\,T<$7.4.}
+    \label{fig:flare2}
+\end{figure}
+%%--------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{M flare on 29th November, 2020}\label{sec:m-obs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The M flare occurred on November 29, 2020, near $\sim [-950\arcsec,-430\arcsec]$ solar coordinates from the AIA perspective.
+In the AIA images, the footpoints were occulted behind the limb.
+The flare was also recorded by {\it STEREO-A}/EUVI, {\it GOES}/SUVI and {\it Hinode}/XRT.
+Along with these instruments, there were observations from {\it GOES}/XRS and {\it Fermi}/GBM.
+There were no observations from STIX for this event.
+
+The flare exhibits a fan which is visible in the hot channels of AIA (131 and 193 {\AA}) and the XRT channels.
+Fig.
+\ref{fig:flare2}a shows an AIA 131 {\AA} image of the flare recorded during the decay phase.
+In Fig.~\ref{fig:flare2}b, we plot an XRT Be-med filter observation taken near simultaneous with the AIA image.
+For the M-class event, the {\it Fermi} observations were periodically eclipsed during the duration of the flare.
+We do not calculate the cumulative non-thermal energy for this event, as during the eclipses there is no reliable way to estimate the instantaneous non-thermal energy deposited.
+Hence, the estimation of cumulative non-thermal energy would not be a fair representation of the total non-thermal energy available.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Thermal Energy}\label{sec:therm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We estimate the thermal energy of the X-class event by calculating the differential emission measure (DEM) of the flaring region from the six AIA passbands including 94 {\AA} (\ion{Fe}{10} $\sim$1.1~MK, \ion{Fe}{18} $\sim$7.1~MK), 131 {\AA} (\ion{Fe}{8} $\sim$0.4~MK, \ion{Fe}{21} $\sim$11~MK), 171 {\AA} (\ion{Fe}{9} $\sim$0.6~MK), 193 {\AA} (\ion{Fe}{12} $\sim$1.6~MK, \ion{Fe}{24} $\sim$17~MK), 211 {\AA} (\ion{Fe}{14} $\sim$2~MK), 335 {\AA} (\ion{Fe}{16} $\sim$2.5~MK) \citep{o'dwyer10,O'Dwyer12}.
+Near the peak of the flare, several AIA frames are saturated in several instances and as such they cannot be used for the analysis.
+The SUVI temperature response is very similar to AIA~\citep{suvi}.
+Therefore, whenever necessary, the specific AIA frames can be replaced by those taken by SUVI for thermal energy estimates after co-aligning and co-registering  the two observations.
+Moreover, we also need to rescale the AIA temperature response functions to account for the binning of the AIA data to match the SUVI resolution.
+Note that since most of the XRT observations during the flare are saturated, we do not include them in our analysis of this flare.
+
+For the M-class event, we estimate the thermal energy using AIA and XRT observations.
+Here, we bin the AIA observations to XRT pixel size, co-align, and calculate the DEMs.
+As described earlier, we rescale the AIA temperature response functions to account for the binning of the AIA data.
+
+We use the regularized inversion method \citep{hannah&kontar12} to calculate the DEMs. The observed flux from the individual passbands can be written as,
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+    F_{i}~=~\int~DEM_{c}(T)~R_{i}(T)~dT+\delta F_{i}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%
+where $R_{i}$ is the temperature response of the passband `i', $\delta F_{i}$ is the error on the observed intensity for the passband `i' and $DEM_{c}(T)$ is the column differential emission measure (in units of $cm^{-5}K^{-1}$).
+The DEM inversion was performed for a temperature range $4.5~\le log(T)\le~8$.
+
+With the inverted DEM, we calculate the column emission measure ($EM^{c}~\mathrm{in~units~of~cm^{-5}}$) and DEM-weighted temperature as:
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+    EM^{c}~=~\int_{T} DEM_{c}(T)~dT
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+    \bar{T}~=~\frac{1}{EM^{c}}\int_{T} DEM_{c}(T)~T~dT
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%--------------
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.8\textwidth,trim={2cm 6cm 2cm 6cm},clip]{flare_orient.pdf}
+    \caption{Panel (a): {\it STEREO-A}/EUVI 171 {\AA} observation of the flare arcade in the decay phase.
+The magenta cross marks a point on the top of the arcade.
+The line of sight (LOS) goes into the page through that point.
+Panel (b): SDO/AIA 171 {\AA} observation of the flare arcade.
+The red line marks the LOS through the arcade from the STEREO-A perspective projected to the AIA perspective.} %Panel (c): Cartoon demonstrating the projection effects of a semicircular loop between STEREO-A and AIA vantages due to the difference between polar ($\theta$) and azimuthal ($\phi$) angles respectively.
+Panel (d) : The calculated LOS map from the AIA perspective, with the calculated loop top height under the assumption of a semi-circular loop geometry.}
+    \label{fig:flare_orient}
+\end{figure}
+%%--------------
+%%--------------
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[width=0.9\textwidth,trim={4cm 5cm 3cm 5cm},clip]{nov29_triangulate.pdf}
+    \caption{Panel (a): SDO/AIA 193 {\AA} observation of the Nov 29 flare in the decay phase.
+The blue cross marks a point on the top of the arcade.
+The LOS goes into the page from AIA perspective.
+Panel (b): {\it STEREO-A}/EUVI 195 {\AA} observation around same time.
+The blue solid line is the LOS from AIA perspective in panel (a) projected onto {\it STEREO-A} perspective.
+We can trace out the height of the flare arcade at various locations using \textit{scc\_measure.pro}.
+The height of the arcade at various points from the Sun's surface is marked in panel (a).}
+    \label{fig:flare_orient2}
+    \end{figure}
+%%--------------
+
+The temperature range of the integration is set to $5 < \log\,T < 7.4$.
+We calculate and plot the emission measure (panel c in Figs.~\ref{fig:flare} \& \ref{fig:flare2}) and the DEM weighted temperature (panel d in Figs.~\ref{fig:flare} \& \ref{fig:flare2}) for all the pixels in the field of view (FOV) for both the flares.
+
+The main goal of calculating the DEM maps is to estimate the thermal energy (using Eqn.~\ref{eq:t_eneg_1}) arising from various parts of the flare arcade.
+As alluded to earlier, one of the most crucial quantity is to obtain the volume of the flaring plasm.
+For our analysis, the volume of the plasma along an individual pixel is given by $V_{j}~=~A\times~LOS_{j}$, where $LOS_{j}$ is the line of sight (LOS) for the j-th pixel in the FOV and $A$ is the physical area of a pixel.
+
+%%--------------
+\begin{figure}[ht!][!h]
+    \centering
+    \includegraphics[width=0.8\textwidth,trim={3cm 2cm 3cm 0cm},clip]{flare_orient_pt2.pdf}
+    \caption{Panel (a): Cartoon demonstrating the projection effects of a semicircular loop between STEREO-A and AIA vantages due to the difference between polar ($\theta$) and azimuthal ($\phi$) angles, respectively.
+Panel (b) : The calculated LOS map from the AIA perspective for the 28th October, 2021 event, with the estimated loop top height under the assumption of a semi-circular loop geometry.}
+    \label{fig:flare_orient_2}
+\end{figure}
+%%--------------
+
+We use the above expression for volume along with the emission measure and DEM weighted temperature estimated from the inverted DEM in Eqn.~\ref{eq:t_eneg_1} and sum over the pixels in the FOV to estimate the thermal energy arising from the FOV.
+This procedure gives us,
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+    U_{Th}~=~\sum_{j}~\frac{3k_{B}A\sqrt{LOS_{j}}}{\sqrt{EM^{c}_{j}}}\int_{T}~DEM_{c}(T)_{j}T~dT
+    \label{eq:t_eneg}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+where $EM^{c}_{j}$ and $DEM_{c}(T)_{j}$ are the column emission measure and the column DEM in 5.0$<$$\log\,T$$<$7.4 for the j-th pixel in the FOV.
+We have used $n_{e}^{2}\times LOS~=EM^{c}$ and a filling factor $\textit{f}~=~1$.
+For the 2020 Nov 29 flare we mask the solar disk while calculating the DEMs and thermal energy.
+As evident from Eqn.~\ref{eq:t_eneg}, one of the major uncertainties in determining the emitting volume depends on determining the LOS for individual pixels in the FOV.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Determining the LOS}\label{sec:los}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To infer the LOS along individual pixels in the FOV for both the flares, we use AIA and STEREO-A/EUI observations, recorded from two different vantage points, to calculate the height of the flare loop.
+We display STEREO-A/EUI and AIA-171 image taken neeary simultaneously in Fig.~\ref{fig:flare_orient} a~\&~b, respectively.
+The magenta cross on Fig.~\ref{fig:flare_orient}.a shows a point at the top of the flare arcade.
+The LOS goes into the page through that point from the {\it STEREO-A} vantage.
+The red line in Fig.~\ref{fig:flare_orient}.b shows the LOS through the point in Fig.~\ref{fig:flare_orient} a projected to {\it SDO}/AIA point of view.
+This demonstrate the geometric effect of observing from different vantage points.
+
+We show the same in Fig.~\ref{fig:flare_orient2} for the Nov 29, 2020 flare.
+The blue cross marked in Fig.~\ref{fig:flare_orient2}.a is the LOS going into the page from AIA perspective.
+The blue line marked in Fig.~\ref{fig:flare_orient2}.b is the same LOS projected onto the STEREO-A perspective.
+Distances on the observation from two different vantages would be projected by the differences in the polar and the azimuthal angle between the two vantages.
+Fig.~\ref{fig:flare_orient_2}.a shows the projection effect of a semicircular loop between AIA and STEREO-A LOS.
+Depending on the orientation of the loops, the projection along the polar and azimuthal angle projects the length of the loop and the height of the loop.
+The height at various position of the flare arcade is marked in Fig.~\ref{fig:flare_orient2}.a.
+We assume a semi-circular loop geometry with the height of the loop top to calculate the LOS along every pixel within the flare arcade.
+
+We use co-temporal {\it STEREO-A} 171 {\AA}, 195 {\AA}, and AIA~171 {\AA}, 193 {\AA} images with \textit{scc\_measure.pro}, available in the \textit{sswidl}, to calculate the height of the loop.
+This routine allows us to select a point on the observation from one of the two vantages.
+The line of sight (LOS) through the same point is shown on the observation from the different vantage.
+The same point can be identified on the projected LOS by the user, by identifying similar emission characteristics.
+The program determines the 3D coordinates of the point (heliographic latitude, longitude and radial distance).
+We carry out the same measurement at various positions along the loop top, to calculate the change in loop height across the arcade.
+With the different height measurements at various locations, we can calculate the volume of the flaring plasma under a semicircular assumption.
+We note that the height estimation using \textit{scc\_measure.pro} is limited by our identification of ``similar emission characteristics" between the two observations from AIA and {\it STEREO-A}.
+
+The extent of the flare arcade is calculated by selecting pixels from the FOV which are located within an emission measure contour of 5\% of the peak emission measure value.
+It is possible to calculate the extent of the flare arcade from the intensity observed from any of the {\it SDO}/AIA or STIX imaging (for further details about the STIX imaging procedure, please refer to \cite{massa20}).
+However, due to the highly multi-thermal nature of the plasma, this procedure might be prone to missing significant portions of the flare arcade.
+The emission measure inferred from the DEM, on the other hand, reflects the density of the plasma in the entirety of the concerned temperature range of $5<\log\,(T)<7.4$.
+Therefore we find that, a 5\% contour of peak emission measure gives a better estimate of the extent of flare arcade.
+Outside of the flare arcade, we assume a LOS~$\sim$~2 Mm (the average thickness of chromosphere).
+
+Figure \ref{fig:flare_orient_2}.b shows an example of the calculated LOS in the FOV for the 2021 October 28 flare.
+The highest point of the flare arcade is oriented from south east towards north west, following the ridge.
+We get an estimate of the highest point of the loop $\simeq$ 22~Mm, which is consistent with the estimates of the height, $H~\simeq~20~Mm$ of the ridge from magnetic loop modelling by \cite{longcope22} for the same event.
+Using the map of the LOS shown in the bottom panel of Fig.
+\ref{fig:flare_orient_2}, we determine the thermal energy in every pixel of the flare using Eqn.~\ref{eq:t_eneg}.
+A similar process is used for the flare loops in the 2020 November 29 flare.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Energy in the non-thermal electrons}\label{sec:non-therm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We estimate the energy in the non-thermal electrons for the 2021 Oct 28 X-class event by fitting the STIX spectra.
+In Fig.~\ref{fig:stix_an}.a, we plot the STIX light curve of the event in 4 to 6 keV (solid black line), 6 to 12 keV (solid magenta line), 12 to 25 keV (solid yellow line) and 25 to 50 keV (solid blue line).
+The attenuator kicked in around $\sim$ 15:28 UT, which drastically cuts down the intensity to avoid saturation.
+The hard X-ray peak is visible in the 25 to 50 keV (solid blue line) at $\sim$ 15:28 UT.
+The soft X-ray peak is visible within the attenuated flux in 6 to 12 keV (solid magenta line) at $\sim$ 15:30 UT.
+
+%%--------------
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={3cm 2cm 6cm 3.5cm},clip,width=0.54\textwidth]{oct28_lc_2.pdf} 
+    \includegraphics[trim={3.5cm 8cm 3cm 2cm},clip,width=0.45\textwidth]{oct28_fit_2.pdf}
+    \caption{Panel a: STIX light curve of the 2021 Oct 28 X-class event in different energy bands as labelled.
+Panel b: STIX spectra integrated between 15:27{--}15:28~UT during impulsive phase, fitted with `\textit{thcik2}' (solid green), `\textit{2vth}' (solid yellow) and the complete fit function `\textit{2vth+thick2}' (solid red line).
+The lower panel shows the normalized residuals of the fit.}
+    \label{fig:stix_an}
+    \end{figure}
+%%--------------
+
+We closely follow the method described in \cite{emslie12} to estimate the energy deposited by the non-thermal electrons.
+We fit the STIX spectra of the event averaged over several time bins during the evolution of the flare with `\textit{2vth}' and `\textit{thick2}' functions available in the `\textit{OSPEX}' X-ray spectra fitting package in {\it sswidl}.
+We show a reference fit to the spectra obtained over a time bin $\sim$ 15:26-15:27 UT in Fig.~\ref{fig:stix_an} panel (b) with `\textit{2vth}' (solid yellow) and `\textit{thick2}' (solid green).
+The function `\textit{2vth}' is a two-component thermal function.
+The parameters are the emission measure and temperature of the two thermal components and the relative abundances of Iron/Nickel, Calcium, Sulfur and Silicon with respect to the coronal abundances of CHIANTI \citep{chianti1,chianti}.
+The `\textit{thick2}' assumes the non-thermal component to be bremsstrahlung from energetic electrons with an injected spectrum $F_{0}(E_{0})~(e^{-}s^{-1}cm^{-2}keV^{-1})$ in the form of a broken power law:
+
+%%--------
+\begin{equation}
+    F_{0}(E_{0})=A
+    \begin{cases}
+        0, & E_{0}<E_{min} \\
+        E_{0}^{-\delta_{1}}, & E_{min} \le E_{0} < E_{b} \\
+        E_{0}^{-\delta_{2}}E_{b}^{\delta_{2}-\delta_{1}}, & E_{b} \le E_{0} < E_{max} \\
+        0, & E_{max} \le E_{0}
+    \end{cases}
+\end{equation}
+%%--------
+
+The parameters of this model spectrum, e.g., the normalization parameter A, the low- and high-energy cutoffs $E_{min}$ and $E_{max}$, break energy $E_{b}$, the power law indices $\delta_{1}$ and $\delta_{2}$ below and above the break are constrained by the fitting.
+We only fix the high energy cutoff at $3.2\times 10^{4}$ keV for every fit.
+The high energy cutoff is fixed much higher than our concerned energy range ($\sim$ O($10^{1}$ keV)), and we can safely assume that it has a negligible effect on fitting the X-ray spectra \citep{emslie12}.
+
+The `\textit{OSPEX}' fitting is done by a forward fitting procedure.
+The parameters of the functions `\textit{2vth}' and `\textit{thick2}' are varied to generate a photon spectrum, which is folded through the detector response matrix to produce a count rate spectrum.
+This count rate spectrum is used to constrain the parameters of the functions through an iterative procedure by minimizing the $\chi^{2}$ between the calculated and measured count rate spectrum.
+We provide the fitted temperature and the EM of the hotter thermal component in Tab.~\ref{tab:tab1} during various phases of the flare.
+The temperatures listed in Tab.~\ref{tab:tab1} is lower than the upper limit of the temperature range used ($log(T_{max})~=~7.4$ and $log(T_{min})~=~5$) to calculate the EM and DEM weighted temperature in \S\ref{sec:therm}.
+
+%%%%%%%%%%%
+\begin{table}
+    \centering
+    \resizebox{0.9\textwidth}{!}{%
+    \begin{tabular}{|cl||c|c|}
+    \hline
+         &  & log(T) & EM \\ 
+         & \hspace{-1cm}Time (UT) & of hotter component & ($cm^{-3}$) \\
+    \hline
+        Impulsive phase & \hspace{1.5cm}15:26 & 7.098 & $10^{48}$\\
+        HXR peak & $\sim$ 15:27:20 - 15:28:20 & 7.19 & $3\times 10^{48}$\\
+        Right after SXR peak & $\sim$ 15:35:39 - 15:36:34 & 6.88 & $4.1\times 10^{49}$\\
+        Into the decay phase & \hspace{0.9cm}14:48:20 & 6.5 & $2\times 10^{49}$\\
+        \hline
+    \end{tabular}}
+    \caption{Fitted temperature of the hotter component of the thermal plasma during various stages of the flare.}
+    \label{tab:tab1}
+\end{table}
+%%%%%%%%%%%
+
+The non-thermal energy in the electrons ($U_{e}$) at any instant $t=t'$ can be estimated by integrating the best-fit electron energy spectrum via: $$U_{e}(t=t')~=~\Delta t\int_{E_{min}}^{E_{max}}~F_{0}(E_{0})(t=t')dE_{0}$$ where the electron energy distribution in constrained by fitting the count spectra for the time interval $t'-\Delta t/2 \le t \le t'+\Delta t/2$.
+The cumulative energy deposited into the foot point over time by the non-thermal electrons is a good indicator for the source of the thermal energy of the plasma.
+We add the energy deposited at the foot points by the non-thermal electrons from every time bin, to estimate the cumulative energy deposited by the non-thermal electrons up until that instant: $$U^{cumulative}_{e}(t)~=~\sum_{t'=t_{0}}^{t}U_{e}(t')$$
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{res}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We plot the estimated thermal and non-thermal energy as a function of time in Fig.~\ref{fig:eneg}.a.
+The black solid curve with crosses and red solid curve shows the evolution of thermal energy estimated using DEM and temperature from AIA and GOES light curves, respectively.
+Note that, since GOES does not provide any spatial information, in order to obtain the effective volume we first estimate the loop length using RTV scaling \citep{rtv78,serio91}.
+For this purpose we use the EM obtained from GOES and assume a volume filling factor of 1.
+Note that since the RTV scaling implicitly assumes that the flare arcade is in mechanical equilibrium, the effective volume estimated using this method will only be applicable during the decay phase of the flare.
+Since, the assumption of filling factor to be 1 may also be susceptible to uncertainties, we also compute and plot the thermal energy evolution curve using \textit{f}~=~0.4 (green solid line with triangles) and \textit{f}~=~0.2 (blue solid line with squares).
+We also over plot, the thermal energy that is computed using the EM and temperature obtained from GOES but the volumed inferred from STIX soft X-ray contours, under the assumption that $V\sim A^{\frac{3}{2}}$ (purple dotted line).
+
+%%###########%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={4cm 1cm 4cm 1cm},clip,width=0.8\textwidth]{flare_eneg.pdf}
+    \caption{Panel (a): Temporal evolution of thermal energy for the 2021 Oct 28 flare as measured using GOES light-curve using the effective volume and a filling factor \textit{f}~=~1 (solid red), \textit{f}~=~0.4 (green triangles), \textit{f}~=~0.2 (blue squares), thermal energy calculated from GOES light curve, but the volume inferred from the area of the of the flaring arcade with STIX SXR images, under the assumption that $V\sim A^{\frac{3}{2}}$ (purple dotted), and DEM obtained from AIA observations (black crosses).
+We also plot the evolution of non-thermal energy as estimated from STIX (lime green circles).
+Panel (b): Temporal evolution of thermal for the 2020 Nov 29 flare as measured from GOES light curves with a constant effective volume (solid red) and that calculated from the DEMs inferred from the imaging and a varying volume from the imaging (solid blue).}
+    \label{fig:eneg}
+\end{figure}
+%%###########%%
+
+The interesting trend in Fig.~\ref{fig:eneg}.a is that the thermal energy calculated from the constrained DEMs (solid black curve with crosses) is closer to a volume filling factor \textit{f}~=~0.2 (solid blue curve with squares) in the impulsive phase, but is asymptotic with a filling factor \textit{f}~=~1 (solid red curve) during the decay phase.
+This result indicates that the flare loops during the impulsive phase do not fill up apparent volumes similar to those in the decay phase.
+The change in the effective filling factor is indicative of the sharp change in the volume during the impulsive phase.
+
+The lime green solid line with circles in Fig.~\ref{fig:eneg}.a, shows the cumulative energy in the non-thermal electrons.
+This quantity is the amount of energy deposited at the flare foot points, and one of the sources of the thermal energy of the flare.
+The cumulative non-thermal energy of electrons $\simeq~1.2\times 10^{31}$ erg $>$ peak thermal energy calculated from the DEM estimates $\simeq~5\times 10^{30}$ erg.
+
+For the 2020 November 29 event, the {\it STEREO-A} perspective looks down into the supra-arcade plasma sheet.
+Thus the LOS of this feature can not be calculated as demonstrated in Section \ref{sec:los} for the supra-arcade pixels.
+For the supra-arcade fan pixels in the FOV, we assume a LOS $\simeq~8~\textrm{Mm}$, as suggested in several other studies \citep[see e.g.,][]{savage10,seaton17,li18}.
+We use these calculated LOS maps, along with Eqn.~\ref{eq:t_eneg_1} to estimate the thermal energy as a function of time and plot it in Fig.~\ref{fig:eneg}.b.
+The blue solid curve shows the thermal energy calculated from the DEMs.
+The red solid curve shows the thermal energy calculated from the GOES light curves and the constant effective volume calculated assuming an RTV loop with a volume filling factor \textit{f}~=~1.
+The thermal energy estimated from the GOES observation, using the effective volume obtained from the RTV approximation is clearly an overestimate in the impulsive phase.
+But similar to the previous scenario, it is a good estimator of the thermal energy in the decay phase.
+
+There have been several studies that suggest that the plasma in the fan is directly heated \citep{hanneman14,chen17,reeves17,warren18,cai22,xie23}.
+Unlike the flare arcade, the thermal output of the fan is not directly related to the energy deposited by the non-thermal electrons and ions at the foot point.
+Hence, this different mechanism should also be reflected in the time evolution of the thermal output of the fan, compared to the thermal output of the loops.
+Under the assumption of the LOS~$\mathrm{\sim 8~Mm}$ in the fan region, we separately calculate the contribution from the fan to the total thermal energy for the 2020 Nov 29 event.
+
+%%###########%%
+\begin{figure}[ht!]
+    \centering
+    \includegraphics[trim={2cm 0cm 1cm 0cm},clip,width=0.8\textwidth]{fan_eneg.pdf}
+    \caption{Calculated thermal energy for the 2020 Nov 29 flare.
+The total thermal energy of the flare (blue dot-dashed) in comparison to the thermal energy from the fan (red dashed) and the Fermi hard X-ray count (black solid).
+The magenta and the green solid line show the fit to the thermal energy output to the fan and the loop's thermal output.}
+    \label{fig:fan_eneg}
+    \end{figure}
+%%###########%%
+
+Fig.~\ref{fig:fan_eneg} shows the thermal energy of the fan as a function of time (red dashed line) in comparison to the total thermal energy of the 2020 Nov 29 event (blue dot-dashed line).
+The thermal energy form the fan is $\sim$ two orders of magnitude lower than the total thermal energy of the event.
+The thermal energy of the fan also peaks much later ($\sim$ 20 minutes) compared to the total thermal energy.
+After the thermal energy of the fan peaks, the thermal energy of the fan (red + sign) and the total thermal energy of the event (blue crosses) are fitted with a power law of the form $at^{-\delta}$ as a function of time.
+The fits are shown with magenta and green solid line for the fan and the total thermal energy, respectively.
+The value of the power law index are -0.95 and -1.1, respectively, for the fan and the total thermal output.
+The plots shows that the thermal energy of the fan decay slower compared to the total thermal output.
+The normalized {\it Fermi} GBM 25 {--} 80 keV count rate (black solid line) peaks at a similar time as the total thermal energy of the event.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary and Discussion}\label{sec:dis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We have used AIA, SUVI, and XRT observations to calculate DEM maps and estimate the thermal energy for two solar flares as a function of time.
+In addition, we have also used observations from AIA and {\it STEREO-A} to calculate the geometry of the flare loops and estimate the LOS for the AIA observations.
+To constrain the non-thermal energy in the 28 October, 2021 event, we have used STIX observations.
+
+Our findings suggest that a single value of volume filling factor is inadequate to describe the evolution of thermal energy throughout the duration of the flare.
+As such we need to estimate the volume of the flaring plasma as a function of time.
+In Fig.~\ref{fig:eneg}.a, the thermal energy calculated from {\it GOES} with various filling factors demonstrates this concept perfectly.
+During the impulsive phase, the thermal energy calculated from the DEMs is consistent with \textit{f}=0.2, and later in the decay phase, it is consistent with \textit{f}=1.
+This result demonstrates how the volume of the flare arcade is changing over time with respect to the volume in the decay phase.
+The thermal energy calculated from $V\sim A^{\frac{3}{2}}$ assumption agrees well with the thermal energy calculated from constrained DEMs in the decay phase.
+But it still predicts higher energy in the impulsive phase.
+This discrepancy signifies that the assumption of self-similar expansion may not be valid at the initial sharp rise in the impulsive phase for some flares.
+Our results are in line with the findings of \cite{hilarie05} (For details, please refer to Tab.5 therein and the corresponding discussion).
+
+Our results also demonstrate the utility of estimating the volume from different vantages as a function of time.
+For events like the X-class event on 2021 October 28, the on-disk imaging allows the estimation of the volume from the flare ribbon area under the assumption of self-similar expansion.
+But for scenarios like the limb event 2020 November 29, where the flare ribbons are not visible from any imaging observation, or the visible foot point and/or visible portions of the loop are projected at a very high angle, estimating the volume of the loop by calculating the height of the loop at various points serves as an important tool in estimating the thermal energy at various phases of the flare.
+
+These results demonstrate that the accurate determination of volume can have significant implications for thermal energy estimates as well as partition between thermal and non-thermal energies.
+While the former related to the total energetics of the flares, the later relates to the efficiency of converting the energy deposited by non-thermal electrons into the thermal energy of the ambient plasma.
+
+For the 2020 November 20 flare, we have also estimated the thermal energy for the fan and compared the evolution of the thermal energy of the fan with respect to the total thermal energy of the event.
+%We have shown that the thermal energy of the fan decays slower compared to the total thermal energy of the event.
+This result suggests that a fundamentally different heating mechanism is responsible for the thermal output of the fan.
+In Fig.~\ref{fig:fan_eneg}, the thermal energy from the fan (red dashed line ) is $\sim$ two orders of magnitude lower than the total thermal energy of the event (blue dot-dashed line).
+The thermal energy also peaks much later ($\sim$ 20 minutes) compared to the total thermal energy.
+This result shows that the fan plasma is being heated directly by a process different from the flare arcade (e.g.
+SADs \citep{reeves17}, plasma flow turbulence \citep{xie23}).
+The fan also cools slower than the arcade, which indicates that either continuous heating is present in the fan during the decay phase of the flare or there is suppression of cooling \citep[e.g.][]{xie23}.
+The event had both foot points occulted from the Earth's perspective, so it is a fair assumption that most of the hard X-ray is from the loop top coronal source.
+This circumstance explains the near-simultaneous peak in {\it Fermi} hard X-ray (black solid line) and the thermal energy peak from the flare.
+
+Our results exhibit the importance of different solar missions that can observe the Sun with higher spatial resolution (to resolve the finer structures better) and from various vantages (to triangulate the geometry).
+The ability to spatially resolve the temperature structure of the flaring plasma not only gives us a better estimation of the thermal energy, but it also allows us to spatially separate various portions of the flaring plasma (e.g.
+for the 2020 November 29 event, we could separate the contribution of the fan from the total thermal energy).
+This separation enables us to demonstrate that a different heating mechanism was at play in the fan.
+However, we do note that the reliability of any such estimations needs to be rigorously tested with observations of various flares from various geometric projections.

### 2024-08-14 chapter7/ms.tex
Updates from Overleaf

@@
 In this chapter we discuss some of the initial flare observations made by SUIT.
+The details of this flares are given in Tab.~\ref{f_list}.
+{\suit} observed an X5 flare on the east limb on 31st Dec, 2023 during its cruise phase.
+We primarily use observations from AIA with {\suit} observations to comment on the thermal structure and kinematics of the event.
+We only have observations in the NB4 (\ion{Mg}{2} h line) channel for this flare as the observation is from during the cruise phase.
 The first flare triggered by the flare detection algorithm was a X6.3 flare from north-west corner of the disk on February 22nd, 2024, which was also observed by several other instruments {\it e.g.} {\it SDO}/AIA, {\it IRIS}, {\it SO}/STIX.
-During the cruise phase, SUIT also observed a X1 flare from the south-east limb of the Sun on December 31st, 2023.
-We only have observations in the NB4 (\ion{Mg}{2} h line) channel for this flare.
-But this provides us with an unprecedented view of post-flare loops and possibly reconnection slingshot in the \ion{Mg}{2} line.
-Subsequent portions of this chapter will be divided into two parts, where we discuss the observations of these two flares separately.
+The final flare discussed in this chapter is an X2.9 flare which occurred on 27th May, 2024 on the south east limb of the Sun.
+Subsequent portions of this chapter will be divided into three parts, where we discuss the observations of these three flares separately.
+
+%----------------------------------------------------
+\begin{table}[ht!]
+\centering
+\caption{Details of the flares studied in this chapter.}
+\label{f_list}
+\resizebox{0.6\linewidth}{!}{%
+\begin{tabular}{lcr}
+\hline
+\hline
+   Event Date  & Peak Time (UT) & Flare Location \\
+\hline
+2023 Dec 31 (X5) & 21:55 & [-968{\arcsec}, 88{\arcsec}] \\
+2024 Feb 22 (X6.3) & 22:34 & [-400{\arcsec}, 350{\arcsec}]\\
+2024 May 27 (X2.9) & 07:08 & [-920{\arcsec}, -250{\arcsec}] \\
+\hline
+\end{tabular}
+}
+\end{table}
+%----------------------------------------------------
 
@@
 %%----------------------------------------------------
-\section{X1 flare observed on Dec 31st, 2023} \label{sec:dec_31st}
+\section{X5 flare observed on Dec 31st, 2023} \label{sec:dec_31st}
 %%----------------------------------------------------
+
+NOAA AR 13536 started to appear on the northeast limb on 31st December 2023.
+It erupted an X5 flare at 21:36 UT.
+{\suit} was still in the cruise phase, on its way to the L1.
+The standard synoptic observation mode was not turned on, and {\suit} was only observed in its NB4 (\ion{Mg}{2} h) channel with a minute cadence.
+AIA, STIX, and SUVI also observed the flare among many other imaging observatories.
+The {\it GOES} Soft X-ray (SXR) peaked $\sim$ 21:55 UT.
+The event was located at the heliographic position of $\sim$ [-968{\arcsec}, 88{\arcsec}].
+
+We use JPL horizons system to get the accurate location of the Aditya-L1 spacecraft.
+We use this location to account for the differences in plate scale between AIA and {\suit} observations.
+We then co-register and co-align AIA 1600 {\AA} and {\suit} NB4 observations.
+It is noteworthy that the {\suit} had $\sim$ 7{\degree} roll with respect to AIA during the cruise phase, which needs to be rotated before co-registering the AIA and {\suit} observations.
+We show a sequence of co-aligned observations in Fig.~\ref{fig:dec_flare_obs}.
+The AIA 1600 {\AA} observations are plotted in green-black colormap and the {\suit} NB4 observations are plotted in yellow.
+We see the rising loop in AIA 1600 {\AA} at 21:39 UT.
+In subsequent frames, we see the ejected plasma blob from NB4 observations is cospatial with the ejected material in AIA 1600 {\AA}.
+
+%%%%%%%%%%
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim = {0.5cm 0.7cm 0.2cm 2cm}, clip, width=0.7\linewidth]{fig1.pdf}
+    \caption{Sequence of coaligned AIA 1600 {\AA} (black-green) and {\suit} NB4 (yellow) observations.
+We see the erupting loop and parts of the dense loops are co-spatial with the ejecta observed in {\suit} NB4 observations.
+An animated version of this sequence is available in the online version of the journal.}
+    \label{fig:dec_flare_obs}
+\end{figure*}
+%%%%%%%%%%
+
+We use DEMs calculated from AIA observations to investigate the thermal structure, using regularized inversion method described by \cite{hannah&kontar12}.
+We show the eruption in AIA 171 {\AA} inverted observation in Fig.~\ref{fig:dec_flare_dem}a.
+The red dashed box marked the region for the DEM analysis.
+In Fig.~\ref{fig:dec_flare_dem}b {--} g, we show the region from the red dashed box in various AIA cornal channels.
+Fig.~\ref{fig:dec_flare_dem}d shows AIA 171 {\AA} inverted (black) co-aligned with \suit~NB4 (yellow) observation.
+As illustrated earlier, the observed plasma blob in NB4 alignes with the brighter parts of the loop observed in various AIA channels.
+AIA channels with relatively hotter temperature response component, {\it i.e.} 94, 131, 193 {\AA} we see parts of the ejected loops which are not visible in colder channels, {\it i.e.} 171, 211, 335 {\AA}.
+In Fig.~\ref{fig:dec_flare_dem}h \& i, we show the emission measure (EM) and DEM weighted temperature of the region, calculated from the AIA observations.
+The 85\% intensity contour of the plasma blob observed in NB4 is marked with solid black line in Fig.~\ref{fig:dec_flare_dem}i.
+We mark a region on the same panel from the center of the ejected loop.
+We plot the DEMs from these two regions.
+We plot the calculated DEMs in Fig.~\ref{fig:dec_flare_dem}j, for the 85\% intensity contour (black circles) and the central part of the loop (red triangles) respectively.
+
+%%%%%%%%%%
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim = {1cm 0.5cm 3cm 0.5cm}, clip, width=0.7\linewidth]{fig2.pdf}
+    \caption{(a) Inverted AIA 171 {\AA} observation during the ejection of the loop.
+Red dashed box marks the region considered for the DEM analysis.
+(b) {--} (g)  AIA observation in 94, 131, 171, 193, 211, and 335 {\AA} of the red dashed region respectively.
+The inverted 171 {\AA} observation (panel d) is overplotted on co-aligned \suit~NB4 observation (yellow).
+(h) Calculated EM from the AIA observations.
+(i) Calculated DEM weighted temperature from the AIA observations.
+The 85\% intensity contour of the \suit~NB4 blob is marked with solid black line.
+The dashed black line marks the central part of the loop.
+(j) The DEM from solid black contour and dashed black contour are plotted with black circles and red triangles respectively.}
+    \label{fig:dec_flare_dem}
+\end{figure*}
+%%%%%%%%%%
+
+We also calculate the velocity of the plasma blob from \suit~NB4 and AIA 1600 {\AA} observations and compare them.
+We show the trajectory of the plasma blob as observed from \suit~NB4 in Fig.~\ref{fig:dec_flare_dem}a.
+The position of the blob at various timestamp are marked with red cross.
+The velocity calculated bu tracing the ejecta is plotted in Fig.~\ref{fig:dec_flare_dem}b with blue circles (AIA 1600 {\AA}) and red triangles (\suit~NB4).
+The vertical dashed black line shows the start of the acceleration of the ejected material.
+Due to the larger field of view (FoV) of \suit~we can track the ejected material further out.
+In Fig.~\ref{fig:dec_flare_dem}c {--} f shows the sequence of observations from AIA 1600 {\AA} (purple) and 171 {\AA} (yellow-black).
+Fig.~\ref{fig:dec_flare_dem}g shows the {\it GOES} 1 {--} 8 {\AA} light curve during the flare.
+The four vertical red lines marks the times of Fig.~\ref{fig:dec_flare_dem}c {--} f.
+The soft X-ray flux reaches a plateau around 21:42 UT and starts to rise again after that, exhibiting multiple eruptions from the same active region.
+
+%%%%%%%%%%
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim = {0cm 1.7cm 0.5cm 2cm}, clip, width=0.7\linewidth]{fig3.pdf} \\
+    \includegraphics[trim = {1.5cm 4cm 2.5cm 5.5cm}, clip, width=0.5\linewidth]{fig3b.pdf} \\
+    \caption{(a)\suit~NB4 observation at 21:42 UT.
+The trajectory of the plasma blob is marked with red crosses.
+(b) The velocity of the ejected material from AIA 1600 {\AA} (blue circle) and \suit~NB4 (red triangle) observation.
+The vertical dashed black line marks the start of acceleration.
+(c) {--} (f) Sequence of AIA 171 {\AA} inverted (yellow black) and 1600 {\AA} (purple) observations.
+A kink develops in the loops at 21:42 UT, marked with black arrow in (d).
+This is later ejected and accelerates.
+(g) GOES 1 {--} 8 {\AA} flux.
+The four vertical lines mark the times of panel (c) {--} (f).}
+    \label{fig:dec_flare_vel}
+\end{figure*}
+%%%%%%%%%%
+
+%%----------------------------------------------------
+\subsection{Discussion} \label{sec:dec_31st_dis}
+%%----------------------------------------------------
+
+For the 31 December, 2023 X5 flare we only have (2k $\times$ 2k) one minute cadence observations in NB4 (\ion{Mg}{2} h).
+We see the eruption associated with the ejection of a plasma blob, which is cospatial with the ejected loops in AIA 1600 {\AA} and 171 {\AA}, as illustrated in Fig.~\ref{fig:dec_flare_obs}.
+We then investigate the thermal structure of the ejected loops from AIA observations, to understand the thermal environment of the plasma environment around the ejected material observed in NB4.
+From the AIA coronal channel observations, we find that parts of the ejected loop appear brighter and this bright region is cospatial with the ejected blob observed in NB4.
+From the DEM analysis we see that the central part of the ejected loop is hotter and less dense, compared to the parts of the loop which appear brighter (this is illustrated in Fig.~\ref{fig:dec_flare_dem}h \& i).
+In Fig.~\ref{fig:dec_flare_dem}i we mark the central part of the ejected loop with dotted black line and the 85\% intensity contour of the ejected NB4 plasma blob in black solid line.
+The DEM from these two regions are marked with red triangles and black circles respectively in Fig.~\ref{fig:dec_flare_dem}j.
+These DEMs clearly show that the region around the ejected material observed with NB4 have more colder material, resulting in overall colder DEM weighted temperature and denser surrounding environment.
+
+%%%%%%%%%%%%%%%%%%%%%%
+\begin{wrapfigure}{l}{0.45\textwidth}
+    \centering
+    \includegraphics[trim={2cm 2.5cm 2cm 8.7cm}, clip, width=0.9\linewidth]{fig4.pdf}
+    \caption{Sequence of cartoons depicting possible ejection mechanism for the cold plasma blob observed in {\suit} NB4.}
+    \label{fig:cart}
+\end{wrapfigure}
+%%%%%%%%%%%%%%%%%%%%%%
+
+We further investigate the kinematics of the ejected material.
+The ejection can be tracked further out with the {\suit} observations, albeit with much lower time cadence (1 minute) compared to AIA 1600 {\AA} (24 s).
+The velocity of the ejection is plotted in Fig.~\ref{fig:dec_flare_vel}b with blue circles (AIA 1600 {\AA}) and red triangles ({\suit} NB4).
+The measured velocities are consistent with each other.
+We see an acceleration at $\sim$ 21:42 UT.
+The tentative start of the acceleration is marked with a vertical dashed black line in Fig.~\ref{fig:dec_flare_vel}b.
+We see two successive eruption from the same active region wit the AIA observations.
+This is also illustrated by the {\it GOES} 1 {--} 8 {\AA} light curve in Fig.~\ref{fig:dec_flare_vel}g, as we see a first peak $\sim$ 21:40 UT and a second peak $\sim$ 21:55 UT.
+The two successive ejection is also consistent with the observed velocity structure.
+
+We show a possible mechanism to explain the ejection of the plasma blob in Fig.~\ref{fig:cart}.
+The initial eruption at $\sim$ 21:40 UT pushes cold dense material, as we see relatively steady rise from Fig.~\ref{fig:dec_flare_vel}b.
+Other loops from the same eruption, reconnects with the previous loops and develops a kink at $\sim$ 21:42 UT.
+The kink developing can be seen in Fig.~\ref{fig:dec_flare_vel}d, marked by black arrow.
+This is equivalent to the configuration in Fig.~\ref{fig:cart}c.
+The release of energy ejects the loop, as the acceleration is seen in the velocity profile after this in Fig.~\ref{fig:dec_flare_vel}b.
+This ejection is also accompanied by a subsequent brightening from the foot point as seen from AIA 1600 {\AA} observations in Fig.~\ref{fig:dec_flare_vel}e \& f.
+The SXR flux from this second eruption eventually peaks at $\sim$ 21:55 UT.
+
+%%----------------------------------------------------
+\section{X2.9 flare observed on May 27th, 2024} \label{sec:dec_31st}
+%%----------------------------------------------------
+
+NOAA AR 13697 was fully visible on the southeast limb from 29th May 2024.
+An X2.9 flare occurred from this active region on 27th May at 06:49 UT.
+The flare was localized by the onboard flare detection algorithm of {\suit} (For further details please refer to \citep{flare_det}).
+The event was located at $\sim$ [-920{\arcsec}, -250{\arcsec}] and the {\it GOES} SXR flux peaked at 07:08 UT.
+The footpoints of the flare were occulted behind the limb, ane the flare loops are only visible once they rise from behind the limb.
+
+Similar to the previous event we use the JPL horizons system to retrieve the position of Aditya-L1 and project the observations to Earth vantage.
+We then co-register and co-align AIA 1600 {\AA}, AIA 131 {\AA} and {\suit} NB4 observations.
+We show a sequence of co-aligned observations in Fig.~\ref{fig:may_flare_obs}.
+In Fig.~\ref{fig:may_flare_obs}a {--} c the {\suit} observations (yellow) are over-plotted on AIA 1600 {\AA} observations (green-black).
+This sequence shows the initial prominence eruption.
+
+%%%%%%%%%%
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim = {0cm 0.7cm 0cm 2cm}, clip, width=0.7\linewidth]{fig1_.pdf}
+    \caption{(a) {--} (c) Sequence of AIA 1600 {\AA} (black-green) observations coaligned with {\suit} NB3 (yellow) observations.}
+    \label{fig:may_flare_obs}
+\end{figure*}
+%%%%%%%%%%
+
+Similar to the previous event, we use DEMs calculated from AIA observations to investigate the thermal structure of the post flare loops.
+We show the post flare loops during the decay phase in Fig.~\ref{fig:may_flare_res}a.
+{\suit} NB4 (\ion{Mg}{2} h observation in yellow) is over-plotted on inverted AIA 131 {\AA} observation (blue-black).
+In Fig.~\ref{fig:may_flare_res}b \& c we plot the emission measure and DEM weighted temperature calculated from the AIA observations.
+The 80\% intensity contour of the off-limb {\suit} NB4 observations are marked in Fig.~\ref{fig:may_flare_res}c.
+
+%%%%%%%%
+\begin{figure*}[ht!]
+    \centering
+    \includegraphics[trim={0.2cm 0cm 2cm 2cm}, clip, width=0.8\textwidth]{Figures/fig5.pdf}
+    \caption{(a) AIA 131 {\AA} observation in inverted colormap (blue-black), coaligned with {\suit} NB3 observation (yellow).
+(b) Calculated emission measure from the AIA observation.
+(c) Calculated DEM weighted temperature from the AIA observation.}
+    \label{fig:may_flare_res}
+\end{figure*}
+%%%%%%%%
+
+%%%%%%%%%
+\subsection{Discussion}\label{may27_dis}
+%%%%%%%%%
+
+Fig.~\ref{fig:may_flare_res}a we see that the {\suit} NB4 off limb features are cospatial wiht the base of the plasma sheet and top of the post flare arcades in AIA 131 {\AA} observations (blue-black).
+We mark the 85\% intensity contour of {\suit} NB4 observation in the subsequent panels b \& c, which show the emission measure and DEM-weighted temperature calculated from the AIA observations.
+
+The {\suit} NB4 observations are co-spatial with low temperature and relatively low-density region at the loop top, just below the plasma sheet.
+There is a higher-density region right on top of this region at the base of the plasma sheet.
+Please note that the density and temperature calculated here are calculated from AIA observations, which are not as sensitive to plasma outside of $\log \mathrm{T} \sim$ 5 {--} 7.5 K.
+The low density at the loop top can easily be attributed to the plasma being outside of this temperature range.
+But that would be in contradiction to one of the standard scenarios of post-flare loops, where it is assumed that the post-flare loop-top brightening is created by a collision of evaporating flows from the foot-points and results in elevated density and temperature at the loop top.
+This has also been demonstrated from 1d loop simulations \citep{sharma16, reeves07}.
+
+%%%%%%%%%%%%
+\section{Outlook}
+%%%%%%%%%%%%

### 2024-08-14 introduction/intro.tex
Updates from Overleaf

@@
 
-The Sun is our nearest astrophysical object, which serves as a natural laboratory for various branches of Physics - atomic physics, spectroscopy, turbulence, magneto-hydrodynamics, stellar evolution, dynamo and magnetism and plays a key role in space and terrestrial weather.
+The Sun is our nearest astrophysical object, which serves as a natural laboratory for various branches of Physics - atomic physics, spectroscopy, turbulence, magneto-hydrodynamics, stellar evolution, dynamo and magnetism and plays a key role in \sroy{driving} space and terrestrial weather.
 The Sun is also the primary source of light and energy on earth.
-So it is only natural that we try to understand the different physical processes involved in the energectics of the Sun, which indirectly affects life on Earth.
-In this chapter I briefly introduce the Sun and various layers of its atmosphere.
-At the end we provide a motivation for the thesis.
+So it is only natural that we try to understand the different physical processes involved in the energectics of the Sun, which directly affects life on Earth.
+In this chapter I briefly introduce the Sun, various layers of its atmosphere \sroy{and solar flares}.
+\sroy{Finally we provide a motivation for the thesis and a brief outline.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Sun}\label{sun}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 The Sun is a G2V star, with surface luminosity $3.86~\times~10^{26}$ W and an effective temperature of $\sim 5780~K$.
-The Sun is mostly made out of Hydrogen(92.1\%) and Helium(7.8\%) along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe.
-The study of the Sun can be mainly divided into three components: the Solar interior, the Solar atmosphere and the Heliosphere.
+The Sun is mostly made out of Hydrogen(92.1\%) and Helium(7.8\%) along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe\sroy{, among others}.
+The study of the Sun can be divided into three components: the Solar interior, the Solar atmosphere and the Heliosphere.
+Fig.~\ref{fig_solar_int} shows a schematic diagram of various layers of the Sun.
+\sroy{Below we briefly describe these three regions.}
 
@@
 
-In the innermost zone of the star the Sun has a temperature of about 15 MK and a density of $1.6~\times~10^{5}~km.m^{-3}$ that fuses Hydrogen into Helium mainly by p-p cycle \citep{bethe38} and to some extent by CNO cycle \citep{bethe39}.
+In the innermost zone, the Sun has a temperature of about 15 MK and a density of $1.6~\times~10^{5}~km.m^{-3}$ that fuses Hydrogen into Helium mainly by p-p cycle \citep{bethe38} and to some extent by CNO cycle \citep{bethe39}.
+Beyond the core we have the optically thick radiative zone, where the Hydrogen and Helium are completely ionized.
+The high energy $\gamma$-ray photons generated in the core, have very small mean free path in this region, as they collide numerous times eventually thermalizing \sroy{and} becoming visible photon.
+Beyond the radiative zone the degree of ionization of Hydrogen and Helium changes drastically giving rise to a sharp temperature gradient \sroy{leading to convective instability}.
+This is the convective zone where the energy from the inner layers of the Sun is transported adiabetically to the surface of the Sun.
+In between the radiative and the convective zone, there is a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine, which is believed to play a major role in generating Sun's magnetic field via the Dynamo process \citep{corbard01}.
 
 %% ############# %%
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
     \includegraphics[width = 0.8\linewidth]{Figures/solar_int.png}
-    \caption{A schematic depiction of the different layers of the Sun.
-The figure also shows some of the most prominent magnetic structures on the Sun e.g sunspot, prominence, coronal hole.
+    \caption{A schematic depiction of the different \sroy{regions} of the Sun, \sroy{including} some of the most prominent magnetic structures on the Sun e.g sunspot, prominence, coronal hole.
 Credit : NASA/Goddard.}
@@
 %% ############# %%
-
-Fig.~\ref{fig_solar_int} shows a schematic diagram of various layers of the Sun.
-Beyond the core we have the optically thick radiative zone, where the Hydrogen and Helium are completely ionized.
-The high energy $\gamma$-ray photons generated in the core, have very small mean free path in this region, as they collide numerous times eventually thermalizing becoming visible photon.
-Beyond the radiative zone the degree of ionization of Hydrogen and Helium changes drastically giving rise to a sharp temperature gradient.
-This is the convective zone where the energy from the inner layers of the Sun is transported adiabetically to the surface of the Sun.
-In between the radiative and the convective zone, there is a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine, which is believed to play a major role in generating Sun's magnetic field via the Dynamo process \citep{corbard01}.
 
@@
 %% ############# %%
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
     \includegraphics[width = 0.8\linewidth]{Figures/solar_atm.png}
-    \caption{The variation of electron temperature (solid line) and electron density ($\mamthrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dotted- dashed line) in the solar atmosphere as derived based on the 1-D model calculations by \sr{Ref.
+    \caption{The variation of electron temperature (solid line) and electron density ($\mamthrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dot-dashed line) in the solar atmosphere as derived based on the 1-D model calculations by \sr{Ref.
 here}.}
@@
 A giant prominence erupted from the south east limb.
-The erupted prominence material was visible in all AIA channels from 304 \AA~(Chromospheric He II, see fig.~\ref{fig:aia-feature} \textbf{panel (a)}) across all six Coronal channels (\textbf{panel (b){--}(g)}).
-The sun spots were also clearly visible in HMI magnetogram and continuum (see fig.~\ref{fig:aia-feature} \textbf{panel (h)}).
-In \textbf{panel (i)} we show the co-aligned AIA 304 \AA, 131 \AA and HMI magnetogram image.
-The sunspots lie at the base of the erupted prominence, accompanied by the hot thermal plasma associated with the accompanying flare.
+The erupted prominence material was visible in all AIA channels from 304 {\AA} (Chromospheric He II, see Fig.~\ref{fig:aia-feature}a) across all six Coronal channels (Fig.~\ref{fig:aia-feature}b {--} g).
+The sun spots were also clearly visible in HMI magnetogram and continuum (see Fig.~\ref{fig:aia-feature}h).
+In Fig.~\ref{fig:aia-feature}i we show the co-aligned AIA 304 {\AA} and HMI magnetogram image.
+The sunspots lie at the base of the erupted prominence, accompanied by the hot thermal plasma associated with the accompanying flare (visible in Fig.~\ref{fig:aia-feature}e {--} f).
 The novelty of such observation lies in the clear spatial connection across various layers of the sun, connected via energy and momentum transported from one layer to the other.
@@
 %%%%%%%%%%%%%
-\begin{figure}
+\begin{figure}[ht!]
     \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
+\begin{table}[ht!]
     \centering
+    \resizebox{\textwidth}{!}{%
+    \begin{tabular}{||c|c|c|c|c|c|c||}
     \hline 
     \hline
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{||c|c|c|c|c|c|c||}
        Study & No. of flares & GOES class range & Thermal model & Thermal spectrum & Thermal volume & Thermal losses \\

### 2024-08-14 main_thesis_file.tex
Updates from Overleaf

@@
 % use "plain" for committee to read, or for printing single-spaced in general
-\documentclass[plain]{hvdthesis}
+\documentclass[keepsake]{hvdthesis}
 
@@
 %\copyright
+
+\newpage
+
+\thispagestyle{plain}
+{\centerline {\em "The first principle is that you must not fool yourself, }}
+{\centerline {\em and you are the easiest person to fool."}}
+{\rightline {\em {--} Richard P. Feynman}}
+
+\newpage
 	%% Abstract
@@
 \newpage
+\clearpage
+
+\thispagestyle{plain}
+%\addcontentsline{toc}{chapter}{List of Publications}
+\chaptermark{List of Publications}
+\vskip 0.5cm
+{\centerline {\Large \bf List of Publications}}
+\vskip 0.5cm
+\normalsize
+
+\input{pub.tex}
+
+\newpage
+\clearpage
 
@@
 \addcontentsline{toc}{chapter}{List of Abbreviations}
-\chaptermark{List of Abbreviations}
+%\chaptermark{List of Abbreviations}
 \vskip 0.5cm
@@
 \newpage
+\clearpage
 	%% Acknowledgments
@@
 %\hfill -- RCH
-%\newpage
 
+\newpage
 \clearpage
@@
 \vspace*{\fill}
-{\centerline {\em Your thoughtful dedication goes here.}}
+{\centerline {\em Dedicated to everyone who pushed me one step at a time,}} 
+{\centerline {\em every time I was about to give up!}}
+{\centerline {\em And to my younger self, who was brave enogh to embark on this journey...}}
 %\vskip 1.5cm
@@
 \chaptermark{SUIT preparatory analysis}
-\begin{quote}
-{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
-{authors,
-{\em journal reference info}}
-\end{quote}
 \input{./chapter3/ms.tex}
@@
 \input{./chapter4/ms.tex}
-%
-%\chapter{Stellar calibration of SUIT}\label{c:chap5}
-%\chaptermark{SUIT stellar calibration}
-%\begin{quote}
-%{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
-%{authors,
-%{\em journal reference info}}
-%\end{quote}
-%\input{./chapter5/ms.tex}
+
 %
@@
 %
-\chapter{First flares observed from {\suit}}\label{c:chap7}
-\chaptermark{Solar flare energy}
+\chapter{First flares observed by {\suit}}\label{c:chap7}
+\chaptermark{First Flares observed with SUIT}
 \begin{quote}
@@
 
+\chapter{Echoes of the Solar Inferno: Summary and Future Prospects}\label{c:chap8}
+\chaptermark{Outlook}
+\input{./chapter8/ms.tex}
+\clearpage
+
 % I changed  thebibliography in hvdthesis.cls, so that it generates
-% a ToC entry, and is headed References instead of Bibliography. -HJC
+% a ToC entry, and is headed References instead of Bibliography. -SR
 \singlespace
-\bibliographystyle{apj}
+%\bibliographystyle{aasjournal}
 \bibliography{your_bib_file}

### 2024-08-14 pub.tex
Updates from Overleaf

\section*{Refereed Journal Publications}

%%%%%%%%%%%
\begin{itemize}
    \item Soumya Roy and Durgesh Tripathi, 2024, ApJ, 964, 106, doi: \href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}
\end{itemize}
%%%%%%%%%%%

\section*{Technical Documents}

%%%%%%%%%%%
\begin{itemize}
    \item Roy, S., et al., "Solar Ultraviolet Imaging Telescope (SUIT) Handbook", ISRO Aditya-L1 mission
    \item Roy, S., et al., "Estimation of Effects of Space-craft Jitter on SUIT Imaging", ISRO Aditya-L1 mission
\end{itemize}
%%%%%%%%%%%

### 2024-08-16 introduction/intro.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Sun}\label{sun}
+\section{The Sun}\label{Sun}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This is the convective zone where the energy from the inner layers of the Sun is transported adiabetically to the surface of the Sun.
-In between the radiative and the convective zone, there is a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine, which is believed to play a major role in generating Sun's magnetic field via the Dynamo process \citep{corbard01}.
+In between the radiative and the convective zone, there is \sroy{believed to be }a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine.
+\sroy{This region} is believed to play a major role in generating Sun's magnetic field via the Dynamo process \citep{corbard01}.
 
@@
     \includegraphics[width = 0.8\linewidth]{Figures/solar_int.png}
-    \caption{A schematic depiction of the different \sroy{regions} of the Sun, \sroy{including} some of the most prominent magnetic structures on the Sun e.g sunspot, prominence, coronal hole.
+    \caption{A schematic depiction of the different \sroy{regions} of the Sun, \sroy{including} some of the most prominent magnetic structures on the Sun e.g Sunspot, prominence, coronal hole.
 Credit : NASA/Goddard.}
@@
 
-The layers outside the convection zone together, form the solar atmosphere - the Photosphere, which is also known as the Sun's surface, the Chromosphere, the transition region and the Corona.
+The layers outside the convection zone together, form the solar atmosphere \sroy{and is further divided into different regions.
+}The Photosphere, which is also known as the Sun's surface, the Chromosphere, the transition region and the Corona.
 While we can define geometrical height or depths to define these layers, it is much more useful to define them using the local optical depths of various spectral lines, which are directly used to observe the layers.
@@
     \includegraphics[width = 0.8\linewidth]{Figures/solar_atm.png}
-    \caption{The variation of electron temperature (solid line) and electron density ($\mamthrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dot-dashed line) in the solar atmosphere as derived based on the 1-D model calculations by \sr{Ref.
+    \caption{The variation of electron temperature (solid line) and electron density ($\mathrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dot-dashed line) in the solar atmosphere as derived based on the 1-D model calculations by \sr{Ref.
 here}.}
@@
 This is in the green part of the visible spectrum and the Sun is opaque in visible beyond this layer, hence it is called to be the surface of the Sun.
-This layer is 400-600 km deep and has an effective temperature of 5780 K.
+This layer is 400-600 km \sroy{thick} and has an effective temperature of 5780 K.
 The magnetic filed lines arising from the tacholine penetrate the Photosphere and creates a `carpet' over the whole region \citep{priest14}.
@@
 Some regions exhibit much stronger magnetic flux density often associated with highly twisted magnetic field structures.
-These magnetic features are manifested as sunspots, spicules, bright points etc.
+These magnetic features are manifested as Sunspots, spicules, \sroy{faculae} etc.
+\sroy{The Sunspots harbour some of the strongest concentrated magnetic fields, reaching up to several kilogauss in strength.
+The other noteworthy solar magnetic structure apart from these are believed to be spatially unresolved flux tubes composing a network with field strengths $\sim$ {\it $O(10^{3} G)$}} \citep{solanki93,grossman96,rubio19}.
 
-As the density changes drastically at the Photosphere compared to the convective zone, the thermalized photons from Sun's core start free streaming again, as the mean free path also increases drastically and as a result perturbs the thermal equilibrium (TE from hereon).
-So, we have to define the thermodynamic quantities of the Photosphere in Local Thermal Equilibrium (LTE from hereon).
-As we move away from the Photosphere, because the density keeps on decreasing steadily, the LTE conditions also start deviating similarly \citep{philips08}.
+As the density changes drastically at the Photosphere compared to the convective zone, the thermalized photons from Sun's core start free streaming, as the mean free path also increases drastically and as a result perturbs the thermal equilibrium (TE).
+\sroy{Therefore} the thermodynamic quantities of the Photosphere \sroy{are defined under the assumption of} Local Thermal Equilibrium (LTE).
+As we move \sroy{higher} from the Photosphere the LTE conditions also start deviating \sroy{because the density keeps on decreasing steadily} \citep{philips08}.
 
@@
 The Chromosphere is a highly non-uniform dynamic layer with a thickness of 1500~--~3000~km, with increasing temperature (upto $10^{4}$ K) and decreasing number density.
-As seen in the fig.
-\ref{fig_solar_atm}, the temperature of the Chromosphere saturates before the dramatic rise in the transition region.
+As seen in the Fig.~\ref{fig_solar_atm}, the temperature of the Chromosphere saturates before the dramatic rise in the transition region.
 This saturation is attributed to a steady deposition of acoustic energy by creation of shock waves \citep{carlsson07}.
@@
 
-In fig.~\ref{fig:sji_features} we show the NOAA AR 13521 in IRIS SJI 2796 {\AA} (left panel) and 2832 {\AA} (right panel).
-The dark sunspots and plage regions surrounding it are clearly visible in the 2832 {\AA} wavelength window.
+In Fig.~\ref{fig:sji_features} we show the NOAA AR 13521 in IRIS SJI 2796 {\AA} (left panel) and 2832 {\AA} (right panel).
+The dark Sunspots and plage regions surrounding it are clearly visible in the 2832 {\AA} wavelength window.
 In the 2796 {\AA} window we see the plage along with light bridges more clearly.
@@
 
-The transition region above the Chromosphere is a thin, dynamic layer where we witness a dramatic increase in temperature by two orders of magnitude along with a similar decrease in electron density by nearly 5-6 orders of magnitude which is demonstrated in fig.
+The transition region above the Chromosphere is a thin, dynamic layer where we witness a dramatic increase in temperature by two orders of magnitude along with a similar decrease in electron density, which is demonstrated in Fig.
 \ref{fig_solar_atm}.
-In general the this layer is roughly $\sim$ 100 km in thickness, but that can change depending on various dynamic conditions of Chromosphere($\sim~10^{4}~K$) below, or Corona($\sim~10^{6}~K$) on top.
+In general the this layer is roughly $\sim$ 100 km in thickness, but that can change depending on various dynamic conditions of Chromosphere($\sim~10^{4}~K$) below, \sroy{and/}or Corona($\sim~10^{6}~K$) on top.
 The transition region is generally characterized by the steep change in the temperature, pressure gradients, drastic change in local optical depth and competition between gas pressure and magnetic pressure.
@@
 
-The outermost layer of the Solar atmosphere is the Corona.
-The Corona is only visible in naked eyes during the total solar eclipse or via Coronagraphs.
-It maintains a steady temperature of 1-2 Mk during ambient conditions, but can rise upto tens of MK during solar flares.
-The coronal continuum spectrum is produced due to Thompson scattering of photons from photosphere off coronal electrons.
+The outermost layer of the atmosphere is the Corona.
+The Corona is only visible in naked eyes during the total solar eclipse or via coronagraphs.
+The coronal continuum spectrum is produced due to Thomson scattering of photons from photosphere off coronal electrons.
 Corona also emits in various emission lines, e.g.
@@
 across a wide band of electromagnetic spectrum ranging from X-ray to visible wavelengths.
-
 Similar to the other layers, the corona exhibits a variety of structures such as ARs, coronal holes, bright points, filaments, flares.
 The flare arcades are most prominently visible in the Corona.
-So, most of our existing studies over the last decade has focused on the coronal features of the flares.
-In fig.~\ref{fig:sji_features} we show one of the most well known and well studied solar eruptions from Aug 31st, 2012.
-A giant prominence erupted from the south east limb.
-The erupted prominence material was visible in all AIA channels from 304 {\AA} (Chromospheric He II, see Fig.~\ref{fig:aia-feature}a) across all six Coronal channels (Fig.~\ref{fig:aia-feature}b {--} g).
-The sun spots were also clearly visible in HMI magnetogram and continuum (see Fig.~\ref{fig:aia-feature}h).
-In Fig.~\ref{fig:aia-feature}i we show the co-aligned AIA 304 {\AA} and HMI magnetogram image.
-The sunspots lie at the base of the erupted prominence, accompanied by the hot thermal plasma associated with the accompanying flare (visible in Fig.~\ref{fig:aia-feature}e {--} f).
-The novelty of such observation lies in the clear spatial connection across various layers of the sun, connected via energy and momentum transported from one layer to the other.
+\sroy{The Corona also exhibits the most intense eruptions in the Solar system known as flares, which can be accompanied by Coronal Mass Ejections (CMEs).
+The Corona maintains a steady temperature of 1-2 MK during ambient conditions, but can rise up to tens of MK during solar flares.}
 
@@
 The flare loops of the associated event is visible in AIA 94 \AA~\textbf{(panel e)} and AIA 131 \AA~\textbf{(panel f)}.
-The sunspots are visible in HMI continuum \textbf{panel (h)}.
+The Sunspots are visible in HMI continuum \textbf{panel (h)}.
 We show a co aligned map of AIA 304 \AA, HMI magnetogram and AIA 131 \AA~in \textbf{panel (i)}.
-The spatial association of the sunspots with the hot flareloop plasma and the prominence eruption is clearly demostrated here.
+The spatial association of the Sunspots with the hot flareloop plasma and the prominence eruption is clearly demostrated here.
 }
@@
 They can also launch high energetic particles into the interplanetary medium.
-Most of the flares occur in magnetic active regions, and the amount of flare energy released is comparable to the free energy stored in the magnetic system.
+Most of the flares occur in magnetic active regions, and the amount of flare energy released is comparable to the free energy stored in the magnetic system \citep{emslie12,ash17}.
 The term "flare" is generally used explicitly for the entire magnetically-driven event's electromagnetic radiation, as it is the most significant fraction of the total energy liberated.
@@
 It is also known that larger events occur much less frequently than smaller events.
+
+In Fig.~\ref{fig:sji_features} we show one of the most well known and well studied solar eruptions from Aug 31st, 2012.
+A giant prominence erupted from the south east limb.
+The erupted prominence material was visible in all AIA channels from 304 {\AA} (Chromospheric He II, see Fig.~\ref{fig:aia-feature}a) across all six Coronal channels (Fig.~\ref{fig:aia-feature}b {--} g).
+The Sun spots were also clearly visible in HMI magnetogram and continuum (see Fig.~\ref{fig:aia-feature}h).
+In Fig.~\ref{fig:aia-feature}i we show the co-aligned AIA 304 {\AA} and HMI magnetogram image.
+The Sunspots lie at the base of the erupted prominence, accompanied by the hot thermal plasma associated with the accompanying flare (visible in Fig.~\ref{fig:aia-feature}e {--} f).
+The novelty of such observation lies in the clear spatial connection across various layers of the Sun, connected via energy and momentum transported from one layer to the other.
 
@@
 Carrington and R.
-Hodgson observed the first flare in the continuum of white light\citep{carrington1859,hodgson1859}.
-The localized brightening on the Sun have remained an enigma ever since.
+Hodgson \sroy{independently} observed the first flare in the continuum of white light\citep{carrington1859,hodgson1859}.
+\sroy{Such} localized brightening on the Sun have remained an enigma ever since.
 We have been observing the local flaring events across all wavelengths from both ground and space based observatories.
@@
 No two events were similar, as there were variations observed in source of size, ejections of plasma along with shock waves driving into the interplanetary space.
-Advances of radio technology during the second world war ensured detection of presence of non-thermal electrons in the solar corona, during military radar operations \citep{hey46}.
+Advances of radio technology during the second world war \sroy{affirmed} detection of presence of non-thermal electrons in the solar corona, during military radar operations \citep{hey46}.
 Around the same time S.E.
 Forbrush noticed ground level cosmic ray enhancement during major solar flares.
-These discoveries eluded that the flaring events do not only involve the thermal plasma, but is somehow connects with high energy particles and involves the corona.
-in the 1950s we started observing the Sun in hard X-rays ($\ge~10~keV$) with rockets and balloons.
+These discoveries eluded that the flaring events do not only involve the thermal plasma, but somehow connect with high energy particles and involves the corona.
+
+In the 1950s we started observing the Sun in hard X-rays ($\ge~10~keV$) with rockets and balloons.
 \cite{peterson59} discovered the first hard X-ray emission during a flare in 1958.
@@
 The logical explanation is: the soft X-ray mainly originates from a thermal plasma heated by the energy of the flaring event deposited by the flare accelerated electrons.
-It is important to mention that we know now, Eqn.\ref{npt_eff_eq} is only valid if cooling by conduction of radiation is negligible.
+It is important to mention that we know now that Eqn.\ref{npt_eff_eq} is only valid if \sroy{cooling by conduction is negligible and/or the role of ions in the flare energy deposition was minimal.}
 
@@
 
-There were several observations like Neupert effect, which would help us to constrain several phenomenon observed in the flares:
+\sroy{Based on various multi-wavelength studies of solar flares, combined with theoretical modelling a `standard' model of solar flares has been advocated by \cite{carmichael64,sturrock66,hirayama74,kopp76}.
+The flares occur due to abrupt release of magnetic free energy which was previously stored in the coronal magnetic field via flux emergence and surface motions \citep{forbes06}.
+Majority of the strongest flares are eruptive in nature.
+The `standard' model attributes the release of flare energy to magnetic reconnection in corona, which happens due to the eruption and/or coronal mass ejection \citep{shibata95,lin_n_forbes00,moore01,priest_n_forbes02}.
+It is noteworthy that, while over the years there have been continuous attempts this is not a all compassing quantitative model.
+Rather it is an attempt to orderly unify multi-wavelength observation and modelling attempts into a structure.
+Naturally the model can not explain all observations from various flares.
+A schematic picture of the model is shown in Fig.~\ref{fig:std_mod}.
+Below we describe the saliant points of the `standard' model:}
 
@@
     \centering
-    \includegraphics[width=0.5\linewidth]{Figures/phu_63_8_818_f2.jpg}
-    \caption{A schematic diagram of the standard model of solar flare (adapted from \cite{lysenko20}).}
+    \hspace{5cm}
+    \includegraphics[trim={1cm 8cm 0cm 8cm}, clip, width=0.95\linewidth]{Figures/std_mod.pdf}
+    \caption{A schematic diagram of the standard model of solar flare.}
+    \label{fig:std_mod}
 \end{figure}
@@
 \begin{enumerate}
-    \item The magnetic reconnetion happens in corona, releasing the magnetic free energy.
+    \item The magnetic reconnection happens in the corona, releasing the magnetic free energy.
 Electrons and energetic particles from the reconnetion site are accelerated along the realigned magnetic field lines.
-The accelerated particles that escape along the open field lines towards the earth gives rise to the particle events seen from earth.
-    \item The accelerated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave observations seen from flares via gyro magnetic radiation.
-    \item The accelerated particles hit the Chromosphere which is considerably denser than the Corona, giving rise to Hard X-ray and gamma ray observed from the foot points.
+The accelerated particles that escape along the open field lines towards the earth give rise to the particle events seen from Earth.
+\sroy{The coronal reconnection source where the energy is released is often observed in HXR.
+The loop top HXR sources are often accompanied by the thermal SXR sources.
+The loop top HXR source is observed above the coronal SXR source \citep{masuda94}.
+Later on, most of the HXR sources were reported to be cospatial with the SXR source \citep{bataglia_n_benz07}.
+This thermal source is distinctly different from the post flare SXR and EUV loops.
+This thermal coronal source appears before the HXR emission begins, completely contrary to the "Neupert" behaviour.
+This SXR loop top source is a key behaviour of pre-flare phase.
+The emission measure of these sources are higher than typical coronal levels, suggesting evaporation from chromosphere before the HXR emission.
+This also suggests that during the early phases of flare, the energy is conducted gradually by thermal particles, compared to the energetic non-thermal particles later on.
+
+    Given the existence of the thermal source, the coronal non-thermal source can be explained by a beam of non-thermal particles injected into the dense coronal thermal source.
+Some of the injected electrons escape the coronal source and precipitate lower.
+This model is known as the intermediate thin-thick target model (ITTT, proposed by \cite{wheatland95} and investigated further by \cite{metclaf99,fletcher98}.) While the ITTT model explains most of the observations from flares there are certain inconsistencies regarding the coronal X-ray source {\it e.g.} the source of coronal SXR in preflare conditions, difference in expected HXR brightness of the cornal source from models to observations still elude us.
+It is fair to summarise that even though we by and large understand under what ambient conditions how the coronal HXR source is created, we do not understand what underlying process cause such an environment to arise.}
+    \item The precipitated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave \sroy{and radio} observations seen from flares via gyro magnetic radiation \sroy{at various frequencies dictated by the characteristics of local plasma}.
+    \item The accelerated particles hit the Chromosphere, which is considerably denser than the Corona, giving rise to Hard X-ray and gamma-ray observed from the foot points.
 This also explains why the coronal hard X-ray source is considerably softer than the foot points.
-The energetic particles deposit their energy into the local Chromosphere, as they go through series of collision and eventually thermalize.
-    \item  As the plasma thermalizes, it starts emitting in thermal bremsstrahlung giving rise to the soft X-ray observed.
+The energetic particles deposit their energy into the local chromosphere as they go through a series of collisions and eventually thermalize \citep{brown83}.
+\sroy{Foot point sources are occasionally detected on H-alpha flare ribbons that are approximately 30,000 km apart, marking the base of a magnetic arcade \citep{masuda01}.}
+
+    \sroy{$\gamma$-ray emission is visible between 0.8 {--} 20 MeV generated by the accelerated ions.
+The neutron capture line at 2.2 MeV forming Deuterium is usually the strongest characteristic line visible from such emissions.
+Protons and other accelerated ions collide with the dense chromosphere and produce neutrons.
+These neutrons are captured by ambient protons to form Deuteron \citep{ramtay74,hua87}.
+There were later RHESSI observations \citep{hurford_2003,hurford_2006} that showed that the $\gamma$-ray footpoints did not coincide with the HXR footpoints.
+This demonstrated that the ions and electrons were accelerated differently, as proposed by \cite{emslie_2004}.}
+    \item  As the plasma thermalizes, it emits in thermal bremsstrahlung, giving rise to the soft X-ray \sroy{radiation}.
 Also, as the energy is deposited into the Chromosphere from the accelerated particles, it heats the local Chromosphere environment it gradually increases the local pressure.
-    \item As the pressure grows, when the pressure gradient builds up enough the local plasma starts expanding upwards(essentially due to buoyancy) and slowly fills up the coronal loops with soft X-ray emitting plasma.
+As the pressure grows, when the pressure gradient builds up enough, the local plasma starts expanding upwards(essentially due to buoyancy) and slowly fills up the coronal loops with soft X-ray emitting plasma.
 This phenomenon is known as "Chromospheric evaporation".
-This was directly observed later on, in blue-shifted lines of hot material.
-    \item This whole scenario explains the Neupert effect.
+This was directly observed in blue-shifted lines of hot material.
+\sroy{This was first reported by \cite{doscheck80,feldman80}.
+\cite{antonucci89} reported velocities of 300 {--} 400 km/s with temperature $\sim$ 20 MK in \ion{Ca}{19}, while later on \cite{milligan06} reported much gentler up-flow with velocities $\sim$ 200 km/s in \ion{Fe}{19} line from {\it SOHO}/CDS observations.
+Several simulations also reproduced evaporation arising from non-thermal particle precipitation \citep{sterling93,hori98,reeves07}.}
+    %\item This whole scenario explains the Neupert effect.
 As the energy form the accelerated particles is converted into the soft X-ray emitting plasma, and it builds up over time.
@@
 For example, there have been observations of flares where the hard X-ray foot point do not form.
-It is proposed that in these cases the plasma in the coronal loops is so dense that the accelerated particle collide enough to thermalize within the flare loops before reaching the Chromosphere, defusing the energy more evenly within the loop, rather than dumping it at the base of the loops \citep{veronig02,veronig04}.
+It is proposed that in these cases the plasma in the coronal loops is so dense that the accelerated particle collide enough to thermalize within the flare loops before reaching the chromosphere, defusing the energy more evenly within the loop, rather than dumping it at the base of the loops \citep{veronig02,veronig04}.
 Another flare which previously occurred at the same region might explain the denser coronal loops \citep{strong84,bone07}.
@@
 The re-configuring of magnetic structure, which almost always involves complex geometry, making almost all events unique in some sense.
-After that the released magnetic free energy is transported across various layers of the sun and converted into various other forms of energy.
-Considering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses.
+After that the released magnetic free energy is transported across various layers of the Sun and converted into various other forms of energy.
+\sroy{The overarching conversion of magnetic energy into various forms {\it i.e.} reconnection outflow, kinetic energy of particles, thermal and kinetic energy of chromospheric plasma is incredibly complex to model.}In case of the eruptive events, there is the added complexity of the kinetic and potential energy of the CMEs, the energy of the shocks and the kinetic energy of the solar energetic particles.
+%Considering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses.
 In case of the eruptive events, there is the added complexity of the kinetic and potential energy of the CMEs, the energy of the shocks and the kinetic energy of the solar energetic particles.
@@
 
+\sroy{In addition to these, there is one more looming question, related to the "standard" model of flares itself, that has been largely unanswered, not due to lack of efforts, rather limited mostly by the technological limitations dictating the detectability of the current instruments.
+In our discussion in \S\ref{sol_flr_std_mod}, we discussed about the fundamental differences inferred between the acceleration mechanisms of electrons and ions inferred from the different locations of the HXR and $\gamma$-ray foot points.
+The production of $\gamma$-ray from nuclear reactions in chromosphere opens up the possibility of high-energy nuclear reactions producing pions ($\pi^{0}$ and $\pi^{\pm}$) along with secondary neutrinos ($\nu$) through the decay of the pions.
+Such reactions would be driven by protons with energy $>$ 300 MeV \citep{ramtay75,hudson_n_ryan_95}.
+Detection of neutrinos will open up a new window in constraining the effects of the accelerated particles in the lower solar atmosphere, {\it i.e.} chromosphere and photosphere and the general characteristics of the local plasma environment.
+Unfortunately, in spite of considerable efforts no flare neutrinos have been detected so far.
+It is understood that the first hurdle is to detect a minute transient signal on top of the large solar neutrino background.
+This informs our required detection thresholds driven by the current ion acceleration models \citep{sol_nu_kamiokande,abe_2022}.
+If the inability to detect flare neutrinos persists, it indicates that not enough protons with energies $>$ 300 MeV is produced even in very large flares.
+That would impose an upper limit of the amount of energy that is deposited in particle acceleration from flaring events and/or the efficiency of the accleration mechanism.}
+
 %% ################################################################# %%
@@
 These include the {\it IRIS} \citep{iris}, AIA 1600, 1700, and 304  {\AA} \citep{aia} and some the filters of {\it Hinode}/SOT \citep{sot}.
-In addition to these, we also have had balloon experiment {\it SUNRISE} \citep{sunrise1,sunrise2}, which provided high resolution imaging of the transition regiopn, from the SuFI instrument \citep{sufi}.
+In addition to these, we also have had balloon experiment {\it SunRISE} \citep{Sunrise1,Sunrise2}, which provided high resolution imaging of the transition regiopn, from the SuFI instrument \citep{sufi}.
 
@@
 We also describe the stellar calibration scheme and the selection criteria for the standard star target.
-We use a sun as a star spectra to evaluate the calibration scheme with the aforementioned throughput model.
+We use a Sun as a star spectra to evaluate the calibration scheme with the aforementioned throughput model.
     \item In chapter \ref{c:chap4}, we discuss the forward modelling pipeline developed for {\suit}.
@@
 We show that the accurate estimate as a function of time can have effects on the accurate estimation of thermal energy and the partition between the thermal and non-thermal component.
+    \item In chapter \ref{c:chap7} we discuss the first flare observations of {\suit}. 
 \end{itemize}

### 2025-04-11 Appendix1/a1.tex
Local changes

%%%%%%%%%%%%
%\renewcommand{\thesection}{6A}
%\section{Calculation of Oscillator strengths for the \ion{Mg}{2}~k~\&~h lines}\label{sec:a1}
%%%%%%%%%%%%

{\bf For a transition from u$\rightarrow$l the oscillator strengths can be expressed as:

%%-----------%%
\begin{equation*}
    f_{lu}~=~\lambda_{lu}^{2}\times \frac{g_{u}}{g_{l}}\times C_{1}\times A_{ul}
\end{equation*}
%%-----------%%
Where, $\mathrm{\lambda_{lu}}$ is the transition wavelength, $\mathrm{g_{u}}$ and $\mathrm{g_{l}}$ are the degeneracy of the upper and lower level and $\mathrm{A_{ul}}$ is the Einstein coefficient for spontaneous emission. Since the \ion{Mg}{2}~k~and~h line transitions happen to same lower energy state from two upper energy states of slightly different energy, this gives us:

%%-----------%%
\begin{equation}\label{eq6.2}
    \frac{f_{k}}{f_{h}}~=~\left(\frac{\lambda_{k}}{\lambda_{h}}\right)^{2}\frac{g_{k}A_{k}}{g_{h}A_{h}}
\end{equation}
%%-----------%%
Both the k and h line transitions are dipole transitions. In case of dipole transitions, the Einstein A coefficient can be expressed as:

%%%%%%%%%%
\begin{equation}
    A_{ul}~=~\frac{C_{2}}{\lambda^{3}}|\bra{l}r\ket{u}|^{2}
\end{equation}
%%%%%%%%%%

\noindent where, $\mathrm{\lambda}$ is the transition wavelength, $\mathrm{J_u}$ is the total angular momentum quantum number of the upper state. This gives us from eqn.~\ref{eq6.2},

%%%%%%%%%%
\begin{equation}\label{eqn6.4}
    \frac{f_k}{f_h}~=~\frac{\lambda_{h}g_k}{\lambda_{k}g_h}\frac{|\bra{3p~^{2}P_{\nicefrac{3}{2}}}\vec{r}\ket{3s~^{2}S_{\nicefrac{1}{2}}}|^{2}}{|\bra{3p~^{2}P_{\nicefrac{1}{2}}}\vec{r}\ket{3s~^{2}S_{\nicefrac{1}{2}}}|^{2}}
\end{equation}
%%%%%%%%%%

Now the radial part of the states $3p~^{2}P_{\nicefrac{3}{2}}$ and $3p~^{2}P_{\nicefrac{3}{2}}$ would be same and cancel out. So, the ratio would depend on the angular part of the wavefunctions. The reduced matrix element for electric dipole transitions between fine-structure states is related to the LS-coupled reduced matrix element by the Wigner-Eckhart theorem:

%%%%%%%%%%
\begin{equation}
    \bra{n'l'j'}r^{(1)}\ket{nlj}~=~(-1)^{l'+s+j+1}\sqrt{(2j'+1)(2j+1)}
    \begin{Bmatrix}
    l' & j' & s\\
    j & l & 1
    \end{Bmatrix} \bra{n'l'}r^{(1)}\ket{nl}
\end{equation}
%%%%%%%%%%

\noindent where $\mathrm{r^{(1)}}$ is the radial part of the position vector operator. For \ion{Mg}{2} the relevant quantum numbers are:

%%%%%%%%%%
\begin{itemize}
    \item l~=~0 (S state), l'~=~1 (P state)
    \item s~=~1/2
    \item j~=~1/2, j'~=~1/2 or 3/2
\end{itemize}
%%%%%%%%%%

\noindent Evaluating the 6j symbols we get:

%%%%%%%%%%%%
\begin{itemize}
    \item For j'~=~3/2: 
        $\begin{Bmatrix}
            1 & 3/2 & 1/2\\
            1/2 & 0 & 1
        \end{Bmatrix}$~=~$1/\sqrt{6}$

    \item For j'~=~1/2:
        $\begin{Bmatrix}
            1 & 1/2 & 1/2\\
            1/2 & 0 & 1
        \end{Bmatrix}$~=~$-1/\sqrt{3}$
\end{itemize}
%%%%%%%%%%%%

\noindent This gives us:

%%%%%%%%%%%%
\begin{equation}
    \frac{|\bra{3p~^{2}P_{\nicefrac{3}{2}}}\vec{r}\ket{3s~^{2}S_{\nicefrac{1}{2}}}|^{2}}{|\bra{3p~^{2}P_{\nicefrac{1}{2}}}\vec{r}\ket{3s~^{2}S_{\nicefrac{1}{2}}}|^{2}}~=~\frac{4.\frac{1}{6}}{2.\frac{1}{3}}~=~1
\end{equation}
%%%%%%%%%%%%

Plugging this back into eqn.~\ref{eqn6.4} we get,

%%%%%%%%%%%%
\begin{align*}
    \frac{f_k}{f_h}~=~\frac{\lambda_h}{\lambda_k}\times \frac{g_k}{g_h}~=~\frac{2.\frac{3}{2}+1}{2.\frac{1}{2}+1}~=~\frac{4}{2}~=~2
\end{align*}
%%%%%%%%%%%%
\noindent where $\frac{\lambda_h}{\lambda_k}~\simeq~1$.}

\renewcommand{\thesection}{\thechapter.\arabic{section}}

% \clearpage
% \renewcommand{\thesection}{\arabic{section}} % Back to normal numbering
% \setcounter{section}{0}

### 2025-04-11 Appendix1/a2.tex
Local changes

The regular observations of solar flares in Soft and Hard X-ray points towards the "thick-target" interpretation \citep{brown71} of flare accelerated electron injection into the Chromosphere. \cite{brown_2003} coined the source-integrated density weighted mean electron flux $\langle nVF\rangle(E)~[\mathrm{e^{-}cm^{-2}s^{-1}keV^{-1}}]$. The observed hard X-ray spectrum then can be expresses as

%%%%%%%
\begin{equation}\label{e1}
    I(\epsilon)~=~\frac{I}{4\pi R^{2}}\int_{\epsilon}^{\infty}~Q(\epsilon,E)\langle nVF\rangle(E)dE~\propto~\epsilon^{-\gamma}
\end{equation}
%%%%%%%

\noindent where R is the distance between the observed and the Sun, and $Q(\epsilon,E)$ is the angle-averaged bremsstrahlung cross section. The usual cold thick target model gives the relation between the mean electron flux and the injected electron rate as

%%%%%%
\begin{equation}\label{e2}
    \langle nVF\rangle(E)~=~\frac{E}{K}\int_{E}^{\infty}\dot{N}(E_{0})dE_{0}
\end{equation}
%%%%%%

\noindent $K~=~2\pi e^{4}ln(\Lambda)$ is the collision parameter, e is the electron charge in esu and $ln(\Lambda)$ is the Coulomb logarithm\citep{spitzer62}. The limitations of the standard "thick-target model" becomes more evident when we try to define the accelerated electron spectrum from eqn.~\ref{e1} and \ref{e2} we get

%%%%%%
\begin{equation}
    \dot{N}(E)~=~\dot{N_{0}}\frac{\delta-1}{E_c}\left (\frac{E}{E_c}\right )^{-\delta}
\end{equation}
%%%%%%

\noindent where $\delta~=~\gamma+1$. Here, $E_c$ is an arbitrary reference energy called the low energy cutoff, to stop the total rate of injected electron, $\dot{N_0}~=~\int_{E_c}^{\infty}~\dot{N}(E_{0})dE_0[s^{-1}]$ from diverging. The associated total power in the electron is given as

%%%%%
\begin{equation}
    P[keV.s^{-1}]~=~\int_{E_c}^{\infty}E_0N(E_0)dE_0~=~\frac{1}{\delta-2}E_c^{2-\delta}[\dot{N(E_c)}E_c^{\delta}]~=~\frac{\delta-1}{\delta-2}E_c\dot{N_0}
\end{equation}
%%%%%

\noindent As a consequence various physical properties become very strongly dependent on the low energy cut off. The low energy cut off results in non-physical discontinuous electron distribution of a Maxwellian and power law electron distribution. There are several different attempts to mitigate the nonphysical divergence of the thick target power law injection of electrons at lower energies. \cite{kontar15, kontar19} assumed a warm-target corona and cold chromosphere and included energy diffusion, transport and thermalization of the injected electrons through a warm layer of plasma on top of the cold target to rewrite eq.~\ref{e2} as

%%%%%
\begin{align}
    \langle nVF\rangle(E)~&=~\frac{E}{2K}e^{-E/k_{B}T}\int_{E_{min}}^{E}\frac{e^{E_0/k_{B}T}}{E_0G(\sqrt{E_0/k_{B}T})}~dE_0~\times \int_{E_0}^{\infty} \dot{N}(E_0)~dE_0 \notag \\
    &\simeq~\Delta EM\sqrt{\frac{8}{\pi m_e}}\frac{E}{(k_B T)^{3/2}}e^{-E/k_B T}~+~\frac{E}{K}\int_{E}^{\infty}~\dot{N}(E_0)~dE_0
\end{align}
%%%%%

\noindent where $\Delta EM$ is the "thermalized emission measure" which is created via the thermalization of the electrons and can be written as

%%%%%%
\begin{equation}
    \Delta EM~\simeq~\frac{\pi}{K}\sqrt{\frac{m_e}{8}}(k_B T)^{2}\frac{\dot{N_0}}{E_{min}^{1/2}}~\mathrm{where}~E_{min}~\simeq~3k_B T\left( \frac{5\lambda}{L} \right)^4
\end{equation}
%%%%%%

\noindent where $\lambda~=~(k_B T)^{2}/2Kn$ is the collisional mean free path of the injected electrons. The half loop length L, temperature T and number density n are the physical parameters associated with the coronal loops, through which the electrons are injected. This is known as the "warm target model". Although this model still features a low energy cutoff to the injected electron spectrum, the cutoff is now not ad hoc, and determined by the collisional parameters of the electrons through the coronal loops which in turn are determined by the physical thermal properties of the coronal loops. While the warm target model attempts to explain the physical significance of the low energy cutoff, the use of a $\kappa$-distribution injection of electrons has also proven to be very promising. The $\kappa$-distribution is regularly used to model the electron spectrum in in-situ observations and magnetic reconnection events in the Earth atmosphere \citep{maksimovic05, imada11}.

Close to the low energy cut off usually it is expected that Langmuir waves will be generated and grow\citep{emslie84, hannah09}. The interaction between the waves and the injected electron would flatten the energy energy distribution around the low energy cut off. To reflect this various studies \citep{kasparova09, bataglia15, effenberger17} have used the Kappa distribution, consisting of a Maxwellian core and smoothly merged power-law tail, along with a prominent thermal component to fit the observed X-ray spectrum. Apart from not requiring an arbitrary low-energy cutoff $E_c$, the kappa distribution can provide crucial information on the finer details of the electron acceleration, including the physical conditions of the chromosphere ({\it e.g.} wave-particle interaction, beam-plasma interaction etc.) responsible for the origin of it. \cite{bian14, arnold21} demonstrated that, in presence of Coulomb collisions and velocity diffusion the stochastic acceleration of electrons during solar flares can result in $\kappa$-distribution. In addition, as the $\kappa$-distribution covers the complete energy spectrum and is well behaved throughout, it can provide information about the electrons at a very low energies, which is not sensitive to exchange instruments but can be observed via diagnostics from EUV observations.

\cite{bian14} derived the $\kappa$-distribution as a result of stochastic acceleration in collisional plasma as

%%%%%%
\begin{equation}\label{e5}
    f_k(v)~=~\frac{n_k}{\pi^{3/2}v_{te}^{3}\kappa^{3/2}}\frac{\Gamma(\kappa)}{\Gamma(\kappa-\frac{3}{2})}\left(1+\frac{v^{2}}{\kappa v_{te}^{2}}\right)^{-\kappa}
\end{equation}
%%%%%%
\noindent where $\kappa~=~\tau_{acc}/2\tau_{c}$ is the kappa index, the ratio of acceleration and collisional decelerations time scale, $v_{te}$ is the thermal speed ($\frac{1}{2}m_ev_{te}^{2}~=~k_{B}T_{\kappa}$). The injected electron rate spectrum and the velocity distribution of the injected electron is given by, $\dot{N}(E)~dE~=~Avf_{k}(v)~d^{3}v$, where A is the injection area. For an isotropic electron distribution ($d^{3}v~=~4\pi v^{2}dv$), plugging in eqn.~\ref{e5} we get:

%%%%%
\begin{equation}\label{e6}
    \dot{N}(E)~=~A\sqrt{\frac{8}{\pi m_{e}k_{B}T_{\kappa}}}\frac{n_k \Gamma(\kappa)}{\Gamma(\kappa-\frac{3}{2})}\frac{E/k_{B}T_{\kappa}}{(1+E/\kappa k_{B}T_{\kappa})^{\kappa}}
\end{equation}
%%%%%

\noindent where $n_{k}[cm^{-3}]~=~\int f_{k}(v)~d^{3}v$ is the total electron number density. So, the total electron injection rate is given by

%%%%%
\begin{equation}\label{e7}
    \dot{N_{0}}~=~\int_{0}^{\infty}\dot{N}(E)~dE~=~2An_k\sqrt{\frac{2k_{B}T_{\kappa}}{m_e}}\frac{\kappa^{1/2}}{(\kappa-2)B(\kappa-3/2,1/2)}
\end{equation}
%%%%%

\noindent pluggin eqn.~\ref{e7} back into eqn.~\ref{e6} we get,

%%%%
\begin{equation}
    \dot{N}(E)~=~\frac{\dot{N_0}}{k_{B}T_{\kappa}}\frac{(\kappa-1)(\kappa-2)}{\kappa^2}\frac{E/k_{B}T_{\kappa}}{(1+E/\kappa k_{B}T_{\kappa})^{\kappa}}
\end{equation}
%%%%

\noindent the associated total power in the electrons is given by,

%%%%%%
\begin{equation}
    P~=~\int_0^{\infty}E_{0}N(E_{0})~dE_{0}~=~\frac{2\dot{N_{0}}k_BT_{\kappa}\kappa}{\kappa-3}
\end{equation}
%%%%%%

%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[trim={0.3cm 4cm 0.2cm 0.2cm}, clip, width=0.95\linewidth]{Figures/fit_kappa.pdf}
    \caption{Top panel: STIX spectra integrated between 15:27:00{--}15:27:10~UT during impulsive phase, fitted with `\textit{thcik\_warm\_kappa}' (solid yellow), `\textit{vth}' (solid green) and the complete fit function `\textit{vth+thick\_warm\_kappa}' (solid red line). Bottom panel: The residue of the fit of the STIX spectra.}
    \label{fig:fit_kappa}
\end{figure}
%%%%%%%%%%

We fit the STIX spectra in the same time window as shown in Fig.~\ref{fig:stix_an} with a {\it vth+thick\_warm} and {\it vth+thick\_warm\_kappa} model to compare the two models. We show the {\it vth} (solid green) + {\it warm kappa} electron injection model (solid yellow) fit in Fig.~\ref{fig:fit_kappa} top panel. Fig.~\ref{fig:fit_kappa} lower panel shows the normalized residual of the fit. In Tab.~\ref{tab:my_label} we list the relevant fit parameters from the two respective models. We show the inferred electron injection rate as a function of the electron energy for the {\it warm target+ power law-electron} injection (solid blue) and {\it warm target+ $\kappa$-electron} injection (dashed red) in Fig.~\ref{fig:e-injection} from the fit parameters listed in Tab.~\ref{tab:my_label} for the two distinct electron models. The key thing to notice is the very similar behavior of the models at the higher energy end. The power law injection model goes to 0 very abruptly at the lower energy cutoff ($E_c$), while the kappa distributed electrons slowly taper off at the lower energy end, providing a more physical picture of the injected electron spectra.

%%%%%%%%%%%
\begin{table}[ht!]
    \centering
    \resizebox{0.6\textwidth}{!}{%
    \begin{tabular}{||lcc||}
    \hline
        Parameters & {\it vth+thick\_warm\_kappa} & {\it vth+thick\_warm}\\
    \hline
     & &  \\
       EM[$10^{49}~cm^{-3}$] & 0.078 & 0.078\\
        &  &   \\
       $k_{B}T[keV]$ & 1.30 & 1.30\\
        & &  \\
       $\dot{N_0}[10^{35}~e^{-1}.s^{-1}]$ & 1.17 & 1.89\\
        & &  \\
        $\delta$ & NA & 3.21 \\
         & &  \\
        $\kappa$ & 5.42 & NA \\
         & &  \\
         $E_c$ & NA & .76\\
          & &  \\
        $k_{B}T_{\kappa}$ & 2.57 & NA \\
         & & \\

    \hline
    \end{tabular}}
    \caption{Comparison of various model parameters between "{\it vth+thick2}", "{\it vth+thick\_warm}" and "{\it vth+thick\_warm\_kappa}" model for the same time window of STIX spectra as shown in Fig.~\ref{fig:stix_an}.}
    \label{tab:my_label}
\end{table}
%%%%%%%%%%%

%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth, trim={0cm 0cm 1cm 1cm}, clip]{Figures/e_ij.pdf}
    \caption{Inferred electron injection rate as a function of energy for power law electron injection (solid blue) and $\kappa$-distributed electron injection (dashed red) from the fit parameters listed in Tab.~\ref{tab:my_label}.}
    \label{fig:e-injection}
\end{figure}
%%%%%%

### 2025-04-11 Outlook/ms.tex
Local changes

\justifying

This thesis addressed several questions regarding solar flares and their effects on the local plasma environment. We also describe multiple initial preparatory analyses we carried out for the design and calibration for {\suit}. We first describe the analysis we carried out with the simulated spacecraft jitter data provided by the ISRO URSC team to quantify the RMS jitter as a function of exposure time. Following this, we describe the throughput model of {\suit}, and using the model, how we carry out the photometric and spectral validation of the payload in the lab. We also describe how this method was used to choose the science filters to be mounted on {\suit}. Subsequently, we describe the on-orbit stellar calibration plan of {\suit} using Sirius-A as a calibration source yet to be carried out. We then describe the forward model pipeline we set up to create mock {\suit} observations to characterize the imaging performance and the effects of the instrument PSF on the imaging. Following this, we use IRIS \ion{Mg}{2} data to investigate the effects of Solar flares on the local plasma environment. We describe how similar observations can be used to regularly monitor the similar effects from {\suit} NB3 and NB4 observations. We then move on to estimating thermal energies in two solar flares. We use DEM analysis with AIA, XRT and SUVI data to estimate the thermal energy of these flares as a function of time. We describe a method to use stereoscopic observations from AIA and {\it STEREO-A} data to accurately determine the flare arcade volume as a function of time. Finally, we describe the first flares observed by {\suit}. The main results of this thesis can be summarised as follows:

%%%%%%%%%%%%%%%%%%%
\begin{enumerate}
    \item The {\suit} payload has two main moving components {\it i.e.}, the shutter door and the filter wheel. We used a Fourier filtering method to isolate the movement with timescale $<$ 2 ms. 2 ms is relevant as that is the maximum permissible exposure time for {\suit}. We find that the RMS and average jitter in the worst possible case {\it i.e.}, when both shutter and FW are moving without any compensation is an order of magnitude smaller than 0.7{\arcsec}, the pixel size of {\suit}. So. it is safe to assume that the jitter would not affect the {\suit} imaging. 
    \item  We use the throughput model to describe how the photometric and spectral validation was carried out on ground, and how the science filters to be mounted on the payload were chosen. Our findings show that the measured data counts per second generally agree within a 20\% margin with those predicted by the throughput model (as detailed in Tab.~\ref{tab:throughput})), with the exception of NB07. A potential cause for this discrepancy is the use of SOLSPEC data for modeling throughput beyond 310 nm, while SOLSTICE data is used for wavelengths below this threshold. It is important to note that SOLSPEC data has a resolution of 0.05 nm, whereas SOLSTICE data offers a finer resolution of 0.025 nm. As a result, the lower resolution of SOLSPEC data reduces the accuracy of the modeled data counts for filters operating beyond 310 nm.

    \item We present the spectral validation results for all filter combinations with transmission bandpasses above 250 nm in Fig.~\ref{fig:sepc_calib}. In this figure, the x and y error bars represent the wavelength bins corresponding to the input slit size and the Poisson uncertainty of the measured ADC counts, respectively. The plots indicate that the measured shape of the instrument's spectral response closely matches the modeled spectral response for all filter combinations with transmission bandpasses above 250 nm.

    The spectral characterization for the NB08 filter could not be completed due to strong ghost reflections near the central patch. These reflections are caused by the absence of a relative tilt between the two stacked filters that create the NB08 bandpass, unlike other filters. As a result, the ghost reflections interfere with the estimation of ensquared energy across the transmission bandpass, compromising the spectral validation for this filter.

    \item We present the forward modelling pipeline setup which would enable us to create mock {\suit} observations from existing MHD simulations using the measured optical response of various components. This can be beneficial in constraining various model parameters by comparing the mock observations with real observations from {\suit}. Using the setup, existing observations from IRIS and measured PSFs we present the imaging performance of {\suit} discussing how various features are observed via {\suit}. We also present the initial deconvolution algorithm designed for deconvolving {\suit} observations and how it restores the observations.

    \item The ratios of \ion{Mg}{2} h and k ratios change during the evolution of flares. Limited by the single flares of C, M and X-class flare we observed, we see significant change only in the M and C class flare. The ratio increases at the onset of the flare, reaching the peak at the impulsive phase and sharply declining afterwards dropping below the pre-flare levels in the decay phase. The variation can be explained by localized heating and chromospheric evaporation in the impulsive phase, and condensation and down flow in decay phase. However this is speculative as we did not see the effects in X-class flare. Our findings indicate that the \ion{Mg}{2} k to h line intensity ratios fluctuate during flares. As shown in Figs. \ref{fig:optical_dep_ev_m},\ref{fig:align_raster_flare2} (right panel), and \ref{fig:optical_dep_ev_c}, the line intensity ratios remain consistent across varying magnetic field strengths, from weak to strong. This consistency suggests that the magnetic field influences both the Mg II k and h lines similarly, causing these effects to cancel out when the ratios are calculated.

    \item The estimation of thermal energy in solar flares depends significantly on the volume estimation. There were existing studies \citep{hilarie05} which already eluded the same. We propose a method with existing tools using stereoscopic observations from AIA and {\it STEREO-A}, to estimate the volume of the flaring arcade as a function of time. This demonstrates that the uncertainty in the volume estimation can lead to significantly overestimate the thermal output of the flare in the impulsive phase and the peak of the flare. Our method of estimating the thermal energy from imaging observations using DEM analysis also enables us to quantify the thermal output of various parts of the flares {\it e.g.} flare arcade, fan etc. separately. Using this, we showed that the fan of the limb event $\mathrm{29^{th}~November}$, 2020 was cooling at a different rate compared to the loops. This indicates that a distinct heating mechanism is at play in the fan which different from the loops, as described in various other studies (e.g. SADs \citep{reeves17}, plasma flow turbulence \citep{xie23}) via different methods.

    \item The first flare observations from {\suit} give us chromospheric diagnostics in various chromospheric and transition region lines. In this thesis, we discuss {\suit} observations of two limb flares and an on-disk flare. The results can be summarised as follows:
    %%%%%%%%%%%
    \begin{itemize}[label=\ding{226}]
        \item {\bf 22 Feb, 2024:} The on-disk flare shows umbral bright flare kernels in NB2 (blue wing of \ion{Mg}{2} window) and NB5 (red wing of \ion{Mg}{2} window). The flare brightening is co-temporal with HXR from STIX observations in NB3 (\ion{Mg}{2} k), NB4 (\ion{Mg}{2} h), and NB8 (\ion{Ca}{2} h). The bright kernels peak in intensity slightly later compared to the transition region lines {\it i.e.} \ion{Mg}{2} k \& h, \ion{Ca}{2} h. We also analyse the XSM spectra to find an excess in the Fe $\sim$ 6.5 keV complex. This excess can not be explained by multi-thermal plasma and satellite lines unaccounted in the fitting \citep{mithun22}. We also find that the excess component peaks in-between the SXR and HXR and corelates well with the SXR flux $>$ 7.12 keV.

        \cite{kowalski19} observed umbral brightening kernels from another X-class flare. The {\it IRIS} raster scans in the 2832 {\AA} window revealed that the brightening was arising due to several \ion{Fe}{2} lines, which is usually in absorption, going into emission. They attributed photospheric heating as the reason for this. Similar observations of photospheric metallic lines going into emission was made by \cite{heinzel14,kleint17}. Due to the co-temporal nature of the NB2 and NB5 brightening with the Fe excess observed in XSM eludes that both of these are driven by the same process. The HXR flux from peak happens earlier, implying that the origin of umbral brightening kernels are not driven by the electron and/or ion beams from the coronal reconnection site. The co-temporal nature of the $>$ 7.12 keV SXR flux implies that this is what drives the formation of the umbral bright kernels as well as the excess in the Fe line observed by XSM. Fe K$\alpha$ fluorescence emission has been reported to exhibit similar characteristics as the excess observed by XSM \citep{doscheck71,tanaka84,phillips12,parmar84}. We believe this is direct observational evidence at photospheric heights, lower than the chromospheric condensation which was suspected to be the source of photospheric heating in \citep{kowalski19}. The flaring soft X-ray $>$ 7.12 keV photoionizes the ambient Fe present at photospheric heights, giving rise to plethora of \ion{Fe}{2} lines resulting in several electronic transitions between various vacated atomic levels. This gives rise to the characteristic K$\alpha$ emission excess observed. This provides us with important metallic lines arising from photospheric heights that can be important diagnostic for characterising solar flare models.

        \item {\bf 31 Dec, 2023:} The X5 flare exhibited an off-limb ejection in NB4 (\ion{Mg}{2} h) which was also observed in multiple AIA channels. We found that the ejecta observed in NB4 was cospatial with the structure observed in AIA 1600 {\AA} and 171 {\AA}. From DEM analysis we find that this region is part of an ejected loop that is denser and cooler compared to the rest of the structure. This might be a line of sight effect. This material is then ejected accelerating as it travels radially outwards. We find that the velocities calculated from AIA 1600 {\AA} and {\suit} NB4 observations are consistent with each other. From AIA 1600 {\AA} observations and STIX HXR light curves, we find that the accelerated ejection of the material is consistent with secondary reconnection at coronal altitudes and multiple ejection from the same active region.

        \item {\bf 27 May, 2024:} The X2.9 flare was accompanied by a large prominence ejection followed by the rising flare arcades. The flare arcades have a cusp shape which are usually observed in homologous flares. For this flare we see post flare loops clearly in NB3, NB4 and NB8. Interestingly the loops are brighter in these lines just below the fan. From DEM analysis this region appears denser and cooler compared to the rest of the post flare loops. We find that a prominence was present in between the flare , which erupted launching colder material into the loops. Thus the loops appear brighter in the Mg and Ca lines. 
    \end{itemize}
    %%%%%%%%%%%

\end{enumerate}
%%%%%%%%%%%%%%%%%%%

The overarching progression of this thesis, starts from various preparatory analysis carried out for {\suit}. These studies helped us in realising several aspects of {\suit} in timely manner. Then we describe a mock observation pipeline setup for {\suit} observations which would allow us existing simulations with observations. Then the thesis delves into various flare observations, from existing observatories in anticipation of {\suit}, and later on, after successful launch and L1 insertion, observations from {\suit} which gives us unique perspective into solar flares and their effects in transition region and beyond. The results of this thesis raises various pressing questions,

\noindent
{\bf Why was changes in \ion{Mg}{2} k to h line intensity ratio not observed in the X-class flare?} We observed the correlated change in the M and C class flare, which can be explained via localised heating evaporation in preflare phase and condensation in the decay phase. But this still needs to be verified with a larger sample of flares. The few X-class flares we have observed with {\suit} show the correlated changes in NB3 (\ion{Mg}{2} k) and NB4 (\ion{Mg}{2} h) line intensity ratio. This raises two distinct possibilities:

    %%%%%%%%%%%
    \begin{itemize}[label=\ding{226}]
        \item There is a possibility that the change was not observed for the X class flare, simply due to the cadence limitations of IRIS raster scan, along with which regions of the flare arcade is being scanned by IRIS because it is well known that the \ion{Mg}{2} profiles vary significantly in shape and spatially within the flaring region \citep{panos18,dalda23}.
        \item The other, more interesting possibility is that in some of the events depending on the "impulsiveness" of the event, there might be different degrees of ionisation at play at the chromosphere. This also might indicate a different energy release mechanism during the preflare and impulsive phase.
        \item One of the crucial tools in this regard would be finding correlations between {\it IRIS} and {\suit} observations. {\it IRIS} has been taking regular planned observations for {\suit} in QS and AR. One of the studies we will conduct immediately, is correlate {\it IRIS} intensities with {\suit} counts using these observations. As highlighted in \cite{roy24}, the {\it IRIS} intensities can be used to probe the local optical depth in the Mg lines. The correlation would immediately allow us to comment on the full-disk \ion{Mg}{2} k to h line intensity ratio continuously across various features using {\suit} observations.
    \end{itemize}
    %%%%%%%%%%%

Irrespective of the scenario further statistical analysis with larger sample size with flares of various "{\it GOES}" class would be beneficial in disentangling between these two scenarios.

\noindent
{\bf How important are high resolution imaging from different vantages?} The importance of accurate volume estimation in estimating the thermal energy is reiterated several times throughout this thesis. The indications of the importance has been demonstrated several times in various other studies \citep{hilarie05,warmuth20}. We demonstrated that the discrepancies arising due to the uncertainties in volume estimation are more important during the impulsive phase and thermal peak of the flares, as the most dynamic changes in the flaring plasma volume happens in the impulsive phase. We overestimate the thermal energy in the impulsive phase and the peak of the flare due to overestimation in volume. In the decay phase, after achieving the mechanical equilibrium the volume changes considerably slower compared to impulsive phase. This also raises a puzzling question regrading flare energetics. It has been demonstrated in various studies \citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17} that although there seems to be enough energy deposited by non-thermal particles to power the thermal components for bigger flares {\it e.g.} M-class and higher, the same can not be said for a lot of smaller flares. This raised a discussion around a secondary energy source to power the thermal component, which is small enough to be inconsequential in bigger flares compared to non-thermal component, but starts to become noticeable for smaller flares. {\bf The question our results raise is, how reliable are our thermal energy estimates used in various statistical studies if we consistently overestimate it in the impulsive phase and at the peak of flares?} The differences between the thermal and non-thermal component can be an overestimate due to the overestimation of the thermal energy. We need rigorous statistical studies with flares of various classes with accurate volume estimation to study how the volume estimation effects the thermal energy estimates.

We proposed a stereoscopic method harnessing the advantage of observing the same structure from different vantages to estimate the volume as a function of time, accurately. While our method is described for EUV observations, a similar method in SXR has been described by \cite{ryan24} using {\it Hinode}/XRT and {\it SO}/STIX observations from different vantages to study the 3D evolution of the thermal loop-top source for a M3.9 flare. Currently this is only feasible in EUV with {\it STEREO-A}/EUI and {\it SO}/EUI.

As {\it SO} and {\it STREO-A} orbits the sun, the angle between the earth vantage and the vantage of these two observatories keep changing over time. This results in varying effectiveness in the triangulation. In ideal scenario, we would require different vantages which do not evolve over time with respect to the Earth vantage. It is possible to achieve that with high resolution observations from L4 and L5 in tandem with orbiting observatories {\it e.g., SO} and {\it STEREO-A}. The technological challenges of putting a fully fledged mission keeps increasing exponentially with increasing distance from Earth. Due to these challenges and exponentially increasing cost in navigating such missions, it would not be feasible to conduct L4/L5 mission with the sole purpose of geometric triangulation.

%%%%%%%%%%
    \begin{wrapfigure}{l}{0.4\textwidth}
    \centering
    \includegraphics[trim={2cm 7cm 2cm 5cm}, clip, width=0.35\textwidth]{l1_l4_l5.pdf}
    \caption[Coverage of the solar surface with observations from various vantages.]{The Plane of projection of sun as seen from different vantages: solid red (observed from earth/L1), dotted black (observed from L4) and black dot-dashed (observed from L5). Figure is not to scale.}
    \label{fig:l1_l4_l5}
    \end{wrapfigure}
%%%%%%%%%%

Nevertheless, there are other unique advantages of such missions. L5 missions provide us the opportunity of predicting geo-effective eruptive events from the sun as it would be observing the regions of the sun turning towards the Earth. {\it Vigil} \citep{vigil} is a mission by ESA which is going to be placed in L5 for this very specific purpose. On the other hand, missions placed at L4 would be observing events on sun which would be more likely to end up being geo-effective. Materials ejected from west limb are more likely to follow the Parker spiral and hit Earth. Missions at L4 have the capability to provide us with high resolution remote observations before, during and after such events. There are various proposals of L4 missions already in discussion \citep{cho23}. The final advantage of continual observations from Earth/L1, L5 and L4 is illustrated in Fig.~\ref{fig:l1_l4_l5}. The plane of projection of solar disk from various perspective are shown in solid red (observed from Earth/L1), dotted black (observed from L4) and dot-dashed black (observed from L5). These combined observations would allow us to cover a significant portions of the far side of the sun. Currently the far side can only be observed during the flyby of orbiters {\it e.g. SO}, {\it STEREO-A}. It is safe to assume that the demographic of future space based solar missions would largely be shaped by the eventual outcome of current Lagrange point missions planned and under consideration.

\noindent
{\bf Importance of current {\suit} flare observations and what are the future prospects?} {\suit} provides first full-disk solar imaging in all of the concerned pass bands. There are previous flare observations in some of the imaging channels {\it e.g.} NB3, NB4 and NB5 from {\it IRIS} and NB8 from {\it Hinode}/SOT, only in smaller spatial windows. One of the key disadvantage of smaller spatial windows is the possibility of missing events due to different pointing. {\suit}, equipped with its flare detection algorithm, has already observed several flares including various limb events. This provides us our first observation of off-limb flares in all these lines. A larger statistical study with such observations combined with EUV, SXR, HXR, H$\alpha$, and WL observations can provide us with more complete picture of how flare energy is deposited across various layers of the solar atmosphere.

### 2025-04-11 Outlook/outlook.tex
Local changes

This thesis addressed several questions regarding solar flares and their effects on the local plasma environment. We first estimate thermal energies in two solar flares. We use DEM analysis with AIA, XRT and SUVI data to estimate the thermal energy of these flares as a function of time. We describe a method to use stereoscopic observations from AIA and {\it STEREO-A} data to accurately determine the flare arcade volume as a function of time. We also describe multiple initial preparatory analyses we carried out for the design and calibration for {\suit}. We first describe the analysis we carried out with the simulated spacecraft jitter data provided by the ISRO URSC team to quantify the RMS jitter as a function of exposure time. Following this, we describe the throughput model of {\suit} and describe how this method was used to choose the science filters to be mounted on {\suit}. Subsequently, we describe the on-orbit stellar calibration plan of {\suit} using Sirius-A as a calibration source, which is yet to be carried out. We then describe the forward model pipeline we set up to create mock {\suit} observations to characterize the imaging performance and the effects of the instrument PSF on the imaging. Following this, we use IRIS \ion{Mg}{2} data to investigate the effects of Solar flares on the local plasma environment. We describe how similar observations can be used to regularly monitor the similar effects from {\suit} NB3 and NB4 observations. Finally, we describe two of the first flares observed by {\suit}. The main results of this thesis can be summarised as follows:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}
    \item The thermal energy estimation for solar flares can be significantly affected by the volume estimates of the flaring plasma in the impulsive phase. For the November 29, 2020, limb event, we also demonstrated directly from the calculated thermal energy that the fan was cooling down slower compared to the loops, indicating a different heating mechanism. This has already been alluded to in various existing studies \citep[e.g.,][]{xie23,reeves19,longcope11}.

    \item The measured PSF across various channels show $\sim~2\arcsec$ radius of 80\% FWHM for the PSF. This illustrates that the imaging from {\suit} would be able to resolve features $\sim~2\arcsec$ apart.

    \item The \ion{Mg}{2} k \& h line intensity ratios can be used to probe the effects of solar flares on the local plasma environment. We believe the correlated change in the line intensity ratio with the SXR light curve is a direct effect of localised heating and an increase in the local optical depth due to the down-flow from the flaring region.

    \item The off-limb plasma blob observed in the December 31st, 2023 event is chromospheric cold material ejected into the atmosphere via an eruption. The blob is then seen accelerated. The acceleration of the plasma blob coincides with the development of a kink on the overlying loop. The acceleration occurs due to ongoing bursty reconnection from the same active region, which erupts into a second flare.

    \item The on-disk flare observed on February 22nd 2024, exhibits penumbral bright kernels in the blue and red wings of \ion{Mg}{2} along with white light. Similar observations were made for a separate event by \cite{kowalski19}. These bright kernels originate due to several metallic lines going into emission in both wings. The red wing enhancement occurs predominantly due to several \ion{Fe}{2} lines. The local plasma at photospheric heights is photoionized by the $\ge$ 7.12 keV SXR, giving rise to the several \ion{Fe}{2} lines in the red wing of \ion{Mg}{2}. This also gives rise to several atomic transitions in the Fe atoms, giving rise to Fe line fluorescence which is observed via the XSM data. Our result proposes a separate possible mechanism that can give rise to penumbral bright kernels instead of previously suggested direct heating by the electron beam (refer to \cite{kowalski19} for further details).

\end{enumerate}  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

These results open up several pathways to explore and pressing questions to answer:

\noindent {\bf Why was changes in \ion{Mg}{2} k to h line intensity ratio not observed in the X-class flare?} We require further analysis with multiple flares of same classes to investigate why the changes in the line intensity ratio was not visible in the X-class flare. There are two distinct possibilities:

%%%%%%%%%%%
    \begin{itemize}[label=\ding{226}]
        \item It is possible that the change was not observed for the X class flare, simply due to the cadence limitations of IRIS raster scan, along with which regions of the flare arcade is being scanned by IRIS because it is well known that the \ion{Mg}{2} profiles vary significantly in shape and spatially within the flaring region \citep{panos18,dalda23}.
        \item The other, more interesting possibility is that in some of the events depending on the "impulsiveness" of the event, there might be different degrees of ionisation at play at the chromosphere. This also might indicate a different energy release mechanism during the preflare and impulsive phase.
        %\item One of the crucial tools in this regard would be finding correlations between {\it IRIS} and {\suit} observations. {\it IRIS} has been taking regular planned observations for {\suit} in QS and AR. One of the studies we will conduct immediately, is correlate {\it IRIS} intensities with {\suit} counts using these observations. As highlighted in \cite{roy24}, the {\it IRIS} intensities can be used to probe the local optical depth in the Mg lines. The correlation would immediately allow us to comment on the full-disk \ion{Mg}{2} k to h line intensity ratio continuously across various features using {\suit} observations.
    \end{itemize}
    %%%%%%%%%%%

\noindent {\bf Continuous full-disk observation of opacity using {\suit} NB3 and NB4 observations,} with the observations highlighted in \cite{roy24}. This provides us with continuous full-disk opacity diagnostic throughout the day, across various solar features and eruptive events, and study any possible correlated photospheric and/or coronal signatures.

%\noindent {\bf How important are high resolution imaging from different vantages?} Our results emphasizes the critical role of accurate volume estimation in determining the thermal energy of solar flares. Discrepancies in volume estimation, particularly during the impulsive phase and thermal peak, may lead to overestimation of thermal energy because rapid changes in plasma volume occur during these stages. In contrast, during the decay phase, the volume stabilizes, reducing errors in energy calculations. A key challenge previously discussed in \S\ref{sol_flr_energ} is the discrepancy in flare energetics: while larger flares (like M-class or above) hold sufficient energy in non-thermal particles to power thermal components, smaller flares often show a deficit, suggesting the necessity of a secondary energy source. The central question raised is the reliability of thermal energy estimates, especially if they are consistently overestimated during the impulsive and peak phases does that have a role to play in the discrepancy observed for the smaller flares? To address this, rigorous statistical studies across different flare classes with accurate volume measurements are needed to understand how volume estimation impacts thermal energy calculations, which in turn requires high resolution imaging of the flaring plasma from various vantages, to harness the stereoscopic method discussed in chapter \ref{c:chap3}. While our method is described for EUV observations, a similar method in SXR has been described by \cite{ryan24} using {\it Hinode}/XRT and {\it SO}/STIX observations from different vantages to study the 3D evolution of the thermal loop-top source for a M3.9 flare. Currently this is only feasible in EUV with {\it STEREO-A}/EUI and {\it SO}/EUI.

\noindent
{\bf How important are high resolution imaging from different vantages?} Our results emphasize the critical role of accurate volume estimation in determining the thermal energy of solar flares. Discrepancies in volume estimation, particularly during the impulsive phase and thermal peak, may lead to overestimation of thermal energy because rapid changes in plasma volume occur during these stages. In contrast, during the decay phase, the volume stabilizes. A key challenge previously discussed in \S\ref{sol_flr_energ} is the discrepancy in flare energetics: while larger flares (like M-class or above) hold sufficient energy in non-thermal particles to power thermal components, smaller flares often show a deficit, suggesting the necessity of a secondary energy source. The central question raised is the reliability of thermal energy estimates, especially if they are consistently overestimated during the impulsive and peak phases—does this contribute to the discrepancy observed in smaller flares? To address this, rigorous statistical studies across different flare classes with accurate volume measurements are needed to understand how volume estimation impacts thermal energy calculations. This, in turn, requires high-resolution imaging of the flaring plasma from various vantages, to harness the stereoscopic method discussed in Chapter~\ref{c:chap3}. While our method is described for EUV observations, a similar method in SXR has been outlined by \cite{ryan24}, using \textit{Hinode}/XRT and \textit{SO}/STIX observations from different vantages to study the 3D evolution of the thermal loop-top source for an M3.9 flare. Currently, this is only feasible in EUV with \textit{STEREO-A}/EUI and \textit{SO}/EUI.

\noindent
{\bf Importance of current {\suit} flare observations and what are the future prospects?} {\suit} provides first full-disk solar imaging in all of the concerned pass bands. There are previous flare observations in some of the imaging channels {\it e.g.} NB3, NB4 and NB5 from {\it IRIS} and NB8 from {\it Hinode}/SOT, only in smaller spatial windows. One of the key disadvantage of smaller spatial windows is the possibility of missing events due to different pointing. {\suit}, equipped with its flare detection algorithm, has already observed several flares including various limb events. This provides us our first observation of off-limb flares in all these lines. A larger statistical study with such observations combined with EUV, SXR, HXR, H$\alpha$, and WL observations can provide us with more complete picture of how flare energy is deposited across various layers of the solar atmosphere.

### 2025-04-11 Outlook/outlook_2.tex
Local changes

\justifying
%XXXXXThis thesis addressed several questions regarding solar flares and their effects on the local plasma environment. We first estimate thermal energies in two solar flares. We use DEM analysis with AIA, XRT and SUVI data to estimate the thermal energy of these flares as a function of time. We describe a method to use stereoscopic observations from AIA and {\it STEREO-A} data to accurately determine the flare arcade volume as a function of time. We also describe multiple initial preparatory analyses we carried out for the design and calibration for {\suit}. We first describe the analysis we carried out with the simulated spacecraft jitter data provided by the ISRO URSC team to quantify the RMS jitter as a function of exposure time. Following this, we describe the throughput model of {\suit} and describe how this method was used to choose the science filters to be mounted on {\suit}. Subsequently, we describe the on-orbit stellar calibration plan of {\suit} using Sirius-A as a calibration source, which is yet to be carried out. We then describe the forward model pipeline we set up to create mock {\suit} observations to characterize the imaging performance and the effects of the instrument PSF on the imaging. Following this, we use IRIS \ion{Mg}{2} data to investigate the effects of Solar flares on the local plasma environment. We describe how similar observations can be used to regularly monitor the similar effects from {\suit} NB3 and NB4 observations. Finally, we describe two of the first flares observed by {\suit}. The main results of this thesis can be summarised as follows:

%\textbf{For the above paragraph -- just compress the three paragraph in the synopsis into one. Then say that we summarise the finding in this thesis below.}

%The below items has to be like abstract for each chapter...

Solar flares are the most powerful magnetic events in the solar system, characterized by sudden, localized brightening in the solar atmosphere. %These eruptions are triggered by magnetic reconnection, releasing vast amounts of energy in the form of radiation and energetic particles. Solar flares often produce large-scale disturbances, including filament or prominence eruptions, coronal mass ejections (CMEs), and wave phenomena such as Moreton waves and EUV waves. 
The energy released during a flare can affect space weather and disrupt systems such as satellite communications, GPS, power grids, etc., including serious risks to astronauts and spacecraft in orbit. Studying the underlying physics of solar flares helps us better predict these events and mitigate their impacts, which is critical for the safety of both space-based infrastructure and terrestrial technology. %Furthermore, solar flares offer a unique opportunity to study plasma physics processes, such as magnetic reconnection, which are central to solar physics, astrophysics, and even fusion research. 
The extensive observations of flares, especially in soft X-ray, hard X-ray, and EUV wavelengths, we have developed a tremendous understanding of the physical processes at work in flares. However, numerous important questions about the origin and evolution of thermal and non-thermal energies in solar flares, their spectral distribution, and the precise mechanisms behind flare initiation remain.

The primary aim of this thesis is to perform a multi-wavelength study of solar flares using existing observations and also contribute towards the development of the new observing facility, the Solar Ultraviolet Imaging Telescope (SUIT) onboard Aditya-L1 that provides crucial data for flare studies. The thesis is structured in two parts. In the first part, we address some of these questions by analyzing the temporal evolution of thermal and non-thermal energies in solar flares using EUV and X-ray data from multiple vantage points. In the second part, we conduct preparatory studies for SUIT that include modeling the instrument's performance, assessing spacecraft jitter profiles, establishing calibration methods using stellar observations, and forward modeling of mock SUIT observations. Below, we provide a detailed summary of the work and results that were obtained. %  In preparation for SUIT operations, we also analyze spectral observations in the near-ultraviolet range and initial flare observations, setting a foundation for future flare studies with SUIT. Finally, we highlight and discuss some of the first flare observations carried out with {\suit} and its implications on our understanding of solar flares. The main results of this thesis can be summarized as follows:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}

    \item The partition between the thermal and the non-thermal energies in solar flares informs us about the relevant physical process taking place during the evolution of the flare. As discussed in \S\ref{sol_flr_energ}, several statistical studies of solar flare energetics \cite[e.g.,][]{warmuth16a, warmuth16b, stosire07, emslie12, inglis14, ash17} have reported on the partition between the thermal and non-thermal energies of the flares. It can be inferred that for bigger flares (e.g., M and X class), there is enough non-thermal energy in electrons to power the thermal radiation. In comparison, there seems to be a deficit in the non-thermal component for the smaller flares. This prompted speculation about a third energy source that could account for the deficit of energy needed to power the thermal component in smaller flares. One of the key similarities of all of these studies was the use of peak thermal energy as the representative of the total thermal energy of the flares. While that is a fair representation of the overall thermal energy budget of an event, it can miss several intricacies throughout the evolution of the flare. In this thesis, we study two flares, one on disk and the other off-limb. We use AIA and XRT observations to compute DEMs and infer the thermal properties of the flaring plasma. We use observations from AIA and EUVI, from a different vantage,  to triangulate the LoS through the flaring plasma. We find that the thermal energy estimation for solar flares can be significantly affected by the volume estimates of the flaring plasma in the impulsive phase. For the November 29, 2020, limb event, we also demonstrated directly from the calculated thermal energy that the cooling pattern of fans is different than the post-flare loops, thereby indicating a possibly different heating mechanism. A hint of such observations has already been alluded to in various existing studies \citep[e.g.,][]{xie23,reeves19,longcope11}.

    \item Estimating the imaging performance of {\suit} was one of the priorities to characterize and quantify the possible science cases. To this end, we designed a pipeline to create mock {\suit} observations using simulated MURaM cubes. We incorporated lab-measured PSF in the pipeline to create realistic mock observations.  The measured PSF across various channels show $\sim~2\arcsec$ radius of 80\% FWHM for the PSF. This illustrates that the imaging from {\suit} would be able to resolve features $\sim~2\arcsec$ apart with reliable photometric accuracy.

    \item The intensity ratios of the \ion{Mg}{2}~k~and~h lines can be used to probe the characteristics of the plasma in the {\bf lower} solar atmosphere {\bf in chromosphere and transition region heights}. To obtain the plasma characteristics in flaring regions, we study the variation of \ion{Mg}{2}~k~and~h intensity ratio for three areas belonging to X-class, M-class, and C-class throughout their evolution. For this purpose, we used existing IRIS observations combined with those from AIA, HMI and GOES X-ray light curves. We co-aligned IRIS 2796~{\AA} observations with those from HMI and obtained artificially rastered magnetic field maps corresponding to IRIS maps. This gives us the measure of the photospheric magnetic field for every pixel of the IRIS rasters. We use a double Gaussian function with a symmetric background about the line core to fit the \ion{Mg}{2} k and h lines. In scenarios where the Mg triplet lines are in emission, they are fitted with separate Gaussian functions. We find that the intensity ratios show significant changes during flares, i.e., it peaks minutes before the GOES SXR peak and falls even below the pre-flare level during the peak and decline phase of the flare. A comparison with photospheric magnetic flux density suggests that the change in ratio is independent of flux density. Given that the \ion{Mg}{2} k to h line intensity ratio is representative of the opacity of the local plasma environment, these results are important in the light of heating and cooling of localized plasma and provide further constraint on the understanding of flare physics.

    \item The several flares observed via {\suit} give us a new perspective on observing various eruptions and how they interact with the local plasma environment.  Here, we report the observation of the first flare X6.3 flare SOL2024-02-22T22:08:00 that was localized and observed with the eight narrow band (NB) filters of SUIT. We have also used the co-spatiotemporal observations from SDO/AIA, SolO/STIX and Global Oscillation Network Group (GONG) H$\alpha$ and GOES. We align and co-register SUIT observations with those from AIA 1600, 1700~{\AA} and GONG H$\alpha$ observations and construct light curves from the same regions on them. We compare these light curves with the full-disk integrated GOES SXR and STIX HXR (25{--}50~keV) light curves. We find that all of the SUIT NB1, NB3, NB4, NB8 filters peak simultaneously with HXR and 1600, 1700~{\AA}. In contrast, the NB3 and NB5 lines peak $\sim$~3 minutes later than the HXR peak. The flare peaks in NB6 and NB7 $\sim$~3 mintes after the GOES soft X-ray peak. To the best of our knowledge, this is the first observation of flare in these wavelengths (except in NB3, NB4 and NB5). Moreover, for the first time, we show the presence of bright kernel NB2. These results demonstrate the capabilities of SUIT observations in flare studies.

\end{enumerate}  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The results obtained in this thesis help us understand various puzzles of solar flares and provide a number of constraints on the modeling. Additionally, they open up several pathways to further explore the physics of flares. The observations from the SUIT instrument open up a new window for studying solar flares. Below we describe a few projects that naturally arise based on this study.

%%%%%%%%%%%
\begin{itemize}[label=\ding{226}]

\item Our results in Chap.~\ref{c:chap3} emphasize the critical role of accurate volume estimation in determining the thermal energy of solar flares. Discrepancies in volume estimation, particularly during the impulsive phase and thermal peak, may lead to overestimation of thermal energy because rapid changes in plasma volume occur during these stages. Therefore, we plan to automate the triangulation method to determine the LoS from earth vantage using observations from various instruments and conduct rigorous statistical studies across different flare classes to understand how volume estimation impacts thermal energy calculations.

%This, in turn, requires high-resolution imaging of the flaring plasma from various vantages to harness the stereoscopic method discussed in chap.~\ref{c:chap3}. While our method is described for EUV observations, a similar method in SXR has been outlined by \cite{ryan24}, using \textit{Hinode}/XRT and \textit{SO}/STIX observations from different vantages to study the 3D evolution of the thermal loop-top source for an M3.9 flare. Currently, this is only feasible in EUV with \textit{STEREO-A}/EUI and \textit{SO}/EUI.
         %\end{enumerate}

\item As alluded to in Chap.~\ref{c:chap6}, we did not observe the correlated change in line intensity rations for the X-class flare. It is possible that the change was not observed for the X class flare, simply due to the cadence limitations of IRIS raster scan, along with which regions of the flare arcade are being scanned by IRIS because it is well known that the \ion{Mg}{2} profiles vary significantly in shape and spatially within the flaring region \citep{panos18,dalda23}. The other and more interesting possibility is that in some of the events, depending on their "impulsiveness", there might be different degrees of ionization at play in the chromosphere. This may also indicate a different energy release mechanism during the pre-flare and impulsive phases of the flare.

\item {\suit} provides the first full-disk solar imaging in 11 filters in the wavelength range of 200{--}400~nm. There are previous flare observations in some of the imaging channels {\it, e.g.} NB3, NB4 and NB5 from {\it IRIS} and NB8 from {\it Hinode}/SOT, only in smaller spatial windows. %Therefore, SUIT observations open up a new window for flare studies. One of the key disadvantages of smaller spatial windows is the possibility of missing events due to different pointing. {\suit}, equipped with its flare detection algorithm, has already observed several flares, including various limb events. This provides us our first observation of off-limb flares in all these lines. A larger statistical study with such observations combined with EUV, SXR, HXR, H$\alpha$, and WL observations can provide a more complete picture of how flare energy is deposited across various layers of the solar atmosphere. We specifically want to explore the observation of the probable flare lines observed in the blue wing of \ion{Mg}{2} discussed in chap.~\ref{c:chap7}. We plan to use flare simulations, together with observations from IRIS and XSM when available to comment on the spectral nature and origin of the penumbral bright flare kernels.

    \end{itemize}
%%%%%%%%%%%

### 2025-04-11 abstract.tex
Local changes

@@
 \abstract{
+
 Solar flares are the largest magnetic eruptions in the Solar system.
 The enigmatic magnetic eruptions have been studied for over a century.
-The effects of flare in the lower solar Atmosphere {\it e.g.} Chromosphere and Photosphere are also very ill-understood.
-There is also a lack of full-disk resolved observation in continuum channels in the NUV regime.
-In addition to this, instead of the availability of plethora of solar observations, we still hardly understand various aspects of the flares.
-Various statistical studies exhibit our lack of understanding between the partition of thermal and non-thermal energy, the conversion mechanism.
-The {\suit} on-board Aditya-L1 by the Indian Space Research Organisation (ISRO), aims to fill the gap of full disk observation in the NUV regime, specifically in 200 {--} 400 nm.
-
-In this thesis we first describe the initial preparatory analysis carried out for {\suit}, including the throughput model, jitter estimation and its effect on imaging, the on ground spectral and photometric validation and the stellar calibration plan.
-We also use EUV, NUV, Soft and Hard X-ray spectroscopy and Full-disk integrated imaging to understand: (\romannum{1}) The effect of Solar flares on the surrounding plasma environment in Chromosphere, (\romannum{2}) The effect of volume estimation on the thermal energy budget of the Solar flare and the efficiency of the conversion from non-thermal to thermal energy.
-We propose a triangulation method using existing tools and observations from different vantages to estimate the volume of the arcade as a function of time.
-We also report the first flare observations from {\suit} and its implications on our understanding of flares moving forward.
+However, their complete spectral energy distribution is not yet derived.
+One of the main missing components is flare energetics in the photosphere and chromosphere.
+While there are many measurements of flare energetics in the extreme-ultraviolet (EUV), soft and hard X-rays, the measurements in other wavelength bands, especially in the near ultraviolet, are sparse.
+The Solar Ultraviolet Imaging Telescope ({\it SUIT}) on board Aditya-L1 by the Indian Space Research Organisation (ISRO) aims to fill the gap by observing the flares in the wavelength band 200 {--} 400 nm.
+Moreover, using the EUV and X-ray observations, there has been great progress in flare physics.
+However, there is a lack in our understanding of the evolution of thermal and non-thermal energy during the course of the evolution of flares and the partition between the thermal and non-thermal energy, including the conversion mechanism at play.
+This thesis is in two parts.
+In one part, we perform the initial preparatory analysis carried out for the {\it SUIT} instrument, including the throughput model, jitter estimation and its effect on imaging, the on-ground spectral and photometric validation, forward modelling of {\it SUIT} observations using the data obtained from realistic MHD simulations from MURaM, and the stellar calibration plan.
+We also carry out analysis with existing IRIS data in anticipation of SUIT, to comment on the effect of solar flares in the local environment.
+In the second part, we use the existing EUV and X-ray observations to study the thermal and non-thermal energy in solar flares and demonstrate the importance of volume estimation on the total thermal energy budget and, thereby, the efficiency of the conversion from non-thermal to thermal energy.
+We propose a triangulation method using existing tools and observations from different vantage points to estimate the volume of emitting plasma in flares as a function of time.
+Finally, we study two flares which are observed by SUIT in NUV combined with EUV, NUV, Soft and Hard X-ray spectroscopy and for the first time we discuss the flare observations and initial results in this broad wavelength coverage.
 

### 2025-04-11 acknowledge.tex
Local changes

\noindent
The journey of a PhD is like a marathon. There are times when you feel like sprinting down the lane, full of energy, driven by small successes, getting stuck on something for a while, and finally finding that "eureka" moment. Other times, you feel out of breath, barely dragging your legs along, just trying to stand. I believe what matters most are the connections you make with people who push you and help you during those difficult moments—because without them, I wouldn't be here writing this acknowledgment!

\noindent
First, I would like to thank Durgesh; this thesis would not have been possible without his guidance. He gave me enough freedom to explore whatever I wanted, offering valuable suggestions along the way but never giving "orders." More importantly, he carefully considered any differing viewpoints I raised from the first day. Without this freedom, I probably wouldn't be as proud of my growth over the past five years. Very few people get the opportunity to contribute to one of their country's first major observatory-class missions. I am especially grateful for the confidence he and Ram placed not only in me but also in several other young students while realizing SUIT. While I worked on the project for only five years, I also want to thank everyone who was part of it before me—without their hard work, I would not have been able to take over so easily.

\noindent
Next, I would like to thank Kathy. Just like Durgesh, she also allowed me the freedom to explore the problems I was given, nudging me in the right direction whenever I got stuck. I also want to thank Chris. His enthusiasm in answering my questions and our discussions on various topics were invaluable. Working at CfA was a remarkable experience. I am grateful to Kathy, Durgesh, the Smithsonian Institution, and CfA for making this possible. Experiencing the life of a graduate student in two very different systems gave me insight into both the challenges and advantages of each. Beyond being a scientific opportunity, it was a profound lesson in becoming an independent person not just a "scientist". Leaving your country and loved ones after twenty-six years to live alone, work, cook, and function as an independent adult in a foreign country is not easy. But those one-and-a-half years helped me mature quickly.

\noindent
Our memories of a place are deeply tied to the people and the experiences we share with them. I want to thank Tatiana and Chad specifically; I will forever cherish the fun we had in the chess club. Those library gatherings early on at CfA were something I looked forward to when I had not yet made many friends. Tatiana, you were a godsend! As someone who isn't very extroverted, you made it easy for me to open up to people at CfA. I also want to thank several people involved in the HSO-Connect project, with whom I had many fruitful academic and non-academic discussions: Sophie, Dana, Ritesh, Xiaoyan, Crisel, Dan, Sam, and Yeimy. Similarly, my time at IUCAA became equally memorable, thanks to many people—whether we were traveling, hiking, playing board games and football, cooking together, or organizing Diwali celebrations for two years in a row.

\noindent
In the early days, I spent a lot of time with Sunil and Sorabh playing FIFA in my room or on the pantry TV. It was a relief to know I wasn’t the only one "wasting" time on "silly video games"! Tathagata, Suprovo, Sorabh, Sunil, Somak Da, Sourabh, Suraj, Dhruv, we spent so much time playing board games I had not even known existed. Ankush, Partha, Biku, Kavita, and Meenakshi, our cooking sessions and hangouts were respites I looked forward to. A special shout out to the football gang {—-} Sunil, Sorabh, Somak Da, Sayak, and Soumil. Thanks to you all, we managed to follow football regularly, despite our busy schedules.

\noindent
I also thank the solar group and its wonderful members for both academic and non-academic discussions over the years: Nived, Vishal, Janmejoy, Megha, Sneha, Rushikesh, Rahul, Sreejith, Abhishek, Deepak, Sargam, and Avyarthana. Megha and Anirban felt like older siblings I could always approach when needed.

\noindent
A special shout-out to Nived! Although we didn't spend much time together, I had more scientific discussions with you than anyone else. I respected your opinions so much that I started running every crazy idea by you first. Your constant presence in my scientific journey has been invaluable.

\noindent
Special thanks to Lindsay Glesener. Many people never realize the impact they can have on others. During the 2023 SF AGU meeting, Chris took me with his group to Berkeley to see the FOXSI-4 assembled. At the time, I was at a low point, doubting my ability to succeed in academia and considering leaving after my PhD. Lindsay shared how, as a PhD student, she accidentally destroyed the CCD hours before the FOXSI-1 launch, delaying it. Despite that, she went on to become the PI of FOXSI-4. Her story rekindled my confidence. Lindsay, I may never tell you this in person, but however long I stay in academia, your story will remain a key source of inspiration.

\noindent
I am deeply grateful to my professors at Presidency University, Kolkata {--} Suchetana and Ritaban for their support during my bachelor’s and master’s programs. Without them, I might not have pursued a PhD in astronomy.

\noindent
This work would not have been possible without the support of my family and friends. I owe my career in physics to the enthusiasm and encouragement of my uncle, Maloy Kumar Roy, and my friend’s father, Ranjan Basak. My uncle Shyamal Kumar Ray has been a constant companion, whether watching football or movies together. Aloke Mitra has been a lifelong pillar of support. Sayan Chakraborty, who started as my teacher, gave me the coding skills that became invaluable during my PhD.

\noindent
Finally, I want to thank my parents. They gave me the freedom to explore whatever I wanted from a very early age. After high school, they supported my decision to pursue a career in basic science, even when friends and relatives were skeptical.

\noindent
This thesis would not have been possible without the open data policies of several instruments. I acknowledge the use of data from AIA, HMI, IRIS, XRT, STIX, Chandrayaan-2/XSM, Stereo-A, GOES/XRS, and GOES/SUVI. I also thank the SUIT and Pegasus servers at IUCAA for providing computational facilities.

### 2025-04-11 chapter2/chap2.tex
Local changes

--- 2024-08-14 chapter2/ms.tex
@@
 These instruments have empowered us with the ability to scrutinize the Sun with exceptional detail.
-Specifically, the space based observatories have added new avenues of observing sun.
-Large portions of the electromagnetic spectra is heavily by Earth's atmosphere \sr{Reference here}.
-
-The studies within this thesis are using solar observations are multi wavelength analysis of solar flares with both imaging and spectroscopy.
-In this chapter we describe the details of the instruments and techniques used for our analysis.
+Specifically, the space based observatories have added new avenues of observing the Sun.
+The studies within this thesis are performed using multi-wavelength imaging and spectroscopic observations of solar flares recorded from space.
+This chapter describes the details of the instruments and techniques used for our analysis.
 
@@
 
-The Solar Dynamics Observatory \citep[SDO;][]{sdo} is a NASA mission designed to understand the causes of solar variability at various spatio temporal and wavelength scales, as well as its impacts on Earth and the near-Earth environment.
+The Solar Dynamics Observatory \citep[SDO;][]{sdo} is a NASA mission designed to understand the causes of solar variability at various spatio-temporal and wavelength scales, as well as its impacts on Earth and the near-Earth environment.
 It is part of NASA’s Living With a Star program and houses multiple instruments onboard to address its numerous scientific goals.
-Among the numerous instruments on-board {\it SDO}, we have extensively used data from two instruments – the Atmospheric Imaging Assembly (AIA) and the Helioseismic and Magnetic Imager (HMI).
+Among the three instruments onboard {\it SDO}, we have extensively used data from two instruments – the Atmospheric Imaging Assembly (AIA) and the Helioseismic and Magnetic Imager (HMI).
 
@@
 
-AIA \citep{aia} obtains full-disk images of the solar transition region and corona at unprecedented spatio-temporal resolution.
+AIA \citep{aia} obtains full-disk images of the solar transition region and corona with 0.6{\arcsec} pixel size and 12s cadence in EUV channels and 24s cadence in UV channel.
 The field of view (FOV) covers up to 0.5 $\mathrm{R_{\odot}}$ above the limb.
-It incorporates several filters at 94 {\AA}, 131 {\AA}, 171 {\AA}, 193 {\AA}, 211 {\AA} and 335 {\AA}, mainly probing the Corona, along with filters at 304 {\AA}, 1600 {\AA}, 1700 {\AA}, and 4500 {\AA}, mainly observing the Chromosphere and Photosphere, providing a total temperature coverage range of 0.06 MK to 20 MK and across various heights.
-Figure 2.1 illustrates the temperature responses of these filters \citep{borner12}, derived based on the CHIANTI model for solar emissivity \citep{chianti,chianti1}.
+It incorporates several filters at 94~{\AA}, 131~{\AA}, 171~{\AA}, 193~{\AA}, 211~{\AA} and 335~{\AA}, mainly probing the corona, along with filters at 304 {\AA}, 1600 {\AA}, 1700 {\AA}, and 4500 {\AA}, mainly observing the chromosphere and photosphere, providing a temperature coverage range of 0.06 MK to 20 MK and across various heights.
 Under different conditions, these AIA filters observe different plasma phenomena \citep{o'dwyer10}.
@@
 Each AIA telescope is accompanied by its own guide telescope to ensure highly accurate image stabilization.
-For ous analysis, we have extensively used the coronal EUV channel observations from AIA, e.g.
+For our analysis, we have extensively used the coronal EUV channel observations from AIA, e.g.
 94 {\AA}, 131 {\AA}, 171 {\AA}, 193 {\AA}, 211 {\AA} and 335 {\AA}.
@@
 We have mainly used the LOS magnetogram for our analysis.
-These magnetograms have a 0.5{\arcsec} per pixel resolution and 45 s cadence.
+These magnetograms have a 0.5{\arcsec} pixel size and {45} s cadence.
 
@@
 IRIS contains a spectrograph and a slit-jaw imager (SJI), observing the chromosphere, the transition region, and the lower corona.
-It primarily observes the Sun in two pass bands around 1400 {\AA} and 2800 {\AA}.
-IRIS provides data at high spatial resolution (0.33 {\arcsec} in FUV and 0.4 {\arcsec} in NUV), high time cadence (up to 1 second), and high spectral resolution (12 or 25 m{\AA} per pixel).
+It primarily observes the Sun in two pass bands around 1400~{\AA} and 2800~{\AA}.
+IRIS provides data at high spatial resolution (0.33 {\arcsec} in FUV and 0.4 {\arcsec} in NUV), high time cadence (up to 1 second), and high spectral resolution (12 or 25 m{\AA}).
 
-IRIS observes three wavelength bands: two in the Far Ultraviolet (FUV) range, spanning 1331.7–1358.4 {\AA} and 1389.0–1407.0 {\AA}, and one in the Near Ultraviolet (NUV) range, covering 2782.7–2851.1 {\AA}.
+IRIS observes three wavelength bands: two in the Far Ultraviolet (FUV) range, spanning 1331.7{--}1358.4~{\AA} and 1389{--}1407~{\AA}, and one in the Near Ultraviolet (NUV) range, covering 2782.7{--}2851.1~{\AA}.
 IRIS measures spectra through two primary modes: raster and sit-and-stare.
@@
 This mode is referred to as sit-and-stare.
-In our analysis, we have used both spectra and SJI imaging from the \ion{Mg}{2} h \& k window and SJI imaging from the \ion{Si}{4} 1402 {\AA} window.
+In our analysis, we have used both spectra and SJI imaging from the \ion{Mg}{2} h~\&~k window and SJI imaging from the \ion{Si}{4} 1402~{\AA} window.
 
@@
 
-Solar Orbiter \citep[SO;][]{so} is a joint mission between the European Space Agency (ESA) and NASA, launched in February 2020 with the goal of studying the Sun and its dynamic behaviour.
-The spacecraft aims to provide unprecedented observations of the Sun's polar regions and the inner heliosphere, offering new insights into solar phenomena such as solar wind, coronal mass ejections, and the Sun's magnetic field.
-We have used observations from the Spectrometer/Telescope for Imaging X-rays (STIX) instrument for our analysis.
-
- STIX \citep{stix,stix1} is designed to study the Sun's X-ray emissions, providing crucial insights into the processes driving solar flares and other high-energy phenomena.
+Solar Orbiter \citep[SO;][]{so} is a joint mission between the European Space Agency (ESA) and NASA, launched in February 2020.
+The Spectrometer/Telescope for Imaging X-rays (STIX) \citep[STIX,][]{stix,stix1} is designed to study the Sun's X-ray emissions, providing crucial insights into solar flares and other high-energy phenomena.
 STIX incorporates a set of collimators and detectors to capture high-resolution images of the Sun in X-rays.
-These images allow scientists to pinpoint the locations and intensities of X-ray emissions associated with solar flares.
-The instrument covers a broad range of X-ray energies, from approximately 4 to 150 keV, enabling it to observe various aspects of solar activity.
-STIX can capture X-ray data with high temporal resolution, allowing scientists to study the rapid evolution of solar flares and other transient events in detail.
-STIX works together with other instruments onboard Solar Orbiter, providing complementary measurements to enhance our understanding of the Sun's dynamic behaviour across different wavelengths and energy ranges.
+These images allow us to pinpoint the locations and intensities of X-ray emissions associated with solar flares.
+The instrument covers a broad range of X-ray energies, from approximately 4 to 150 keV, probing both thermal and non-thermal X-rays.
+STIX provides X-ray imaging with a spatial resolution $\sim$ 7 {\arcsec} at the shortest wavelengths using Fourier imaging techniques.
+Notably, the spatial resolution depends on the visibilities at various energies.
+STIX can operate at a temporal cadence as high as 0.1 s.
+The cadence of observation is adjustable depending on the flaring activity.
+The instrument operates in two data modes: the low-resolution background monitoring mode in quiet conditions and the high-resolution mode activated during solar flares.
+STIX works together with other instruments onboard the Solar Orbiter, providing complementary measurements to enhance our understanding of the Sun's dynamic behaviour across different wavelengths and energy ranges.
 
@@
 {\it STEREO-A} and its twin spacecraft {\it STEREO-B} (Behind) were designed to provide stereoscopic views of the Sun, enabling three-dimensional observations of solar phenomena such as coronal mass ejections (CMEs) and solar flares.
-Extreme Ultraviolet Imager \citep[{\it EUVI};][]{euvi} is one of the key instruments onboard the {\it STEREO-A} spacecraft.
-{\it EUVI} is designed to capture images of the Sun in the extreme ultraviolet (EUV) wavelength range.
+Extreme Ultraviolet Imager \citep[EUVI;][]{euvi} is one of the key instruments onboard the {\it STEREO-A} spacecraft.
+EUVI is designed to capture images of the Sun in the extreme ultraviolet (EUV) wavelength range.
 This range of wavelengths is particularly useful for studying the Sun's outer atmosphere, known as the corona, and observing features such as solar flares, coronal loops, and coronal holes.
 
-{\it EUVI} can capture high-resolution images of the Sun's corona, with spatial resolutions in order of a few arcseconds.
-It can observe the Sun in 171 {\AA}, 195 {\AA}, 284 {\AA} and 304 {\AA} simultaneously.
-{\it EUVI} provides continuous observations of the Sun from the STEREO-A spacecraft's vantage point, located slightly ahead of Earth in its orbit around the Sun.
-This allows {\it EUVI} to monitor solar activity over extended periods and to track the evolution of solar features such as sunspots, flares, and coronal mass ejections (CMEs).
-We have used 171 {\AA} and 195 {\AA} observations from EUVI for our analysis.
+EUVI can capture high-resolution images of the Sun's corona, with spatial resolutions in order of a few arcseconds when the respective spacecraft is at the perihelion.
+It observes the Sun in 171~{\AA}, 195~{\AA}, 284~{\AA} and 304~{\AA}, simultaneously.
+EUVI provides continuous observations of the Sun from the STEREO-A spacecraft's vantage point, located slightly ahead of Earth in its orbit around the Sun.
+This allows EUVI to monitor solar activity over extended periods and to track the evolution of solar features such as AR, flares, and CMEs.
+We have used 171~{\AA} and 195~{\AA} observations from EUVI for our analysis.
 
@@
 Also known as Solar-B before its launch, {\it Hinode} is dedicated to studying the Sun's magnetic field and its dynamic behaviour, focusing on understanding the mechanisms driving solar activity and space weather phenomena.
-The X-Ray Telescope\citep[XRT;][]{xrt} is one of the key instruments aboard the {\it Hinode} spacecraft.
+The X-Ray Telescope \citep[XRT;][]{xrt} is one of the key instruments aboard the {\it Hinode} spacecraft.
 
-{XRT captures high-resolution solar corona images in X-ray wavelengths, allowing us to study phenomena such as solar flares, coronal loops, etc.
-Its imaging capabilities enable us to investigate the solar corona's structure, dynamics, and heating mechanisms.
-XRT utilizes narrow-band filters to isolate specific X-ray emission lines emitted by highly ionized elements in the solar corona.
+XRT captures solar corona images in X-ray wavelengths, allowing us to study phenomena such as solar flares, coronal loops, etc.
+Its imaging capabilities enable us to investigate the solar corona's structure, dynamics, and heating mechanisms with a pixel size 1.028{\arcsec}/pix and a Field of View (FoV) size (34{\arcmin}$\times$34{\arcmin}).
+XRT utilizes narrow-band filters to isolate specific X-ray emission lines emitted by highly ionized elements in the solar corona sensitive to temperatures from 1 {--} 30 MK.
 XRT provides continuous observations of the solar corona from the vantage point of the {\it Hinode} spacecraft, which orbits the Earth in a Sun-synchronous polar orbit.
-This allows XRT to monitor solar activity over extended periods.
+The cadence of XRT observations can range from 30 {--} 60 s in the regular synoptic mode and upto 2 s in flare mode.
 In our analysis, we used XRT imaging observation from various filters.
+%\info{When you discussing all these instruments, you should have a scheme, i.e., what parameters you are going to be mentioning for each, e.g.
+spatial resolution, wavelength band, temperature coverage where available, spectral resolution etc...
+and be consistent throughout the chapter.}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%--------------------------------------------------------------
 \section{Geostationary Operational Environmental Satellites (GOES)}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%--------------------------------------------------------------
 
@@
 This information is crucial for forecasting space weather events and assessing their potential impact on satellite communications, navigation systems, and power grids.
-Among the numerous instruments on-board {\GOES}, we have used data from two instruments extensively {--} X-Ray Sensor (XRS) and Solar Ultra Violet Imager (SUVI).
+Among the numerous instruments on-board {\it GOES}, we have used data from two instruments extensively {--} X-Ray Sensor (XRS) and Solar Ultra Violet Imager (SUVI).
 
@@
 The primary function of the XRS is to continuously monitor and measure full disk integrated solar soft X-ray emissions, particularly those associated with solar flares.
-XRS is designed to detect and measure solar X-ray emissions in two energy bands: short wavelength (0.5 to 4 {\AA}) and long wavelength (1 to 8 {\AA}).
+XRS is designed to detect and measure solar X-ray emissions in two energy bands: short wavelength (0.5 to 4 {\AA}) and long wavelength (1 to 8 {\AA}) with a 2 s cadence during nominal operations.
 
@@
 Solar Ultraviolet Imager \citep[SUVI;][]{suvi} is an instrument aboard {\it GOES}, designed to observe the Sun in the EUV spectrum, providing crucial data for monitoring solar activity and space weather.
-SUVI captures images of the Sun in 94 {\AA}, 131 {\AA}, 171 {\AA}, 195 {\AA}, 284 {\AA} and 304 {\AA}.
-These wavelengths are very similar to AIA and provide complementary observations.
-The FoV of SUVI is rotated by $\sim~45^{o}$, and hence, provides a larger radial distance coverage along the diagonals.
+SUVI captures images of the Sun in 94 {\AA}, 131 {\AA}, 171 {\AA}, 195 {\AA}, 284 {\AA} and 304 {\AA} with a 2.5{\arcsec} pixel size.
+These wavelengths are very similar to AIA and provide complementary observations and very similar temperature coverage as AIA.
+The FoV of SUVI is rotated by $\sim~45^{o}$, and provides a larger radial distance coverage along the diagonals.
 In our analysis, we have used SUVI observations from 94 {\AA}, 131 {\AA}, 171 {\AA}, and 195 {\AA}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Various Plasma Diagnostic Methods}
+\section{Techniques for Astrophysical Plasma Diagnostic}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-We employ various techniques throughout this thesis to infer electron density, ion and electron temperature, velocity, thermal structure of the plasma observed in both Chromosphere and Corona.
+We employ various techniques throughout this thesis to infer electron density, ion and electron temperature, velocity, and thermal structure of the plasma observed in both Chromosphere and Corona.
 It is standard practice to use atomic databases like CHIANTI \citep{chianti,chianti1} to derive the plasma properties.
@@
 Differential emission measure analysis is a commonly employed method with instruments that observe multiple spectral bands to determine the temperature and emission measure of optically thin coronal plasma exhibiting multiple thermal components along a line of sight.
-However, the inversion process is often challenging due to its ill-posed nature and the frequent lack of sufficient constraints, making it an under determined problem.
+However, the inversion process is often challenging due to its ill-posed nature and the frequent lack of sufficient constraints, making it an under-determined problem.
 One of the very first DEM calculation algorithm was {\it xrt\_dem\_iterative}, which was designed and validated for use with XRT data \citep{golub04,weber04}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Plasma Velocity from Spectra}
+\subsection{Doppler Velocity from Spectra}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Numerous modern and historical imaging, spectroscopic, and polarimetric instruments have significantly contributed to our comprehension of the Sun and its atmosphere.
-Several of these instruments, previously discussed, have been utilized in this thesis.
-While certain instruments are ground-based telescopes, others operate from space.
-Space-based instruments primarily observe the Sun in Ultraviolet (UV), extreme ultraviolet (EUV), and X-ray bands, capturing radiation emitted from upper atmospheric layers like the transition region and corona, which possess elevated temperatures.
-Over recent decades, various studies of the Sun have effectively unveiled the physical characteristics of the gas in its upper atmospheric layers using observations recorded by X-ray imaging (e.g., {\it Hinode} X-ray Telescope \citep[{\it Hindoe}/XRT,][]{xrt}) and spectroscopy (e.g., the Spectrometer/Telescope for Imaging X-rays on {\it Solar Orbiter} \citep[{\it SO}/STIX,][]{stix}) as well as extreme ultraviolet (EUV) imaging (e.g., Atmospheric Imaging Assembly on the {\it Solar Dynamic Observatory} \cite[{\it SDO}/AIA,][]{aia}; Extreme ultraviolet Imaging Telescope on {\it Solar and Heliospheric Observatory} \cite[{\it SoHO}/EIT,][]{eit}; Solar Ultraviolet Imager on the {\it Geostationary Operational Environmental Satellites} \citep[{\it GOES}/SUVI,][]{suvi}; the Extreme Ultraviolet Imager on {\it Solar Terrestrial Relations Observatory-A} \cite[{\it STEREO-A}/EUVI,][]{stereo,euvi}; the Extreme-Ultraviolet Imager on {\it SO} \citep[{\it SO}/EUI][]{eui}) and spectroscopy (e.g., \citep[Hinode/EIS,][]{eis}), among others.
-Instruments such as the {\it Transition Region and Coronal Explorer} \citep[{\it TRACE},][]{trace}, the Solar Ultraviolet Measurements of Emitted Radiation on {\it SoHO} \citep[{\it SoHO}/SUMER,][]{sumer}, and {\it Interface Region Imaging Spectrograph} \citep[{\it IRIS},][]{iris} have facilitated detailed examinations of the chromosphere and the transition region.
-These missions offer continuous full-disk and Region of Interest (RoI) coverage of the Sun across X-ray and EUV wavelengths.
-However, the scenario is notably different in the Near-Ultraviolet (NUV) regime, where there is evidently a lack of continuous full solar disk coverage within this wavelength range.
-
-A significant challenge in conducting solar observations in the UV range from the ground is the substantial attenuation caused by the Earth's atmosphere.
-To overcome this obstacle, one of the pioneering approaches involved the deployment of stratospheric balloon-borne instruments in 1970 and 1971, as documented by \cite{herse79}.
-This instrument featured a 20 cm telescope capable of imaging the Sun within the 200-460 nm range.
-Subsequently, the Rasolba balloon experiment utilized a 30 cm telescope equipped with an ultraviolet spectrograph, yielding high-resolution spectra of the Sun spanning 190 to 295 nm \citep{samain85,staath95}.
-Building upon these endeavors, the Sunrise project \citep{sunrise1,sunrise2} emerged as a balloon-borne observatory designed to observe the Sun in the Near Ultraviolet (NUV) range using a 1 m diameter telescope.
-Sunrise conducted two flights, in June 2009 and June 2013, respectively, and provided high-resolution imaging at wavelengths of 214, 300, 312, 388, and 397 nm with the Sunrise Filter Imager \citep[SuFI,][]{sufi} in 2009, and at 214, 279, and 397 nm in 2017 \citep{sunrise2}.
-Additionally, Dopplergrams and vector magnetograms were obtained in \ion{Fe}{1} 525.02 nm using the Imaging Magnetograph eXperiment \citep[IMaX,][]{imax} at various locations on the solar disk.
-Throughout these flights, Sunrise observed a variety of solar phenomena, including emerging flux events \citep{centeno17}, properties and dynamics of moving magnetic features around pores \citep{kaithakkal17}, proper motion of bright points in quiet sun and active regions \citep{jafarzadeh17}, and properties of fibrils \citep{gaferia17}.
-These observations underscored the wealth of information carried by this wavelength range and paved the way for full-disk coverage of the Sun in the NUV.
-
 The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article}, iss one of the seven payloads aboard the Aditya-L1 mission \citep{adityal1, aditya} led by the Indian Space Research Organization (ISRO).
 Launched on September 2, 2023, the satellite orbits around the Sun-Earth L1 point in a halo orbit.
-Equipped with eleven science filters, comprising eight narrow band and three broad band filters, SUIT possesses a distinctive capability to explore various heights within the solar photosphere and chromosphere.
+Equipped with eleven science filters, comprising eight narrow-band and three broad-band filters, SUIT possesses a distinctive capability to explore various heights within the solar photosphere and chromosphere.
 This capability aids in understanding the diverse physical processes involved in the transport of mass and energy across different layers of the Sun.
@@
 
-{\suit} is designed to deliver continuous full-disk and Region of Interest (RoI) solar images, boasting a plate scale of 0.7 \arcsec.
+{\suit} is designed to deliver continuous full-disk and Region of Interest (RoI) solar images, boasting a plate scale of 0.7{\arcsec}.
 It possesses the ability to track RoIs while compensating for the effects of differential rotation, as outlined by \cite{suit_algo}.
@@
 \begin{itemize}
-    \item dynamic coupling between the lower and the middle solar atmosphere
-    \item measurement of solar spectral radiance in the NUV.
-    \item spectral energy distribution of solar flares in NUV
-    \item dynamics of chromospheric eruptive phenomena at various spatio temporal scales
+    \item Dynamic coupling between the lower and the middle solar atmosphere
+    \item Measurement of solar spectral radiance in the NUV.
+    \item Spectral energy distribution of solar flares in NUV
+    \item Dynamics of chromospheric eruptive phenomena at various spatiotemporal scales
     \item Initiation of Coronal Mass Ejections(CMEs) and space weather: the kinematics of erupting prominence during the early phase.
@@
 With its 11 science filters (3 broadband and eight narrow band), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another.
-SUIT will provide full disk as well as partial disk images of the Sun with a pixel size of 0.7".
 Through SUIT imaging, we would be able to resolve solar flares spatially on the surface of the Sun, for the first time in near ultra-violet (NUV), which will help us to address the questions regarding their build-up and triggering mechanism.
@@
     \includegraphics[width = \linewidth]{Figures/Krucker_2015_ApJ_802_19_page-0004.jpg}
-    \caption{X-ray and optical imaging of the three flares at the peak time of the impulsive phase: the images are from HMI with the pre-flare image subtracted.
+    \caption[X-ray and optical imaging of the three flares at the peak of the flare.]{X-ray and optical imaging of the three flares at the peak time of the impulsive phase: the images are from HMI with the pre-flare image subtracted.
 The contours represent RHESSI Clean maps in the thermal (red, 12–15 keV) and non-thermal (blue, 30–80 keV) HXR range \citep{krucker15}.}
@@
     \includegraphics[width = 0.7\linewidth]{Figures/nphys1741_page-0002.png}
-    \caption{Averaged TSI variations during flares.
+    \caption[Averaged TSI variations during flares of various strengths.]{Averaged TSI variations during flares.
 The TSI time-series averages over four exclusive sets of solar flares of decreasing amplitude.

### 2025-04-11 chapter2/chap2_2.tex
Local changes

--- 2025-04-11 chapter2/chap2.tex
@@
 
-The remarkable technological progress attained in the last few decades has yielded significant benefits in the form of highly advanced imaging, spectroscopic, and polarimetric instruments designed for astronomical observations.
-These instruments have empowered us with the ability to scrutinize the Sun with exceptional detail.
-Specifically, the space based observatories have added new avenues of observing the Sun.
+The remarkable technological progress attained in the last decades has yielded significant benefits in the form of highly advanced imaging, spectroscopic, and polarimetric instruments designed for astronomical observations.
+These instruments have empowered us with the ability to scrutinise the Sun with exceptional detail.
+Specifically, space-based observatories have added new avenues for observing the Sun.
 The studies within this thesis are performed using multi-wavelength imaging and spectroscopic observations of solar flares recorded from space.
-This chapter describes the details of the instruments and techniques used for our analysis.
+This chapter briefly describes and provides relevant details of instruments whose observations are used in this thesis.
+Moreover, we also discuss the data analysis techniques used for our analysis.
 
@@
 
-The Solar Dynamics Observatory \citep[SDO;][]{sdo} is a NASA mission designed to understand the causes of solar variability at various spatio-temporal and wavelength scales, as well as its impacts on Earth and the near-Earth environment.
+The solar Dynamics Observatory \citep[SDO;][]{sdo} is a NASA mission designed to understand the causes of solar variability at various spatio-temporal and wavelength scales, as well as its impacts on Earth and the near-Earth environment.
 It is part of NASA’s Living With a Star program and houses multiple instruments onboard to address its numerous scientific goals.
@@
 Solar Orbiter \citep[SO;][]{so} is a joint mission between the European Space Agency (ESA) and NASA, launched in February 2020.
-The Spectrometer/Telescope for Imaging X-rays (STIX) \citep[STIX,][]{stix,stix1} is designed to study the Sun's X-ray emissions, providing crucial insights into solar flares and other high-energy phenomena.
+The Spectrometer/Telescope for Imaging X-rays \citep[STIX,][]{stix,stix1} is designed to study the Sun's X-ray emissions, providing crucial insights into solar flares and other high-energy phenomena.
 STIX incorporates a set of collimators and detectors to capture high-resolution images of the Sun in X-rays.
@@
 The instrument covers a broad range of X-ray energies, from approximately 4 to 150 keV, probing both thermal and non-thermal X-rays.
-STIX provides X-ray imaging with a spatial resolution $\sim$ 7 {\arcsec} at the shortest wavelengths using Fourier imaging techniques.
+STIX provides X-ray imaging with a spatial resolution $\sim$ 7{\arcsec} at the shortest wavelengths using Fourier imaging techniques.
 Notably, the spatial resolution depends on the visibilities at various energies.
@@
 The instrument operates in two data modes: the low-resolution background monitoring mode in quiet conditions and the high-resolution mode activated during solar flares.
-STIX works together with other instruments onboard the Solar Orbiter, providing complementary measurements to enhance our understanding of the Sun's dynamic behaviour across different wavelengths and energy ranges.
+STIX works together with other instruments onboard the solar Orbiter, providing complementary measurements to enhance our understanding of the Sun's dynamic behaviour across different wavelengths and energy ranges.
 
@@
 {\it Hinode} \citep{hinode}, meaning "Sunrise" in Japanese, is a space mission launched by the Japan Aerospace Exploration Agency (JAXA) in collaboration with NASA and the UK Space Agency in September 2006.
-Also known as Solar-B before its launch, {\it Hinode} is dedicated to studying the Sun's magnetic field and its dynamic behaviour, focusing on understanding the mechanisms driving solar activity and space weather phenomena.
+Also known as solar-B before its launch, {\it Hinode} is dedicated to studying the Sun's magnetic field and its dynamic behaviour, focusing on understanding the mechanisms driving solar activity and space weather phenomena.
 The X-Ray Telescope \citep[XRT;][]{xrt} is one of the key instruments aboard the {\it Hinode} spacecraft.
@@
 This information is crucial for forecasting space weather events and assessing their potential impact on satellite communications, navigation systems, and power grids.
-Among the numerous instruments on-board {\it GOES}, we have used data from two instruments extensively {--} X-Ray Sensor (XRS) and Solar Ultra Violet Imager (SUVI).
+Among the numerous instruments on-board {\it GOES}, we have used data from two instruments extensively {--} X-Ray Sensor (XRS) and solar Ultra Violet Imager (SUVI).
 
@@
 
-In Eqn.~\ref{eqn:dem}, $\mathrm{g_{i}}$ is the counts observed in some specific filter (usually in units of $\mathrm{DN.s^{-1}.pix^{-1}}$), $\mathrm{\delta g_{i}}$ is the observed error, $\mathrm{R_{i}}$ is the temperature response function of the specific filter and DEM(T) describes the thermal distribution of the local plasma  (usually in units of $\mathrm{cm^{-5}.K^{-1}}$).
+In Eqn.~\ref{eqn:dem}, $\mathrm{g_{i}}$ is the counts observed in some specific filter (usually in units of $\mathrm{DN.s^{-1}.pix^{-1}}$), $\mathrm{\delta g_{i}}$ is the observed error, $\mathrm{R_{i}}$ is the temperature response function of the specific filter and {\bf $\mathrm{\zeta(T)}$} describes the thermal distribution of the local plasma  (usually in units of $\mathrm{cm^{-5}.K^{-1}}$).
 For multiple filter observations, this problem can be posed as a matrix equation in the form of $\Vec{g}~=~\mathbb{R}~\Vec{\zeta}\implies \Vec{\zeta}~=~\mathbb{R}^{-1}\Vec{g}$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Doppler Velocity from Spectra}
+\subsection{Doppler and Non-thermal Velocity from Spectra}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Solar Ultraviolet Imaging Telescope}\label{sec:suit}
+\section{The solar Ultraviolet Imaging Telescope (SUIT)}\label{sec:suit}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article}, iss one of the seven payloads aboard the Aditya-L1 mission \citep{adityal1, aditya} led by the Indian Space Research Organization (ISRO).
+The solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article}, is one of the seven payloads aboard the Aditya-L1 mission \citep{adityal1, aditya} led by the Indian Space Research Organization (ISRO).
 Launched on September 2, 2023, the satellite orbits around the Sun-Earth L1 point in a halo orbit.
@@
 Additionally, SUIT is equipped with onboard intelligence to detect and localize flares, and it can autonomously adjust exposure times to prevent saturation.
-The primary scientific inquiries targeted by SUIT include \citep{suit_science, suit_main}:
+The primary scientific inquiries targeted by SUIT include \citep{suit_main}:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{SUIT \& Solar Flares}\label{sec:suit_and_flare}
+\subsection{SUIT \& solar Flares}\label{sec:suit_and_flare}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1} of the Indian Space Research Organization (ISRO).
-With its 11 science filters (3 broadband and eight narrow band), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another.
-Through SUIT imaging, we would be able to resolve solar flares spatially on the surface of the Sun, for the first time in near ultra-violet (NUV), which will help us to address the questions regarding their build-up and triggering mechanism.
+The solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1} of the Indian Space Research Organization (ISRO).
+With its eleven science filters (three broadband and eight narrow band), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another.
+Through SUIT imaging, we would be able to resolve solar flares spatially on the surface of the Sun, for the first time in near ultra-violet (NUV) {\bf 200 {-- 400} nm regime}, which will help us to address the questions regarding their build-up and triggering mechanism.
 In addition, to measure the spatially resolved solar spectral irradiance within the wavelength range that is central for studying the Chemistry of oxygen and ozone in the Stratosphere of Earth's atmosphere.
@@
 This may have implications on the physics of the origin of solar flares and different physics processes and contribute to the solar spectral irradiance as a function of the solar activity cycle.
-Although we have been observing Sun and Solar flares in various wavelengths, the spectral energy distribution of the radiated energy from the flares is still very poorly understood.
+Although we have been observing Sun and solar flares in various wavelengths, the spectral energy distribution of the radiated energy from the flares is still very poorly understood.
 The first solar flares were observed from the ground in the visible domain \citep{carrington1859,neidig93}.
@@
 Also, the flares in NUV are not observable from any ground-based instrumentation as most of the NUV gets absorbed in the upper atmosphere, thus requires space-based observations.
+{\bf The attenuation is usually given by
+
+%%%%%%%%%
+\begin{equation}
+    \mathrm{I~=~I_{0}e^{-\alpha d}}
+\end{equation}
+%%%%%%%%%
+
+where the I and $\mathrm{I_{0}}$ are the initial and transmitted intensity respectively, `d' is the distance traveled by the incident flux.
+The attenuation coefficient ($\mathrm{\alpha}$) is defined in units of $\mathrm{length^{-1}}$ and given by the Linke-Borne formula \citep{linke22, middleton51}, $\mathrm{\alpha~=~A\lambda^{-B}}$, which depends on various physical parameters of the atmosphere, e.g., density, temperature, pressure, composition of the air column etc.
+Under average atmospheric conditions, the attenuation coefficient varies significantly in the wavelength range 200 {--} 400 nm, varying from > $\mathrm{4~km^{-1}}$ around $\sim$ 200 nm, to < $\mathrm{0.4~km^{-1}}$ around $\sim$ 400 nm \citep[see Fig.7, Fig.83 and the accompanying discussions in][]{baum_thes}.}
 
@@
 Similarly, \cite{krucker15} constrained the cospatial WL and HXR foot points within the chromosphere for three flares.
-With the help of SUIT, we would be able to localize the WL flares and resolve them on various parts of the Solar disk, which along with observations from Interface Region Imaging Telescope (IRIS), Helioseismic and Magnetic Imager (HMI), would help us localize the source of the WL foot points and also comment on the formation mechanism of the WL itself.
+With the help of SUIT, we would be able to localize the WL flares and resolve them on various parts of the solar disk, which along with observations from Interface Region Imaging Telescope (IRIS), Helioseismic and Magnetic Imager (HMI), would help us localize the source of the WL foot points and also comment on the formation mechanism of the WL itself.
 
@@
 
-Finally, one of the major question of interest is how the Solar flares affect the Spectral Solar Irradiance (SSI) and Total Solar Irradiance (TSI) variability from a short to much longer, Solar Cycle timescale.
+Finally, one of the major question of interest is how the solar flares affect the Spectral solar Irradiance (SSI) and Total solar Irradiance (TSI) variability from a short to much longer, solar Cycle timescale.
 \cite{kretzschmar10,kretzschmar11} performed statistical studies using a large number of flare observations across a wide energy range.
-For this purpose, they used the full Sun observations of Solar flux from Solar and Heliospheric Observatory (SoHO), three visible Solar irradiances from VIRGO/Solar Photometer (SPM) pass bands centred on 402 nm, 500 nm, and 862 nm, respectively, from 1996 to 2008.
+For this purpose, they used the full Sun observations of solar flux from solar and Heliospheric Observatory (SoHO), three visible solar irradiances from VIRGO/Solar Photometer (SPM) pass bands centred on 402 nm, 500 nm, and 862 nm, respectively, from 1996 to 2008.
 Additionally, they also use the EUV irradiance in the ranges 0.1-50 nm and 26-34 nm measured by SOHO/Solar EUV Monitor \citep{judge98} and SXR measurements from GOES satellites.
@@
 For example, the Earth's atmospheric chemistry and composition respond to any changes in solar UV output in a very nonlinear fashion \citep{haigh07}.
-Since the number of flares also shows a change with solar activity, it is prudent to ask how much flares contribute to the solar spectral irradiance in NUV.
+Since the number of flares also shows a change with solar activity, it is prudent to ask how much do flares contribute to the solar spectral irradiance in NUV {\bf over solar cycle timescales}.
 This is particularly important because the irradiance in NUV plays a key role in heating the upper and middle layers of the Earth's atmosphere directly and their coupling with the Stratosphere.
 It also directly influences the middle and lower atmosphere chemistry and composition via the Ozone-Oxygen cycle.
+{\bf In certain extreme cases, a single flare can drive noticeable changes in the upper atmospheric conditions, e.g., the X-class flare on 7th September, 2011 induced a large variation in the E-layer conductivity driven by the $\mathrm{Ly-\alpha}$ radiation \citep[see Fig.10 and the accompanying discussion in][]{milligan20}.}
 

### 2025-04-11 chapter3/chap3.tex
Local changes

--- 2024-08-14 chapter6/ms.tex
@@
 
-There are several studies \citep{hilarie05,caspi10} that estimate the thermal energy as a function of time. The thermal energy of the flares is defined as 
+There are several studies \citep{hilarie05,caspi10} that estimate thermal energy as a function of time. The thermal energy of the flares is defined as 
 \begin{equation}
@@
     \includegraphics[trim={0cm 0.5cm 1.2cm 0.5cm},clip,width=\textwidth]{flare_pos.pdf}
-    \caption{Position of various instruments during the flares.
+    \caption[Position of various instruments during the flares.]{Position of various instruments during the flares.
 AIA 193~{\AA} observations during 2021 Oct 28 (panel a) and EUVI 171~{\AA} observation during 2020 Nov 29 (panel c) in Heliographic Stonyhurst (HGS) coordinates.
@@
 We also estimate the cumulative non-thermal energy deposited by the non-thermal electrons and compare it with our thermal energy estimates for the flare observed on 28 October, 2021.
-In \S\ref{sec:obs} we discuss the observations used in this paper and details of our analysis.
+In \S\ref{sec:obs} we discuss the observations used in this {\bf chapter} and details of our analysis.
 We discuss our method for estimating the thermal energy in \S\ref{sec:therm}.
@@
     \includegraphics[width=0.95\textwidth,trim={0.3cm 4cm 0cm 2cm},clip]{oct28_align_new.pdf}
-    \caption{X-class flare observed on October 28, 2021.
+    \caption[Observation of the X-class flare on October 28, 2021.]{X-class flare observed on October 28, 2021.
 Panel (a): the post eruption arcade as observed in AIA 193~{\AA}.
@@
     \includegraphics[trim={4.8cm 2.5cm 6cm 2.5cm},clip,width=0.8\textwidth]{nov_29_align.pdf}
-    \caption{M-class flare on Nov 29, 2020 as observed nearly simultaneously by AIA~{131 \AA} (panel a) and XRT Be-med filer (panel b) and the derived EM map (panel c) and DEM weighted temperature (panel d).
+    \caption[Observation of the M-class flare on November 29, 2020.]{M-class flare on Nov 29, 2020 as observed nearly simultaneously by AIA~{131 \AA} (panel a) and XRT Be-med filer (panel b) and the derived EM map (panel c) and DEM weighted temperature (panel d).
 The EM map is obtained by integrating over the temperature range of 5$<\log\,T<$7.4.}
@@
 
-%%--------------
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.8\textwidth,trim={2cm 6cm 2cm 6cm},clip]{flare_orient.pdf}
-    \caption{Panel (a): {\it STEREO-A}/EUVI 171 {\AA} observation of the flare arcade in the decay phase.
-The magenta cross marks a point on the top of the arcade.
-The line of sight (LOS) goes into the page through that point.
-Panel (b): SDO/AIA 171 {\AA} observation of the flare arcade.
-The red line marks the LOS through the arcade from the STEREO-A perspective projected to the AIA perspective.} %Panel (c): Cartoon demonstrating the projection effects of a semicircular loop between STEREO-A and AIA vantages due to the difference between polar ($\theta$) and azimuthal ($\phi$) angles respectively.
-Panel (d) : The calculated LOS map from the AIA perspective, with the calculated loop top height under the assumption of a semi-circular loop geometry.}
-    \label{fig:flare_orient}
-\end{figure}
-%%--------------
-%%--------------
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.9\textwidth,trim={4cm 5cm 3cm 5cm},clip]{nov29_triangulate.pdf}
-    \caption{Panel (a): SDO/AIA 193 {\AA} observation of the Nov 29 flare in the decay phase.
-The blue cross marks a point on the top of the arcade.
-The LOS goes into the page from AIA perspective.
-Panel (b): {\it STEREO-A}/EUVI 195 {\AA} observation around same time.
-The blue solid line is the LOS from AIA perspective in panel (a) projected onto {\it STEREO-A} perspective.
-We can trace out the height of the flare arcade at various locations using \textit{scc\_measure.pro}.
-The height of the arcade at various points from the Sun's surface is marked in panel (a).}
-    \label{fig:flare_orient2}
-    \end{figure}
-%%--------------
-
 The temperature range of the integration is set to $5 < \log\,T < 7.4$.
@@
 For our analysis, the volume of the plasma along an individual pixel is given by $V_{j}~=~A\times~LOS_{j}$, where $LOS_{j}$ is the line of sight (LOS) for the j-th pixel in the FOV and $A$ is the physical area of a pixel.
-
-%%--------------
-\begin{figure}[ht!][!h]
-    \centering
-    \includegraphics[width=0.8\textwidth,trim={3cm 2cm 3cm 0cm},clip]{flare_orient_pt2.pdf}
-    \caption{Panel (a): Cartoon demonstrating the projection effects of a semicircular loop between STEREO-A and AIA vantages due to the difference between polar ($\theta$) and azimuthal ($\phi$) angles, respectively.
-Panel (b) : The calculated LOS map from the AIA perspective for the 28th October, 2021 event, with the estimated loop top height under the assumption of a semi-circular loop geometry.}
-    \label{fig:flare_orient_2}
-\end{figure}
-%%--------------
 
@@
 
-To infer the LOS along individual pixels in the FOV for both the flares, we use AIA and STEREO-A/EUI observations, recorded from two different vantage points, to calculate the height of the flare loop.
-We display STEREO-A/EUI and AIA-171 image taken neeary simultaneously in Fig.~\ref{fig:flare_orient} a~\&~b, respectively.
-The magenta cross on Fig.~\ref{fig:flare_orient}.a shows a point at the top of the flare arcade.
-The LOS goes into the page through that point from the {\it STEREO-A} vantage.
-The red line in Fig.~\ref{fig:flare_orient}.b shows the LOS through the point in Fig.~\ref{fig:flare_orient} a projected to {\it SDO}/AIA point of view.
-This demonstrate the geometric effect of observing from different vantage points.
-
-We show the same in Fig.~\ref{fig:flare_orient2} for the Nov 29, 2020 flare.
-The blue cross marked in Fig.~\ref{fig:flare_orient2}.a is the LOS going into the page from AIA perspective.
-The blue line marked in Fig.~\ref{fig:flare_orient2}.b is the same LOS projected onto the STEREO-A perspective.
-Distances on the observation from two different vantages would be projected by the differences in the polar and the azimuthal angle between the two vantages.
-Fig.~\ref{fig:flare_orient_2}.a shows the projection effect of a semicircular loop between AIA and STEREO-A LOS.
-Depending on the orientation of the loops, the projection along the polar and azimuthal angle projects the length of the loop and the height of the loop.
-The height at various position of the flare arcade is marked in Fig.~\ref{fig:flare_orient2}.a.
-We assume a semi-circular loop geometry with the height of the loop top to calculate the LOS along every pixel within the flare arcade.
-
 We use co-temporal {\it STEREO-A} 171 {\AA}, 195 {\AA}, and AIA~171 {\AA}, 193 {\AA} images with \textit{scc\_measure.pro}, available in the \textit{sswidl}, to calculate the height of the loop.
@@
 The line of sight (LOS) through the same point is shown on the observation from the different vantage.
-The same point can be identified on the projected LOS by the user, by identifying similar emission characteristics.
+The same point can be identified on the projected LOS by the user by identifying similar emission characteristics.
 The program determines the 3D coordinates of the point (heliographic latitude, longitude and radial distance).
@@
 We note that the height estimation using \textit{scc\_measure.pro} is limited by our identification of ``similar emission characteristics" between the two observations from AIA and {\it STEREO-A}.
+We choose multiple points on the top of the arcade, and calculate the height of the arcade at various locations tracing the looptop.
+The number of points we consider is not fixed and varies from frame to frame.
+After this, using the chosen points we interpolate to get the loop top from the AIA perspective, and the calculated height at these points gives us how the height of the loop top changes across the arcade.
+We assume a semi-circular loop geometry with the height of the loop top to calculate the LOS along every pixel within the flare arcade.
+It is worth reiterating that a majority of the uncertainty in determining the LoS would be arising from the identification of the loop top in two different vantages.
+
+To infer the LoS along individual pixels in the FOV for both the flares, we use AIA and STEREO-A/EUI observations, recorded from two different vantage points, to calculate the height of {\bf both flare loops}.
+We show the STEREO-A/EUI 195~{\AA} and AIA 193~{\AA} observation for the Nov 29, 2020 flare in Fig.~\ref{fig:flare_orient2} panel b and a respectively.
+The blue cross marked in Fig.~\ref{fig:flare_orient2}.a is the LOS going into the page from AIA perspective.
+The blue line marked in Fig.~\ref{fig:flare_orient2}.b is the same LOS projected onto the STEREO-A perspective.
+The red crosses marked on the AIA 193~{\AA} loops mark the LoS going into the page, to infer the looptop from the AIA perspective.
+The red crosses marked on Fig.~\ref{fig:flare_orient2}.b EUVI 195~{\AA} observations marks the position of the looptop along the LoS from AIA perspective considered to find the looptop from EUVI perspective.
+In Fig.~\ref{fig:flare_orient2}.c we show the inferred LoS map for these two frames.
+The fan is assumed to have a constant LoS depth as mentioned earlier.
+For the loops we calculate the LoS assuming a semi-circular loop geometry with the height inferred from \textit{scc\_measure.pro}.
+The inferred LoS is lower near the loop top, and increases as we move closer the the foot points, exhibiting the variable LoS across the observation frame.
+
+We display STEREO-A/EUVI and AIA-171 {\bf images} taken {\bf nearly} simultaneously in Fig.~\ref{fig:flare_orient} a~\&~b, respectively for the 28 Oct, 2021 event.
+The red and black cross on Fig.~\ref{fig:flare_orient}.a shows a point at the top of the flare arcade.
+The LOS goes into the page through that point from the {\it STEREO-A} vantage.
+The blue line in Fig.~\ref{fig:flare_orient}.b shows the LOS through the point in Fig.~\ref{fig:flare_orient} a projected to {\it SDO}/AIA point of view.
+This demonstrates the geometric effect of observing from different vantage points.
+In Fig.~\ref{fig:flare_orient}.c we show the inferred LoS map from the AIA perspective.
+
+%We show the same in Fig.~\ref{fig:flare_orient2} for the Nov 29, 2020 flare.
+The blue cross marked in Fig.~\ref{fig:flare_orient2}.a is the LOS going into the page from AIA perspective.
+The blue line marked in Fig.~\ref{fig:flare_orient2}.b is the same LOS projected onto the STEREO-A perspective.
+The red crosses marked on the AIA 193~{\AA} loops mark the LoS going into the page, to infer the looptop from the AIA perspective.
+The red crosses marked on Fig.~\ref{fig:flare_orient2}.b EUVI 195~{\AA} observations marks the position of the looptop along the LoS from AIA perspective considered to find the looptop from EUVI perspective.
+Distances on the observation from two different vantages would be projected by the differences in the polar and the azimuthal angle between the two vantages.
+
+%Fig.~\ref{fig:flare_orient_2}.a shows the projection effect of a semicircular loop between AIA and STEREO-A LOS.
+Depending on the orientation of the loops, the projection along the polar and azimuthal angle projects the length of the loop and the height of the loop.
+The height at various {\bf positions} of the flare arcade is marked in Fig.~\ref{fig:flare_orient2}.a.
+We assume a semi-circular loop geometry with the height of the loop top to calculate the LOS along every pixel within the flare arcade.
+
+%%--------------
+\begin{figure*}[!h]
+    \centering
+    \includegraphics[width=\textwidth, trim={1cm 0cm 1cm 3cm}, clip]{paper_plot_los.pdf}
+    \caption[LoS triangulation for the Nov 29th, 2020 flare]{(a) SDO/AIA 193 {\AA} observation of the Nov 29 flare in the decay phase.
+The red and blue crosses marks various points on the top of the arcade used to trace the looptop.
+The LOS goes into the page from AIA perspective.
+(b) {\it STEREO-A}/EUVI 195 {\AA} observation around same time.
+The blue solid line is the LOS from AIA perspective in panel (a) projected onto {\it STEREO-A} perspective.
+The red crosses mark the other red crosses from AIA perspective marked on the looptop visible from Stereo-A perspective.
+The line of sight of the region is shown in panel (c).
+The LoS is higher near the base of the loops and lower near the looptop.
+The fan is assumed to be constant LoS.}
+    \label{fig:flare_orient2}
+\end{figure*}
+%%--------------
+
+%%--------------
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth, trim={1cm 0cm 1cm 3cm}, clip]{paper_plot_los_2.pdf}
+    \caption[LoS triangulation for the Oct 28th, 2021 flare]{(a) {\it STEREO-A}/EUVI 171 {\AA} observation of the {\bf Oct 28} flare arcade in the decay phase.
+The red and black cross marks a point on the top of the arcade.
+The line of sight (LOS) goes into the page through that point.
+(b) SDO/AIA 171 {\AA} observation of the flare arcade.
+The blue line marks the LOS through the arcade from the STEREO-A perspective projected to the AIA perspective.
+The red crosses mark the other red crosses from Stereo-A perspective marked on the loop top visible from AIA perspective.
+The line of sight of the region is shown in panel (c).}
+    \label{fig:flare_orient}
+\end{figure*}
+%%--------------
 
@@
 
-Figure \ref{fig:flare_orient_2}.b shows an example of the calculated LOS in the FOV for the 2021 October 28 flare.
-The highest point of the flare arcade is oriented from south east towards north west, following the ridge.
-We get an estimate of the highest point of the loop $\simeq$ 22~Mm, which is consistent with the estimates of the height, $H~\simeq~20~Mm$ of the ridge from magnetic loop modelling by \cite{longcope22} for the same event.
-Using the map of the LOS shown in the bottom panel of Fig.
-\ref{fig:flare_orient_2}, we determine the thermal energy in every pixel of the flare using Eqn.~\ref{eq:t_eneg}.
-A similar process is used for the flare loops in the 2020 November 29 flare.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We estimate the energy in the non-thermal electrons for the 2021 Oct 28 X-class event by fitting the STIX spectra.
-In Fig.~\ref{fig:stix_an}.a, we plot the STIX light curve of the event in 4 to 6 keV (solid black line), 6 to 12 keV (solid magenta line), 12 to 25 keV (solid yellow line) and 25 to 50 keV (solid blue line).
+In Fig.~\ref{fig:stix_an}.a, we plot the STIX light curve of the event in 4 to 10 keV (solid blue line), 10 to 15 keV (solid orange line), 15 to 25 keV (solid green line) and 25 to 50 keV (solid red line).
 The attenuator kicked in around $\sim$ 15:28 UT, which drastically cuts down the intensity to avoid saturation.
@@
 %%--------------
-\begin{figure}[ht!]
+\begin{figure*}
     \centering
-    \includegraphics[trim={3cm 2cm 6cm 3.5cm},clip,width=0.54\textwidth]{oct28_lc_2.pdf} 
-    \includegraphics[trim={3.5cm 8cm 3cm 2cm},clip,width=0.45\textwidth]{oct28_fit_2.pdf}
-    \caption{Panel a: STIX light curve of the 2021 Oct 28 X-class event in different energy bands as labelled.
-Panel b: STIX spectra integrated between 15:27{--}15:28~UT during impulsive phase, fitted with `\textit{thcik2}' (solid green), `\textit{2vth}' (solid yellow) and the complete fit function `\textit{2vth+thick2}' (solid red line).
-The lower panel shows the normalized residuals of the fit.}
+    \includegraphics[trim={0cm 3cm 1.3cm 3cm}, clip, width=\textwidth]{Figures/oct_28_lc_3.pdf}
+    \caption[STIX light curve and spectra fit for the 2021 Oct 28 flare]{Panel a: STIX light curve of the 2021 Oct 28 X-class event in different energy bands as labeled.
+Panel b: STIX spectra integrated between 15:27:00{--}15:27:10~UT during impulsive phase, fitted with `\textit{thcik2}' (solid yellow), `\textit{vth}' (solid green) and the complete fit function `\textit{vth+thick2}' (solid red line).
+The panel (c) shows the normalized residuals of the fit.}
     \label{fig:stix_an}
-    \end{figure}
+    \end{figure*}
 %%--------------
@@
 We closely follow the method described in \cite{emslie12} to estimate the energy deposited by the non-thermal electrons.
-We fit the STIX spectra of the event averaged over several time bins during the evolution of the flare with `\textit{2vth}' and `\textit{thick2}' functions available in the `\textit{OSPEX}' X-ray spectra fitting package in {\it sswidl}.
-We show a reference fit to the spectra obtained over a time bin $\sim$ 15:26-15:27 UT in Fig.~\ref{fig:stix_an} panel (b) with `\textit{2vth}' (solid yellow) and `\textit{thick2}' (solid green).
-The function `\textit{2vth}' is a two-component thermal function.
+We fit the STIX spectra of the event averaged over several time bins during the evolution of the flare with `\textit{vth}' and `\textit{thick2}' functions available in the `\textit{OSPEX}' X-ray spectra fitting package in {\it sswidl}.
+We show a reference fit to the spectra obtained over a time bin $\sim$ 15:27:00-15:27:10 UT in Fig.~\ref{fig:stix_an} panel (b) with `\textit{vth}' (solid green) and `\textit{thick2}' (solid yellow).
+The function `\textit{vth}' is a two-component thermal function.
 The parameters are the emission measure and temperature of the two thermal components and the relative abundances of Iron/Nickel, Calcium, Sulfur and Silicon with respect to the coronal abundances of CHIANTI \citep{chianti1,chianti}.
@@
 The high energy cutoff is fixed much higher than our concerned energy range ($\sim$ O($10^{1}$ keV)), and we can safely assume that it has a negligible effect on fitting the X-ray spectra \citep{emslie12}.
+{\bf While this serves our purpose of quantifying the bulk non-thermal energy as a function of time, there can be finer details of the physical parameters from the "cold thick target" model that can pose non-physical conditions during the early rise phase of the flares.
+This can also have noticeable effect on the total thermal energy budget of the flare.
+To mitigate this several modifications of the cold thick target model have been proposed, e.g., local re-acceleration of electrons and ions \citep{brown09}, warm thick target model \citep{kontar15, kontar19} and injection of kappa distributed electrons instead of power law \citep{kasparova09, bataglia15, effenberger17}.
+We describe the physical origin of some of these models and their effects on the inferred injected electron spectra in Appendix~\ref{c:a2}.
+We also fit two of the modified models to the same spectra and compare the differences that arise due to that.}
 
 The `\textit{OSPEX}' fitting is done by a forward fitting procedure.
-The parameters of the functions `\textit{2vth}' and `\textit{thick2}' are varied to generate a photon spectrum, which is folded through the detector response matrix to produce a count rate spectrum.
+The parameters of the functions `\textit{vth}' and `\textit{thick2}' are varied to generate a photon spectrum, which is folded through the detector response matrix to produce a count rate spectrum.
 This count rate spectrum is used to constrain the parameters of the functions through an iterative procedure by minimizing the $\chi^{2}$ between the calculated and measured count rate spectrum.
 We provide the fitted temperature and the EM of the hotter thermal component in Tab.~\ref{tab:tab1} during various phases of the flare.
-The temperatures listed in Tab.~\ref{tab:tab1} is lower than the upper limit of the temperature range used ($log(T_{max})~=~7.4$ and $log(T_{min})~=~5$) to calculate the EM and DEM weighted temperature in \S\ref{sec:therm}.
+The temperatures listed in Tab.~\ref{tab:tab1} is lower than the upper limit of the temperature range used ($5.0 \geq \log\,T \leq 7.4)$ %($log(T_{max})~=~7.4$ and $log(T_{min})~=~5$)
+to calculate the EM and DEM weighted temperature in \S\ref{sec:therm}.
 
@@
          &  & log(T) & EM \\ 
-         & \hspace{-1cm}Time (UT) & of hotter component & ($cm^{-3}$) \\
+         & \hspace{-1cm}Time (UT) & of thermal component & ($cm^{-3}$) \\
     \hline
@@
 The cumulative energy deposited into the foot point over time by the non-thermal electrons is a good indicator for the source of the thermal energy of the plasma.
-We add the energy deposited at the foot points by the non-thermal electrons from every time bin, to estimate the cumulative energy deposited by the non-thermal electrons up until that instant: $$U^{cumulative}_{e}(t)~=~\sum_{t'=t_{0}}^{t}U_{e}(t')$$
+We add the energy deposited at the foot points by the non-thermal electrons from every time bin, to estimate the cumulative energy deposited by the non-thermal electrons up until that instant: $$U^{cumulative}_{e}(t)~=~\sum_{t'=t_{0}}^{t}U_{e}(t')$$.
 
@@
     \includegraphics[trim={4cm 1cm 4cm 1cm},clip,width=0.8\textwidth]{flare_eneg.pdf}
-    \caption{Panel (a): Temporal evolution of thermal energy for the 2021 Oct 28 flare as measured using GOES light-curve using the effective volume and a filling factor \textit{f}~=~1 (solid red), \textit{f}~=~0.4 (green triangles), \textit{f}~=~0.2 (blue squares), thermal energy calculated from GOES light curve, but the volume inferred from the area of the of the flaring arcade with STIX SXR images, under the assumption that $V\sim A^{\frac{3}{2}}$ (purple dotted), and DEM obtained from AIA observations (black crosses).
+    \caption[Temporal evolution of the thermal and non-thermal energy for both flares.]{Panel (a): Temporal evolution of thermal energy for the 2021 Oct 28 flare as measured using GOES light-curve using the effective volume and a filling factor \textit{f}~=~1 (solid red), \textit{f}~=~0.4 (green triangles), \textit{f}~=~0.2 (blue squares), thermal energy calculated from GOES light curve, but the volume inferred from the area of the of the flaring arcade with STIX SXR images, under the assumption that $V\sim A^{\frac{3}{2}}$ (purple dotted), and DEM obtained from AIA observations (black crosses).
 We also plot the evolution of non-thermal energy as estimated from STIX (lime green circles).
@@
     \includegraphics[trim={2cm 0cm 1cm 0cm},clip,width=0.8\textwidth]{fan_eneg.pdf}
-    \caption{Calculated thermal energy for the 2020 Nov 29 flare.
+    \caption[Calculated thermal energy for the loops and the fan for the November 29th, 2020 flare.]{Calculated thermal energy for the 2020 Nov 29 flare.
 The total thermal energy of the flare (blue dot-dashed) in comparison to the thermal energy from the fan (red dashed) and the Fermi hard X-ray count (black solid).

### 2025-04-11 chapter4/chap4.tex
Local changes

\justifying

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The remarkable technological progress attained in the last few decades has yielded significant benefits in the form of highly advanced imaging, spectroscopic, and polarimetric instruments designed for astronomical observations. These instruments have empowered us with the ability to scrutinize the Sun with exceptional detail. While some of these are ground-based telescopes, the others operate from space. Primarily, space-based instruments observe the Sun in Ultraviolet (UV), extreme ultraviolet (EUV), and X-ray bands, capturing radiation from upper atmospheric layers such as the transition region and corona, which emit due to their elevated temperatures. Various studies of the Sun over the last few decades have successfully uncovered the physical properties of the gas in the upper layers of the solar atmosphere using the observations recorded by X-ray imaging ({\it Hinode} X-ray Telescope \citep[{\it Hindoe}/XRT,][]{xrt}) and spectroscopy (the Spectrometer/Telescope for Imaging X-rays on {\it Solar Orbiter} \citep[{\it SO}/STIX,][]{stix}) and Extreme Ultraviolet (EUV) imaging (Atmospheric Imaging Assembly on the {\it Solar Dynamic Observatory} \cite[{\it SDO}/AIA,][]{aia}, Extreme ultraviolet Imaging Telescope on {\it Solar and Heliospheric Observatory} \cite[{\it SoHO}/EIT,][]{eit}, Solar Ultraviolet Imager on the {\it Geostationary Operational Environmental Satellites} \citep[{\it GOES}/SUVI,][]{suvi}, the Extreme Ultraviolet Imager on {\it Solar Terrestrial Relations Observatory-A} \cite[{\it STEREO-A}/EUVI,][]{stereo,euvi}, the Extreme-Ultraviolet Imager on {\it SO} \citep[{\it SO}/EUI][]{eui}) and spectroscopy \citep[Hinode/EIS,][]{eis}, among many others. The {\it Transition Region and Coronal Explorer} \citep[{\it TRACE},][]{trace}, the Solar Ultraviolet Measurements of Emitted Radiation on {\it SoHO} \citep[{\it SoHO}/SUMER,][]{sumer} and the {\it Interface Region Imaging Spectrograph} \citep[~{\it IRIS},][]{iris} allowed us to probe the chromosphere and the transition region in detail. These missions provide us with continuous full disk and Region of Interest (RoI) coverage of the Sun over the X-ray and EUV wavelengths. The situation is rather different in the Near-Ultraviolet (NUV) regime. There is clearly a lack of continuous coverage of the full solar disk in this wavelength range.

One of the key challenges of carrying out solar observations in the UV regime from the ground is the strong attenuation by the Earth's atmosphere. One of the first stratospheric balloon-borne instruments was flown in 1970 and 1971 by \cite{herse79} to circumnavigate this. The instrument carried a 20 cm telescope that imaged the sun in 200{--}460 nm. The Rasolba balloon experiment was composed of a 30 cm telescope with an ultraviolet spectrograph. They obtained high-resolution spectra of the Sun in the spectral range 190 {--} 295 nm \citep{samain85,staath95}. Sunrise \citep{sunrise1,sunrise2} is a balloon-borne observatory that followed up these instruments to observe the Sun in the Near UltraViolet (NUV) regime with a telescope of 1 m diameter. It has flown twice, in June 2009 and June 2013, respectively and provided us with high-resolution imaging in 214, 300, 312, 388 and 397~nm with the Sunrise Filter Imager \citep[SuFI,][]{sufi} in 2009 and at 214, 279 and 397~nm in 2017 \citep{sunrise2}, Dopplergrams and vector magnetograms in \ion{Fe}{1} 525.02 nm with the Imaging Magnetograph eXperiment \citep[IMaX,][]{imax} at various locations on the solar disk.  During these two flights, along with quiet sun and active regions, Sunrise observed various solar phenomena, e.g. emerging flux events \citep{centeno17}, properties and dynamics of moving magnetic features around pores \citep{kaithakkal17}, proper motion of bright points in quiet sun and active regions \citep{jafarzadeh17}, properties of fibrils \citep{gaferia17} etc. These observations demonstrated the wealth of information this wavelength range carries and opened the path for full disk coverage of the Sun in the NUV.

The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1, aditya} of the Indian Space Research Organization (ISRO), launched on September 2, 2023. The satellite is placed in a halo orbit around the Sun-Earth L1 point. With its eleven science bandpasses (eight narrow bands and three broad bands), {\suit} has the unique capability to probe different heights in the solar photosphere and chromosphere, helping us to understand various physical processes responsible for the transport of mass and energy from one layer to another. Moreover, SUIT provides the unique opportunity to measure the spatially resolved solar spectral irradiance in the NUV, which is central to our understanding of Sun climate relations.

{\suit} is designed to continuously provide full-disk and RoI images of the Sun, with a 0.7{\arcsec} pixel size. It can track the RoIs while compensating for the differential rotation \citep{suit_algo}. Moreover, it can detect and localise flares with onboard intelligence and can automatically control the exposure time to avoid saturation. The main science questions that {\suit} aims to address are \citep[][]{suit_science,suit_main}:

\begin{itemize}
    \item Coupling and dynamics of the solar atmosphere: {\it How is energy channelled and transferred from the photosphere to the chromosphere in the solar atmosphere?}
    \item Sun-Climate Relationship: {\it Understanding the Variability of Solar Spectral Irradiance (SSI) and NUV radiance of various features on the Sun.}
    \item Solar Flare Dynamics and Energy Distribution: {\it At Which wavelength Do flares emit the majority of their energy, and what proportion of this energy is from the NUV Range? What is the spectral energy distribution of flares?}
    \item Physics of eruptions at various spatiotemporal scales: {\it what physical processes drive eruptive phenomena observed at various spatiotemporal scales in the Photosphere and Chromosphere?}
\end{itemize}

In this work, we aim to forward model the observations recorded by {\suit} using the Max Planck Institute/University of Chicago Radiative Magneto Hydrodynamics \citep[MURaM,][]{muram} and MPS-ATLAS codes as well as observations recorded by the Interface Region Imaging Spectrograph (IRIS). MURaM is a three-dimensional (3D) MHD code designed to facilitate realistic simulations of magneto-convection and other related magnetic features (such as pores, sunspots and emerging flux) in the upper convection zone and photosphere. The simulation includes the effects of non-gray radiative transfer, partial ionization, full compressibility and open boundary conditions. The simulation gives us various physical quantities such as density, temperature, magnetic flux density etc. The MPS-ATLAS \citep{witzke12} code, which solves the radiative transfer equation varies rapidly with the help of opacity distribution functions, can be applied to the model atmosphere obtained from MURaM to synthesize the spectrum. Since the MURaM simulation cubes used here do not include the non-local thermodynamic equilibrium, these cannot be used to forward model the observations for chromospheric filter. Therefore, for this purpose, we utilize the observations recorded by~{\it IRIS} in \ion{Mg}{2} lines. {\bf The \ion{Mg}{2} h \& k lines, located at approximately 2803.5 and 2796.3~{\AA}, respectively, are among the most prominent spectral features in the near-ultraviolet (NUV) range. These lines are primarily formed in the upper chromosphere and the lower transition region \citep{leenarts13a, leenarts13b}, making them valuable diagnostics for studying chromospheric dynamics and heating. The Mg II lines exhibit core reversals due to non-LTE (local thermodynamic equilibrium) effects, providing insights into velocity flows, turbulence, and heating mechanisms in the solar atmosphere. Their strong sensitivity to temperature and density variations makes them particularly useful for investigating solar flares, where enhanced emission in these lines indicates energy deposition in the chromosphere.}

The rest of the {\bf chapter} is structured as follows. In \S\ref{sec:inst} we briefly describe details of the payload and present the effective area of various filter combinations. We present our method for calculating intensity maps from model atmospheres computed from MURaM, using MPS-ATLAS in \S\ref{sec:mps}. We present the measured point spread function (PSF) for the eleven science filters of {\suit} and the effects of the instrument PSF on the imaging in \S\ref{sec:psf} with the calculated intensity maps presented in \S\ref{sec:mps} and~{\it IRIS} observations. Finally, we summarize and conclude in \S\ref{sec:con}.

%%---------------------------------------------------
\begin{figure}
    \centering
    \includegraphics[trim={0.4cm 3.8cm 1cm 0cm},clip,width=0.85\textwidth]{optical_comp.jpeg}
    \caption[Transmission curves of various components of {\suit}]{Transmission as a function of wavelength of thermal filter (panel a), science filters (panels c and d), band pass filters (panel e) and the field corrector lens (panel f). We also plot the reflectivity of the mirrors in panel b and the quantum efficiency curve of the detector (panel g). Labels on x-axes are wavelength in nanometers.} 
    \label{fig:tras_prof}
\end{figure}
%%---------------------------------------------------
%%---------------------------------------------------
\begin{figure}
    \centering
    \includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=0.85\textwidth]{eff_area.pdf}
    \caption{The effective area curves for all science filters as labelled.}
    \label{fig:eff_area}
\end{figure}
%%---------------------------------------------------

%%---------------------------------------------------
\section{The Instrument} \label{sec:inst}
%%---------------------------------------------------
The {\suit} is a two mirror off-axis telescope, which is designed to image the Sun with a plate scale of ~0.7{\arcsec}, and a field of view (FOV) of 0.75{\degree} on a 4096~$\times$~4096 charged coupled device (CCD), which has 12~$\mu$m pixel size. %Figure~\ref{fig:layout} shows a schematic diagram of the {\suit}. 
The entrance of the payload consists of an entrance door mechanism and a thermal filter(TF). The TF \cite[][]{thermal_filter_1, thermal_filter_2} is designed to cut down most of the incoming visible ($\approx$ 99.75\%) and infrared($\approx$ 99.5\%) radiation and transmits a very small fraction ($\approx$ 0.3\%) of the radiation within 200{--}400~nm. The transmitted light passes through the telescope and gets reflected from the primary and secondary mirrors, respectively, to arrive at the shutter mechanism, which is located between the secondary mirror and the filter wheels. For more details on the instrument, see \cite{article,suit_main}.

%%---------------------------%%
\begin{figure*}
    \centering
    \includegraphics[trim={2.7cm 6.7cm 2.7cm 4.5cm},clip,width=0.9\textwidth]{measured_psf.pdf}
    \caption{The measured PSF for the various filter combinations. The colourmap is area normalized, i.e. the sum of the PSF over the total area is unity.}
    \label{fig:psf_3d}
\end{figure*}
%%---------------------------%%

{\suit} has 11 science filters (first column Table~\ref{tab:science_filters}) and five bandpass filters (BPFs), which are used to keep the photon flux within the dynamic range of the CCD. Out of these five bandpass filters, while two are the spare copies NB08 and BB01, we designed three additional bandpass filters, namely, BP02, BP03 and BP04. These 16 filters are mounted on two filter wheels (FWs), each holding eight filters. The combination of the appropriate science filter and band pass filter is achieved by rotating the two filter wheels independently. Note that the secondary piece of BB01 is used as a combination of filter NB01 and BB01. Similarly, NB08 is combined with an identical NB08. Between the FWs and the detectors, a focusing lens is mounted on a piezo motor, which can be used as a focusing mechanism.  Fig.~\ref{fig:tras_prof} displays the transmission profile of the individual components in the optical path.

%%---------------------------%%
\begin{figure*}
    \centering
    %\hspace{-1cm}
    \includegraphics[trim={1.5cm 3cm 2.5cm 4cm},clip,width=0.85\textwidth]{psf_ese_2.eps}
    \caption{The encircled energy curve for the measured PSF. The 95\% encircled energy radius are marked with the vertical dashed red line. The angular scale of the 95\% encircled energy radius is also quoted in each panel for the specific filter combination.}
    \label{fig:psf_ese}
\end{figure*}
%%---------------------------%%

%%---------------------------------------------------
\subsection{Effective Area of SUIT}\label{eff_area}
%%---------------------------------------------------
Let $p(\lambda)$ be the incident photon flux on the entrance aperture. The photo-electron count at the detector, also known as Data Number (DN) is given by,

 $$   DN=\int~p(\lambda)~R(\lambda)~t~d\lambda $$

\noindent where $R(\lambda)$ is the instrument effective area for the specific filter combination and $t$ is the exposure time. The instrumental response, $R(\lambda)$, is computed by multiplying the measured response of all the optical components along the ray path.

Hence,
    $$ R(\lambda)~=~TF(\lambda)\times PM(\lambda)\times SM(\lambda)\times SF_{i}(\lambda)\times $$
    $$ CF(\lambda)\times L(\lambda)\times QE(\lambda) \times A$$

\noindent where A is the entrance aperture area and TF($\lambda$), PM($\lambda$), SM($\lambda$), SF$_{i}$($\lambda$), CF($\lambda$), L($\lambda$) and QE($\lambda$) are the measured responses as a function of wavelength of thermal filter, primary mirror, secondary mirror, science filters, band pass filters, field corrector lens and the quantum efficiency of the CCD, respectively. The obtained effective area curves for each filter are shown in Fig.~\ref{fig:eff_area}.

%%---------------------------------------------------------------
\begin{figure*}
    \begin{center}
        \begin{tikzpicture}[node distance=2cm]
            \node(muram)[io]{Model 3D atmospheres simulated by the radiative-MHD code MURaM};
            \node(slice)[io,right of=muram,xshift=3.5cm]{Slice the MURaM cubes and interpolate them to various $\mu$ values};
            \node(filter)[io,below of=muram,yshift=-1cm]{Use \suit~ science filter profiles accounting for all the optics on the ray path};
            \node(odf)[io,right of=filter,xshift=3.5cm]{Generate ODF tables for various filters using the MPS-ATLAS code};
            \node(rdt)[io,right of=odf,xshift=3.5cm,yshift=1.5cm]{Use ODF tables and 1D ray-atmospheres from the 3D MHD cube to carry out RT calculations using MPS-ATLAS};
            \node(int)[io,below of=rdt,yshift=-3.5cm]{Integrate the generated spectra for each pixel of the cube over the wavelength range of the filter profile to generate the intensity map};
            \node(conv)[io,left of=int,xshift=-4.5cm]{Convolve the total emergent intensity maps with relevant \suit~ PSF and bin to \suit~ plate scale to create mock observation};
            \draw[arrow](muram)--(slice);
            \draw[arrow](slice)--(rdt);
            \draw[arrow](filter)--(odf);
            \draw[arrow](odf)--(rdt);
            \draw[arrow](rdt)--(int);
            \draw[arrow](int)--(conv);
        \end{tikzpicture}
        \caption{The flow chart shows the entire process of generating the simulated intensity maps, from the data cubes and characterizing the filters.}
        \label{fig:flow}
    \end{center}
\end{figure*}
%%---------------------------------------------------------------

%%---------------------------------------------------------------
\subsection{The Point Spread Function (PSF) of {\suit}} \label{sec:psf}
%%-----------------------------------------------------------------
In Fig.~\ref{fig:psf_3d}, we plot the measured Point Spread Function (PSF) at the centre of the CCD for the different science filter combinations for {\suit}. The PSFs are highly peaked at the centre. The scattered light background becomes clearly visible due to the log scaling of the color bar and is more than two orders of magnitude lower than the peak.

Fig.~\ref{fig:psf_ese} shows the encircled energy curve for the measured PSFs for various filter combinations normalized to the total integral of unity. The vertical dashed lines in each plot show the radius within which 95\% of the incident light falls. For example, for the NB02 filter, 95\% of the incident light from a point source arrives within a 2.31{\arcsec} radius ($\sim$ 4.6{\arcsec} diameter) and 5\% of the light falls outside that region. Note that while the 95\% diameter is 4.6{\arcsec}, the PSF is strongly peaked. The overall diameter is considerably larger than the highly peaked part of the PSF because of the presence of a pedestal in the PSF. The pedestal is visible in all of the cases at the base of the central peak, although it is about 2 order of magnitude lower in all the cases (see Fig.~\ref{fig:psf_3d}). In some cases (e.g. NB01, BB02 etc.) a few or multiple smaller peaks apart form the pedestal are also visible. Similar radii for other filters are quoted in the corresponding panels of Fig.~\ref{fig:psf_ese}. The encircled count curves help us characterize the stray light for various filter combinations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Forward Modeling SUIT intensity maps using MPS-ATLAS and MURaM} \label{sec:mps}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

One of the essential steps of characterizing the science filters was to conduct a thorough throughput modeling for the concerned filter combinations. However, quantifying the effects of the wavelength response of the optical components and the PSF on the spatially resolved observations, as well as the contrast variation, requires detailed modeling with resolved simulations of the Sun's surface. For this purpose, we use the MPS-ATLAS code. It is an updated version of the well established ATLAS9 \citep{atlas9} code that can efficiently generate Opacity Distribution Functions (ODFs), model atmospheres, and calculate emergent spectra in local thermodynamic equilibrium (LTE) for a given wavelength range by solving radiative transfer (RT) equation in plane parallel geometry using the assumptions of local-thermodynamic-equilibrium (LTE).

%%----------------------------------------------------------
\begin{figure}
    \centering
    \includegraphics[width=.85\textwidth]{mps.pdf}
    \caption{Forward modelled intensity maps at various $\mu$ values for BB02 filter of SUIT.}
    \label{fig:flux_maps}
\end{figure}
%%----------------------------------------------------------

%%----------------------------------------------------------
\begin{figure}
    \centering
    \includegraphics[trim={0cm 6cm 0cm 5cm}, clip, width=.85\textwidth]{mps_sim.pdf}
    \caption{Forward modelled intensity maps for various science filters of SUIT.}
    \label{fig:flux_maps_filt}
\end{figure}
%%----------------------------------------------------------

We use 3D MHD model atmospheres simulated by \cite{rempel20} and 1.5D RT with MPS-ATLAS \citep[see e.g.,][for details]{anusha21} with measured filter profiles of {\suit}, to calculate the emergent intensity. The 3D MHD simulation employs a symmetric lower boundary condition for the magnetic field and a variety of initial magnetic field configurations to create small-scale variations and various levels of magnetization. The RT equation is solved using the method of ODFs, accounting for both continuum and line opacities within the concerned wavelength range. This takes into account both continuum and line opacity within the concerned wavelength range. Accurately accounting for the line opacity is one of the major challenges in synthesizing spectra over a broad wavelength range. In the ODFs method, the opacity is sorted without the information of the corresponding wavelength within small intervals of wavelengths known as bins. The geometric mean of the sorted opacity values for multiple sub intervals within a given wavelength bin is pre-tabulated over atmospheric parameters such as temperature, pressure and micro-turbulent velocities. During RT calculations, opacity is then interpolated for the required grid parameters of the atmospheric model. The primary goal of the ODF method is to significantly minimize the computational time required for RT calculations. This becomes particularly crucial when computing emergent spectra across numerous atmospheres, such as those arising from 3D MHD simulations.

\cite{anusha21} developed an optimized method using the MPS-ATLAS code that allows us to use an arbitrary filter profile instead of a rectangular filter profile. We use this method, with our measured effective area, to forward model intensity maps for NB01, NB02, NB05, NB06, NB07, BB01, BB02 and BB03 filter combinations that {\suit} is using.

We describe the end-to-end procedure in Figure~\ref{fig:flow}. The 3D MHD model atmospheres are sliced at various angles and interpolated to various Line of sight (LOS) angles. As described earlier, the ODF tables are generated for various atmospheric parameters, such as temperature, pressure and micro-turbulent velocities, for the measured science filter profiles. The generated ODF tables are used to solve the RT through the model atmosphere using the MPS-ATLAS code. This provides us the emergent intensity as a function of wavelength for all the rays of the model atmosphere. Integrating this intensity across the wavelength range, we determine the total emergent intensity for each filter.

Figure~\ref{fig:flux_maps} displays the {\suit}'s BB02 intensity maps obtained at various $\mu$ values, namely $\mu$~=~1.0, 0.8, 0.7 and 0.6, respectively. The spatial scale of the region is $(9~\textrm{Mm}\times9~\textrm{Mm})$ with $(512\times512)$ pixels, with a pixel size of $\simeq 0.025{\arcsec}/\textrm{pixel}$. This is at a much higher resolution than that of {\suit}, which is $\sim \textrm{0.7"/pixel}$. Moreover, these intensity maps do not include the effects of the instrument point spread function (PSF). Therefore,  we first need to convolve the computed intensity maps with the measured PSF of {\suit}, and then bin it to {\suit} plate scale to obtain synthetic observables that are comparable to {\suit} observations. Fig.~\ref{fig:flux_maps_filt} displays the simulated intensity maps for the {\suit} BB filters across the same MURaM cube.

We use the MURaM and MPS-ATLAS codes to forward model the observations for NB01, NB02, NB06, NB07, BB01, BB02 and BB03. We note that since the MURaM simulations studied here cannot be used for the chromospheric filters, namely NB03 (\ion{Mg}{2}~k), NB04 (\ion{Mg}{2}~h) and NB08 (\ion{Ca}{2}~k), we have used observations recorded by~{\it IRIS} to forward model the NB03 and NB04 filter observations.~{\it IRIS} also provides spectra corresponding to the continuum filter NB05. Hence, we forward model NB05, also using~{\it IRIS} observations. Forward modelling of SUIT observations using~{\it IRIS} data is straightforward as we do not need to use any MHD simulation cube and RT code. However, the convolution with the spatial PSF and the application of the spectral filter profile, etc. still must be carried out. For our analysis, we use dense raster scans from~{\it IRIS}. The dense rasters usually have $\sim$ 0.33{--}0.4 \arcsec per pixel spatial resolution. This spatial resolution is half of the pixel size of \suit. In addition to that, the 95\% encircled energy radius for most of the \suit~filter combinations is $\sim$ 2\arcsec. Hence, we can safely ignore the instrument characteristics of~{\it IRIS}. For the two filters where we are using~{\it IRIS} data, the bottom right box in Fig.~\ref{fig:flow} is replaced by~{\it IRIS} observations.

%%----------------------------------------------------------------------------
\begin{figure}
    \centering
    \includegraphics[trim={5cm 1cm 5cm 2.7cm},clip,width=0.85\textwidth]{BB3_convolve.pdf}
    \caption[The effects of convolution on the simulated BB03 intensity map]{The effects of convolution on the simulated BB03 intensity map. Panel a) MPS-ATLAS simulated BB03 intensity map. Panel b) convolved and binned BB03 intensity map. The normalized intensity variation along the horizontal and vertical black lines are plotted in panel c and d, respectively. The blue curves correspond to the simulated BB03 filter, whereas the orange curves correspond to convolved binned data.}
    \label{fig:BB3_conv}
\end{figure}
%%----------------------------------------------------------------------------

%%-------------------------------------------------------------------------
\subsection{{\suit} filters forward modeled with MPS-ATLAS}\label{sec:mps_contrast}
%%-------------------------------------------------------------------------

Following the procedure described above, we forward model the intensity maps in  NB01, NB02, NB06, NB07, BB01, BB02 and BB03. Since the spatial extent of the simulation box is much smaller compared to the size required to reliably convolve with the {\suit} PSF, we stitched the same simulated box multiple times to be able to convolve with the measured PSFs of SUIT. This could be done without problems due to the use of periodic boundary conditions in the MURaM simulation setup. Fig.~\ref{fig:BB3_conv}.a displays the stitched images obtained for BB03. In Fig.~\ref{fig:BB3_conv}.b, we display the corresponding image that is convolved with the PSF of the respective filter of SUIT and binned to its plate scale.

To compare the intensity contrast before and after the convolution, we plot intensity across a small part of the vertical (panel c) and a horizontal cut (panel d). The blue curves represent the intensity cut through the MPS-ATLAS simulated intensity maps, while the orange dashed curves are for convolved-binned intensity maps. The contrast variation across the cuts reproduces the intensity peaks and troughs in similar regions. These intensity cuts demonstrate that we can reproduce the intensity contrasts in the forward-modelled data with reasonably similar spatial positions. The forward-modelled observational features appear broader, with reduced contrast. This reduction in contrast, is anticipated given the difference in the plate scale of simulation and that of forward-modelled observations. The 95\% encircled energy is largely ~ 2{\arcsec} for most filter combinations (see Fig.~\ref{fig:psf_ese}). This would imply that the intensity from a point source would be redistributed to a circle of 2{\arcsec} radius. So, if we have two equally bright/dark point sources, they would be merged if the distance between them is 2{\arcsec} or less. Hence, we should be able to study contrast variation at the spatial scale of $\sim$ 2{\arcsec} using {\suit} observations. We have performed this exercise on all the filters corresponding to the photosphere and continuum and have obtained similar results.

%%----------------------------------------------------------------------------
\subsection{NB03 \& NB04}\label{sec:nb3_contrast}
%%----------------------------------------------------------------------------

As alluded earlier, to forward model NB03 and NB04 observations, we have used~{\it IRIS} archival data. The~{\it IRIS} obtains UV spectra with high spatial (0.33{--}0.4{\arcsec} per pixel), temporal (1s), and spectral resolution ($\sim$26 and $\sim$53~m{\AA}) and images of the scanned regions using the slit-jaw imager. In the spectral channels, the strongest lines that~{\it IRIS} regularly observes are \ion{C}{2}, \ion{Mg}{2} and \ion{Si}{4}. Here we use the very large and dense 320 step raster observation from 11th July, 2023 of a sunspot in AR 13363. The sunspot was located at the heliographic position of $\sim [-180\arcsec,-397\arcsec]$. The~{\it IRIS} raster had a FoV of $\sim [112\arcsec,175\arcsec]$. We use \textit{iris\_getwindata.pro} available in the \textit{sswidl} distribution to get the calibrated spectra over the raster FoV. This gives us the calibrated spectra for all the pixels in the raster FoV in units of $erg.cm^{-2}.s^{-1}.sr^{-1}.pix^{-1}$. We multiply the entire spectra of each pixel through the NB03 and NB04 effective area (see            
Fig.~\ref{fig:eff_area} panel b) and convolve with the measured PSF (see            Fig.~\ref{fig:psf_3d}) to forward model NB03, NB04 observations. Consequently, the observed intensity is,

$$DN_{NB03}~=~\int~{\it IRIS}\_spec(\lambda)~R_{NB03}(\lambda)~t~d\lambda$$
and 
$$DN_{NB04}~=~\int~{\it IRIS}\_spec(\lambda)~R_{NB04}(\lambda)~t~d\lambda$$

\noindent where $R_{NB03}$ and $R_{NB04}$ are the measured effective area for the respective filter combinations. Fig.~\ref{fig:nb3_conv}.a shows the~{\it IRIS} raster FoV intensity map in the \ion{Mg}{2}~k line. The~{\it IRIS} image convolved with NB03 (NB04) PSF and binned to the {\suit} plate scale is shown in Figs.~\ref{fig:nb3_conv}.b(c).

To compare the intensity contrast obtained from SUIT images with those from~{\it IRIS} observations, in Figs.~\ref{fig:nb3_conv}.e \& f, we plot the normalized intensity profiles along the vertical (panel d) and horizontal (panel e) lines shown in panels a, b and c for NB03 and NB04 as labelled. The horizontal white dotted line encounters a light bridge on the western end of the sunspot (marked with a white arrow in Fig.~\ref{fig:nb3_conv} panels a, b \& c). We see three dips in the intensity profile in Fig.~\ref{fig:nb3_conv} panel e, as the horizontal white dotted line encounters the sunspot thrice. In both panels d \& e, NB03 (orange dashed line) and NB04 (black dot dashed line) has a lower contrast (peak to trough variation) compared to~{\it IRIS} (red solid line) and NB04 (black dot-dashed line) contrast. This is in line with our measurements of the PSF for NB03 \& NB04, as the measured PSF for NB03 has a higher scatter component in the background compared to NB04 (see panel c \& d in Fig.~\ref{fig:psf_3d}, Fig.~\ref{fig:psf_3d}). Therefore,  NB03 has a higher radius for 95\% encircled count (see NB03 and NB04 in Fig.~\ref{fig:psf_ese}). A higher radius for 95\% encircled count results in lower contrast in the convolved mock NB03 map.

%%%%%%%%-----------------%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[trim={5cm 0.6cm 6cm 0cm},clip,width=0.85\textwidth]{nb3_conv_edit.pdf}
    \caption[Effects of convolution on the~{\it IRIS} raster observation with the NB03 \& NB04 PSF]{Effects of convolution on the~{\it IRIS} raster observation with the NB03 \& NB04 PSF. Original (panel a), convolved with NB03 PSF and binned to {\suit} plate scale (panel b), convolved with NB04 and binned (panel c)~{\it IRIS} intensity maps obtained in \ion{Mg}{2}~k. Normalized intensity variation along the vertical-solid (horizontal-dashed) white line marked in panel a, b \& c are shown in panel d (panel e). Red-solid curves correspond to original~{\it IRIS} image, orange-dashed curves correspond to mock NB03 and black dot-dashed curves correspond to NB04.}
\label{fig:nb3_conv}
\end{figure}
%%%%%%%%-----------------%%%%%%%%%%%%%%%

%%-------------------------------------------
\subsection{NB05}\label{sec:nb5_contrast}
%%-------------------------------------------

The NB05 channel (with the central wavelength at 283.2~nm) is also observed by~{\it IRIS}. Therefore, we use the~{\it IRIS} 2832~{\AA} window observation of the same AR~13363 mentioned in \S\ref{sec:nb3_contrast}. %We use \textit{iris\_getwindata.pro} to get the spectra of the pixels in the raster FOV in units of $erg.cm^{-2}.s^{-1}.sr^{-1}.pix^{-1}$. Similarly, the whole spectrum is passed through the measured NB5 effective area and convolved with the measured PSF. 
In Fig.~\ref{fig:nb5_conv}.a, we plot the integrated intensity of the~{\it IRIS} 2832~{\AA} window. In panel b we plot the same region passed through the NB05 effective area and convolved and binned to {\suit} plate scale. In panels c and d we plot the normalized~{\it IRIS} intensity (red solid line) and normalized {\suit} NB05 intensity (orange dashed line) along the white dashed line and blue solid line marked in panels a and b, respectively. The features marked (`1' \& `2') in panels a and b are also marked in the normalized intensity variation panel e. Although there is a significant loss in contrast, the features are still identifiable. As demonstrated previously, various features are reproduced in the same spatial location with reduced contrast.

%%%%%%%%-----------------%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[trim={0.5cm 0.2cm 2cm 0cm},clip,width=0.85\textwidth]{NB5_feature_1.pdf}
    \includegraphics[trim={2.7cm 0.2cm 3cm 2cm},clip,width=0.95\textwidth]{NB5_feature_2.pdf}
    \caption[Effects of convolution on the~{\it IRIS} raster observation with the NB05 PSF]{Effects of convolution on the~{\it IRIS} raster observation with the NB05 PSF. We plot the~{\it IRIS} raster intensity map obtained in 2832~{\AA} continuum in panel a and the convolved-binned intensity image in panel b. 
    The normalized intensity variation obtained from both images along the white-dashed and blue-solid lines are shown in panels c and d, where red solid lines correspond to the original~{\it IRIS} image and orange dashed lines correspond to the convolved-binned intensity map. The two thin features marked by `1' and `2' within the sunspot in panels a and b are also marked in the intensity variation plot.}
\label{fig:nb5_conv}
\end{figure}
%%%%%%%%-----------------%%%%%%%%%%%%%%%

We have also used a very large, dense 320-step raster observation from 20th July 2023 of a sunspot in AR 13376 to create the mock observation. The sunspot was located at the heliographic position of $\sim [-147",325"]$. The~{\it IRIS} raster had a field of view (FoV) $\sim [112",119"]$. As described earlier, we forward modeled SUIT observations in the NB05 passband for this region. In Fig.~\ref{fig:nb5_conv_1} panel a we plot the integrated map obtained in~{\it IRIS} 2832~{\AA} window. In panel b we plot the same region passed through the NB05 effective area and convolved-binned to the {\suit} plate scale. In panel c(d) we plot a cropped view of the sunspot in the southern part of the region in~{\it IRIS} 2832~{\AA} ({\suit}~NB05 convolved). The light bridge within this sunspot narrows in thickness as we move from the upper-left to the lower-right. We take multiple measurements close to one another and average them to calculate the thickness of the light bridge at some specific location. In the northern part, the lightbrdge is $\sim 2\arcsec$ thick in the~{\it IRIS} observation and 4$\arcsec$ in the mock NB05 observation (see upper set of white arrows in panels c and d). It narrows down to 1$\arcsec$ in the southern part in the~{\it IRIS} observation, and 1.8$\arcsec$ in the mock NB05 observation (lower set of white arrows).

We take a slice through the sunspot and the light bridge, marked with a vertical white line in Fig.~\ref{fig:nb5_conv_1} panel c. The intensity along this line for normalized~{\it IRIS} contrast (solid red line) and convolved NB05 contrast (dot-dashed blue line), is plotted in Fig.~\ref{fig:nb5_conv_1} panel e. The light bridge is marked with a black arrow in the intensity profile.

%%%%%%%%-----------------%%%%%%%%%%%%%%%
\begingroup
    \centering
    \includegraphics[trim={3cm 4cm 3cm 0cm},clip,width=0.85\textwidth]{suit_sunspot_part1.pdf} \\
    \includegraphics[trim={1cm 0.2cm 1cm 1cm},clip,width=0.85\textwidth]{suit_sunspot_contrast_2.pdf}
    \captionof{figure}[Effects of convolution on the~{\it IRIS} raster observation with the NB05 PSF]{Effects of convolution on the~{\it IRIS} raster observation with the NB05 PSF. Panel (a):~{\it IRIS} raster intensity in 2832~\AA\ continuum.A large sunspot with a thin, light bridge in the middle is present in the southern part of the region. Panel (b): The~{\it IRIS} raster observation in panel a convolved with the NB05 PSF (see fig.~\ref{fig:psf_3d} panel e). Panel (c) \& (d): Zoomed view of the larger sunspot in the South in~{\it IRIS} and the simulated \suit\ NB05 map, respectively. The light bridge in the middle of the sunspot is marked by a set of four white arrows. The thickness of the light bridge at two locations is marked in both the panels. The normalized intensity along the vertical  white line drawn in panel (c) is plotted in panel (e). The normalized intensity of the original~{\it IRIS} (mock NB05) observation is plotted in solid red (dot-dashed blue) line. The light bridge is marked in the intensity profile with a black arrow.}
    \label{fig:nb5_conv_1}
\endgroup
%%%%%%%%-----------------%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}\label{sec:con}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The observation of any optical telescope is convolved by the PSF of the telescope. The PSF represents the response of the optical system to a point source. It quantifies the extent of blurring of a point source when imaged through the optical system, as well as the effects of various components like scattering, diffraction, etc. We have applied the measured PSF at the \suit\ detector plane for various filter combinations to the emergent radiation from MURaM simulation cubes (computed by MPS-ATLAS) and to pre-existing~{\it IRIS} observations to create mock {\suit} observations. The {\suit} PSF in all of the filter combinations is highly peaked with a pedestal $\sim$ two orders of magnitude lower (see Fig.~\ref{fig:psf_3d}). In most of the filter combinations the 95\% encircled count radius is $\sim$ 1.4 {--} 2.5{\arcsec}. This would imply that two equally bright or dark features on the Sun $\sim$ 2{\arcsec} apart would be merged in the corresponding {\suit} observation. Hence, we could resolve features on a spatial scale of $>$ 2.5{\arcsec} for the corresponding filters in {\suit} observations. These projections are more relevant for line filters in {\suit} (e.g. NB03(\ion{Mg}{2} k), NB04(\ion{Mg}{2} h, NB08 (\ion{Ca}{2} h)), as it would exhibit more features in close proximity (bright points in ARs and QS, the plage regions around sunspots, small eruptions in ARs). These projections are made with the measured PSF at the center of the CCD. The PSF distortions increase gradually as we move away from the centre of the CCD, with more angular elongation.

We believe the forward modeling pipeline will help us simulate {\suit} observations from existing MHD simulations and compare them to real {\suit} observations to constrain current model parameters. The comparisons with forward-modelled mock {\suit} observation with real {\suit} observations over time would also provide useful insights into the degradation of the instrument with respect to the on-ground projections. The deconvolution algorithm would be useful to improve the contrast across {\suit} observations and spatially localize features more reliably on the solar surface.

### 2025-04-11 chapter5/chap5.tex
Local changes

\justifying

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{secc3_intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\suit~consists of two main sub-units: The \suit~optics package - comprising an off-axis Ritchey-Chr\'{e}tien telescope, and \suit~Electronics package - responsible for imaging with the telescope and communicating with the satellite. The main components of the \textit{SUIT} optics package include a multi-operation entrance door, a thermal filter to limit the amount of incoming sunlight, primary and secondary mirrors, a shutter mechanism to control exposure times, baffles to reduce stray and scattered light, a motorized filter wheel assembly, a piezoelectric focusing mechanism, and a CCD detector. Figure \ref{fig:suit} shows a schematic diagram of the telescope (For further details, please refer to \cite{suit_main}).

%%%%%%%%%%%%%%%%%%
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{SUITLayout.jpg}
    \caption{Schematic diagram of the \textit{SUIT} telescope.}
    \label{fig:suit}
\end{figure}
%%%%%%%%%%%%%%%%%%

\suit~observes the Sun in eleven spectral bands, of which three are broadband (referred to as BB) and eight are narrow bands (referred to as NB), as listed in Table~\ref{tab:science_filters}. These are used to image different heights of the solar atmosphere, from the photosphere to the chromosphere. In the wavelength range of interest, i.e., 200{--}400 nm, the solar flux increases by two orders of magnitude, as can be seen in the combined spectrum obtained from solar flux measured by SOLSPEC (see Fig.~\ref{fig:sun_spec}). {\bf Therefore, we must employ certain combination filters to control solar flux levels and achieve the best signal-to-noise ratio (SNR) at each bandpass within the nominal exposure time while maintaining the spectral purity of the passband by suppressing leakage of light from wavelength bands outside of the science interest.} These combination filters are listed in the second column of Table~\ref{tab:science_filters}. In total, \textit{SUIT} has 16 filters mounted on two filter wheels, each having eight slots. A given filter combination is achieved by rotating the two filter wheels independently and placing the desired filter combination in the beam path. {\bf For example, \textit{SUIT} uses BB1 as a combination filter for BB1, as this particular filter aims to measure the irradiance of the entire Herzberg Continuum. On the other hand, the NB8 filter aims to accurately observe the line core of the \ion{Ca}{2}~h line ($\sim$396.85~nm). Several strong flare lines close to the line core go into emission during a flare (e.g. $\mathrm{H\epsilon}$ at $\sim$ 397~nm). Combining NB08 with another NB8 results in lower SNR for a given exposure time, as opposed to combining it with a bandpass filter. But we decided to chose this combination for maintaining the spectral purity at the expense of cadence or SNR. Similar choices regarding spectral purity were made for the band NB7 (CN Band), where we specifically wanted to probe the CN band in the continuum. The position of the various filters on the filter wheel also plays an important role in dictating the cadence of the observations, e.g. the BB filters are usually not planned to be used in normal flare observations. So, the NB filters and their corresponding combination filters have to be arranged in such a way as to minimize the time taken to rotate the filter wheel, achieve the planned filter combination, and maintain an acceptable cadence. The choice of filter combination is a delicate optimization between suppressing the out-of-band leakage and achieving a reasonable SNR within an acceptable exposure time. Additionally, the positions of combination filters on the filter wheel must be chosen to minimize the time spent in rotating the filter wheels from one combination to other dictating the cadence of observation.}

%------------------------------------------------------------
\begin{figure}[ht!]
    \begin{center}
    \begin{tabular}{c}
    \includegraphics[trim={0.8cm 0.3cm 2cm 2.2cm},clip,width=0.8\linewidth]{solar_spec_3.pdf}
    \end{tabular}
    \end{center}
\caption[The solar spectrum obtained from SOLSPEC.]{The solar spectrum from SOLSPEC. Parts of the solar spectra marked in red show the wavelength range covered by {\suit}'s observation passbands. The inset plot shows a dramatic rise in solar irradiance within \suit's observation band. } 
\label{fig:sun_spec} 
\end{figure} 
%-----------------------------------------------------------

%-----------------------------------------------------------
\begin{table}[ht!]
\begin{center}
\resizebox{0.8\textwidth}{!}{%
\begin{tabular}{||l|c|c|c|r||}
\hline
\textbf{Science}  &	\textbf{Combination} &	\textbf{Central} & \textbf{Bandpass} &\textbf{Science} \\
\textbf{Filter}	&	\textbf{Filter}     &	\textbf{Wavelength  (nm)}	&		\textbf{(nm)	}	   	&\textbf{target}		\\
\hline
NB1     & BB1 		& 214.0 		    & 11.0 		& Continuum\\
NB2 	& BP2		& 276.7				& 0.4 		& Mg~\rm{II}~k blue wing \\
NB3 	& BP2		& 279.6 			& 0.4 		& Mg~\rm{II}~k\\
NB4 	& BP2		& 280.3				& 0.4 		& Mg~\rm{II}~h\\
NB5		& BP2		& 283.2				& 0.4 		& Mg~\rm{II}~h red wing\\
NB6 	& BP3		& 300.0 			&1.0 		& Continuum\\
NB7 	& BP3		& 388.0				&1.0 		& CN Band\\
NB8		& NB8		& 396.85 			& 0.1 		& Ca~\rm{II}~h\\
BB1 	& BB1		& 220.0				& 40.0		& Herzberg Continuum \\
BB2 	& BP4		& 277.0 			& 58.0       & Hartley Band\\
BB3 	& BP4		& 340.0				& 40.0        & Huggins Band\\
\hline
\end{tabular}}
\end{center}
\caption[Science filters on-board {\suit}]{List of science filters on board \suit. Columns from left to right denote filter mnemonics (including science and combination filters; NB: Narrowband, BB: Broadband, BP: Bandpass), central wavelengths for science filters and corresponding bandpasses, and the observation interest for the filter.} 
\label{tab:science_filters}
\end{table}
%-----------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis of Spacecraft jitter simulation for {\suit}}\label{sec:suit_jitter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

One of the key steps in estimating the imaging performance was to quantify if the RMS level of spacecraft jitter would affect the imaging across various exposure times. For this purpose, we analyzed the simulated spacecraft drift data provided by the ISRO URSC team to quantify the RMS jitter as a function of exposure time. Two main moving components within the payload can generate significant jitter on the payload, namely the shutter vane and the filter wheel (FW) movement. The spacecraft has a filter wheel movement torque compensator in place to minimize the jitter generated by the FW movement. So, four main scenarios were simulated to be analyzed, arranged from least to most amount of jitter:

%%%
\begin{enumerate}
    \item No shutter torque + no filter movement
    \item Only shutter torque
    \item Shutter torque + FW movement + FW compensation torque
    \item Shutter torque + FW movement + no FW compensation torque
\end{enumerate}
%%%

%%%%%%%%
\begin{figure}[ht!]
    \centering
    \includegraphics[trim={1cm 0cm 1cm 1cm},clip,width=0.9\textwidth]{jitter_sim.pdf}
    \caption[Simulated drift for the yaw, roll and pitch axis as a function of time.]{The simulated drift for the yaw (blue solid), roll (red dashed) and pitch (green dot-dashed) axis of the payload as a function of time for the aforementioned four cases in \S\ref{sec:suit_jitter} in the four panels respectively as marked.}
    \label{fig:jitter_sim}
\end{figure}
%%%%%%%%

The Fig.~\ref{fig:jitter_sim} shows the simulated drift for the aforementioned four cases. We did a Fourier analysis of the simulated drift data to characterize the spacecraft jitter from the spacecraft drift. The Fig.~\ref{fig:jitter_sim_ps} shows the power spectrum for the simulated drift shown in Fig.~\ref{fig:jitter_sim}. The SUIT imaging channels have a maximum possible exposure$~\sim$~1.4 s, which corresponds to a frequency of~$\sim$~0.7 Hz and lower exposures would correspond to a higher frequency. So, signals in the Fourier transform corresponding to 0.7 Hz or higher are capable of affecting the imaging within the exposure window. We assumed any signal with a frequency 0.5 Hz or greater from the Fourier transform to be Jitter signal. We then took a frequency cut at 0.5 Hz, of the power spectrum to filter the drift from the jitter and then took an inverse FT to reconstruct the jitter signal for the three axis. To calculate the amount of RMS jitter on various time scales relevant in the context of SUIT exposure times, we took the extracted jitter signal and picked out bins of multiple time scales and calculated the RMS jitter for them. We had several bins for each time scale, each of which gave us RMS jitter and maximum jitter within that bin. We averaged all the bins to estimate the RMS jitter and maximum Jitter for that specific timescale. Figures \ref{fig:rms_jitter} ad \ref{fig:max_jitter} shows the RMS and maximum jitter as a function of timescale. SUIT has a 0.7\arcsec/pix resolution. Both the average and the maximum jitter even in the worst case scenario, i.e when shutter torque and FW movement is present but the FW movement compensation is not employed, is much lower than the pixel size of SUIT within timescales relevant to exposure times for SUIT. We did not need to account for the jitter while characterizing the imaging performance.

%%-----------------------------%%
\begin{figure}[ht!]
    \centering
    \includegraphics[trim={0cm 0cm 1cm 1cm},clip,width=0.9\textwidth]{jitter_psd.pdf}
    \caption[Fourier transform of the simulated drift for the yaw, roll and pitch axis.]{Fourier Transform of the simulated drift for the yaw (blue circle), roll (red triangle) and pitch (green square) axis of the payload as a function of time for the aforementioned four cases in \S\ref{sec:suit_jitter} in the four panels respectively as marked.}
    \label{fig:jitter_sim_ps}
\end{figure}
%%-----------------------------%%

%%-----------------------------%%
\begin{figure}[ht!]
    \centering
    \includegraphics[trim={0cm 0cm 1cm 1cm},clip,width=1.0\textwidth]{rms_jitter.pdf}
    \caption{The RMS jitter at various timescales for the four scenarios of operation as labelled.}
    \label{fig:rms_jitter}
\end{figure}
%%-----------------------------%%

%%-----------------------------%%
\begin{figure}[ht!]
    \centering
    \includegraphics[trim={0cm 0cm 1cm 1cm},clip,width=1.0\textwidth]{max_jitter.pdf}
    \caption{The Maximum jitter at various timescales for the four scenarios of operations as labelled.}
    \label{fig:max_jitter}
\end{figure}
%%-----------------------------%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Throughput model of {\suit}}\label{sec:suit_throughput}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The design of the \suit~telescope prioritizes throughput and photometric accuracy requirements. Optical parameters of various optical elements, such as the reflectivity of primary and secondary mirrors, transmission of the thermal filter, field corrector lens, spectral transmission of the science filter, and combination filter, are optimized to maximize throughput within their corresponding wavelength ranges.

The optical response of \suit~is evaluated based on the solar spectral irradiance and the throughput characteristics of each sub-assembly. Experimental throughput data is compared with a throughput model to validate the consistency between experimental and simulated results. This validation process is crucial for determining exposure times for the payload across the eleven science bandpasses in different operational modes.

The throughput of \suit~is modeled using the Sun-as-a-Star spectrum to predict counts for specific science filter combinations. The measured wavelength responses of individual components are utilized to estimate these counts. If the photon flux incident at the entrance aperture is denoted by $P(\lambda)$, then the recorded data number in the images can be expressed as:

%%%%%%%%%
 \begin{equation}\label{eq1}
     DN~=~\int~P(\lambda)~R(\lambda)~t~d\lambda
 \end{equation}
 %%%%%%%%%
where $R(\lambda)$ is the effective area for the specific science filter combination, and $t$ is the exposure time for that filter. The effective area $R(\lambda)$ is derived by multiplying the measured response of all the optical sub-assemblies in the beam path-

%%%%%%%%%
\begin{equation}
    R(\lambda)~=~TF(\lambda)\times PM(\lambda)\times SM(\lambda)\times SF_{i}(\lambda)\times SF_{j}(\lambda)\times L(\lambda)\times QE(\lambda)\times A
    \label{eq:eff_area}
\end{equation}
%%%%%%%%%
where $TF(\lambda), PM(\lambda), SM(\lambda), SF_{i}(\lambda), SF_{j}(\lambda), L(\lambda)~and~QE(\lambda)$ are the measured responses as a function of wavelength of thermal filter, primary mirror, secondary mirror, filters in filter wheel 1 and 2, field corrector lens and the quantum efficiency of the CCD. The effective area curves for each filter are shown in Fig.~\ref{fig:eff_area}.

%%%%%%%%%%%
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{eff_area.pdf}
    \caption{The effective area curves for SUIT science filters.}
    \label{fig:eff_area}
\end{figure}
%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Choice of Science filters for {\suit}}\label{sec:sc_filt_choice}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

One of the key uses of the throughput model is that it allows us to predict the average count from a Sun as a star spectra. under certain assumptions, we can then estimate how much SNR we can expect from the darkest features, {\it e.g.} sunspots on the sun. The science filters for {\suit} were manufactured by Materion Corp. As mentioned in Tb.~\ref{tab:science_filters}, the eleven bandpasses are achieved by combining eight science filters with four distinct combination filters (three bandpasses and two science filters combined with themselves). Materion manufactured several copies of each filter. We chose the best-performing ones out of these, which would eventually mounted on the payload. The selection for the filters was mainly based on the following three criteria:

%%%%%%%%%%
\begin{itemize}
    \item The cosmetics of the filters. The intended transmission for individual filters is achieved with custom coating. We would like to choose filters with the least amount of pinholes, scratches and digs, {\it i.e.} cosmetic damages on the coating. Along with this, we also do not use the filters that have pinholes in the same location on both sides of the filter.
    \item The average SNR for a Sun as a star observation. We choose the filters with higher average SNR for the filter combinations.
    \item We choose the filters with the least amount of out-of-band flux. The out-of-band is defined by wavelength range outside of the 99\% effective area about the peak wavelength. 
\end{itemize}
The choice of filter profiles should be an optimization of these 3 criteria.
%%%%%%%%%%%

%%-----------------------------------%%
\subsection{Exposure Time Calculation}
%%-----------------------------------%%
One of the key requirements to calculate the SNR for any science filter combination is to calculate the necessary exposure time, for that specific combination. For example, if we require an SNR of 100 in the dark regions and `N' is the total photo electron count in some exposure time `$\mathrm{t_{e}}$', then,

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{align*}
    & \mathrm{\frac{N}{\sqrt{N}} = 100} \\
    \implies & \mathrm{\sqrt{N} = 100} \\
    \implies & \mathrm{N = 10^{4}} \\
    \implies & \mathrm{photoelctron~per~second~in~dark~featurs \times t_{e} = 10^{4}} \\
    \implies & \mathrm{t_{e} = \frac{10^{4}}{photoelctron~per~second~in~dark}}
\end{align*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

However, this does not take into account the amount of out-of-band leakage, which is going to contribute to the SNR being the dominant component in the noise. If we incorporate that into the calculation, we can increase the amount of exposure time required to reach the highest possible SNR as long as we do not exceed the maximum exposure time 1.4 seconds. So now,

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{align}
    & \mathrm{\frac{N}{\sqrt{N}+Leakage~in~dark} = SNR_{max}} \notag \\
    \implies & \mathrm{\frac{photoelctron~per~second~in~dark \times t_{e}}{\sqrt{photoelctron~per~second~in~dark \times t_{e}}+leak~per~second~in~dark \times t_{e}} = SNR_{max}} \notag \\
    \implies & \mathrm{\frac{photoelctron~per~second~in~dark \times \sqrt{t_{e}}}{\sqrt{photoelctron~per~second~in~dark}+leak~per~second~in~dark \times \sqrt{t_{e}}} = SNR_{max}} \notag \\
    \implies & \mathrm{t_{e} = \frac{SNR_{max}^{2} \times photoelctron~per~second~in~dark}{(photoelctron~per~second~in~dark-SNR_{max} \times leak~per~second~in~dark)^{2}}} \notag\\
\end{align}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the limit, $$\mathrm{leak~per~second~in~dark \to 0}$$ this expression reduces to $\mathrm{t_{e} = \frac{SNR_{max}^{2}}{photoelctron~per~second~in~dark}}$. With this definition of exposure time we calculate the SNR for all the filter combination.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Filter Choice for BB2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This section details the selection process for the BB2 filters, which was also applied to the other passbands. Figure~\ref{fig:bb2_cosmetics} presents the cosmetics spreadsheet provided by the vendor. The defects in the coating were characterized based on their nature and size, such as digs, pinholes, and scratches. In Figure~\ref{fig:bb2_cosmetics}, several pinholes are marked with red circles for BB2 filter serials \#1, 2, and 5. Filters \#3 and 4 are in better condition in terms of the cosmetics of the coating.

\begin{wrapfigure}{r}{0.45\textwidth}
    \centering
    \vspace{-20pt} % Adjust vertical spacing here
    \resizebox{0.45\textwidth}{!}{%
    \begin{tabular}{||c|c|c|c|c|c||}
        \hline
        BP4  & BB2 & BB2 & BB2 & BB2 & BB2 \\
        Filter choice & \#1 & \#2 & \#3 & \#4 & \#5 \\
    \hline
    \hline
      \#4 & 48 & 66 & 68 & 67 & 66 \\
      \#2 & 47 & 64 & 66 & 66 & 64 \\
      \#3 & 48 & 65 & 67 & 67 & 65 \\
      \hline
    \end{tabular}}
    \captionof{table}{SNR for various choices of BB2 filters}
    \label{tab:bb2_snr}
    \vspace{-10pt} % Adjust vertical spacing here
\end{wrapfigure}

The table~\ref{tab:bb2_snr} shows the SNR at the dark features on sun, calculated using a sample spectra and measured response for BB2 filters. Based on the cosmetic quality rest of the BB2 filters \#3 and 4 were already more preferred. Similarly in this case also they show a better SNR compared to the rest of the filters. A similar cosmetic quality inspection was done for BP3 filters. After combining all these information, finally BB2 \#3 was chosen to be mounted on the spacecraft. Similar analysis was done for all possible combinations of the science filters to finally choose the ones to be mounted. 
%and performance data, filters \#3 and 4 were selected for BB2. The selection process considered both the cosmetic defects and the optical performance criteria.

%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[trim={1cm 6cm 1.2cm 2cm}, clip, width=0.8\linewidth]{bb2_cosmetics.pdf}
    \caption{Materion provided cosmetics report for various option of BB2 filters.}
    \label{fig:bb2_cosmetics}
\end{figure}
%%%%%%%%%%%%

%\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Photometric Calibration and Spectral Validation {\suit}}\label{sec:suit_radiometric}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%To achieve the scientific goals, photometric and spectral calibration of the payload is of utmost importance. The photometric throughput of the telescope is modeled during instrument design to ensure the required photometric throughput accuracy of 1\%. For this purpose, Light of a known wavelength and measured intensity is fed into the payload from a monochromator after collimation. The payload is operated in a vacuum chamber to simulate space-like conditions in this setup. For the details of the experimental setup refer to \cite{sarkar24}. We use these measurements and compare them with our throughput model to validate the measurements of the transmission profiles. We also use these measurements to validate the spectral transmission profile of the science filter channels.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Photometric Calibration}\label{sec:calibration}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%In this test, an optical fiber is used to feed light from the monochromator at the focal plane of the SUIT collimator. The monochromator uses a grating with a density of 1200 lines per mm (lpmm) and a nominal dispersion of 1.44 nm/mm, blazed at 500 nm. The spectral resolution of the monochromator depends on the entrance slit or the exit slit, whichever is geometrically wider. In our case, an entrance slit width of 3 mm is used to maximize the light output from the spectrograph. The emergent monochromatic light has a wavelength band of \(3 \times 1.44 = 4.32\) nm. This wavelength band accommodates the complete transmission spectrum of all the narrow band science filters being tested. The fiber carries light from the monochromator, which is collimated and fed into~\suit.

%A UV-enhanced photo diode, certified by the National Institute of Science and Technology (NIST) as traceable (specifically the Newport 918D-UV-OD3R model), is used to quantify the net output flux of the collimator. Both the monochromator and photo diode are set to align with the wavelength corresponding to the science filter under test. It's noteworthy that the Xenon lamp's spectral intensity remains stable within a 4.32 nm band, exhibiting a flat profile. By dividing the measured photo diode's output flux(\(nWm^{-2}\)), by the wavelength band of the spectrograph, we derive the spectral flux from the collimator(\(Wm^{-2}nm^{-1}\)). Following this, the photo diode is removed from the beam path, and an image of the fiber bundle is captured using \suit. The fiber face is obscured to record the background value, and another exposure is initiated. These findings are directly comparable with the modeled throughput derived from the Sun-as-a-Star spectrum for various filter wavelength bands. The following steps are followed to do that:

%\begin{itemize}
 %    \item The background count is estimated by taking the median of the fiber occulted image.
  %   \item From the background corrected optical fiber images, we calculate the 99\% ensquared energy radius and the total enclosed data counts ($DN_{0.99}$).
   %  \item The photo diode gives the measurement of corresponding input flux ($E_{0.99}$) in units of $nW.m^{-2}$ for an input spectral bin of 4.32 nm. The flux is divided by the spectral bin size to get the spectral irradiance per unit area in units of $nW.m^{-2}.nm^{-1}$. The ratio of $DN_{0.99}$ and ${E_{0.99}}$ tells the expected counts for any given input flux, $F~=~\nicefrac{DN_{0.99}}{E_{0.99}}$ in units of $DN.s^{-1}/(nW.m^{-2}.nm^{-1})$ for that science filter bandpass.
    % \item We use a composite SOLar STellar Irradiance Comparison Experiment (SOLSTICE; 115{--}320 nm) onboard the SOlar Radiation and Climate Experiment (SORCE) \cite{rottman05,harder05,mcclintock05} satellite and SOLar SPECtrometer (SOLSPEC) \cite{thuillier09} solar spectrum as our standard for solar radiation. Using the spectra, we can calculate the total energy input from the Sun for the concerned filter within the wavelength extent, $E_{\odot}~=~\int_{\lambda_{1}}^{\lambda_{2}}~P(\lambda)~d\lambda$, where $P(\lambda)$ is the SOLSTICE, SOLSPEC composite solar spectrum. Here, $\lambda_{2}-\lambda_{1}$ is the extent of the concerned band.
     %\item Using eqn.\ref{eq1} along with the aforementioned spectrum, we can calculate the expected count observed (i.e., $DN_{throughput}~=~\int~P(\lambda)~R(\lambda)~t~d\lambda$) for a given filter combination.
     %\item $F~=~\nicefrac{DN_{0.99}}{E_{0.99}}$ is multiplied with the total energy input from the Sun ($E_{\odot}$) for the concerned filter to find the photo electrons collected per second ($DN_{measured}~=~E_{\odot}\times~F$).
 %\end{itemize}

%In Table~\ref{tab:throughput}, we present a comparison between the solar counts derived from our measurements and those calculated from the throughput model for specific filter combinations. It's noteworthy that NB01, BB01, and BB02 have transmission below 250~nm. The atmosphere significantly attenuates UV light below this wavelength as it passes through the monochromator and collimator, resulting in insufficient signal strength for measurement. Moreover, the radiance of the Xenon light source increases nearly linearly by 60 times between 200~nm and 300~nm, and then remains relatively constant up to 400~nm. Consequently, this phenomenon leads to an inadequate signal-to-noise ratio (SNR) in the output during photometric calibration and spectral validation for these filters.

%Our findings indicate that the measured data counts per second align within a 20\% margin of those derived from the throughput model (refer to Table \ref{tab:throughput}), except for NB07. One possible explanation for this discrepancy lies in the utilization of SOLSPEC data for modeling the throughput beyond 310~nm, while SOLSTICE data is employed for modeling throughput below this threshold. It's worth noting that SOLSPEC data provides a resolution of 0.05~nm, unlike SOLSTICE data, which offers a finer resolution of 0.025~nm. Consequently, this discrepancy leads to reduced accuracy in the modeled data counts for filters operating beyond 310 nm.

%-----------------------------------------------------------
%\begin{table}[ht]
%\begin{center}
%\resizebox{\textwidth}{!}{%
%\begin{tabular}{||c|c|c|c||}
%\hline
%Science & Counts calculated & Counts calculated & Ratio of \\
%filter & from measurement & from throughput model &  \\
 %& $DN_{measured}~=~E_{\odot}\times~F$ & $DN_{throughput}~=~\int~P(\lambda)~R(\lambda)~t~d\lambda$ & $\frac{DN_{measured}}{DN_{throughput}}$\\
 %& ($Data~number~s^{-1}$) & ($Data~number~s^{-1}$) & \\
%\hline
%NB03 & 18531 & 15520 & 1.19 \\
%NB04 & 35040 & 36717 & 0.95 \\
%NB05 & 124116 & 131625 & 0.943 \\
%NB06 & 105138 & 107064 & 0.98 \\
%NB07 & 750744 & 391364 & 1.91 \\
%NB08 & 26523 & 24096 & 1.1 \\
%BB03 & 511722 & 434532 & 1.18 \\
%\hline

%\end{tabular}}
%\end{center}
%\caption{Comparison of the data numbers derived from throughput model (using SOLSTICE and SOLSPEC data) with the data numbers inferred from the measurements.} 
%\label{tab:throughput}
%\end{table}
%-----------------------------------------------------------

%Surprisingly, the modeled counts for NB08, despite falling beyond 310 nm, do not exhibit significant deviation. This can be attributed to the extremely narrow bandpass of NB08, which is merely 0.01 nm wide and centered at the prominent Ca-II h spectral line. Conversely, BB03 features a broader effective bandpass of 40 nm, rendering the model less sensitive to minor fluctuations in the sparsely sampled SOLSPEC solar spectrum. Consequently, this results in comparable data counts per second to those observed in the laboratory.

%To validate this hypothesis, we compare the throughput modeled for the NB06 filter using lower-resolution SOLSPEC data with that calculated using higher-resolution SOLSTICE data. From Table \ref{tab:throughput}, it is evident that the ratio of measured to modeled throughput for NB06, when modeled using higher-resolution SOLSTICE data, is 0.98. However, when the NB06 throughput is modeled using lower-resolution SOLSPEC data, the obtained ratio is approximately 1.8, similar to what is observed for NB07 throughput modeled with SOLSPEC data. Hence, the high ratio for NB07 in Table \ref{tab:throughput} can be attributed to the sparsely populated SOLSPEC data used for modeling the throughput.

%################################### 
%\subsection{Full Payload Spectral Validation}\label{valid}
%###################################

%Spectral validation is aimed at confirming the transmission profile of the \textit{SUIT} payload with various science filters across different wavelengths within their respective bandpasses. Light from the monochromator is collimated and directed into the payload, as previously described. The wavelength band of the light source is selected to allow for multiple measurements to be taken at non-overlapping wavelength bins within the transmission band of a given filter. A holographic grating with a density of 2400 lines per mm (lpmm), blazed at 220 nm, is employed in the monochromator. The nominal dispersion of this grating is 0.74 nm/mm. The entrance slit width of the monochromator is configured to be 200 microns, resulting in a wavelength bin size of (0.74 nm/mm $\times$ 0.2 mm = 0.148 nm). This light is then introduced into the payload, and readings are acquired across the transmission spectrum of the science filter, ensuring that adjacent readings remain independent of each other. The total energy is quantified at each measured wavelength, allowing for the spectral response of the entire telescope across the concerned filters to be determined.

%Subsequently, the entrance slit width of the monochromator is enlarged to 3 mm, and the light output is gauged from the clear aperture of the collimator using the NIST traceable photo diode to validate the spectral flux being supplied to the \textit{SUIT} payload. This data serves as a basis for obtaining photometric calibration to match the measured spectral flux. For further details of the experimental setup refer to \cite{sarkar24}. The following steps were followed to perform the spectral validation:

 %%%%%%%%%%
 %\begin{itemize}
 %\item Like image acquisition during photometric calibration - the fiber face is opened and closed consecutively to record light from the data and the contribution from the background.
 %\item The median value of the background image is subtracted from the fiber image, and we calculate the radius, which encircles 99\% of the total intensity contributed by the fiber bundle in the corrected image.
 %\item The total counts within the 99\% ensquared energy radius ($C_{i}$) is calculated in units of ADC counts/s.
 %\item The corresponding energy input is derived from photo-diode measurement ($E_{i}$) in units of $nW.m^{-2}.nm^{-1}$.
 %\item The same measurement can be carried out for various wavelength points within the bandpass of the concerned filter combination. The ratio of these two quantities, $F_{i}~=~\frac{C_{i}}{E_{i}}$ yield the spectral calibration for that filter combination in units of $\nicefrac{ADC~counts.s^{-1}}{nW.m^{-2}.nm^{-1}}$ as a function of wavelength.
 %\end{itemize}
 %%%%%%%%%%

%In Fig.~\ref{fig:nb2_images}, we show the captured images for the NB02 filter combination at various wavelengths of incident light. The same was performed for all other filter combinations. The measurement wavelength and the calculated 99\% ensquared energy radius are quoted at the top of each panel. We plot the spectral validation results of all filter combinations with transmission bandpasses above 250 nm in Fig.~\ref{fig:sepc_calib}. The \textit{x} and \textit{y} error bars in Fig.~\ref{fig:sepc_calib} represent wavelength bins for the given input slit size and the Poisson uncertainty of the measured ADC counts, respectively. The plots demonstrate that the measured shape of the instrument spectral response agrees well with the modeled spectral response for all filter combinations with transmission bandpass above 250 nm.

%We could not carry out the spectral characterization for the NB08 filter due to the appearance of multiple strong ghost reflections close to the central patch. It is to be noted that the bandpass for NB08 is facilitated by a stack of two filters, which, unlike other filters, have no relative tilt between them, resulting in strong ghost reflections. These affect the estimation of ensquared energy across the transmission bandpass, affecting spectral validation results for this filter.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}
%\begin{center}
%\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=0.9\linewidth]{nb2_images_edit.pdf}
%\end{center}
%\caption[Images captured at various wavelengths for the NB02 filter of SUIT.]{\label{fig:nb2_images} Images captured at various wavelengths for the NB02 filter of \suit. The measurement wavelength and the 99\% ensquared energy radius are quoted at the top of each panel. The axes of the images are in units of image pixels.} 
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}
%\begin{center}
%\includegraphics[trim={2.1cm 3.2cm 1.2cm 5.2cm},clip,width=0.95\textwidth] {spec_calib_new.pdf}
%\end{center}
%\caption [Spectral validation for various filter combination passbands inferred from the imaging measurements (blue markers)]{Spectral validation for various filter combinations inferred from the imaging measurements (blue markers). The wavelength bins give the $x$ errors for the given input slit size. The Poisson uncertainty of the measured ADC counts gives the $y$ errors. The red solid curve shows the effective area calculated from measured transmission profiles of each component using Eqn \ref{eq:eff_area}.}
%\label{fig:sepc_calib}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%In Fig. \ref{fig:nb8_ghost} (a), we depict the fiber image captured at 396.85 nm. The position of the central image of the fiber, along with the sparsely spaced ghost reflections, is delineated by a white dashed box. Fig. \ref{fig:nb8_ghost} (b) offers a magnified perspective of this box, revealing the sparsely shaped ghost reflections indicated by white arrows. Some ghost reflections are observed very close to the central patch. Fig. \ref{fig:nb8_ghost} (c) provides a closer view around the central patch, with solid and dotted arrows indicating two closely spaced ghost reflections situated very close to the center. Given that these ghost reflections appear in proximity to the central patch and the relative brightness of the central patch to the ghost reflections fluctuates with wavelength, the estimation of the 99\% ensquared energy radius is also influenced.

%%%%%%%%%%%%%%
%\begin{figure}[ht!]
 %   \centering
  %  \includegraphics[width=0.8\textwidth]{nb8_ghost_im.pdf}
   % \caption[The ghost reflections of the optical fiber as seen with the NB08 filter.]{(a) The ghost reflections of the optical fiber as seen with the NB08 filter. The input beam is centered at 396.85 nm. The position of the ghost reflections is marked with a white dashed box. (b) The zoomed-in view of the white dashed box. The arrows indicate sparsely spaced ghost reflections. (c) The arrows indicate two closely spaced ghost reflections close to the center. (d) 99\% ensquared energy box around the fiber bundle at 396.85 nm. (e) 99\% ensquared energy box around the fiber bundle at 396.60 nm.}
    %\label{fig:nb8_ghost}
%\end{figure}
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Calibration of  {\suit}}\label{sec:stellar_calib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To address these scientific objectives as outlined in \S\ref{sec:suit}, the necessity of absolute stellar calibration is manifold. \suit, with its capabilities, images the Sun and dynamic processes such as solar flares and jets occurring in the solar atmosphere, including eruptions of various scales. Additionally, these images assist us in measuring solar spectral irradiance across 11 different passbands in the NUV. With absolute calibration, we would be able to probe the underlying physical mechanisms driving these processes and can derive the spectral energy distribution in absolute units.

Many properties of white-light flares are also observable in the near-ultraviolet (NUV) regime. Typically, there are significant correlations between different flare quantities in white light and X-ray emissions, such as white-light excess and soft X-ray flux \citep{benz16,hudson16}. These correlations enable us to infer underlying mechanisms that likely drive the correlation between these quantities, such as the mechanisms responsible for transferring energy and mass across different layers of the Sun. In our case, \suit~would observe the Sun alongside HEL1OS and SoLEXS \citep{solexs}. For comparative purposes across observations from three different instruments, absolute calibration becomes essential.

Furthermore, in conjunction with \suit, the HEL1OS and SoLEXS data provide broad coverage of the electromagnetic spectrum from hard X-rays to the NUV. This comprehensive coverage allows us not only to study the initiation and triggering of eruptive events but also to examine these quantities over a solar cycle and assess their contribution to changes in the solar spectral irradiance. Lastly, it's important to note that the Earth's atmosphere absorbs UV and X-ray emissions. UV radiation below 310 nm is largely absorbed by the atmosphere, while radiation beyond 310 nm can penetrate it. The absorption dynamics are primarily governed by oxygen ($O_{2}$) below 200 nm and ozone ($O_{3}$) beyond 240 nm, with both substances actively participating in the absorption process between 200 and 240 nm \citep{haigh07}. Therefore, understanding the solar spectral irradiance in the 200-400 nm range is pivotal for comprehending the dynamics and chemistry of Earth's atmosphere, particularly the ozone-oxygen cycle. This data is a crucial input for atmospheric modelling and provides insights into the Sun-Earth atmosphere connection. With absolute stellar calibration, \textit{SUIT} would furnish us with the solar irradiance in these bands and the radiance of various features on the solar disk before it encounters atmospheric attenuation.

{\suit} is equipped with 16 calibration LEDs, 8 each emitting at peak wavelengths 258nm and 356nm, respectively. However, it's worth noting that LEDs may degrade over time and do not offer fluxes corresponding to each individual filter. We have obtained measurements of the flux-to-count ratio at various wavelengths within the extent of the science filter bands. This data will undoubtedly assist us in providing absolute calibration to \suit~observations. Nevertheless, while we can quantify how the overall throughput of the science filter combinations changes over time, we cannot quantify how the effective area of the science filter combination degrades as a function of wavelength. This degradation would impact the radiometric calibration using these measurements over time. Therefore, calibration through alternative methods is necessary, such as utilizing standard astronomical sources.

In an ideal scenario, the captured image would remain unaltered, devoid of any artefacts introduced by the instrument. However, in practice, the obtained image is influenced by the instrument response, which can degrade over time. Radiometric calibration involves quantifying the instrumental response and using it to predict the actual signal received from the source.

Furthermore, \suit~ lacks in-band spectral resolution and lacks an accurate on-board calibration lamp corresponding to the wavelength coverage of each individual filter. Therefore, it becomes imperative to convert the total in-band photo-electron count to the corresponding energy in real units. This necessity arises because photons across a wide band possess varying energy levels, making it challenging, if not impossible, to ascertain the distribution of photo-electrons across a wavelength band.

In principle, for any astronomical source, we encounter,

%------------------------------------------------------------
\begin{equation*}
    \mathrm{DN(\lambda) = R(\lambda) \times F(\lambda)}
\end{equation*}
%------------------------------------------------------------

where $\mathrm{F(\lambda)}$, $\mathrm{DN(\lambda)}$ and $\mathrm{R(\lambda)}$ are the emitted {\bf photon} flux, measured signal and the response of the system at the wavelength $\lambda$, respectively. Here, $R(\lambda)$ (instrument response) will consist of the response from all the components of the telescope, namely the thermal filter, the primary and secondary mirrors, the science filter in conjunction with the bandpass filer, the focusing lens, the QE and the electronics efficiency of the detector (a CCD in this case). In the case of a standard source, we can write,

%------------------------------------------------------------
\begin{align*}
    &\mathrm{DN(\lambda)_{calib} = R(\lambda)_{calib} \times F(\lambda)_{calib}} \\
    \implies &\mathrm{R(\lambda)_{calib} = \frac{DN(\lambda)_{calib}}{F(\lambda)_{calib}}}
\end{align*}
%------------------------------------------------------------

\noindent where the subscript `calib' denotes all variables related to the standard absolute calibration source. The parameter $\mathrm{R(\lambda)_{calib}}$ represents a calibration factor acquired by observing a standard source using an instrument. Photon flux {\bf from a source} can be straightforwardly computed from an absolutely calibrated spectrum {\bf $\mathrm{S(\lambda)}$ using the formula $\mathrm{F(\lambda) = S(\lambda) \times \frac{\lambda}{hc}}$.}

Similarly, for the target source under observation, we have,

%------------------------------------------------------------
\begin{align}
    &\mathrm{DN(\lambda)_{target} = R(\lambda)_{target} \times F(\lambda)_{target}} \nonumber \\
    \implies &\mathrm{F(\lambda)_{target} = \frac{DN(\lambda)_{target}}{R(\lambda)_{calib}}}
\end{align}
%------------------------------------------------------------
where, it is assumed that the instrumental response remains unchanged from the calibrated source to the target source being observed, and hence $\mathrm{R(\lambda)_{target}=R(\lambda)_{calib}}$.

%------------------------------------------------------------
\subsection{Requirements of the calibration source} \label{req}
%------------------------------------------------------------

In general, for radiometric calibration, on-board standard sources such as diodes, LEDs, etc., or astronomical sources like standard stars are employed. However, in a space-based mission, the on-board artificial sources themselves undergo significant degradation, which needs to be meticulously modeled. Therefore, it is preferable to utilize standard stars as calibration sources, provided they satisfy the essential conditions listed below \citep{article2}.

%%%%%%%%%%%%%%%
\begin{itemize}
    \item The calibration source must exhibit adequate brightness within the wavelength region of interest, which spans from 200 to 400 nm in the current context, to achieve the requisite photometric accuracy across all science filters. In our case, the thermal filter at the entrance aperture significantly attenuates in-band solar flux (along with nearly all out-band flux) reaching the detector to prevent pixel saturation. This mechanism applies equally to the calibration sources. Hence, the calibration source must possess sufficient brightness to attain an acceptable signal-to-noise ratio (SNR) within a reasonable observation time.
    \item Ideally, the standard calibration source should exhibit minimal variability, with any changes occurring over timescales significantly longer than the time required to accumulate a sufficient number of photons from the source to achieve the desired level of photometric accuracy.
    \item  Preferably, the calibration source should not be integrated into a complex system. However, if it is, any accompanying components should be sufficiently weak so that the photon flux from them does not significantly contribute to the total flux of the system. Otherwise, it would be necessary to model the contribution of the companion(s) separately.
\end{itemize}
%%%%%%%%%%%%%%%

Any astronomical source that meets these criteria and has its spectral energy distribution (SED) studied and calibrated to absolute units would be suitable for radiometric calibration. Stars such as Sirius A (HD48915/HR2491) and Vega (HR7001) largely fulfill the aforementioned criteria, with the exception of Sirius A, which has a white dwarf companion known as Sirius B. However, the apparent magnitudes of Sirius A and Sirius B are $-1.46$ \citep{hoffleit91} and $8.44$ \citep{mccook99,holberg13} respectively, ensuring that the contribution from Sirius B is mostly negligible. The absolute calibrated spectra for both stars are depicted in Fig.~\ref{fig:spec_1} and are sourced from the CALSPEC archive, which contains composite stellar spectra used as flux standards in the Hubble Space Telescope (HST) system.

%------------------------------------------------------------
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\linewidth]{spectrum_sir_veg.pdf}
    \caption[Spectra of Vega and Sirius A]{Calibrated spectra of Vega and Sirius A taken from \href{https://www.stsci.edu/hst/instrumentation/reference-data-for-calibration-and-tools/astronomical-catalogs/calspec}{CALSPEC}, Vega in Blue and Sirius A in Orange.}
    \label{fig:spec_1}
\end{figure}
%------------------------------------------------------------

%------------------------------------------------------------
\subsection{Exposure time for the calibration sources}\label{expo_time}
%------------------------------------------------------------

A high level of photometric accuracy is essential for imaging the Sun and monitoring spectral irradiance. It's noteworthy that the total energy output from the Sun at wavelengths below 400 nm comprises only about 8\% of the total solar irradiance (TSI). However, there is a recorded variability of over 60\% in radiation below 400 nm over a solar cycle \citep{krivova06}, whereas the variability in TSI over a solar cycle is approximately 0.1\%. Photometric accuracy is defined as the ratio of the Poisson noise of the signal to the signal itself. The number of photo-electrons produced in a given exposure time is given by Eqn.~\ref{eq1},\ref{eq:eff_area}. We aim for a photometric accuracy of 0.2\%, which corresponds to a photo-electron count of $\sim 2.5 \times 10^{5}$. Considering this requirement, we compute the exposure times required for both Vega and Sirius A, which are given in Table~\ref{tab_2}.

%-------------------------------------------------
\begin{table}[ht!]
\centering
\resizebox{0.7\textwidth}{!}{%
\begin{tabular}{ccccc}
\hline
        & Exposure time(minutes) & Exposure time(minutes) \\
        Band & Vega & Sirius A\\
        \hline
        NB1 & 8 & 2\\
        NB2 & 23 & 6\\
        NB3 & 23 & 6\\
        NB4 & 19 & 5\\
        NB5 & 16.5 & 4\\
        NB6 & 15 & 3.5\\
        NB7 & 12 & 3\\
        NB8 & 368 & 90\\
        BB1 & 2 & 0.5\\
        BB2 & 20 & 5\\
        BB3 & 13 & 3\\
        \hline
    \end{tabular}}
    \caption{The exposure time required to obtain $2.5 \times 10^{5}$ photo-electrons to achieve 0.2\% photometric accuracy in each of the science filters for both Vega and Sirius A.}
\label{tab_2}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Method for Calibration}\label{cal_meth}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

With the exposure times calculated for all filters, for calibration purposes, we will assume a photometric accuracy of 0.2\% across all bands for the calibration source. This implies that the Poisson noise arising from the total photo electron count is 0.2\%, corresponding to a total photo electron count of approximately $2.5 \times 10^{5}$. As described in Section \ref{sec:stellar_calib}, the flux from the target source is given by $F(\lambda)_{\text{target}}=\frac{S(\lambda)_{\text{target}}}{R(\lambda)_{\text{calib}}}$, where we assume that the instrumental response $R(\lambda)_{\text{calib}}$ remains unchanged from the calibration source to the target source. Therefore, given a calibration source using the absolute spectra ($F(\lambda)_{\text{calib}}$) and the signal ($S(\lambda)_{\text{calib}}$) received from it, we can quantify the telescope responses at various bandpasses ($R(\lambda)_{\text{calib}}$).

In the case of \suit, though there is no spectral resolution within the bands, and the only information we will obtain from an observation is the total number of photo electron counts from the bands for a given exposure time. The general method is as follows:

\begin{itemize}
    \item Given the spectra of a calibration source one can create the photo elctron count profiles using the instrument filter profiles.

    \item One can calculate the total number of photo elctrons generated for some exposure time as:
    \begin{equation*}
        DN_{calib} = \int P(\lambda)_{calib\hspace{0.1cm}}R(\lambda)\hspace{0.1cm}A\hspace{0.1cm}t\hspace{0.1cm} d\lambda
    \end{equation*}
    \noindent where, $P(\lambda)$ is the photon flux from the Calibration source.

    \item The inband energy from the spectra of the calibration source for the same exposure time can be calculated. The FWHM is taken to be the extent of each band while calculating the total energy.
    \begin{equation*}
        T_{calib} = \int_{inband} F(\lambda)_{calib}\hspace{0.1cm} A\hspace{0.1cm}t\hspace{0.1cm} d\lambda
    \end{equation*}
    \item The ratio of these two quantities give the calibration constant, `C' for each band, C = $\frac{T_{calib}}{DN_{calib}}$
\end{itemize}

To estimate how well this method performs, we use Vega (Sirius~A) as the calibration source and produce the phtoelctron count profiles from Sirius~A (Vega) and the Sun. The total count arising from each band multiplied by the calibration constant(C) should give the total energy from the spectra.

%------------------------------------------------------------
\subsection{Sirius A as calibration source}\label{sirius}
%------------------------------------------------------------

Table~\ref{tab:my_table_sun_sir} shows the performance of the method for a Sirius A as the calibrating source and sun as a target with 200s exposure in all bands. The uncertainties in the table~\ref{tab:my_table_sun_sir} are obtained by propagating the uncertainties of the \href{https://www.stsci.edu/hst/instrumentation/reference-data-for-calibration-and-tools/astronomical-catalogs/calspec}{CALSPEC} spectra. Key thing to note here, the comparisons for solar spectra are made with a sun as a star spectra, while SUIT is going to observe the full solar disk on $(4k \times 4k)$ CCD. We have to add the contribution from all the pixels to have the full disk contribution. In practice, in the stellar pointing calibration run \suit~will be re-pointed towards Sirius A and the measurements would be used for absolute calibration.

%------------------------------------------------------------
\begin{table}[ht!]
\small
\centering
\resizebox{0.9\textwidth}{!}{%
    \begin{tabular}{|ccccc|}
    \hline
        Band & $(C=\frac{T_{sir}}{DN_{sir}})\times 10^{15}$ & DN/$10^{13}$ & Predicted Energy & Energy from \\
         & (J/DN) & & ($C \times DN$) & spectra(J) \\
        \hline
        \hline
        NB1 & $(72.62\pm0.88)$ & $(9.47 \pm 9.7 \times 10^{-7})$ & $(6.881 \pm 0.083)$ & 6.839\\
        \hline
        NB2 & $(5.164\pm0.062)$ & $(20.6\pm1.4\times10^{-6})$ & $(1.065\pm0.013)$ & $1.072$\\
        \hline
        NB3 & $(3.627\pm0.044)$ & $(10.5\pm1.0\times10^{-6})$ & $(3.854\pm0.043)\times10^{-1}$ & $3.884\times10^{-1}$ \\
        \hline
        NB4 & $(3.253\pm0.039)$ & $(12.3\pm1.1\times10^{-6})$ & $(4.003\pm0.048)\times10^{-1}$ & $(4.001\times10^{-1})$ \\
        \hline
        NB5 & $(3.160\pm0.038)$ & $(40.6\pm2.0\times10^{-6})$ & $(1.284\pm0.016)$ & $1.307$ \\
        \hline
        NB6 & $(7.295\pm0.088)$ & $(65.7 \pm 2.6 \times 10^{-6})$ & $(4.797\pm0.058)$ & $4.836$ \\
        \hline
        NB7 & $(8.715\pm0.010)$ & $(123 \pm 4 \times 10^{-6})$ & $(1.073\pm0.013)\times10^{1}$ & $1.055\times10^{1}$ \\
        \hline
        NB8 & $(17.71\pm0.21)$ & $(5.01 \pm 7.1 \times 10^{-7})$ & $(8.88\pm0.11)\times10^{-1}$ & $8.93\times10^{-1}$ \\
        \hline
        BB1 & $(28.50\pm0.41)$ & $(46.0 \pm 2.1 \times 10^{-6})$ & $(13.114\pm0.188)$ & 13.113 \\
        \hline
        BB2 & $(469.9\pm5.7)$ &$(28.3 \pm 1.7 \times 10^{-6})$ & $(132.997\pm1.607)$ & 132.994 \\
        \hline
        BB3 & $(221.1\pm2.7)$ & $(176 \pm 4 \times 10^{-6})$ & $(3.903\pm0.047)\times10^{2}$ & $3.896\times10^{2}$\\
        \hline
    \end{tabular}}
    \caption{The performance of the method with Sirius A as calibrating source and sun as a target with 200s exposure in all bands.}
\label{tab:my_table_sun_sir}
\end{table}
%------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Filter Choice for {\suit}}\label{sec:suit_filter_choice}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Discussion}\label{sec:c3_outlook}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\suit~is our first full-disk eye on the Sun in \ion{Mg}{2} window and \ion{Ca}{2} h line and the various continuum channels onboard. The narrow band continuum and line channels provide us with a targeted view into various layers of the solar atmosphere, while the three broadband channels are designed to probe the radiance from the Sun to investigate the effect of NUV radiation on Earth's atmosphere over the duration of a solar cycle. This chapter focused on the various initial preparatory analysis we carried out in anticipation of \suit, and some of the calibration scheme planning initially carried on.

The initial jitter estimation was done from simulations provided by the ISRO URSC team. That exhibited the jitter to be minimal compared to \suit~exposure timescales, hence would have no noticeable effects on the imaging. Properly estimating the spacecraft jitter in orbit would be possible once the stellar calibration is done. During the stellar calibration, the long exposure of Sirius-A, {\it, i.e.} a point source, would be carried out in a series of short exposures. This would give us the opportunity to quantify the amount of jitter in the spacecraft.

The initial throughput model of \suit~was designed out of the necessity of a robust throughput model to estimate the expected SNR of various vendor-provided science filters, according to the scientific cases. It proved useful in finalizing the choice of the science filters to be mounted on the payload. The throughput model also proved useful in designing our stellar calibration scheme and provided a useful benchmark for validating the photometric performance of the payload on the ground. The spectral validation of the science filters is important primarily for verifying the science filter combinations are observing the necessary wavelength windows. The necessity of an accurate throughput model, spectral and photometric validation of the payload, and stellar calibration of the payload are intertwined with one another. A full characterization of all of these quantities is only possible after stellar calibration is carried out.

### 2025-04-11 chapter6/chap6.tex
Local changes

--- 2024-08-14 chapter5/ms.tex
@@
 %%---------------------------------------------------------------
-\begin{equation*}
-\Omega_{ij}=\frac{8\pi}{\sqrt{3}}~\frac{I_{H}}{\Delta \epsilon_{ij}}g\omega_{i}~f_{ij}
-\end{equation*}
+\begin{equation}
+\mathrm{\Omega_{ij}=\frac{8\pi}{\sqrt{3}}~\frac{I_{H}}{\Delta \epsilon_{ij}}g\omega_{i}~f_{ij}}
+\end{equation}
 %%---------------------------------------------------------------
 
-\noindent Here, $I_{H}$ denotes the ionization energy of hydrogen, $\Delta \epsilon_{ij}$ represents the threshold energy for the transition, $g$ is the Gaunt factor, $\omega_{i}$ is the statistical weight of the level, and $f_{ij}$ stands for the oscillator strength.
+Here, $I_{H}$ denotes the ionization energy of hydrogen, $\Delta \epsilon_{ij}$ represents the threshold energy for the transition, $g$ is the Gaunt factor, $\omega_{i}$ is the statistical weight of the level, and $f_{ij}$ stands for the oscillator strength.
 In optically thin conditions, the intensity ratio of the k to h line equals the ratio of collision strengths, as the escape probability of photons is unity.
 As the  \ion{Mg}{2} k and h lines share the same ionization state and originate from a transition to a shared lower level, and given that the statistical weight ($\omega_{i}$) is the same in both cases, the line intensity ratio is simply the ratio of oscillator strengths ($f_{ij}$).
-Consequently, this ratio is expected to be 2:1 in optically thin conditions and lower when the medium is optically thick \citep{kerr15,levens19}.
+Consequently, this ratio is expected to be 2:1 in optically thin conditions \citep{kerr15,levens19}.{\bf For further details on the ratio of the oscilator strengths please refer to \S\ref{sec:a1}.}
+
+{\bf Under optically thick conditions the radiation is absorbed and re-emitted more effectively by the medium.
+As a result the radiation field in the medium becomes "thermalized", meaning the population of the energy levels are dictated by the Boltzmann distribution, rather than the specific radiative process or the specific line strengths.
+As a result the intensity of the lines are no longer individually dependent on their Einstein coefficients or the detailed radiative processes but are instead controlled by the overall temperature and the combined behavior of the radiation field in an optically thick medium.
+This leads to a situation where both the upper levels for the \ion{Mg}{2}~k~and~h lines are very similar, as they are formed at relatively similar heights.
+So the intensity ratio is closer to 1:1 \citep{kerr15, levens19}.
+This ratio has been used before to comment on the opacity of the local plasma environment.
+It has been demonstrated from previous solar observations, that the \ion{Mg}{2} lines exhibit no central reversal $\sim$ 6\arcsec~above the limb, and $\sim$ 12\arcsec~above the limb the line intensity ratio is 2:1, implying that the lines become optically thin \citep{doschek_n_feldman_77, feldman_n_doscheck_77}.
+on the contrary, \cite{kneer81} showed from sunspot spectra, although the \ion{Mg}{2} lines show no central reversal, the ratio was still lower 2:1, implying optically thick conditions.
+}
 
@@
     \centering
-\includegraphics[trim={7cm 5cm 7.7cm 6cm},clip,width=\textwidth]{Figures/Flare_M_Nov04_2015_2.eps}
-\caption{The M3.7 flare observed on November 4th, 2015.
+\includegraphics[trim={0.4cm 7cm 2.5cm 6.5cm},clip,width=\linewidth]{Figures/Flare_M_Nov04_2015_2.pdf}
+\caption[The observations of the M3.7 flare on November 4th, 2015]{The M3.7 flare observed on November 4th, 2015.
 Panel a: GOES flux plot in 0.5{--}4~{\AA} (blue) and 1.0{--}8.0~{\AA} (red).
@@
     \begin{center}
-    \includegraphics[width=\textwidth]{Figures/nov_flare_304_aa_evolv.eps}
+    \includegraphics[trim={1cm 1.2cm 1cm 2.3cm}, clip, width=\textwidth]{Figures/nov_flare_304_aa_evolv.eps}
     \end{center}
-    \caption{Sequence of AIA 304~{\AA}~images for the Nov 4th, 2015 flare.
+    \caption[Sequence of AIA 304 {\AA} images for the Nov 4th, 2015 flare.]{Sequence of AIA 304~{\AA}~images for the Nov 4th, 2015 flare.
 The white dotted box shows the portion of the IRIS raster FOV which scanned the ribbons.
@@
     \begin{center}
-        \includegraphics[trim={4.5cm 5.5cm 6cm 4cm},clip,width=\textwidth]{Figures/nov_flare_aia_waves_2.pdf}
+        \includegraphics[trim={4.7cm 5.5cm 6.5cm 4.2cm},clip,width=\textwidth]{Figures/nov_flare_aia_waves_2.pdf}
     \end{center}
-    \caption{The Nov 4th, 2015 flare in the six Coronal channels of the SDO/AIA at the soft X-ray peak (panels (a)-(f)) and during the decline phase (panels (g)-(l)) of the flare.}
+    \caption[The six coronal channel observations from SDO/AIA for the Nov 4th, 2015 flare.]{The Nov 4th, 2015 flare in the six Coronal channels of the SDO/AIA at the soft X-ray peak (panels (a)-(f)) and during the decline phase (panels (g)-(l)) of the flare.}
     \label{flare_m_aia}
@@
 \includegraphics[trim={7cm 5cm 6cm 15cm},width=0.7\textwidth]{Figures/m_flare_iris.pdf}
-\caption{Obtained images in  \ion{Mg}{2} h (panel a) and k (panel b) and corresponding co-aligned and artificially rastered HMI LOS magnetic field map (panel c) for the M3.7 flare observed on November 4th, 2015.
+\caption[\ion{Mg}{2}~h and k line intensity observation with artificially rastered HMI LOS magnetic field for the November 4th, 2015 flare.]{Obtained images in \ion{Mg}{2}~h (panel a) and k (panel b) and corresponding co-aligned and artificially rastered HMI LOS magnetic field map (panel c) for the M3.7 flare observed on November 4th, 2015.
 The magenta and lime green contours on panel c show the contours of  \ion{Mg}{2}~h (panel a) and k (panel b) intensity.} \label{fig:aligned_raster}
@@
     \includegraphics[trim={0cm 3cm 0.5cm 3cm},clip,width=\textwidth]{Figures/pix_fit.pdf}
-    \caption{Fit of the  \ion{Mg}{2} window for the pixel marked in northern ribbon (southern ribbon) in Fig.~\ref{fig:aligned_raster} in top panel (bottom panel) from various times during the evolution of the flare.
+    \caption[Fit of the \ion{Mg}{2}~window for a pixel.]{Fit of the \ion{Mg}{2} window for the pixel marked in northern ribbon (southern ribbon) in Fig.~\ref{fig:aligned_raster} in top panel (bottom panel) from various times during the evolution of the flare.
 }
@@
 \includegraphics[trim={1.5cm 4cm 0.5cm 4cm},clip,width=0.8\textwidth]{Figures/m_flare_iris_pt2.pdf}
-\caption{The 1{--}8~{\AA} GOES light curve of the flare over-plotted with the time variation of  \ion{Mg}{2} k/h line intensity ratio for the northern (black) and southern (green) asterisks marked in panels a, b \& c.}
+\caption[The 1{--}8~{\AA} GOES light curve of the flare over-plotted with the time variation of \ion{Mg}{2}~k/h line intensity ratio.]{The 1{--}8~{\AA} GOES light curve of the flare over-plotted with the time variation of  \ion{Mg}{2} k/h line intensity ratio for the northern (black) and southern (green) asterisks marked in panels a, b \& c.}
 \label{fig:aligned_iris_ratio}
@@
     \includegraphics[trim={8cm 1cm 2cm 0.2cm},clip,width=0.9\textwidth]{Figures/Flare-m-optical-depth-2.jpeg}
-    \caption{ \ion{Mg}{2} k to h line intensity ratio for various magnetic flux density bins at various time steps during the evolution of the flare.}
+    \caption{\ion{Mg}{2}~k to h line intensity ratio for various magnetic flux density bins at various time steps during the evolution of the flare.}
     \label{fig:optical_depth_m}
@@
     \includegraphics[trim={3cm 3cm 2cm 4cm},clip,width=\textwidth]{Figures/Nov-11-2015-optical-dep-ev-5.pdf}
-    \caption{Time evolution of the  \ion{Mg}{2} k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin as labeled for the Nov 4, 2015 flare.
+    \caption[Time evolution of the \ion{Mg}{2}~k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin.]{Time evolution of the \ion{Mg}{2}~k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin as labeled for the Nov 4, 2015 flare.
 For better visibility, the 20.9{--}184.4 G and 348.9{--}513.3 G points are offset by 30s and -30s respectively.
@@
     \centering
-\hspace*{-.5in}
-\includegraphics[width=\textwidth,trim={7cm 5cm 7.7cm 6cm},clip]{Figures/Flare_X_oct22_2014_2.eps}
-\caption{The X class flare observed on October 22, 2014.
+\includegraphics[width=\textwidth,trim={0.5cm 7cm 3cm 4.5cm},clip]{Figures/Flare_X_oct22_2013.pdf}
+\caption[The observations of the X flare on November 4th, 2015]{The X class flare observed on October 22, 2014.
 Panel a: GOES flux plot in 0.5{--}4~{\AA} (blue) and 1.0{--}8.0~{\AA} (red).
@@
 %    \hspace{2in}
-    \includegraphics[trim={6cm 3cm 6cm 3cm},clip,width=0.45\textwidth]{Figures/contour_paper_plot_oct28.pdf}
-    \includegraphics[trim={3cm 2cm 2cm 3cm},clip,width=0.45\textwidth]{Figures/Oct-22-2014-optical-dep-ev-2.pdf}
-    \caption{Obtained intensity maps in  \ion{Mg}{2}~k (panel a) and h (panel b) lines at the peak of the flare.
-The rastrered HMI LOS magnetic field density map is shown in panel c.
-The black and lime green contours on panel c show the contours of  \ion{Mg}{2}~k (panel a) and h (panel b) intensity.}
+    \includegraphics[trim={0.1cm 0.2cm 8cm 0.2cm},clip,width=0.5\textwidth]{Figures/contour_paper_plot_oct28.pdf}
+    \includegraphics[trim={0.1cm 1cm 0.1cm 1cm},clip,width=0.7\textwidth]{Figures/Oct-22-2014-optical-dep-ev-2.pdf}
+    \caption[Top panel: \ion{Mg}{2}~h and k line intensity observation with artificially rastered HMI LoS magnetic field for the October 22, 2014 flare.]{Obtained intensity maps in  \ion{Mg}{2}~k (panel a) and h (panel b) lines at the peak of the flare.
+The rastrered HMI LoS magnetic field density map is shown in panel c.
+The black and lime green contours on panel c show the contours of  \ion{Mg}{2}~k (panel a) and h (panel b) intensity.
+Bottom panel: Time evolution of the \ion{Mg}{2}~k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin as labeled for the Oct 22, 2014 flare.
+The over-plotted red solid line displays the 1{--}8~{\AA} GOES X-ray light curve.}
 \label{fig:align_raster_flare2}
@@
     \centering
-\hspace*{-.6in}
-\includegraphics[width=1.12\textwidth,trim={7cm 5cm 7.7cm 6cm},clip]{Figures/Flare_C_feb03_2015_2.eps}
+\includegraphics[width=\textwidth,trim={0cm 4.5cm 3cm 4cm},clip]{Figures/Flare_C_feb03_2015.pdf}
 %\includegraphics[width=.7\textwidth]{figures/Feb_03_2015/Feb-04-2015-optical-dep-ev-2.eps}
-\caption{The C class flare observed on February 3rd, 2015.
+\caption[The observations of the X flare on February 3rd, 2015.]{The C class flare observed on February 3rd, 2015.
 Panel a: GOES flux plot in 0.5{--}4~{\AA} (blue) and 1.0{--}8.0~{\AA} (red).
@@
 %\hspace*{-1.in}
-\includegraphics[width=0.5\textwidth,trim={4cm 5cm 4cm 4cm},clip]{Figures/contour_paper_plot_feb-03-2015.pdf}
-\caption{Obtained intensity maps in  \ion{Mg}{2}~k (panel a) and h (panel b) lines at the peak of the flare.
+\includegraphics[width=0.7\textwidth,trim={4cm 5cm 4cm 4cm},clip]{Figures/contour_paper_plot_feb-03-2015.pdf}
+\caption[\ion{Mg}{2}~h and k line intensity observation with artificially rastered HMI LOS magnetic field for the February 3rd, 2015 flare.]{Obtained intensity maps in  \ion{Mg}{2}~k (panel a) and h (panel b) lines at the peak of the flare.
 The rastrered HMI LOS magnetic field density map is shown in panel c.
@@
     \includegraphics[trim={2cm 3cm 2cm 3cm},clip,width=0.8\textwidth]{Figures/Feb-04-2015-optical-dep-ev-2.pdf}
-    \caption{Time evolution of the  \ion{Mg}{2} k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin as labeled for the Feb 3, 2015 flare.
-Over-plotted red solid line displays the 1{--}8~{\AA} GOES X-ray light curve.}
+    \caption[Time evolution of the \ion{Mg}{2}~k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin for the February 3rd, 2015 flare.]{Time evolution of the \ion{Mg}{2}~k to h line intensity ratio obtained from averaged spectrum over the corresponding magnetic flux bin as labeled for the Feb 3, 2015 flare.
+The over-plotted red solid line displays the 1{--}8~{\AA} GOES X-ray light curve.}
     \label{fig:optical_dep_ev_c}
@@
 %%--------------------------------------------------
-\section{Outlook}
+\section{Summary and Discussion}
 %%--------------------------------------------------
@@
 The  \ion{Mg}{2}~k to h line intensity ratios serve as a valuable diagnostic for assessing the opacity of the local plasma and can provide insights into changes in the local plasma environment within the solar chromosphere during flares.
-In this study, we investigated the temporal variation of  \ion{Mg}{2}k to h line intensity ratios during the evolution of three flares classified as X-class, M-class, and C-class.
+In this study, we investigated the temporal variation of  \ion{Mg}{2}k to h line intensity ratios during the evolution of three X-class, M-class, and C-class flares.
 We also examined the variation of intensity ratios across different magnetic flux density bins, utilizing observations from IRIS and HMI.

### 2025-04-11 chapter7/chap7.tex
Local changes

\justifying

%%----------------------------------------------------
\section{Introduction} \label{sec:intro}
%%----------------------------------------------------

Flares are the largest magnetic event in our solar system. They are characterized by the explosive release of magnetic free energy and localized heating in the solar atmosphere. They manifest differently across various wavelengths. The footpoints of the post flare loops are visible in hard X-ray, for electrons and $\gamma$-rays, for ions. In contrast, the loops are filled with plasma emitting in soft X-ray and Extreme Ultraviolet (EUV) \citep{fletcher11}. The corresponding white light and Near Ultraviolet (NUV) counterparts arise due to changes in ionization and local opacity in the photospheric and chromospheric heights. These are usually some of the most impulsive signatures of flares \citep{watanabe17,hudson06}. The NUV and white light emission have also been demonstrated to be co-spatial and co-temporal with hard X-ray \citep{hudson92, oliverso12}. One of the major puzzling aspects regarding the origin and energetics of solar flares is the origin of the white light (WL) continuum. According to the standard model of flares, the energetic electrons are accelerated along the loops and are stopped via numerous collisions and thermalization when the ambient medium has enough density, usually known as the `thick target' model (For further details, please refer to \cite{brown73,benz17,fletcher11}). We usually believe that these densities are reached within the chromosphere. This explains the co-spatial and co-temporal nature of WL and Hard X-ray. The theory, on the other hand, predicts parts of the WL being created in the upper photosphere, depths inaccessible to electrons in the standard `thick-target' model.

There have been various attempts to modify the thick target model to account for various observations from solar flares, e.g. a warm target model \cite{kontar15,kontar19}, local re-acceleration of electrons \citep{brown73}, acceleration of protons along with electrons which are expected to penetrate deeper. There were also attempts to explain the source of WL with photospheric `back-warming' \citep{metclaff90}, where the upper photosphere is ionized via energy transported radiatively from the chromosphere. There have been several observations where the WL emission has been associated with enhancement observed in the 2832~{\AA} continuum of IRIS SJI \citep{heinzel14,kleint16,kleint17,kowalski17,kowalski19}. In this paper, we discuss the {\suit} observations of the February 22, 2024, X-class flare. Continuum bright kernels were observed in the red wing (283~nm) and blue wing (276~nm) of the Mg window. To the best of our knowledge, this is the first observation of continuum enhancement of the blue wing of Mg window. The rest of the paper is structured as follows: in \S\ref{sec:obs} we discuss the observations of the flare from various observatories, i.e, {\suit}, IRIS, GOES and STIX. In \S\ref{sec:bright_ker}, we discuss the observations specifically related to the penumbral bright kernels and how they compare across various wavelengths. In \S3, We summarize our findings and discuss the implications it can have regarding our understanding of the origin of WL emission is solar flares.

%%%%%%% ############# %%%%%%%
\section{Observation \& Data Analysis}\label{sec:obs}
%%%%%%% ############# %%%%%%%

NOAA AR 13590 was visible on the north-east of the Solar disk on February 22, 2024. The AR was around a large sunspot in a cluster of sunspots, accompanied by a complex magnetic field structure. The active region flared multiple times during the same day, including an X1.7 flare that peaked around $\sim$ 06:32 UT, an M4.8 flare that peaked around $\sim$ 20:46 UT and an X6.3 flare that peaked $\sim$ 22:34 UT . {\suit} is equipped with an onboard flare detection algorithm. Once the flare detection algorithm flags a flare and localizes the position of the flare on the detector, the program sequence prioritizes reading a fixed smaller Region of Interest (RoI) around the location for fast, higher cadence observation (for further details, please refer to \cite{flare_det}). The X6.3 flare was one of the first flares to be flagged by the on-board flare detection algorithm. {\suit} did not observe the X1.7 flare because, during that time, the payload was off-pointed to verify the stellar calibration program sequences. The flares were also observed by {\it SDO}/AIA, {\it SO}/STIX. {\it IRIS} observed the eastern edge of the X6.3 flare ribbons in a small [66",62"] field of view (FoV) with a 4-step raster and 15 s raster cadence.

%%%%%%%%%%%%%%%%%%%
\begin{figure*}
    \centering
    \includegraphics[trim = {2cm 2.5cm 2.8cm 1.8cm}, clip, width=\linewidth]{Figures/feb_22nd/fig_1.pdf} 
    \caption[SUIT observation of the flare at the respective peak of all filters]{(a) Parts of the full-disk (2k$\times$2k) observation in NB4 (Mg II h) showing the flaring region and sunspot. The dashed magenta box marks the extent of the {\suit} RoI used for the subsequent analysis. {(b)} Cropped observation of the flare from the magenta dashed box in (a), from various science filters of \suit. Two bright umbral kernels are marked in NB2 and NB5 with blue arrows.}
    \label{fig:flare_obs}
\end{figure*}
%%%%%%%%%%%%%%%%%%%

Fig.~\ref{fig:flare_obs}a shows a cutout of the full-disk (2k$\times$2k) observation in NB4 (Mg II h). The magenta dashed box shows the region considered for the subsequent analysis in this paper. We plot the observation from the dashed magenta box marked in Fig.~\ref{fig:flare_obs}a in various \suit~narrow bands during their respective peaks in Fig.~\ref{fig:flare_obs}b. The NB2 (Mg II blue wing), NB3 (Mg II k), NB4 (Mg II h) and NB5 (Mg II red wing) cover the entire Mg window. NB7 and NB8 show the continuum on the red side of the Balmer jump and the Ca II h line, respectively. We see two kernels of umbral brightening during the respective peaks of NB2 and NB5 (marked by white and black arrows in Fig.~\ref{fig:flare_obs}b respectively).

The X6.3 flare provides a good example of the response of the local plasma environment to the flare in the NUV regime in 200 {--} 400 nm. The flare peaked around $\sim$ 22:34 UT in the {\it GOES} observation. Images from six narrow band (NB) channels of {\suit} are shown in Fig.~\ref{fig:flare_obs}c at around $\sim$ 22:28-22:29 UT. This is at the peak of the NB3 (Mg II k 279.6 nm) channel, as observed by \suit. The 60\% peak intensity contour of the NB3 intensity is marked with the black line in all figures of Fig.~\ref{fig:flare_obs}c. From the figure, we also see a similar structure in the NB4 (Mg II h 280.3 nm) and NB8 (Ca II h 396.9 nm). No similar structure is observed in the other continuum channels of Fig.~\ref{fig:flare_obs}c.

%%%%%%%%%
\begin{figure*}
    \centering
    \includegraphics[trim={0.2cm 2.5cm 2cm 4cm},clip,width=\linewidth]{Figures/feb_22nd/suit_roi_nb3_peak.pdf}
    \caption[{\suit} observations of the flare from various NB filters during NB3 peak]{{\suit} observations of the flare from various NB filters during NB3 peak. 60\% peak intensity contour of NB3 is marked across the NB filter observations.}
    \label{fig:flare_nb3_peak}
\end{figure*}
%%%%%%%%%

In Fig.~\ref{fig:flare_lc_suit}.a, we show the GOES 1 {--} 8 {\AA} light curve in comparison to the peak normalised NB3, NB4 and NB8 light curves. All the NB light curves behave remarkably similarly. The vertical dotted black line across all the panels in Fig.~\ref{fig:flare_lc_suit} denotes the peak intensity in NB3. NB3, NB4, and NB8 peaks at the same time around $\sim$ 22:29 UT. We co-align and co-register {\it GONG}-H$\alpha$ observation with SUIT observations and plot the light curve from the same contour region. The {\it GONG} light curve also peaks at around $\sim$ 22:29 UT. Both NB8 and {\it GONG}-H$\alpha$ show less contrast variation in the light curve than NB3 and NB4.

We show the GOES 1 {--} 8 {\AA} light curve in comparison to the NB5 (Redwing of the Mg lines, blue dashed), NB6 and NB7 continuum channels in Fig.~\ref{fig:flare_lc_suit}b. NB5 shows signs of flare response, although much weaker than NB3, NB4 and NB8. NB5 peaks around $\sim$ 22:31 UT, about $\sim$ 3 minutes later than NB3. Similar traits were observed from the images also, as pointed out in Fig.~\ref{fig:flare_obs}c and the accompanying discussions. More interestingly, NB6 (green dot-dashed line) and NB7 (black dotted line) do not show the hallmark sign of a flare light curve, i.e. gradual increase and decrease in the intensity. These bands exhibit a sharp rise in intensity during the impulsive phase of the flare. Finally, in Fig.~\ref{fig:flare_lc_suit}c, we show the {\it GOES} 1 {--} 8 {\AA} light curve in comparison to the STIX hard and soft X-ray light curve. The hard X-ray peaks around a similar time, around $\sim$ 22:29 UT, similar to NB3.

%%%%%%%%%
\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth,trim={1cm 2cm 1cm 4.2cm},clip]{Figures/feb_22nd/lc_4.pdf}
    \caption[Light curve of the {\suit} NB3 contour from various observatories]{{\bf Top panel:} Light curves from the pixels within intensity contour picked from \suit~NB3, NB4, NB8 and co-aligned GONG H$\alpha$ observations in comparison to the GOES SXR light curve. The NB4 light curve in the first panel is offset by -0.1 s from NB3 for better visibility. The vertical dotted dark line marks the flare's peak in NB3 observation. {\bf Middle panel:} the light curve arising from the NB2 and NB5 pixels from within the NB3 intensity contour in comparison to the GOES SXR light curve. {\bf Bottom panel:} the STIX HXR, NB6, NB7 and NB1 lightcurve compared to the GOES SXR lightcurve. }
    \label{fig:flare_lc_suit}
\end{figure*}
%%%%%%%%%

%%%%%%%%%%%%
\subsubsection{Observation and characterization of the umbral bright kernels}\label{sec:bright_ker}
%%%%%%%%%%%%

One of the curious features of this flare was the short-lived transient bright kernels observed in NB2 and NB5. Similar observations were made by \cite{kowalski19}. They observed umbral brightness kernels in the IRIS SJI 2832 {\AA}~channel for the X1 solar flare SOL2014-10-25T17:08:00. The SJI 2832 {\AA}~probes the sun in a similar wavelength range as {\suit} NB5. They observed the umbral brightening to be arising from a plethora of photospheric absorption lines, mostly Fe II going into emission. They attributed photospheric heating as the cause for the Fe II absorption lines going into emission. Unfortunately, as IRIS was not observing the main flaring region, there is no way to comment on the spectral nature of the brightening kernels. This might indicate the possible observation of new flare lines in the blue wing of the \ion{Mg}{2} lines. We further investigate the light curves of the bright kernels to possibly comment on their origin.

We compare the light curves arising from the bright kernels with GOES soft X-ray and STIX hard X-ray in Fig.~\ref{fig:nb2_lc}. The top panels show the NB2 and NB5 observations at their respective peaks. The two bright kernels are marked with a black dotted line, and a magenta dashed line. The counts from these marked regions are added to create the light curves for the bright kernels. In Fig.~\ref{fig:nb2_lc} middle and bottom panel, we compare the GOES soft X-ray and STIX hard X-ray light curves with respect to the bright kernels observed in NB2 and NB5, respectively. We observed that in NB2, the peak of the light curve is co-temporal with STIX hard X-ray. In NB5, the peak appears slightly later than the hard X-ray peak.

%%%%%%%%%
\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth,trim={0.5cm 10cm 2cm 0.2cm},clip]{Figures/feb_22nd/nb2_nb5_ker.pdf}
    \caption[Observation of the penumbral bright kernels in NB02 and NB05]{{\bf Top panels}: The NB2 and NB5 observation during the respective peaks. The bright penumbral kernels are marked with black dots and magenta dashed boxes. {\bf Middle panel}: Light curve of the two boxes from NB2 in comparison to GOES 1 {--} 8~{\AA} and STIX 25{--}80 keV light curve. {\bf Bottom panel}: Light curve of the two boxes from NB5 in comparison to GOES 1 {--} 8~{\AA} and STIX 25{--}80 keV light curve. The vertical dashed and dot-dashed lines mark the peaks of STIX hard X-ray and GOES soft X-ray light curves.}
    \label{fig:nb2_lc}
\end{figure*}
%%%%%%%%%

%%%%%%%%%
\subsection{Discussion}\label{sec:disc}
%%%%%%%%%

In this letter, we highlighted the first {\suit} observations of an X-class flare. We see penumbral bright kernels and enhancement in the red wing of the Mg window, similar to \cite{kowalski19,kowalski17,kleint17}. In most cases, these continuum enhancements are associated with WL flares. In this event, we also see bright kernels and enhancements in the blue wing of the Mg window. To the best of our knowledge, this is the first such observation in the blue wing. Unfortunately, we can not comment on the spectral nature of the bright kernels as {\suit} is only an imager. Further exploration is necessary to comment on the spectral nature of the bright kernels.

### 2025-04-11 chapter7/chap7_2.tex
Local changes

%----------------------------------------------
\section{Introduction} \label{sec:intro}
%----------------------------------------------

As alluded to earlier in chap.~\ref{c:intro}, flares manifest differently across various wavelengths. It is known that the foot-points of the post-flare loops are observed in hard X-rays (due to electrons) and $\gamma$~rays (due to ions). However, the post-flare loops themselves are observed in soft X-ray and Extreme Ultraviolet (EUV) \citep{fletcher11,TriBC_2004,tripathi06}. The corresponding white light and Near Ultraviolet (NUV) counterparts are believed to arise due to changes in ionization and local opacity in the photospheric and chromospheric heights. %These are usually \textbf{detected?} in some of the most impulsive signatures of flares \citep{watanabe17,hudson06}. 
The NUV and white light emission have also been demonstrated to be co-spatial and co-temporal with hard X-ray \citep{hudson92, oliverso12}.

One of the major puzzling aspects regarding the origin and energetics of solar flares is the origin of the white light (WL) continuum. According to the standard model of flares, the energetic electrons are accelerated along the loops and are stopped via numerous collisions and thermalization when the ambient medium has enough density, usually known as the `thick target' model \citep[see][for further details]{brown73,benz17,fletcher11}. It is believed that such densities are already present within the chromosphere, explaining the co-spatiotemporal nature of WL and Hard X-ray emission. The theoretical estimations, on the other hand, predict that parts of the WL emission may originate in the upper photosphere, i.e., depths which are inaccessible to electrons in the standard `thick-target' model.

There have been various attempts to modify the thick target model to account for various observations from solar flares, e.g., a warm target model \citep{kontar15,kontar19}, local re-acceleration of electrons \citep{brown73}, acceleration of protons along with electrons which are expected to penetrate deeper. There were also attempts to explain the source of WL with photospheric `back-warming' \citep{metclaff90}, where the upper photosphere is ionized via energy transported radiatively from the chromosphere. There have been several observations where the WL emission has been associated with enhancement observed in the 2832~{\AA} continuum of IRIS SJI \citep{heinzel14,kleint16,kleint17,kowalski17,kowalski19}.

In this chapter, we discuss the X-class flare recorded by the Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{suit,suit_main} on board Aditya-L1 \citep{adityal1} on February 22, 2024. This is the first flare that was localized and observed with the onboard flare detection module. %Continuum bright kernels were observed in the red wing (283~nm) and blue wing (276~nm) of the Mg window. To the best of our knowledge, this is the first observation of continuum enhancement of the blue wing of Mg window. 
The rest of the {\bf chapter} is structured as follows: in \S\ref{obs}, we discuss the observations of the flare and the dataset used for its study. \S\ref{res} we discuss the data analysis and results. Finally, in \S\ref{sec:disc}, we summarize, conclude and discuss the importance of these observations in flare studies. 
%In \S\ref{sec:bright_ker}, we discuss the observations specifically related to the penumbral bright kernels and how they compare across various wavelengths. In \S3, We summarize our findings and discuss the implications it can have regarding our understanding of the origin of WL emission is solar flares.
%-----------------------------------------------
\section{Observations and Data}\label{obs} 
%-----------------------------------------------
Active Region NOAA 13590 appeared on Feb. 18, 2024, at the northeast limb of the solar disk. On Feb. 22, 2024, it was located at N17E26 with $\beta\gamma\delta$ configuration and produced multiple flares, including the M4.8, X~1.7 and X6.3.% , an M4.8 aflare peaking around $\sim$ 06:32 UT, 20:46 UT and an X6.3 flare that peaked $\sim$ 22:34 UT .

Using the onboard flare detection algorithm based on intensity thresholding \citep{flare_det}, SUIT detected, localized and observed the X6.3 flare in flare mode. SUIT instrument carries 11 filters (8 narrow bands and 3 broad bands) tuned to observe the solar photosphere and chromosphere at various wavelengths in 200-400~{nm} wavelength range (see Table~\ref{tab:science_filters}). SUIT provides images at a pixel size of 0.7{\arcsec}. The four out of eight narrow band filters are tuned to observe the \ion{Mg}{2} blue wing continuum (NB2), \ion{Mg}{2}~k (NB3), \ion{Mg}{2}~h (NB5) and \ion{Mg}{2} red wing continuum (NB5). The NB6 and NB7 continuum filters are towards the blue and red sides of the Balmer jump (364.5~nm), respectively.

It provides both full disk and region of interest (ROI) observations as per the observational sequence being used. While in regular observations, the RoI is defined using ground commands, flare mode automatically defines the RoI based on the detected location and observes in the eight narrowband filters. Under this observation mode, the temporal cadence is $\approx$1~min. SUIT did not detect the X1.7 as the spacecraft was off-pointed for the stellar calibration sequence. The X6.3 flare that SUIT detected started at 22:08~UT and peaked at 22:34~UT. In the flare mode, it was observed in all eight narrowband filers. The flares were also observed by GOES, {\it SDO}/AIA, {\it SO}/STIX, GONG H$\alpha$. In this study, we have used AIA~1600 \& 1700~{\AA}, GONG~H$\alpha$ images and full disk integrated GOES soft-ray (1{--}8~{\AA}) and STIX Hard X-ray (25{--}50~keV) along with SUIT observations.

%-----------------------------------------------
\begin{figure*}[!h]
    \centering
    \includegraphics[trim = {2cm 2.5cm 2cm 1.8cm}, clip, width=0.9\textwidth]{Figures/feb_22nd/suit_roi_all_peak.pdf} 
    \caption[SUIT observation of the flare in all NB filters at their respective peaks]{(a) Parts of the full-disk (2k$\times$2k) observation in NB4 (\ion{Mg}{2}~h) showing the flaring region and sunspot. The over-plotted blue box shows the RoI localized by the onboard flare detection algorithm, and the white dashed box locates the region used for the subsequent analysis. (b) SUIT Narrowband images recorded at the peak of flares in the respective filters. The size of the images corresponds to the white-boxed region shown in panel a. The arrows mark the two bright umbral kernels.}
    \label{fig:flare_obs}
\end{figure*}
%-----------------------------------------------

\newpage

%-----------------------------------------------
\section{Data Analysis and results}\label{res}
%-----------------------------------------------

%-----------------------------------------------
%\begin{figure}
\begin{wrapfigure}{l}{0.5\textwidth}
    \centering
    \hspace{-1cm}
   \includegraphics[trim={1.5cm 2.5cm 1.5cm 1cm},clip,width=\linewidth]{Figures/feb_22nd/suit_roi_aia_peak.pdf}
    \caption[AIA and GONG observations of the flare]{Co-aligned and co-registered AIA 1600, 1700~{\AA} and GONG H{$\alpha$} observation near the NB3 peak in a, b and c, respectively. The over-plotted contours show 60\% of the peak intensity observed in NB3.}\label{aia}
\end{wrapfigure}
%\end{figure}
%-----------------------------------------------

Figure~\ref{fig:flare_obs}.a displays shows a cutout of the full-disk (2k$\times$2k) image taken in NB4 (\ion{Mg}{2}~h) filter. The over-plotted blue box shows the region of interest automatically defined by the onboard flare detection algorithm. As we can see, the auto-defined RoI fully covers the flare. The flare detection algorithm is designed to define the RoI, which is centred on the flaring region. In the current observation, we can see that the RoI is not properly centred at the flare. However, since then, various parameters of the flare detection and localization algorithm have been tweaked to achieve better detection and localization. The white dashed box locates the region we have considered for further study in this {\bf chapter}. Fig.~\ref{fig:flare_obs}.{b-i} displays the flares in each narrow band filter at their respective peak. The field of view (FOV) corresponds to the dashed white box in panel a. As can be seen, the flare is observed in all the narrow band filters of SUIT, including the two flare kernels observed as penumbral brightening, which are located by black arrows. % in d during the respective peaks of NB2 and NB5 (marked by black arrows in Fig.~\ref{fig:flare_obs}c and f respectively).
%-----------------------------------------------
\begin{figure*}
    \centering
    \includegraphics[trim={0.2cm 2.5cm 1cm 3.5cm},clip,width=\linewidth]{Figures/feb_22nd/suit_roi_nb3_peak.pdf}
    \caption[SUIT observation of the flare in all NB filters at NB3 peak]{Flare as observed in all narrow band filters at the time of peak intensity in NB3. The over-plotted black contours show 60\% of the peak intensity observed in NB3.}
    \label{fig:flare_nb3_peak}
\end{figure*}
%-----------------------------------------------

In Fig.~\ref{fig:flare_nb3_peak}, we plot the flare as observed in each narrow band filter at the peak intensity in NB3(\ion{Mg}{2}~k).%channel at around $\sim$ 22:28-22:29 UT. 
The over-plotted black contours represent 60\% of the peak intensity observed in NB3. The features observed in NB8 (\ion{Ca}{2}~h) are very similar in morphology to those in NB3 and NB4. While there appears to be a hint of such features in other continuum channels, it is not clearly discernible.

%-----------------------------------------------
\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth,trim={1cm 2cm 1cm 4.2cm},clip]{Figures/feb_22nd/lc_4.pdf}
    \caption[Comparison of SUIT NB lightcurve with other observatories]{Light curves obtained over the contoured region from AIA 1600 (blue dashed), AIA 1700~{\AA} (black do-dashed), NB3 (black dotted), NB4 (green dot-dashed), NB8 (magenta dashed), NB2 (blue dotted), NB5 (green dashed), NB1 (green triangles), NB6 (magenta squares) and NB7 (blue dotted) as labelled. For comparison, we have also over-plotted the light curves obtained from coaligned GONG H-alpha observations (blue squares) in panel (a), full-sun integrated GOES/SXR in 1{--}8~{\AA} (red solid) and STIX/HRX (black dashed) in panel (c).}
    \label{fig:flare_lc_suit}
\end{figure*}
%-----------------------------------------------

To compare the SUIT observations with those from AIA and H$\alpha$, in Fig.~\ref{aia}, we plot display AIA~1600 (panel a), AIA~1700 (panel b) and GONG-H$\alpha$ recorded at near simultaneous time to the peak of NB3 observations. The over-plotted contours are the same as those in Fig~\ref{fig:flare_nb3_peak}. These images clearly reveal the presence of clear signatures of the flare kernels in AIA UV and H$\alpha$ observations, co-spatial to the NB3 (\ion{Mg}{2}~k) observations.

In order to understand the temporal evolution of the flare, we plot the lightcurves in Fig.~\ref{fig:flare_lc_suit} obtained from various filters of SUIT, GOES, STIX, AIA 1600 \& 1700, and GONG H$\alpha$, as labelled. Note that the GOES and STIX lightcurves are full Sun integrated, whereas those for other observations are obtained over the contoured region Figs.~\ref{fig:flare_nb3_peak}~\&~\ref{aia}, and normalized to their respective max intensities. The vertical dotted black line across all the panels locates the peak intensity in NB3.

The lightcurves reveal that the flare peaks in all the SUIT channels (except NB6 and NB7), AIA 1600 \& 1700, H$\alpha$ and STIX before it achieves its maximum intensity in GOES. The STIX peak coincides with that in SUIT NB1, NB3, NB4, NB8 as well as AIA and H$\alpha$. Note that SUIT NB3, NB4 and NB8 primarily observe the chromospheric signatures, similar to GONG H$\alpha$. Fig.~\ref{fig:flare_lc_suit}.b, shows that the lightcurves of NB3, NB4, and NB8 peak at the same time around $\sim$ 22:29~UT, which is similar to that H$\alpha$. However, NB8 and {\it GONG}-H$\alpha$ show less contrast variation ($\sim$ 40\% change for NB8 (\ion{Ca}{2} h) and GONG H$\alpha$, compared to the $\sim$ 80\% change for NB3 (\ion{Mg}{2} k) and NB4 (\ion{Mg}{2} h)) than that shown by NB3 and NB4. This may be attributed to the larger enhancement in the continuum in NB8 (\ion{Ca}{2}) and H$\alpha$ than that in \ion{Mg}{2}.

Figure~\ref{fig:flare_lc_suit}.c shows that the lightcurves of SUIT NB2 and NB5 (blue and red wing of \ion{Mg}{2}) peak about 3 minutes after the NB3 peak (also STIX hard X-ray peak). This is also apparent in the images shown in Fig~\ref{fig:flare_obs}. Moreover, unlike other lightcurves, NB6 and NB7 lightcurves do not show a gradual increase and decrease. Instead, they exhibit a rather sharp rise, albeit very small ($\sim$ 0.03\%), in intensity during the impulsive phase of the flare.

%%--------------------------------------------
\section{Summary and Discussion}\label{sec:disc}
%%--------------------------------------------

In this {\bf chapter}, we have performed a multi-wavelength study of the X-6.3 flare observed on Feb 22, 2024, using the observations recorded by SUIT, AIA, STIX and GONG. Moreover, this is the first flare detected and localized by the onboard algorithm for flare identification on SUIT and observed in flare mode. Below we summarize the obtained results.
\begin{itemize}
    \item The flare is observed in all narrow band filters of SUIT. The flare was also observed in AIA 1700 and 1600, GONG~H$\alpha$, GOES soft X-rays (SXR) and STIX hard X-rays (HXR).
    \item The flare peak in all SUIT channels (except NB6 and NB7) and those in AIA 1600 \& 1700~{\AA}, GONG~H$\alpha$ and STIX HXR observations and is $\sim$ 5 minutes prior to the GOES SXR peak. The flare peaks are observed in NB6 and NB7 after $\sim$ 3 minutes after the GOES SXR peak.
    \item The flare peak in NB3 and NB4 coincides with that in AIA 1600 \& 1700~{\AA} and STIX 25{--}50~keV observations.
    \item The flare attains its peak in NB2 and NB5, blue and red wing of \ion{Mg}{2} lines, after about 3 minutes it does in NB3.    
\end{itemize}

The results demonstrate that the flare signatures detected by SUIT in all its narrow band channels are very tightly related to HXR observations recorded by STIX. These results highlight the first {\suit} observations of an X-class flare. The observations of flare kernels and enhancement in the intensity in the red wing of the \ion{Mg}{2} window, i.e., NB5 is similar to those observed by \cite{kowalski19,kowalski17,kleint17} using the observations recorded by the Interface Region Imaging Spectrometer \citep[IRIS,][]{iris}. For the flare studied here, we also detect the bright kernels and intensity enhancements in the blue wing of the Mg window, i.e., in NB2 filter. To the best of our knowledge, this is the first such observation in the blue wing of \ion{Mg}{2}. Unfortunately, we can not comment on the spectral nature of the bright kernels as SUIT is only an imager. Further exploration is necessary to comment on the spectral nature of the bright kernels and their possible origin. It is important to highlight that in the observation reported by \cite{kowalski19}, the appearance of flare kernel and intensity enhancement in SJI recorded at 2832~{\AA} (similar to SUIT NB5 filter) corresponded with a plethora of photospheric absorption lines, mostly \ion{Fe}{2}, turning into emission, which was attributed to photospheric heating.  would  Therefore, no such analysis was possible.

### 2025-04-11 chapter8/chap8.tex
Local changes

--- 2024-07-27 chapter7/ms.tex
@@
-\justifying
-
-%%----------------------------------------------------
-\section{Introduction} \label{sec:intro}
-%%----------------------------------------------------
-
-The Solar Ultraviolet Imaging Telescope onboard {\it Aditya-L1} \citep[{\it Aditya-L1}/SUIT,][]{article,ghosh16,adityal1,suit_main} provides a targeted probe into the Chromosphere and Transition region.
-It provides continuous full-disk and Region of Interest (RoI) coverage of the Sun in eleven pass bands.
-The details of these bands are provided in chapter~\ref{c:chap3} Tab.~\ref{tab:science_filters}.
-The eight narrow bands provide coverage across the \ion{Mg}{2} k and h lines, \ion{Ca}{2} h line, the CN band, red and blue wing of the \ion{Mg}{2} window and parts of the NUV continuum.
-As alluded earlier, this provides unprecedented coverage of the Chromospheric and Transition region structure of solar flares.
-
-The {\it Aditya-L1} was launched on September 2nd, 2023.
-The first light observations were made on December 5th, 2023 while the payload was still in cruise phase.
-For the majority of the cruise phase the payload only operated in the 2k synoptic mode, i.e.
-it only captured continuous (2k $\times$ 2k) observations in NB4 (\ion{Mg}{2} h line) with one minute cadence.
-The L1 insertion was carried out on January 6th, 2024.
-Following that the payload also started taking (4k $\times$ 4k) observations in all eleven science filters.
-Various components of the flare detection algorithm were progressively turned on.
-In this chapter we discuss some of the initial flare observations made by SUIT.
-The first flare triggered by the flare detection algorithm was a X6.3 flare from north-west corner of the disk on February 22nd, 2024, which was also observed by several other instruments {\it e.g.} {\it SDO}/AIA, {\it IRIS}, {\it SO}/STIX.
-During the cruise phase, SUIT also observed a X1 flare from the south-east limb of the Sun on December 31st, 2023.
-We only have observations in the NB4 (\ion{Mg}{2} h line) channel for this flare.
-But this provides us with an unprecedented view of post-flare loops and possibly reconnection slingshot in the \ion{Mg}{2} line.
-Subsequent portions of this chapter will be divided into two parts, where we discuss the observations of these two flares separately.
-
 %%----------------------------------------------------
@@
     \includegraphics[width=0.5\textwidth]{suit_roi_all_peak.pdf}
-    \caption{\suit~observations of the flare from various NB filters. Top panel: during NB3 peak. Bottom panel: During the peak of individual bands.}
+    \caption[{\suit} observations of the February 22nd, 2024 flare from various NB filters.]{\suit~observations of the flare from various NB filters.
+Top panel: during NB3 peak.
+Bottom panel: During the peak of individual bands.}
     \label{fig:flare_nb3_peak}
@@
     \includegraphics[width=0.8\textwidth,trim={2.3cm 2.5cm 0cm 4.5cm},clip]{lc_suit_contour.pdf}
-    \caption{Light curves from the pixels within intensity contour picked from \suit~and co-aligned AIA observations.
+    \caption[Light curves of the {\suit} observations from NB3 contours.]{Light curves from the pixels within intensity contour picked from \suit~and co-aligned AIA observations.
 The NB4 light curve in the second panel is offset by -0.1 from NB3 for better visibility.
@@
     \includegraphics[trim={1.8cm 2.5cm 3cm 3cm},clip,width=0.75\textwidth]{xsm_spec.pdf}
-    \caption{Top panel: XSM observation of the two flares.
+    \caption[XSM observation of the February 22nd, 2024 flare.]{Top panel: XSM observation of the two flares.
 The red shaded region marks the window when the Be filter was inserted.
@@
     \includegraphics[trim={0.5cm 1cm 0.5cm 0.7cm}, clip, width=0.77\textwidth]{xsm_fit.pdf}
-    \caption{XSM spectra in 3 {--} 8.5 keV binned between 22:27:20 {--} 22:27:25 UT.
-Top panel shows the fit with ``chisoth+chisoth" model.
-Bottom panel shows the same spectra fitted with ``chisoth+chisoth+gaussian" model.}
+    \caption[Fits of the observed XSM spectra.]{XSM spectra in 3 {--} 8.5 keV binned between 22:27:20 {--} 22:27:25 UT.
+Top panel shows the fit with ``chisoth" model.
+Bottom panel shows the same spectra fitted with ``chisoth+gaussian" model.}
     \label{fig:xsm_fit}
@@
     \includegraphics[trim={1.3cm 0.1cm 0.3cm 1.2cm}, clip, width=0.95\textwidth]{fe_excess_4.pdf}
-    \caption{Fe excess emission from 6.4 keV(blue solid) in comparison to STIX 25-50 keV(black dashed), GOES 1 {--} 8 $\AA$ (dotted red) and XSM 7.12 {--} 8.5 keV (green dot-dashed) light curve.}
+    \caption[Fe excess light curve as a function of time.]{Fe excess emission from 6.4 keV(blue solid) in comparison to STIX 25-50 keV(black dashed), GOES 1 {--} 8 $\AA$ (dotted red) and XSM 7.12 {--} 8.5 keV (green dot-dashed) light curve.}
     \label{fig:fe_excess}
@@
 The consistent increase in continuum intensity is happening across the Balmer jump ($\lambda$~=~364.5 nm).
-
-%%----------------------------------------------------
-\section{X1 flare observed on Dec 31st, 2023} \label{sec:dec_31st}
-%%----------------------------------------------------

### 2025-04-11 introduction/intro.tex
Local changes

--- 2024-07-22 introduction/intro.tex
@@
 The Sun is our nearest astrophysical object, which serves as a natural laboratory for various branches of Physics - atomic physics, spectroscopy, turbulence, magneto-hydrodynamics, stellar evolution, dynamo and magnetism and plays a key role in space and terrestrial weather.
-The Sun is also the primary source of light and energy on earth.
-So it is only natural that we try to understand the different physical processes involved in the energectics of the Sun, which indirectly affects life on Earth.
-In this chapter I briefly introduce the Sun and various layers of its atmosphere.
-At the end we provide a motivation for the thesis.
-
-The Sun is a G2V star, with surface luminosity $3.86~\times~10^{26}$ W and an effective temperature of $\sim 5780~K$.
-The Sun is mostly made out of Hydrogen(92.1\%) and Helium(7.8\%) along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe.
-The study of the Sun can be mainly divided into three components: the Solar interior, the Solar atmosphere and the Heliosphere.
+The Sun is also the primary source of light and energy on Earth.
+So it is only natural that we try to understand the different physical processes involved in the energetics of the Sun, which directly affects life on Earth.
+In this chapter, I briefly introduce the Sun, various layers of its atmosphere and Solar flares.
+Finally, we provide a motivation for the thesis and a brief outline.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The solar interior}\label{solar_int}
+\section{The Sun}\label{Sun}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-In the innermost zone of the star the Sun has a temperature of about 15 MK and a density of $1.6~\times~10^{5}~km.m^{-3}$ that fuses Hydrogen into Helium mainly by p-p cycle \citep{bethe38} and to some extent by CNO cycle \citep{bethe39}.
+The Sun is a G2V star, with surface luminosity $3.86~\times~10^{26}$~W and an effective temperature of $\sim 5780~K$.
+The Sun is mostly made out of Hydrogen (92.1\%) and Helium (7.8\%), along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe, among others.
+The study of the Sun can be divided into three components, \textit{viz.} the Solar interior, the Solar atmosphere and the Heliosphere.
+Fig.~\ref{fig_solar_int} shows a schematic diagram of various regions of the Sun.
+Below, we briefly describe these three regions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Solar interior}\label{solar_int} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\info{First you have to say what is the interior! For example the interior is made of three regions -- the core, the radiative zone and the convective zone. The innermost zone, i.e., the core}
+Depending on various physical characteristics, the Solar interior can be divided into three zones {\it e.g.} the core, radiative zone and convective zone.
+In the innermost zone, the core, the Sun has a temperature of about 15~MK and a density of $\mathrm{1.6\times 10^{5}~km.m^{-3}}$.
+Here Hydrogen fuses into Helium primarily by p-p chain reaction \citep{bethe38} and to some extent by CNO cycle \citep{bethe39}.
+Beyond the core, we have the optically thick radiative zone, where the Hydrogen and Helium are completely ionized due to very high density.
+The high energy $\gamma$-ray photons generated in the core have a very small mean free path in this region, as they collide numerous times and propagate across this region.
+As we move radially outwards, temperature and density both decrease slowly due to gravitational equilibrium.
+Due to this reduction of temperature, there is a decrease in the thermal motion of the particles, and the hydrogen and helium start to recombine, giving rise to an increase in opacity at the top of the radiative zone.
+This change in opacity makes the propagation of photons via radiation less efficient, as photons get trapped and reabsorbed more.
+This creates a sharp temperature gradient due to the "photon pileup".
+This temperature gradient gives rise "convective instability".
+This is the convective zone where the energy from the inner layers of the Sun is transported adiabatically to the surface of the Sun.
+%In between the radiative and the convective zone, there is \sroy{believed to be }a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tachocline.
+\sroy{This region} is believed to play a major role in generating Sun's magnetic field via the Dynamo process \citep{corbard01}.
 
 %% ############# %%
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
-    \includegraphics[width = 0.8\linewidth]{Figures/solar_int.png}
-    \caption{A schematic depiction of the different layers of the Sun.
-The figure also shows some of the most prominent magnetic structures on the Sun e.g sunspot, prominence, coronal hole.
-Credit : NASA/Goddard.}
+    \includegraphics[trim={2cm 11cm 0.5cm 8cm}, clip, width=0.9\textwidth]{solar_int.pdf}
+    \caption[A schematic depiction of the different regions of the Sun.]{A schematic depiction of the different regions of the Sun, including some of the most prominent magnetic structures on the Sun e.g., Sunspot, prominence, coronal hole.}
     \label{fig_solar_int}
@@
 
-Fig.~\ref{fig_solar_int} shows a schematic diagram of various layers of the Sun.
-Beyond the core we have the optically thick radiative zone, where the Hydrogen and Helium are completely ionized.
-The high energy $\gamma$-ray photons generated in the core, have very small mean free path in this region, as they collide numerous times eventually thermalizing becoming visible photon.
-Beyond the radiative zone the degree of ionization of Hydrogen and Helium changes drastically giving rise to a sharp temperature gradient.
-This is the convective zone where the energy from the inner layers of the Sun is transported adiabetically to the surface of the Sun.
-In between the radiative and the convective zone, there is a thin layer, roughly at $\sim~0.7~R_{\odot}$ known as the tacholine, which is believed to play a major role in generating Sun's magnetic field via the Dynamo process \citep{corbard01}.
-
-The core and the radiative zone of the Sun rotates as a solid body, whereas the convective zone rotates differentially.
+The core and the radiative zone of the Sun rotate as a solid body, whereas the convective zone rotates deferentially.
 The rotation period varies from $\sim~25~days$ to $\sim~35~days$ from the equator to the pole.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The solar atmosphere}\label{solar_atmos}
+\section{The Solar atmosphere}\label{solar_atmos}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The layers outside the convection zone together, form the solar atmosphere - the Photosphere, which is also known as the Sun's surface, the Chromosphere, the transition region and the Corona.
+The layers outside the convection zone together form the Solar atmosphere and is further divided into different regions.
+The photosphere, which is also known as the Sun's surface, the chromosphere, the transition region and the corona.
 While we can define geometrical height or depths to define these layers, it is much more useful to define them using the local optical depths of various spectral lines, which are directly used to observe the layers.
-This also gives us a idea about which spectral features originate mainly from which portions of the solar atmosphere.
-Fig.~\ref{fig_solar_atm} shows the variation of temperature and number density across various layers of the Solar atmosphere \sr{Ref.
-here}.
+This also gives us an idea about which spectral features originate mainly from which portions of the Solar atmosphere.
+Fig.~\ref{fig_solar_atm} shows the variation of temperature and number density across various layers of the Solar atmosphere \citep{philips08}.
 
 %% ############# %%
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
     \includegraphics[width = 0.8\linewidth]{Figures/solar_atm.png}
-    \caption{The variation of electron temperature (solid line) and electron density ($\mamthrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dotted- dashed line) in the solar atmosphere as derived based on the 1-D model calculations by \sr{Ref.
-here}.}
+    \caption[Density and temperature profiles across various layers of the Sun.]{The variation of electron temperature (solid line) and electron density ($\mathrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dot-dashed line) in the Solar atmosphere \citep{philips08}.}
     \label{fig_solar_atm}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Photosphere}\label{photosphere}
+\subsection{The photosphere}\label{photosphere}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The Photosphere is defined to be the layer where $\tau_{\lambda~\sim~5000}~=~1$.
+The photosphere is defined to be the layer where $\tau_{\lambda~\sim~5500}=1$.
 This is in the green part of the visible spectrum and the Sun is opaque in visible beyond this layer, hence it is called to be the surface of the Sun.
-This layer is 400-600 km deep and has an effective temperature of 5780 K.
-The magnetic filed lines arising from the tacholine penetrate the Photosphere and creates a `carpet' over the whole region \citep{priest14}.
-As mentioned earlier, this is the Solar surface known as the `Quite Sun'(QS).
-This region exhibits an average magnetic flux density of \textbf{10 -- 50~G}.
-The QS surface is covered with cells of roughly four size- granule, meso granules, super granules and giant cells.
-Some regions exhibit much stronger magnetic flux density often associated with highly twisted magnetic field structures.
-These magnetic features are manifested as sunspots, spicules, bright points etc.
+This layer is 400{--}600~km thick and has an effective temperature of 5780 K.
+The magnetic field lines arising from the tachocline penetrate the photosphere and create a `carpet' over the whole region \citep{priest14}.
+As mentioned earlier, this is the Solar surface known as the `quiet Sun'(QS).
+This region exhibits an average magnetic flux density of 10 {--} 50 G.
+The QS surface is covered with cells of roughly four sizes, namely, granules, mesogranules, supergranules and giant cells.
 
-As the density changes drastically at the Photosphere compared to the convective zone, the thermalized photons from Sun's core start free streaming again, as the mean free path also increases drastically and as a result perturbs the thermal equilibrium (TE from hereon).
-So, we have to define the thermodynamic quantities of the Photosphere in Local Thermal Equilibrium (LTE from hereon).
-As we move away from the Photosphere, because the density keeps on decreasing steadily, the LTE conditions also start deviating similarly \citep{philips08}.
+Some regions exhibit much stronger magnetic flux density, often associated with highly twisted magnetic field structures.
+These magnetic features are manifested as Sunspots.
+The Sunspots harbour some of the strongest concentrated magnetic fields, reaching up to several kilogauss in strength.
+The other noteworthy Solar magnetic structure apart from these are believed to be spatially unresolved flux tubes composing a network with field strengths $\sim$ {\it $O(10^{3} G)$}\citep{solanki93,grossman96,rubio19}.
+
+As the density changes drastically at the photosphere compared to the convective zone, the thermalized photons from the Sun's core start free streaming, as the mean free path also increases drastically and, as a result, perturbs the thermal equilibrium (TE).
+Therefore, the thermodynamic quantities of the photosphere are defined under the assumption of Local Thermal Equilibrium (LTE).
+As we move higher from the photosphere, the LTE conditions also start deviating because the density keeps on decreasing steadily \citep{philips08}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Chromosphere}\label{chromosphere}
+\subsection{The chromosphere}\label{chromosphere}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The Chromosphere is a highly non-uniform dynamic layer with a thickness of 1500~--~3000~km, with increasing temperature (upto $10^{4}$ K) and decreasing number density.
-As seen in the fig.
-\ref{fig_solar_atm}, the temperature of the Chromosphere saturates before the dramatic rise in the transition region.
-This saturation is attributed to a steady deposition of acoustic energy by creation of shock waves \citep{carlsson07}.
-The Chromosphere also exhibits a sharp gradient in the plasma $\beta$ factor, non-LTE conditions, dominance of wave motions \sr{Ref.
-here}.
+The chromosphere is a highly non-uniform dynamic layer with a thickness of 1500 {--} 3000 km, with increasing temperature (up to $10^{4}$ K) and decreasing number density.
+As seen in Fig.~\ref{fig_solar_atm}, the temperature of the chromosphere saturates before the dramatic rise in the transition region.
+This saturation is attributed to a steady deposition of acoustic energy by the creation of shock waves \citep{carlsson07}.
+The chromosphere also exhibits a sharp gradient in the plasma $\beta$ factor, non-LTE conditions, and the dominance of wave motions.
+The observable features in the chromosphere are active regions, sunspots, plages and also light bridges as labelled in images taken by IRIS SJI (slit-jaw imager) 2796 {\AA} (left panel) and 2832 {\AA} (right panel) displayed in Fig.~\ref{fig:sji_features}.
 
@@
     \centering
-    \includegraphics[trim={1cm 3cm 2cm 5cm},clip,width=0.8\textwidth]{Figures/sji_images.pdf}
-    \caption{IRIS SJI Slit-jaw images of NOAA AR 13521 on Dec 21st, 2023 in \ion{Mg}{2} 2796 {\AA}~(left panel) showing the upper Chromosphere.
-The right panel shows the same active region in 2832 {\AA}~continuum corresponding to upper photosphere.}
+    \includegraphics[trim={1cm 3cm 2cm 5cm},clip,width=0.95\textwidth]{Figures/sji_images.pdf}
+    \caption[IRIS SJI observation of NOAA AR 13521 on Dec 21st, 2023.]{IRIS slit-jaw images of NOAA AR 13521 taken in \ion{Mg}{2} 2796 {\AA} (left panel) and 2832 {\AA}~continuum (right panel) showing the upper chromosphere and upper photosphere, respectively.
+Different features are labelled.}
     \label{fig:sji_features}
@@
 %%%%%%%%%%%%%%%%
-
-In fig.~\ref{fig:sji_features} we show the NOAA AR 13521 in IRIS SJI 2796 {\AA} (left panel) and 2832 {\AA} (right panel).
-The dark sunspots and plage regions surrounding it are clearly visible in the 2832 {\AA} wavelength window.
-In the 2796 {\AA} window we see the plage along with light bridges more clearly.
 
@@
 
-The transition region above the Chromosphere is a thin, dynamic layer where we witness a dramatic increase in temperature by two orders of magnitude along with a similar decrease in electron density by nearly 5-6 orders of magnitude which is demonstrated in fig.
-\ref{fig_solar_atm}.
-In general the this layer is roughly $\sim$ 100 km in thickness, but that can change depending on various dynamic conditions of Chromosphere($\sim~10^{4}~K$) below, or Corona($\sim~10^{6}~K$) on top.
-The transition region is generally characterized by the steep change in the temperature, pressure gradients, drastic change in local optical depth and competition between gas pressure and magnetic pressure.
-The transition region also manifests the ARs as various magnetic features such as small scale brightening, jets, spicules, fibrils etc.
+The transition region above the chromosphere is a thin, dynamic layer where we witness a dramatic increase in temperature by two orders of magnitude along with a similar decrease in electron density, demonstrated in Fig.~\ref{fig_solar_atm}.
+In general, this layer is roughly $\sim$100~km in thickness, but that can change depending on various dynamic conditions of chromosphere ($\sim~10^{4}~K$) below, and corona ($\sim~10^{6}~K$) on top.
+The transition region is generally characterized by steep changes in temperature, pressure gradients, local optical depth, and competition between gas and magnetic pressure.
+The transition region also manifests the ARs as various magnetic features such as small-scale brightening, jets, spicules, fibrils etc.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Corona}\label{corona}
+\subsection{The corona}\label{corona}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The outermost layer of the Solar atmosphere is the Corona.
-The Corona is only visible in naked eyes during the total solar eclipse or via Coronagraphs.
-It maintains a steady temperature of 1-2 Mk during ambient conditions, but can rise upto tens of MK during solar flares.
-The coronal continuum spectrum is produced due to Thompson scattering of photons from photosphere off coronal electrons.
-Corona also emits in various emission lines, e.g.
-Mg, Fe, Si, S, Ca, O etc.
-across a wide band of electromagnetic spectrum ranging from X-ray to visible wavelengths.
-
-Similar to the other layers, the corona exhibits a variety of structures such as ARs, coronal holes, bright points, filaments, flares.
-The flare arcades are most prominently visible in the Corona.
-So, most of our existing studies over the last decade has focused on the coronal features of the flares.
-In fig.~\ref{fig:sji_features} we show one of the most well known and well studied solar eruptions from Aug 31st, 2012.
-A giant prominence erupted from the south east limb.
-The erupted prominence material was visible in all AIA channels from 304 \AA~(Chromospheric He II, see fig.~\ref{fig:aia-feature} \textbf{panel (a)}) across all six Coronal channels (\textbf{panel (b){--}(g)}).
-The sun spots were also clearly visible in HMI magnetogram and continuum (see fig.~\ref{fig:aia-feature} \textbf{panel (h)}).
-In \textbf{panel (i)} we show the co-aligned AIA 304 \AA, 131 \AA and HMI magnetogram image.
-The sunspots lie at the base of the erupted prominence, accompanied by the hot thermal plasma associated with the accompanying flare.
-The novelty of such observation lies in the clear spatial connection across various layers of the sun, connected via energy and momentum transported from one layer to the other.
+The outermost layer of the atmosphere is the corona.
+The corona maintains a temperature of 1-2~MK during ambient conditions but can rise up to tens of MK during explosive eruptions such as Solar flares.
+Due to such high temperatures, the coronal gas is fully ionized.
+It is only visible to the naked eye during the total Solar eclipse or with coronagraphs due to Thomson scattering of the photosphere with free electrons in the corona.
+corona also emits in various emission lines, e.g.
+Mg, Fe, Si, S, Ca, O, etc., across a wide band of electromagnetic spectrum ranging from X-ray to visible wavelengths.
+Similar to the other layers, the corona exhibits a variety of structures such as ARs, coronal holes, bright points, filaments, and flares.
+The flare arcades are most prominently visible in the corona.
+%\info{I made a lot of changes in this section.
+please see if all is consistent.}
 
 %%%%%%%%%%%%%
-\begin{figure}
+\begin{figure}[ht!]
     \centering
     \includegraphics[width=\textwidth]{Figures/aia_features.pdf}
-    \caption{Image of the prominence eruption and associated flare from NOAA AR 11562 on Aug 31st, 2012$\sim$19:50 UT.
+    \caption[Different parts of a flare eruption observed across various wavelengths]{AIA observations of prominence eruption and associated flare as observed on Aug 31st, 2012$\sim$19:50 UT.
+Different features across different wavelengths have been labelled.}
+    %\caption[Different parts of a flare eruption observed across various wavelengths.]{Image of the prominence eruption and associated flare from NOAA AR 11562 on Aug 31st, 2012$\sim$19:50 UT.
 The prominence is visible in all of the AIA channels.
@@
 The flare loops of the associated event is visible in AIA 94 \AA~\textbf{(panel e)} and AIA 131 \AA~\textbf{(panel f)}.
-The sunspots are visible in HMI continuum \textbf{panel (h)}.
+The Sunspots are visible in HMI continuum \textbf{panel (h)}.
 We show a co aligned map of AIA 304 \AA, HMI magnetogram and AIA 131 \AA~in \textbf{panel (i)}.
-The spatial association of the sunspots with the hot flareloop plasma and the prominence eruption is clearly demostrated here.
+The spatial association of the Sunspots with the hot flareloop plasma and the prominence eruption is clearly demonstrated here.
 }
@@
 
+%\info{I would write the caption of Fig.~\ref{fig:aia-feature} as: AIA observations of prominence eruption and associated flare as observed on Aug 31st, 2012$\sim$19:50 UT.
+Different features have been labelled.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Solar flares are the most powerful magnetic events in the solar system.
-They are described as a sudden increase in brightness in localized areas on Sun.
-Within tens of minutes, they can release over $10^{32}$ erg of energy, which is emitted across the entire electromagnetic spectrum from radio to gamma rays.
-They can also launch high energetic particles into the interplanetary medium.
-Most of the flares occur in magnetic active regions, and the amount of flare energy released is comparable to the free energy stored in the magnetic system.
-The term "flare" is generally used explicitly for the entire magnetically-driven event's electromagnetic radiation, as it is the most significant fraction of the total energy liberated.
-The total energy released varies from event to event.
-It is also known that larger events occur much less frequently than smaller events.
+Solar flares are the most powerful energetic explosions in the Solar system.
+They are described as a sudden increase in brightness in localized areas of the Sun.
+Within tens of minutes, they can release over $10^{32}$ erg of energy, which is emitted across the entire electromagnetic spectrum, i.e., from radio to gamma rays.
+They can also launch highly energetic particles into the interplanetary medium.
+Flares occur in magnetic active regions.
+It has been estimated that the amount of flare energy released is comparable to the free energy stored in the magnetic system \citep{emslie12,ash17}.
+%The term "flare" is generally used explicitly for the entire magnetically-driven event's electromagnetic radiation, as it is the most significant fraction of the total energy liberated.
+The total energy released varies from event to event. It is also known that larger events occur much less frequently than smaller events.
 
-%% ##################################################### %%
+Fig.~\ref{fig:sji_features} displays one of the most well-known and well-studied Solar eruptions from Aug 31st, 2012.
+During this event, an associated giant prominence erupted from the southeast limb, which was visible in all AIA channels as shown in Fig.~\ref{fig:aia-feature}.
+The sunspots were also clearly visible and labelled in the HMI continuum (see Fig.~\ref{fig:aia-feature}h).
+In Fig.~\ref{fig:aia-feature}i, we show the co-aligned AIA 304 {\AA} and HMI continuum observation.
+The Sunspots lie at the base of the erupted prominence, accompanied by the hot thermal plasma associated with the accompanying flare (visible in Fig.~\ref{fig:aia-feature}e {--} f).
+The novelty of such observation lies in the clear spatial connection across various layers of the Sun, connected via energy and momentum transported from one layer to the other.
+
+%------------------------------------
 \subsection{Brief history of flare observation}\label{sol_flr_1}
-%% ##################################################### %%
+%------------------------------------
 
-In September 1, 1859, R.C.
+On September 1, 1859, R.C.
 Carrington and R.
-Hodgson observed the first flare in the continuum of white light\citep{carrington1859,hodgson1859}.
-The localized brightening on the Sun have remained an enigma ever since.
-We have been observing the local flaring events across all wavelengths from both ground and space based observatories.
-Shortly after the observation by Carrington and Hodgson, people started studying the Sun extensively in the H$\alpha$ line which is formed in the Chromosphere, and the reports of flaring events became more and more frequent and progressively more and more complex.
-No two events were similar, as there were variations observed in source of size, ejections of plasma along with shock waves driving into the interplanetary space.
-Advances of radio technology during the second world war ensured detection of presence of non-thermal electrons in the solar corona, during military radar operations \citep{hey46}.
-Around the same time S.E.
-Forbrush noticed ground level cosmic ray enhancement during major solar flares.
-These discoveries eluded that the flaring events do not only involve the thermal plasma, but is somehow connects with high energy particles and involves the corona.
-in the 1950s we started observing the Sun in hard X-rays ($\ge~10~keV$) with rockets and balloons.
+Hodgson independently observed the first flare in white-light continuum~\citep{carrington1859,hodgson1859}.
+Such localized brightening on the Sun has remained an enigma ever since.
+Shortly after the observation by Carrington and Hodgson, the Sun was being studied extensively in the H$\alpha$ wavelength, which essentially images the chromosphere, and the reports of flaring events became increasingly frequent and progressively more complex.
+No two events were similar, as there were variations observed in the size of the source, ejections of plasma, and shock waves driving into the interplanetary space.
+Advances in radio technology during the Second World War affirmed the detection of the presence of non-thermal electrons in the Solar corona during military radar operations \citep{hey46}.
+Around the same time, S.E.
+Forbrush noticed ground-level cosmic ray enhancement during major Solar flares.
+These discoveries eluded that the flaring events do not only involve the thermal plasma but somehow connect with high energy particles and involve the corona.
+
+In the late 1950s, using rockets and balloons, the Sun was observed with hard X-rays ($\ge~10~keV$).
 \cite{peterson59} discovered the first hard X-ray emission during a flare in 1958.
-Later on, it was deduced from the observations of the enhancements observed in radio and hard X-rays that, the the ejected energetic particles may contain a substantial fraction of the initial energy released \citep{brown71}.
-The hard X-ray is created by the bremsstrahlung of the electrons colliding into dense material, resulting in a power-law energy distribution.
-The broadband radio emission from 1 to 100 GHz is created from gyrosynchrotron emission.
-Finally, observations in EUV and soft X-ray($\le$~10~keV) have shown that the energy released form the flare heats the plasma contained in the coronal loops to temperatures beyond 30 MK.
+Later on, it was deduced from the enhancements observed in radio and hard X-rays that the ejected energetic particles may contain a substantial fraction of the initial energy released \citep{brown71}.
+Note that while the hard X-ray is created by the bremsstrahlung radiation of the electrons colliding into dense material, resulting in a power-law energy distribution, the broadband radio emission from 1 to 100 GHz is created from gyrosynchrotron emission.
+Flares are now routinely observed with different space-borne instruments, in particular in the EUV and soft X-ray($\le$~10~keV), which shows that the energy released from the flare heats the local plasma to temperatures beyond 30~MK.
 
 %% ################################################################# %%
-\subsection{Neupert effect}\label{npt_eff}
+%\subsection{Neupert effect}\label{npt_eff} \info{I would not give it a name of new subsection}
 %% ################################################################# %%
 
-\cite{neupert68} observed a curious correlation that, the soft X-ray flux during the rise phase of the flare is proportional to the time integral of the centimeter radio flux since the start of the flare.
-The centimeter radio flux is emitted by relativistic electrons.
-So, later on the same correlation was found between the hard X-ray flux and soft X-ray flux and can be expressed as,
+\cite{neupert68} observed a curious correlation that the soft X-ray flux during the rising phase of the flare is proportional to the time integral of the centimetre radio flux since the start of the flare, suggesting a correlation between thermal plasma and the energetic electrons.
+Note that the centimetre radio flux is emitted by relativistic electrons.
+A similar correlation was found between the hard X-ray and soft X-ray flux later on.
+Such correlation can be expressed as,
 
@@
 
-This empirical relation is known as the ``Neupert effect''.
-\cite{neupert68} had already suggested that this may be due to a causal relationship between the thermal plasma and the energetic electrons.
-The logical explanation is: the soft X-ray mainly originates from a thermal plasma heated by the energy of the flaring event deposited by the flare accelerated electrons.
-It is important to mention that we know now, Eqn.\ref{npt_eff_eq} is only valid if cooling by conduction of radiation is negligible.
+\noindent and is known as the ``Neupert effect''.
+This relationship shows that the soft X-ray radiation primarily originates from a thermal plasma which is heated by the energy of the flaring event deposited by the accelerated electrons.
+We note, however, that Eqn.\ref{npt_eff_eq} is only valid if cooling by conduction is negligible and/or the role of ions in the flare energy deposition is minimal \citep{veronig05}.
 
 %% ################################################################# %%
-\subsection{``Standard'' model of solar flare}\label{sol_flr_std_mod}
+\subsection{``Standard'' model of Solar flare}\label{sol_flr_std_mod}
 %% ################################################################# %%
 
-There were several observations like Neupert effect, which would help us to constrain several phenomenon observed in the flares:
+Based on various multi-wavelength studies of Solar flares, combined with theoretical modelling a `standard' model of Solar flares has been advocated by \cite{carmichael64,sturrock66,hirayama74,kopp76}, and termed as \textsl{CSHKP} model.
+The flares occur due to the abrupt release of magnetic free energy, which was previously stored in the coronal magnetic field via flux emergence and surface motions \citep{forbes06}.
+The majority of the strongest flares are eruptive in nature.
+The `standard' model attributes the release of flare energy to magnetic reconnection in the corona, which happens due to the eruption and/or coronal mass ejection \citep{shibata95,lin_n_forbes00,moore01,priest_n_forbes02}.
+It is noteworthy that, despite continuous attempts over the decades, this is not at all a quantitative model.
+Rather, it is an attempt to unify the multi-wavelength observations and modelling attempts in an orderly manner.
+Naturally, the model can not explain all the observations from various flares.
+A schematic picture of the model is shown in Fig.~\ref{fig:std_mod}.
+Below we describe the salient points of the `standard' model:
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
+\begin{figure}[ht!]
     \centering
-    \includegraphics[width=0.5\linewidth]{Figures/phu_63_8_818_f2.jpg}
-    \caption{A schematic diagram of the standard model of solar flare (adapted from \cite{lysenko20}).}
+    \hspace{5cm}
+    \includegraphics[trim={1cm 8cm 0cm 8cm}, clip, width=0.95\linewidth]{Figures/std_mod.pdf}
+    \caption{A schematic diagram of the standard model of Solar flare.}
+    \label{fig:std_mod}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%
-\begin{enumerate}
-    \item The magnetic reconnetion happens in corona, releasing the magnetic free energy.
-Electrons and energetic particles from the reconnetion site are accelerated along the realigned magnetic field lines.
-The accelerated particles that escape along the open field lines towards the earth gives rise to the particle events seen from earth.
-    \item The accelerated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave observations seen from flares via gyro magnetic radiation.
-    \item The accelerated particles hit the Chromosphere which is considerably denser than the Corona, giving rise to Hard X-ray and gamma ray observed from the foot points.
+
+%\info{This whole description of Standard Model needs to be rewritten.
+You are going too lateral.
+Here, the aim is not to bring out the caveats, etc, but to outline the standard model.
+As you say that you are giving the salient features...
+so just provide that!
+Not more than 2-3 sentences in each bullet.}
+
+%\begin{enumerate}
+    %\item In the standard model, following the reconnection event occurring that releases the magnetic free energy, electrons and ions from the reconnection site are accelerated along the realigned magnetic field lines.
+The accelerated particles that escape along the open \info{field lines do not open during flares!
+Please read Aly and Sturocck paper on this!
+Very interesting concept!} field lines towards the Earth give rise to the particle events seen from Earth \info{which particles are you talking about?
+There are different kinds of particles -- particles accelerated due to shock waves that come very fast ...
+remember proton showers on the detector and other particles which are frozen in the field...
+they come later}.
+The coronal reconnection source where the energy is released is often observed in HXR.
+The loop-top HXR \info{are these same as the reconnection source?} sources are often accompanied by the thermal SXR sources.
+The loop top HXR source is observed above the coronal SXR source \citep{masuda94}.
+Later on, most of the HXR sources were reported to be cospatial with the SXR source \citep{bataglia_n_benz07}.
+This thermal source is distinctly different from the post-flare SXR and EUV loops.
+This thermal coronal source appears before the HXR emission begins, completely contrary to the "Neupert" behaviour.
+This SXR loop top source is a key behaviour of the pre-flare phase.
+The emission measure of these sources is higher than typical coronal levels, suggesting evaporation from the chromosphere before the HXR emission.
+This also suggests that during the early phases of a flare, the energy is conducted gradually by thermal particles, compared to the energetic non-thermal particles later on.
+
+    %Given the existence of the thermal source, the coronal non-thermal source can be explained by a beam of non-thermal particles injected into the dense coronal thermal source.
+Some of the injected electrons escape the coronal source and precipitate lower.
+This model is known as the intermediate thin-thick target model (ITTT, proposed by \cite{wheatland95} and investigated further by \cite{metclaf99,fletcher98}.) While the ITTT model explains most of the observations from flares there are certain inconsistencies regarding the coronal X-ray source {\it e.g.} the source of coronal SXR in preflare conditions, difference in expected HXR brightness of the cornal source from models to observations still elude us.
+It is fair to summarise that even though we by and large understand under what ambient conditions how the coronal HXR source is created, we do not understand what underlying process cause such an environment to arise.
+
+    %\item The precipitated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave and radio observations seen from flares via gyro magnetic radiation at various frequencies dictated by the characteristics of local plasma.
+
+    %\item The accelerated particles hit the chromosphere, which is considerably denser than the corona, giving rise to Hard X-ray and gamma-ray observed from the foot points.
 This also explains why the coronal hard X-ray source is considerably softer than the foot points.
-The energetic particles deposit their energy into the local Chromosphere, as they go through series of collision and eventually thermalize.
-    \item  As the plasma thermalizes, it starts emitting in thermal bremsstrahlung giving rise to the soft X-ray observed.
-Also, as the energy is deposited into the Chromosphere from the accelerated particles, it heats the local Chromosphere environment it gradually increases the local pressure.
-    \item As the pressure grows, when the pressure gradient builds up enough the local plasma starts expanding upwards(essentially due to buoyancy) and slowly fills up the coronal loops with soft X-ray emitting plasma.
+The energetic particles deposit their energy into the local chromosphere as they go through a series of collisions and eventually thermalize \citep{brown83}.
+\sroy{Foot point sources are occasionally detected on H-alpha flare ribbons that are approximately 30,000 km apart, marking the base of a magnetic arcade \citep{masuda01}.}
+
+    %\sroy{$\gamma$-ray emission is visible between 0.8 {--} 20 MeV generated by the accelerated ions.
+The neutron capture line at 2.2 MeV forming Deuterium is usually the strongest characteristic line visible from such emissions.
+Protons and other accelerated ions collide with the dense chromosphere and produce neutrons.
+These neutrons are captured by ambient protons to form Deuteron \citep{ramtay74,hua87}.
+There were later RHESSI observations \citep{hurford_2003,hurford_2006} that showed that the $\gamma$-ray footpoints did not coincide with the HXR footpoints.
+This demonstrated that the ions and electrons were accelerated differently, as proposed by \cite{emslie_2004}.}
+    %\item  As the plasma thermalizes, it emits in thermal bremsstrahlung, giving rise to the soft X-ray \sroy{radiation}.
+Also, as the energy is deposited into the chromosphere from the accelerated particles, it heats the local chromosphere environment it gradually increases the local pressure.
+As the pressure grows, when the pressure gradient builds up enough, the local plasma starts expanding upwards(essentially due to buoyancy) and slowly fills up the coronal loops with soft X-ray emitting plasma.
 This phenomenon is known as "Chromospheric evaporation".
-This was directly observed later on, in blue-shifted lines of hot material.
-    \item This whole scenario explains the Neupert effect.
+This was directly observed in blue-shifted lines of hot material.
+\sroy{This was first reported by \cite{doscheck80,feldman80}.
+\cite{antonucci89} reported velocities of 300 {--} 400 km/s with temperature $\sim$ 20 MK in \ion{Ca}{19}, while later on \cite{milligan06} reported much gentler up-flow with velocities $\sim$ 200 km/s in \ion{Fe}{19} line from {\it SOHO}/CDS observations.
+Several simulations also reproduced evaporation arising from non-thermal particle precipitation \citep{sterling93,hori98,reeves07}.}
+    %\item This whole scenario explains the Neupert effect.
 As the energy form the accelerated particles is converted into the soft X-ray emitting plasma, and it builds up over time.
 That explains the soft X-ray being proportional to the time integral of the hard X-ray flux.
+%\end{enumerate}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%
+\begin{enumerate}
+    \item In the standard model, following the reconnection event occurring that releases the magnetic free energy, electrons and ions from the reconnection site are accelerated along the realigned magnetic field lines downwards.
+In the case of an associated CME, parts of the magnetic energy is deposited as kinetic energy.
+The coronal reconnection source where the energy is released is often observed in HXR.
+The loop-top HXR sources are often accompanied by the thermal SXR sources.
+The loop top HXR source is observed above the coronal SXR source \citep{masuda94}.
+
+    \item The precipitated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave and radio observations seen from flares via gyro magnetic radiation at various frequencies dictated by the characteristics of local plasma.
+
+    \item The accelerated particles hit the chromosphere, which is considerably denser than the corona, giving rise to Hard X-rays and gamma-rays observed from the foot points.
+This also explains why the coronal hard X-ray source is considerably softer than the foot points.
+The energetic particles deposit their energy into the local chromosphere as they go through a series of collisions and eventually thermalize \citep{brown83}.
+Foot point sources are occasionally detected on H-alpha flare ribbons that are approximately 30,000 km apart, marking the base of a magnetic arcade \citep{masuda01}.
+
+    \item $\gamma$-ray emission is visible between 0.8 {--} 20 MeV generated by the accelerated ions.
+The neutron capture line at 2.2 MeV forming Deuterium is usually the strongest characteristic line visible from such emissions.
+Protons and other accelerated ions collide with the dense chromosphere and produce neutrons.
+These neutrons are captured by ambient protons to form Deuteron \citep{ramtay74,hua87}.
+There were later RHESSI observations \citep{hurford_2003,hurford_2006} that showed that the $\gamma$-ray foot-points did not coincide with the HXR foot-points.
+This demonstrated that the ions and electrons were accelerated differently, as proposed by \cite{emslie_2004}.
+
+    \item  The thermalized plasma emits in thermal bremsstrahlung, giving rise to soft X-ray and EUV radiation.
+The heating of the local chromosphere gradually increases the local pressure.
+When the growing pressure gradient builds up enough, the local plasma starts expanding upwards and slowly fills up the coronal loops with soft X-ray-emitting plasma.
+This phenomenon is known as "Chromospheric evaporation".
+This was first reported by \cite{doscheck80,feldman80}.
+\cite{antonucci89} reported velocities of 300 {--} 400 km/s with temperature $\sim$ 20 MK in \ion{Ca}{19}, while later on \cite{milligan06} reported much gentler up-flow with velocities $\sim$ 200 km/s in \ion{Fe}{19} line from {\it SOHO}/CDS observations.
+Several simulations also reproduced evaporation arising from non-thermal particle precipitation \citep{sterling93,hori98,reeves07}.
 \end{enumerate}
@@
 
-This whole scenario is known as the ``Standard'' model of solar flare.
-While the standard model is an attempt to explain and unify various kind of differences seen from the numerous flares we observe, there are several cases where the standard model cannot explain the observations.
-For example, there have been observations of flares where the hard X-ray foot point do not form.
-It is proposed that in these cases the plasma in the coronal loops is so dense that the accelerated particle collide enough to thermalize within the flare loops before reaching the Chromosphere, defusing the energy more evenly within the loop, rather than dumping it at the base of the loops \citep{veronig02,veronig04}.
+It is important to emphasise that while the standard model attempts to explain and unify various kinds of differences seen from the numerous flares we observe, there are several cases where the standard model cannot explain the observations.
+For example, there have been observations of flares where the hard X-ray footpoint does not form.
+It is proposed that in these cases, the plasma in the coronal loops is so dense that the accelerated particles pass through enough collisions to thermalize within the flare loops before reaching the chromosphere.
+In this process, they may defuse the energy more evenly within the loop rather than impulsively dumping it at the base of the loops \citep{veronig02,veronig04}.
 Another flare which previously occurred at the same region might explain the denser coronal loops \citep{strong84,bone07}.
@@
 %% ################################################################# %%
-\subsection{The energectics of solar flares}\label{sol_flr_energ}
+\subsection{The energetics of Solar flares}\label{sol_flr_energ}
 %% ################################################################# %%
 
-With an experience of observing solar flares for more than 150 years, remarkably enough, we have barely started scratching the surface of the complexity involved with the solar flares.
-The re-configuring of magnetic structure, which almost always involves complex geometry, making almost all events unique in some sense.
-After that the released magnetic free energy is transported across various layers of the sun and converted into various other forms of energy.
-Considering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses.
+Given the rich history of flare observations over more than 150 years, remarkably enough, we have barely started scratching the surface of the complexities involved in the physics of Solar flares.
+The reconfiguration of the magnetic structures, which almost always involves complex geometry, makes almost all events unique in some sense.
+Following the reconfiguration of the magnetic field, the released magnetic free energy is transported across various layers of the Sun and converted into various other forms of energy.
+The overarching conversion of magnetic energy into various forms, i.e., reconnection outflow, particle acceleration, thermal and kinetic energy of chromospheric plasma, etc, has proven incredibly complex to model.
+In cases where flares are associated with eruptions, e.g., CMEs, there is the added complexity of the kinetic and potential energy of the CMEs, the associated shocks and the kinetic energy of the Solar energetic particles.
+%Considering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses.
 In case of the eruptive events, there is the added complexity of the kinetic and potential energy of the CMEs, the energy of the shocks and the kinetic energy of the solar energetic particles.
 
-In order to constrain the models of solar eruptions and various nuanced aspects of it, like magnetic reconnection, particle acceleration, heating etc.
-detailed quantitative characterization is absolutely necessary.
-There have been several studies that have tried to quantify the partition between various subsets of the energies.
-The questions that are particularly important are:
+To constrain the models of Solar flares and the various associated phenomena, detailed quantitative characterization is absolutely necessary.
+%There have been several studies quantifying the partition between various subsets of the energies.
+The questions which are of particular importance are:
 
@@
 \begin{itemize}
-    \item \textbf{If an active region can have enough free energy to account for the total energy released in the solar flares and/or CMEs.}
-    \item \textbf{What is the energy partition between flares and CMEs.}
-    \item \textbf{If the non-thermal component have enough energy to power up the thermal component.}
+    \item Do active regions have enough free energy to account for the total energy released in the solar flares and their associated phenomena?
+    \item What is the energy partition between flares and CMEs?
+    \item Do the non-thermal component of flares have enough energy to completely power the thermal component or an extra energy source is required to power the thermal component?
 \end{itemize}
@@
 
-It is generally well known by now that the active region have enough magnetic free energy to power the flare and CME \citep{emslie12,ash17}.
-The partition of energy between the flare and associated CME is much more fuzzy.
-\cite{emslie12} found that the flare and CME have energies of same order of magnitude, while \cite{ash17} concluded the flare dominates the CME in-terms of the energy.
-However the simple question, whether the non-thermal component of the flares have enough energy is still not resolved as even the most recent studies contradict each other in the most puzzling fashion.
-\cite{warmuth20} discussed the contradictions arising from some of the studies\citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17}.
-The details of the studies can be summarized as follows:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{itemize}
+%    \item \textbf{If an active region can have enough free energy to account for the total energy released in the solar flares and/or CMEs.}
+%    \item \textbf{What is the energy partition between flares and CMEs.}
+%    \item \textbf{If the non-thermal component have enough energy to power up the thermal component.}
+%\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+While it is now established the active regions have enough magnetic free energy to power the flare and CME and other associated phenomena  \citep{emslie12,ash17}, the energy partition between the flare and associated CME is much more fuzzy.
+\cite{emslie12} found that the flare and CME have energies of the same order of magnitude, while \cite{ash17} concluded the energy in the flare dominates that of the associated CME.
+
+The question about the non-thermal component having sufficient energy to power the thermal component is still unresolved, as even the most recent studies contradict each other in the most puzzling fashion.
+\cite{warmuth20} discussed the contradictions arising from some of the studies~\citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17}, the details of which are summarized in Table~\ref{tab1}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
+\begin{table}[ht!]
     \centering
+    \resizebox{\textwidth}{!}{%
+    \begin{tabular}{||c|c|c|c|c|c|c||}
     \hline 
     \hline
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{||c|c|c|c|c|c|c||}
        Study & No. of flares & GOES class range & Thermal model & Thermal spectrum & Thermal volume & Thermal losses \\
@@
     \end{tabular}}
-    \caption{The details of the studies.}
+    \caption{Observational summary of the flares as described in \cite{warmuth20}.}
     \label{tab1}
@@
 The bolometric energy serves as a representation of the overall energy released during solar flares.
-Regardless of how energy is released in a solar flare, whether through direct plasma heating, rapid bulk flows, or non thermal particle processes—the ultimate outcome is thermalization and subsequent radiation across the electromagnetic spectrum.
-Given that bolometric energy encompasses the entire spectrum, it is anticipated to reflect the total energy originally released.
-It's important to note that this specifically pertains to the energy liberated within the flare and does not encompass the energy associated with a concurrent coronal mass ejection (CME) or filament eruption.
-\cite{warmuth20} used the bolometric energy released in solar flares, to compare various studies on equal footing.
+Regardless of the mechanism of energy release, e.g., through direct plasma heating, rapid bulk flows, or non-thermal particles, etc., the ultimate outcome is the thermalization of the plasma and the subsequent radiation.
+Since the bolometric energy encompasses the entire electromagnetic spectrum, it reflects the total energy originally of the flare.
+Note, however, that this bolometric energy only pertains to the energy liberated within the flare and does not include the energy associated with the concurrent CME.
+%\cite{warmuth20} used the bolometric energy released in solar flares to compare various studies on equal footing.
 Here we will discuss some of the main issues \cite{warmuth20} identifies comparing these studies.
 
-The calculated thermal energy of all studies show an excellent correlation with the {\it GOES} class.
-Fig.~\ref{fig:goes-therm} left panel shows the peak thermal energy as a function of peak {\it GOES} flux for all the flares from the five studies.
-EM12 and WM16 are consistently one order of magnitude lower than the bolometric energy.
-Interpolation of E12 and WM16 are about half an order of magnitude lower compared to IC14, while S07 is very consistent with the extrapolation.
-The energies of A17 is about an order of magnitude higher compared to other studies, and even higher than the extrapolated bolometric energy for flares of same class from \cite{kretzschmar11} and E12.
-There can be several reason of these differences between the studies arising.
-
-A possible reason can be attributed to different thermal models used to model the thermal component of the flares.
-{\it RHESSI} usually yields a higher temperature and lower emission measure compared to {\it GOES} due to the highly multi thermal nature of the flaring plasma \citep{bataglia05,ryan14,warmuth16a}.
-Although the {\it GOES} temperature is higher by a factor of 1.4, it is not dependant on the flare class.
-Along with that, \cite{warmuth20} also investigated whether assuming a isothermal or multi thermal model introduces any differences in the thermal energy estimates.
-They reported no significant differences due to differences of models (refer to Fig.
-2 and the corresponding discussion in \cite{warmuth20}).
+Fig.~\ref{fig:goes-therm} displays correlation plots between peak thermal energy and peak GOES flux (left panel) for various flares studied by various authors and corresponding (where available) volume estimates of the thermal plasma (right panel).
+The plots show that the estimated thermal energy obtained in all studies shows an excellent correlation with peak {\it GOES} flux.
+Also plotted are the bolometric energies obtained by \cite{emslie12, kretzschmar11}.
+%Fig.~\ref{fig:goes-therm} left panel shows the peak thermal energy as a function of peak {\it GOES} flux for all the flares from the five studies.
+Note that the thermal energy obtained by E12 (open red diamonds) and WM16 (filled black circles) are consistently one order of magnitude lower than the bolometric energy (open green diamonds and solid green line) of flares with similar peak GOES flux.
+Extrapolation of E12 and WM16 is about half an order of magnitude lower compared to IC14 (open blue triangles), while S07 (open pink flipped triangles) is very consistent with the extrapolation.
+Note that the energies estimated in A17 (orange plus signs) are about an order of magnitude higher than that obtained in other studies and even higher than the extrapolated bolometric energy for flares of the same class from \cite{kretzschmar11} and E12.
+These results present a contradiction in the results obtained in different studies.
+While there could be several reasons for these differences, they can be attributed to differences in modelling the thermal component of the flares.
+For example, {\it RHESSI} usually yields a higher temperature and lower emission measure compared to {\it GOES} due to the highly multi-thermal nature of the flaring plasma \citep{bataglia05,ryan14,warmuth16a}.
+Although the {\it GOES} temperature is higher by a factor of 1.4, it is not dependent on the flare class.
+Moreover, \cite{warmuth20} also investigated whether assuming an isothermal or multi-thermal model introduces any differences in the thermal energy estimates.
+They reported no significant differences due to differences in models (refer to Fig.2 and the corresponding discussion in \cite{warmuth20}).
+Notably, these comparisons of isothermal and models are made by fitting spectra obtained by spatially binning spectra.
+This does not really incorporate the multithermal nature of the plasma varying spatially.
 
@@
     \centering
-    \includegraphics[width=0.45\textwidth,trim={0cm 0cm 0cm 0.02cm},clip]{goes_flux_therm.jpg}
-    \includegraphics[width=0.45\textwidth,trim={0cm 0cm 0cm 0.02cm},clip]{goes_flux_vol.jpg}
-    \caption{{\it GOES} peak thermal energy (left panel) and volume of the thermal plasma (right panel) as a function of the peak {\it GOES} flux for all the flares from five studies (figure credit: \cite{warmuth20}).
+    \includegraphics[width=0.49\textwidth,trim={0cm 0cm 0cm 0.02cm},clip]{goes_flux_therm.jpg}
+    \includegraphics[width=0.49\textwidth,trim={0cm 0cm 0cm 0.02cm},clip]{goes_flux_vol.jpg}
+    \caption[Correlation of peak {\it GOES} flux with peak thermal energy and flaring plasma volume.]{{\it GOES} peak thermal energy (left panel) and volume of the thermal plasma (right panel) as a function of the peak {\it GOES} flux for all the flares from five studies (figure credit: \cite{warmuth20}).
 The C values show the linear correlation coefficient for various studies.}
@@
 
-The thermal energy estimated usually depends on the source volume, $U_{Th}\sim V$.
+The thermal energy estimated usually depends on the source volume, $\mathrm{U_{Th}\sim n_{e}k_{B}TVf}$.
+Fig.~\ref{fig:goes-therm} right panel shows the volumes used for various studies to estimate the thermal energy as a function of the peak {\it GOES} flux.
 Apart from S07 and A17, all other studies used {\it RHESSI} imaging to estimate the flare volume with a filling factor $f=1$.
@@
 In contrast, A17 estimated the volume based on the flare area exceeding a certain threshold in the emission measure obtained from the spatial synthesis DEM method.
-Fig.~\ref{fig:goes-therm} right panel shows the volumes used for various studies to estimate the thermal energy as a function of the peak {\it GOES} flux.
+
 It is worth noting that the volume estimates from E12 and WM16 align closely, as do those from A+17, despite employing entirely different methodologies.
@@
 Intriguingly, this discrepancy aligns with the additional volume required to account for the higher thermal energies observed in IC14.
-The uncertainty in detecting volume can be due to the CLEAN algorithm systematically overestimates the source size \citep{warmuth13a}.
-There has also been studies demonstrating that {\it RHESSI} has difficulties in resolving small sources \citep{dennis09,warmuth13b}, that would be applicable for small thermal sources in the micro flares.
+The uncertainty in detecting volume can be due to the CLEAN (Component Least Squares Deconvolution) algorithm systematically overestimating the source size \citep{warmuth13a}.
+There have also been studies demonstrating that {\it RHESSI} has difficulties in resolving small sources \citep{dennis09,warmuth13b}, that would be applicable for small thermal sources in the microflares.
 This illustrates the requirement for better volume estimation for better estimates of the thermal energy of flares.
 
-We can conclude a few more puzzling questions from these studies as a whole:
+We can conclude a few more puzzling questions from these studies as a whole: %\info{These are not questions but more like statements. Please make them questions.}
 
-%%%%%%%%%
+%--------------------------------------------------------------------
 \begin{itemize}
     \item The primary challenge in estimating the thermal energy of the hot plasma stems from determining the temperature distribution of the plasma using Differential Emission Measure (DEM), and the radiating plasma volume.
+How strongly do the uncertainties of determining the thermal energy depend on the uncertainties of the volume estimation and the highly mutithermal nature of the flaring plasma?
     \item The dissipation of energy from the hot plasma is substantial.
 Although there is widespread agreement regarding radiative losses across studies, the extent of conductive losses disagree significantly between the studies.
-    \item The non-thermal energy in injected electrons is strongly dependent on the poorly constrained low-energy cutoff.
+Why do various studies vary so significantly on the extent of conductive losses across the literature and what effect does it have on the thermal evolution of the flares?
+    \item How much do the non-thermal energy in injected electrons depend on the poorly constrained low-energy cutoff?
     \item The thermal and non-thermal energy partition changes with flare class.
-In smaller flares, there appears to be a deficiency of energetic electrons, whereas in larger flares, the injected non-thermal energy seems to sufficient in powering the thermal component.
+In smaller flares, there appears to be a deficiency of energetic electrons, whereas in larger flares, the injected non-thermal energy seems to be sufficient in powering the thermal component.
 Does this signify the existence of an additional third heating source?
 \end{itemize}
-%%%%%%%%%
+%--------------------------------------------------------------------
 
-%% ################################################################# %%
+In the limited scope of this thesis we can only address some aspects of these persisting questions. Here we briefly outline these questions:
+%--------------------------------------------------------------------
+\begin{itemize}
+\item How does the thermal and non-thermal energy partition change over the duration of flares?
+What effect do the uncertainties of volume estimation have, on the thermal energy estimates and what conclusions can we draw from that regarding the tension in the thermal and non-thermal energy sources?
+\item Flares connect various layers of the solar atmosphere via different mechanisms during various stages of its evolution.
+How does the signature of flares look in the NUV regime which mainly originate in the photosphere, chromosphere and transition region.
+The transition region is one of the least observed part of the solar atmosphere in context of flares.
+What is the spectral energy distribution of flares across various wavelength regime and layers, specifically in NUV?
+\end{itemize}
+%--------------------------------------------------------------------
+
+%\info{I would also suggest that you use this section to identifiy all the questions that you are going address in the thesis...
+partition between thermal and non-thermal is one, other is NUV radiation in flare etc...}
+
+%In addition to these, there is one more looming question, related to the "standard" model of flares itself, that has been largely unanswered, not due to lack of efforts, rather limited mostly by the technological limitations dictating the detectability of the current instruments.
+In \S\ref{sol_flr_std_mod}, we discussed about the fundamental differences inferred between the acceleration mechanisms of electrons and ions inferred from the different locations of the HXR and $\gamma$-ray foot points.
+The production of $\gamma$-ray from nuclear reactions in chromosphere opens up the possibility of high-energy nuclear reactions producing pions ($\pi^{0}$ and $\pi^{\pm}$) along with secondary neutrinos ($\nu$) through the decay of the pions.
+Such reactions would be driven by protons with energy $>$ 300 MeV \citep{ramtay75,hudson_n_ryan_95}.
+Detection of neutrinos will open up a new window in constraining the effects of the accelerated particles in the lower solar atmosphere, i.e., chromosphere and photosphere and the general characteristics of the local plasma environment.
+Unfortunately, in spite of considerable efforts no flare neutrinos have been detected so far.
+It is understood that the first hurdle is to detect a minute transient signal on top of the large solar neutrino background.
+This informs our required detection thresholds driven by the current ion acceleration models \citep{sol_nu_kamiokande,abe_2022}.
+If the inability to detect flare neutrinos persists, it indicates that not enough protons/ions with energies $>$ 300 MeV is produced even in very large flares.
+That would impose an upper limit of the amount of energy that is deposited in particle acceleration from flaring events and/or the efficiency of the acceleration mechanism.
+\info{this discussion is good here but not necessary.
+I leave it to you to decide!}
+
+%--------------------------------------------------------------------
 \section{Motivation}\label{sec:mot}
-%% ################################################################# %%
+%--------------------------------------------------------------------
+%\info{This section is what we shall use as the synopsis.
+So, it should have : 1 st para: What are flares and why are they important.
+2nd para: what is know and what is missing (only the most important aspects).
+3rd Para: what is the overall goal, and what extra do you do?
+Just briefly.
+Thereafter Chapter wise summary.}
 
-The main motivation of this thesis is to add understanding of effects of flares on the surrounding environment in lower and upper solar atmosphere, to answer some of the questions posed above.
-We have used imaging and spectroscopic observations from multiple space based observatories ({\it e.g.} AIA, HMI, IRIS, XRT, etc.).
-This research contributes to creating a perspective of flare energetics and its effect on the surrounding plasma environment from Chromosphere to Corona.
+%The main motivation of this thesis is to add understanding of effects of flares on the surrounding environment in lower and upper solar atmosphere, to answer some of the questions posed above.
+We have used imaging and spectroscopic observations from multiple space based observatories, e.g., AIA, HMI, IRIS, XRT, etc.
+This research contributes to creating a perspective of flare energetics and its effect on the surrounding plasma environment from chromosphere to corona.
+\info{again written with Capital C...}
 
-The solar flares are the strongest magnetic event in our solar system connecting various layers of the solar atmosphere ({\it e.g.} from Photosphere to Corona), coupled via mass and energy transport.
-While the Coronal manifestation of solar flares have been studied extensively with several instruments, there are only a few imaging and spectroscopic instruments observing the Photosphere to transition region.
-These include the {\it IRIS} \citep{iris}, AIA 1600, 1700, and 304  {\AA} \citep{aia} and some the filters of {\it Hinode}/SOT \citep{sot}.
-In addition to these, we also have had balloon experiment {\it SUNRISE} \citep{sunrise1,sunrise2}, which provided high resolution imaging of the transition regiopn, from the SuFI instrument \citep{sufi}.
+The solar flares are the strongest magnetic event in our solar system connecting various layers of the solar atmosphere ({\it e.g.} from photosphere to corona), coupled via mass and energy transport.
+While the coronal manifestation of solar flares has been studied extensively with several instruments, there are only a few imaging and spectroscopic instruments observing the photosphere to transition region.
+These include the {\it IRIS} \citep{iris}, AIA 1600, 1700, and 304~{\AA} \citep{aia} and some other filters of {\it Hinode}/SOT \citep{sot}.
+In addition to these, we also have had balloon experiment {\it SunRISE} \citep{Sunrise1,Sunrise2}, which provided high-resolution imaging of the chromosphere, from the SuFI instrument \citep{sufi}.
 
-This illustrates the necessity of more observatories operating at the transition region wavelengths for more comprehensive understanding about how the solar flares manifest and affect the dynamics and heating of the lower solar atmosphere.
+This illustrates the necessity of more observatories operating at the chromospheric wavelengths for a more comprehensive understanding of how the solar flares manifest and affect the dynamics and heating of the lower solar atmosphere.
+More specifically, there is a gap in understanding the spectral energy distribution of flares and the flare signatures in NUV arising from the chromosphere and photosphere.
+
+The main motivation of this thesis is to add an understanding of the effects of flares on the surrounding environment in the lower and upper solar atmosphere to answer some of the questions posed in \S\ref{sol_flr_energ}.
+We have used imaging and spectroscopic observations from multiple space-based observatories, e.g., AIA, HMI, IRIS, XRT, etc.
+This research contributes to creating a perspective of flare energetics and its effect on the surrounding plasma environment from the chromosphere to the corona.
+
+%\info{Shouldn't the above two paragraphs swapped?}
+
+%This illustrates the necessity of more observatories operating at the transition region \info{There is a lot of upper transition region data e.g., 171, what is missing is chromosphere.
+SUIT does not observe transition region} wavelengths for more comprehensive understanding about how the solar flares manifest and affect the dynamics and heating of the lower solar atmosphere.
 In this regard, {\suit} onboard Aditya-L1 will play a crucial role in probing the lower solar atmosphere.
-The various imaging channels of {\suit} would observe the manifestation of flares in transition region at various heights (NB3 $\implies$ \ion{Mg}{2} k 279.6 nm, NB4 $\implies$ \ion{Mg}{2} h 280.3 nm, NB8 $\implies$ \ion{Ca}{2} h 396.8 nm), further lower in the transition region (NB2 $\implies$ blue wing of Mg window, NB5 $\implies$ red wing of Mg window) and Sunspots and possible signature of umbral brightening due to flares at the Photosphere (NB6 300 nm and NB7 388 nm) in full disk.
+The various imaging channels of {\suit} would observe the manifestation of flares in transition region at various heights (NB3 $\implies$ \ion{Mg}{2} k 279.6 nm, NB4 $\implies$ \ion{Mg}{2} h 280.3 nm, NB8 $\implies$ \ion{Ca}{2} h 396.8 nm), further lower in the transition region (NB2 $\implies$ blue wing of Mg window, NB5 $\implies$ red wing of Mg window) and Sunspots and possible signature of umbral brightening due to flares at the photosphere (NB6 300 nm and NB7 388 nm) in full disk.
 This would also allow us to probe the interaction of the flaring region, with other active regions on disk, giving us a comprehensive overview of the effect of solar flares and their manifestation in the lower solar atmosphere.
@@
 It is carried out partly, as various preparatory analysis for {\suit}, forward modelling {\suit} observations, designing the stellar calibration scheme for {\suit}, analysis of existing transition region observations in anticipation of {\suit} observations, analysis of coronal observations of solar flares, and analysis of first solar flare observations by {\suit}.
-Here we will briefly discuss the structure of the rest of the thesis:
+Here, I will briefly discuss the structure of the rest of the thesis:
 
@@
 \begin{itemize}
-    \item In chapter \ref{c:chap2}, we review various space based missions available and used in this thesis.
-We also discuss various analysis techniques used in this thesis.
+
+    \item In chapter \ref{c:chap2}, we review various space based missions and their respective payloads which are used in this thesis.
+We discuss various analysis techniques used in this thesis.
 We also motivate the importance of {\suit} and its main science goals.
-We also briefly discuss the specific questions regarding solar flares we can address with {\suit}.
-    \item In chapter \ref{c:chap3}, we discussed some of the initial preparatory analysis we did for {\suit}, including the throughput model for {\suit}, how the filters mounted on {\suit} were chosen, the analysis of spacecraft jitter simulation and what effect it would have on the imaging.
-We also describe the stellar calibration scheme and the selection criteria for the standard star target.
-We use a sun as a star spectra to evaluate the calibration scheme with the aforementioned throughput model.
+In addition, we briefly discuss the specific questions regarding solar flares we can address with {\suit}.
+
+    \item We address the issues raised in \S\ref{sol_flr_std_mod} regarding the uncertainties of volume estimation for flaring plasma and its effects on the thermal energy estimation in chapter \ref{c:chap3}.
+We use observations from {\it SDO}/AIA, {\it STEREO-A}/EUVI, {\it SO}/STIX, {\it GOES}/SUVI to estimate the thermal energy of two solar flares.
+We propose a method using existing tools, to use observations from different vantages ({\it e.g.} AIA and EUVI from different angles) to accurately calculate the volume of the flare arcade and estimate the thermal energy.
+We show that the accurate estimate as a function of time can have effects on the accurate estimation of thermal energy and the partition between the thermal and non-thermal component.
+
     \item In chapter \ref{c:chap4}, we discuss the forward modelling pipeline developed for {\suit}.
@@
 We also discuss a preliminary version of the deconvolution algorithm that will be deployed in the data reduction pipeline.
-    \item In chapter \ref{c:chap5}, we use existing {\it IRIS} observations of three solar flares to probe how the lower solar atmosphere is affected by the flares.
+
+    \item In chapter \ref{c:chap5}, we discussed some of the initial preparatory analysis we did for {\suit}, including the throughput model for {\suit}, how the filters mounted on {\suit} were chosen, the analysis of spacecraft jitter simulation and what effect it would have on the imaging.
+We also describe the stellar calibration scheme and the selection criteria for the standard star target.
+We use a Sun-as-a-star spectra to evaluate the calibration scheme with the aforementioned throughput model.
+
+    \item In chapter \ref{c:chap6}, we use existing {\it IRIS} observations of three solar flares to probe how the lower solar atmosphere is affected by the flares.
 The ratio of the \ion{Mg}{2} k and h lines, is a proxy for the optical depth of the surrounding plasma.
@@
 We can use a similar method to give full disk context of optical depth, with respect to eruptive events.
-    \item We address the issues raised in \S\ref{sol_flr_std_mod} regarding the uncertainties of volume estimation for flaring plasma and its effects on the thermal energy estimation in chapter \ref{c:chap6}.
-We use observations from {\it SDO}/AIA, {\it STEREO-A}/EUVI, {\it SO}/STIX, {\it GOES}/SUVI to estimate the thermal energy of two solar flares.
-We propose a new  using existing tools, to use observations from different vantages ({\it e.g.} AIA and EUVI from different angles) to accurately calculate the volume of the flare arcade and estimate the thermal energy.
-We show that the accurate estimate as a function of time can have effects on the accurate estimation of thermal energy and the partition between the thermal and non-thermal component.
+
+    \item In Chapter \ref{c:chap7}, we discuss some of the first flares observed by {\suit}.
+First, we report the observation of the limb event on 31st December 2023.
+We see an ejection of a plasma blob from the flaring active region in the NB4 (Mg \Romannum{2} h) pass-band.
+We find that the plasma blob aligned with the bright parts of the ejected loops, as observed from AIA.
+From a DEM analysis we find that the region is denser and cooler compared to the rest of the ejected loop structure.
+Further, we find that the velocity of the ejected plasma is consistent with the observations from AIA 1600 {\AA}.
+The velocity shows a rapid acceleration, which is co-temporal with the development of a kink in the 1600 {\AA} loops.
+The HXR lightcurve is also indicative of ongoing bursty reconnection during this time.
+We believe a bursty reconnection associated with the ejection of chromospheric material can explain the {\suit} observations.
+
+    Next, we discuss the observations of the X-class flare on 22nd February 2024 in chapter 8.
+The flare was associated with penumbral bright kernels observed in NB2 (blue wing of Mg \Romannum{2} window) and NB5 (red wing of Mg \Romannum{2} window).
+The kernels were also observed in HMI WL observations.
+Similar observations were made by \cite{kowalski19} with SJI 2832 {\AA} for a different event.
+They attributed the bright kernels to various photospheric metallic lines going into emission.
+They demonstrated this could be possible due to the electron beam's localised heating in the photosphere.
+We use {\it Chandrayan-2}/XSM observations to show that the appearance of bright kernels does not align with the HXR peak observed from STIX but rather with the photospheric Fe line fluorescence.
+We show the appearance of these photospheric metal lines can also be explained via Fe line fluorescence.
+
+    \item Finally in Chapter \ref{c:chap8} we present a summary of the results obtained in the various projects in context of the overarching perspective of flare energetics and its signature in the chromosphere and photosphere in NUV.
+We also discuss the caveats, the eventual progression of these projects and what new questions they open up.
+Moreover, we also discuss the likely required observations to address the questions regarding flares and which questions they would address.
+   % \item In chapter \ref{c:chap7} we discuss the first flare observations of {\suit}. What do you find? 
 \end{itemize}
+
+%\listoftodos
 %%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-04-11 introduction/intro_2.tex
Local changes

--- 2025-04-11 introduction/intro.tex
@@
 So it is only natural that we try to understand the different physical processes involved in the energetics of the Sun, which directly affects life on Earth.
-In this chapter, I briefly introduce the Sun, various layers of its atmosphere and Solar flares.
+In this chapter, I briefly introduce the Sun, various layers of its atmosphere and solar flares.
 Finally, we provide a motivation for the thesis and a brief outline.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{The Sun}\label{Sun}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The Sun is mostly made out of Hydrogen (92.1\%) and Helium (7.8\%), along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe, among others.
-The study of the Sun can be divided into three components, \textit{viz.} the Solar interior, the Solar atmosphere and the Heliosphere.
+The study of the Sun can be divided into three components, \textit{viz.} the solar interior, the solar atmosphere and the Heliosphere.
 Fig.~\ref{fig_solar_int} shows a schematic diagram of various regions of the Sun.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Solar interior}\label{solar_int} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\info{First you have to say what is the interior! For example the interior is made of three regions -- the core, the radiative zone and the convective zone. The innermost zone, i.e., the core}
-Depending on various physical characteristics, the Solar interior can be divided into three zones {\it e.g.} the core, radiative zone and convective zone.
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Solar Interior}\label{solar_int} 
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Depending on various physical characteristics, the solar interior can be divided into three zones {\it e.g.} the core, radiative zone and convective zone.
 In the innermost zone, the core, the Sun has a temperature of about 15~MK and a density of $\mathrm{1.6\times 10^{5}~km.m^{-3}}$.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Solar atmosphere}\label{solar_atmos}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Solar Atmosphere}\label{solar_atmos}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The layers outside the convection zone together form the Solar atmosphere and is further divided into different regions.
+The layers outside the convection zone together form the solar atmosphere and is further divided into different regions.
 The photosphere, which is also known as the Sun's surface, the chromosphere, the transition region and the corona.
 While we can define geometrical height or depths to define these layers, it is much more useful to define them using the local optical depths of various spectral lines, which are directly used to observe the layers.
-This also gives us an idea about which spectral features originate mainly from which portions of the Solar atmosphere.
-Fig.~\ref{fig_solar_atm} shows the variation of temperature and number density across various layers of the Solar atmosphere \citep{philips08}.
+This also gives us an idea about which spectral features originate mainly from which portions of the solar atmosphere.
+Fig.~\ref{fig_solar_atm} shows the variation of temperature and number density across various layers of the solar atmosphere \citep{philips08}.
 
@@
     \includegraphics[width = 0.8\linewidth]{Figures/solar_atm.png}
-    \caption[Density and temperature profiles across various layers of the Sun.]{The variation of electron temperature (solid line) and electron density ($\mathrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dot-dashed line) in the Solar atmosphere \citep{philips08}.}
+    \caption[Density and temperature profiles across various layers of the Sun.]{The variation of electron temperature (solid line) and electron density ($\mathrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dot-dashed line) in the solar atmosphere \citep{philips08}.}
     \label{fig_solar_atm}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The photosphere}\label{photosphere}
+\subsection{The Photosphere}\label{photosphere}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This is in the green part of the visible spectrum and the Sun is opaque in visible beyond this layer, hence it is called to be the surface of the Sun.
-This layer is 400{--}600~km thick and has an effective temperature of 5780 K.
+This layer is 400{--}600~km thick and has an effective temperature of $\sim$5780~K.
 The magnetic field lines arising from the tachocline penetrate the photosphere and create a `carpet' over the whole region \citep{priest14}.
-As mentioned earlier, this is the Solar surface known as the `quiet Sun'(QS).
-This region exhibits an average magnetic flux density of 10 {--} 50 G.
+As mentioned earlier, this is the solar surface known as the `quiet Sun' (QS).
+This region exhibits an average magnetic flux density of 10{--}50 G.
 The QS surface is covered with cells of roughly four sizes, namely, granules, mesogranules, supergranules and giant cells.
@@
 The Sunspots harbour some of the strongest concentrated magnetic fields, reaching up to several kilogauss in strength.
-The other noteworthy Solar magnetic structure apart from these are believed to be spatially unresolved flux tubes composing a network with field strengths $\sim$ {\it $O(10^{3} G)$}\citep{solanki93,grossman96,rubio19}.
+The other noteworthy solar magnetic structure apart from these are believed to be spatially unresolved flux tubes composing a network with field strengths $\sim$ {\it $O(10^{3} G)$}\citep{solanki93,grossman96,rubio19}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The chromosphere}\label{chromosphere}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The Chromosphere}\label{chromosphere}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The chromosphere is a highly non-uniform dynamic layer with a thickness of 1500 {--} 3000 km, with increasing temperature (up to $10^{4}$ K) and decreasing number density.
+The chromosphere is a highly non-uniform dynamic layer with a thickness of 1500{--}3000~km, with increasing temperature (up to $10^{4}$ K) and decreasing number density.
 As seen in Fig.~\ref{fig_solar_atm}, the temperature of the chromosphere saturates before the dramatic rise in the transition region.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The corona}\label{corona}
+\subsection{The Corona}\label{corona}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The outermost layer of the atmosphere is the corona.
-The corona maintains a temperature of 1-2~MK during ambient conditions but can rise up to tens of MK during explosive eruptions such as Solar flares.
+The corona maintains a temperature of 1-2~MK during ambient conditions but can rise up to tens of MK during explosive eruptions such as solar flares.
 Due to such high temperatures, the coronal gas is fully ionized.
-It is only visible to the naked eye during the total Solar eclipse or with coronagraphs due to Thomson scattering of the photosphere with free electrons in the corona.
-corona also emits in various emission lines, e.g.
-Mg, Fe, Si, S, Ca, O, etc., across a wide band of electromagnetic spectrum ranging from X-ray to visible wavelengths.
+It is only visible to the naked eye during the total solar eclipse or with coronagraphs due to Thomson scattering of the photospheric visible photons with free electrons in the corona.
+Corona also emits in various emission lines of e.g.
+Mg, Fe, Si, S, Ca, O, etc.
+and their ions, across a wide band of electromagnetic spectrum ranging from X-ray to visible wavelengths.
 Similar to the other layers, the corona exhibits a variety of structures such as ARs, coronal holes, bright points, filaments, and flares.
@@
 
-Solar flares are the most powerful energetic explosions in the Solar system.
+solar flares are the most powerful energetic explosions in the solar system.
 They are described as a sudden increase in brightness in localized areas of the Sun.
@@
 It has been estimated that the amount of flare energy released is comparable to the free energy stored in the magnetic system \citep{emslie12,ash17}.
-%The term "flare" is generally used explicitly for the entire magnetically-driven event's electromagnetic radiation, as it is the most significant fraction of the total energy liberated.
-The total energy released varies from event to event. It is also known that larger events occur much less frequently than smaller events.
+The total energy released varies from event to event.
+It is also known that larger events occur much less frequently than smaller events.
 
-Fig.~\ref{fig:sji_features} displays one of the most well-known and well-studied Solar eruptions from Aug 31st, 2012.
+Fig.~\ref{fig:sji_features} displays one of the most well-known and well-studied solar eruptions from Aug 31st, 2012.
 During this event, an associated giant prominence erupted from the southeast limb, which was visible in all AIA channels as shown in Fig.~\ref{fig:aia-feature}.
-The sunspots were also clearly visible and labelled in the HMI continuum (see Fig.~\ref{fig:aia-feature}h).
+The sunspots are also clearly visible and labelled in the HMI continuum (see Fig.~\ref{fig:aia-feature}h).
 In Fig.~\ref{fig:aia-feature}i, we show the co-aligned AIA 304 {\AA} and HMI continuum observation.
-The Sunspots lie at the base of the erupted prominence, accompanied by the hot thermal plasma associated with the accompanying flare (visible in Fig.~\ref{fig:aia-feature}e {--} f).
+The prominences are rooted at the sunspot penumbra, accompanied by the hot thermal plasma associated with the accompanying flare (visible in Fig.~\ref{fig:aia-feature} e {--} f).
 The novelty of such observation lies in the clear spatial connection across various layers of the Sun, connected via energy and momentum transported from one layer to the other.
@@
 Carrington and R.
-Hodgson independently observed the first flare in white-light continuum~\citep{carrington1859,hodgson1859}.
+Hodgson independently observed the first flare in white-light continuum \citep{carrington1859, hodgson1859}.
 Such localized brightening on the Sun has remained an enigma ever since.
@@
 No two events were similar, as there were variations observed in the size of the source, ejections of plasma, and shock waves driving into the interplanetary space.
-Advances in radio technology during the Second World War affirmed the detection of the presence of non-thermal electrons in the Solar corona during military radar operations \citep{hey46}.
+Advances in radio technology during the Second World War affirmed the detection of the presence of non-thermal electrons in the solar corona during military radar operations \citep{hey46}.
 Around the same time, S.E.
-Forbrush noticed ground-level cosmic ray enhancement during major Solar flares.
+Forbrush noticed ground-level cosmic ray enhancement during major solar flares.
 These discoveries eluded that the flaring events do not only involve the thermal plasma but somehow connect with high energy particles and involve the corona.
 
-In the late 1950s, using rockets and balloons, the Sun was observed with hard X-rays ($\ge~10~keV$).
+In the late 1950s, using rockets and balloons, the Sun was observed in hard X-rays ($\ge10~keV$).
 \cite{peterson59} discovered the first hard X-ray emission during a flare in 1958.
@@
 This relationship shows that the soft X-ray radiation primarily originates from a thermal plasma which is heated by the energy of the flaring event deposited by the accelerated electrons.
-We note, however, that Eqn.\ref{npt_eff_eq} is only valid if cooling by conduction is negligible and/or the role of ions in the flare energy deposition is minimal \citep{veronig05}.
+We note, however, that Eqn.~\ref{npt_eff_eq} is only valid if cooling by conduction is negligible and/or the role of ions in the flare energy deposition is minimal \citep{veronig05}.
 
 %% ################################################################# %%
-\subsection{``Standard'' model of Solar flare}\label{sol_flr_std_mod}
+\subsection{``Standard'' model of solar flare}\label{sol_flr_std_mod}
 %% ################################################################# %%
 
-Based on various multi-wavelength studies of Solar flares, combined with theoretical modelling a `standard' model of Solar flares has been advocated by \cite{carmichael64,sturrock66,hirayama74,kopp76}, and termed as \textsl{CSHKP} model.
+Based on various multi-wavelength studies of solar flares, combined with theoretical modelling a `standard' model of solar flares has been advocated by \cite{carmichael64,sturrock66,hirayama74,kopp76}, and termed as \textsl{CSHKP} model.
 The flares occur due to the abrupt release of magnetic free energy, which was previously stored in the coronal magnetic field via flux emergence and surface motions \citep{forbes06}.
@@
     \includegraphics[trim={1cm 8cm 0cm 8cm}, clip, width=0.95\linewidth]{Figures/std_mod.pdf}
-    \caption{A schematic diagram of the standard model of Solar flare.}
+    \caption{A schematic diagram of the standard model of solar flare.}
     \label{fig:std_mod}
@@
 \begin{enumerate}
-    \item In the standard model, following the reconnection event occurring that releases the magnetic free energy, electrons and ions from the reconnection site are accelerated along the realigned magnetic field lines downwards.
+    \item In the standard model, following the reconnection event that releases the magnetic free energy, electrons and ions from the reconnection site are accelerated along the realigned magnetic field lines downwards.
 In the case of an associated CME, parts of the magnetic energy is deposited as kinetic energy.
@@
 
-    \item The precipitated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave and radio observations seen from flares via gyro magnetic radiation at various frequencies dictated by the characteristics of local plasma.
-
-    \item The accelerated particles hit the chromosphere, which is considerably denser than the corona, giving rise to Hard X-rays and gamma-rays observed from the foot points.
+    \item The accelerated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave and radio observations seen from flares via gyro magnetic radiation at various frequencies dictated by the characteristics of local plasma.
+Finally, the accelerated particles hit the chromosphere, which is considerably denser than the corona, giving rise to Hard X-rays and sometimes also gamma-rays observed from the foot points.
 This also explains why the coronal hard X-ray source is considerably softer than the foot points.
 The energetic particles deposit their energy into the local chromosphere as they go through a series of collisions and eventually thermalize \citep{brown83}.
-Foot point sources are occasionally detected on H-alpha flare ribbons that are approximately 30,000 km apart, marking the base of a magnetic arcade \citep{masuda01}.
+Foot point sources are occasionally detected on H-alpha flare ribbons marking the base of a magnetic arcade \citep{masuda01}.
+The ribbon brightening is usually observed to propagate along the ribbons while they separate further from each other, signifying continued reconnection \citep{tripathi06}.
 
-    \item $\gamma$-ray emission is visible between 0.8 {--} 20 MeV generated by the accelerated ions.
+    \item $\gamma$-ray emission from solar flares is visible between 0.8 {--} 20 MeV generated by the accelerated ions.
 The neutron capture line at 2.2 MeV forming Deuterium is usually the strongest characteristic line visible from such emissions.
-Protons and other accelerated ions collide with the dense chromosphere and produce neutrons.
-These neutrons are captured by ambient protons to form Deuteron \citep{ramtay74,hua87}.
-There were later RHESSI observations \citep{hurford_2003,hurford_2006} that showed that the $\gamma$-ray foot-points did not coincide with the HXR foot-points.
+Flare-accelerated protons and ions colliding with the dense chromosphere can produce neutrons.
+It is suggested that these neutrons are captured by ambient protons to form Deuteron, giving rise to the 2.2 MeV characteristic bump \citep{ramtay74,hua87}.
+Later, RHESSI observations \citep{hurford_2003,hurford_2006} showed that the $\gamma$-ray foot-points did not coincide with the HXR foot-points.
 This demonstrated that the ions and electrons were accelerated differently, as proposed by \cite{emslie_2004}.
@@
     \item  The thermalized plasma emits in thermal bremsstrahlung, giving rise to soft X-ray and EUV radiation.
-The heating of the local chromosphere gradually increases the local pressure.
-When the growing pressure gradient builds up enough, the local plasma starts expanding upwards and slowly fills up the coronal loops with soft X-ray-emitting plasma.
-This phenomenon is known as "Chromospheric evaporation".
+The heating of the local chromosphere increases the local pressure.
+When the growing pressure gradient builds up enough, the local plasma expands upwards and fills up the coronal loops with soft X-ray-emitting plasma.
+This phenomenon is known as "chromospheric evaporation".
 This was first reported by \cite{doscheck80,feldman80}.
@@
 It is important to emphasise that while the standard model attempts to explain and unify various kinds of differences seen from the numerous flares we observe, there are several cases where the standard model cannot explain the observations.
-For example, there have been observations of flares where the hard X-ray footpoint does not form.
+For example, there have been observations of flares where the hard X-ray footpoint does not form \citep{veronig02,veronig04}.
 It is proposed that in these cases, the plasma in the coronal loops is so dense that the accelerated particles pass through enough collisions to thermalize within the flare loops before reaching the chromosphere.
-In this process, they may defuse the energy more evenly within the loop rather than impulsively dumping it at the base of the loops \citep{veronig02,veronig04}.
+In this process, they may defuse the energy more evenly within the loop rather than impulsively dumping it at the base of the loops.
 Another flare which previously occurred at the same region might explain the denser coronal loops \citep{strong84,bone07}.
@@
 %% ################################################################# %%
-\subsection{The energetics of Solar flares}\label{sol_flr_energ}
+\section{Motivation of the thesis: the energetics of solar flares}\label{sol_flr_energ}
 %% ################################################################# %%
 
-Given the rich history of flare observations over more than 150 years, remarkably enough, we have barely started scratching the surface of the complexities involved in the physics of Solar flares.
+Given the rich history of flare observations over more than 150 years, we have learnt a lot about their charactershtics and dyamics.
+However, there are several complexities involved in the physics of solar flares, which are still fully understood.
 The reconfiguration of the magnetic structures, which almost always involves complex geometry, makes almost all events unique in some sense.
 Following the reconfiguration of the magnetic field, the released magnetic free energy is transported across various layers of the Sun and converted into various other forms of energy.
-The overarching conversion of magnetic energy into various forms, i.e., reconnection outflow, particle acceleration, thermal and kinetic energy of chromospheric plasma, etc, has proven incredibly complex to model.
-In cases where flares are associated with eruptions, e.g., CMEs, there is the added complexity of the kinetic and potential energy of the CMEs, the associated shocks and the kinetic energy of the Solar energetic particles.
+The overarching conversion of magnetic energy into various forms, i.e., reconnection outflow, particle acceleration, thermal and kinetic energy of chromospheric plasma, etc., has proven incredibly complex to model.
+In cases where flares are associated with eruptions, e.g., CMEs, there is the added complexity of the kinetic and potential energy of the CMEs, the associated shocks and the kinetic energy of the solar energetic particles.
 %Considering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses.
@@
 
-To constrain the models of Solar flares and the various associated phenomena, detailed quantitative characterization is absolutely necessary.
+To constrain the models of solar flares and the various associated phenomena, detailed quantitative characterization is absolutely necessary.
 %There have been several studies quantifying the partition between various subsets of the energies.
@@
 Note that the energies estimated in A17 (orange plus signs) are about an order of magnitude higher than that obtained in other studies and even higher than the extrapolated bolometric energy for flares of the same class from \cite{kretzschmar11} and E12.
-These results present a contradiction in the results obtained in different studies.
+
+The above described results present a contradiction in the results obtained in different studies.
 While there could be several reasons for these differences, they can be attributed to differences in modelling the thermal component of the flares.
@@
 
-The thermal energy estimated usually depends on the source volume, $\mathrm{U_{Th}\sim n_{e}k_{B}TVf}$.
+The thermal energy is estimated using $$\mathrm{U_{Th}\sim n_{e}k_{B}TVf}$$
+\noindent where n$_e$ is the electron density, k$_B$ is Boltzmann's constant, T is the temperature, V is the volume of the flaring plasma, and f is the filling factor.
+
  Fig.~\ref{fig:goes-therm} right panel shows the volumes used for various studies to estimate the thermal energy as a function of the peak {\it GOES} flux.
@@
 There have also been studies demonstrating that {\it RHESSI} has difficulties in resolving small sources \citep{dennis09,warmuth13b}, that would be applicable for small thermal sources in the microflares.
-This illustrates the requirement for better volume estimation for better estimates of the thermal energy of flares.
+%This illustrates the requirement for better volume estimation for better estimates of the thermal energy of flares.
 
-We can conclude a few more puzzling questions from these studies as a whole: %\info{These are not questions but more like statements. Please make them questions.}
+From the above-described studies, it is clear that there are number of questions that are crucial to describe the physics of solar flares. We allude to these below.
+
+%We can conclude a few more puzzling questions from these studies as a whole: %\info{These are not questions but more like statements. Please make them questions.}
 
@@
 
-In the limited scope of this thesis we can only address some aspects of these persisting questions. Here we briefly outline these questions:
+In the limited scope of this thesis address the following pressing questions through multiwavelength observations and contribution in the development of new instruments:
 %--------------------------------------------------------------------
@@
 What effect do the uncertainties of volume estimation have, on the thermal energy estimates and what conclusions can we draw from that regarding the tension in the thermal and non-thermal energy sources?
+
 \item Flares connect various layers of the solar atmosphere via different mechanisms during various stages of its evolution.
@@
 %--------------------------------------------------------------------
-\section{Motivation}\label{sec:mot}
+%\section{Motivation}\label{sec:mot}. 
 %--------------------------------------------------------------------
@@
 
-The solar flares are the strongest magnetic event in our solar system connecting various layers of the solar atmosphere ({\it e.g.} from photosphere to corona), coupled via mass and energy transport.
+%The solar flares are the strongest magnetic event in our solar system connecting various layers of the solar atmosphere ({\it e.g.} from photosphere to corona), coupled via mass and energy transport.
 While the coronal manifestation of solar flares has been studied extensively with several instruments, there are only a few imaging and spectroscopic instruments observing the photosphere to transition region.
@@
 In addition to these, we also have had balloon experiment {\it SunRISE} \citep{Sunrise1,Sunrise2}, which provided high-resolution imaging of the chromosphere, from the SuFI instrument \citep{sufi}.
+\textbf{where are you using Sunrise?}
 
-This illustrates the necessity of more observatories operating at the chromospheric wavelengths for a more comprehensive understanding of how the solar flares manifest and affect the dynamics and heating of the lower solar atmosphere.
+%This illustrates the necessity of more observatories operating at the chromospheric wavelengths for a more comprehensive understanding of how the solar flares manifest and affect the dynamics and heating of the lower solar atmosphere.
 More specifically, there is a gap in understanding the spectral energy distribution of flares and the flare signatures in NUV arising from the chromosphere and photosphere.
 
-The main motivation of this thesis is to add an understanding of the effects of flares on the surrounding environment in the lower and upper solar atmosphere to answer some of the questions posed in \S\ref{sol_flr_energ}.
+%The main motivation of this thesis is to add an understanding of the effects of flares on the surrounding environment in the lower and upper solar atmosphere to answer some of the questions posed in \S\ref{sol_flr_energ}.
 We have used imaging and spectroscopic observations from multiple space-based observatories, e.g., AIA, HMI, IRIS, XRT, etc.
@@
 
-The work within this thesis spans across various layers of the solar atmosphere to understand how solar flare couples these layers.
-It is carried out partly, as various preparatory analysis for {\suit}, forward modelling {\suit} observations, designing the stellar calibration scheme for {\suit}, analysis of existing transition region observations in anticipation of {\suit} observations, analysis of coronal observations of solar flares, and analysis of first solar flare observations by {\suit}.
-Here, I will briefly discuss the structure of the rest of the thesis:
+This thesis primarily focuses on studies of solar flares and their signatures in various layers of the solar atmosphere by using multi-wavelength observation and contribution to the development of the solar Ultraviolet Imaging Telescope (SUIT) on board the Aditya-L1 mission.
+The rest of the thesis is structured as follows:
 
@@
 
-    \item In chapter \ref{c:chap2}, we review various space based missions and their respective payloads which are used in this thesis.
-We discuss various analysis techniques used in this thesis.
-We also motivate the importance of {\suit} and its main science goals.
-In addition, we briefly discuss the specific questions regarding solar flares we can address with {\suit}.
+	\item Chapter~\ref{c:chap2}: To perform various studies in this thesis, we have used observations from several instruments.
+Moreover, we have used several techniques to analyse the data and derive physical parameters from these observations.
+Therefore, we dedicate this chapter to providing relevant details of each instrument we have used.
+Moreover, we discuss the analysis techniques by providing relevant details and salient features.
+We emphasise the {\suit} instrument, mention its primary science goals, and briefly discuss the specific questions that {\suit} can address regarding solar flares.
 
-    \item We address the issues raised in \S\ref{sol_flr_std_mod} regarding the uncertainties of volume estimation for flaring plasma and its effects on the thermal energy estimation in chapter \ref{c:chap3}.
-We use observations from {\it SDO}/AIA, {\it STEREO-A}/EUVI, {\it SO}/STIX, {\it GOES}/SUVI to estimate the thermal energy of two solar flares.
-We propose a method using existing tools, to use observations from different vantages ({\it e.g.} AIA and EUVI from different angles) to accurately calculate the volume of the flare arcade and estimate the thermal energy.
-We show that the accurate estimate as a function of time can have effects on the accurate estimation of thermal energy and the partition between the thermal and non-thermal component.
+	\item Chapter~\ref{c:chap3}: This chapter addresses the partition between solar flares' thermal and non-thermal energy and their time evolution in two flares.
+For this purpose, we use multi-wavelength observations from two vantage points recorded by {\it SDO}/AIA, {\it STEREO-A}/EUVI, {\it SO}/STIX, {\it GOES}/SUVI.
+Using existing tools and the observations from two vantage points, we propose a new method to accurately calculate the volume of the flaring plasma, which is a crucial parameter in the derivation of thermal energy.
+We demonstrate that an accurate estimate of the volume of flaring plasma as a function of time can affect the accurate estimation of thermal energy and, therefore, will have significant implications on the partition between the thermal and non-thermal energy components.
 
-    \item In chapter \ref{c:chap4}, we discuss the forward modelling pipeline developed for {\suit}.
-We use MPS-Atlas simulation and {\it IRIS} observations, with measured transmission profiles of various optical components and the PSF to forward model {\suit} observations.
-We also discuss a preliminary version of the deconvolution algorithm that will be deployed in the data reduction pipeline.
+	\item Chapter~\ref{c:chap4}: Here we discuss some of the initial preparatory analysis we performed for {\suit} instrument, including the throughput model, selection of science filters, modelling of the spacecraft jitter and its effects on the imaging performance of the instrument.
+We also describe a scheme for absolute calibration using standard stars like Vega and Sirius.
+For this purpose, we have used Sun-as-a-star spectra combined with the instrument's throughput model to evaluate the calibration scheme.
 
-    \item In chapter \ref{c:chap5}, we discussed some of the initial preparatory analysis we did for {\suit}, including the throughput model for {\suit}, how the filters mounted on {\suit} were chosen, the analysis of spacecraft jitter simulation and what effect it would have on the imaging.
-We also describe the stellar calibration scheme and the selection criteria for the standard star target.
-We use a Sun-as-a-star spectra to evaluate the calibration scheme with the aforementioned throughput model.
+	\item Chapter~\ref{c:chap5}: Having derived the instrument model for SUIT, we now forward the model to the expected observations the instrument will record.
+For this purpose, we use MPS-Atlas simulation and {\it IRIS} observations, with measured transmission profiles of various optical components and the PSF.
 
-    \item In chapter \ref{c:chap6}, we use existing {\it IRIS} observations of three solar flares to probe how the lower solar atmosphere is affected by the flares.
-The ratio of the \ion{Mg}{2} k and h lines, is a proxy for the optical depth of the surrounding plasma.
-Hence, we use the observations of \ion{Mg}{2} lines along HMI magnetic field measurements to investigate the effects of magnetic field, if any.
-\cite{kerr15} conducted a similar study and found signatures of localised heating in the line intensity ratio.
-We found, that the line intensity ratio shows a correlated increase and decrease with the flare light curve.
-We argue this to be signature of plasma flow associated with flare, and a change in density of the local environment.
-This acts as a prelude of what is achievable with {\suit}.
-We can use a similar method to give full disk context of optical depth, with respect to eruptive events.
+	\item Chapter~\ref{c:chap6}: The two filters, among 11, that SUIT has are tuned to observe the Mg~\Romannum{2}~h~\&~k lines.
+Therefore, in preparation for SUIT, we study three flares belonging to three different classes, namely X, M and C, observed by IRIS in spectroscopy mode.
+We study the ratio of the two spectral lines \textit{viz.}, Mg~\Romannum{2}~h~\&~k for the three flares.
+The ratio of the Mg \Romannum{2}~k\&~h lines is a proxy for the optical depth of the surrounding plasma.
+We found that the line intensity ratio shows a correlated increase and decrease with the flare light curve.
+We argue this to be the signature of plasma flow associated with flare and a change in the density of the local environment.
+%Such studies could b This acts as a prelude of what is achievable with {\suit}.
+We can use a similar method to give full disk context of optical depth with respect to eruptive events.
 
-    \item In Chapter \ref{c:chap7}, we discuss some of the first flares observed by {\suit}.
-First, we report the observation of the limb event on 31st December 2023.
-We see an ejection of a plasma blob from the flaring active region in the NB4 (Mg \Romannum{2} h) pass-band.
-We find that the plasma blob aligned with the bright parts of the ejected loops, as observed from AIA.
-From a DEM analysis we find that the region is denser and cooler compared to the rest of the ejected loop structure.
-Further, we find that the velocity of the ejected plasma is consistent with the observations from AIA 1600 {\AA}.
-The velocity shows a rapid acceleration, which is co-temporal with the development of a kink in the 1600 {\AA} loops.
-The HXR lightcurve is also indicative of ongoing bursty reconnection during this time.
-We believe a bursty reconnection associated with the ejection of chromospheric material can explain the {\suit} observations.
+	\item Chapter~\ref{c:chap7}: The SUIT instrument was switched on Nov 20th, 2023, while still in the cruise phase, with a first light on December 6th.
+The spacecraft was inserted into the halo orbit around L1 point on Jan 06, 2024.
+Since the first light, it has detected several flares, both with and without getting into flare mode.
+In this Chapter, we discuss the first flare observed on Feb 22, 2024, after enabling the flare detection algorithm.
+We discuss the first results and show the capabilities of the SUIT instrument for flare physics.
 
-    Next, we discuss the observations of the X-class flare on 22nd February 2024 in chapter 8.
-The flare was associated with penumbral bright kernels observed in NB2 (blue wing of Mg \Romannum{2} window) and NB5 (red wing of Mg \Romannum{2} window).
-The kernels were also observed in HMI WL observations.
-Similar observations were made by \cite{kowalski19} with SJI 2832 {\AA} for a different event.
-They attributed the bright kernels to various photospheric metallic lines going into emission.
-They demonstrated this could be possible due to the electron beam's localised heating in the photosphere.
-We use {\it Chandrayan-2}/XSM observations to show that the appearance of bright kernels does not align with the HXR peak observed from STIX but rather with the photospheric Fe line fluorescence.
-We show the appearance of these photospheric metal lines can also be explained via Fe line fluorescence.
+    \item Chapter~\ref{c:chap8}: Finally, we summarize the results obtained in the various projects in the context of the overarching perspective of flare energetics and its signature in the chromosphere and photosphere in NUV.
+We also discuss the caveats and the eventual progression of these projects, as well as the future prospects.
 
-    \item Finally in Chapter \ref{c:chap8} we present a summary of the results obtained in the various projects in context of the overarching perspective of flare energetics and its signature in the chromosphere and photosphere in NUV.
-We also discuss the caveats, the eventual progression of these projects and what new questions they open up.
-Moreover, we also discuss the likely required observations to address the questions regarding flares and which questions they would address.
+	% and what new questions they open up. Moreover, we also discuss the likely required observations to address the questions regarding flares and which questions they would address.
    % \item In chapter \ref{c:chap7} we discuss the first flare observations of {\suit}. What do you find? 
 \end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2025-04-11 main_thesis_file.tex
Local changes

@@
 % use "plain" for committee to read, or for printing single-spaced in general
-\documentclass[keepsake]{hvdthesis}
+\documentclass[plain]{hvdthesis}
 
@@
 
-\author{Soumya Roy}
-\title{Dynamics of the Lower Solar Atmosphere}
+\author{Soumya Roy | {\lbng \*s*eoumYo ray}}
+\title{Solar Flares Across the Spectrum: Observations and Instrumentation}
 \department{Jawaharlal Nehru University, New Delhi, India}
@@
 % include the dissertation acceptance form
-\includepdf[pages={1}]{placeholder_dac.pdf}
+% \includepdf[pages={1}]{placeholder_dac.pdf}
 
@@
 
+\newpage
+
+\includepdf[pages={1,2,3}]{placeholder_dac.pdf}
 \newpage
@@
 {\centerline {\em every time I was about to give up!}}
-{\centerline {\em And to my younger self, who was brave enogh to embark on this journey...}}
+{\centerline {\em And to my younger self, who was brave enough to embark on this journey...}}
 %\vskip 1.5cm
@@
 \chapter[Introduction]{Introduction}\label{c:intro}
-\input{./introduction/intro}
+\input{./introduction/intro_2}
 \clearpage
@@
 \chaptermark{Solar Observatories and Analysis Techniques}
-\input{./chapter2/ms.tex}
+\input{./chapter2/chap2_2}
 \clearpage
 %
-\chapter{Intital preparatory analysis for SUIT}\label{c:chap3}
+\chapter{Estimating thermal energy of two Solar Flares}\label{c:chap3}
+\chaptermark{Solar flare energy}
+%\begin{quote}
+%{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
+%{authors,
+%{\em journal reference info}}
+%\end{quote}
+\input{./chapter3/chap3}
+\clearpage
+
+\chapter{Forward modelling SUIT observations}\label{c:chap4}
+\chaptermark{SUIT forward model}
+%\begin{quote}
+%{\em ~~~~~~~This thesis chapter originally appeared in the literature as} 
+%{authors,
+%{\em journal reference info}}
+%\end{quote}
+\input{./chapter4/chap4}
+%
+\chapter{Intital preparatory analysis for SUIT}\label{c:chap5}
+
 \chaptermark{SUIT preparatory analysis}
-\input{./chapter3/ms.tex}
+\begin{quote}
+    { \em~~~~~~~This thesis chapter originally appeared in the literature as} \\
+{{\em {\bf Photometric calibration and spectral validation of
+the Solar Ultraviolet Imaging Telescope onboard
+Aditya-L1}, Sarkar, J., Roy, S., Ramaprakash, A.N., et.
+al.,  2025,  J.
+Astron.
+Telesc.
+Instrum.
+Syst.
+11(1), 014005 (2025), doi:\href{https://www.spiedigitallibrary.org/journals/Journal-of-Astronomical-Telescopes-Instruments-and-Systems/volume-11/issue-1/014005/Photometric-calibration-and-spectral-validation-of-the-Solar-Ultraviolet-Imaging/10.1117/1.JATIS.11.1.014005.short}{10.1117/1.JATIS.11.1.014005}.}
+\end{quote}
+\input{./chapter5/chap5}
 \clearpage
 %
-\chapter{Forward modelling SUIT observations}\label{c:chap4}
-\chaptermark{SUIT forward model}
-\begin{quote}
-{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
-{authors,
-{\em journal reference info}}
-\end{quote}
-\input{./chapter4/ms.tex}
 
 %
-\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap5}
+\chapter{Effects of Solar flares on the local plasma environment from Mg II observations}\label{c:chap6}
 \chaptermark{Solar flares Mg II}
@@
 { ~~~~~~~This thesis chapter originally appeared in the literature as} \\
-{{\em The Evolution of the Ratio of \ion{Mg}{2} Intensities During Solar Flares, Roy, S., \& Tripathi, D.
+{{\em {\bf The Evolution of the Ratio of \ion{Mg}{2} Intensities During Solar Flares}, Roy, S., \& Tripathi, D.
 2024, ApJ, 964, 106, doi:\href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}}.}
 \end{quote}
-\input{./chapter5/ms.tex}
-\clearpage
-%
-\chapter{Estimating thermal energy of two Solar Flares}\label{c:chap6}
-\chaptermark{Solar flare energy}
-\begin{quote}
-{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
-{authors,
-{\em journal reference info}}
-\end{quote}
-\input{./chapter6/ms.tex}
+\input{./chapter6/chap6}
 \clearpage
@@
 \chapter{First flares observed by {\suit}}\label{c:chap7}
-\chaptermark{First Flares observed with SUIT}
-\begin{quote}
-{\em ~~~~~~~This thesis chapter originally appeared in the literature as} \\
-{authors,
-{\em journal reference info}}
-\end{quote}
-\input{./chapter7/ms.tex}
+\chaptermark{First flares}
+%\begin{quote}
+{\em ~~~~~~~This thesis chapter originally appeared in the literature as}\\ 
+{{\em {\bf Near- and Mid-ultraviolet Observations of X-6.3 Flare on 2024 February 22 Recorded by the Solar Ultraviolet Imaging Telescope on board Aditya-L1}, Roy, S., Tripathi, D., Padinhatteeri, S., \& Ramaprakash, A.
+N., et.
+al., 2024, ApJL, 981, L19, doi:\href{https://iopscience.iop.org/article/10.3847/2041-8213/adb0be}{10.3847/2041-8213/adb0be}}.}
+%{authors,
+%{\em journal reference info}}
+%\end{quote}
+\input{./chapter7/chap7_2}
 \clearpage
 %
+%
+\chapter{Echoes of the Solar Inferno: Summary and Future Prospects}\label{c:chap8}
+\chaptermark{Summary \& Outlook}
+\input{./Outlook/outlook_2}
+\clearpage
+%
+\appendix
+\chapter{Calculation of Oscillator strengths for the Mg~\Romannum{2}~k~\&~h lines}\label{c:a1}
+\chaptermark{Oscilator Strength Calculation}
+\input{./Appendix1/a1}
+\clearpage
 
-\chapter{Echoes of the Solar Inferno: Summary and Future Prospects}\label{c:chap8}
-\chaptermark{Outlook}
-\input{./chapter8/ms.tex}
+\chapter{Modifications of the cold thick target model}\label{c:a2}
+\chaptermark{Kappa Distribution Fit}
+\input{./Appendix1/a2}
 \clearpage

### 2025-04-11 pub.tex
Local changes

@@
 \begin{itemize}
-    \item Soumya Roy and Durgesh Tripathi, 2024, ApJ, 964, 106, doi: \href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}
+    \item ``Evolution of the Ratio of \ion{Mg}{2} Intensities during Solar Flares", {\bf Soumya Roy} and Durgesh Tripathi, 2024, ApJ, 964, 106, doi: \href{https://iopscience.iop.org/article/10.3847/1538-4357/ad2a46}{10.3847/1538-4357/ad2a46}\footnotemark[1]
+    \item ``Near and Mid-ultraviolet Observations of X-6.3 Flare on 2024 February 22 Recorded by the Solar Ultraviolet Imaging Telescope on board Aditya-L1", {\bf Soumya Roy}, Durgesh, Tripathi, Sreejith, P, \& Ramaprakash, A.
+N., et.
+al., 2024, ApJL, 981, L19, doi:\href{https://iopscience.iop.org/article/10.3847/2041-8213/adb0be}{10.3847/2041-8213/adb0be}\footnotemark[1]
+    \item ``Photometric Calibration \& Spectral Validation of the Solar Ultraviolet Imaging Telescope onboard Aditya-L1", Janmejoy Sarkar, {\bf Soumya Roy}, A.
+N.
+Ramaprakash,...
+2024, J.
+Astron.
+Telesc.
+Instrum.
+Syst.
+11(1), 014005 (2025), doi:\href{https://www.spiedigitallibrary.org/journals/Journal-of-Astronomical-Telescopes-Instruments-and-Systems/volume-11/issue-1/014005/Photometric-calibration-and-spectral-validation-of-the-Solar-Ultraviolet-Imaging/10.1117/1.JATIS.11.1.014005.short}{10.1117/1.JATIS.11.1.014005}\footnotemark[1]
+    \item ``Science Filter Characterization of the Solar Ultraviolet Imaging Telescope (SUIT) on board Aditya-L1", Janmejoy Sarkar, Rushikesh Deogaonkar, Ravi Kesharwani, ...
+{\bf Soumya Roy},...
+2024, Exp.
+Astron., 59, 3 (2025), doi: \href{https://doi.org/10.1007/s10686-024-09973-5}{10.1007/s10686-024-09973-5}
+    \item ``Solar Ultraviolet Imaging Telescope on board Aditya-L1", Durgesh Tripathi, A.
+N.
+Ramaprakash, Sreejith P,...
+{\bf Soumya Roy},...
+2025, Sol.
+Phys., 300, 30, \href{10.1007/s11207-025-02423-1}{10.1007/s11207-025-02423-1}\footnotemark[1]
+    \item ``X-class flare on Dec 31, 2023, observed by the Solar Ultraviolet Imaging Telescope", {\bf Soumya Roy}, Durgesh Tripathi, Sreejith P, \& A.
+N.
+Ramaprakash, et.
+al., 2025, ApJL, 983, L6, \href{https://doi.org/10.3847/2041-8213/adc387}{10.3847/2041-8213/adc387}
+    \item ``Test and Calibration of the Solar Ultraviolet
+Imaging Telescope (SUIT) on board Aditya-L1", Janmejoy Sarkar, Nived V. N., {\bf Soumya Roy}, Rushikesh Deogaonkar et al., 2025, Accepted for publication in Sol. Phys.
+
+\end{itemize}
+%%%%%%%%%%%
+
+\section*{Submitted Articles}
+
+%%%%%%%%%%%
+\begin{itemize}
+    \item ``Evolution of thermal and cumulative non-thermal energy in solar flares", {\bf Soumya Roy}, Sophie Musset, Katharine K.
+Reeves, Durgesh Tripathi, Christopher S.
+Moore, 2024, Submitted to ApJ\footnotemark[1]{}\footnotetext{Part of this thesis}
+    \item ``Forward Modeling Observations of the Solar Ultraviolet Imaging Telescope (SUIT) on board Aditya-L1", {\bf Soumya Roy}, L.
+S.
+Anusha, Durgesh Tripathi, et al.
+2024, Submitted to ApJ\footnotemark[1]{}\footnotetext{Part of this thesis}
+    %\item ``Critical Science Plan of the Solar Ultraviolet Imaging Telescope (SUIT) onboard Aditya-L1 mission", Durgesh Tripathi, A. N. Ramaprakash, ... {\bf Soumya Roy}, in Preparation
 \end{itemize}
@@
     \item Roy, S., et al., "Solar Ultraviolet Imaging Telescope (SUIT) Handbook", ISRO Aditya-L1 mission
-    \item Roy, S., et al., "Estimation of Effects of Space-craft Jitter on SUIT Imaging", ISRO Aditya-L1 mission
+    \item Roy, S., et al., "Estimation of Effects of Space-craft Jitter on SUIT Imaging", ISRO Aditya-L1 mission\footnotemark[1]{}
 \end{itemize}
